### 2022-05-10 analysis/gafo-cc-analysis.Rmd
add first round of data

---
title: "Gafo-cc-analysis"
output: html_document
date: '2022-03-26'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(brms)
```

```{r}
mdata <- read_csv("../data/gafo-cc-clean-data.csv")%>%
  mutate(ageinyears = scale(ageinyears),
         targetcentralityx = scale(targetcentralityx),
         trialnr = scale(trialnr),
         children = scale(children),
         youngerchildren = scale(youngerchildren),
         touchscreen = factor(touchscreen.x),
        screen = factor(screen))
```

```{r}
bm_base <- brm(abs(clickdistfromtargetcenterx) ~ ageinyears  + targetcentralityx + (trialnr|subjid), 
                              data   = mdata, 
                              family = Gamma(link = "log"),
                              warmup = 1000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4)%>%
  add_criterion(., c("waic","loo"))

bm_null <- brm(abs(clickdistfromtargetcenterx) ~ 1 + (trialnr|subjid), 
                              data   = mdata, 
                              family = Gamma(link = "log"),
                              warmup = 1000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4)%>%
  add_criterion(., c("waic","loo"))

loo_compare(bm_base, bm_null)%>%as_tibble(rownames = "model")

```

```{r}
plot(bm_age)

pp_check(bm_age)+xlim(0,2000)

bm_age
```

```{r}
bm_screen <- brm(abs(clickdistfromtargetcenterx) ~ ageinyears  + targetcentralityx + screen + (trialnr|subjid), 
                              data   = mdata, 
                              family = Gamma(link = "log"),
                              warmup = 1000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4)%>%
  add_criterion(., c("waic","loo"))

bm_touch <- brm(abs(clickdistfromtargetcenterx) ~ ageinyears  + targetcentralityx + touchscreen + (trialnr|subjid), 
                              data   = mdata, 
                              family = Gamma(link = "log"),
                              warmup = 1000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4)%>%
  add_criterion(., c("waic","loo"))
```

```{r}
bm_child <- brm(abs(clickdistfromtargetcenterx) ~ ageinyears  + targetcentralityx + children + (trialnr|subjid), 
                              data   = mdata, 
                              family = Gamma(link = "log"),
                              warmup = 1000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4)%>%
  add_criterion(., c("waic","loo"))

bm_young <- brm(abs(clickdistfromtargetcenterx) ~ ageinyears  + targetcentralityx + youngerchildren + (trialnr|subjid), 
                              data   = mdata, 
                              family = Gamma(link = "log"),
                              warmup = 1000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4)%>%
  add_criterion(., c("waic","loo"))
```

### 2022-05-10 analysis/gafo-cc-data-processing.Rmd
add first round of data

---
title: "Gafo-cc data processing"
output: html_document
---

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(prettyR) # for describe()
library(jsonlite) # for reading in json files
library(stringr)
library(eeptools)
library(lubridate) # for date handling
library(readxl)

options(scipen = 999)
theme_set(theme_classic())
```

# Namibia

```{r read_data}
# get all .json files
files <- list.files("../../raw_data/gafo-cc/namibia/", pattern = "*.json",recursive = T)

# convert json files to tibbles
raw_data_namibia <- tibble()
for (f in files) {
  jf <- paste("../../raw_data/gafo-cc/namibia/", f, sep = "")
  jd <- jsonlite::fromJSON(paste(readLines(jf, warn = "FALSE"), collapse = ""))

  # needed because hedge trials have numbers, box trials have characters
  jd$targetPosition <- factor(as.character(jd$targetPosition))

  raw_data_namibia <- bind_rows(raw_data_namibia, jd)
}
# remove variables that we don't need anymore
rm(f, files, jf, jd)
```

```{r}
tidy_data_namibia <- raw_data_namibia %>%

  # convert all character vectors into factors
  mutate_if(is.character, as.factor) %>%

  mutate(

    # attention! the SVG coord system starts with 0, 0 in upper left corner
    # we transform the values so that 0, 0 is lower left corner (for plots etc)
    clickScaledY = 1080 - clickScaledY,
    targetY = 1080 - targetY, 
    targetCenterY = 1080 - targetCenterY, 
    eyeCenterRightY = 1080 - eyeCenterRightY,
    eyeCenterLeftY = 1080 - eyeCenterLeftY,
    pupilFinalRightY = 1080 - pupilFinalRightY,
    pupilFinalLeftY = 1080 - pupilFinalLeftY, 
    targetCentralityX = abs(960 - targetCenterX),

    # similarly here: in svg coords, negative click distance means up. 
    # here we invert it, so that negative values mean down
    clickDistFromTargetCenterY = clickDistFromTargetCenterY * -1, 
    clickDistFromTargetBBoxY = clickDistFromTargetBBoxY * -1,

    # positive values for inward clicks (i.e.,towards the center), negative for outward clicks
    centralityBias = ifelse(targetCenterX <= 1920/2,
                            clickDistFromTargetCenterX, 
                            clickDistFromTargetCenterX*-1),

    inwardClick = ifelse(centralityBias > 0, TRUE, FALSE),

    # did the participant click on the right box?
    # also for hedge version, here we imagine a box surrounding the target center 
    # this way, we can compare hedge and box version ;) 
    boxWidth = 218, 
    boxBorderLeft = targetCenterX - boxWidth/2, 
    boxBorderRight = targetCenterX + boxWidth/2,
    correctBox = ifelse(boxBorderLeft <= clickScaledX & clickScaledX <= boxBorderRight, TRUE, FALSE),

    datacollection = as.factor("in-person - supervised"), 
    sample = as.factor("na"),
    studytype = as.factor("vali"), 
  ) 
```

```{r demographics}
raw_demographics_namibia <- bind_rows(
  read_xlsx("../../raw_data/gafo-cc/namibia/Data FarmSix 2022.xlsx", sheet = 1)%>%mutate(ID = paste0("H",str_pad(ID, 7, pad = "0"))),
  read_xlsx("../../raw_data/gafo-cc/namibia/Data Khwe 2022.xlsx", sheet = 1)%>%mutate(ID = paste0("K",str_pad(ID, 7, pad = "0")))%>%rename(sex = `...7`)
  )

tidy_demographics_namibia <- raw_demographics_namibia %>% 
  mutate(
    ageInYears = as.numeric(difftime(TestDate,BirthDate, units = "days")/365.25),
  ) %>%
  rename(subjID = ID) %>% 
  select(-c(`First Name`, Name, BirthDate, TestDate, Comment))%>% 
  rename_all(tolower)%>%
  filter(!is.na(ageinyears))
```

```{r}
data_namibia <- tidy_demographics_namibia%>%
  left_join(tidy_data_namibia%>%rename_all(tolower),by = c("subjid"))
```

# Leipzig

```{r}
system("rsync -zaP ccp-odcJ:/srv/ccp-odc/gafo-leipzig/data/ ~/Work/Local/Quantex/Gafo/raw_data/gafo-cc/leipzig/")
```

```{r read_data}
# get all .json files
files <- list.files("../../raw_data/gafo-cc/leipzig/", pattern = "*.json",recursive = T)

# convert json files to tibbles
raw_data_leipzig <- tibble()
for (f in files) {
  jf <- paste("../../raw_data/gafo-cc/leipzig/", f, sep = "")
  jd <- jsonlite::fromJSON(paste(readLines(jf, warn = "FALSE"), collapse = ""))

  # needed because hedge trials have numbers, box trials have characters
  jd$targetPosition <- factor(as.character(jd$targetPosition))

  raw_data_leipzig <- bind_rows(raw_data_leipzig, jd)
}
# remove variables that we don't need anymore
rm(f, files, jf, jd)
```

```{r}
tidy_data_leipzig <- raw_data_leipzig %>%

  # convert all character vectors into factors
  mutate_if(is.character, as.factor) %>%

  mutate(

    # attention! the SVG coord system starts with 0, 0 in upper left corner
    # we transform the values so that 0, 0 is lower left corner (for plots etc)
    clickScaledY = 1080 - clickScaledY,
    targetY = 1080 - targetY, 
    targetCenterY = 1080 - targetCenterY, 
    eyeCenterRightY = 1080 - eyeCenterRightY,
    eyeCenterLeftY = 1080 - eyeCenterLeftY,
    pupilFinalRightY = 1080 - pupilFinalRightY,
    pupilFinalLeftY = 1080 - pupilFinalLeftY, 
    targetCentralityX = abs(960 - targetCenterX),

    # similarly here: in svg coords, negative click distance means up. 
    # here we invert it, so that negative values mean down
    clickDistFromTargetCenterY = clickDistFromTargetCenterY * -1, 
    clickDistFromTargetBBoxY = clickDistFromTargetBBoxY * -1,

    # positive values for inward clicks (i.e.,towards the center), negative for outward clicks
    centralityBias = ifelse(targetCenterX <= 1920/2,
                            clickDistFromTargetCenterX, 
                            clickDistFromTargetCenterX*-1),

    inwardClick = ifelse(centralityBias > 0, TRUE, FALSE),

    # did the participant click on the right box?
    # also for hedge version, here we imagine a box surrounding the target center 
    # this way, we can compare hedge and box version ;) 
    boxWidth = 218, 
    boxBorderLeft = targetCenterX - boxWidth/2, 
    boxBorderRight = targetCenterX + boxWidth/2,
    correctBox = ifelse(boxBorderLeft <= clickScaledX & clickScaledX <= boxBorderRight, TRUE, FALSE),

    datacollection = as.factor("in-person - supervised"), 
    sample = as.factor("na"),
    studytype = as.factor("vali"), 
  ) %>%
  mutate(subjID = as.character(subjID),
         subjID = ifelse(subjID == "VcyYgGQx", "VcyYgFQx", subjID),
         subjID = ifelse(subjID == "R9V7qHrx", "R9v7qHrx", subjID),
         subjID = ifelse(subjID == "QZJvSwfQ","QZJvSwftQ",  subjID),
         subjID = ifelse(subjID == "TSPeVFYf", "tSPeVFYf", subjID),
         subjID =as.factor(subjID))

#unique(tidy_data_leipzig$subjID)
```

```{r demographics}
raw_demographics_leipzig <- bind_rows(
  read_xlsx("../../../../../Cloud/QuantEx/Gafo-cc/docs/Gafo-cc-leipzig-participants.xlsx", sheet = 1)
  )

tidy_demographics_leipzig <- raw_demographics_leipzig %>% 
  mutate(
    test_date = as.Date(test_date, format = "%d/%m/%Y"),
    birth_date = as.Date(birth_date, origin = "1899-12-30"),
    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
  ) %>%
  select(-c(first_name, last_name, id, test_date, birth_date))%>%
  rename(subjid = code)%>%
  filter(!is.na(ageinyears),
         status == "keep")
```

```{r}
tidy_demographics_leipzig%>%
  filter(!subjid %in% tidy_data_leipzig$subjID)
```

```{r}
data_leipzig <- tidy_demographics_leipzig%>%
  left_join(tidy_data_leipzig%>%rename_all(tolower),by = c("subjid"))%>%
  distinct(subjid, trialnr, .keep_all = TRUE)

```

```{r}
data_leipzig%>%
  group_by(subjid)%>%
  summarise(n())

```

# Nigeria

```{r read_data}
# get all .json files
files <- list.files("../../../../../Cloud/QuantEx/Gafo-cc/data/nigeria/", pattern = "*.json",recursive = T)

# convert json files to tibbles
raw_data_nigeria <- tibble()
for (f in files) {
  jf <- paste("../../../../../Cloud/QuantEx/Gafo-cc/data/nigeria/", f, sep = "")
  jd <- jsonlite::fromJSON(paste(readLines(jf, warn = "FALSE"), collapse = ""))

  # needed because hedge trials have numbers, box trials have characters
  jd$targetPosition <- factor(as.character(jd$targetPosition))

  raw_data_nigeria <- bind_rows(raw_data_nigeria, jd)
}
# remove variables that we don't need anymore
rm(f, files, jf, jd)
```

```{r}
tidy_data_nigeria <- raw_data_nigeria %>%

  # convert all character vectors into factors
  mutate_if(is.character, as.factor) %>%

  mutate(

    # attention! the SVG coord system starts with 0, 0 in upper left corner
    # we transform the values so that 0, 0 is lower left corner (for plots etc)
    clickScaledY = 1080 - clickScaledY,
    targetY = 1080 - targetY, 
    targetCenterY = 1080 - targetCenterY, 
    eyeCenterRightY = 1080 - eyeCenterRightY,
    eyeCenterLeftY = 1080 - eyeCenterLeftY,
    pupilFinalRightY = 1080 - pupilFinalRightY,
    pupilFinalLeftY = 1080 - pupilFinalLeftY, 
    targetCentralityX = abs(960 - targetCenterX),

    # similarly here: in svg coords, negative click distance means up. 
    # here we invert it, so that negative values mean down
    clickDistFromTargetCenterY = clickDistFromTargetCenterY * -1, 
    clickDistFromTargetBBoxY = clickDistFromTargetBBoxY * -1,

    # positive values for inward clicks (i.e.,towards the center), negative for outward clicks
    centralityBias = ifelse(targetCenterX <= 1920/2,
                            clickDistFromTargetCenterX, 
                            clickDistFromTargetCenterX*-1),

    inwardClick = ifelse(centralityBias > 0, TRUE, FALSE),

    # did the participant click on the right box?
    # also for hedge version, here we imagine a box surrounding the target center 
    # this way, we can compare hedge and box version ;) 
    boxWidth = 218, 
    boxBorderLeft = targetCenterX - boxWidth/2, 
    boxBorderRight = targetCenterX + boxWidth/2,
    correctBox = ifelse(boxBorderLeft <= clickScaledX & clickScaledX <= boxBorderRight, TRUE, FALSE),

    datacollection = as.factor("in-person - supervised"), 
    sample = as.factor("na"),
    studytype = as.factor("vali"), 
  ) 
```

```{r demographics}
raw_demographics_nigeria <- bind_rows(
  read_xlsx("../../../../../Cloud/QuantEx/Gafo-cc/data/nigeria/gafo-cc-nigeria-participants.xlsx", sheet = 1)
  )

tidy_demographics_nigeria <- raw_demographics_nigeria %>% 
  mutate(
    test_date = as.Date(test_date, format = "%d.%m.%Y"),
    birth_date = as.Date(birth_date, format = "%d.%m.%Y"),
    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
  )  %>%
  select(-c(first_name, last_name, test_date, birth_date, `...14`, `...15`, comment))%>%
  rename(subjid = id)%>%
  filter(!is.na(ageinyears))
```

```{r}
data_nigeria <- tidy_demographics_nigeria%>%
  left_join(tidy_data_nigeria%>%rename_all(tolower),by = c("subjid"))
```

# Merge
```{r}

data <- bind_rows(
  data_namibia,
  data_leipzig,
  data_nigeria
)%>%
  #mutate(community = paste0("c",as.character(as.numeric(as.factor(community)))))%>%
  filter(trialtype == "test")

data%>%
  group_by(community)%>%
  summarise(n= n_distinct(subjid))

```
```{r}
write_csv(data,"../data/gafo-cc-clean-data.csv")
```

### 2022-05-10 analysis/gafo-cc-visuals.Rmd
add first round of data

---
title: "Gafo-cc visuals"
output: html_document
---

```{r}
library(tidyverse)
library(ggpubr)
library(ggthemes)
library(tidyboot)
```

```{r}
data <- read_csv("../data/gafo-cc-clean-data.csv")
```

```{r}
data%>%
  group_by(community,subjid, ageinyears)%>%
  summarise(impr = mean(abs(clickdistfromtargetcenterx)))%>%
  ggplot(aes(x = ageinyears, y = impr, col = community))+
  geom_point(pch = 1)+
  geom_smooth(method = "lm")+
  scale_color_colorblind()+
  ylim(0,1000)+
  labs(x = "Age (in years)", y ="Imprecision")+
  scale_x_continuous(breaks = 2:8)+
  theme_minimal()

```

```{r}
data%>%
  group_by(targetcentralityx)%>%
  #summarise(impr = mean(clickdistfromtargetcenterx))%>%
  mutate(chance_upper = (targetcentralityx + 960)/2,
         chance_lower = -((targetcentralityx + 960)/2))%>%
  ggplot(aes(x = targetcentralityx, y = clickdistfromtargetcenterx))+
  geom_hline(yintercept = 0, lty = 3, alpha = 0.75)+
  #geom_line(aes(x = targetcentralityx, y = chance_upper), lty = 3, alpha = .75, col = "firebrick")+
  #geom_line(aes(x = targetcentralityx, y = chance_lower), lty = 3, alpha = .75, col = "firebrick")+
  geom_point(pch = 1, alpha = 0.75)+
  #ylim(-1500,1500)+
  theme_minimal()

```

```{r}
ptp <- data%>%
  mutate(targetposition = factor(targetposition, levels = c(1:10)))%>%
  group_by(community, targetposition)%>%
  tidyboot_mean(col= abs(clickdistfromtargetcenterx))

ggplot(ptp, aes(x = targetposition, y = mean, col = community))+
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .2))+
  labs(x = "Binned target position", y = "Mean imprecision")+
  #ylim(0,1000)+
  theme_minimal()
```

### 2022-06-04 analysis/gafo-cc-analysis.Rmd
add data

@@
 library(brms)
+library(tidybayes)
 ```
@@
          children = scale(children),
+         household = scale(household),
          youngerchildren = scale(youngerchildren),
-         touchscreen = factor(touchscreen.x),
+         touchscreen = factor(touchscreen),
         screen = factor(screen))
+
+unique(mdata$community)
 ```
@@
 ```{r}
-bm_base <- brm(abs(clickdistfromtargetcenterx) ~ ageinyears  + targetcentralityx + (trialnr|subjid), 
+bm_base <- brm(abs(clickdistfromtargetcenterx) ~ ageinyears  + targetcentralityx + (trialnr|subjid) + (1|community), 
                               data   = mdata, 
@@
 
-bm_null <- brm(abs(clickdistfromtargetcenterx) ~ 1 + (trialnr|subjid), 
+bm_null <- brm(abs(clickdistfromtargetcenterx) ~ 1 + (trialnr|subjid)+ (1|community), 
                               data   = mdata, 
@@
 ```{r}
-plot(bm_age)
+plot(bm_base)
 
-pp_check(bm_age)+xlim(0,2000)
+pp_check(bm_base)
 
@@
 ```{r}
-bm_screen <- brm(abs(clickdistfromtargetcenterx) ~ ageinyears  + targetcentralityx + screen + (trialnr|subjid), 
+ps <- bm_base%>%posterior_samples()%>%
+  select(starts_with("r_community"))%>%
+  pivot_longer(cols = everything(), names_to = "param", values_to = "value")%>%
+  filter(grepl("Intercept", param))
+
+ggplot(ps,aes(y = param, x = value)) +
+ stat_halfeye(alpha = .7, .width = c(.95, .80)) +
+    labs(x = "Posterior estimate", y ="")+
+  guides(fill = "none")+
+  #geom_vline(xintercept = 0, linetype = "dashed") +
+  xlim(-0.2, 0.5)+
+  theme_minimal()
+```
+
+```{r}
+bm_screen <- brm(abs(clickdistfromtargetcenterx) ~ ageinyears  + targetcentralityx  + (1|subjid) + (screen + children + household|community), 
+                              data   = mdata%>%filter(community != "chimfunshi_kumwenda"), 
+                              family = Gamma(link = "log"),
+                              warmup = 1000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4)%>%
+  add_criterion(., c("waic","loo"))
+
+bm_touch <- brm(abs(clickdistfromtargetcenterx) ~ ageinyears  + targetcentralityx + (1|subjid) + (1|community), 
                               data   = mdata, 
@@
 
-bm_touch <- brm(abs(clickdistfromtargetcenterx) ~ ageinyears  + targetcentralityx + touchscreen + (trialnr|subjid), 
-                              data   = mdata, 
-                              family = Gamma(link = "log"),
-                              warmup = 1000, 
-                              iter   = 4000, 
-                              chains = 4, 
-                              cores  = 4)%>%
-  add_criterion(., c("waic","loo"))
+```
+```{r}
+ps <- bm_screen%>%posterior_samples()%>%
+  select(starts_with("r_community"))%>%
+  pivot_longer(cols = everything(), names_to = "param", values_to = "value")%>%
+  filter(grepl("Intercept", param))
+
+ggplot(ps,aes(y = param, x = value)) +
+ stat_halfeye(alpha = .7, .width = c(.95, .80)) +
+    labs(x = "Posterior estimate", y ="")+
+  guides(fill = "none")+
+  #geom_vline(xintercept = 0, linetype = "dashed") +
+  xlim(-0.2, 0.5)+
+  theme_minimal()
 ```

### 2022-06-04 analysis/gafo-cc-data-processing.Rmd
add data

@@
 library(readxl)
+library(readODS)
 
@@
     studytype = as.factor("vali"), 
-  ) 
+  ) %>%
+  select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
 ```
@@
          subjID = ifelse(subjID == "TSPeVFYf", "tSPeVFYf", subjID),
-         subjID =as.factor(subjID))
+         subjID =as.factor(subjID))%>%
+  select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
 
@@
     test_date = as.Date(test_date, format = "%d/%m/%Y"),
-    birth_date = as.Date(birth_date, origin = "1899-12-30"),
+    birth_date = as.Date(birth_date, format = "%d.%m.%Y"),
     ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
@@
 # get all .json files
-files <- list.files("../../../../../Cloud/QuantEx/Gafo-cc/data/nigeria/", pattern = "*.json",recursive = T)
+files <- list.files("../../../../../Cloud/QuantEx/Gafo-cc/data/nigeria/JSONs/", pattern = "*.json",recursive = T)
 
@@
 for (f in files) {
-  jf <- paste("../../../../../Cloud/QuantEx/Gafo-cc/data/nigeria/", f, sep = "")
+  jf <- paste("../../../../../Cloud/QuantEx/Gafo-cc/data/nigeria/JSONs/", f, sep = "")
   jd <- jsonlite::fromJSON(paste(readLines(jf, warn = "FALSE"), collapse = ""))
@@
     studytype = as.factor("vali"),
-  ) 
+    subjID = as.character(subjID),
+    subjID = ifelse(subjID == "nlger002", "niger002", subjID)
+  ) %>%
+  select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
 ```
@@
 tidy_demographics_nigeria <- raw_demographics_nigeria %>% 
+  filter(community!= "leipzig")%>%
   mutate(
+    birth_date = ifelse(birth_date == "10.11.1016", "10.11.2016", birth_date),
     test_date = as.Date(test_date, format = "%d.%m.%Y"),
@@
 data_nigeria <- tidy_demographics_nigeria%>%
-  left_join(tidy_data_nigeria%>%rename_all(tolower),by = c("subjid"))
+  left_join(tidy_data_nigeria%>%rename_all(tolower),by = c("subjid"))%>%
+  mutate(location = community,
+         community = "akure")
+```
+
+# Zambia
+
+```{r read_data}
+# get all .json files
+files <- list.files("../../../../../Cloud/QuantEx/Gafo-cc/data/zambia/", pattern = "*.json",recursive = T)
+
+# convert json files to tibbles
+raw_data_zambia <- tibble()
+for (f in files) {
+  jf <- paste("../../../../../Cloud/QuantEx/Gafo-cc/data/zambia/", f, sep = "")
+  jd <- jsonlite::fromJSON(paste(readLines(jf, warn = "FALSE"), collapse = ""))
+
+  # needed because hedge trials have numbers, box trials have characters
+  jd$targetPosition <- factor(as.character(jd$targetPosition))
+
+  raw_data_zambia <- bind_rows(raw_data_zambia, jd)
+}
+# remove variables that we don't need anymore
+rm(f, files, jf, jd)
+```
+
+```{r}
+tidy_data_zambia <- raw_data_zambia %>%
+
+  # convert all character vectors into factors
+  mutate_if(is.character, as.factor) %>%
+
+  mutate(
+
+    # attention! the SVG coord system starts with 0, 0 in upper left corner
+    # we transform the values so that 0, 0 is lower left corner (for plots etc)
+    clickScaledY = 1080 - clickScaledY,
+    targetY = 1080 - targetY, 
+    targetCenterY = 1080 - targetCenterY, 
+    eyeCenterRightY = 1080 - eyeCenterRightY,
+    eyeCenterLeftY = 1080 - eyeCenterLeftY,
+    pupilFinalRightY = 1080 - pupilFinalRightY,
+    pupilFinalLeftY = 1080 - pupilFinalLeftY, 
+    targetCentralityX = abs(960 - targetCenterX),
+
+    # similarly here: in svg coords, negative click distance means up. 
+    # here we invert it, so that negative values mean down
+    clickDistFromTargetCenterY = clickDistFromTargetCenterY * -1, 
+    clickDistFromTargetBBoxY = clickDistFromTargetBBoxY * -1,
+
+    # positive values for inward clicks (i.e.,towards the center), negative for outward clicks
+    centralityBias = ifelse(targetCenterX <= 1920/2,
+                            clickDistFromTargetCenterX, 
+                            clickDistFromTargetCenterX*-1),
+
+    inwardClick = ifelse(centralityBias > 0, TRUE, FALSE),
+
+    # did the participant click on the right box?
+    # also for hedge version, here we imagine a box surrounding the target center 
+    # this way, we can compare hedge and box version ;) 
+    boxWidth = 218, 
+    boxBorderLeft = targetCenterX - boxWidth/2, 
+    boxBorderRight = targetCenterX + boxWidth/2,
+    correctBox = ifelse(boxBorderLeft <= clickScaledX & clickScaledX <= boxBorderRight, TRUE, FALSE),
+
+    datacollection = as.factor("in-person - supervised"), 
+    sample = as.factor("na"),
+    studytype = as.factor("vali")
+  ) %>%
+  select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
+```
+
+```{r demographics}
+raw_demographics_zambia <- bind_rows(
+  read_ods("../../../../../Cloud/QuantEx/Gafo-cc/data/zambia/gafo-cc-sambia-participants.ods", sheet = 1)
+  )
+
+tidy_demographics_zambia <- raw_demographics_zambia %>% 
+  filter(community!= "leipzig")%>%
+  mutate(
+    test_date = as.Date(test_date, format = "%d/%m/%Y"),
+    birth_date = as.Date(birth_date, format = "%d/%m/%Y"),
+    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
+  )  %>%
+  select(-c(first_name, last_name, test_date, birth_date, comment))%>%
+  rename(subjid = id)%>%
+  filter(!is.na(ageinyears))
+```
+
+```{r}
+data_zambia <- tidy_demographics_zambia%>%
+  left_join(tidy_data_zambia%>%rename_all(tolower),by = c("subjid"))%>%
+  mutate(community = "chimfunshi_kumwenda")
 ```
@@
   data_leipzig,
-  data_nigeria
+  data_nigeria,
+  data_zambia
 )%>%
@@
 ```
+
 ```{r}

### 2022-06-04 analysis/gafo-cc-visuals.Rmd
add data

@@
 data%>%
+  group_by(community)%>%
+  summarise(n= n_distinct(subjid))
+```
+
+```{r}
+data%>%
   group_by(community,subjid, ageinyears)%>%
@@
   geom_point(pch = 1)+
-  geom_smooth(method = "lm")+
+  geom_smooth(method = "glm")+
   scale_color_colorblind()+
@@
 ggplot(ptp, aes(x = targetposition, y = mean, col = community))+
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .2))+
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
   labs(x = "Binned target position", y = "Mean imprecision")+
+  scale_color_colorblind()+
   #ylim(0,1000)+

### 2022-06-21 analysis/gafo-cc-analysis.Rmd
prep model run on cluster

@@
          household = scale(household),
-         youngerchildren = scale(youngerchildren),
+         younger_children = scale(younger_children),
          touchscreen = factor(touchscreen),
-        screen = factor(screen))
+        screen = factor(screen))%>%
+  filter(community == "leipzig" |community == "akure")
 
-unique(mdata$community)
+mdata%>%
+  ggplot(aes(x = abs(clickdistfromtargetcenterx)))+
+  geom_density()
+
+c(
+  lower = exp(4 - 2 * 1.75),
+  higher = exp(4 + 2 * 1.75)
+)
+
 ```
@@
 ```{r}
-bm_base <- brm(abs(clickdistfromtargetcenterx) ~ ageinyears  + targetcentralityx + (trialnr|subjid) + (1|community), 
+bm_gam <- brm(abs(clickdistfromtargetcenterx) ~ 1, 
+                              data   = mdata, 
+                              family = Gamma(link = "log"),
+                              warmup = 1000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4)%>%
+  add_criterion(., c("waic","loo"))
+
+bm_log <- brm(abs(clickdistfromtargetcenterx) ~ 1, 
+                              data   = mdata, 
+                              family = lognormal(),
+                              warmup = 1000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4)%>%
+  add_criterion(., c("waic","loo"))
+
+bm_slog <- brm(abs(clickdistfromtargetcenterx) ~ 1, 
+                              data   = mdata, 
+                              family = shifted_lognormal(),
+                              warmup = 1000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4)%>%
+  add_criterion(., c("waic","loo"))
+
+bm_exg<- brm(abs(clickdistfromtargetcenterx) ~ 1, 
+                              data   = mdata, 
+                              family = exgaussian(),
+                              warmup = 1000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4)%>%
+  add_criterion(., c("waic","loo"))
+
+bm_wei<- brm(abs(clickdistfromtargetcenterx) ~ 1, 
+                              data   = mdata, 
+                              family = weibull(),
+                              warmup = 1000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4)%>%
+  add_criterion(., c("waic","loo"))
+
+loo_compare(bm_gam, bm_log,bm_slog, bm_exg,bm_wei)%>%as_tibble(rownames = "model")
+
+pp_check(bm_gam)+xlim(0,3000)
+pp_check(bm_log)+xlim(0,3000)
+pp_check(bm_slog)+xlim(0,3000)
+pp_check(bm_exg)+xlim(0,3000)
+pp_check(bm_wei)+xlim(0,3000)
+```
+
+```{r}
+bm_base_gam <- brm(abs(clickdistfromtargetcenterx) ~ targetcentralityx + (trialnr|subjid) + (0+ageinyears|community), 
+                              data   = mdata, 
+                              family = Gamma(link = "log"),
+                              warmup = 2000, 
+                              iter   = 5000,
+                   control = list(adapt_delta = 0.95),
+                              chains = 4, 
+                              cores  = 4)%>%
+  add_criterion(., c("waic","loo"))
+
+bm_base_wei <- brm(abs(clickdistfromtargetcenterx) ~ targetcentralityx + (trialnr|subjid) + (0+ageinyears|community), 
+                              data   = mdata, 
+                              family = weibull(),
+                              warmup = 2000, 
+                              iter   = 5000, 
+                   control = list(adapt_delta = 0.95),
+                              chains = 4, 
+                              cores  = 4)%>%
+  add_criterion(., c("waic","loo"))
+
+loo_compare(bm_base_gam,bm_base_wei)%>%as_tibble(rownames = "model")
+
+pp_check(bm_base_gam)+xlim(0,3000)
+pp_check(bm_base_wei)+xlim(0,3000)
+
+```
+
+```{r}
+bm_base <- brm(abs(clickdistfromtargetcenterx) ~ ageinyears  + targetcentralityx + (trialnr|subjid) + (ageinyears|community), 
                               data   = mdata, 
@@
 bm_screen <- brm(abs(clickdistfromtargetcenterx) ~ ageinyears  + targetcentralityx  + (1|subjid) + (screen + children + household|community), 
-                              data   = mdata%>%filter(community != "chimfunshi_kumwenda"), 
+                              data   = mdata, 
                               family = Gamma(link = "log"),

### 2022-06-21 analysis/gafo-cc-data-processing.Rmd
prep model run on cluster

@@
 
+```{r}
+tidy_data_zambia%>%
+  summarise(n = n_distinct(subjID))
+```
+
 ```{r demographics}
@@
 data <- bind_rows(
-  data_namibia,
+  data_namibia%>%rename(younger_children = youngerchildren),
   data_leipzig,
@@
 
+data_nigeria$younger_children
 ```

### 2022-06-21 analysis/gafo-cc-visuals.Rmd
prep model run on cluster

@@
   summarise(n= n_distinct(subjid))
+
+data%>%
+  summarise(n= n_distinct(subjid))
 ```
@@
 ```{r}
+random <- tibble()
+
+for (j in 1:100) {
+
+for (i in 1:960) {
+
+  chance = abs(i + sample(-960:960,1))
+
+  random <- bind_rows(
+    random,
+    tibble(location = i, 
+           iter = j,
+           lower = chance, 
+           upper = -chance)
+  )
+}
+
+}
+
+chance <- random%>%
+  group_by(location)%>%
+  summarise(lower = mean(lower),
+            upper = mean(upper))
+
 data%>%
   group_by(targetcentralityx)%>%
-  #summarise(impr = mean(clickdistfromtargetcenterx))%>%
   mutate(chance_upper = (targetcentralityx + 960)/2,
-         chance_lower = -((targetcentralityx + 960)/2))%>%
-  ggplot(aes(x = targetcentralityx, y = clickdistfromtargetcenterx))+
+         chance_lower = -((targetcentralityx + 960)/2),
+         center_lower = -targetcentralityx,
+         center_upper = targetcentralityx)%>%
+  ggplot(aes(x = targetcentralityx, y = clickdistfromtargetcenterx, col = community))+
   geom_hline(yintercept = 0, lty = 3, alpha = 0.75)+
-  #geom_line(aes(x = targetcentralityx, y = chance_upper), lty = 3, alpha = .75, col = "firebrick")+
-  #geom_line(aes(x = targetcentralityx, y = chance_lower), lty = 3, alpha = .75, col = "firebrick")+
-  geom_point(pch = 1, alpha = 0.75)+
+  geom_line(aes(x = targetcentralityx, y = center_upper), lty = 1, alpha = .75, col = "firebrick")+
+  geom_line(aes(x = targetcentralityx, y = center_lower), lty = 1, alpha = .75, col = "firebrick")+
+  geom_line(aes(x = targetcentralityx, y = chance_upper), lty = 3, alpha = .75, col = "firebrick")+
+  geom_line(aes(x = targetcentralityx, y = chance_lower), lty = 3, alpha = .75, col = "firebrick")+
+  geom_point(pch = 1, alpha = 0.5)+
+  scale_color_colorblind()+
   #ylim(-1500,1500)+
@@
 
+range(data$targetcentralityx)
 ```
@@
 ```
+
+```{r}
+pscreen1 <- data%>%
+  mutate(screen = factor(screen),
+         touchscreen = factor(touchscreen))%>%
+  pivot_longer(cols = c(screen, touchscreen), names_to = "predictor", values_to = "value")%>%
+  group_by(community, subjid, predictor, value)%>%
+  summarise(mean= mean(abs(clickdistfromtargetcenterx)))
+
+pscreen2 <- data%>%
+  mutate(screen = factor(screen),
+         touchscreen = factor(touchscreen))%>%
+  pivot_longer(cols = c(screen, touchscreen), names_to = "predictor", values_to = "value")%>%
+  group_by(community, predictor, value)%>%
+  tidyboot_mean(col= abs(clickdistfromtargetcenterx))
+
+ggplot(pscreen%>%filter(!is.na(value)), aes(x = value, y = mean, col = community))+
+  geom_point(data = pscreen1%>%filter(!is.na(value)), aes(x = value, y = mean, col = community), pch = 1, alpha = .5, position = position_dodge(width = .5))+
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.75, position = position_dodge(width = .5))+
+  facet_grid(~predictor, scales = "free_x")+
+  scale_x_discrete(labels = c("no", "yes"))+
+  scale_color_colorblind()+
+  #ylim(0,1000)+
+  theme_few()
+```
+
+```{r}
+pred <- data%>%
+  group_by(community, subjid, household, children, younger_children)%>%
+  summarise(mean= mean(abs(clickdistfromtargetcenterx)))%>%
+  pivot_longer(cols = c(household, children, younger_children), names_to = "predictor", values_to = "value")%>%
+  group_by(community,predictor)%>%
+  mutate(value = scale(value))
+
+ggplot(pred, aes(x = value, y = mean, col = community))+
+  geom_point(pch = 1)+
+  geom_smooth(method = "glm")+
+  facet_grid(~predictor, scales = "free_x")+
+  stat_cor()+
+  scale_color_colorblind()+
+  ylim(0,1000)+
+  theme_minimal()
+```

### 2022-07-08 analysis/gafo-cc-visuals.Rmd
run cc model leip and ak on cluster

@@
   geom_smooth(method = "glm")+
-  scale_color_colorblind()+
+  scale_color_colorblind(name = "", labels = c("Nigeria", "Namibia", "Sambia", "Namibia", "Germany"))+
   ylim(0,1000)+
@@
   scale_x_continuous(breaks = 2:8)+
-  theme_minimal()
+  theme_minimal()+
+  theme(legend.position = "bottom")
 
+```
+```{r}
+ggsave("../visuals/dev_site.png", width = 5, height = 6, bg = "white")
 ```
@@
 ```{r}
-random <- tibble()
-
-for (j in 1:100) {
-
-for (i in 1:960) {
-
-  chance = abs(i + sample(-960:960,1))
-
-  random <- bind_rows(
-    random,
-    tibble(location = i, 
-           iter = j,
-           lower = chance, 
-           upper = -chance)
-  )
-}
-
-}
-
-chance <- random%>%
-  group_by(location)%>%
-  summarise(lower = mean(lower),
-            upper = mean(upper))
-
 data%>%
@@
 
-range(data$targetcentralityx)
 ```

### 2022-07-20 analysis/gafo-cc-model-hier.Rmd
prep hier model run

---
title: "model"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(coda)
library(jsonlite)
library(ggthemes)
library(ggpubr)
library(data.table)
library(truncnorm)
library(matrixStats)
library(tidyboot)

estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}

hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}

hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
```

# Data

```{r}
data <- read_csv("../data/gafo-cc-clean-data.csv")
```

## Click distribution based on performance

# Model

```{r, message=FALSE, warning=F}
model <- rbindlist(
  list(
     fread("../model/output/gafo-cc-hier_gran_20_chain1.csv"),
     fread("../model/output/gafo-cc-hier_gran_20_chain2.csv")
    ), use.names=TRUE)

saveRDS(model, "../model/output/gafo-cc-model_hier.rds")
# 
# model <- readRDS("../model/output/gafo-cc-model.rds")
```

## Global Paramters

### Guessing

```{r}
model%>%
  filter(scope == "global", 
         parameter == "guessing")%>%
ggplot(aes(x= value, fill = factor(chain)))+
  geom_density(alpha = .5)+
  facet_grid(community~type, scales = "free_y")+
  theme_few()+
  scale_fill_viridis_d()
```

### Bias

```{r}
model%>%
  filter(scope == "global", 
         parameter == "bias")%>%
ggplot(aes(x= value, fill = factor(chain)))+
  geom_density(alpha = .5)+
  facet_grid(community~type)+
  theme_few()+
  scale_fill_viridis_d()
```

### Inference

```{r}
model%>%
  filter(scope == "global", 
         parameter == "inference")%>%
ggplot(aes(x= value, fill = factor(chain)))+
  geom_density(alpha = .5)+
  facet_wrap(~type, scales = "free_y")+
  theme_minimal()+
  scale_fill_viridis_d()
```

## Community Paramters

### Guessing

```{r}
model%>%
  filter(scope == "community", 
         parameter == "guessing")%>%
ggplot(aes(x= value, fill = factor(chain)))+
  geom_density(alpha = .5)+
  facet_grid(community~type, scales = "free_y")+
  theme_few()+
  scale_fill_viridis_d()
```

### Bias

```{r}
model%>%
  filter(scope == "community", 
         parameter == "bias")%>%
ggplot(aes(x= value, fill = factor(chain)))+
  geom_density(alpha = .5)+
  facet_grid(community~type)+
  theme_few()+
  scale_fill_viridis_d()
```

### Inference

```{r}
model%>%
  filter(scope == "community", 
         parameter == "inference")%>%
ggplot(aes(x= value, fill = factor(chain)))+
  geom_density(alpha = .5)+
  facet_wrap(community~type, scales = "free_y")+
  theme_minimal()+
  scale_fill_viridis_d()
```

## Development

### Guessing
```{r}
guess_map <- model%>%
  filter(scope == "global", 
         parameter == "guessing")%>%
  group_by(community, type)%>%
  summarise(mode = estimate_mode(value))%>%
  pivot_wider(names_from = "type", values_from = "mode")%>%
  expand_grid(age = seq(0,3, by = 0.1))%>%
  mutate(guess = plogis(intercept + slope * age))

guess_samp <- model%>%
  filter(scope == "global",
         parameter == "guessing")%>%
  pivot_wider(names_from = "type", values_from = "value")%>%
  #sample_n(1000)%>%
  expand_grid(age = seq(0,3, by = 0.1))%>%
  mutate(guess = plogis(intercept + slope * age))

# guess_samp <- model%>%
#   filter(scope == "global", 
#          parameter == "guessing")%>%
#   pivot_wider(names_from = "type", values_from = "value")%>%
#   group_by(chain)%>%
#   expand_grid(age = seq(0,3, by = 0.1))%>%
#   mutate(sd_inf = exp(intercept + slope * age))%>%
#   group_by(age)%>%
#   summarise(uci = hdi_upper(sd_inf),
#             lci = hdi_lower(sd_inf))

ggplot()+
  geom_line(data = guess_samp, aes(x = age+3, y = guess, group = paste(chain,iteration)), alpha = .01)+
  #geom_line(data = inf_samp, aes(x = age+3, y = uci), lty = 2)+
  #geom_line(data = inf_samp, aes(x = age+3, y = lci), lty = 2)+
  geom_line(data = guess_map, aes(x = age+3, y = guess), col = "firebrick")+
  facet_grid(~community)+
  xlim(3,6)+
  xlab("Age")+
  ylim(0,1)+
  theme_minimal()
```

### Bias
```{r}
bias_map <- model%>%
  filter(scope == "global", 
         parameter == "bias")%>%
  group_by(community,type)%>%
  summarise(mode = estimate_mode(value))%>%
  pivot_wider(names_from = "type", values_from = "mode")%>%
  expand_grid(age = seq(0,3, by = 0.1))%>%
  mutate(bias = plogis(intercept + slope * age))

bias_samp <- model%>%
  filter(scope == "global",
         parameter == "bias")%>%
  pivot_wider(names_from = "type", values_from = "value")%>%
  #sample_n(1000)%>%
  expand_grid(age = seq(0,3, by = 0.1))%>%
  mutate(bias = plogis(intercept + slope * age))

# bias_samp <- model%>%
#   filter(scope == "global", 
#          parameter == "bias")%>%
#   pivot_wider(names_from = "type", values_from = "value")%>%
#   group_by(chain)%>%
#   expand_grid(age = seq(0,3, by = 0.1))%>%
#   mutate(sd_inf = exp(intercept + slope * age))%>%
#   group_by(age)%>%
#   summarise(uci = hdi_upper(sd_inf),
#             lci = hdi_lower(sd_inf))

ggplot()+
  geom_line(data = bias_samp, aes(x = age+3, y = bias, group = paste(chain,iteration)), alpha = .01)+
  #geom_line(data = inf_samp, aes(x = age+3, y = uci), lty = 2)+
  #geom_line(data = inf_samp, aes(x = age+3, y = lci), lty = 2)+
  geom_line(data = bias_map, aes(x = age+3, y = bias), col = "firebrick")+
  xlim(3,6)+
  facet_grid(~community)+
  xlab("Age")+
  ylim(0,1)+
  theme_minimal()
```

### Inference

```{r}
inf_map <- model%>%
  filter(scope == "global", 
         parameter == "inference")%>%
  group_by(community,type)%>%
  summarise(mode = estimate_mode(value))%>%
  pivot_wider(names_from = "type", values_from = "mode")%>%
  expand_grid(age = seq(0,3, by = 0.1))%>%
  mutate(sd_inf = plogis(intercept + slope * age))

inf_samp <- model%>%
  filter(scope == "global",
         parameter == "inference")%>%
  pivot_wider(names_from = "type", values_from = "value")%>%
  group_by(chain)%>%
  #sample_n(1000)%>%
  expand_grid(age = seq(0,3, by = 0.1))%>%
  mutate(sd_inf = plogis(intercept + slope * age))

# inf_samp <- model%>%
#   filter(scope == "global",
#          parameter == "inference")%>%
#   pivot_wider(names_from = "type", values_from = "value")%>%
#   group_by(chain)%>%
#   expand_grid(age = seq(0,3, by = 0.1))%>%
#   mutate(sd_inf = exp(intercept + slope * age))%>%
#   group_by(age)%>%
#   summarise(uci = hdi_upper(sd_inf),
#             lci = hdi_lower(sd_inf))

ggplot()+
  geom_line(data = inf_samp, aes(x = age+3, y = sd_inf, group = paste(chain,iteration)), alpha = .01, size = 0.1)+
   # geom_line(data = inf_samp, aes(x = age+3, y = uci), lty = 2)+
   # geom_line(data = inf_samp, aes(x = age+3, y = lci), lty = 2)+
  geom_line(data = inf_map, aes(x = age+3, y = sd_inf), col = "firebrick")+
  xlim(3,6)+
  facet_grid(~community)+
  labs(x = "Age", y = "Gaze inference precision (across individuals)")+
  ylim(0,1)+
  theme_minimal()
```

```{r}
ggsave("../graphs/sd_dev.png", width = 8, height = 4, scale = 1, bg = "white")
```

```{r}
alt <- model%>%
  filter(scope == "global", 
         parameter != "inference")%>%
  group_by(community,parameter,type)%>%
  summarise(mode = estimate_mode(value))%>%
  filter(type != "sigma")%>%
  pivot_wider(names_from = c("parameter", "type"), values_from = "mode")%>%
  expand_grid(age = seq(0,3, by = 0.1))%>%
  mutate(guess = plogis(guessing_intercept + guessing_slope * age),
         bias_raw = plogis(bias_intercept + bias_slope * age),
         inference = 1- guess,
         center_bias = guess * bias_raw,
         random_guessing = 1- inference - center_bias)%>%
  ungroup()%>%
  select(age,community, center_bias, random_guessing, inference)%>%
  pivot_longer(names_to = "parameter", values_to = "value", cols = c(center_bias, random_guessing, inference))%>%
  mutate(parameter = factor(parameter, levels = c("inference", "random_guessing", "center_bias")))

ggplot(alt, aes(x = age+3, y = value, fill = parameter))+
  geom_area(alpha = .9)+
  xlim(3,6)+
  xlab("Age")+
  ylim(0,1)+
  facet_grid(~community)+
  scale_fill_colorblind()+
  theme_minimal()
```

## Individual

### Guessing

```{r}
model%>%
  filter(scope == "id", 
         parameter == "guessing")%>%
  ggplot(aes(x = value, fill = factor(chain)))+
  geom_density(alpha = .25)+
  facet_wrap(~id, scales = "free")+
  theme_minimal()+
  scale_fill_colorblind()
```

### Inference

```{r}
model%>%
  filter(scope == "id", 
         parameter == "inference")%>%
  ggplot(aes(x = value, fill = factor(chain)))+
  geom_density(alpha = .25)+
  facet_wrap(~id, scales = "free")+
  theme_minimal()+
  scale_fill_colorblind()+
  xlim(0,2)
```

### Relation between paramters

```{r}
rel <- model%>%
  filter(scope == "id")%>%
  group_by(parameter, id)%>%
  summarise(mode = estimate_mode(value))%>%
  left_join(data%>%rename(id = subjID)%>%select(id, ageInYears))

ggplot(rel,aes(x = parameter, y = mode))+
  geom_line(aes(group = id), alpha = .25)+
  geom_point(col = "dodgerblue", pch = 1,alpha = .5)+
  facet_grid(~ageInYears)+
  theme_minimal()
```

### 2022-07-20 analysis/gafo-cc-visuals.Rmd
prep hier model run

@@
   geom_smooth(method = "glm")+
-  scale_color_colorblind(name = "", labels = c("Nigeria", "Namibia", "Sambia", "Namibia", "Germany"))+
+  scale_color_colorblind(name = "")+
   ylim(0,1000)+

### 2022-07-20 analysis/gafo-cc-model-hier.Rmd
prep merge

@@
      fread("../model/output/gafo-cc-hier_gran_20_chain1.csv"),
-     fread("../model/output/gafo-cc-hier_gran_20_chain2.csv")
-    ), use.names=TRUE)
+     fread("../model/output/gafo-cc-hier_gran_20_chain2.csv"),
+     fread("../model/output/gafo-cc-hier_gran_20_chain3.csv")
+    ), use.names=TRUE)#%>%saveRDS("../models/output/model_kids_box.rds")
 
-saveRDS(model, "../model/output/gafo-cc-model_hier.rds")
+# saveRDS(model, "../model/output/gafo-cc-model.rds")
 # 
@@
   geom_density(alpha = .5)+
-  facet_wrap(community~type, scales = "free_y")+
+  facet_grid(community~type, scales = "free_y")+
   theme_minimal()+
@@
 
-### Guessing
+### Global
+
+#### Guessing
+
 ```{r}
@@
   pivot_wider(names_from = "type", values_from = "mode")%>%
-  expand_grid(age = seq(0,3, by = 0.1))%>%
+  expand_grid(age = seq(0,5.5, by = 0.1))%>%
   mutate(guess = plogis(intercept + slope * age))
@@
   #sample_n(1000)%>%
-  expand_grid(age = seq(0,3, by = 0.1))%>%
+  expand_grid(age = seq(0,5.5, by = 0.1))%>%
   mutate(guess = plogis(intercept + slope * age))
@@
 ggplot()+
-  geom_line(data = guess_samp, aes(x = age+3, y = guess, group = paste(chain,iteration)), alpha = .01)+
+  geom_line(data = guess_samp, aes(x = age+2.5, y = guess, group = paste(chain,iteration)), alpha = .01)+
   #geom_line(data = inf_samp, aes(x = age+3, y = uci), lty = 2)+
   #geom_line(data = inf_samp, aes(x = age+3, y = lci), lty = 2)+
-  geom_line(data = guess_map, aes(x = age+3, y = guess), col = "firebrick")+
+  geom_line(data = guess_map, aes(x = age+2.5, y = guess), col = "firebrick")+
   facet_grid(~community)+
-  xlim(3,6)+
+  #xlim(3,6)+
   xlab("Age")+
@@
 
-### Bias
+#### Bias
 ```{r}
@@
   pivot_wider(names_from = "type", values_from = "mode")%>%
-  expand_grid(age = seq(0,3, by = 0.1))%>%
+  expand_grid(age = seq(0,5.5, by = 0.1))%>%
   mutate(bias = plogis(intercept + slope * age))
@@
   #sample_n(1000)%>%
-  expand_grid(age = seq(0,3, by = 0.1))%>%
+  expand_grid(age = seq(0,5.5, by = 0.1))%>%
   mutate(bias = plogis(intercept + slope * age))
@@
 ggplot()+
-  geom_line(data = bias_samp, aes(x = age+3, y = bias, group = paste(chain,iteration)), alpha = .01)+
+  geom_line(data = bias_samp, aes(x = age+2.5, y = bias, group = paste(chain,iteration)), alpha = .01)+
   #geom_line(data = inf_samp, aes(x = age+3, y = uci), lty = 2)+
   #geom_line(data = inf_samp, aes(x = age+3, y = lci), lty = 2)+
-  geom_line(data = bias_map, aes(x = age+3, y = bias), col = "firebrick")+
-  xlim(3,6)+
+  geom_line(data = bias_map, aes(x = age+2.5, y = bias), col = "firebrick")+
+  #xlim(3,6)+
   facet_grid(~community)+
@@
 
-### Inference
+#### Inference
 
@@
   pivot_wider(names_from = "type", values_from = "mode")%>%
-  expand_grid(age = seq(0,3, by = 0.1))%>%
+  expand_grid(age = seq(0,5.5, by = 0.1))%>%
   mutate(sd_inf = plogis(intercept + slope * age))
@@
   #sample_n(1000)%>%
-  expand_grid(age = seq(0,3, by = 0.1))%>%
+  expand_grid(age = seq(0,5.5, by = 0.1))%>%
   mutate(sd_inf = plogis(intercept + slope * age))
@@
 ggplot()+
-  geom_line(data = inf_samp, aes(x = age+3, y = sd_inf, group = paste(chain,iteration)), alpha = .01, size = 0.1)+
+  geom_line(data = inf_samp, aes(x = age+2.5, y = sd_inf, group = paste(chain,iteration)), alpha = .01, size = 0.1)+
    # geom_line(data = inf_samp, aes(x = age+3, y = uci), lty = 2)+
    # geom_line(data = inf_samp, aes(x = age+3, y = lci), lty = 2)+
-  geom_line(data = inf_map, aes(x = age+3, y = sd_inf), col = "firebrick")+
-  xlim(3,6)+
+  geom_line(data = inf_map, aes(x = age+2.5, y = sd_inf), col = "firebrick")+
+  #xlim(3,6)+
+  facet_grid(~community)+
+  labs(x = "Age", y = "Gaze inference precision (across individuals)")+
+  ylim(0,1)+
+  theme_minimal()
+```
+
+```{r}
+ggsave("../graphs/sd_dev.png", width = 8, height = 4, scale = 1, bg = "white")
+```
+
+### Community level
+
+#### Guessing
+```{r}
+guess_map_com <- model%>%
+  filter(scope == "community", 
+         parameter == "guessing")%>%
+  group_by(community, type)%>%
+  summarise(mode = estimate_mode(value))%>%
+  pivot_wider(names_from = "type", values_from = "mode")%>%
+  expand_grid(age = seq(0,5.5, by = 0.1))%>%
+  mutate(guess = plogis(intercept + slope * age))
+
+guess_samp_com <- model%>%
+  filter(scope == "community",
+         parameter == "guessing")%>%
+  pivot_wider(names_from = "type", values_from = "value")%>%
+  #sample_n(1000)%>%
+  expand_grid(age = seq(0,5.5, by = 0.1))%>%
+  mutate(guess = plogis(intercept + slope * age))
+
+# guess_samp <- model%>%
+#   filter(scope == "global", 
+#          parameter == "guessing")%>%
+#   pivot_wider(names_from = "type", values_from = "value")%>%
+#   group_by(chain)%>%
+#   expand_grid(age = seq(0,3, by = 0.1))%>%
+#   mutate(sd_inf = exp(intercept + slope * age))%>%
+#   group_by(age)%>%
+#   summarise(uci = hdi_upper(sd_inf),
+#             lci = hdi_lower(sd_inf))
+
+ggplot()+
+  geom_line(data = guess_samp_com, aes(x = age+2.5, y = guess, group = paste(chain,iteration)), alpha = .01)+
+  #geom_line(data = inf_samp, aes(x = age+3, y = uci), lty = 2)+
+  #geom_line(data = inf_samp, aes(x = age+3, y = lci), lty = 2)+
+  geom_line(data = guess_map_com, aes(x = age+2.5, y = guess), col = "firebrick")+
+  facet_grid(~community)+
+  #xlim(3,6)+
+  xlab("Age")+
+  ylim(0,1)+
+  theme_minimal()
+```
+
+#### Bias
+```{r}
+bias_map_com <- model%>%
+  filter(scope == "community", 
+         parameter == "bias")%>%
+  group_by(community,type)%>%
+  summarise(mode = estimate_mode(value))%>%
+  pivot_wider(names_from = "type", values_from = "mode")%>%
+  expand_grid(age = seq(0,5.5, by = 0.1))%>%
+  mutate(bias = plogis(intercept + slope * age))
+
+bias_samp_com <- model%>%
+  filter(scope == "community",
+         parameter == "bias")%>%
+  pivot_wider(names_from = "type", values_from = "value")%>%
+  #sample_n(1000)%>%
+  expand_grid(age = seq(0,5.5, by = 0.1))%>%
+  mutate(bias = plogis(intercept + slope * age))
+
+# bias_samp <- model%>%
+#   filter(scope == "global", 
+#          parameter == "bias")%>%
+#   pivot_wider(names_from = "type", values_from = "value")%>%
+#   group_by(chain)%>%
+#   expand_grid(age = seq(0,3, by = 0.1))%>%
+#   mutate(sd_inf = exp(intercept + slope * age))%>%
+#   group_by(age)%>%
+#   summarise(uci = hdi_upper(sd_inf),
+#             lci = hdi_lower(sd_inf))
+
+ggplot()+
+  geom_line(data = bias_samp_com, aes(x = age+2.5, y = bias, group = paste(chain,iteration)), alpha = .01)+
+  #geom_line(data = inf_samp, aes(x = age+3, y = uci), lty = 2)+
+  #geom_line(data = inf_samp, aes(x = age+3, y = lci), lty = 2)+
+  geom_line(data = bias_map_com, aes(x = age+2.5, y = bias), col = "firebrick")+
+  #xlim(3,6)+
+  facet_grid(~community)+
+  xlab("Age")+
+  ylim(0,1)+
+  theme_minimal()
+```
+
+#### Inference
+
+```{r}
+inf_map_com <- model%>%
+  filter(scope == "community", 
+         parameter == "inference")%>%
+  group_by(community,type)%>%
+  summarise(mode = estimate_mode(value))%>%
+  pivot_wider(names_from = "type", values_from = "mode")%>%
+  expand_grid(age = seq(0,5.5, by = 0.1))%>%
+  mutate(sd_inf = plogis(intercept + slope * age))
+
+inf_samp_com <- model%>%
+  filter(scope == "community",
+         parameter == "inference")%>%
+  pivot_wider(names_from = "type", values_from = "value")%>%
+  group_by(chain)%>%
+  #sample_n(1000)%>%
+  expand_grid(age = seq(0,5.5, by = 0.1))%>%
+  mutate(sd_inf = plogis(intercept + slope * age))
+
+# inf_samp <- model%>%
+#   filter(scope == "global",
+#          parameter == "inference")%>%
+#   pivot_wider(names_from = "type", values_from = "value")%>%
+#   group_by(chain)%>%
+#   expand_grid(age = seq(0,3, by = 0.1))%>%
+#   mutate(sd_inf = exp(intercept + slope * age))%>%
+#   group_by(age)%>%
+#   summarise(uci = hdi_upper(sd_inf),
+#             lci = hdi_lower(sd_inf))
+
+ggplot()+
+  geom_line(data = inf_samp_com, aes(x = age+2.5, y = sd_inf, group = paste(chain,iteration)), alpha = .01, size = 0.1)+
+   # geom_line(data = inf_samp, aes(x = age+3, y = uci), lty = 2)+
+   # geom_line(data = inf_samp, aes(x = age+3, y = lci), lty = 2)+
+  geom_line(data = inf_map_com, aes(x = age+2.5, y = sd_inf), col = "firebrick")+
+  #xlim(3,6)+
   facet_grid(~community)+
@@
 alt <- model%>%
-  filter(scope == "global", 
+  filter(scope == "community", 
          parameter != "inference")%>%
@@
   pivot_wider(names_from = c("parameter", "type"), values_from = "mode")%>%
-  expand_grid(age = seq(0,3, by = 0.1))%>%
+  expand_grid(age = seq(0,5.5, by = 0.1))%>%
   mutate(guess = plogis(guessing_intercept + guessing_slope * age),
@@
 
-ggplot(alt, aes(x = age+3, y = value, fill = parameter))+
-  geom_area(alpha = .9)+
-  xlim(3,6)+
+ggplot(alt, aes(x = age+2.5, y = value, fill = parameter))+
+  geom_area(alpha = .75)+
+  #xlim(3,6)+
   xlab("Age")+
@@
   geom_density(alpha = .25)+
-  facet_wrap(~id, scales = "free")+
+  facet_wrap(community~id, scales = "free")+
   theme_minimal()+
-  scale_fill_colorblind()
+  scale_fill_colorblind()+
+theme(
+  strip.background = element_blank(),
+  strip.text.x = element_blank()
+)
 ```
@@
   geom_density(alpha = .25)+
-  facet_wrap(~id, scales = "free")+
+  facet_wrap(community~id, scales = "free")+
   theme_minimal()+
   scale_fill_colorblind()+
-  xlim(0,2)
+theme(
+  strip.background = element_blank(),
+  strip.text.x = element_blank()
+)
 ```

### 2022-07-20 analysis/gafo-cc-model.Rmd
prep merge

---
title: "model"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(coda)
library(jsonlite)
library(ggthemes)
library(ggpubr)
library(data.table)
library(truncnorm)
library(matrixStats)
library(tidyboot)

estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}

hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}

hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
```

# Data

```{r}
data <- read_csv("../data/gafo-cc-clean-data.csv")

```

## Click distribution based on performance

# Model

```{r, message=FALSE, warning=F}
model <- rbindlist(
  list(
     fread("../model/output/gafo-cc_gran_20_chain1.csv"),
     fread("../model/output/gafo-cc_gran_20_chain2.csv"),
     fread("../model/output/gafo-cc_gran_20_chain3.csv"),
     fread("../model/output/gafo-cc_gran_20_chain4.csv"),
     fread("../model/output/gafo-cc_gran_20_chain5.csv"),
     fread("../model/output/gafo-cc_gran_20_chain6.csv"),
     fread("../model/output/gafo-cc_gran_20_chain7.csv"),
     fread("../model/output/gafo-cc_gran_20_chain8.csv")
    ), use.names=TRUE)#%>%saveRDS("../models/output/model_kids_box.rds")

# saveRDS(model, "../model/output/gafo-cc-model.rds")
# 
# model <- readRDS("../model/output/gafo-cc-model.rds")
```

## Global Paramters

### Guessing

```{r}
model%>%
  filter(scope == "global", 
         parameter == "guessing")%>%
ggplot(aes(x= value, fill = factor(chain)))+
  geom_density(alpha = .5)+
  facet_wrap(community~type, scales = "free_y", nrow = 2)+
  theme_few()+
  scale_fill_viridis_d()
```

### Bias

```{r}
model%>%
  filter(
         parameter == "bias")%>%
ggplot(aes(x= value, fill = factor(chain)))+
  geom_density(alpha = .5)+
  facet_grid(community~type)+
  theme_few()+
  scale_fill_viridis_d()
```

### Inference

```{r}
model%>%
  filter(scope == "global", 
         parameter == "inference")%>%
ggplot(aes(x= value, fill = factor(chain)))+
  geom_density(alpha = .5)+
  facet_wrap(~type, scales = "free_y")+
  theme_minimal()+
  scale_fill_viridis_d()
```
## Development

### Guessing
```{r}
guess_map <- model%>%
  filter(scope == "global", 
         parameter == "guessing")%>%
  group_by(community, type)%>%
  summarise(mode = estimate_mode(value))%>%
  pivot_wider(names_from = "type", values_from = "mode")%>%
  expand_grid(age = seq(0,5.5, by = 0.1))%>%
  mutate(guess = plogis(intercept + slope * age))

guess_samp <- model%>%
  filter(scope == "global",
         parameter == "guessing")%>%
  pivot_wider(names_from = "type", values_from = "value")%>%
  sample_n(1000)%>%
  expand_grid(age = seq(0,5.5, by = 0.1))%>%
  mutate(guess = plogis(intercept + slope * age))

# guess_samp <- model%>%
#   filter(scope == "global", 
#          parameter == "guessing")%>%
#   pivot_wider(names_from = "type", values_from = "value")%>%
#   group_by(chain)%>%
#   expand_grid(age = seq(0,3, by = 0.1))%>%
#   mutate(sd_inf = exp(intercept + slope * age))%>%
#   group_by(age)%>%
#   summarise(uci = hdi_upper(sd_inf),
#             lci = hdi_lower(sd_inf))

ggplot()+
  geom_line(data = guess_samp, aes(x = age+2.5, y = guess, group = paste(chain,iteration)), alpha = .01)+
  #geom_line(data = inf_samp, aes(x = age+3, y = uci), lty = 2)+
  #geom_line(data = inf_samp, aes(x = age+3, y = lci), lty = 2)+
  geom_line(data = guess_map, aes(x = age+2.5, y = guess), col = "firebrick")+
  facet_grid(~community)+
  #xlim(2.5,8)+
  xlab("Age")+
  #ylim(0,1)+
  theme_minimal()
```

### Bias
```{r}
bias_map <- model%>%
  filter(scope == "global", 
         parameter == "bias")%>%
  group_by(community,type)%>%
  summarise(mode = estimate_mode(value))%>%
  pivot_wider(names_from = "type", values_from = "mode")%>%
  expand_grid(age = seq(0,5.5, by = 0.1))%>%
  mutate(bias = plogis(intercept + slope * age))

bias_samp <- model%>%
  filter(scope == "global",
         parameter == "bias")%>%
  pivot_wider(names_from = "type", values_from = "value")%>%
  sample_n(1000)%>%
  expand_grid(age = seq(0,5.5, by = 0.1))%>%
  mutate(bias = plogis(intercept + slope * age))

# bias_samp <- model%>%
#   filter(scope == "global", 
#          parameter == "bias")%>%
#   pivot_wider(names_from = "type", values_from = "value")%>%
#   group_by(chain)%>%
#   expand_grid(age = seq(0,3, by = 0.1))%>%
#   mutate(sd_inf = exp(intercept + slope * age))%>%
#   group_by(age)%>%
#   summarise(uci = hdi_upper(sd_inf),
#             lci = hdi_lower(sd_inf))

ggplot()+
  geom_line(data = bias_samp, aes(x = age+2.5, y = bias, group = paste(chain,iteration)), alpha = .01)+
  #geom_line(data = inf_samp, aes(x = age+3, y = uci), lty = 2)+
  #geom_line(data = inf_samp, aes(x = age+3, y = lci), lty = 2)+
  geom_line(data = bias_map, aes(x = age+2.5, y = bias), col = "firebrick")+
  #xlim(3,6)+
  facet_grid(~community)+
  xlab("Age")+
  #ylim(0,1)+
  theme_minimal()
```

### Inference

```{r}
inf_map <- model%>%
  filter(scope == "global", 
         parameter == "inference")%>%
  group_by(community,type)%>%
  summarise(mode = estimate_mode(value))%>%
  pivot_wider(names_from = "type", values_from = "mode")%>%
  expand_grid(age = seq(0,5.5, by = 0.1))%>%
  mutate(sd_inf = plogis(intercept + slope * age))

inf_samp <- model%>%
  filter(scope == "global",
         parameter == "inference")%>%
  pivot_wider(names_from = "type", values_from = "value")%>%
  group_by(chain)%>%
  sample_n(1000)%>%
  expand_grid(age = seq(0,5.5, by = 0.1))%>%
  mutate(sd_inf = plogis(intercept + slope * age))

# inf_samp <- model%>%
#   filter(scope == "global",
#          parameter == "inference")%>%
#   pivot_wider(names_from = "type", values_from = "value")%>%
#   group_by(chain)%>%
#   expand_grid(age = seq(0,3, by = 0.1))%>%
#   mutate(sd_inf = exp(intercept + slope * age))%>%
#   group_by(age)%>%
#   summarise(uci = hdi_upper(sd_inf),
#             lci = hdi_lower(sd_inf))

ggplot()+
  geom_line(data = inf_samp, aes(x = age+2.5, y = sd_inf, group = paste(chain,iteration)), alpha = .01, size = 0.1)+
   # geom_line(data = inf_samp, aes(x = age+3, y = uci), lty = 2)+
   # geom_line(data = inf_samp, aes(x = age+3, y = lci), lty = 2)+
  geom_line(data = inf_map, aes(x = age+2.5, y = sd_inf), col = "firebrick")+
  #xlim(3,6)+
  facet_grid(~community)+
  labs(x = "Age", y = "Gaze inference precision (across individuals)")+
  #ylim(0,1)+
  theme_minimal()
```

```{r}
ggsave("../graphs/sd_dev.png", width = 8, height = 4, scale = 1, bg = "white")
```

```{r}
alt <- model%>%
  filter(scope == "global", 
         parameter != "inference",
         chain != 7,
         chain != 2)%>%
  group_by(community,parameter,type)%>%
  summarise(mode = estimate_mode(value))%>%
  filter(type != "sigma")%>%
  pivot_wider(names_from = c("parameter", "type"), values_from = "mode")%>%
  expand_grid(age = seq(0,3, by = 0.1))%>%
  mutate(guess = plogis(guessing_intercept + guessing_slope * age),
         bias_raw = plogis(bias_intercept + bias_slope * age),
         inference = 1- guess,
         center_bias = guess * bias_raw,
         random_guessing = 1- inference - center_bias)%>%
  ungroup()%>%
  select(age,community, center_bias, random_guessing, inference)%>%
  pivot_longer(names_to = "parameter", values_to = "value", cols = c(center_bias, random_guessing, inference))%>%
  mutate(parameter = factor(parameter, levels = c("inference", "random_guessing", "center_bias")))

ggplot(alt, aes(x = age+3, y = value, fill = parameter))+
  geom_area(alpha = .9)+
  xlim(3,6)+
  xlab("Age")+
  ylim(0,1)+
  facet_grid(~community)+
  scale_fill_colorblind()+
  theme_minimal()
```

## Individual

### Guessing

```{r}
model%>%
  filter(scope == "id", 
         parameter == "guessing")%>%
  ggplot(aes(x = value, fill = factor(chain)))+
  geom_density(alpha = .25)+
  facet_wrap(~id, scales = "free")+
  theme_void()+
  scale_fill_colorblind()
```

### Inference

```{r}
model%>%
  filter(scope == "id", 
         parameter == "inference")%>%
  ggplot(aes(x = value, fill = factor(chain)))+
  geom_density(alpha = .25)+
  facet_wrap(~id, scales = "free")+
  theme_minimal()+
  scale_fill_colorblind()+
  xlim(0,2)
```

### Relation between paramters

```{r}
rel <- model%>%
  filter(scope == "id")%>%
  group_by(parameter, id)%>%
  summarise(mode = estimate_mode(value))%>%
  left_join(data%>%rename(id = subjID)%>%select(id, ageInYears))

ggplot(rel,aes(x = parameter, y = mode))+
  geom_line(aes(group = id), alpha = .25)+
  geom_point(col = "dodgerblue", pch = 1,alpha = .5)+
  facet_grid(~ageInYears)+
  theme_minimal()
```

### 2022-07-28 analysis/gafo-cc-data-processing.Rmd
extended hierarchical model

@@
 library(readODS)
+library(truncnorm)
 
@@
     studytype = as.factor("vali"), 
-  ) %>%
-  select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
+  ) #%>% select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
+
 ```
@@
 raw_demographics_namibia <- bind_rows(
-  read_xlsx("../../raw_data/gafo-cc/namibia/Data FarmSix 2022.xlsx", sheet = 1)%>%mutate(ID = paste0("H",str_pad(ID, 7, pad = "0"))),
-  read_xlsx("../../raw_data/gafo-cc/namibia/Data Khwe 2022.xlsx", sheet = 1)%>%mutate(ID = paste0("K",str_pad(ID, 7, pad = "0")))%>%rename(sex = `...7`)
+  read_xlsx("../../raw_data/gafo-cc/namibia/GaFo Data Haikom 2022.xlsx", sheet = 1)%>%mutate(ID = paste0("H",str_pad(ID, 7, pad = "0")))%>%mutate(site = Community, Community = "hai||om"),
+  read_xlsx("../../raw_data/gafo-cc/namibia/Data Khwe 2022.xlsx", sheet = 1)%>%mutate(ID = paste0("K",str_pad(ID, 7, pad = "0")))%>%rename(Sex = `...7`)%>%mutate(site = Community, Community = "khwe")
   )
@@
   filter(!is.na(ageinyears))
+
 ```
@@
          subjID = ifelse(subjID == "TSPeVFYf", "tSPeVFYf", subjID),
-         subjID =as.factor(subjID))%>%
-  select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
+         subjID =as.factor(subjID))#%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
 
@@
 # get all .json files
-files <- list.files("../../../../../Cloud/QuantEx/Gafo-cc/data/nigeria/JSONs/", pattern = "*.json",recursive = T)
+files <- list.files("../../../../../../Cloud/QuantEx/Gafo-cc/data/nigeria/JSONs/", pattern = "*.json",recursive = T)
 
@@
 for (f in files) {
-  jf <- paste("../../../../../Cloud/QuantEx/Gafo-cc/data/nigeria/JSONs/", f, sep = "")
+  jf <- paste("../../../../../../Cloud/QuantEx/Gafo-cc/data/nigeria/JSONs/", f, sep = "")
   jd <- jsonlite::fromJSON(paste(readLines(jf, warn = "FALSE"), collapse = ""))
@@
     subjID = ifelse(subjID == "nlger002", "niger002", subjID)
-  ) %>%
-  select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
+  ) #%>% select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
 ```
@@
 raw_demographics_nigeria <- bind_rows(
-  read_xlsx("../../../../../Cloud/QuantEx/Gafo-cc/data/nigeria/gafo-cc-nigeria-participants.xlsx", sheet = 1)
+  read_xlsx("../../../../../../Cloud/QuantEx/Gafo-cc/data/nigeria/gafo-cc-nigeria-participants.xlsx", sheet = 1)
   )
+
+read_xlsx("../../../../../../Cloud/QuantEx/Gafo-cc/data/nigeria/gafo-cc-nigeria-participants.xlsx", sheet = 1)
 
@@
     studytype = as.factor("vali")
-  ) %>%
-  select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
+  ) #%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
 ```
@@
   left_join(tidy_data_zambia%>%rename_all(tolower),by = c("subjid"))%>%
-  mutate(community = "chimfunshi_kumwenda")
+  mutate(community = "chimfunshi")
 ```
@@
 
-data_nigeria$younger_children
 ```
@@
 ```
+
+# Data for model
+
+```{r}
+mdata <- data%>%
+  filter(community == "leipzig" | community == "akure",
+         voiceover == F)%>%
+  mutate(agecentered = ageinyears - min(ageinyears))%>%
+  select(-c(screen,touchscreen.x, household, children, younger_children, sex,ageinyears, wrongareaclick, earlyclick, durationanimationballoontotal, durationanimationcomplete, responsetime, clientscreenwidth, clientscreenheight, clientscreenscaling, clickoriginalx, clickoriginaly, hitbbtargetx, hitbbtargety, clickdistfromtargetbboxx, clickedarea, studyversion, boxesnr,population, inhouse, touchscreen.y , os, mobile, browser, browserversion, safari, iossafari,target, voiceover, epoch, timestamp, inwardclick, boxwidth,boxborderleft, boxborderright , correctbox, datacollection, sample, studytype, comment, status))
+
+write(toJSON(mdata), file = "../model/model_data/gafo-cc-model-data.json")
+
+mdata%>%
+  filter(is.na(agecentered))
+
+mdata%>%
+  filter(trialnr == 5)%>%
+  select(subjid,agecentered)
+```
+
+```{r}
+mdata_small <- mdata%>%
+  filter(subjid %in% c("VcyYgFQx", "k1mQYc2K", "niger007","niger057"))
+
+write(toJSON(mdata_small), file = "../model/model_data/gafo-cc-model-data-small.json")
+```
+
+```{r}
+prior <- dtruncnorm(seq(from = 0, to = 2900, by = 20), a = 1, b = 2920, mean = 1450, sd = 100)
+
+length(prior)
+
+write(toJSON(prior, digits = 4, use_signif = TRUE), file = "../model/model_data/centerBias_extended.json")
+```

### 2022-08-01 analysis/gafo-cc-model-hier-extended.Rmd
update from server

---
title: "model"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(coda)
library(jsonlite)
library(ggthemes)
library(ggpubr)
library(data.table)
library(truncnorm)
library(matrixStats)
library(tidyboot)

estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}

hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}

hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
```

# Data

```{r}
data <- read_csv("../data/gafo-cc-clean-data.csv")
```

## Click distribution based on performance

# Model

```{r, message=FALSE, warning=F}
model <- rbindlist(
  list(
     fread("../model/output/gafo-cc-hier_extended_gran_20_chain1.csv"),
     fread("../model/output/gafo-cc-hier_extended_gran_20_chain3.csv"),
     fread("../model/output/gafo-cc-hier_extended_gran_20_chain6.csv")
    ), use.names=TRUE)

#saveRDS(model, "../model/output/gafo-cc-model_hier.rds")
# 
# model <- readRDS("../model/output/gafo-cc-model.rds")
```

## Global Paramters

### Guessing

```{r}
model%>%
  filter(scope == "global", 
         parameter == "guessing")%>%
ggplot(aes(x= value, fill = factor(chain)))+
  geom_density(alpha = .5)+
  facet_grid(community~type, scales = "free_y")+
  theme_few()+
  scale_fill_viridis_d()
```

### Bias

```{r}
model%>%
  filter(scope == "global", 
         parameter == "bias")%>%
ggplot(aes(x= value, fill = factor(chain)))+
  geom_density(alpha = .5)+
  facet_grid(community~type)+
  theme_few()+
  scale_fill_viridis_d()
```

### Inference

```{r}
model%>%
  filter(scope == "global", 
         parameter == "inference")%>%
ggplot(aes(x= value, fill = factor(chain)))+
  geom_density(alpha = .5)+
  facet_wrap(~type, scales = "free_y")+
  theme_minimal()+
  scale_fill_viridis_d()
```

## Community Paramters

### Guessing

```{r}
model%>%
  filter(scope == "community", 
         parameter == "guessing")%>%
ggplot(aes(x= value, fill = factor(chain)))+
  geom_density(alpha = .5)+
  facet_grid(community~type, scales = "free_y")+
  theme_few()+
  scale_fill_viridis_d()
```

### Bias

```{r}
model%>%
  filter(scope == "community", 
         parameter == "bias")%>%
ggplot(aes(x= value, fill = factor(chain)))+
  geom_density(alpha = .5)+
  facet_grid(community~type)+
  theme_few()+
  scale_fill_viridis_d()
```

### Inference

```{r}
model%>%
  filter(scope == "community", 
         parameter == "inference")%>%
ggplot(aes(x= value, fill = factor(chain)))+
  geom_density(alpha = .5)+
  facet_wrap(community~type, scales = "free_y")+
  theme_minimal()+
  scale_fill_viridis_d()
```

## Development

### Guessing
```{r}
guess_map <- model%>%
  filter(scope == "community", 
         parameter == "guessing")%>%
  group_by(community, type)%>%
  summarise(mode = estimate_mode(value))%>%
  pivot_wider(names_from = "type", values_from = "mode")%>%
  expand_grid(age = seq(0,3, by = 0.1))%>%
  mutate(guess = plogis(intercept + slope * age))

guess_samp <- model%>%
  filter(scope == "community",
         parameter == "guessing")%>%
  pivot_wider(names_from = "type", values_from = "value")%>%
  #sample_n(1000)%>%
  expand_grid(age = seq(0,3, by = 0.1))%>%
  mutate(guess = plogis(intercept + slope * age))

# guess_samp <- model%>%
#   filter(scope == "global", 
#          parameter == "guessing")%>%
#   pivot_wider(names_from = "type", values_from = "value")%>%
#   group_by(chain)%>%
#   expand_grid(age = seq(0,3, by = 0.1))%>%
#   mutate(sd_inf = exp(intercept + slope * age))%>%
#   group_by(age)%>%
#   summarise(uci = hdi_upper(sd_inf),
#             lci = hdi_lower(sd_inf))

ggplot()+
  geom_line(data = guess_samp, aes(x = age+3, y = guess, group = paste(chain,iteration)), size = .01)+
  #geom_line(data = inf_samp, aes(x = age+3, y = uci), lty = 2)+
  #geom_line(data = inf_samp, aes(x = age+3, y = lci), lty = 2)+
  geom_line(data = guess_map, aes(x = age+3, y = guess), col = "firebrick")+
  facet_grid(~community)+
  #xlim(3,6)+
  xlab("Age")+
  ylim(0,1)+
  theme_minimal()
```

### Bias
```{r}
bias_map <- model%>%
  filter(scope == "community", 
         parameter == "bias")%>%
  group_by(community,type)%>%
  summarise(mode = estimate_mode(value))%>%
  pivot_wider(names_from = "type", values_from = "mode")%>%
  expand_grid(age = seq(0,3, by = 0.1))%>%
  mutate(bias = plogis(intercept + slope * age))

bias_samp <- model%>%
  filter(scope == "community",
         parameter == "bias")%>%
  pivot_wider(names_from = "type", values_from = "value")%>%
  #sample_n(1000)%>%
  expand_grid(age = seq(0,3, by = 0.1))%>%
  mutate(bias = plogis(intercept + slope * age))

# bias_samp <- model%>%
#   filter(scope == "global", 
#          parameter == "bias")%>%
#   pivot_wider(names_from = "type", values_from = "value")%>%
#   group_by(chain)%>%
#   expand_grid(age = seq(0,3, by = 0.1))%>%
#   mutate(sd_inf = exp(intercept + slope * age))%>%
#   group_by(age)%>%
#   summarise(uci = hdi_upper(sd_inf),
#             lci = hdi_lower(sd_inf))

ggplot()+
  geom_line(data = bias_samp, aes(x = age+3, y = bias, group = paste(chain,iteration)), alpha = .01)+
  #geom_line(data = inf_samp, aes(x = age+3, y = uci), lty = 2)+
  #geom_line(data = inf_samp, aes(x = age+3, y = lci), lty = 2)+
  geom_line(data = bias_map, aes(x = age+3, y = bias), col = "firebrick")+
  #xlim(3,6)+
  facet_grid(~community)+
  xlab("Age")+
  ylim(0,1)+
  theme_minimal()
```

### Inference

```{r}
inf_map <- model%>%
  filter(scope == "community", 
         parameter == "inference")%>%
  group_by(community,type)%>%
  summarise(mode = estimate_mode(value))%>%
  pivot_wider(names_from = "type", values_from = "mode")%>%
  expand_grid(age = seq(0,5.5, by = 0.1))%>%
  mutate(sd_inf = plogis(intercept + slope * age))

inf_samp <- model%>%
  filter(scope == "community",
         parameter == "inference")%>%
  pivot_wider(names_from = "type", values_from = "value")%>%
  group_by(chain)%>%
  #sample_n(1000)%>%
  expand_grid(age = seq(0,5.5, by = 0.1))%>%
  mutate(sd_inf = plogis(intercept + slope * age))

# inf_samp <- model%>%
#   filter(scope == "global",
#          parameter == "inference")%>%
#   pivot_wider(names_from = "type", values_from = "value")%>%
#   group_by(chain)%>%
#   expand_grid(age = seq(0,3, by = 0.1))%>%
#   mutate(sd_inf = exp(intercept + slope * age))%>%
#   group_by(age)%>%
#   summarise(uci = hdi_upper(sd_inf),
#             lci = hdi_lower(sd_inf))

ggplot()+
  geom_line(data = inf_samp, aes(x = age+3, y = sd_inf, group = paste(chain,iteration)), alpha = .01, size = 0.1)+
   # geom_line(data = inf_samp, aes(x = age+3, y = uci), lty = 2)+
   # geom_line(data = inf_samp, aes(x = age+3, y = lci), lty = 2)+
  geom_line(data = inf_map, aes(x = age+3, y = sd_inf), col = "firebrick")+
  #xlim(3,6)+
  facet_grid(~community)+
  labs(x = "Age", y = "Gaze inference precision (across individuals)")+
  ylim(0,1)+
  theme_minimal()
```

```{r}
ggsave("../graphs/sd_dev.png", width = 8, height = 4, scale = 1, bg = "white")
```

```{r}
alt <- model%>%
  filter(scope == "global", 
         parameter != "inference")%>%
  group_by(community,parameter,type)%>%
  summarise(mode = estimate_mode(value))%>%
  filter(type != "sigma")%>%
  pivot_wider(names_from = c("parameter", "type"), values_from = "mode")%>%
  expand_grid(age = seq(0,3, by = 0.1))%>%
  mutate(guess = plogis(guessing_intercept + guessing_slope * age),
         bias_raw = plogis(bias_intercept + bias_slope * age),
         inference = 1- guess,
         center_bias = guess * bias_raw,
         random_guessing = 1- inference - center_bias)%>%
  ungroup()%>%
  select(age,community, center_bias, random_guessing, inference)%>%
  pivot_longer(names_to = "parameter", values_to = "value", cols = c(center_bias, random_guessing, inference))%>%
  mutate(parameter = factor(parameter, levels = c("inference", "random_guessing", "center_bias")))

ggplot(alt, aes(x = age+3, y = value, fill = parameter))+
  geom_area(alpha = .9)+
  xlim(3,6)+
  xlab("Age")+
  ylim(0,1)+
  facet_grid(~community)+
  scale_fill_colorblind()+
  theme_minimal()
```

## Individual

### Guessing

```{r}
model%>%
  filter(scope == "id", 
         parameter == "guessing")%>%
  ggplot(aes(x = value, fill = factor(chain)))+
  geom_density(alpha = .25)+
  facet_wrap(~id, scales = "free")+
  theme_minimal()+
  scale_fill_colorblind()
```

### Inference

```{r}
model%>%
  filter(scope == "id", 
         parameter == "inference")%>%
  ggplot(aes(x = value, fill = factor(chain)))+
  geom_density(alpha = .25)+
  facet_wrap(~id, scales = "free")+
  theme_minimal()+
  scale_fill_colorblind()+
  xlim(0,2)
```

### Relation between paramters

```{r}
rel <- model%>%
  filter(scope == "id")%>%
  group_by(parameter, id)%>%
  summarise(mode = estimate_mode(value))%>%
  left_join(data%>%rename(id = subjID)%>%select(id, ageInYears))

ggplot(rel,aes(x = parameter, y = mode))+
  geom_line(aes(group = id), alpha = .25)+
  geom_point(col = "dodgerblue", pch = 1,alpha = .5)+
  facet_grid(~ageInYears)+
  theme_minimal()
```

### 2022-08-01 analysis/gafo-cc-model-hier.Rmd
update from server

@@
      fread("../model/output/gafo-cc-hier_gran_20_chain2.csv"),
-     fread("../model/output/gafo-cc-hier_gran_20_chain3.csv")
+     fread("../model/output/gafo-cc-hier_gran_20_chain3.csv"),
+     fread("../model/output/gafo-cc-hier_gran_20_chain4.csv"),
+     fread("../model/output/gafo-cc-hier_gran_20_chain5.csv")
     ), use.names=TRUE)#%>%saveRDS("../models/output/model_kids_box.rds")
 
-# saveRDS(model, "../model/output/gafo-cc-model.rds")
+#saveRDS(model, "../model/output/gafo-cc-model_hier.rds")
 # 
@@
   filter(scope == "global", 
-         parameter == "guessing")%>%
+         parameter == "guessing",
+         chain != 1)%>%
 ggplot(aes(x= value, fill = factor(chain)))+
@@
   filter(scope == "global", 
-         parameter == "inference")%>%
+         parameter == "inference",
+         chain != 1)%>%
 ggplot(aes(x= value, fill = factor(chain)))+
@@
   filter(scope == "community", 
-         parameter == "guessing")%>%
+         parameter == "guessing",
+         chain != 1)%>%
 ggplot(aes(x= value, fill = factor(chain)))+
@@
   filter(scope == "community", 
-         parameter == "bias")%>%
+         parameter == "bias",
+         chain != 1)%>%
 ggplot(aes(x= value, fill = factor(chain)))+
@@
 guess_map <- model%>%
-  filter(scope == "global", 
+  filter(scope == "community", 
          parameter == "guessing")%>%
@@
 guess_samp <- model%>%
-  filter(scope == "global",
+  filter(scope == "community",
          parameter == "guessing")%>%
   pivot_wider(names_from = "type", values_from = "value")%>%
-  #sample_n(1000)%>%
+  sample_n(1000)%>%
+  group_by(community)%>%
   expand_grid(age = seq(0,5.5, by = 0.1))%>%
@@
 bias_map <- model%>%
-  filter(scope == "global", 
+  filter(scope == "community", 
          parameter == "bias")%>%
@@
 bias_samp <- model%>%
-  filter(scope == "global",
+  filter(scope == "community",
          parameter == "bias")%>%
   pivot_wider(names_from = "type", values_from = "value")%>%
-  #sample_n(1000)%>%
+  sample_n(1000)%>%
   expand_grid(age = seq(0,5.5, by = 0.1))%>%
@@
 inf_map <- model%>%
-  filter(scope == "global", 
+  filter(scope == "community", 
          parameter == "inference")%>%
@@
 inf_samp <- model%>%
-  filter(scope == "global",
+  filter(scope == "community",
          parameter == "inference")%>%
@@
   group_by(chain)%>%
-  #sample_n(1000)%>%
+  sample_n(1000)%>%
   expand_grid(age = seq(0,5.5, by = 0.1))%>%

### 2022-08-01 analysis/gafo-cc-model.Rmd
update from server

@@
   filter(scope == "global", 
-         parameter == "guessing")%>%
+         parameter == "guessing",
+         chain != 5,
+         chain != 6)%>%
 ggplot(aes(x= value, fill = factor(chain)))+
@@
   filter(
-         parameter == "bias")%>%
+         parameter == "bias",
+         chain != 5)%>%
 ggplot(aes(x= value, fill = factor(chain)))+
@@
   filter(scope == "global", 
-         parameter == "inference")%>%
+         parameter == "inference",
+         chain != 5,
+         chain != 4)%>%
 ggplot(aes(x= value, fill = factor(chain)))+
   geom_density(alpha = .5)+
-  facet_wrap(~type, scales = "free_y")+
+  facet_wrap(community~type, scales = "free_y")+
   theme_minimal()+
@@
   filter(scope == "global", 
-         parameter != "inference",
-         chain != 7,
-         chain != 2)%>%
+         parameter != "inference")%>%
   group_by(community,parameter,type)%>%

### 2022-12-05 analysis/gafo-cc-data-processing.Rmd
update repo

@@
     studytype = as.factor("vali"), 
-  ) #%>% select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
+  ) %>%
+  mutate(subjID = toupper(subjID))%>%select(-touchScreen)#%>% select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
 
@@
 raw_demographics_namibia <- bind_rows(
-  read_xlsx("../../raw_data/gafo-cc/namibia/GaFo Data Haikom 2022.xlsx", sheet = 1)%>%mutate(ID = paste0("H",str_pad(ID, 7, pad = "0")))%>%mutate(site = Community, Community = "hai||om"),
-  read_xlsx("../../raw_data/gafo-cc/namibia/Data Khwe 2022.xlsx", sheet = 1)%>%mutate(ID = paste0("K",str_pad(ID, 7, pad = "0")))%>%rename(Sex = `...7`)%>%mutate(site = Community, Community = "khwe")
-  )
+  read_xlsx("../../raw_data/gafo-cc/namibia/Data Haikom 2022.xlsx", sheet = 1, col_types = c("numeric", "text", "text", "text", "date", "date", "text", "numeric", "numeric", "numeric", "numeric", "numeric", "text"))%>%mutate(ID = paste0("H",str_pad(ID, 7, pad = "0")))%>%mutate(site = Community, Community = "hai||om"),
+  read_xlsx("../../raw_data/gafo-cc/namibia/Data Khwe 2022.xlsx", sheet = 1, col_types = c("numeric", "text", "text", "text", "date", "date", "text", "numeric", "numeric", "numeric", "numeric", "numeric", "text"))%>%mutate(ID = paste0("K",str_pad(ID, 7, pad = "0")))%>%rename(Sex = `...7`)%>%mutate(site = Community, Community = "khwe"),
+    read_xlsx("../../raw_data/gafo-cc/namibia/Data Windhoek 2022 completed.xlsx", sheet = 1)%>%
+    select(ID, Community,`First Name`,Name,	BirthDate,	TestDate,	Sex,	Screen,	Touchscreen,	Household,	Children,	YoungerChildren)%>%mutate(ID = paste0("W",str_pad(ID, 7, pad = "0")))%>%mutate(site = Community, Community = "windhoek")
+  )%>%
+  filter(!grepl("rop",Comment))
+
+testdates <- tidy_data_namibia%>%
+  select(subjID, timestamp)%>%
+  mutate(test_date = as.Date(substr(timestamp, 0,10)))%>%
+  select(subjID, test_date)%>%
+  distinct(subjID, .keep_all = T)%>%
+  mutate(subjID = toupper(subjID))
 
 tidy_demographics_namibia <- raw_demographics_namibia %>% 
+  rename(subjID = ID)%>%
+  left_join(testdates)%>%
   mutate(
-    ageInYears = as.numeric(difftime(TestDate,BirthDate, units = "days")/365.25),
+    ageInYears = as.numeric(difftime(test_date,BirthDate, units = "days")/365.25),
   ) %>%
-  rename(subjID = ID) %>% 
-  select(-c(`First Name`, Name, BirthDate, TestDate, Comment))%>% 
+  select(-c(`First Name`, Name, BirthDate, TestDate,test_date, Comment))%>% 
   rename_all(tolower)%>%
   filter(!is.na(ageinyears))
-
 ```
@@
 data_namibia <- tidy_demographics_namibia%>%
-  left_join(tidy_data_namibia%>%rename_all(tolower),by = c("subjid"))
+  left_join(tidy_data_namibia%>%rename_all(tolower),by = c("subjid"))%>%
+  distinct(subjid, trialnr, .keep_all = T)
+
 ```
@@
 ```{r}
-system("rsync -zaP ccp-odcJ:/srv/ccp-odc/gafo-leipzig/data/ ~/Work/Local/Quantex/Gafo/raw_data/gafo-cc/leipzig/")
+system("rsync -zaP ccp-odcJ:/srv/ccp-odc/gafo-leipzig/data/ ~/Work/Local/QuantEx/Gafo/raw_data/gafo-cc/leipzig/")
 ```
@@
          subjID = ifelse(subjID == "TSPeVFYf", "tSPeVFYf", subjID),
-         subjID =as.factor(subjID))#%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
+         subjID =as.factor(subjID))%>%select(-touchScreen)#%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
 
@@
     subjID = ifelse(subjID == "nlger002", "niger002", subjID)
-  ) #%>% select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
+  ) %>%select(-touchScreen)#%>% select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
 ```
@@
   )
-
-read_xlsx("../../../../../../Cloud/QuantEx/Gafo-cc/data/nigeria/gafo-cc-nigeria-participants.xlsx", sheet = 1)
 
@@
     studytype = as.factor("vali")
-  ) #%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
+  ) %>%select(-touchScreen)#%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
 ```
@@
 
+# Stanford
+
+```{r}
+data_stanford <- read.csv("../../raw_data/gafo-cc/stanford/tidy_data_extra.csv")%>%
+  mutate(subjID = paste0("S",subjID),
+         community = "stanford",
+         screen = ifelse(screen == "yes", 1, 0),
+         touchscreen = ifelse(screen == "touchscreen", 1, 0),
+         browserVersion = factor(browserVersion),
+         targetPosition = factor(targetPosition))%>%
+  select(-touchScreen)%>%
+  rename(ageinyears = age)%>%
+  rename_all(tolower)
+```
+
 # Merge
@@
   data_nigeria,
-  data_zambia
+  data_zambia,
+  data_stanford
 )%>%
@@
 
+```{r}
+data%>%
+  select(-touchscreen)%>%
+  filter(community == "windhoek")%>%
+  rename(touchscreen = touchscreen.x)%>%
+  group_by(subjid, community, sex, screen, touchscreen, household,children,younger_children, ageinyears)%>%
+    summarise(precision = mean(abs(clickdistfromtargetcenterx)))%>%
+  write_csv(.,"../data/gafo-cc-windhoek.csv")
+```
+
 # Data for model
@@
 ```{r}
+
+data <- read_csv("../data/gafo-cc-clean-data.csv")
+
 mdata <- data%>%
@@
   mutate(agecentered = ageinyears - min(ageinyears))%>%
-  select(-c(screen,touchscreen.x, household, children, younger_children, sex,ageinyears, wrongareaclick, earlyclick, durationanimationballoontotal, durationanimationcomplete, responsetime, clientscreenwidth, clientscreenheight, clientscreenscaling, clickoriginalx, clickoriginaly, hitbbtargetx, hitbbtargety, clickdistfromtargetbboxx, clickedarea, studyversion, boxesnr,population, inhouse, touchscreen.y , os, mobile, browser, browserversion, safari, iossafari,target, voiceover, epoch, timestamp, inwardclick, boxwidth,boxborderleft, boxborderright , correctbox, datacollection, sample, studytype, comment, status))
+  select(-c(screen,touchscreen.x, household, children, younger_children, sex,ageinyears, wrongareaclick, earlyclick, durationanimationballoontotal, durationanimationcomplete, responsetime, clientscreenwidth, clientscreenheight, clientscreenscaling, clickoriginalx, clickoriginaly, hitbbtargetx, hitbbtargety, clickdistfromtargetbboxx, clickedarea, studyversion, boxesnr,population, inhouse, touchscreen.y , os, mobile, browser, browserversion, safari, iossafari,target, voiceover, epoch, timestamp, inwardclick, boxwidth,boxborderleft, boxborderright , correctbox, datacollection, sample, studytype, comment, status, site))
 
@@
 
-mdata%>%
-  filter(is.na(agecentered))
+display(communities)%>%
+  filter(is.na(community))
 
@@
   select(subjid,agecentered)
+
+range(mdata$clickscaledx+500)
 ```

### 2022-12-05 analysis/gafo-cc-visuals.Rmd
update repo

@@
 ```{r}
-data <- read_csv("../data/gafo-cc-clean-data.csv")
+data <- read_csv("../data/gafo-cc-clean-data.csv")%>%
+  mutate(community = recode(community,
+                            akure = "akure (nigeria)",
+                            leipzig = "leipzig (germany)",
+                            `hai||om` = "hai||om (namibia)",
+                            khwe = "khwe (namibia)",
+                            windhoek = "windhoek (namibia)",
+                            stanford = "stanford (usa)",
+                            chimfunshi = "chimfunshi (sambia)"))
 ```
@@
 data%>%
+  filter(community != "chimfunshi (sambia)")%>%
   group_by(community,subjid, ageinyears)%>%
@@
   ggplot(aes(x = ageinyears, y = impr, col = community))+
-  geom_point(pch = 1)+
+  geom_point(alpha = .25)+
   geom_smooth(method = "glm")+
-  scale_color_colorblind(name = "")+
+  scale_color_colorblind(name = "Community")+
   ylim(0,1000)+
-  labs(x = "Age (in years)", y ="Imprecision")+
+  labs(x = "Age (in years)", y ="Imprecision (average click distance from target)")+
   scale_x_continuous(breaks = 2:8)+
   theme_minimal()+
-  theme(legend.position = "bottom")
+  theme(legend.position = "right")
 
@@
 ```{r}
-ggsave("../visuals/dev_site.png", width = 5, height = 6, bg = "white")
+ggsave("../visuals/dev_site.png", width = 8, height = 6, bg = "white")
 ```
@@
 ```{r}
-ptp <- data%>%
+ggsave("../visuals/dev_site.png", width = 8, height = 6, bg = "white")
+```
+
+```{r}
+ptp<- data%>%
+  filter(community != "chimfunshi (sambia)")%>%
   mutate(targetposition = factor(targetposition, levels = c(1:10)))%>%
@@
   geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
-  labs(x = "Binned target position", y = "Mean imprecision")+
-  scale_color_colorblind()+
-  #ylim(0,1000)+
+  labs(x = "Target position (binned)", y = "Imprecision (average click distance from target)")+
+  scale_color_colorblind(name = "Community")+
+  ylim(0,1000)+
   theme_minimal()
@@
 ```{r}
+ggsave("../visuals/target_position_site.png", width = 8, height = 6, bg = "white")
+```
+
+```{r}
 pscreen1 <- data%>%
+  group_by(community)%>%
+  mutate(clickdistfromtargetcenterx = scale(abs(clickdistfromtargetcenterx)))%>%
   mutate(screen = factor(screen),
@@
   pivot_longer(cols = c(screen, touchscreen), names_to = "predictor", values_to = "value")%>%
-  group_by(community, subjid, predictor, value)%>%
-  summarise(mean= mean(abs(clickdistfromtargetcenterx)))
+  group_by(subjid, predictor, value)%>%
+  summarise(mean= mean(clickdistfromtargetcenterx))
 
 pscreen2 <- data%>%
+  group_by(community)%>%
+  mutate(clickdistfromtargetcenterx = scale(abs(clickdistfromtargetcenterx)))%>%
   mutate(screen = factor(screen),
@@
   pivot_longer(cols = c(screen, touchscreen), names_to = "predictor", values_to = "value")%>%
-  group_by(community, predictor, value)%>%
-  tidyboot_mean(col= abs(clickdistfromtargetcenterx))
+  group_by(predictor, value)%>%
+  tidyboot_mean(col= clickdistfromtargetcenterx)
 
-ggplot(pscreen%>%filter(!is.na(value)), aes(x = value, y = mean, col = community))+
-  geom_point(data = pscreen1%>%filter(!is.na(value)), aes(x = value, y = mean, col = community), pch = 1, alpha = .5, position = position_dodge(width = .5))+
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.75, position = position_dodge(width = .5))+
+ggplot(pscreen2%>%filter(!is.na(value)), aes(x = value, y = mean))+
+  geom_jitter(data = pscreen1%>%filter(!is.na(value)), aes(x = value, y = mean), pch = 1, alpha = .25, height = 0)+
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.75, position = position_dodge(width = .5), col = "firebrick")+
   facet_grid(~predictor, scales = "free_x")+
   scale_x_discrete(labels = c("no", "yes"))+
+  labs(y = "Imprecision (scaled within community)", x = "Predictor value")+
   scale_color_colorblind()+
+
   #ylim(0,1000)+
-  theme_few()
+  theme_bw()
+```
+
+```{r}
+ggsave("../visuals/pred_screen.png", width = 8, height = 6, bg = "white")
 ```
@@
 pred <- data%>%
-  group_by(community, subjid, household, children, younger_children)%>%
-  summarise(mean= mean(abs(clickdistfromtargetcenterx)))%>%
+  group_by(community)%>%
+  mutate(clickdistfromtargetcenterx = scale(abs(clickdistfromtargetcenterx)), 
+         household = scale(household), 
+         children = scale(children),
+         younger_children = scale(younger_children))%>%
+  group_by(subjid, household, children, younger_children)%>%
+  summarise(mean= mean(clickdistfromtargetcenterx))%>%
   pivot_longer(cols = c(household, children, younger_children), names_to = "predictor", values_to = "value")%>%
-  group_by(community,predictor)%>%
+  group_by(predictor)%>%
   mutate(value = scale(value))
 
-ggplot(pred, aes(x = value, y = mean, col = community))+
+ggplot(pred, aes(x = value, y = mean))+
   geom_point(pch = 1)+
@@
   scale_color_colorblind()+
-  ylim(0,1000)+
-  theme_minimal()
+  labs(y = "Imprecision (scaled within community)", x = "Predictor value (scaled within community)")+
+  #ylim(0,1000)+
+  theme_bw()
 ```
+
+```{r}
+ggsave("../visuals/pred_household.png", width = 12, height = 6, bg = "white")
+```

### 2022-12-06 analysis/gafo-cc-data-processing.Rmd
add more data

@@
 raw_demographics_leipzig <- bind_rows(
-  read_xlsx("../../../../../Cloud/QuantEx/Gafo-cc/docs/Gafo-cc-leipzig-participants.xlsx", sheet = 1)
+  #read_xlsx("../../../../../Cloud/QuantEx/Gafo-cc/docs/", sheet = 1)
+  read_xlsx("../../raw_data/gafo-cc/leipzig/Gafo-cc-leipzig-participants.xlsx", sheet = 1)
   )
@@
 ```{r}
+data%>%
+  filter(community == "leipzig")%>%
+  mutate(age_group = substr(ageinyears, 1,1))%>%
+  group_by(screen, age_group)%>%
+  summarise(n = n_distinct(subjid))
+```
+
+```{r}
 write_csv(data,"../data/gafo-cc-clean-data.csv")
@@
 mdata <- data%>%
-  filter(community == "leipzig" | community == "akure",
+  filter(community != "chimfunshi",
          voiceover == F)%>%
   mutate(agecentered = ageinyears - min(ageinyears))%>%
-  select(-c(screen,touchscreen.x, household, children, younger_children, sex,ageinyears, wrongareaclick, earlyclick, durationanimationballoontotal, durationanimationcomplete, responsetime, clientscreenwidth, clientscreenheight, clientscreenscaling, clickoriginalx, clickoriginaly, hitbbtargetx, hitbbtargety, clickdistfromtargetbboxx, clickedarea, studyversion, boxesnr,population, inhouse, touchscreen.y , os, mobile, browser, browserversion, safari, iossafari,target, voiceover, epoch, timestamp, inwardclick, boxwidth,boxborderleft, boxborderright , correctbox, datacollection, sample, studytype, comment, status, site))
+  select(-c(sex,ageinyears, wrongareaclick, earlyclick, durationanimationballoontotal, durationanimationcomplete, responsetime, clientscreenwidth, clientscreenheight, clientscreenscaling, clickoriginalx, clickoriginaly, hitbbtargetx, hitbbtargety, clickdistfromtargetbboxx, clickedarea, studyversion, boxesnr,population, inhouse, os, mobile, browser, browserversion, safari, iossafari,target, voiceover, epoch, timestamp, inwardclick, boxwidth,boxborderleft, boxborderright , correctbox, datacollection, sample, studytype, comment, status, site, `phone number in DB`,`location` ))
 
 write(toJSON(mdata), file = "../model/model_data/gafo-cc-model-data.json")
+
+write_csv(mdata, file = "../model/model_data/gafo-cc-model-data.csv")
 

### 2022-12-12 analysis/gafo-cc-data-processing.Rmd
fix touch screen stanford

@@
          screen = ifelse(screen == "yes", 1, 0),
-         touchscreen = ifelse(screen == "touchscreen", 1, 0),
+         touchscreen = ifelse(touchscreen == "yes", 1, 0),
          browserVersion = factor(browserVersion),
@@
 ```{r}
-write_csv(data,"../data/gafo-cc-clean-data.csv")
+write_csv(data,"../data/gafo-cc-clean-data-incl-fam.csv")
 ```

### 2023-05-03 analysis/gafo-cc-data-processing.Rmd
move to cluster

--- 2022-12-06 analysis/gafo-cc-data-processing.Rmd
@@
 
+```{r}
+data_namibia%>%
+  filter(community == "windhoek")%>%
+  mutate(age_group = substr(ageinyears, 1,1))%>%
+  group_by(age_group)%>%
+  summarise(n = n_distinct(subjid))
+
+data_namibia%>%
+  filter(community == "windhoek")%>%
+  group_by(ageinyears)%>%
+  summarise(n= n_distinct(subjid))%>%
+  ggplot(aes(x = ageinyears, y = ""))+
+  geom_count(alpha = .5)+
+  xlim(2.5, 8)+
+  theme_bw()
+```
+
 # Leipzig
@@
 # get all .json files
-files <- list.files("../../raw_data/gafo-cc/leipzig/", pattern = "*.json",recursive = T)
+files <- list.files("../../raw_data/gafo-cc/leipzig/", pattern = "*.json",recursive = T)%>% str_subset(pattern = "gafo--", negate = T)
 
@@
 raw_demographics_leipzig <- bind_rows(
-  #read_xlsx("../../../../../Cloud/QuantEx/Gafo-cc/docs/", sheet = 1)
-  read_xlsx("../../raw_data/gafo-cc/leipzig/Gafo-cc-leipzig-participants.xlsx", sheet = 1)
+  read_xlsx("../../../../../../Cloud/QuantEx/Gafo-cc/docs/Gafo-cc-leipzig-participants.xlsx", sheet = 1)
+  #read_xlsx("../../raw_data/gafo-cc/leipzig/Gafo-cc-leipzig-participants.xlsx", sheet = 1)
   )
@@
   rename(subjid = code)%>%
-  filter(!is.na(ageinyears),
-         status == "keep")
+  filter(status == "keep")
 ```
@@
 
+data_leipzig%>%
+  #group_by(subjid)%>%
+  summarise(n = n_distinct(subjid))
+
+data_leipzig%>%
+  mutate(age_group = substr(ageinyears, 1, 1))%>%
+  select(subjid, sex, age_group, screen, touchscreen, household, children, younger_children)%>%
+  na.omit()%>%
+  group_by(age_group, sex)%>%
+  summarise(n = n_distinct(subjid))
+
+data_leipzig%>%
+  mutate(age_group = substr(ageinyears, 1, 1))%>%
+  select(subjid, sex, age_group, screen, touchscreen, household, children, younger_children)%>%
+  na.omit()%>%
+  group_by(age_group)%>%
+  summarise(n = n_distinct(subjid))
 ```
@@
   mutate(location = community,
-         community = "akure")
+         community = "akure")%>%
+  distinct(subjid, trialnr, .keep_all = TRUE)
 ```
@@
 # get all .json files
-files <- list.files("../../../../../Cloud/QuantEx/Gafo-cc/data/zambia/", pattern = "*.json",recursive = T)
+files <- list.files("../../raw_data/gafo-cc/zambia/", pattern = "*.json",recursive = T)
 
@@
 for (f in files) {
-  jf <- paste("../../../../../Cloud/QuantEx/Gafo-cc/data/zambia/", f, sep = "")
+  jf <- paste("../../raw_data/gafo-cc/zambia/", f, sep = "")
   jd <- jsonlite::fromJSON(paste(readLines(jf, warn = "FALSE"), collapse = ""))
@@
     sample = as.factor("na"),
-    studytype = as.factor("vali")
+    studytype = as.factor("vali"),
+    subjID = paste0("z", subjID),
   ) %>%select(-touchScreen)#%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
@@
 raw_demographics_zambia <- bind_rows(
-  read_ods("../../../../../Cloud/QuantEx/Gafo-cc/data/zambia/gafo-cc-sambia-participants.ods", sheet = 1)
+  read_xlsx("../../raw_data/gafo-cc/zambia/Gafo_cc_Zambia_April23_Final.xlsx", sheet = 1)
   )
@@
   mutate(
-    test_date = as.Date(test_date, format = "%d/%m/%Y"),
-    birth_date = as.Date(birth_date, format = "%d/%m/%Y"),
+    #test_date = as.Date(test_date, format = "%d/%m/%Y"),
+    #birth_date = as.Date(birth_date, format = "%d/%m/%Y"),
     ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
+    id = paste0("z", id),
+    screen = ifelse(screen == "yes", 1, 0),
+    touchscreen = ifelse(touchscreen == "yes", 1, 0)
   )  %>%
-  select(-c(first_name, last_name, test_date, birth_date, comment))%>%
+  filter(status == "keep")%>%
+  select(-c(test_date, birth_date, comment, Age, consent_signed, Nr, status))%>%
   rename(subjid = id)%>%
@@
   left_join(tidy_data_zambia%>%rename_all(tolower),by = c("subjid"))%>%
-  mutate(community = "chimfunshi")
+  mutate(community = "chimfunshi")%>%
+  distinct(subjid, trialnr, .keep_all = TRUE)
 ```
@@
   rename(ageinyears = age)%>%
+  rename_all(tolower)%>%
+  distinct(subjid, trialnr, .keep_all = T)
+```
+
+```{r}
+data_stanford%>%
+  mutate(age_group = substr(ageinyears, 1,1))%>%
+  group_by(age_group)%>%
+  summarise(n = n_distinct(subjid))
+
+```
+
+# Plymouth
+
+```{r}
+system("rsync -zaP ccp-odcJ:/srv/ccp-odc/gafo-uk/data/ ~/Work/Local/QuantEx/Gafo/raw_data/gafo-cc/plymouth/")
+```
+
+```{r read_data}
+# get all .json files
+files <- list.files("../../raw_data/gafo-cc/plymouth/", pattern = "*.json",recursive = T)%>% str_subset(pattern = "gafo--", negate = T)
+
+# convert json files to tibbles
+raw_data_plymouth <- tibble()
+for (f in files) {
+  jf <- paste("../../raw_data/gafo-cc/plymouth/", f, sep = "")
+  jd <- jsonlite::fromJSON(paste(readLines(jf, warn = "FALSE"), collapse = ""))
+
+  # needed because hedge trials have numbers, box trials have characters
+  jd$targetPosition <- factor(as.character(jd$targetPosition))
+
+  raw_data_plymouth <- bind_rows(raw_data_plymouth, jd)
+}
+# remove variables that we don't need anymore
+rm(f, files, jf, jd)
+```
+
+```{r}
+tidy_data_plymouth <- raw_data_plymouth %>%
+
+  # convert all character vectors into factors
+  mutate_if(is.character, as.factor) %>%
+
+  mutate(
+
+    # attention! the SVG coord system starts with 0, 0 in upper left corner
+    # we transform the values so that 0, 0 is lower left corner (for plots etc)
+    clickScaledY = 1080 - clickScaledY,
+    targetY = 1080 - targetY, 
+    targetCenterY = 1080 - targetCenterY, 
+    eyeCenterRightY = 1080 - eyeCenterRightY,
+    eyeCenterLeftY = 1080 - eyeCenterLeftY,
+    pupilFinalRightY = 1080 - pupilFinalRightY,
+    pupilFinalLeftY = 1080 - pupilFinalLeftY, 
+    targetCentralityX = abs(960 - targetCenterX),
+
+    # similarly here: in svg coords, negative click distance means up. 
+    # here we invert it, so that negative values mean down
+    clickDistFromTargetCenterY = clickDistFromTargetCenterY * -1, 
+    clickDistFromTargetBBoxY = clickDistFromTargetBBoxY * -1,
+
+    # positive values for inward clicks (i.e.,towards the center), negative for outward clicks
+    centralityBias = ifelse(targetCenterX <= 1920/2,
+                            clickDistFromTargetCenterX, 
+                            clickDistFromTargetCenterX*-1),
+
+    inwardClick = ifelse(centralityBias > 0, TRUE, FALSE),
+
+    # did the participant click on the right box?
+    # also for hedge version, here we imagine a box surrounding the target center 
+    # this way, we can compare hedge and box version ;) 
+    boxWidth = 218, 
+    boxBorderLeft = targetCenterX - boxWidth/2, 
+    boxBorderRight = targetCenterX + boxWidth/2,
+    correctBox = ifelse(boxBorderLeft <= clickScaledX & clickScaledX <= boxBorderRight, TRUE, FALSE),
+
+    datacollection = as.factor("in-person - supervised"), 
+    sample = as.factor("na"),
+    studytype = as.factor("vali"), 
+  ) %>%
+  mutate(subjID =as.factor(subjID))%>%select(-touchScreen)%>%
+  distinct(subjID, trialNr, .keep_all = T)#%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
+
+#unique(tidy_data_leipzig$subjID)
+```
+
+```{r}
+tidy_data_plymouth%>%
+  filter(trialType == "test")%>%
+  group_by(subjID)%>%
+  summarise(n = n())
+
+tidy_data_plymouth%>%
+  filter(trialType == "test")%>%
+  summarise(n = n_distinct(subjID))
+```
+
+```{r demographics}
+raw_demographics_plymouth <- bind_rows(
+  read_xlsx("../../raw_data/gafo-cc/plymouth/participants_information.xlsx", sheet = 1)
+  )
+
+test_date_plymouth <- tidy_data_plymouth%>%
+  select(subjID, timestamp)%>%
+  mutate(test_date = as.Date(substr(timestamp, 1,10),format = "%Y-%m-%d"))%>%
+  select(-timestamp)%>%
   rename_all(tolower)
+
+tidy_demographics_plymouth <- raw_demographics_plymouth %>% 
+  select(-test_date)%>%
+  left_join(test_date_plymouth)%>%
+  mutate(
+    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
+    younger_children = ifelse(younger_children == "N/A", NA, younger_children),
+    younger_children = as.numeric(younger_children)
+  )  %>%
+  select(-c(test_date, birth_date, comment))%>%
+  filter(!is.na(ageinyears))
+```
+```{r}
+data_plymouth <- tidy_demographics_plymouth%>%
+  left_join(tidy_data_plymouth%>%rename_all(tolower),by = c("subjid"))%>%
+  distinct(subjid, trialnr, .keep_all = TRUE)
+
+data_plymouth%>%
+  #mutate(age_group = substr(ageinyears, 1,1))%>%
+  #group_by(age_group)%>%
+  summarise(n = n_distinct(subjid))
+
+data_plymouth%>%
+  group_by(subjid)%>%
+  summarise(n())
+
+```
+
+# Mexico
+
+```{r read_data}
+# get all .json files
+files <- list.files("../../../../../../Cloud/QuantEx/Gafo-cc/data/mexico/", pattern = "*.json",recursive = T)
+
+# convert json files to tibbles
+raw_data_mex <- tibble()
+for (f in files) {
+  jf <- paste("../../../../../../Cloud/QuantEx/Gafo-cc/data/mexico/", f, sep = "")
+  jd <- jsonlite::fromJSON(paste(readLines(jf, warn = "FALSE"), collapse = ""))
+
+  # needed because hedge trials have numbers, box trials have characters
+  jd$targetPosition <- factor(as.character(jd$targetPosition))
+
+  raw_data_mex <- bind_rows(raw_data_mex, jd)
+}
+# remove variables that we don't need anymore
+rm(f, files, jf, jd)
+```
+
+```{r}
+tidy_data_mex <- raw_data_mex %>%
+
+  # convert all character vectors into factors
+  mutate_if(is.character, as.factor) %>%
+
+  mutate(
+
+    # attention! the SVG coord system starts with 0, 0 in upper left corner
+    # we transform the values so that 0, 0 is lower left corner (for plots etc)
+    clickScaledY = 1080 - clickScaledY,
+    targetY = 1080 - targetY, 
+    targetCenterY = 1080 - targetCenterY, 
+    eyeCenterRightY = 1080 - eyeCenterRightY,
+    eyeCenterLeftY = 1080 - eyeCenterLeftY,
+    pupilFinalRightY = 1080 - pupilFinalRightY,
+    pupilFinalLeftY = 1080 - pupilFinalLeftY, 
+    targetCentralityX = abs(960 - targetCenterX),
+
+    # similarly here: in svg coords, negative click distance means up. 
+    # here we invert it, so that negative values mean down
+    clickDistFromTargetCenterY = clickDistFromTargetCenterY * -1, 
+    clickDistFromTargetBBoxY = clickDistFromTargetBBoxY * -1,
+
+    # positive values for inward clicks (i.e.,towards the center), negative for outward clicks
+    centralityBias = ifelse(targetCenterX <= 1920/2,
+                            clickDistFromTargetCenterX, 
+                            clickDistFromTargetCenterX*-1),
+
+    inwardClick = ifelse(centralityBias > 0, TRUE, FALSE),
+
+    # did the participant click on the right box?
+    # also for hedge version, here we imagine a box surrounding the target center 
+    # this way, we can compare hedge and box version ;) 
+    boxWidth = 218, 
+    boxBorderLeft = targetCenterX - boxWidth/2, 
+    boxBorderRight = targetCenterX + boxWidth/2,
+    correctBox = ifelse(boxBorderLeft <= clickScaledX & clickScaledX <= boxBorderRight, TRUE, FALSE),
+
+    datacollection = as.factor("in-person - supervised"), 
+    sample = as.factor("na"),
+    studytype = as.factor("vali")
+  ) %>%select(-touchScreen)#%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
+```
+
+```{r}
+tidy_data_mex%>%
+  summarise(n = n_distinct(subjID))
+```
+
+```{r demographics}
+raw_demographics_mex <- bind_rows(
+  read_xlsx("../../../../../../Cloud/QuantEx/Gafo-cc/data/mexico/participants.xlsx", sheet = 1)
+  )%>%
+  filter(!is.na(lastname))%>%
+  mutate(birth_date = ifelse(birth_date == 29042017, 20170429, birth_date))
+
+tidy_demographics_mex <- raw_demographics_mex %>% 
+  mutate(
+
+    test_date = as.Date(as.character(test_date), format = "%Y%m%d"),
+    birth_date = as.Date(as.character(birth_date), format = "%Y%m%d"),
+    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
+  )  %>%
+  select(-c(name, lastname, test_date, birth_date, comment))%>%
+  filter(!is.na(ageinyears))
+
+```
+
+```{r}
+data_mex <- tidy_demographics_mex%>%
+  left_join(tidy_data_mex%>%rename_all(tolower),by = c("subjid"))%>%
+  mutate(community = "mexico")%>%
+  distinct(subjid, trialnr, .keep_all = TRUE)
+
+data_mex%>%summarise(n = n_distinct(subjid))
+```
+
+# China
+
+```{r}
+system("rsync -zaP ccp-odcJ:/srv/ccp-odc/gafo-china/data/ ~/Work/Local/QuantEx/Gafo/raw_data/gafo-cc/china/")
+```
+
+```{r read_data}
+# get all .json files
+files <- list.files("../../raw_data/gafo-cc/china/", pattern = "*.json",recursive = T)%>% str_subset(pattern = "gafo--", negate = T)
+
+# convert json files to tibbles
+raw_data_china <- tibble()
+for (f in files) {
+  jf <- paste("../../raw_data/gafo-cc/china/", f, sep = "")
+  jd <- jsonlite::fromJSON(paste(readLines(jf, warn = "FALSE"), collapse = ""))
+
+  # needed because hedge trials have numbers, box trials have characters
+  jd$targetPosition <- factor(as.character(jd$targetPosition))
+
+  raw_data_china <- bind_rows(raw_data_china, jd)
+}
+# remove variables that we don't need anymore
+rm(f, files, jf, jd)
+```
+
+```{r}
+tidy_data_china <- raw_data_china %>%
+
+  # convert all character vectors into factors
+
+  mutate(
+
+    # attention! the SVG coord system starts with 0, 0 in upper left corner
+    # we transform the values so that 0, 0 is lower left corner (for plots etc)
+    clickScaledY = 1080 - clickScaledY,
+    targetY = 1080 - targetY, 
+    targetCenterY = 1080 - targetCenterY, 
+    eyeCenterRightY = 1080 - eyeCenterRightY,
+    eyeCenterLeftY = 1080 - eyeCenterLeftY,
+    pupilFinalRightY = 1080 - pupilFinalRightY,
+    pupilFinalLeftY = 1080 - pupilFinalLeftY, 
+    targetCentralityX = abs(960 - targetCenterX),
+
+    # similarly here: in svg coords, negative click distance means up. 
+    # here we invert it, so that negative values mean down
+    clickDistFromTargetCenterY = clickDistFromTargetCenterY * -1, 
+    clickDistFromTargetBBoxY = clickDistFromTargetBBoxY * -1,
+
+    # positive values for inward clicks (i.e.,towards the center), negative for outward clicks
+    centralityBias = ifelse(targetCenterX <= 1920/2,
+                            clickDistFromTargetCenterX, 
+                            clickDistFromTargetCenterX*-1),
+
+    inwardClick = ifelse(centralityBias > 0, TRUE, FALSE),
+
+    # did the participant click on the right box?
+    # also for hedge version, here we imagine a box surrounding the target center 
+    # this way, we can compare hedge and box version ;) 
+    boxWidth = 218, 
+    boxBorderLeft = targetCenterX - boxWidth/2, 
+    boxBorderRight = targetCenterX + boxWidth/2,
+    correctBox = ifelse(boxBorderLeft <= clickScaledX & clickScaledX <= boxBorderRight, TRUE, FALSE),
+
+    datacollection = as.factor("in-person - supervised"), 
+    sample = as.factor("na"),
+    studytype = as.factor("vali"), 
+  ) %>%
+  mutate(subjID = ifelse(grepl("2023-04-13T03:1", timestamp), "china075", subjID),
+         subjID = ifelse(grepl("2023-04-13T07:0", timestamp), "china077", subjID))%>%
+  select(-touchScreen)%>%
+  distinct(subjID, trialNr, .keep_all = T)%>%
+   mutate_if(is.character, as.factor)#%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
+
+#unique(tidy_data_leipzig$subjID)
+
+tidy_data_china%>%
+  filter(subjID == "china077")
+
+```
+
+```{r demographics}
+raw_demographics_china <- bind_rows(
+  read_xlsx("../../raw_data/gafo-cc/china/gafo-cc-participants_China_0421.xlsx", sheet = 1, 
+            col_types = c("text", "text", "text", "skip", "skip", "skip", "date", "date", "numeric", "text", "numeric", "numeric", "numeric", "numeric", "numeric", "text"))
+  )%>%
+  filter(!row_number() == 1)
+
+tidy_demographics_china <- raw_demographics_china %>% 
+  mutate(
+    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25)
+  )  %>%
+  select(-c(test_date, birth_date, comment))%>%
+  filter(status == "included", 
+         !is.na(ageinyears))%>%
+  select(-status)%>%
+  rename(subjid = id)
+
+tidy_demographics_china%>%
+  arrange(ageinyears)
+```
+
+```{r}
+data_china <- tidy_demographics_china%>%
+  left_join(tidy_data_china%>%rename_all(tolower),by = c("subjid"))%>%
+  distinct(subjid, trialnr, .keep_all = TRUE)
+
+data_china%>%
+  #mutate(age_group = substr(ageinyears, 1,1))%>%
+  #group_by(age_group)%>%
+  summarise(n = n_distinct(subjid))
+
+data_china%>%
+  group_by(subjid)%>%
+  summarise(n())
+
 ```
@@
 data <- bind_rows(
+  data_zambia,
   data_namibia%>%rename(younger_children = youngerchildren),
@@
   data_nigeria,
-  data_zambia,
-  data_stanford
+  data_plymouth,
+  data_stanford,
+  data_mex,
+  data_china
 )%>%
   #mutate(community = paste0("c",as.character(as.numeric(as.factor(community)))))%>%
-  filter(trialtype == "test")
+  filter(trialtype == "test")%>%
+  mutate(age_group = substr(ageinyears, 1,1))
+
+write_csv(data,"../data/gafo-cc-clean-data.csv")
+
+data%>%
+  filter(touchscreen == 2)
+```
+
+```{r}
+data_plymouth%>%
+  summarise(n= n_distinct(subjid))
 
@@
   summarise(n= n_distinct(subjid))
-
-```
-
-```{r}
-data%>%
-  filter(community == "leipzig")%>%
-  mutate(age_group = substr(ageinyears, 1,1))%>%
-  group_by(screen, age_group)%>%
-  summarise(n = n_distinct(subjid))
-```
-
-```{r}
-write_csv(data,"../data/gafo-cc-clean-data.csv")
 ```

### 2023-05-03 analysis/gafo-cc-visuals.Rmd
move to cluster

@@
                             stanford = "stanford (usa)",
-                            chimfunshi = "chimfunshi (sambia)"))
+                            chimfunshi = "chimfunshi (sambia)",
+                            mexico = "ocuilan (mexico)",
+                            plymouth = "plymouth (uk)",
+                            beijing = "beijing (china)"))
 ```
@@
   summarise(n= n_distinct(subjid))
+
+data%>%
+  group_by(community, age_group)%>%
+  summarise(n = n_distinct(subjid))
 ```
@@
 data%>%
-  filter(community != "chimfunshi (sambia)")%>%
+  #filter(community != "chimfunshi (sambia)")%>%
   group_by(community,subjid, ageinyears)%>%
@@
   geom_point(alpha = .25)+
-  geom_smooth(method = "glm")+
-  scale_color_colorblind(name = "Community")+
+  geom_smooth(method = "lm")+
+  scale_color_ptol(name = "Community")+
   ylim(0,1000)+
+  #facet_wrap(~community)+
   labs(x = "Age (in years)", y ="Imprecision (average click distance from target)")+
@@
 ```{r}
+data%>%
+  distinct(targetposition, targetcentralityx)%>%
+  expand_grid(random_click = runif(10000, min = 0, max = 1920))%>%
+  mutate(dist = abs(targetcentralityx - random_click))%>%
+  group_by(targetposition)%>%
+  summarise(random = mean(dist))
+
+```
+
+```{r}
 ptp<- data%>%
-  filter(community != "chimfunshi (sambia)")%>%
+  #filter(community != "chimfunshi (sambia)")%>%
   mutate(targetposition = factor(targetposition, levels = c(1:10)))%>%
+  #group_by(community, targetposition, age_group)%>%
   group_by(community, targetposition)%>%
@@
 
+alt1 <- data%>%
+  mutate(targetposition = factor(targetposition, levels = c(1:10)))%>%
+  group_by(targetposition)%>%
+  summarise(center = mean(targetcentralityx))%>%
+  mutate(group = "group")%>%
+  ungroup()
+
+alt2 <- data%>%
+  distinct(targetposition, targetcentralityx)%>%
+  expand_grid(random_click = runif(10000, min = 0, max = 1920))%>%
+  mutate(dist = abs(targetcentralityx - random_click))%>%
+  group_by(targetposition)%>%
+  summarise(random = mean(dist))%>%
+  mutate(group = "group")
+
 ggplot(ptp, aes(x = targetposition, y = mean, col = community))+
+  geom_line(data = alt1, aes(x = targetposition, y = center, group = group), lty = 3, alpha = 0.75, col = "black")+
+  geom_line(data = alt2, aes(x = targetposition, y = random, group = group), lty = 3, alpha = 0.75,  col = "black")+
   geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
   labs(x = "Target position (binned)", y = "Imprecision (average click distance from target)")+
-  scale_color_colorblind(name = "Community")+
+  scale_color_ptol(name = "Community")+
+  #facet_grid(~age_group)+
   ylim(0,1000)+
@@
          younger_children = scale(younger_children))%>%
-  group_by(subjid, household, children, younger_children)%>%
+  group_by(subjid,community, household, children, younger_children)%>%
   summarise(mean= mean(clickdistfromtargetcenterx))%>%

### 2023-05-31 analysis/gafo-cc-data-processing.Rmd
try running cv on cluster

@@
 
-# Leipzig
+1^# Leipzig
 
@@
   #read_xlsx("../../raw_data/gafo-cc/leipzig/Gafo-cc-leipzig-participants.xlsx", sheet = 1)
-  )
+  )%>%
+  mutate(status = ifelse(code == "o9qVPfZD", "keep", status))
 
@@
     ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
+    sex = ifelse(sex == "w", "f", sex)
   ) %>%
@@
   # convert all character vectors into factors
-  mutate_if(is.character, as.factor) %>%
 
@@
     sample = as.factor("na"),
-    studytype = as.factor("vali"), 
+    studytype = as.factor("vali")
   ) %>%
-  mutate(subjID =as.factor(subjID))%>%select(-touchScreen)%>%
+  mutate(subjID = ifelse(grepl("2023-03-11T19:4", timestamp) & subjID == "uksch048", "uksch049", subjID))%>%
+  mutate(subjID =as.factor(subjID))%>%
+  select(-touchScreen)%>%
+  mutate_if(is.character, as.factor)%>% 
   distinct(subjID, trialNr, .keep_all = T)#%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
 
-#unique(tidy_data_leipzig$subjID)
+unique(raw_data_plymouth$subjID)
 ```
@@
   summarise(n = n_distinct(subjID))
+
+tidy_data_plymouth%>%
+  filter(subjID == "uksch048")
 ```
@@
 raw_demographics_plymouth <- bind_rows(
-  read_xlsx("../../raw_data/gafo-cc/plymouth/participants_information.xlsx", sheet = 1)
-  )
+  read_xlsx("../../raw_data/gafo-cc/plymouth/participants_information_updated_2023_May.xlsx", sheet = 1)
+  )%>%
+  filter(tested == "yes")
 
@@
   select(-timestamp)%>%
-  rename_all(tolower)
+  rename_all(tolower)%>%
+  distinct(subjid, test_date)
 
@@
   filter(!is.na(ageinyears))
+
 ```
+
 ```{r}
@@
   #mutate(age_group = substr(ageinyears, 1,1))%>%
-  #group_by(age_group)%>%
+  group_by(age)%>%
   summarise(n = n_distinct(subjid))
@@
 data_plymouth%>%
-  group_by(subjid)%>%
+  group_by(age)%>%
   summarise(n())
@@
 data_mex%>%summarise(n = n_distinct(subjid))
+
+```
+```{r}
+# data_liz <- bind_rows(data_mex%>%
+#   filter(trialtype == "test", voiceover == F)%>%
+#   mutate(click_distance = abs(clickdistfromtargetcenterx))%>%
+#   select("subjid" ,"community" ,"ageinyears" , "trialnr", "targetposition",  "click_distance", "sex", "economical_activity_dad" , "economical_activity_mom"   ,    "parents_education_level_dad"  , "parents_education_level_mom" ,  "income" ,    "screen"           ,             "touchscreen"       ,            "household"     ,                "children" ,
+#         "younger_children"),
+# 
+# data_leipzig%>%
+#   filter(trialtype == "test", voiceover == F)%>%
+#   mutate(click_distance = abs(clickdistfromtargetcenterx))%>%
+#   select("subjid" ,"community" ,"ageinyears" , "trialnr", "targetposition",  "click_distance", "sex", "screen"           ,             "touchscreen"       ,            "household"     ,                "children" ,
+#         "younger_children")
+# )
+# 
+# 
+#   write_csv(data_liz, "../data/gafo-cc-data-lizbeth.csv")
+#   
+# 
+# data_liz <- read_csv("gafo-cc-data-lizbeth.csv")
+# 
+# 
+# data_liz_agg <- data_liz%>%
+#   group_by(subjid, community, ageinyears, sex, economical_activity_dad, economical_activity_mom, parents_education_level_dad, parents_education_level_mom, income, screen, touchscreen, household, children, younger_children)%>%
+#   summarise(mean_distance = mean(click_distance))%>% # aggregate data to get average click distance
+#   ungroup()%>%
+#   mutate(mean_distance_scale = scale(mean_distance, scale = F, center = T), # make the DV so that it has a mean of 0
+#          z_ageinyears = scale(ageinyears, scale = F, center = T), # scale numeric variables
+#          f_income = factor(income),# convert numeric variable into a factor because different values represent different categories
+#          z_household = scale(household)) 
+# 
+# 
+# library(lme4)
+# 
+# m1 <- lm(mean_distance_scale ~ z_ageinyears + community, data = data_liz_agg)
+# 
+# drop1(m1, test = "Chisq") # to get p-values for entire factors you need to use drop1
+# 
+# summary(m1)
 ```
@@
 
+# Argentina
+
+```{r read_data}
+# get all .json files
+files <- list.files("../../../../../../Cloud/QuantEx/Gafo-cc/data/argentina/", pattern = "*.json",recursive = T)
+
+# convert json files to tibbles
+raw_data_arg <- tibble()
+for (f in files) {
+  jf <- paste("../../../../../../Cloud/QuantEx/Gafo-cc/data/argentina/", f, sep = "")
+  jd <- jsonlite::fromJSON(paste(readLines(jf, warn = "FALSE"), collapse = ""))
+
+  # needed because hedge trials have numbers, box trials have characters
+  jd$targetPosition <- factor(as.character(jd$targetPosition))
+
+  raw_data_arg <- bind_rows(raw_data_arg, jd)
+}
+# remove variables that we don't need anymore
+rm(f, files, jf, jd)
+```
+
+```{r}
+tidy_data_arg <- raw_data_arg %>%
+
+  # convert all character vectors into factors
+  mutate_if(is.character, as.factor) %>%
+
+  mutate(
+
+    # attention! the SVG coord system starts with 0, 0 in upper left corner
+    # we transform the values so that 0, 0 is lower left corner (for plots etc)
+    clickScaledY = 1080 - clickScaledY,
+    targetY = 1080 - targetY, 
+    targetCenterY = 1080 - targetCenterY, 
+    eyeCenterRightY = 1080 - eyeCenterRightY,
+    eyeCenterLeftY = 1080 - eyeCenterLeftY,
+    pupilFinalRightY = 1080 - pupilFinalRightY,
+    pupilFinalLeftY = 1080 - pupilFinalLeftY, 
+    targetCentralityX = abs(960 - targetCenterX),
+
+    # similarly here: in svg coords, negative click distance means up. 
+    # here we invert it, so that negative values mean down
+    clickDistFromTargetCenterY = clickDistFromTargetCenterY * -1, 
+    clickDistFromTargetBBoxY = clickDistFromTargetBBoxY * -1,
+
+    # positive values for inward clicks (i.e.,towards the center), negative for outward clicks
+    centralityBias = ifelse(targetCenterX <= 1920/2,
+                            clickDistFromTargetCenterX, 
+                            clickDistFromTargetCenterX*-1),
+
+    inwardClick = ifelse(centralityBias > 0, TRUE, FALSE),
+
+    # did the participant click on the right box?
+    # also for hedge version, here we imagine a box surrounding the target center 
+    # this way, we can compare hedge and box version ;) 
+    boxWidth = 218, 
+    boxBorderLeft = targetCenterX - boxWidth/2, 
+    boxBorderRight = targetCenterX + boxWidth/2,
+    correctBox = ifelse(boxBorderLeft <= clickScaledX & clickScaledX <= boxBorderRight, TRUE, FALSE),
+
+    datacollection = as.factor("in-person - supervised"), 
+    sample = as.factor("na"),
+    studytype = as.factor("vali"),
+  ) %>%select(-touchScreen)#%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
+```
+
+```{r}
+tidy_data_arg%>%
+  summarise(n = n_distinct(subjID))
+
+tidy_data_arg%>%
+  group_by(subjID)%>%
+  summarise(n = n())
+```
+
+```{r demographics}
+raw_demographics_arg <- bind_rows(
+  read_xlsx("../../../../../../Cloud/QuantEx/Gafo-cc/data/argentina/gafo-cc-arg-participants.xlsx", sheet = 1, 
+            col_types = c("text", "text", "text", "text", "date", "date", "text", "text", "text", "numeric", "numeric", "numeric", "numeric", "numeric", "text"))
+  )
+
+tidy_demographics_arg <- raw_demographics_arg %>% 
+  filter(touchscreen!= "null")%>%
+  mutate(
+    test_date = as.Date(test_date, format = "%d/%m/%Y"),
+    birth_date = as.Date(birth_date, format = "%d/%m/%Y"),
+    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25)
+  )  %>%
+  #filter(status == "keep")%>%
+  select(-c(test_date, birth_date, comment, Edad))%>%
+  rename(subjid = id)%>%
+  filter(!is.na(ageinyears))%>%
+  mutate(touchscreen = as.numeric(touchscreen),
+         household = as.numeric(household),
+         children = as.numeric(children),
+         younger_children = as.numeric(younger_children))
+
+tidy_demographics_arg%>%
+  filter(ageinyears < 0)
+```
+
+```{r}
+data_arg <- tidy_demographics_arg%>%
+  left_join(tidy_data_arg%>%rename_all(tolower),by = c("subjid"))%>%
+  mutate(community = "buenos_aires")%>%
+  distinct(subjid, trialnr, .keep_all = TRUE)
+```
+
 # Merge
@@
   data_mex,
-  data_china
+  data_china, 
+  data_arg
 )%>%
@@
   filter(trialtype == "test")%>%
-  mutate(age_group = substr(ageinyears, 1,1))
+  mutate(age_group = substr(ageinyears, 1,1), 
+         trialnr = as.numeric(factor(trialnr)))%>%
+  select(subjid, community, age_group, ageinyears, sex, screen, touchscreen, household, children, younger_children, trialnr, targetposition, targetcentralityx, clickdistfromtargetcenterx)%>%
+  filter(ageinyears > 1)
 
@@
 data%>%
-  filter(touchscreen == 2)
+  #group_by(community)%>%
+  summarise(n = n_distinct(subjid))
 ```
@@
 ```{r}
-data_plymouth%>%
+data%>%
+  filter(touchscreen == 2)%>%
+  distinct(subjid)
+
+unique(data$screen)
+
+unique(data$touchscreen)
+
+unique(data$household)
+
+unique(data$children)
+
+unique(data$younger_children)
+```
+
+```{r}
+data_arg%>%
   summarise(n= n_distinct(subjid))

### 2023-07-29 analysis/gafo-cc-analysis.Rmd
test run model per site

--- 2022-05-10 analysis/gafo-cc-analysis.Rmd
@@
 library(tidyverse)
+library(tidybayes)
+library(ggthemes)
 library(brms)
@@
 mdata <- read_csv("../data/gafo-cc-clean-data.csv")%>%
+  ungroup()%>%
   mutate(ageinyears = scale(ageinyears),
@@
          trialnr = scale(trialnr),
-         children = scale(children),
-         youngerchildren = scale(youngerchildren),
-         touchscreen = factor(touchscreen.x),
-        screen = factor(screen))
-```
+         #children = scale(children),
+         #household = scale(household),
+         #younger_children = scale(younger_children),
+         touchscreen = factor(touchscreen),
+        screen = factor(screen),
+        click = abs(clickdistfromtargetcenterx))%>%
+  #filter(community != "chimfunshi")%>%
+  select(subjid,community,ageinyears,children, household, younger_children,trialnr, screen,touchscreen, targetcentralityx, click )
 
-```{r}
-bm_base <- brm(abs(clickdistfromtargetcenterx) ~ ageinyears  + targetcentralityx + (trialnr|subjid), 
-                              data   = mdata, 
-                              family = Gamma(link = "log"),
-                              warmup = 1000, 
-                              iter   = 4000, 
-                              chains = 4, 
-                              cores  = 4)%>%
-  add_criterion(., c("waic","loo"))
-
-bm_null <- brm(abs(clickdistfromtargetcenterx) ~ 1 + (trialnr|subjid), 
-                              data   = mdata, 
-                              family = Gamma(link = "log"),
-                              warmup = 1000, 
-                              iter   = 4000, 
-                              chains = 4, 
-                              cores  = 4)%>%
-  add_criterion(., c("waic","loo"))
-
-loo_compare(bm_base, bm_null)%>%as_tibble(rownames = "model")
+mdata%>%
+  ggplot(aes(x = click))+
+  geom_density()
 
@@
 ```{r}
-plot(bm_age)
+bm_int_id <- brm(click ~ ageinyears  * targetcentralityx + (targetcentralityx+trialnr|subjid) + (ageinyears * targetcentralityx |community),
+                              data   = mdata,
+                              family = Gamma(link = "log"),
+                              warmup = 2000,
+                              iter   = 6000,
+                              chains = 4,
+                              cores  = 4,
+                 control = list(adapt_delta = 0.95),
+                              backend = "cmdstanr")%>%
+  add_criterion(., c("waic","loo"))
 
-pp_check(bm_age)+xlim(0,2000)
+bm_id <- brm(click ~ ageinyears  + targetcentralityx + (targetcentralityx|subjid) + (ageinyears |community), 
+                              data   = mdata, 
+                              family = Gamma(link = "log"),
+                              warmup = 2000, 
+                              iter   = 6000, 
+                              chains = 4, 
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")%>%
+  add_criterion(., c("waic","loo"))
 
-bm_age
+# bm_int <- brm(click ~ ageinyears  * targetcentralityx + (trialnr|subjid) + (ageinyears * targetcentralityx |community), 
+#                               data   = mdata, 
+#                               family = Gamma(link = "log"),
+#                               warmup = 2000, 
+#                               iter   = 6000, 
+#                               chains = 4, 
+#                               cores  = 4,
+#               control = list(adapt_delta = 0.95),
+#                               backend = "cmdstanr")%>%
+#   add_criterion(., c("waic","loo"))
+# 
+bm_base <- brm(click ~ ageinyears  + targetcentralityx + (1|subjid) + (ageinyears |community),
+                              data   = mdata,
+                              family = Gamma(link = "log"),
+                              warmup = 2000,
+                              iter   = 6000,
+                              chains = 4,
+                              cores  = 4,
+               control = list(adapt_delta = 0.95),
+                              backend = "cmdstanr")%>%
+  add_criterion(., c("waic","loo"))
+
+bm_fix <- brm(click ~ ageinyears  + targetcentralityx + (1|subjid) + (1 |community),
+                              data   = mdata,
+                              family = Gamma(link = "log"),
+                              warmup = 2000,
+                              iter   = 6000,
+                              chains = 4,
+                              cores  = 4,
+               control = list(adapt_delta = 0.95),
+                              backend = "cmdstanr")%>%
+  add_criterion(., c("waic","loo"))
+# 
+# bm_nage <- brm(click ~ targetcentralityx + (trialnr|subjid) + (1 |community), 
+#                               data   = mdata, 
+#                               family = Gamma(link = "log"),
+#                               warmup = 2000, 
+#                               iter   = 6000, 
+#                               chains = 4, 
+#                               cores  = 4,
+#                control = list(adapt_delta = 0.95),
+#                               backend = "cmdstanr")%>%
+#   add_criterion(., c("waic","loo"))
+# 
+# bm_ntc <- brm(click ~ ageinyears  + (trialnr|subjid) + (ageinyears|community), 
+#                               data   = mdata, 
+#                               family = Gamma(link = "log"),
+#                               warmup = 2000, 
+#                               iter   = 6000, 
+#                               chains = 4, 
+#                               cores  = 4,
+#               control = list(adapt_delta = 0.95),
+#                               backend = "cmdstanr")%>%
+#   add_criterion(., c("waic","loo"))
+
+bm_co <- brm(click ~ 1 + (1|subjid)+ (1|community), 
+                              data   = mdata, 
+                              family = Gamma(link = "log"),
+                              warmup = 2000, 
+                              iter   = 6000, 
+                              chains = 4, 
+                              cores  = 4,
+               control = list(adapt_delta = 0.95),
+                              backend = "cmdstanr")%>%
+  add_criterion(., c("waic","loo"))
+
+bm_null <- brm(click ~ 1 + (1|subjid), 
+                              data   = mdata, 
+                              family = Gamma(link = "log"),
+                              warmup = 2000, 
+                              iter   = 6000, 
+                              chains = 4, 
+                              cores  = 4,
+               control = list(adapt_delta = 0.95),
+                              backend = "cmdstanr")%>%
+  add_criterion(., c("waic","loo"))
+
+loo_compare(bm_null,
+            bm_co,
+            #bm_ntc,
+            #bm_nage,
+            #bm_base,
+            #bm_fix,
+            #bm_int,
+            #bm_id,
+            #bm_int_id, 
+            criterion = "loo")%>%as_tibble(rownames = "model")%>%left_join(
+model_weights(bm_null,
+            bm_co,
+            #bm_ntc,
+            #bm_nage,
+            #bm_base,
+            #bm_fix,
+            #bm_int,
+            #bm_id,
+            #bm_int_id, 
+            weights = "loo")%>%as_tibble(rownames = "model")%>%rename(waic_weight = value))
+
 ```
@@
 ```{r}
-bm_screen <- brm(abs(clickdistfromtargetcenterx) ~ ageinyears  + targetcentralityx + screen + (trialnr|subjid), 
-                              data   = mdata, 
-                              family = Gamma(link = "log"),
-                              warmup = 1000, 
+plot(bm_int_id)
+
+pp_check(bm_int_id)
+
+```
+
+```{r}
+ndata <- mdata%>%
+  distinct(community)%>%
+  expand_grid(ageinyears = unique(mdata$ageinyears))%>%
+  expand_grid(targetcentralityx = c(min(mdata$targetcentralityx),max(mdata$targetcentralityx)))
+
+post <- fitted(bm_id, newdata = ndata, re_formula =~(ageinyears|community))%>%
+  as_tibble() %>%
+  bind_cols(ndata)%>%
+  mutate(ageinyears = ageinyears + mean(data$ageinyears),
+         targetcentralityx = factor(targetcentralityx, labels = c("middle","edge")))
+
+ggplot()+
+  geom_smooth(data = post, aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
+  theme_bw()+
+  scale_color_ptol(name = "Community")+
+  scale_fill_ptol(name = "Community")+
+  facet_grid(~targetcentralityx)+
+  labs(x = "Age", y="Imprecision")
+
+range(mdata$targetcentralityx)
+```
+
+```{r}
+ndata <- mdata%>%
+  distinct(community)%>%
+  expand_grid(ageinyears = c(-1,0,1))%>%
+  expand_grid(targetcentralityx = c(min(mdata$targetcentralityx),max(mdata$targetcentralityx)))
+
+post <- fitted(bm_int_id, newdata = ndata, re_formula =~(targetcentralityx|community))%>%
+  as_tibble() %>%
+  bind_cols(ndata)
+
+ggplot()+
+  geom_smooth(data = post, aes(x = targetcentralityx, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
+  theme_bw()+
+  scale_color_ptol(name = "Community")+
+  scale_fill_ptol(name = "Community")+
+  facet_grid(~ageinyears)+
+  labs(x = "Target centrality", y="Imprecision")
+
+range(mdata$ageinyears)
+```
+
+```{r}
+ps <- bm_int_id%>%posterior_samples()%>%
+  select(b_targetcentralityx, contains("targetcentralityx") & starts_with("r_community"))%>%
+  select(!contains("ageinyears"))%>%
+  pivot_longer(cols = c(-b_targetcentralityx), names_to = "site", values_to = "value")%>%
+  mutate(site= str_remove(site,"r_community"),
+         site= str_remove(site,"Intercept"),
+         site= str_remove(site,"targetcentralityx"),
+         site= str_remove(site,"\\["),
+         site= str_remove(site,"\\]"),
+         site= str_remove(site,"\\,"))%>%
+  mutate(est = value + b_targetcentralityx)
+
+ggplot(ps,aes(y = site, x = est)) +
+ stat_halfeye(alpha = .7, .width = c(.95, .80)) +
+    labs(x = "Posterior estimate", y ="")+
+  guides(fill = "none")+
+  #facet_grid(~type, scales = "free_x")+
+  #geom_vline(xintercept = 0, linetype = "dashed") +
+  theme_bw()
+```
+```{r}
+ps <- bm_int_id%>%posterior_samples()%>%
+  select("b_Intercept", "b_targetcentralityx",starts_with("r_community"))%>%
+  pivot_longer(cols = c(3:50), names_to = "site", values_to = "value")%>%
+  mutate(type = ifelse(grepl("Intercept", site), "intercept", "age"),
+         site= str_remove(site,"r_community"),
+         site= str_remove(site,"Intercept"),
+         site= str_remove(site,"ageinyears"),
+         site= str_remove(site,"\\["),
+         site= str_remove(site,"\\]"),
+         site= str_remove(site,"\\,"))%>%
+  pivot_longer(cols = c(b_Intercept, b_ageinyears), names_to = "fix_param", values_to = "fix_value")%>%
+  mutate(fix_param= tolower(str_remove(fix_param,"b_")),
+         fix_param = ifelse(fix_param == "ageinyears", "age", fix_param))%>%
+  filter(type == fix_param)%>%
+  mutate(est = value + fix_value)
+
+ggplot(ps,aes(y = site, x = est)) +
+ stat_halfeye(alpha = .7, .width = c(.95, .80)) +
+    labs(x = "Posterior estimate", y ="")+
+  guides(fill = "none")+
+  facet_grid(~type, scales = "free_x")+
+  #geom_vline(xintercept = 0, linetype = "dashed") +
+  theme_bw()
+```
+
+# Screens
+
+```{r}
+sdata <- mdata%>%
+  group_by(subjid, ageinyears,community,screen, touchscreen)%>%
+  summarise(mean_click = mean(click))%>%
+  group_by(community)%>%
+  mutate(mean_click = scale(mean_click))%>%
+  na.omit()
+
+```
+
+```{r}
+bm_s_base <- brm(mean_click ~ ageinyears  + (ageinyears |community), 
+                              data   = sdata, 
+                              family = "Gaussian",
+                              warmup = 2000, 
                               iter   = 4000, 
                               chains = 4, 
-                              cores  = 4)%>%
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")%>%
   add_criterion(., c("waic","loo"))
 
-bm_touch <- brm(abs(clickdistfromtargetcenterx) ~ ageinyears  + targetcentralityx + touchscreen + (trialnr|subjid), 
-                              data   = mdata, 
-                              family = Gamma(link = "log"),
-                              warmup = 1000, 
+bm_s_s_fix <- brm(mean_click ~ ageinyears  + screen + (ageinyears |community), 
+                              data   = sdata, 
+                              family = "Gaussian",
+                              warmup = 2000, 
                               iter   = 4000, 
                               chains = 4, 
-                              cores  = 4)%>%
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")%>%
+  add_criterion(., c("waic","loo"))
+
+bm_s_s_rand <- brm(mean_click ~ ageinyears  + screen + (ageinyears + screen|community), 
+                              data   = sdata, 
+                              family = "Gaussian",
+                              warmup = 2000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")%>%
+  add_criterion(., c("waic","loo"))
+
+bm_s_ts_fix <- brm(mean_click ~ ageinyears  + touchscreen + (ageinyears |community), 
+                              data   = sdata, 
+                              family = "Gaussian",
+                              warmup = 2000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")%>%
+  add_criterion(., c("waic","loo"))
+
+bm_s_ts_rand <- brm(mean_click ~ ageinyears  + touchscreen + (ageinyears + touchscreen|community), 
+                              data   = sdata, 
+                              family = "Gaussian",
+                              warmup = 2000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")%>%
   add_criterion(., c("waic","loo"))
@@
 ```{r}
-bm_child <- brm(abs(clickdistfromtargetcenterx) ~ ageinyears  + targetcentralityx + children + (trialnr|subjid), 
+loo_compare(bm_s_base,
+            bm_s_s_fix,
+            bm_s_s_rand,
+            bm_s_ts_fix,
+            bm_s_ts_rand
+            )%>%as_tibble(rownames = "model")%>%left_join(
+model_weights(bm_s_base, bm_s_s_fix,
+            bm_s_s_rand,
+            bm_s_ts_fix,
+            bm_s_ts_rand,
+            weights = "waic")%>%as_tibble(rownames = "model")%>%rename(waic_weight = value))
+```
+
+# Household demographics
+
+```{r}
+cdata <- mdata%>%
+  group_by(subjid, community, ageinyears, children, household, younger_children)%>%
+  summarise(mean_click = mean(click))%>%
+  group_by(community)%>%
+  mutate(children = scale(children), 
+         household = scale(household), 
+         younger_children = scale(younger_children), 
+         #mean_click = scale(mean_click)
+         )%>%
+  na.omit()
+
+ggplot(cdata, aes(x = mean_click))+
+  geom_density()
+```
+
+```{r}
+bm_dem_base <- brm(mean_click ~ ageinyears  + (ageinyears |community), 
+                              data   = cdata, 
+                              lognormal(),
+                              warmup = 2000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")%>%
+  add_criterion(., c("waic","loo"))
+
+bm_dem_hh_fix <- brm(mean_click ~ ageinyears  + household + (ageinyears |community), 
+                              data   = cdata, 
+                              family = Gamma(link = "log"),
+                              warmup = 2000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")%>%
+  add_criterion(., c("waic","loo"))
+
+bm_dem_hh_rand <- brm(mean_click ~ ageinyears  + household + (ageinyears + household|community), 
+                              data   = cdata, 
+                              family = lognormal(),
+                              warmup = 2000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")%>%
+  add_criterion(., c("waic","loo"))
+
+bm_dem_hh_rand_int <- brm(mean_click ~ ageinyears  * household + (ageinyears * household|community), 
+                              data   = cdata, 
+                              lognormal(),
+                              warmup = 2000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")%>%
+  add_criterion(., c("waic","loo"))
+
+bm_dem_c_fix <- brm(mean_click ~ ageinyears  + children + (ageinyears |community), 
+                              data   = cdata, 
+                              lognormal(),
+                              warmup = 2000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")%>%
+  add_criterion(., c("waic","loo"))
+
+bm_dem_c_rand <- brm(mean_click ~ ageinyears  + children + (ageinyears + children|community), 
+                              data   = cdata, 
+                              lognormal(),
+                              warmup = 2000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")%>%
+  add_criterion(., c("waic","loo"))
+
+bm_dem_yc_fix <- brm(mean_click ~ ageinyears  + younger_children + (ageinyears |community), 
+                              data   = cdata, 
+                              lognormal(),
+                              warmup = 2000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")%>%
+  add_criterion(., c("waic","loo"))
+
+bm_dem_yc_rand <- brm(mean_click ~ ageinyears  + younger_children + (ageinyears + younger_children|community), 
+                              data   = cdata, 
+                              lognormal(),
+                              warmup = 2000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")%>%
+  add_criterion(., c("waic","loo"))
+
+```
+
+```{r}
+
+loo_compare(bm_dem_base,
+            bm_dem_hh_fix,
+            bm_dem_hh_rand,
+            #bm_dem_hh_rand_int,
+            bm_dem_c_fix,
+            bm_dem_c_rand,
+            bm_dem_yc_fix#,
+            #bm_dem_yc_rand
+            )%>%as_tibble(rownames = "model")%>%left_join(
+model_weights(bm_dem_base,
+            bm_dem_hh_fix,
+            bm_dem_hh_rand,
+            #bm_dem_hh_rand_int,
+            bm_dem_c_fix,
+            bm_dem_c_rand,
+            bm_dem_yc_fix,
+            #bm_dem_yc_rand,
+            weights = "waic")%>%as_tibble(rownames = "model")%>%rename(waic_weight = value))
+```
+```{r}
+ncdata <- cdata%>%
+  distinct(community)%>%
+  expand_grid(ageinyears = 0)%>%
+  expand_grid(household = c(min(cdata$household):max(cdata$household)))
+
+cpost <- fitted(bm_dem_hh_fix, newdata = ncdata, re_formula =~(1|community))%>%
+  as_tibble() %>%
+  bind_cols(ncdata)
+
+ggplot()+
+  geom_smooth(data = cpost, aes(x = household, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
+  theme_bw()+
+  scale_color_ptol(name = "Community")+
+  scale_fill_ptol(name = "Community")+
+  facet_grid(~ageinyears)+
+  labs(x = "Household size (scaled)", y="Imprecision")
+
+range(mdata$targetcentralityx)
+```
+```{r}
+ncdata <- cdata%>%
+  distinct(community)%>%
+  expand_grid(ageinyears = 0)%>%
+  expand_grid(household = c(min(cdata$household):max(cdata$household)))
+
+cpost <- fitted(bm_dem_hh_rand, newdata = ncdata, re_formula =~(household|community))%>%
+  as_tibble() %>%
+  bind_cols(ncdata)
+
+ggplot()+
+  geom_smooth(data = cpost, aes(x = household, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
+  theme_bw()+
+  scale_color_ptol(name = "Community")+
+  scale_fill_ptol(name = "Community")+
+  facet_grid(~community)+
+  labs(x = "Household size (scaled)", y="Imprecision")
+
+```
+
+```{r}
+as_draws_df(bm_dem_hh_rand)%>%
+  select(contains("household"))%>%
+  pivot_longer(cols = contains("household]"), names_to = "community", values_to = "value")%>%
+  mutate(post = value + b_household)%>%
+  ggplot(aes(x= post, y = community))+
+  stat_slabinterval()+
+  theme_bw()
+```
+
+# Household and screens
+
+```{r}
+scdata <- mdata%>%
+  filter(touchscreen != 2
+         )%>%
+  group_by(subjid, community, ageinyears, touchscreen, household, children, younger_children)%>%
+  summarise(mean_click = mean(click))%>%
+  mutate(older_children = children - 1 - younger_children)%>%
+  group_by(community)%>%
+  mutate(
+         household = scale(household), 
+         children = scale(children), 
+         older_children = scale(older_children),
+         younger_children = scale(younger_children)
+
+         #mean_click = scale(mean_click)
+         )%>%
+  na.omit()%>%
+  filter(touchscreen != 2)%>%
+  mutate(touchscreen = droplevels(touchscreen))
+
+```
+
+```{r}
+bm_base <- brm(mean_click ~ ageinyears + (ageinyears |community), 
+                              data   = scdata, 
+                              family = lognormal(),
+                              warmup = 2000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")%>%
+  add_criterion(., c("waic","loo"))
+
+bm_full_fix <- brm(mean_click ~ ageinyears + touchscreen + household + younger_children + children + (ageinyears |community), 
+                              data   = scdata, 
+                              family = lognormal(),
+                              warmup = 2000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")%>%
+  add_criterion(., c("waic","loo"))
+
+bm_fullc_fix <- brm(mean_click ~ ageinyears + touchscreen + younger_children + older_children + (ageinyears |community), 
+                              data   = scdata, 
+                              family = lognormal(),
+                              warmup = 2000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")%>%
+  add_criterion(., c("waic","loo"))
+
+bm_full_rand <- brm(mean_click ~ ageinyears + touchscreen + household + younger_children + children + (touchscreen + household + younger_children + children + ageinyears |community), 
+                              data   = scdata, 
+                              family = lognormal(),
+                              warmup = 2000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")%>%
+  add_criterion(., c("waic","loo"))
+
+bm_hhts_fix <- brm(mean_click ~ ageinyears + touchscreen + household + (ageinyears |community), 
+                              data   = scdata, 
+                              family = lognormal(),
+                              warmup = 2000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")%>%
+  add_criterion(., c("waic","loo"))
+
+bm_hhts_rand <- brm(mean_click ~ ageinyears + touchscreen + household + (touchscreen + household  + ageinyears |community), 
+                              data   = scdata, 
+                              family = lognormal(),
+                              warmup = 2000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")%>%
+  add_criterion(., c("waic","loo"))
+
+bm_hhts_rand_2 <- brm(mean_click ~ ageinyears + touchscreen + household + (household  + ageinyears |community), 
+                              data   = scdata, 
+                              family = lognormal(),
+                              warmup = 2000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")%>%
+  add_criterion(., c("waic","loo"))
+
+bm_cts_fix <- brm(mean_click ~ ageinyears + touchscreen + children + (ageinyears |community), 
+                              data   = scdata, 
+                              family = lognormal(),
+                              warmup = 2000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")%>%
+  add_criterion(., c("waic","loo"))
+
+bm_cts_fix_int <- brm(mean_click ~ ageinyears * children + touchscreen  + (ageinyears |community), 
+                              data   = scdata, 
+                              family = lognormal(),
+                              warmup = 2000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")%>%
+  add_criterion(., c("waic","loo"))
+
+bm_cts_rand <- brm(mean_click ~ ageinyears + children + touchscreen + (ageinyears + children + touchscreen |community), 
+                              data   = scdata, 
+                              family = lognormal(),
+                              warmup = 2000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")%>%
+  add_criterion(., c("waic","loo"))
+
+bm_cts_rand_int <- brm(mean_click ~ ageinyears * children + touchscreen + (ageinyears * children + touchscreen |community), 
+                              data   = scdata, 
+                              family = lognormal(),
+                              warmup = 2000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")%>%
+  add_criterion(., c("waic","loo"))
+
+bm_ycts_fix <- brm(mean_click ~ ageinyears + touchscreen + younger_children + (ageinyears |community), 
+                              data   = scdata, 
+                              family = lognormal(),
+                              warmup = 2000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")%>%
+  add_criterion(., c("waic","loo"))
+
+bm_octs_fix <- brm(mean_click ~ ageinyears + touchscreen + older_children + (ageinyears |community), 
+                              data   = scdata, 
+                              family = lognormal(),
+                              warmup = 2000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")%>%
+  add_criterion(., c("waic","loo"))
+```
+
+```{r}
+loo_compare(bm_base,
+            bm_full_fix, 
+            bm_full_rand,
+            bm_fullc_fix,
+            bm_cts_fix,
+            bm_ycts_fix,
+            bm_octs_fix
+            #bm_hhts_fix#,
+            #bm_cts_fix_int,
+            #bm_cts_rand_int,
+            #bm_cts_rand#,
+            #bm_hhts_rand_2, 
+            #bm_hhts_rand
+            )%>%as_tibble(rownames = "model")
+
+model_weights(bm_base, 
+            bm_octs_fix, criterion = "loo")%>%as_tibble(rownames = "model")
+
+fixef(bm_octs_fix)
+```
+```{r}
+ndata <- scdata%>%
+  distinct(community, ageinyears)
+
+post <- fitted(bm_base, newdata = ndata, re_formula =~(ageinyears|community))%>%
+  as_tibble() %>%
+  bind_cols(ndata)%>%
+  mutate(ageinyears = ageinyears + mean(data$ageinyears))
+
+ggplot()+
+  geom_smooth(data = post, aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
+  theme_bw()+
+  scale_color_ptol(name = "Community")+
+  scale_fill_ptol(name = "Community")+
+  labs(x = "Age", y="Imprecision")#+
+  facet_wrap(~community)+guides(col = "none", fill = "none")
+```
+
+```{r}
+pssc <- bm_octs_fix%>%posterior_samples()%>%
+  select("b_ageinyears","b_touchscreen1", "b_older_children")%>%
+  pivot_longer(cols = everything(), names_to = "parameter", values_to = "value")%>%
+  mutate(parameter= tolower(str_remove(parameter,"b_")))
+
+ggplot(pssc,aes(y = parameter, x = value)) +
+ stat_halfeye(alpha = .7, .width = c(.95, .89)) +
+    labs(x = "Posterior estimate", y ="")+
+  guides(fill = "none")+
+  #facet_grid(~type, scales = "free_x")+
+  geom_vline(xintercept = 0, linetype = "dashed") +
+  theme_bw()
+```
+
+```{r}
+as_draws_df(bm_cts_rand_int)%>%
+  select(contains("children"))%>%
+  select(contains("children"))%>%
+  pivot_longer(cols = contains("children]"), names_to = "community", values_to = "value")%>%
+  mutate(post = value + b_children, 
+         community = str_remove(community, "r_community"),
+         community = str_remove(community, ",children"))%>%
+  ggplot(aes(x= post, y = community))+
+  stat_slabinterval()+
+  xlim(-0.15, 0.1)+
+  theme_bw()
+```
+
+```{r}
+ncdata <- scdata%>%
+  distinct(community)%>%
+  expand_grid(ageinyears = 0)%>%
+  mutate(touchscreen = 1)%>%
+  expand_grid(children = c(min(scdata$children):max(scdata$children)))
+
+cpost <- fitted(bm_cts_rand_int, newdata = ncdata, re_formula =~(children|community))%>%
+  as_tibble() %>%
+  bind_cols(ncdata)
+
+ggplot()+
+  geom_smooth(data = cpost, aes(x = children, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
+  theme_bw()+
+  scale_color_ptol(name = "Community")+
+  scale_fill_ptol(name = "Community")+
+  facet_grid(~community)+
+  labs(x = "No of children (scaled)", y="Imprecision")
+
+```
+
+# Cross-validation
+
+```{r}
+
+bm_base <- brm(click ~ targetcentralityx + ageinyears + (trialnr + targetcentralityx|subjid),
                               data   = mdata, 
                               family = Gamma(link = "log"),
-                              warmup = 1000, 
-                              iter   = 4000, 
+                              warmup = 2000, 
+                              iter   = 6000, 
                               chains = 4, 
-                              cores  = 4)%>%
-  add_criterion(., c("waic","loo"))
+                              cores  = 4,
+                              threads = threading(8),
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")
 
-bm_young <- brm(abs(clickdistfromtargetcenterx) ~ ageinyears  + targetcentralityx + youngerchildren + (trialnr|subjid), 
+bm_cult <- brm(click ~ targetcentralityx + ageinyears + (trialnr + targetcentralityx|subjid)+ (1 |community),
                               data   = mdata, 
                               family = Gamma(link = "log"),
-                              warmup = 1000, 
-                              iter   = 4000, 
+                              warmup = 2000, 
+                              iter   = 6000, 
                               chains = 4, 
-                              cores  = 4)%>%
-  add_criterion(., c("waic","loo"))
+                              cores  = 4,
+                              threads = threading(8),
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")
+
+bm_cult_x_age <- brm(click ~ targetcentralityx + ageinyears + (trialnr + targetcentralityx|subjid)+ (ageinyears |community),
+                              data   = mdata, 
+                              family = Gamma(link = "log"),
+                              warmup = 2000, 
+                              iter   = 6000, 
+                              chains = 4, 
+                              cores  = 4,
+                              threads = threading(8),
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")
+
 ```
+
+```{r}
+six_fold_cross_validation <- function(data, m1, m2, m3, repeats) {
+
+  N_ids = n_distinct(data$subjid)
+#Prepare results DF
+  results <- tibble(m1_score=numeric(), m2_score=numeric() , m3_score=numeric(), m3_beats_m2=logical(), m3_beats_m1=logical(), m2_beats_m1=logical(), m1 = character(), m2 = character(), m3 = character())
+
+#Repeat the whole shebang several times
+  for(i in 1:repeats) {
+
+  # Split dataset into 6 bins
+  bin_data <- data%>%group_by(community) %>% mutate(bin = rep(1:6, length.out = n()))
+
+for(j in 1:6) {
+    # Use bin j as "hold out" data
+    testing_ids <- bin_data%>%filter(bin == j)%>%pull(subjid)
+    training_ids <- bin_data%>%filter(bin != j)%>%pull(subjid)
+    # Safety check - is partition complete and disjoint?
+    stopifnot(length(testing_ids) + length(training_ids) == N_ids)
+    stopifnot(length(intersect(testing_ids, training_ids)) == 0)
+# Create two separate dataframes
+    testing_data <- filter(data, subjid %in% testing_ids)
+    training_data <- filter(data, subjid %in% training_ids)
+
+    # Train models
+    up_m1 <- update(m1, newdata=training_data, cores=4,backend = "cmdstanr")
+    up_m2 <- update(m2, newdata=training_data, cores=4,backend = "cmdstanr")
+    up_m3 <- update(m3, newdata=training_data, cores=4,backend = "cmdstanr")
+
+    # Sample predictions
+    preds_m1 <- posterior_predict(up_m1, newdata=testing_data, allow_new_levels=TRUE, sample_new_levels="gaussian")
+    preds_m2 <- posterior_predict(up_m2, newdata=testing_data, allow_new_levels=TRUE, sample_new_levels="gaussian")
+    preds_m3 <- posterior_predict(up_m3, newdata=testing_data, allow_new_levels=TRUE, sample_new_levels="gaussian")
+
+    # Evaluate predictive accuracy
+  score_m1 <- mean(sqrt(colMeans((testing_data$mean_click - t(preds_m1))**2)))
+  score_m2 <- mean(sqrt(colMeans((testing_data$mean_click - t(preds_m2))**2)))
+  score_m3 <- mean(sqrt(colMeans((testing_data$mean_click - t(preds_m3))**2)))
+
+  m1_name <-  as.character(substitute(m1))
+  m2_name <-  as.character(substitute(m2))
+  m3_name <-  as.character(substitute(m3))
+
+    # Record results
+    results <- add_row(results,
+                       m1_score = score_m1, 
+                       m2_score = score_m2, 
+                       m3_score = score_m3, 
+                       m3_beats_m2 = m3_score < m2_score,
+                       m3_beats_m1 = m3_score < m1_score,
+                       m2_beats_m1 = m2_score < m1_score, 
+                       m1  = m1_name, 
+                       m2 = m2_name, 
+                       m3 = m3_name)
+ }
+  }
+  return(results)
+}
+```
+
+## Test for importance of culture and effect of age
+
+```{r}
+cv_cult <- six_fold_cross_validation(scdata, bm_base, bm_cult, bm_cult_x_age, 2)
+```
+
+## Test for

### 2023-07-29 analysis/gafo-cc-data-processing.Rmd
test run model per site

@@
 
+unique(tidy_data_namibia$subjID)
 ```
@@
   mutate(age_group = substr(ageinyears, 1,1))%>%
-  group_by(age_group)%>%
+  #group_by(age_group)%>%
   summarise(n = n_distinct(subjid))
@@
 
-1^# Leipzig
+# Leipzig
 
@@
   ) %>%
-  mutate(subjID = ifelse(grepl("2023-03-11T19:4", timestamp) & subjID == "uksch048", "uksch049", subjID))%>%
+  mutate(subjID = ifelse(grepl("2023-03-11T19:4", timestamp) & subjID == "uksch048", "uksch049", subjID),
+         subjID = ifelse(subjID == "Uksch002", "uksch002", subjID),
+         subjID = ifelse(subjID == "Uksch003", "uksch003", subjID))%>%
   mutate(subjID =as.factor(subjID))%>%
@@
 tidy_data_plymouth%>%
-  filter(subjID == "uksch048")
+  filter(subjID == "uksch002")
 ```
@@
 tidy_demographics_plymouth <- raw_demographics_plymouth %>% 
-  select(-test_date)%>%
-  left_join(test_date_plymouth)%>%
+  #select(-test_date)%>%
+  #left_join(test_date_plymouth)%>%
   mutate(
@@
   #mutate(age_group = substr(ageinyears, 1,1))%>%
-  group_by(age)%>%
+  #group_by(age)%>%
   summarise(n = n_distinct(subjid))
@@
 
+ data_plymouth%>%
+   filter(is.na(durationanimationballoontotal))
 ```
@@
 
+n_distinct(tidy_data_china$subjID)
+
+tidy_data_china%>%
+  group_by(subjID)%>%
+  summarise(n())
 ```
@@
 raw_demographics_china <- bind_rows(
-  read_xlsx("../../raw_data/gafo-cc/china/gafo-cc-participants_China_0421.xlsx", sheet = 1, 
+  read_xlsx("../../raw_data/gafo-cc/china/gafo-cc-participants_China_0608_final_updated.xlsx", sheet = 1, 
             col_types = c("text", "text", "text", "skip", "skip", "skip", "date", "date", "numeric", "text", "numeric", "numeric", "numeric", "numeric", "numeric", "text"))
@@
 tidy_demographics_arg <- raw_demographics_arg %>% 
-  filter(touchscreen!= "null")%>%
+  filter(Status== "keep")%>%
   mutate(
@@
 tidy_demographics_arg%>%
-  filter(ageinyears < 0)
+  filter(ageinyears < 2)
+```
+
+```{r}
+raw_demographics_arg%>%
+  filter(!id %in% tidy_data_arg$subjID)
+
+tidy_data_arg%>%
+  filter(!subjID %in% raw_demographics_arg$id)
 ```
@@
   distinct(subjid, trialnr, .keep_all = TRUE)
+
+data_arg%>%
+  group_by(community)%>%
+  summarise(n = n_distinct(subjid))
+
+data_arg%>%
+  group_by(subjid)%>%
+  summarise(n = n())
+```
+
+# India
+
+```{r read_data}
+# get all .json files
+files <- list.files("../../../../../../Cloud/QuantEx/Gafo-cc/data/india/Data/India_Data/", pattern = "*.json",recursive = T)
+
+# convert json files to tibbles
+raw_data_ind <- tibble()
+for (f in files) {
+  jf <- paste("../../../../../../Cloud/QuantEx/Gafo-cc/data/india/Data/India_Data/", f, sep = "")
+  jd <- jsonlite::fromJSON(paste(readLines(jf, warn = "FALSE"), collapse = ""))
+
+  # needed because hedge trials have numbers, box trials have characters
+  jd$targetPosition <- factor(as.character(jd$targetPosition))
+
+  raw_data_ind <- bind_rows(raw_data_ind, jd)
+}
+# remove variables that we don't need anymore
+rm(f, files, jf, jd)
+```
+
+```{r}
+tidy_data_ind <- raw_data_ind %>%
+
+  # convert all character vectors into factors
+  mutate_if(is.character, as.factor) %>%
+
+  mutate(
+
+    # attention! the SVG coord system starts with 0, 0 in upper left corner
+    # we transform the values so that 0, 0 is lower left corner (for plots etc)
+    clickScaledY = 1080 - clickScaledY,
+    targetY = 1080 - targetY, 
+    targetCenterY = 1080 - targetCenterY, 
+    eyeCenterRightY = 1080 - eyeCenterRightY,
+    eyeCenterLeftY = 1080 - eyeCenterLeftY,
+    pupilFinalRightY = 1080 - pupilFinalRightY,
+    pupilFinalLeftY = 1080 - pupilFinalLeftY, 
+    targetCentralityX = abs(960 - targetCenterX),
+
+    # similarly here: in svg coords, negative click distance means up. 
+    # here we invert it, so that negative values mean down
+    clickDistFromTargetCenterY = clickDistFromTargetCenterY * -1, 
+    clickDistFromTargetBBoxY = clickDistFromTargetBBoxY * -1,
+
+    # positive values for inward clicks (i.e.,towards the center), negative for outward clicks
+    centralityBias = ifelse(targetCenterX <= 1920/2,
+                            clickDistFromTargetCenterX, 
+                            clickDistFromTargetCenterX*-1),
+
+    inwardClick = ifelse(centralityBias > 0, TRUE, FALSE),
+
+    # did the participant click on the right box?
+    # also for hedge version, here we imagine a box surrounding the target center 
+    # this way, we can compare hedge and box version ;) 
+    boxWidth = 218, 
+    boxBorderLeft = targetCenterX - boxWidth/2, 
+    boxBorderRight = targetCenterX + boxWidth/2,
+    correctBox = ifelse(boxBorderLeft <= clickScaledX & clickScaledX <= boxBorderRight, TRUE, FALSE),
+
+    datacollection = as.factor("in-person - supervised"), 
+    sample = as.factor("na"),
+    studytype = as.factor("vali"),
+  ) %>%select(-touchScreen)#%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
+```
+
+```{r}
+tidy_data_ind%>%
+  summarise(n = n_distinct(subjID))
+
+tidy_data_ind%>%
+  group_by(subjID)%>%
+  summarise(n = n())
+
+```
+
+```{r }
+raw_demographics_ind <- read_xlsx("../../../../../../Cloud/QuantEx/Gafo-cc/data/india/gafo-cc-india-participants.xlsx", sheet = 1)
+
+tidy_demographics_ind <- raw_demographics_ind %>% 
+  mutate(
+    test_date = as.Date(as.character(test_date), format = "%Y%m%d"),
+    birth_date = as.Date(as.character(birth_date), format = "%Y%m%d"),
+    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
+  )  %>%
+  select(-c(first_name, last_name, test_date, birth_date, comment))%>%
+  filter(!is.na(ageinyears))%>%
+  rename(subjid = id)
+
+```
+
+```{r}
+data_ind <- tidy_demographics_ind%>%
+  left_join(tidy_data_ind%>%rename_all(tolower),by = c("subjid"))%>%
+  mutate(community = "india")%>%
+  distinct(subjid, trialnr, .keep_all = TRUE)
+
+data_ind%>%
+  group_by(subjid)%>%
+  summarise(n = n())
+
+```
+
+# Auckland
+
+```{r}
+system("rsync -zaP ccp-odcJ:/srv/ccp-odc/gafo-newzealand/data/ ~/Work/Local/QuantEx/Gafo/raw_data/gafo-cc/auckland/")
+```
+
+```{r read_data}
+# get all .json files
+files <- list.files("../../raw_data/gafo-cc/auckland/", pattern = "*.json",recursive = T)%>% str_subset(pattern = "gafo--", negate = T)
+
+# convert json files to tibbles
+raw_data_nz <- tibble()
+for (f in files) {
+  jf <- paste("../../raw_data/gafo-cc/auckland/", f, sep = "")
+  jd <- jsonlite::fromJSON(paste(readLines(jf, warn = "FALSE"), collapse = ""))
+
+  # needed because hedge trials have numbers, box trials have characters
+  jd$targetPosition <- factor(as.character(jd$targetPosition))
+
+  raw_data_nz <- bind_rows(raw_data_nz, jd)
+}
+# remove variables that we don't need anymore
+rm(f, files, jf, jd)
+```
+
+```{r}
+tidy_data_nz <- raw_data_nz %>%
+
+  # convert all character vectors into factors
+
+  mutate(
+
+    # attention! the SVG coord system starts with 0, 0 in upper left corner
+    # we transform the values so that 0, 0 is lower left corner (for plots etc)
+    clickScaledY = 1080 - clickScaledY,
+    targetY = 1080 - targetY, 
+    targetCenterY = 1080 - targetCenterY, 
+    eyeCenterRightY = 1080 - eyeCenterRightY,
+    eyeCenterLeftY = 1080 - eyeCenterLeftY,
+    pupilFinalRightY = 1080 - pupilFinalRightY,
+    pupilFinalLeftY = 1080 - pupilFinalLeftY, 
+    targetCentralityX = abs(960 - targetCenterX),
+
+    # similarly here: in svg coords, negative click distance means up. 
+    # here we invert it, so that negative values mean down
+    clickDistFromTargetCenterY = clickDistFromTargetCenterY * -1, 
+    clickDistFromTargetBBoxY = clickDistFromTargetBBoxY * -1,
+
+    # positive values for inward clicks (i.e.,towards the center), negative for outward clicks
+    centralityBias = ifelse(targetCenterX <= 1920/2,
+                            clickDistFromTargetCenterX, 
+                            clickDistFromTargetCenterX*-1),
+
+    inwardClick = ifelse(centralityBias > 0, TRUE, FALSE),
+
+    # did the participant click on the right box?
+    # also for hedge version, here we imagine a box surrounding the target center 
+    # this way, we can compare hedge and box version ;) 
+    boxWidth = 218, 
+    boxBorderLeft = targetCenterX - boxWidth/2, 
+    boxBorderRight = targetCenterX + boxWidth/2,
+    correctBox = ifelse(boxBorderLeft <= clickScaledX & clickScaledX <= boxBorderRight, TRUE, FALSE),
+
+    datacollection = as.factor("in-person - supervised"), 
+    sample = as.factor("na"),
+    studytype = as.factor("vali")
+  ) %>%
+  mutate(subjID = ifelse(grepl("2023-03-11T19:4", timestamp) & subjID == "uksch048", "uksch049", subjID),
+         subjID = ifelse(subjID == "Uksch002", "uksch002", subjID),
+         subjID = ifelse(subjID == "Uksch003", "uksch003", subjID))%>%
+  mutate(subjID =as.factor(subjID))%>%
+  select(-touchScreen)%>%
+  mutate_if(is.character, as.factor)%>% 
+  distinct(subjID, trialNr, .keep_all = T)#%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
+
+unique(tidy_data_nz$subjID)
+```
+
+```{r}
+tidy_data_nz%>%
+  filter(trialType == "test")%>%
+  group_by(subjID)%>%
+  summarise(n = n())
+
+tidy_data_nz%>%
+  filter(trialType == "test")%>%
+  summarise(n = n_distinct(subjID))
+
+tidy_data_nz%>%
+  filter(subjID == "uksch002")
+```
+
+```{r demographics}
+raw_demographics_nz <- bind_rows(
+  read_xlsx("../../../../../../Cloud/QuantEx/Gafo-cc/data/new_zealand/gafo-cc-new-zealand-participants.xlsx", sheet = 1)
+  )
+
+tidy_demographics_nz <- raw_demographics_nz %>% 
+  mutate(
+
+    test_date = as.Date(as.character(test_date), format = "%Y%m%d"),
+    birth_date = as.Date(as.character(birth_date), format = "%Y%m%d"),
+    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
+  )  %>%
+  select(-c(first_name, last_name, test_date, birth_date, comment))%>%
+  filter(!is.na(ageinyears))%>%
+  rename(subjid = id)
+
+```
+
+```{r}
+data_nz <- tidy_demographics_nz%>%
+  left_join(tidy_data_nz%>%rename_all(tolower),by = c("subjid"))%>%
+  distinct(subjid, trialnr, .keep_all = TRUE)
+
+data_nz%>%
+  #mutate(age_group = substr(ageinyears, 1,1))%>%
+  #group_by(age)%>%
+  summarise(n = n_distinct(subjid))
+
+data_nz%>%
+  group_by(age)%>%
+  summarise(n())
 ```
@@
   data_china, 
-  data_arg
+  data_arg,
+  data_ind,
+  #data_nz
 )%>%
   #mutate(community = paste0("c",as.character(as.numeric(as.factor(community)))))%>%
-  filter(trialtype == "test")%>%
+  filter(trialtype == "test",
+         voiceover == F
+         )%>%
   mutate(age_group = substr(ageinyears, 1,1), 
          trialnr = as.numeric(factor(trialnr)))%>%
-  select(subjid, community, age_group, ageinyears, sex, screen, touchscreen, household, children, younger_children, trialnr, targetposition, targetcentralityx, clickdistfromtargetcenterx)%>%
+  select(subjid, community, age_group, ageinyears, sex, screen, touchscreen, household, children, younger_children, trialnr, targetposition,targetcenterx, targetcentralityx, clickdistfromtargetcenterx)%>%
   filter(ageinyears > 1)
@@
 data%>%
-  select(-touchscreen)%>%
-  filter(community == "windhoek")%>%
-  rename(touchscreen = touchscreen.x)%>%
+  #select(-touchscreen)%>%
+  filter(community == "hai||om" | community == "plymouth")%>%
+  #rename(touchscreen = touchscreen.x)%>%
   group_by(subjid, community, sex, screen, touchscreen, household,children,younger_children, ageinyears)%>%
     summarise(precision = mean(abs(clickdistfromtargetcenterx)))%>%
-  write_csv(.,"../data/gafo-cc-windhoek.csv")
+  write_csv(.,"../data/gafo-cc-uk-namibia.csv")
 ```
@@
 
-mdata <- data%>%
-  filter(community != "chimfunshi",
+haillom_data <- data%>%
+  filter(community == "hai||om",
          voiceover == F)%>%
   mutate(agecentered = ageinyears - min(ageinyears))%>%
-  select(-c(sex,ageinyears, wrongareaclick, earlyclick, durationanimationballoontotal, durationanimationcomplete, responsetime, clientscreenwidth, clientscreenheight, clientscreenscaling, clickoriginalx, clickoriginaly, hitbbtargetx, hitbbtargety, clickdistfromtargetbboxx, clickedarea, studyversion, boxesnr,population, inhouse, os, mobile, browser, browserversion, safari, iossafari,target, voiceover, epoch, timestamp, inwardclick, boxwidth,boxborderleft, boxborderright , correctbox, datacollection, sample, studytype, comment, status, site, `phone number in DB`,`location` ))
-
-write(toJSON(mdata), file = "../model/model_data/gafo-cc-model-data.json")
+  select(-c(sex,ageinyears, wrongareaclick, earlyclick, durationanimationballoontotal, durationanimationcomplete, responsetime, clientscreenwidth, clientscreenheight, clientscreenscaling, clickoriginalx, clickoriginaly, hitbbtargetx, hitbbtargety, clickdistfromtargetbboxx, clickedarea, studyversion, boxesnr,population, inhouse, os, mobile, browser, browserversion, safari, iossafari,target, voiceover, epoch, timestamp, inwardclick, boxwidth,boxborderleft, boxborderright , correctbox, datacollection, sample, studytype, comment, status, site,`location` ))
+
+write(toJSON(haillom_data), file = "../model/model_data/haillom-model-data.json")
 
 write_csv(mdata, file = "../model/model_data/gafo-cc-model-data.csv")
-
-display(communities)%>%
-  filter(is.na(community))
-
-mdata%>%
-  filter(trialnr == 5)%>%
-  select(subjid,agecentered)
-
-range(mdata$clickscaledx+500)
 ```

### 2023-07-30 analysis/gafo-cc-model.Rmd
chimfunshi model comparison prep

--- 2022-07-20 analysis/gafo-cc-model.Rmd
@@
 
-## Click distribution based on performance
+# Model comparison
 
-# Model
+## Hai||om
 
 ```{r, message=FALSE, warning=F}
-model <- rbindlist(
+haillom_model_comparison <- rbindlist(
   list(
-     fread("../model/output/gafo-cc_gran_20_chain1.csv"),
-     fread("../model/output/gafo-cc_gran_20_chain2.csv"),
-     fread("../model/output/gafo-cc_gran_20_chain3.csv"),
-     fread("../model/output/gafo-cc_gran_20_chain4.csv"),
-     fread("../model/output/gafo-cc_gran_20_chain5.csv"),
-     fread("../model/output/gafo-cc_gran_20_chain6.csv"),
-     fread("../model/output/gafo-cc_gran_20_chain7.csv"),
-     fread("../model/output/gafo-cc_gran_20_chain8.csv")
-    ), use.names=TRUE)#%>%saveRDS("../models/output/model_kids_box.rds")
+     fread("../model/output/haillom_model_comparison_chain1.csv"),
+     fread("../model/output/haillom_model_comparison_chain1.csv"),
+     fread("../model/output/haillom_model_comparison_chain1.csv"),
+     fread("../model/output/haillom_model_comparison_chain1.csv"),
+     fread("../model/output/haillom_model_comparison_chain1.csv"),
+     fread("../model/output/haillom_model_comparison_chain1.csv")
+    ), use.names=TRUE)%>%saveRDS("../models/output/haillom_model_comparison.rds")%>%
+  group_by(chain, iteration, model)%>%
+  summarise(like = sum(loglike))%>%
+  mutate(community = "hai||om")
 
-# saveRDS(model, "../model/output/gafo-cc-model.rds")
-# 
-# model <- readRDS("../model/output/gafo-cc-model.rds")
-```
-
-## Global Paramters
-
-### Guessing
-
-```{r}
-model%>%
-  filter(scope == "global", 
-         parameter == "guessing")%>%
-ggplot(aes(x= value, fill = factor(chain)))+
-  geom_density(alpha = .5)+
-  facet_wrap(community~type, scales = "free_y", nrow = 2)+
-  theme_few()+
-  scale_fill_viridis_d()
-```
-
-### Bias
-
-```{r}
-model%>%
-  filter(
-         parameter == "bias")%>%
-ggplot(aes(x= value, fill = factor(chain)))+
-  geom_density(alpha = .5)+
-  facet_grid(community~type)+
-  theme_few()+
-  scale_fill_viridis_d()
-```
-
-### Inference
-
-```{r}
-model%>%
-  filter(scope == "global", 
-         parameter == "inference")%>%
-ggplot(aes(x= value, fill = factor(chain)))+
-  geom_density(alpha = .5)+
-  facet_wrap(~type, scales = "free_y")+
-  theme_minimal()+
-  scale_fill_viridis_d()
-```
-## Development
-
-### Guessing
-```{r}
-guess_map <- model%>%
-  filter(scope == "global", 
-         parameter == "guessing")%>%
-  group_by(community, type)%>%
-  summarise(mode = estimate_mode(value))%>%
-  pivot_wider(names_from = "type", values_from = "mode")%>%
-  expand_grid(age = seq(0,5.5, by = 0.1))%>%
-  mutate(guess = plogis(intercept + slope * age))
-
-guess_samp <- model%>%
-  filter(scope == "global",
-         parameter == "guessing")%>%
-  pivot_wider(names_from = "type", values_from = "value")%>%
-  sample_n(1000)%>%
-  expand_grid(age = seq(0,5.5, by = 0.1))%>%
-  mutate(guess = plogis(intercept + slope * age))
-
-# guess_samp <- model%>%
-#   filter(scope == "global", 
-#          parameter == "guessing")%>%
-#   pivot_wider(names_from = "type", values_from = "value")%>%
-#   group_by(chain)%>%
-#   expand_grid(age = seq(0,3, by = 0.1))%>%
-#   mutate(sd_inf = exp(intercept + slope * age))%>%
-#   group_by(age)%>%
-#   summarise(uci = hdi_upper(sd_inf),
-#             lci = hdi_lower(sd_inf))
-
-ggplot()+
-  geom_line(data = guess_samp, aes(x = age+2.5, y = guess, group = paste(chain,iteration)), alpha = .01)+
-  #geom_line(data = inf_samp, aes(x = age+3, y = uci), lty = 2)+
-  #geom_line(data = inf_samp, aes(x = age+3, y = lci), lty = 2)+
-  geom_line(data = guess_map, aes(x = age+2.5, y = guess), col = "firebrick")+
-  facet_grid(~community)+
-  #xlim(2.5,8)+
-  xlab("Age")+
-  #ylim(0,1)+
-  theme_minimal()
-```
-
-### Bias
-```{r}
-bias_map <- model%>%
-  filter(scope == "global", 
-         parameter == "bias")%>%
-  group_by(community,type)%>%
-  summarise(mode = estimate_mode(value))%>%
-  pivot_wider(names_from = "type", values_from = "mode")%>%
-  expand_grid(age = seq(0,5.5, by = 0.1))%>%
-  mutate(bias = plogis(intercept + slope * age))
-
-bias_samp <- model%>%
-  filter(scope == "global",
-         parameter == "bias")%>%
-  pivot_wider(names_from = "type", values_from = "value")%>%
-  sample_n(1000)%>%
-  expand_grid(age = seq(0,5.5, by = 0.1))%>%
-  mutate(bias = plogis(intercept + slope * age))
-
-# bias_samp <- model%>%
-#   filter(scope == "global", 
-#          parameter == "bias")%>%
-#   pivot_wider(names_from = "type", values_from = "value")%>%
-#   group_by(chain)%>%
-#   expand_grid(age = seq(0,3, by = 0.1))%>%
-#   mutate(sd_inf = exp(intercept + slope * age))%>%
-#   group_by(age)%>%
-#   summarise(uci = hdi_upper(sd_inf),
-#             lci = hdi_lower(sd_inf))
-
-ggplot()+
-  geom_line(data = bias_samp, aes(x = age+2.5, y = bias, group = paste(chain,iteration)), alpha = .01)+
-  #geom_line(data = inf_samp, aes(x = age+3, y = uci), lty = 2)+
-  #geom_line(data = inf_samp, aes(x = age+3, y = lci), lty = 2)+
-  geom_line(data = bias_map, aes(x = age+2.5, y = bias), col = "firebrick")+
-  #xlim(3,6)+
-  facet_grid(~community)+
-  xlab("Age")+
-  #ylim(0,1)+
-  theme_minimal()
-```
-
-### Inference
-
-```{r}
-inf_map <- model%>%
-  filter(scope == "global", 
-         parameter == "inference")%>%
-  group_by(community,type)%>%
-  summarise(mode = estimate_mode(value))%>%
-  pivot_wider(names_from = "type", values_from = "mode")%>%
-  expand_grid(age = seq(0,5.5, by = 0.1))%>%
-  mutate(sd_inf = plogis(intercept + slope * age))
-
-inf_samp <- model%>%
-  filter(scope == "global",
-         parameter == "inference")%>%
-  pivot_wider(names_from = "type", values_from = "value")%>%
-  group_by(chain)%>%
-  sample_n(1000)%>%
-  expand_grid(age = seq(0,5.5, by = 0.1))%>%
-  mutate(sd_inf = plogis(intercept + slope * age))
-
-# inf_samp <- model%>%
-#   filter(scope == "global",
-#          parameter == "inference")%>%
-#   pivot_wider(names_from = "type", values_from = "value")%>%
-#   group_by(chain)%>%
-#   expand_grid(age = seq(0,3, by = 0.1))%>%
-#   mutate(sd_inf = exp(intercept + slope * age))%>%
-#   group_by(age)%>%
-#   summarise(uci = hdi_upper(sd_inf),
-#             lci = hdi_lower(sd_inf))
-
-ggplot()+
-  geom_line(data = inf_samp, aes(x = age+2.5, y = sd_inf, group = paste(chain,iteration)), alpha = .01, size = 0.1)+
-   # geom_line(data = inf_samp, aes(x = age+3, y = uci), lty = 2)+
-   # geom_line(data = inf_samp, aes(x = age+3, y = lci), lty = 2)+
-  geom_line(data = inf_map, aes(x = age+2.5, y = sd_inf), col = "firebrick")+
-  #xlim(3,6)+
-  facet_grid(~community)+
-  labs(x = "Age", y = "Gaze inference precision (across individuals)")+
-  #ylim(0,1)+
-  theme_minimal()
+ haillom_model_comparison <- readRDS("../model/output/haillom_model_comparison.rds")
 ```
@@
 ```{r}
-ggsave("../graphs/sd_dev.png", width = 8, height = 4, scale = 1, bg = "white")
+haillom_model_comparison%>%
+  group_by(community, model,chain)%>%
+  summarise(margllh = logSumExp(like))%>%
+  pivot_wider(names_from = model, values_from = margllh)
+```
+
+# Summary
+
+```{r}
+bind_rows(
+  haillom_model_comparison
+) %>%
+  group_by(community, model)%>%
+  summarise(margllh = logSumExp(like))%>%
+  pivot_wider(names_from = model, values_from = margllh)%>%
+  summarise(bf_inf_center = inf - center, 
+            bf_inf_guess = inf - guess)
+
 ```
@@
 ```{r}
-alt <- model%>%
-  filter(scope == "global", 
-         parameter != "inference",
-         chain != 7,
-         chain != 2)%>%
-  group_by(community,parameter,type)%>%
-  summarise(mode = estimate_mode(value))%>%
-  filter(type != "sigma")%>%
-  pivot_wider(names_from = c("parameter", "type"), values_from = "mode")%>%
-  expand_grid(age = seq(0,3, by = 0.1))%>%
-  mutate(guess = plogis(guessing_intercept + guessing_slope * age),
-         bias_raw = plogis(bias_intercept + bias_slope * age),
-         inference = 1- guess,
-         center_bias = guess * bias_raw,
-         random_guessing = 1- inference - center_bias)%>%
-  ungroup()%>%
-  select(age,community, center_bias, random_guessing, inference)%>%
-  pivot_longer(names_to = "parameter", values_to = "value", cols = c(center_bias, random_guessing, inference))%>%
-  mutate(parameter = factor(parameter, levels = c("inference", "random_guessing", "center_bias")))
-
-ggplot(alt, aes(x = age+3, y = value, fill = parameter))+
-  geom_area(alpha = .9)+
-  xlim(3,6)+
-  xlab("Age")+
-  ylim(0,1)+
-  facet_grid(~community)+
+bind_rows(
+  haillom_model_comparison
+)%>%
+  ggplot(aes(x = like))+
+  geom_histogram(alpha = .5, aes(fill = model), col = "black")+
+  facet_wrap(~community, scales = "free")+
   scale_fill_colorblind()+
-  theme_minimal()
+  xlim(-8000, -5000)+
+  theme_bw()
 ```
-
-## Individual
-
-### Guessing
-
-```{r}
-model%>%
-  filter(scope == "id", 
-         parameter == "guessing")%>%
-  ggplot(aes(x = value, fill = factor(chain)))+
-  geom_density(alpha = .25)+
-  facet_wrap(~id, scales = "free")+
-  theme_void()+
-  scale_fill_colorblind()
-```
-
-### Inference
-
-```{r}
-model%>%
-  filter(scope == "id", 
-         parameter == "inference")%>%
-  ggplot(aes(x = value, fill = factor(chain)))+
-  geom_density(alpha = .25)+
-  facet_wrap(~id, scales = "free")+
-  theme_minimal()+
-  scale_fill_colorblind()+
-  xlim(0,2)
-```
-
-### Relation between paramters
-
-```{r}
-rel <- model%>%
-  filter(scope == "id")%>%
-  group_by(parameter, id)%>%
-  summarise(mode = estimate_mode(value))%>%
-  left_join(data%>%rename(id = subjID)%>%select(id, ageInYears))
-
-ggplot(rel,aes(x = parameter, y = mode))+
-  geom_line(aes(group = id), alpha = .25)+
-  geom_point(col = "dodgerblue", pch = 1,alpha = .5)+
-  facet_grid(~ageInYears)+
-  theme_minimal()
-```

### 2023-07-30 analysis/gafo-cc-data-processing.Rmd
chimfunshi model comparison prep

@@
 ```{r}
-
-data <- bind_rows(
+merge_raw_data <- bind_rows(
   data_zambia,
@@
   mutate(age_group = substr(ageinyears, 1,1), 
-         trialnr = as.numeric(factor(trialnr)))%>%
+         trialnr = as.numeric(factor(trialnr)))
+
+write_csv(merge_raw_data,"../data/gafo-cc-raw-data.csv")
+
+data <- merge_raw_data%>%
   select(subjid, community, age_group, ageinyears, sex, screen, touchscreen, household, children, younger_children, trialnr, targetposition,targetcenterx, targetcentralityx, clickdistfromtargetcenterx)%>%
@@
 write_csv(data,"../data/gafo-cc-clean-data.csv")
+
+```
+
+```{r}
+data <- read_csv("../data/gafo-cc-clean-data.csv")
 
@@
   summarise(n = n_distinct(subjid))
-```
-
-```{r}
+
 data%>%
@@
 ```{r}
-
-data <- read_csv("../data/gafo-cc-clean-data.csv")
-
-haillom_data <- data%>%
+merge_raw_data <- read_csv("../data/gafo-cc-raw-data.csv")
+```
+
+```{r}
+chimfunshi_data <- merge_raw_data%>%
+  filter(community == "chimfunshi",
+         voiceover == F)%>%
+  mutate(agecentered = ageinyears - min(ageinyears))%>%
+  select(-c(sex,ageinyears, wrongareaclick, earlyclick, durationanimationballoontotal, durationanimationcomplete, responsetime, clientscreenwidth, clientscreenheight, clientscreenscaling, clickoriginalx, clickoriginaly, hitbbtargetx, hitbbtargety, clickdistfromtargetbboxx, clickedarea, studyversion, boxesnr,population, inhouse, os, mobile, browser, browserversion, safari, iossafari,target, voiceover, epoch, timestamp, inwardclick, boxwidth,boxborderleft, boxborderright , correctbox, datacollection, sample, studytype, comment, status, site,`location` ))
+
+write(toJSON(chimfunshi_data), file = "../model/model_data/chimfunshi-model-data.json")
+```
+
+```{r}
+haillom_data <- merge_raw_data%>%
   filter(community == "hai||om",

### 2023-09-15 analysis/gafo-cc-data-processing.Rmd
prep merge

@@
 # get all .json files
-files <- list.files("../../raw_data/gafo-cc/auckland/", pattern = "*.json",recursive = T)%>% str_subset(pattern = "gafo--", negate = T)
+files <- list.files("../../../../../../Cloud/QuantEx/Gafo-cc/data/new_zealand/data/", pattern = "*.json",recursive = T)
 
@@
 for (f in files) {
-  jf <- paste("../../raw_data/gafo-cc/auckland/", f, sep = "")
+  jf <- paste("../../../../../../Cloud/QuantEx/Gafo-cc/data/new_zealand/data/", f, sep = "")
   jd <- jsonlite::fromJSON(paste(readLines(jf, warn = "FALSE"), collapse = ""))
@@
 data_nz <- tidy_demographics_nz%>%
+  filter(subjid != "NZ000001")%>%
   left_join(tidy_data_nz%>%rename_all(tolower),by = c("subjid"))%>%
@@
   summarise(n())
+```
+
+# Turkey
+
+```{r read_data}
+# get all .json files
+files <- list.files("../../../../../../Cloud/QuantEx/Gafo-cc/data/turkey/data/", pattern = "*.json",recursive = T)
+
+# convert json files to tibbles
+raw_data_tur <- tibble()
+for (f in files) {
+  jf <- paste("../../../../../../Cloud/QuantEx/Gafo-cc/data/turkey/data/", f, sep = "")
+  jd <- jsonlite::fromJSON(paste(readLines(jf, warn = "FALSE"), collapse = ""))
+
+  # needed because hedge trials have numbers, box trials have characters
+  jd$targetPosition <- factor(as.character(jd$targetPosition))
+
+  raw_data_tur <- bind_rows(raw_data_tur, jd)
+}
+# remove variables that we don't need anymore
+rm(f, files, jf, jd)
+```
+
+```{r}
+tidy_data_tur <- raw_data_tur %>%
+
+  # convert all character vectors into factors
+  mutate_if(is.character, as.factor) %>%
+
+  mutate(
+
+    # attention! the SVG coord system starts with 0, 0 in upper left corner
+    # we transform the values so that 0, 0 is lower left corner (for plots etc)
+    clickScaledY = 1080 - clickScaledY,
+    targetY = 1080 - targetY, 
+    targetCenterY = 1080 - targetCenterY, 
+    eyeCenterRightY = 1080 - eyeCenterRightY,
+    eyeCenterLeftY = 1080 - eyeCenterLeftY,
+    pupilFinalRightY = 1080 - pupilFinalRightY,
+    pupilFinalLeftY = 1080 - pupilFinalLeftY, 
+    targetCentralityX = abs(960 - targetCenterX),
+
+    # similarly here: in svg coords, negative click distance means up. 
+    # here we invert it, so that negative values mean down
+    clickDistFromTargetCenterY = clickDistFromTargetCenterY * -1, 
+    clickDistFromTargetBBoxY = clickDistFromTargetBBoxY * -1,
+
+    # positive values for inward clicks (i.e.,towards the center), negative for outward clicks
+    centralityBias = ifelse(targetCenterX <= 1920/2,
+                            clickDistFromTargetCenterX, 
+                            clickDistFromTargetCenterX*-1),
+
+    inwardClick = ifelse(centralityBias > 0, TRUE, FALSE),
+
+    # did the participant click on the right box?
+    # also for hedge version, here we imagine a box surrounding the target center 
+    # this way, we can compare hedge and box version ;) 
+    boxWidth = 218, 
+    boxBorderLeft = targetCenterX - boxWidth/2, 
+    boxBorderRight = targetCenterX + boxWidth/2,
+    correctBox = ifelse(boxBorderLeft <= clickScaledX & clickScaledX <= boxBorderRight, TRUE, FALSE),
+
+    datacollection = as.factor("in-person - supervised"), 
+    sample = as.factor("na"),
+    studytype = as.factor("vali"),
+  ) %>%select(-touchScreen)#%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
+```
+
+```{r}
+tidy_data_tur%>%
+  summarise(n = n_distinct(subjID))
+
+tidy_data_tur%>%
+  group_by(subjID)%>%
+  summarise(n = n())
+
+```
+
+```{r }
+raw_demographics_tur <- read_xlsx("../../../../../../Cloud/QuantEx/Gafo-cc/data/turkey/gafo-cc-turkey-participants.xlsx", sheet = 1)
+
+tidy_demographics_tur <- raw_demographics_tur %>% 
+  mutate(
+    test_date = as.Date(as.character(test_date), format = "%Y%m%d"),
+    birth_date = as.Date(as.character(birth_date), format = "%Y%m%d"),
+    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
+  )  %>%
+  select(-c(first_name, last_name, test_date, birth_date, comment))%>%
+  #filter(!is.na(ageinyears))%>%
+  rename(subjid = id)
+
+```
+
+```{r}
+data_tur <- tidy_demographics_tur%>%
+  left_join(tidy_data_tur%>%rename_all(tolower),by = c("subjid"))%>%
+  mutate(community = "turkey")%>%
+  distinct(subjid, trialnr, .keep_all = TRUE)%>%
+  mutate(subjid = recode(subjid, 
+                     "EBRAR100" = "TUR00002",
+                     "FATMA400" = "TUR00003",
+                     "ASYAA200" = "TUR00004"))
+
+data_tur%>%
+  group_by(subjid)%>%
+  summarise(n = n())
+
+data_tur%>%
+  group_by(subjid)%>%
+  summarise(n = n(), 
+            mean = mean(abs(clickdistfromtargetcenterx)))
+
 ```
@@
   data_ind,
-  #data_nz
+  data_nz
 )%>%

### 2023-09-15 analysis/gafo-cc-data-processing.Rmd

@@
 ```{r}
+akure_data <- merge_raw_data%>%
+  filter(community == "akure",
+         voiceover == F)%>%
+  mutate(agecentered = ageinyears - min(ageinyears))%>%
+  select(-c(sex,ageinyears, wrongareaclick, earlyclick, durationanimationballoontotal, durationanimationcomplete, responsetime, clientscreenwidth, clientscreenheight, clientscreenscaling, clickoriginalx, clickoriginaly, hitbbtargetx, hitbbtargety, clickdistfromtargetbboxx, clickedarea, studyversion, boxesnr,population, inhouse, os, mobile, browser, browserversion, safari, iossafari,target, voiceover, epoch, timestamp, inwardclick, boxwidth,boxborderleft, boxborderright , correctbox, datacollection, sample, studytype, comment, status, site,`location` ))
+
+write(toJSON(akure_data), file = "../model/model_data/akure-model-data.json")
+```
+
+```{r}
+buenos_aires_data <- merge_raw_data%>%
+  filter(community == "buenos_aires",
+         voiceover == F)%>%
+  mutate(agecentered = ageinyears - min(ageinyears))%>%
+  select(-c(sex,ageinyears, wrongareaclick, earlyclick, durationanimationballoontotal, durationanimationcomplete, responsetime, clientscreenwidth, clientscreenheight, clientscreenscaling, clickoriginalx, clickoriginaly, hitbbtargetx, hitbbtargety, clickdistfromtargetbboxx, clickedarea, studyversion, boxesnr,population, inhouse, os, mobile, browser, browserversion, safari, iossafari,target, voiceover, epoch, timestamp, inwardclick, boxwidth,boxborderleft, boxborderright , correctbox, datacollection, sample, studytype, comment, status, site,`location` ))
+
+write(toJSON(buenos_aires_data), file = "../model/model_data/buenos_aires-model-data.json")
+```
+
+```{r}
+beijing_data <- merge_raw_data%>%
+  filter(community == "beijing",
+         voiceover == F)%>%
+  mutate(agecentered = ageinyears - min(ageinyears))%>%
+  select(-c(sex,ageinyears, wrongareaclick, earlyclick, durationanimationballoontotal, durationanimationcomplete, responsetime, clientscreenwidth, clientscreenheight, clientscreenscaling, clickoriginalx, clickoriginaly, hitbbtargetx, hitbbtargety, clickdistfromtargetbboxx, clickedarea, studyversion, boxesnr,population, inhouse, os, mobile, browser, browserversion, safari, iossafari,target, voiceover, epoch, timestamp, inwardclick, boxwidth,boxborderleft, boxborderright , correctbox, datacollection, sample, studytype, comment, status, site,`location` ))
+
+write(toJSON(beijing_data), file = "../model/model_data/beijing-model-data.json")
+```
+
+```{r}
+india_data <- merge_raw_data%>%
+  filter(community == "india",
+         voiceover == F)%>%
+  mutate(agecentered = ageinyears - min(ageinyears))%>%
+  select(-c(sex,ageinyears, wrongareaclick, earlyclick, durationanimationballoontotal, durationanimationcomplete, responsetime, clientscreenwidth, clientscreenheight, clientscreenscaling, clickoriginalx, clickoriginaly, hitbbtargetx, hitbbtargety, clickdistfromtargetbboxx, clickedarea, studyversion, boxesnr,population, inhouse, os, mobile, browser, browserversion, safari, iossafari,target, voiceover, epoch, timestamp, inwardclick, boxwidth,boxborderleft, boxborderright , correctbox, datacollection, sample, studytype, comment, status, site,`location` ))
+
+write(toJSON(india_data), file = "../model/model_data/india-model-data.json")
+```
+
+```{r}
+mexico_data <- merge_raw_data%>%
+  filter(community == "mexico",
+         voiceover == F)%>%
+  mutate(agecentered = ageinyears - min(ageinyears))%>%
+  select(-c(sex,ageinyears, wrongareaclick, earlyclick, durationanimationballoontotal, durationanimationcomplete, responsetime, clientscreenwidth, clientscreenheight, clientscreenscaling, clickoriginalx, clickoriginaly, hitbbtargetx, hitbbtargety, clickdistfromtargetbboxx, clickedarea, studyversion, boxesnr,population, inhouse, os, mobile, browser, browserversion, safari, iossafari,target, voiceover, epoch, timestamp, inwardclick, boxwidth,boxborderleft, boxborderright , correctbox, datacollection, sample, studytype, comment, status, site,`location` ))
+
+write(toJSON(mexico_data), file = "../model/model_data/mexico-model-data.json")
+```
+
+```{r}
 chimfunshi_data <- merge_raw_data%>%

### 2023-09-19 analysis/gafo-cc-visuals.Rmd
update repo

@@
 library(tidyboot)
+library(maps)
+library(brms)
 ```
@@
                             plymouth = "plymouth (uk)",
-                            beijing = "beijing (china)"))
+                            beijing = "beijing (china)", 
+                            india = "pune (india)",
+                            buenos_aires = "buenos aires (argentina)",
+                            auckland = "auckland (new zealand)",
+                            turkey = "malatya (turkey)"))
+```
+
+```{r}
+library(pals)
+
+library(RColorBrewer)
+qual_col_pals = brewer.pal.info[brewer.pal.info$colorblind == TRUE,]
+col_vector = unlist(mapply(brewer.pal, qual_col_pals$maxcolors, rownames(qual_col_pals)))
+
+colors=kelly(n=n_distinct(data$community)+1)
+
+colors <- colors[ !colors == '#F2F3F4']
+
 ```
@@
 data%>%
-  #filter(community != "chimfunshi (sambia)")%>%
   group_by(community,subjid, ageinyears)%>%
@@
   geom_point(alpha = .25)+
-  geom_smooth(method = "lm")+
-  scale_color_ptol(name = "Community")+
+  geom_smooth(method = "glm")+
+  scale_color_manual(name = "Community", values = colors)+
   ylim(0,1000)+
-  #facet_wrap(~community)+
+  facet_wrap(~community)+
   labs(x = "Age (in years)", y ="Imprecision (average click distance from target)")+
@@
 alt2 <- data%>%
-  distinct(targetposition, targetcentralityx)%>%
-  expand_grid(random_click = runif(10000, min = 0, max = 1920))%>%
-  mutate(dist = abs(targetcentralityx - random_click))%>%
+  distinct(targetposition, targetcenterx)%>%
+  expand_grid(random_click = runif(1000, min = 0, max = 1920))%>%
+  mutate(dist = abs(targetcenterx - random_click))%>%
   group_by(targetposition)%>%
@@
 ggplot(ptp, aes(x = targetposition, y = mean, col = community))+
-  geom_line(data = alt1, aes(x = targetposition, y = center, group = group), lty = 3, alpha = 0.75, col = "black")+
-  geom_line(data = alt2, aes(x = targetposition, y = random, group = group), lty = 3, alpha = 0.75,  col = "black")+
+  #geom_line(data = alt1, aes(x = targetposition, y = center, group = group), lty = 3, alpha = 0.75, col = "black")+
+  #geom_line(data = alt2, aes(x = targetposition, y = random, group = group), lty = 3, alpha = 0.75,  col = "black")+
   geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
   labs(x = "Target position (binned)", y = "Imprecision (average click distance from target)")+
-  scale_color_ptol(name = "Community")+
+  scale_color_manual(name = "Community", values = colors)+
   #facet_grid(~age_group)+
@@
 ggsave("../visuals/target_position_site.png", width = 8, height = 6, bg = "white")
+```
+
+```{r}
+ptp2<- data%>%
+  #filter(community != "chimfunshi (sambia)")%>%
+  mutate(targetposition = factor(targetposition, levels = c(1:10)))%>%
+  #group_by(community, targetposition, age_group)%>%
+  group_by(community,age_group, targetposition)%>%
+  tidyboot_mean(col= abs(clickdistfromtargetcenterx))
+
+ptp2%>%
+  #filter(community == "leipzig (germany)")%>%
+  ggplot(.,aes(x = targetposition, y = mean, col = community))+
+  #geom_line(data = alt1, aes(x = targetposition, y = center, group = group), lty = 3, alpha = 0.75, col = "black")+
+  #geom_line(data = alt2, aes(x = targetposition, y = random, group = group), lty = 3, alpha = 0.75,  col = "black")+
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
+  labs(x = "Target position (binned)", y = "Imprecision (average click distance from target)")+
+  scale_color_manual(name = "Community", values = colors)+
+  facet_grid(~factor(age_group))+
+  ylim(0,1000)+
+  theme_few()
+```
+
+```{r}
+ggsave("../visuals/target_position_site_age.png", width = 12, height = 4, bg = "white", scale = 1.5)
 ```
@@
 ```
+
+# Model based developmental trajectories
+
+```{r}
+ddata <- data%>%
+  mutate(click = abs(clickdistfromtargetcenterx))%>%
+  group_by(subjid, community, ageinyears)%>%
+  summarise(mean_click = mean(click))%>%
+  ungroup()%>%
+  mutate(ageinyears = ageinyears - min(ageinyears))
+
+bm_base <- brm(mean_click ~ ageinyears + (ageinyears |community), 
+                              data   = ddata, 
+                              family = lognormal(),
+                              warmup = 2000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4,
+             control = list(adapt_delta = 0.95))
+```
+
+```{r}
+ndata <- ddata%>%
+  distinct(community, ageinyears)
+
+post <- fitted(bm_base, newdata = ndata, re_formula =~(ageinyears|community))%>%
+  as_tibble() %>%
+  bind_cols(ndata)%>%
+  mutate(ageinyears = ageinyears + min(data$ageinyears))
+
+ggplot()+
+  geom_smooth(data = post, aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
+  theme_minimal()+
+  geom_point(data = ddata, aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.5)+
+  scale_fill_manual(name = "Community", values = colors)+
+  scale_color_manual(name = "Community", values = colors)+
+  labs(x = "Age", y="Imprecision")#+
+  facet_wrap(~community)+guides(col = "none", fill = "none")
+```
+
+```{r}
+ggsave("../visuals/dev.png", width = 12, height = 8, bg = "white")
+```
+
+# Map
+
+```{r}
+world <- map_data("world")
+
+```
+
+```{r}
+data_map <- read_csv("../data/gafo-cc-clean-data.csv")%>%
+  mutate(region = recode(community,
+                            akure = "Nigeria",
+                            leipzig = "Germany",
+                            `hai||om` = "Namibia",
+                            khwe = "Namibia",
+                            windhoek = "Namibia",
+                            stanford = "USA",
+                            chimfunshi = "Zambia",
+                            mexico = "Mexico",
+                            plymouth = "UK",
+                            beijing = "China",
+                            india = "India",
+                            buenos_aires = "Argentina",
+                            auckland = "New Zealand",
+                            turkey = "Turkey"))%>%
+  mutate(loc_lat = recode(community,
+                            akure = 7.251070,
+                            leipzig = 51.339695,
+                            `hai||om` = -18.771648361967873,
+                            khwe = -17.95549,
+                            windhoek = -22.560881,
+                            stanford = 37.427475,
+                            chimfunshi = -12.541857285496434,
+                            mexico = 18.9802204332881, 
+                            plymouth = 50.37469737043179,
+                            beijing = 39.91475103408255, 
+                            india = 18.5265350616402,
+                            buenos_aires = -34.60217085665333,
+                            auckland = -36.850146242932965,
+                          turkey = 38.35501382975052))%>%
+    mutate(loc_long = recode(community,
+                            akure = 5.203540,
+                            leipzig = 12.373075,
+                            `hai||om` = 17.968581283099287,
+                            khwe = 22.558622,
+                            windhoek = 17.065756,
+                            stanford = -122.169716,
+                            chimfunshi = 27.85405941279387,
+                            mexico = -99.41965213620936,
+                            plymouth = -4.140423156946285,
+                            beijing = 116.40832763995694, 
+                            india = 73.86056457627757,
+                            buenos_aires = -58.39139837939201,
+                            auckland = 174.7651647587945, 
+                            turkey = 38.33313216647862))%>%
+  group_by(community, loc_lat, loc_long, region)%>%
+  summarise(Participants = n_distinct(subjid))
+
+selWorld <- left_join(world, data_map, by = "region")%>%
+  filter(region != "Antarctica")%>%
+  mutate(fill = ifelse(is.na(Participants), "out", "in"))%>% 
+  filter(! long > 180)
+```
+```{r}
+
+plain <- theme(
+  axis.text = element_blank(),
+  axis.line = element_blank(),
+  axis.ticks = element_blank(),
+  panel.border = element_blank(),
+  panel.grid = element_blank(),
+  axis.title = element_blank(),
+  panel.background = element_rect(fill = "white"),
+  plot.title = element_text(hjust = 0.5)
+)
+
+new_scale <- function(new_aes) {
+  structure(ggplot2::standardise_aes_names(new_aes), class = "new_aes")
+}
+
+#' Convenient functions
+new_scale_fill <- function() {
+  new_scale("fill")
+}
+
+new_scale_color <- function() {
+  new_scale("colour")
+}
+
+new_scale_colour <- function() {
+  new_scale("colour")
+}
+
+#' Special behaviour of the "+" for adding a `new_aes` object
+#' It changes the name of the aesthethic for the previous layers, appending
+#' "_new" to them. 
+ggplot_add.new_aes <- function(object, plot, object_name) {
+  plot$layers <- lapply(plot$layers, bump_aes, new_aes = object)
+  plot$scales$scales <- lapply(plot$scales$scales, bump_aes, new_aes = object)
+  plot$labels <- bump_aes(plot$labels, new_aes = object)
+  plot
+}
+
+bump_aes <- function(layer, new_aes) {
+  UseMethod("bump_aes")
+}
+
+bump_aes.Scale <- function(layer, new_aes) {
+  old_aes <- layer$aesthetics[remove_new(layer$aesthetics) %in% new_aes]
+  new_aes <- paste0(old_aes, "_new")
+
+  layer$aesthetics[layer$aesthetics %in% old_aes] <- new_aes
+
+  if (is.character(layer$guide)) {
+    layer$guide <- match.fun(paste("guide_", layer$guide, sep = ""))()
+  }
+  layer$guide$available_aes[layer$guide$available_aes %in% old_aes] <- new_aes
+  layer
+}
+
+bump_aes.Layer <- function(layer, new_aes) {
+  original_aes <- new_aes
+
+  old_aes <- names(layer$mapping)[remove_new(names(layer$mapping)) %in% new_aes]
+  new_aes <- paste0(old_aes, "_new")
+
+  old_geom <- layer$geom
+
+  old_setup <- old_geom$handle_na
+  new_setup <- function(self, data, params) {
+    colnames(data)[colnames(data) %in% new_aes] <- original_aes
+    old_setup(data, params)
+  }
+
+  new_geom <- ggplot2::ggproto(paste0("New", class(old_geom)[1]), old_geom,
+                               handle_na = new_setup)
+
+  new_geom$default_aes <- change_name(new_geom$default_aes, old_aes, new_aes)
+  new_geom$non_missing_aes <- change_name(new_geom$non_missing_aes, old_aes, new_aes)
+  new_geom$required_aes <- change_name(new_geom$required_aes, old_aes, new_aes)
+  new_geom$optional_aes <- change_name(new_geom$optional_aes, old_aes, new_aes)
+
+  layer$geom <- new_geom
+
+  old_stat <- layer$stat
+
+  old_setup2 <- old_stat$handle_na
+  new_setup <- function(self, data, params) {
+    colnames(data)[colnames(data) %in% new_aes] <- original_aes
+    old_setup2(data, params)
+  }
+
+  new_stat <- ggplot2::ggproto(paste0("New", class(old_stat)[1]), old_stat,
+                               handle_na = new_setup)
+
+  new_stat$default_aes <- change_name(new_stat$default_aes, old_aes, new_aes)
+  new_stat$non_missing_aes <- change_name(new_stat$non_missing_aes, old_aes, new_aes)
+  new_stat$required_aes <- change_name(new_stat$required_aes, old_aes, new_aes)
+  new_stat$optional_aes <- change_name(new_stat$optional_aes, old_aes, new_aes)
+
+  layer$stat <- new_stat
+
+  layer$mapping <- change_name(layer$mapping, old_aes, new_aes)
+  layer
+}
+
+bump_aes.list <- function(layer, new_aes) {
+  old_aes <-  names(layer)[remove_new(names(layer)) %in% new_aes]
+  new_aes <- paste0(old_aes, "_new")
+
+  names(layer)[names(layer) %in% old_aes] <- new_aes
+  layer
+}
+
+change_name <- function(list, old, new) {
+  UseMethod("change_name")
+}
+
+change_name.character <- function(list, old, new) {
+  list[list %in% old] <- new
+  list
+}
+
+change_name.default <- function(list, old, new) {
+  nam <- names(list)
+  nam[nam %in% old] <- new
+  names(list) <- nam
+  list
+}
+
+change_name.NULL <- function(list, old, new) {
+  NULL
+}
+
+remove_new <- function(aes) {
+  stringi::stri_replace_all(aes, "", regex = "(_new)*")
+}
+```
+
+```{r}
+ggplot(data = selWorld, mapping = aes(x = long, y = lat, group = group)) + 
+  coord_map("moll")+
+  geom_polygon(aes(fill = fill)) +
+  scale_fill_manual(breaks = c("out", "in"), values = c("grey", "#DBD56E"), guide = "none")+
+  new_scale("fill") +
+  geom_point(pch = 21, data = data_map, aes(x = loc_long, y = loc_lat, fill = Participants), col = "black", inherit.aes = F, size = 2.5, stroke = 0.5)+
+  #scale_fill_distiller(palette ="RdBu", direction = -1) + # or direction=1
+  scale_fill_viridis_c(direction = -1, guide = guide_colourbar(direction = "horizontal", title.position = "top", title.hjust = 0.5), name = "Sample size")+
+  plain+
+  theme(legend.position = c(0.15, 0.25), legend.background = element_blank())
+```
+```{r}
+ggsave("../visuals/map.png", width = 12, height = 6, bg = "white")
+```

### 2023-10-24 analysis/gafo-cc-visuals.Rmd
update data

@@
                             auckland = "auckland (new zealand)",
-                            turkey = "malatya (turkey)"))
+                            turkey = "malatya (turkey)",
+                            bandongo = "bandongo (rep. congo)",
+                            bayaka = "bayaka (rep. congo)"))
 ```
@@
   ylim(0,1000)+
-  facet_wrap(~community)+
+  #facet_wrap(~community)+
   labs(x = "Age (in years)", y ="Imprecision (average click distance from target)")+

### 2023-12-11 analysis/gafo-cc-analysis.Rmd
prep model runs

@@
   mutate(older_children = children - 1 - younger_children)%>%
+  ungroup()%>%
   group_by(community)%>%
@@
              control = list(adapt_delta = 0.95),
-             backend = "cmdstanr")%>%
+             #backend = "cmdstanr"
+             )%>%
   add_criterion(., c("waic","loo"))
@@
              control = list(adapt_delta = 0.95),
-             backend = "cmdstanr")%>%
+             #backend = "cmdstanr"
+             )%>%
   add_criterion(., c("waic","loo"))
 
-bm_full_rand <- brm(mean_click ~ ageinyears + touchscreen + household + younger_children + children + (touchscreen + household + younger_children + children + ageinyears |community), 
+bm_full_rand <- brm(mean_click ~ ageinyears + touchscreen + household + younger_children + older_children + (touchscreen + household + younger_children + older_children + ageinyears |community), 
                               data   = scdata, 
@@
              control = list(adapt_delta = 0.95),
-             backend = "cmdstanr")%>%
+            # backend = "cmdstanr"
+             )%>%
+  add_criterion(., c("waic","loo"))
+
+bm_octs_fix_int <- brm(mean_click ~  touchscreen + ageinyears * older_children + (ageinyears |community), 
+                              data   = scdata, 
+                              family = lognormal(),
+                              warmup = 2000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+            # backend = "cmdstanr"
+             )%>%
+  add_criterion(., c("waic","loo"))
+
+bm_octs_rand <- brm(mean_click ~ ageinyears + touchscreen + older_children + (ageinyears + older_children |community), 
+                              data   = scdata, 
+                              family = lognormal(),
+                              warmup = 2000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+             #backend = "cmdstanr"
+             )%>%
+  add_criterion(., c("waic","loo"))
+
+bm_octs_rand_int <- brm(mean_click ~ touchscreen + ageinyears*older_children + (ageinyears * older_children |community), 
+                              data   = scdata, 
+                              family = lognormal(),
+                              warmup = 2000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+             #backend = "cmdstanr"
+             )%>%
   add_criterion(., c("waic","loo"))
@@
 loo_compare(bm_base,
-            bm_full_fix, 
+            #bm_full_fix, 
             bm_full_rand,
             bm_fullc_fix,
-            bm_cts_fix,
-            bm_ycts_fix,
-            bm_octs_fix
+            #bm_cts_fix,
+            #bm_ycts_fix,
+            bm_octs_fix,
+            bm_octs_fix_int,
+            bm_octs_rand_int,
+            bm_octs_rand#,
+            #bm_full_rand
             #bm_hhts_fix#,
@@
 model_weights(bm_base,
-            bm_octs_fix, criterion = "loo")%>%as_tibble(rownames = "model")
+            #bm_full_fix, 
+            bm_full_rand,
+            bm_fullc_fix,
+            #bm_cts_fix,
+            #bm_ycts_fix,
+            bm_octs_fix,
+            bm_octs_fix_int,
+            bm_octs_rand_int,
+            bm_octs_rand,
+            #bm_full_rand
+            #bm_hhts_fix#,
+            #bm_cts_fix_int,
+            #bm_cts_rand_int,
+            #bm_cts_rand#,
+            #bm_hhts_rand_2, 
+            #bm_hhts_rand,
+            criterion = "loo")%>%as_tibble(rownames = "model")
 
-fixef(bm_octs_fix)
+fixef(bm_cts_rand)
 ```
@@
   theme_bw()+
-  scale_color_ptol(name = "Community")+
-  scale_fill_ptol(name = "Community")+
+  scale_color_manual(name = "Community", values = colors)+
+  scale_fill_manual(name = "Community", values = colors)+
   labs(x = "Age", y="Imprecision")#+
@@
   mutate(touchscreen = 1)%>%
-  expand_grid(children = c(min(scdata$children):max(scdata$children)))
+  expand_grid(older_children = c(min(scdata$older_children):max(scdata$older_children)))
 
-cpost <- fitted(bm_cts_rand_int, newdata = ncdata, re_formula =~(children|community))%>%
+cpost <- fitted(bm_octs_rand, newdata = ncdata, re_formula =~(older_children|community))%>%
   as_tibble() %>%
@@
 ggplot()+
-  geom_smooth(data = cpost, aes(x = children, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
+  geom_smooth(data = cpost, aes(x = older_children, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
   theme_bw()+
-  scale_color_ptol(name = "Community")+
-  scale_fill_ptol(name = "Community")+
-  facet_grid(~community)+
-  labs(x = "No of children (scaled)", y="Imprecision")
+  scale_color_manual(name = "Community", values = colors)+
+  scale_fill_manual(name = "Community", values = colors)+
+  facet_wrap(~community, nrow = 2)+
+  labs(x = "No of children older than the target child (scaled)", y="Imprecision")
 
+```
+
+```{r}
+ncdata <- scdata%>%
+  distinct(community)%>%
+  expand_grid(ageinyears = c(-1, 0, 1))%>%
+  mutate(touchscreen = 1)%>%
+  expand_grid(older_children = c(min(scdata$older_children):max(scdata$older_children)))
+
+cpost <- fitted(bm_octs_rand_int, newdata = ncdata, re_formula =~(older_children|community))%>%
+  as_tibble() %>%
+  bind_cols(ncdata)
+
+ggplot()+
+  geom_smooth(data = cpost, aes(x = older_children, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill = factor(ageinyears), col = factor(ageinyears)), stat = "identity", alpha = .25)+
+  theme_bw()+
+  scale_color_ptol()+
+  scale_fill_ptol()+
+  facet_wrap(~community, nrow = 2)+
+  labs(x = "No of children older than the target child (scaled)", y="Imprecision")
+
+```
+
+```{r}
+ggsave("../visuals/old_child_site.png", width = 12, height = , bg = "white")
 ```

### 2023-12-11 analysis/gafo-cc-data-processing.Rmd
add model data

--- 2023-09-15 analysis/gafo-cc-data-processing.Rmd
@@
 tidy_data_nz%>%
-  filter(trialType == "test")%>%
+  #filter(trialType == "test")%>%
   group_by(subjID)%>%
@@
 
-data_nz%>%
-  group_by(age)%>%
-  summarise(n())
+# data_nz%>%
+#   group_by(age)%>%
+#   summarise(n())
 ```
@@
     studytype = as.factor("vali"),
-  ) %>%select(-touchScreen)#%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
+    subjID = as.character(subjID),
+    subjID = ifelse(subjID == "TUR79000", "TUR00079",subjID),
+    subjID = ifelse(subjID == "TUR80000", "TUR00080",subjID),
+    subjID = ifelse(subjID == "TUR81000", "TUR00081",subjID),
+    subjID = ifelse(subjID == "TUR83000", "TUR00083",subjID),
+    subjID = ifelse(subjID == "TUR84000", "TUR00084",subjID),
+    subjID = ifelse(subjID == "TUR85000", "TUR00085",subjID)
+  ) %>%select(-touchScreen)%>%
+  mutate(subjID = factor(subjID))#%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
 ```
@@
 
+unique(tidy_data_tur$subjID)
 ```
@@
   mutate(subjid = recode(subjid, 
-                     "EBRAR100" = "TUR00002",
-                     "FATMA400" = "TUR00003",
-                     "ASYAA200" = "TUR00004"))
+                     "EBRAR100" = "TUR00001",
+                     "FATMA400" = "TUR00002",
+                     "ASYAA200" = "TUR00003"))
 
@@
 data_tur%>%
+  mutate(age_group = substr(ageinyears, 1,1))%>%
+  group_by(age_group)%>%
+  summarise(n = n_distinct(subjid))
+
+```
+
+# Congo
+
+```{r read_data}
+# get all .json files
+files <- list.files("../../../../../../Cloud/QuantEx/Gafo-cc/data/congo/data_GaFo/", pattern = "*.json",recursive = T)
+
+# convert json files to tibbles
+raw_data_cong <- tibble()
+for (f in files) {
+  jf <- paste("../../../../../../Cloud/QuantEx/Gafo-cc/data/congo/data_GaFo/", f, sep = "")
+  jd <- jsonlite::fromJSON(paste(readLines(jf, warn = "FALSE"), collapse = ""))
+
+  # needed because hedge trials have numbers, box trials have characters
+  jd$targetPosition <- factor(as.character(jd$targetPosition))
+
+  raw_data_cong <- bind_rows(raw_data_cong, jd)
+}
+# remove variables that we don't need anymore
+rm(f, files, jf, jd)
+```
+
+```{r}
+tidy_data_cong <- raw_data_cong %>%
+
+  # convert all character vectors into factors
+  mutate_if(is.character, as.factor) %>%
+
+  mutate(
+
+    # attention! the SVG coord system starts with 0, 0 in upper left corner
+    # we transform the values so that 0, 0 is lower left corner (for plots etc)
+    clickScaledY = 1080 - clickScaledY,
+    targetY = 1080 - targetY, 
+    targetCenterY = 1080 - targetCenterY, 
+    eyeCenterRightY = 1080 - eyeCenterRightY,
+    eyeCenterLeftY = 1080 - eyeCenterLeftY,
+    pupilFinalRightY = 1080 - pupilFinalRightY,
+    pupilFinalLeftY = 1080 - pupilFinalLeftY, 
+    targetCentralityX = abs(960 - targetCenterX),
+
+    # similarly here: in svg coords, negative click distance means up. 
+    # here we invert it, so that negative values mean down
+    clickDistFromTargetCenterY = clickDistFromTargetCenterY * -1, 
+    clickDistFromTargetBBoxY = clickDistFromTargetBBoxY * -1,
+
+    # positive values for inward clicks (i.e.,towards the center), negative for outward clicks
+    centralityBias = ifelse(targetCenterX <= 1920/2,
+                            clickDistFromTargetCenterX, 
+                            clickDistFromTargetCenterX*-1),
+
+    inwardClick = ifelse(centralityBias > 0, TRUE, FALSE),
+
+    # did the participant click on the right box?
+    # also for hedge version, here we imagine a box surrounding the target center 
+    # this way, we can compare hedge and box version ;) 
+    boxWidth = 218, 
+    boxBorderLeft = targetCenterX - boxWidth/2, 
+    boxBorderRight = targetCenterX + boxWidth/2,
+    correctBox = ifelse(boxBorderLeft <= clickScaledX & clickScaledX <= boxBorderRight, TRUE, FALSE),
+
+    datacollection = as.factor("in-person - supervised"), 
+    sample = as.factor("na"),
+    studytype = as.factor("vali"),
+  ) %>%select(-touchScreen)#%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
+```
+
+```{r}
+tidy_data_cong%>%
+  summarise(n = n_distinct(subjID))
+
+tidy_data_cong%>%
+  group_by(subjID)%>%
+  summarise(n = n())
+
+```
+
+```{r }
+raw_demographics_cong <- bind_rows(
+    read_xlsx("../../../../../../Cloud/QuantEx/Gafo-cc/data/congo/gafo-cc-congo-participants_2023_V3.xlsx", sheet = 1)%>%
+      mutate(household = as.character(household),
+             children = as.character(children),
+             younger_children = as.character(younger_children)),
+    read_xlsx("../../../../../../Cloud/QuantEx/Gafo-cc/data/congo/gafo-cc-congo-participants_2023_V3.xlsx", sheet = 2),
+  )
+
+tidy_demographics_cong <- raw_demographics_cong %>%
+  filter(birth_date != "NA")%>%
+  filter(status == "keep", id != "BD000001", id != "BY000001")%>%
+  mutate(
+    test_date = as.Date(as.character(test_date), format = "%Y%m%d"),
+    birth_date = as.Date(as.character(birth_date), format = "%Y%m%d"),
+    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
+    screen = ifelse(screen == "fallaci", 0, 1), 
+    touchscreen = ifelse(touchscreen == "fallaci", 0, 1),
+    household = as.numeric(household), 
+    children = as.numeric(children),
+    younger_children = as.numeric(younger_children)
+  )  %>%
+  select(-c(first_name, last_name, test_date, birth_date, comment))%>%
+  #filter(!is.na(ageinyears))%>%
+  rename(subjid = id)
+
+```
+
+```{r}
+data_cong <- tidy_demographics_cong%>%
+  left_join(tidy_data_cong%>%rename_all(tolower),by = c("subjid"))%>%
+  #mutate(community = "congo")%>%
+  distinct(subjid, trialnr, .keep_all = TRUE)
+
+data_cong%>%
+  group_by(subjid)%>%
+  summarise(n = n())
+
+data_cong%>%
   group_by(subjid)%>%
@@
 ```
-
 # Merge
@@
   data_ind,
-  data_nz
+  data_nz, 
+  data_tur,
+  data_cong
 )%>%
@@
 
+methods_data <- merge_raw_data%>%
+  select(subjid, community, age_group, ageinyears, trialnr, targetposition,targetcentralityx, clickdistfromtargetcenterx)%>%
+  filter(ageinyears > 1)
+
+write_csv(methods_data,"../../tango-cc-methods/data/data.csv")
+```
+
+```{r}
+fam_excl <- bind_rows(
+  data_zambia,
+  data_namibia%>%rename(younger_children = youngerchildren),
+  data_leipzig,
+  data_nigeria,
+  data_plymouth,
+  data_stanford,
+  data_mex,
+  data_china, 
+  data_arg,
+  data_ind,
+  data_nz, 
+  data_tur,
+  data_cong
+)%>%
+  filter(trialtype != "test")%>%
+  group_by(subjid,community)%>%
+  mutate(click = abs(clickdistfromtargetcenterx))%>%
+  summarise(mean_click = mean(click))%>%
+  filter(mean_click > 100)%>%
+  pull(subjid)
 ```
@@
 ```{r}
-merge_raw_data <- read_csv("../data/gafo-cc-raw-data.csv")
-```
-
-```{r}
-chimfunshi_data <- merge_raw_data%>%
-  filter(community == "chimfunshi",
+
+communities <- unique(merge_raw_data$community)
+
+for (i in communities) {
+
+m_data <- merge_raw_data%>%
+  filter(community == i,
          voiceover == F)%>%
@@
 
-write(toJSON(chimfunshi_data), file = "../model/model_data/chimfunshi-model-data.json")
-```
-
-```{r}
-haillom_data <- merge_raw_data%>%
-  filter(community == "hai||om",
-         voiceover == F)%>%
-  mutate(agecentered = ageinyears - min(ageinyears))%>%
-  select(-c(sex,ageinyears, wrongareaclick, earlyclick, durationanimationballoontotal, durationanimationcomplete, responsetime, clientscreenwidth, clientscreenheight, clientscreenscaling, clickoriginalx, clickoriginaly, hitbbtargetx, hitbbtargety, clickdistfromtargetbboxx, clickedarea, studyversion, boxesnr,population, inhouse, os, mobile, browser, browserversion, safari, iossafari,target, voiceover, epoch, timestamp, inwardclick, boxwidth,boxborderleft, boxborderright , correctbox, datacollection, sample, studytype, comment, status, site,`location` ))
-
-write(toJSON(haillom_data), file = "../model/model_data/haillom-model-data.json")
-
-write_csv(mdata, file = "../model/model_data/gafo-cc-model-data.csv")
+write(toJSON(m_data), file = paste0("../model/model_data/", i, "-model-data.json"))
+
+#write_csv(mdata, file = "../model/model_data/", i, "-model-data.csv")
+
+}
+
 ```

### 2023-12-13 analysis/gafo-cc-data-processing.Rmd
update figures

@@
 ```
+# Uganda
+
+```{r read_data}
+# get all .json files
+files <- list.files("../../raw_data/gafo-cc/uganda/", pattern = "*.json",recursive = T)%>% str_subset(pattern = "gafo--", negate = T)
+
+# convert json files to tibbles
+raw_data_uganda <- tibble()
+for (f in files) {
+  jf <- paste("../../raw_data/gafo-cc/uganda/", f, sep = "")
+  jd <- jsonlite::fromJSON(paste(readLines(jf, warn = "FALSE"), collapse = ""))
+
+  # needed because hedge trials have numbers, box trials have characters
+  jd$targetPosition <- factor(as.character(jd$targetPosition))
+
+  raw_data_uganda <- bind_rows(raw_data_uganda, jd)
+}
+# remove variables that we don't need anymore
+rm(f, files, jf, jd)
+```
+
+```{r}
+tidy_data_uganda <- raw_data_uganda %>%
+
+  # convert all character vectors into factors
+
+  mutate(
+
+    # attention! the SVG coord system starts with 0, 0 in upper left corner
+    # we transform the values so that 0, 0 is lower left corner (for plots etc)
+    clickScaledY = 1080 - clickScaledY,
+    targetY = 1080 - targetY, 
+    targetCenterY = 1080 - targetCenterY, 
+    eyeCenterRightY = 1080 - eyeCenterRightY,
+    eyeCenterLeftY = 1080 - eyeCenterLeftY,
+    pupilFinalRightY = 1080 - pupilFinalRightY,
+    pupilFinalLeftY = 1080 - pupilFinalLeftY, 
+    targetCentralityX = abs(960 - targetCenterX),
+
+    # similarly here: in svg coords, negative click distance means up. 
+    # here we invert it, so that negative values mean down
+    clickDistFromTargetCenterY = clickDistFromTargetCenterY * -1, 
+    clickDistFromTargetBBoxY = clickDistFromTargetBBoxY * -1,
+
+    # positive values for inward clicks (i.e.,towards the center), negative for outward clicks
+    centralityBias = ifelse(targetCenterX <= 1920/2,
+                            clickDistFromTargetCenterX, 
+                            clickDistFromTargetCenterX*-1),
+
+    inwardClick = ifelse(centralityBias > 0, TRUE, FALSE),
+
+    # did the participant click on the right box?
+    # also for hedge version, here we imagine a box surrounding the target center 
+    # this way, we can compare hedge and box version ;) 
+    boxWidth = 218, 
+    boxBorderLeft = targetCenterX - boxWidth/2, 
+    boxBorderRight = targetCenterX + boxWidth/2,
+    correctBox = ifelse(boxBorderLeft <= clickScaledX & clickScaledX <= boxBorderRight, TRUE, FALSE),
+
+    datacollection = as.factor("in-person - supervised"), 
+    sample = as.factor("na"),
+    studytype = as.factor("vali")
+  ) %>%
+  mutate(subjID = ifelse(subjID == "ugaand04", "ugand004", subjID),
+         subjID =as.factor(subjID))%>%
+  select(-touchScreen)%>%
+  mutate_if(is.character, as.factor)%>% 
+  distinct(subjID, trialNr, .keep_all = T)#%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
+
+unique(tidy_data_uganda$subjID)
+```
+
+```{r}
+tidy_data_uganda%>%
+  filter(trialType == "test")%>%
+  group_by(subjID)%>%
+  summarise(n = n())
+
+tidy_data_uganda%>%
+  filter(trialType == "test")%>%
+  summarise(n = n_distinct(subjID))
+
+```
+
+```{r demographics}
+raw_demographics_uganda <- read_xlsx("../../raw_data/gafo-cc/uganda/gafo_uganda_participants.xlsx", sheet = 1)[-1, ]
+
+tidy_demographics_uganda <- raw_demographics_uganda %>%
+  rename(subjid = id)%>%
+  mutate_all(tolower)%>%
+  filter(status == "keep")%>%
+  mutate(
+    test_date = as.Date(as.character(test_date), format = "%Y%m%d"),
+    birth_date = as.Date(as.character(birth_date), format = "%Y%m%d"),
+    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
+    screen = as.numeric(screen), 
+    touchscreen = as.numeric(touchscreen),
+    household = as.numeric(household), 
+    children = as.numeric(children),
+    younger_children = as.numeric(younger_children)
+  )  %>%
+  select(-c(test_date, birth_date, comment, age))%>%
+  filter(!is.na(ageinyears))
+
+```
+
+```{r}
+data_uganda <- tidy_demographics_uganda%>%
+  left_join(tidy_data_uganda%>%rename_all(tolower),by = c("subjid"))%>%
+  distinct(subjid, trialnr, .keep_all = TRUE)
+
+data_uganda%>%
+  mutate(age_group = substr(ageinyears, 1,1))%>%
+  group_by(age_group)%>%
+  summarise(n = n_distinct(subjid))
+
+```
+
 # Merge
@@
   data_tur,
-  data_cong
+  data_cong,
+  data_uganda
 )%>%

### 2023-12-13 paper/paper.Rmd
update figures

---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - "Writing - Review & Editing"
      - "Supervision"

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  One or two sentences to put the results into a more **general context**.
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "keywords"
wordcount         : "X"

bibliography      : "r-references.bib"
csl: science.csl

floatsintext      : yes
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

Participants in the study lived in 17 different communities spread over five continents. Taken together, the countries from which data was contributed to the study represent 46% of the world's population.

# Results

# Discussion

# Methods

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

\newpage

# References

::: {#refs custom-style="Bibliography"}
:::

### 2024-01-02 analysis/gafo-cc-model.Rmd
update model comparison

@@
 ```{r, message=FALSE, warning=F}
-haillom_model_comparison <- rbindlist(
-  list(
-     fread("../model/output/haillom_model_comparison_chain1.csv"),
-     fread("../model/output/haillom_model_comparison_chain1.csv"),
-     fread("../model/output/haillom_model_comparison_chain1.csv"),
-     fread("../model/output/haillom_model_comparison_chain1.csv"),
-     fread("../model/output/haillom_model_comparison_chain1.csv"),
-     fread("../model/output/haillom_model_comparison_chain1.csv")
-    ), use.names=TRUE)%>%saveRDS("../models/output/haillom_model_comparison.rds")%>%
-  group_by(chain, iteration, model)%>%
-  summarise(like = sum(loglike))%>%
-  mutate(community = "hai||om")
+# haillom_model_comparison <- rbindlist(
+#   list(
+#      fread("../model/output/haillom_model_comparison_chain1.csv"),
+#      fread("../model/output/haillom_model_comparison_chain2.csv"),
+#      fread("../model/output/haillom_model_comparison_chain3.csv"),
+#      fread("../model/output/haillom_model_comparison_chain4.csv"),
+#      fread("../model/output/haillom_model_comparison_chain5.csv"),
+#      fread("../model/output/haillom_model_comparison_chain6.csv")
+#     ), use.names=TRUE)%>%
+#   group_by(chain, iteration, model)%>%
+#   summarise(like = sum(loglike))%>%
+#   mutate(community = "hai||om")%>%
+#   saveRDS("../model/output/haillom_model_comparison.rds")
 
@@
   group_by(community, model,chain)%>%
-  summarise(margllh = logSumExp(like))%>%
+  summarise(margllh = logSumExp(like), 
+            n = n_distinct(iteration))%>%
+  pivot_wider(names_from = model, values_from = margllh)
+```
+
+## Chimfunshi
+
+```{r, message=FALSE, warning=F}
+# chimfunshi_model_comparison <- rbindlist(
+#   list(
+#      fread("../model/output/chimfunshi_model_comparison_chain1.csv"),
+#      fread("../model/output/chimfunshi_model_comparison_chain2.csv"),
+#      fread("../model/output/chimfunshi_model_comparison_chain3.csv"),
+#      fread("../model/output/chimfunshi_model_comparison_chain4.csv"),
+#      fread("../model/output/chimfunshi_model_comparison_chain5.csv"),
+#      fread("../model/output/chimfunshi_model_comparison_chain6.csv")
+#     ), use.names=TRUE)%>%
+#   group_by(chain, iteration, model)%>%
+#   summarise(like = sum(loglike))%>%
+#   mutate(community = "chimfunshi")%>%
+#   saveRDS("../model/output/chimfunshi_model_comparison.rds")
+
+ chimfunshi_model_comparison <- readRDS("../model/output/chimfunshi_model_comparison.rds")
+```
+
+```{r}
+chimfunshi_model_comparison%>%
+  group_by(community, model,chain)%>%
+  summarise(margllh = logSumExp(like), 
+            n = n_distinct(iteration))%>%
+  pivot_wider(names_from = model, values_from = margllh)
+```
+
+## Mexico
+
+```{r, message=FALSE, warning=F}
+# mexico_model_comparison <- rbindlist(
+#   list(
+#      fread("../model/output/mexico_model_comparison_chain1.csv"),
+#      fread("../model/output/mexico_model_comparison_chain2.csv"),
+#      fread("../model/output/mexico_model_comparison_chain3.csv"),
+#      fread("../model/output/mexico_model_comparison_chain4.csv"),
+#      fread("../model/output/mexico_model_comparison_chain5.csv"),
+#      fread("../model/output/mexico_model_comparison_chain6.csv")
+#     ), use.names=TRUE)%>%
+#   group_by(chain, iteration, model)%>%
+#   summarise(like = sum(loglike))%>%
+#   mutate(community = "mexico")%>%
+#   saveRDS("../model/output/mexico_model_comparison.rds")
+
+ mexico_model_comparison <- readRDS("../model/output/mexico_model_comparison.rds")
+```
+
+```{r}
+mexico_model_comparison%>%
+  group_by(community, model,chain)%>%
+  summarise(margllh = logSumExp(like), 
+            n = n_distinct(iteration))%>%
+  pivot_wider(names_from = model, values_from = margllh)
+```
+
+## India
+
+```{r, message=FALSE, warning=F}
+# india_model_comparison <- rbindlist(
+#   list(
+#      fread("../model/output/india_model_comparison_chain1.csv"),
+#      fread("../model/output/india_model_comparison_chain2.csv"),
+#      fread("../model/output/india_model_comparison_chain3.csv"),
+#      fread("../model/output/india_model_comparison_chain4.csv"),
+#      fread("../model/output/india_model_comparison_chain5.csv"),
+#      fread("../model/output/india_model_comparison_chain6.csv")
+#     ), use.names=TRUE)%>%
+#   group_by(chain, iteration, model)%>%
+#   summarise(like = sum(loglike))%>%
+#   mutate(community = "india")%>%
+#   saveRDS("../model/output/india_model_comparison.rds")
+
+  india_model_comparison <- readRDS("../model/output/india_model_comparison.rds")
+```
+
+```{r}
+india_model_comparison%>%
+  group_by(community, model,chain)%>%
+  summarise(margllh = logSumExp(like), 
+            n = n_distinct(iteration))%>%
+  pivot_wider(names_from = model, values_from = margllh)
+```
+
+## Akure
+
+```{r, message=FALSE, warning=F}
+# nigeria_model_comparison <- rbindlist(
+#   list(
+#      fread("../model/output/akure_model_comparison_chain1.csv"),
+#      fread("../model/output/akure_model_comparison_chain2.csv"),
+#      fread("../model/output/akure_model_comparison_chain3.csv"),
+#      fread("../model/output/akure_model_comparison_chain4.csv"),
+#      fread("../model/output/akure_model_comparison_chain5.csv"),
+#      fread("../model/output/akure_model_comparison_chain6.csv")
+#     ), use.names=TRUE)%>%
+#   group_by(chain, iteration, model)%>%
+#   summarise(like = sum(loglike))%>%
+#   mutate(community = "nigeria")%>%
+#   saveRDS("../model/output/nigeria_model_comparison.rds")
+
+nigeria_model_comparison <- readRDS("../model/output/nigeria_model_comparison.rds")
+```
+
+```{r}
+nigeria_model_comparison%>%
+  group_by(community, model,chain)%>%
+  summarise(margllh = logSumExp(like), 
+            n = n_distinct(iteration))%>%
+  pivot_wider(names_from = model, values_from = margllh)
+```
+
+## Beijing
+
+```{r, message=FALSE, warning=F}
+# china_model_comparison <- rbindlist(
+#   list(
+#      fread("../model/output/beijing_model_comparison_chain1.csv"),
+#      fread("../model/output/beijing_model_comparison_chain2.csv"),
+#      fread("../model/output/beijing_model_comparison_chain3.csv"),
+#      fread("../model/output/beijing_model_comparison_chain4.csv"),
+#      fread("../model/output/beijing_model_comparison_chain5.csv"),
+#      fread("../model/output/beijing_model_comparison_chain6.csv")
+#     ), use.names=TRUE)%>%
+#   group_by(chain, iteration, model)%>%
+#   summarise(like = sum(loglike))%>%
+#   mutate(community = "china")%>%
+#   saveRDS("../model/output/china_model_comparison.rds")
+
+china_model_comparison <- readRDS("../model/output/china_model_comparison.rds")
+```
+
+```{r}
+china_model_comparison%>%
+  group_by(community, model,chain)%>%
+  summarise(margllh = logSumExp(like), 
+            n = n_distinct(iteration))%>%
+  pivot_wider(names_from = model, values_from = margllh)
+```
+
+## Buenos Aires
+
+```{r, message=FALSE, warning=F}
+# argentina_model_comparison <- rbindlist(
+#   list(
+#      fread("../model/output/buenos_aires_model_comparison_chain1.csv"),
+#      fread("../model/output/buenos_aires_model_comparison_chain2.csv"),
+#      fread("../model/output/buenos_aires_model_comparison_chain3.csv"),
+#      fread("../model/output/buenos_aires_model_comparison_chain4.csv"),
+#      fread("../model/output/buenos_aires_model_comparison_chain5.csv"),
+#      fread("../model/output/buenos_aires_model_comparison_chain6.csv")
+#     ), use.names=TRUE)%>%
+#   group_by(chain, iteration, model)%>%
+#   summarise(like = sum(loglike))%>%
+#   mutate(community = "argentina")%>%
+#   saveRDS("../model/output/argentina_model_comparison.rds")
+
+argentina_model_comparison <- readRDS("../model/output/argentina_model_comparison.rds")
+```
+
+```{r}
+argentina_model_comparison%>%
+  group_by(community, model,chain)%>%
+  summarise(margllh = logSumExp(like), 
+            n = n_distinct(iteration))%>%
+  pivot_wider(names_from = model, values_from = margllh)
+```
+
+## Leipzig
+
+```{r, message=FALSE, warning=F}
+# leipzig_model_comparison <- rbindlist(
+#   list(
+#      fread("../model/output/leipzig_model_comparison_chain1.csv"),
+#      fread("../model/output/leipzig_model_comparison_chain2.csv"),
+#      fread("../model/output/leipzig_model_comparison_chain3.csv"),
+#      fread("../model/output/leipzig_model_comparison_chain4.csv"),
+#      fread("../model/output/leipzig_model_comparison_chain5.csv"),
+#      fread("../model/output/leipzig_model_comparison_chain6.csv")
+#     ), use.names=TRUE)%>%
+#   group_by(chain, iteration, model)%>%
+#   summarise(like = sum(loglike))%>%
+#   mutate(community = "leipzig")%>%
+#   saveRDS("../model/output/leipzig_model_comparison.rds")
+
+leipzig_model_comparison <- readRDS("../model/output/leipzig_model_comparison.rds")
+```
+
+```{r}
+leipzig_model_comparison%>%
+  group_by(community, model,chain)%>%
+  summarise(margllh = logSumExp(like), 
+            n = n_distinct(iteration))%>%
+  pivot_wider(names_from = model, values_from = margllh)
+```
+
+## Auckland
+
+```{r, message=FALSE, warning=F}
+# auckland_model_comparison <- rbindlist(
+#   list(
+#     fread("../model/output/auckland_model_comparison_chain1.csv"),
+#     fread("../model/output/auckland_model_comparison_chain2.csv"),
+#     fread("../model/output/auckland_model_comparison_chain3.csv"),
+#     fread("../model/output/auckland_model_comparison_chain4.csv"),
+#     fread("../model/output/auckland_model_comparison_chain5.csv"),
+#     fread("../model/output/auckland_model_comparison_chain6.csv")
+#   ), use.names=TRUE)%>%
+#   group_by(chain, iteration, model)%>%
+#   summarise(like = sum(loglike))%>%
+#   mutate(community = "auckland")%>%
+#   saveRDS("../model/output/auckland_model_comparison.rds")
+
+auckland_model_comparison <- readRDS("../model/output/auckland_model_comparison.rds")
+```
+
+```{r}
+auckland_model_comparison%>%
+  group_by(community, model,chain)%>%
+  summarise(margllh = logSumExp(like), 
+            n = n_distinct(iteration))%>%
+  pivot_wider(names_from = model, values_from = margllh)
+```
+
+## bandongo
+
+```{r, message=FALSE, warning=F}
+# bandongo_model_comparison <- rbindlist(
+#   list(
+#     fread("../model/output/bandongo_model_comparison_chain1.csv"),
+#     fread("../model/output/bandongo_model_comparison_chain2.csv"),
+#     fread("../model/output/bandongo_model_comparison_chain3.csv"),
+#     fread("../model/output/bandongo_model_comparison_chain4.csv"),
+#     fread("../model/output/bandongo_model_comparison_chain5.csv"),
+#     fread("../model/output/bandongo_model_comparison_chain6.csv")
+#   ), use.names=TRUE)%>%
+#   group_by(chain, iteration, model)%>%
+#   summarise(like = sum(loglike))%>%
+#   mutate(community = "bandongo")%>%
+#   saveRDS("../model/output/bandongo_model_comparison.rds")
+
+bandongo_model_comparison <- readRDS("../model/output/bandongo_model_comparison.rds")
+```
+
+```{r}
+bandongo_model_comparison%>%
+  group_by(community, model,chain)%>%
+  summarise(margllh = logSumExp(like), 
+            n = n_distinct(iteration))%>%
+  pivot_wider(names_from = model, values_from = margllh)
+```
+
+## bayaka
+
+```{r, message=FALSE, warning=F}
+# bayaka_model_comparison <- rbindlist(
+#   list(
+#     fread("../model/output/bayaka_model_comparison_chain1.csv"),
+#     fread("../model/output/bayaka_model_comparison_chain2.csv"),
+#     fread("../model/output/bayaka_model_comparison_chain3.csv"),
+#     fread("../model/output/bayaka_model_comparison_chain4.csv"),
+#     fread("../model/output/bayaka_model_comparison_chain5.csv"),
+#     fread("../model/output/bayaka_model_comparison_chain6.csv")
+#   ), use.names=TRUE)%>%
+#   group_by(chain, iteration, model)%>%
+#   summarise(like = sum(loglike))%>%
+#   mutate(community = "bayaka")%>%
+#   saveRDS("../model/output/bayaka_model_comparison.rds")
+
+bayaka_model_comparison <- readRDS("../model/output/bayaka_model_comparison.rds")
+```
+
+```{r}
+bayaka_model_comparison%>%
+  group_by(community, model,chain)%>%
+  summarise(margllh = logSumExp(like), 
+            n = n_distinct(iteration))%>%
+  pivot_wider(names_from = model, values_from = margllh)
+```
+
+## khwe
+
+```{r, message=FALSE, warning=F}
+khwe_model_comparison <- rbindlist(
+  list(
+    fread("../model/output/khwe_model_comparison_chain1.csv"),
+    fread("../model/output/khwe_model_comparison_chain2.csv"),
+    fread("../model/output/khwe_model_comparison_chain3.csv"),
+    fread("../model/output/khwe_model_comparison_chain4.csv"),
+    fread("../model/output/khwe_model_comparison_chain5.csv"),
+    fread("../model/output/khwe_model_comparison_chain6.csv")
+  ), use.names=TRUE)%>%
+  group_by(chain, iteration, model)%>%
+  summarise(like = sum(loglike))%>%
+  mutate(community = "khwe")%>%
+  saveRDS("../model/output/khwe_model_comparison.rds")
+
+khwe_model_comparison <- readRDS("../model/output/khwe_model_comparison.rds")
+```
+
+```{r}
+khwe_model_comparison%>%
+  group_by(community, model,chain)%>%
+  summarise(margllh = logSumExp(like), 
+            n = n_distinct(iteration))%>%
+  pivot_wider(names_from = model, values_from = margllh)
+```
+
+## plymouth
+
+```{r, message=FALSE, warning=F}
+plymouth_model_comparison <- rbindlist(
+  list(
+    fread("../model/output/plymouth_model_comparison_chain1.csv"),
+    fread("../model/output/plymouth_model_comparison_chain2.csv"),
+    fread("../model/output/plymouth_model_comparison_chain3.csv"),
+    fread("../model/output/plymouth_model_comparison_chain4.csv"),
+    fread("../model/output/plymouth_model_comparison_chain5.csv"),
+    fread("../model/output/plymouth_model_comparison_chain6.csv")
+  ), use.names=TRUE)%>%
+  group_by(chain, iteration, model)%>%
+  summarise(like = sum(loglike))%>%
+  mutate(community = "plymouth")%>%
+  saveRDS("../model/output/plymouth_model_comparison.rds")
+
+plymouth_model_comparison <- readRDS("../model/output/plymouth_model_comparison.rds")
+```
+
+```{r}
+plymouth_model_comparison%>%
+  group_by(community, model,chain)%>%
+  summarise(margllh = logSumExp(like), 
+            n = n_distinct(iteration))%>%
+  pivot_wider(names_from = model, values_from = margllh)
+```
+
+## stanford
+
+```{r, message=FALSE, warning=F}
+stanford_model_comparison <- rbindlist(
+  list(
+    fread("../model/output/stanford_model_comparison_chain1.csv"),
+    fread("../model/output/stanford_model_comparison_chain2.csv"),
+    fread("../model/output/stanford_model_comparison_chain3.csv"),
+    fread("../model/output/stanford_model_comparison_chain4.csv"),
+    fread("../model/output/stanford_model_comparison_chain5.csv"),
+    fread("../model/output/stanford_model_comparison_chain6.csv")
+  ), use.names=TRUE)%>%
+  group_by(chain, iteration, model)%>%
+  summarise(like = sum(loglike))%>%
+  mutate(community = "stanford")%>%
+  saveRDS("../model/output/stanford_model_comparison.rds")
+
+stanford_model_comparison <- readRDS("../model/output/stanford_model_comparison.rds")
+```
+
+```{r}
+stanford_model_comparison%>%
+  group_by(community, model,chain)%>%
+  summarise(margllh = logSumExp(like), 
+            n = n_distinct(iteration))%>%
+  pivot_wider(names_from = model, values_from = margllh)
+```
+
+## turkey
+
+```{r, message=FALSE, warning=F}
+turkey_model_comparison <- rbindlist(
+  list(
+    fread("../model/output/turkey_model_comparison_chain1.csv"),
+    fread("../model/output/turkey_model_comparison_chain2.csv"),
+    fread("../model/output/turkey_model_comparison_chain3.csv"),
+    fread("../model/output/turkey_model_comparison_chain4.csv"),
+    fread("../model/output/turkey_model_comparison_chain5.csv"),
+    fread("../model/output/turkey_model_comparison_chain6.csv")
+  ), use.names=TRUE)%>%
+  group_by(chain, iteration, model)%>%
+  summarise(like = sum(loglike))%>%
+  mutate(community = "turkey")%>%
+  saveRDS("../model/output/turkey_model_comparison.rds")
+
+turkey_model_comparison <- readRDS("../model/output/turkey_model_comparison.rds")
+```
+
+```{r}
+turkey_model_comparison%>%
+  group_by(community, model,chain)%>%
+  summarise(margllh = logSumExp(like), 
+            n = n_distinct(iteration))%>%
+  pivot_wider(names_from = model, values_from = margllh)
+```
+
+## windhoek
+
+```{r, message=FALSE, warning=F}
+windhoek_model_comparison <- rbindlist(
+  list(
+    fread("../model/output/windhoek_model_comparison_chain1.csv"),
+    fread("../model/output/windhoek_model_comparison_chain2.csv"),
+    fread("../model/output/windhoek_model_comparison_chain3.csv"),
+    fread("../model/output/windhoek_model_comparison_chain4.csv"),
+    fread("../model/output/windhoek_model_comparison_chain5.csv"),
+    fread("../model/output/windhoek_model_comparison_chain6.csv")
+  ), use.names=TRUE)%>%
+  group_by(chain, iteration, model)%>%
+  summarise(like = sum(loglike))%>%
+  mutate(community = "windhoek")%>%
+  saveRDS("../model/output/windhoek_model_comparison.rds")
+
+windhoek_model_comparison <- readRDS("../model/output/windhoek_model_comparison.rds")
+```
+
+```{r}
+windhoek_model_comparison%>%
+  group_by(community, model,chain)%>%
+  summarise(margllh = logSumExp(like), 
+            n = n_distinct(iteration))%>%
   pivot_wider(names_from = model, values_from = margllh)
@@
 ```{r}
-bind_rows(
-  haillom_model_comparison
+bf_comparison <- bind_rows(
+  haillom_model_comparison,
+  chimfunshi_model_comparison,
+  mexico_model_comparison,
+  india_model_comparison,
+  nigeria_model_comparison,
+  china_model_comparison,
+  argentina_model_comparison,
+  leipzig_model_comparison,
+  auckland_model_comparison,
+  bandongo_model_comparison,
+  bayaka_model_comparison,
+  khwe_model_comparison,
+  plymouth_model_comparison,
+  stanford_model_comparison,
+  turkey_model_comparison,
+  windhoek_model_comparison
 ) %>%
@@
 
+saveRDS(bf_comparison, "../model/output/bf_comparison.rds")
+
 ```
-
-```{r}
-bind_rows(
-  haillom_model_comparison
-)%>%
-  ggplot(aes(x = like))+
-  geom_histogram(alpha = .5, aes(fill = model), col = "black")+
-  facet_wrap(~community, scales = "free")+
-  scale_fill_colorblind()+
-  xlim(-8000, -5000)+
-  theme_bw()
-```

### 2024-01-03 analysis/gafo-cc-analysis.Rmd
add model for cluster run

@@
 library(brms)
+library(ggridges)
 ```
@@
   ungroup()%>%
+  mutate(older_children = children - 1 - younger_children)%>%
   mutate(ageinyears = scale(ageinyears),
@@
          trialnr = scale(trialnr),
-         #children = scale(children),
-         #household = scale(household),
-         #younger_children = scale(younger_children),
          touchscreen = factor(touchscreen),
@@
         click = abs(clickdistfromtargetcenterx))%>%
-  #filter(community != "chimfunshi")%>%
-  select(subjid,community,ageinyears,children, household, younger_children,trialnr, screen,touchscreen, targetcentralityx, click )
+  group_by(community)%>%
+  mutate(children = scale(children),
+         household = scale(household),
+         younger_children = scale(younger_children),
+         older_children = scale(older_children))%>%
+  select(subjid,community,ageinyears,children, household, younger_children,older_children, trialnr, screen,touchscreen, targetcentralityx, click )
 
@@
 
-bm_octs_rand <- brm(mean_click ~ ageinyears + touchscreen + older_children + (ageinyears + older_children |community), 
+bm_octs_rand <- brm(mean_click ~ ageinyears + touchscreen + older_children + (ageinyears + touchscreen + older_children |community), 
                               data   = scdata, 
@@
             bm_octs_fix,
-            bm_octs_fix_int,
-            bm_octs_rand_int,
+            #bm_octs_fix_int,
+            #bm_octs_rand_int,
             bm_octs_rand,
@@
 
-fixef(bm_cts_rand)
+fixef(bm_octs_rand)
 ```
@@
 ```{r}
-as_draws_df(bm_cts_rand_int)%>%
+as_draws_df(bm_octs_rand)%>%
   select(contains("children"))%>%
@@
   pivot_longer(cols = contains("children]"), names_to = "community", values_to = "value")%>%
-  mutate(post = value + b_children, 
+  mutate(post = value + b_older_children, 
          community = str_remove(community, "r_community"),
-         community = str_remove(community, ",children"))%>%
+         community = str_remove(community, ",older_children]"),
+         community = str_remove(community, "\\["))%>%
   ggplot(aes(x= post, y = community))+
-  stat_slabinterval()+
-  xlim(-0.15, 0.1)+
+  geom_vline(xintercept = 0, lty = 3, alpha = 0.75)+
+  geom_density_ridges(rel_min_height = 0.01, col = "white", alpha = .75)+
+  #stat_pointinterval()+
+  #xlim(-0.15, 0.1)+
   theme_bw()
+
+as_draws_df(bm_octs_rand)%>%
+  select(contains("touchscreen"))%>%
+  select(contains("touchscreen"))%>%
+  pivot_longer(cols = contains("touchscreen1]"), names_to = "community", values_to = "value")%>%
+  mutate(post = value + b_touchscreen1, 
+         community = str_remove(community, "r_community"),
+         community = str_remove(community, ",touchscreen1]"),
+         community = str_remove(community, "\\["))%>%
+  ggplot(aes(x= post, y = community))+
+  geom_vline(xintercept = 0, lty = 3, alpha = 0.75)+
+  geom_density_ridges(rel_min_height = 0.01, col = "white", alpha = .75)+
+  #stat_pointinterval()+
+  #xlim(-0.15, 0.1)+
+  theme_bw()
+
+as_draws_df(bm_octs_rand)%>%
+  select(contains("ageinyears"))%>%
+  select(contains("ageinyears"))%>%
+  pivot_longer(cols = contains("ageinyears]"), names_to = "community", values_to = "value")%>%
+  mutate(post = value + b_ageinyears, 
+         community = str_remove(community, "r_community"),
+         community = str_remove(community, ",ageinyears]"),
+         community = str_remove(community, "\\["))%>%
+  ggplot(aes(x= post, y = community))+
+  geom_vline(xintercept = 0, lty = 3, alpha = 0.75)+
+  geom_density_ridges(rel_min_height = 0.01, col = "white", alpha = .75)+
+  #stat_pointinterval()+
+  #xlim(-0.15, 0.1)+
+  theme_bw()
+
+bind_rows(
+as_draws_df(bm_octs_rand)%>%
+  select(contains("children"))%>%
+  select(contains("children"))%>%
+  pivot_longer(cols = contains("children]"), names_to = "community", values_to = "value")%>%
+  mutate(post = value + b_older_children, 
+         community = str_remove(community, "r_community"),
+         community = str_remove(community, ",older_children]"),
+         community = str_remove(community, "\\["))%>%
+  select(community, post)%>%
+  mutate(type = "older_children"),
+
+as_draws_df(bm_octs_rand)%>%
+  select(contains("touchscreen"))%>%
+  select(contains("touchscreen"))%>%
+  pivot_longer(cols = contains("touchscreen1]"), names_to = "community", values_to = "value")%>%
+  mutate(post = value + b_touchscreen1, 
+         community = str_remove(community, "r_community"),
+         community = str_remove(community, ",touchscreen1]"),
+         community = str_remove(community, "\\["))%>%
+  select(community, post)%>%
+  mutate(type = "touchscreen"),
+
+as_draws_df(bm_octs_rand)%>%
+  select(contains("ageinyears"))%>%
+  select(contains("ageinyears"))%>%
+  pivot_longer(cols = contains("ageinyears]"), names_to = "community", values_to = "value")%>%
+  mutate(post = value + b_ageinyears, 
+         community = str_remove(community, "r_community"),
+         community = str_remove(community, ",ageinyears]"),
+         community = str_remove(community, "\\["))%>%
+  select(community, post)%>%
+  mutate(type = "ageinyears")
+
+)%>%
+  ggplot(aes(x= post, y = community))+
+  geom_density_ridges(rel_min_height = 0.005, col = "black", alpha = .75, fill = NA)+
+  geom_vline(xintercept = 0, lty = 3)+
+  facet_grid(~type, scales = "free_x")+
+  #stat_pointinterval(size = 0.1)+
+  #xlim(-0.15, 0.1)+
+  theme_minimal()+
+  theme(panel.border = element_rect(colour = "black", fill=NA, size = .5))
+
 ```
@@
 ggsave("../visuals/old_child_site.png", width = 12, height = , bg = "white")
+```
+
+# Trial level analysis
+
+```{r}
+bm_trial_base <- brm(click ~ targetcentralityx + ageinyears + (targetcentralityx|subjid)+ (ageinyears + targetcentralityx |community),
+                              data   = mdata, 
+                              family = Gamma(link = "log"),
+                              warmup = 2000, 
+                              iter   = 6000, 
+                              chains = 4, 
+                              cores  = 4,
+                              threads = threading(8),
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")%>%
+  add_criterion(., c("waic","loo"))
+
+bm_trial_pred <- brm(click ~ targetcentralityx + ageinyears + touchscreen + older_children + (targetcentralityx|subjid)+ (ageinyears + touchscreen + older_children |community),
+                              data   = mdata, 
+                              family = Gamma(link = "log"),
+                              warmup = 2000, 
+                              iter   = 6000, 
+                              chains = 4, 
+                              cores  = 4,
+                              threads = threading(8),
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")%>%
+  add_criterion(., c("waic","loo"))
 ```

### 2024-01-15 analysis/gafo-cc-data-processing.Rmd
update supplement

@@
     ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
-    screen = ifelse(screen == "fallaci", 0, 1), 
-    touchscreen = ifelse(touchscreen == "fallaci", 0, 1),
+    #screen = ifelse(screen == "fallaci", 0, 1), 
+    #touchscreen = ifelse(touchscreen == "fallaci", 0, 1),
     household = as.numeric(household), 
@@
   mutate(age_group = substr(ageinyears, 1,1), 
-         trialnr = as.numeric(factor(trialnr)))
-
+         trialnr = as.numeric(factor(trialnr)), 
+         sex = ifelse(sex == "F", "f", sex),
+         sex = ifelse(sex == "female", "f", sex),
+         sex = ifelse(sex == "male", "m", sex),
+         sex = ifelse(sex == "NaN", NA, sex), 
+         screen = ifelse(touchscreen == 1, 1, screen),
+         household = ifelse(household == "NaN", NA, household),
+         children = ifelse(children == "NaN", NA, children),
+         younger_children = ifelse(younger_children == "NaN", NA, younger_children))
+
+```
+
+# Quality checks
+
+```{r}
+# data checks
+
+## communities
+unique(merge_raw_data$community)
+
+## age ranges
+range(merge_raw_data$ageinyears)
+
+## sex  
+unique(merge_raw_data$sex)
+
+## screen and touchscreen
+unique(merge_raw_data$screen)
+unique(merge_raw_data$touchscreen)
+# check NAs
+merge_raw_data%>%
+  filter(is.na(screen), trialnr == 1)
+
+merge_raw_data%>%
+  filter(is.na(touchscreen), trialnr == 1)
+
+### check if there are cases that say they don't have a screen but do say they have a touch screen 
+merge_raw_data%>%
+  filter(screen == 0 & touchscreen == 1, trialnr == 1)
+
+# household
+unique(merge_raw_data$household)
+
+merge_raw_data%>%
+  filter(is.na(household), trialnr == 1)
+
+# children 
+unique(merge_raw_data$children)
+## check number of children - should include the one being tested, therefore cannot be 0
+merge_raw_data%>%
+  filter(children == 0, trialnr == 1)
+
+## check if there are cases with more younger children than children (cannot be)
+
+merge_raw_data%>%
+  filter(children < younger_children, trialnr == 1)
+
+merge_raw_data%>%
+  filter(children == younger_children, trialnr == 1)
+
+```
+
+```{r}
 write_csv(merge_raw_data,"../data/gafo-cc-raw-data.csv")
-
+```
+
+```{r}
 data <- merge_raw_data%>%

### 2024-01-15 paper/supplement.Rmd
update supplement

---
title: "Unity in diversity: Children from 17 communities process gaze in similar ways"
subtitle: "Supplementary material"
author: "..."
output: 
  bookdown::pdf_document2:
    toc: yes 
    number_sections: false    
  bookdown::html_document2:
    toc: yes
    toc_float: true
    fig_caption: yes
    #code_folding: hide
    number_sections: false
bibliography: ../../../../References/library.bib
#csl: pnas.csl
header-includes:
  \usepackage{caption}
  \renewcommand{\figurename}{Supplementary Figure}
  \renewcommand{\tablename}{Supplementary Table}
---

```{r, echo=FALSE}
library(tidyverse)
library(ggpubr)
library(ggthemes)
library(tidyboot)
library(maps)
library(brms)
library(cowplot)
library(ggridges)

estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}

hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}

hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}

knitr::opts_chunk$set(echo=F, warning=FALSE, message=FALSE, size="small")

```

```{r}
data <- read_csv("../data/gafo-cc-clean-data.csv")%>%
  mutate(continent = ifelse(
    community %in% c("leipzig", "plymouth"), "Europe", 
    ifelse(
      community %in% c("akure", "hai||om", "khwe", "chimfunshi", "bandongo", "bayaka", "windhoek", "uganda"), "Africa",
      ifelse(community %in% c("stanford", "mexico", "buenos_aires"), "America",
             ifelse(community %in% c("india", "beijing", "turkey"), "Asia", "Oceania"))
    )
  ))%>%
  mutate(continent = factor(continent, levels = c("America", "Africa", "Europe", "Asia", "Oceania"), ordered = T))%>%
  mutate(community = recode(community,
                            akure = "Akure (Nigeria)",
                            leipzig = "Leipzig (Germany)",
                            `hai||om` = "Hai||om (Namibia)",
                            khwe = "Khwe (Namibia)",
                            windhoek = "Windhoek (Namibia)",
                            stanford = "Stanford (USA)",
                            chimfunshi = "Chimfunshi (Sambia)",
                            mexico = "Ocuilan (Mexico)",
                            plymouth = "Plymouth (UK)",
                            beijing = "Beijing (China)", 
                            india = "Pune (India)",
                            buenos_aires = "Buenos Aires (Argentina)",
                            auckland = "Auckland (New Zealand)",
                            turkey = "Malatya (Turkey)",
                            bandongo = "Bandongo (Rep. Congo)",
                            bayaka = "BaYaka (Rep. Congo)", 
                            uganda = "Nyabyeya (Uganda)"))
```

# Overview

in the section [site descriptions](#site-descriptions)

# Participants

```{r demtable, echo=F}
demtab <- data %>%
  separate(community, into = c("community", "country"), sep = " \\(")%>%
  mutate(country = str_remove(country, "\\("),
         country = str_remove(country, "\\)"))%>%
  distinct(subjid, .keep_all = T)%>%
  group_by(community, country, continent)%>%
  summarise(N = n_distinct(subjid), 
            m = sum(sex == "m", na.rm = T), 
            mean_age = mean(ageinyears),
            min_age = min(ageinyears), 
            max_age = max(ageinyears))%>%
  mutate_if(is.numeric, format, digits = 2, nsmall = 2)%>%
  mutate(age = paste(mean_age, " (", min_age, " - ", max_age, ")"))%>%
  select(-c(mean_age, min_age, max_age))%>%
  arrange(continent)

knitr::kable(demtab,
             col.names = c("Community", "Country", "Continent", "N", "Sex (male)", "Age (range)"),
             caption = "Participant demographics.", note = "Column age shows mean and range in paranthesis.", digits = 2, align = "l")
```

A total of `r sum(as.numeric(demtab$N))` children between `r round(min(data$ageinyears), 2)` and `r round(max(data$ageinyears), 2)` provided data for the study. Children lived in `r n_distinct(data$community)` different communities, located in `r n_distinct(data$country)` different countries. Table \@ref(tab:demtable) gives the sample size per community together with some basic demographic information. Additional children were recruited but did not contribute data to the study. The recruitment strategy varied from community to community and we therefore cannot provide detailed information about the number of children that were excluded. All children who contributed at least five valid data points were included in the final sample. We did not exclude any participants for performance reasons. A detailed description of each site and the way children were recruited can be found below.

```{r}
data%>%
  group_by(community,continent)%>%
  distinct(subjid, .keep_all = T)%>%
  mutate(dens = approxfun(density(ageinyears))(ageinyears))%>%
  ggplot(aes(y = community, x = ageinyears))+
  facet_grid(continent~., scales = "free", space = "free_y")+
  geom_density_ridges(col = "white")+
  #geom_point(alpha = .1)+
  theme_few()
```

## Site descriptions

### Chimfunshi (Sambia) - Location

### Hai||om (Namibia) - Ethnic group

### Khwe (Namibia) - Ethnic group

### Windhoek (Namibia) - Location

### Leipzig (Germany) - Location

### Akure (Nigeria) - Location

### Plymouth (UK) - Location

### Stanford (USA) - Location

### Ocuilan (Mexico) - Location

### Beijing (China) - Location

### Buenos Aires (Argentina) - Location

### Pune (India) - Location

### Auckland (New Zealand) - Location

### Malatya (Turkey) - Location

### Bandongo (Rep. Congo) - Ethnic group

### Bayaka (Rep. Congo) - Ethnic group

### Nyabyeya (Uganda) - Location

# Method

We adapted the task developed by Prein and colleagues [@prein2023tango]. We refer to the original publication for a detailed description of its development, implementation and psychometric evaluation (in Germany). Below give an overview and focus on the cross-cultural adaptation of the task. The task itself, including all the versions used in the study, can be accessed via the following website: https://ccp-odc.eva.mpg.de/tango-cc/

## Design

## Setup and Procedure

The task was implemented as a browser-based interactive picture book. Participants saw animated agents on a touch screen device, listened to pre-recorded audio instructions and responded by touching the screen. In all communities, a research assistant, fluent in the local language(s), guided the child through the task.

Figure X shows a screenshot from the task. The task was introduced verbally by the assistant as the balloon game in which the participant would play with other children to find a balloon. On each trial, participants saw an agent located in a window in the center of the screen. A balloon fell down from its starting position just below the agent. The agent's gaze followed the trajectory of the balloon. That is, the pupils and the iris were programmed to align with the center of the balloon. Once the balloon had landed on the ground, the agent was instructed to locate it, that is, to touch the location on the screen where they thought the balloon was. On each trial, we recorded the exact x-coordinate of the participant's touch.

There were two types of familiarization trials. In fam1 trials, the balloon fell down and landed in plain sight. Participants simply had to touch the visible balloon. In fam2 trials, the trajectory of the balloon was visible but it landed behind a small barrier (usually a hedge - see Figure XXB). Thus, participants needed to touch the hedge where they saw the balloon land. Next came test trials. Here, the barrier moved up and covered the balloons trajectory. That is, participants only saw the agents eyes move, but not the balloon. They had to infer the location of the balloon based on the agent's gaze direction. During fam1, fam2 and the first test trial, children heard voice overs commenting what happened on the screen. Critically, the agent was described as wanting to help the child and to always look at the balloon (see section [script](#appendix-script) for the English wording).

Children completed one fam1 trial, two fam2 trials and 16 test trials. We excluded the first test trial from the analysis because of the voice-over. Thus, 15 test trials were used in the analysis below.

Each child saw eight different agents, four male, four female. The agent changed from trial to trail, with alternating genders. A coin toss before the first trial decided whether the first agent was male or female. The order in which agents were shown was randomized with the constraint that all agents had to be shown once until an agent was shown again. The color of the balloon also changed from trial to trial in a random order, also with the constraint that all colors appeared once before any one was repeated.

The location (x-coordinate) where the balloon landed was determined in the following way: The screen was divided in ten equally sized bins. On each trial, one of the bins was randomly selected and the exact x-coordinate was randomly chosen within that bin. Constraints were that the balloon landed in each bin equally often and the same bin appeared no more than twice in a row.

All children were tested with a touch screen device with a size between 11 and 13 inch equipped with a webcam. The data was either stored locally or sent to a server. In addition to the behavioral data, we stored the webcam recording of the session for verification purposes.

## Culture-specific adaptations

The following components of the task were adapted to each cultural settings: voice-overs, agents, background. The voice overs were originally formulated in British English and German (see section [script](#script)). For each setting, they were first translated/adapted to the local language. In some cases (BaYaka and Bandongo) this was done by first translating them to French. The translations were done by native or near-native speakers. They were not exact translations of the original text but were adapted so that children from the respective community would understand them. For example, the word "hedge" in the British English version  was changed to "bush" for the Nigerian English version to adjust for how children in the respective community would refer to the thing they saw. The content of each utterance was comparable across languages.

The agents were drawn for each cultural setting in close collaboration with local researchers and/or research assistants. They were meant to show young adults and represent the diversity in appearance prevalent in the local population. See section [agents](#agents)) for all faces used in the study.

## Questionnaire

# Analysis

# Appendix

## Script

### Welcome (before the start of the task):

Hello! Great that you’re here. We’ll now play a balloon game. Can you see the children in the picture over there? We want to play together with the children using the balloon. We’ll now talk you through exactly what will happen.

### Fam 1

Look, a girl/boy is standing in the window. And can you see the balloon over there? The balloon always falls down and lands on the ground. And you have to find it! The girl/boy helps you and always looks at the balloon.

[balloon falls down]

Where is the balloon? Touch the balloon!

### Fam 2

Perfect, that was great! Now, we’ll continue playing. Can you see the girl/boy and the balloon again? The balloon will fall down again. This time, it will fall behind a hedge. And you have to find it! The girl/boy helps you and looks at the balloon.

[balloon falls down]

Where is the balloon? On the hedge, touch where the balloon is.

### Test

Nice, good job! Now, we’ll continue playing. There is the balloon, the girl/boy and the hedge. The hedge is growing a bit now.

The balloon is behind the hedge now. You can’t see it - but the girl/boy can! The balloon falls to the ground and you have to find it. Remember - the girl/boy always looks at the balloon!

### Goodbye

The children are super happy after playing. Thanks a lot for your help! See you soon and goodbye!

## Agents

Figure

\newpage

# References

### 2024-01-16 paper/supplement.Rmd
update supplement

@@
     number_sections: false
-bibliography: ../../../../References/library.bib
+bibliography: library.bib
 #csl: pnas.csl
@@
 
-```{r, echo=FALSE}
+```{r, echo=FALSE, message=F}
 library(tidyverse)
@@
 library(ggridges)
+library(papaja)
 
@@
              col.names = c("Community", "Country", "Continent", "N", "Sex (male)", "Age (range)"),
-             caption = "Participant demographics.", note = "Column age shows mean and range in paranthesis.", digits = 2, align = "l")
+             caption = "Participant demographics.", 
+             #ote = "Column age shows mean and range in paranthesis.", digits = 2, align = "l"
+             )
 ```
@@
 ```{r}
-data%>%
+page <- data%>%
   group_by(community,continent)%>%
@@
   facet_grid(continent~., scales = "free", space = "free_y")+
-  geom_density_ridges(col = "white")+
-  #geom_point(alpha = .1)+
-  theme_few()
+  geom_density_ridges(
+    jittered_points = TRUE,
+    position = position_points_jitter(width = 0, height = 0),
+    point_shape = '|',  point_alpha = 0.5, alpha = 0.7,
+  )+
+  labs(x = "Age (in years)", y= "")+
+  theme_few()+
+  theme(strip.background = element_blank(),strip.text.y = element_blank())
+
+pred_agg_i <- data%>%
+  mutate(older_children = children - 1 - younger_children)%>%
+  group_by(community, subjid)%>%
+  summarise(screen = mean(screen, na.rm = T),
+            touchscreen = mean(touchscreen, na.rm = T), 
+            older_children = mean(older_children, na.rm = T), 
+            household = mean(household, na.rm = T))
+
+pred_agg_g <- data%>%
+  mutate(older_children = children - 1 - younger_children)%>%
+  group_by(community, continent)%>%
+  summarise(screen = mean(screen, na.rm = T),
+            touchscreen = mean(touchscreen, na.rm = T), 
+            older_children = mean(older_children, na.rm = T), 
+            younger_children = mean(younger_children, na.rm = T), 
+            children = mean(children, na.rm = T), 
+            household = mean(household, na.rm = T))%>%
+  pivot_longer(names_to = "dem", values_to = "value", cols = c(screen, touchscreen, older_children,children, younger_children, household))
+
+ppred <- pred_agg_g%>%
+  filter(dem == "screen" | dem == "touchscreen")%>%
+  ggplot(aes(y = community, x = dem, fill = value))+
+  geom_point(pch = 22, size = 10, stroke = 0)+
+  facet_grid(continent~., scales = "free", space = "free_y")+
+  labs(x = "", y= "")+
+  scale_fill_viridis_c(name = "Prevalence")+
+  theme_few()+
+  scale_x_discrete(guide = guide_axis(n.dodge = 2))+
+  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), strip.text.y.right = element_text(angle = 0))
+```
+
+```{r figpred1, include = T, fig.align = "center", fig.cap = "Age distribution (left) and prevalence of different types of technology by community.
+Left: dots show individual data points.
+Right: color shows the proportion of children with access to screens or touchscreens."}
+techpred <- plot_grid(page, ppred, align = "h", rel_widths = c(1, 0.5))
+
+ggsave(plot = techpred, "../visuals/techpred.png", height = 10, width = 10, scale = 1)
+
+knitr::include_graphics("../visuals/techpred.png")
+
 ```
@@
 
+The descriptions below give detailed information about each data collection site, including the strategy used for recruiting children. The order is alphabetically.
+
+### Akure (Nigeria) - Location
+
+**References and further readings:**
+
+* ...
+
+### Auckland | Tāmaki Makaurau (New Zealand) - Location
+
+Auckland | Tāmaki Makaurau is the largest city of New Zealand | Aotearoa with a population of about 1.5 million people.
+The city is located on the North Island | Te Ika-a-Māui inbetween the Hauraki Gulf | Tīkapa Moana to the East and the Waitākere Ranges to the West.
+The climate is defined as either oceanic (Cfb) or subtropical (NIWA).
+Temperatures are mild throughout the year, with an average temperature of 23.7 during summer and 14.7 during winter months.
+
+The median age in the Auckland region was 34.7 years.
+181,194 Māori people with a median age of 24.9 years were counted in the 2018 census.
+Overall the population is composed of 53.5% European, 28.2% Asian, 15.5% Pacific Peoples, 11.5% Māori, 2.3% Middle Eastern / Latin American / African and 1.1% Other ethnicity.
+92.7% are English speakers, with 4.4% speaking Northern Chinese (Mandarin Chinese), 4.4% speaking Samoan and 2.4% speaking te reo Māori.
+
+Māori peoples arrived in Auckland | Tāmaki Makaurau around 1350 from other Pacific Islands.
+Before the arrival of European New Zealanders | Pākehā New Zealand was populated by about 20,000 Māori.
+Aotearoa was colonized by the Dutch and British Empires in the 18th Century.
+The effects the British Monarchy had on Aotearoa have been at the center of long lasting societal disputes.
+The Treaty of Waitangi | Te Tiriti o Waitangi is a document signed by 240 Māori chiefs and representatives of the British Crown in 1840 trying to establish a cooperative relationship while redeeming some of the mistakes that have been made.
+This document is still important for the revitalization of Māori culture throughout Aotearoa.
+
+51.9% of the people in Auckland are employed full time, with an unemployment rate of 4.1% and 30.4% not in the labor force (i.e.
+retirees).
+The main occupations are professionals (25.9%) and managers (18.1%) with only 5.9% operating machinery and 7.9% laborers.
+The people of Auckland are part of a service society with a median income of 34,400NZD and 19.8% of the population earning more than 70,000NZD.
+
+Auckland is made up of mainly sub-urban areas with single family housing.
+45.4% of the population own or partly own a house.
+People mostly live with their core family in loosely separated areas of the city.
+Those areas commonly have an economical center with shops and restaurants as well as a mix of private and public education institutions.
+The socialization goals and cultural norms are comparable to most western, democratic societies.
+High education standards are deemed as vital for success.
+Success is determined by career paths, income and general success in professional and private aspects of life.
+Sport plays a central role in most aspects of society.
+The role of sports is viewed as essential for living a healthy and successful life and as such is a central part in education programs.
+
+Education levels are generally good in Auckland.
+18.6% of the population hold a Bachelor's Degree.
+Interestingly about 9.1% move overseas for their secondary education.
+Parenting and childcare practises are comparable to other western cultures, with some adjustments being implemented in recent years to include more Māori cultural practises in education programs.
+Such as starting the day or specific activities | hui with Karakia, a form of incantation to ensure a favorable outcome to important events and undertakings.
+(see Literature for further information on early childhood education in New Zealand.)
+
+Aotearoa is an industrialized nation, nearly everybody has a smartphone and uses technology in their everyday life.
+Many administrative processes are very much digitized.
+There is no perceived mistrust towards technology and new developments are generally embraced with great interest.
+
+For this study we reached out to early childcare centers and schools.
+Two early childcare centers and one primary school agree to participate.
+Some additional children were tested during home visit sessions.
+All three educational institutions are visited by children from different cultural and socio-economic backgrounds.
+One early childcare center is affiliated with the University of Auckland and prioritizes children from University students and staff in their admission process.
+Testing sessions took place in separated spaces (office or break rooms) with one participant at a time.
+Participants received a certificate “for becoming a junior scientist” and a small gift (coloring book or sticker set) after their participation.
+(All numbers in the above description are from the 2018 census data report.)
+
+**References and further readings:**
+
+* Gunn, A.
+C., Child, C., Madden, B., Purdue, K., Surtees, N., Thurlow, B., & Todd, P.
+(2004).
+Building inclusive communities in early childhood education: Diverse perspectives from Aotearoa/New Zealand.
+Contemporary Issues in Early Childhood, 5(3), 293-308.
+* Shuker, M. J., & Cherrington, S. (2016). Diversity in New Zealand early childhood education: Challenges and opportunities. International Journal of Early Years Education, 24(2), 172-187.
+* Tesar, M. (2015). New Zealand perspectives on early childhood education: Nāku te rourou nāu te rourou ka ora ai te iwi. Journal of Pedagogy, 6(2), 9-18.
+* New Zealand Census 2018 for Auckland Region: https://www.stats.govt.nz/tools/2018-census-place-summaries/auckland-region#population-and-dwellings
+
+### Bandongo (Rep. Congo) - Ethnic group
+
+**References and further readings:**
+
+* ...
+
+### Bayaka (Rep. Congo) - Ethnic group
+
+**References and further readings:**
+
+* ...
+
+### Beijing (China) - Location
+
+Beijing, a municipality directly under the Central Government, is the capital of the People's Republic of China and the country's political, economic, cultural and transportation center as well as a famous historic city and a modern international city.
+Beijing covers an area of 16,410.54 square kilometers (sq.km) with a population of 21,843,000 in 2022.
+Beijing ranked second in Chinese cities in terms of GDP in 2022.
+Geographically, Beijing is located in the northern part of the North China Plain.
+
+Beijing is an inland city and is surrounded by mountains to its west, north and northeast.
+Mountain areas occupy about 62% of the municipality's total area.
+The land is characterized by urban and suburban areas, with parks, squares, and historical buildings located mostly in the downtown districts, and flat agricultural land and mountains in the suburban districts.
+Beijing has a temperate, continental monsoonal climate, characterized by short spring and autumns, hot and rainy summers, and cold and dry winters.
+Its average annual temperature is 11 to 14oC.
+The coldest month in Beijing is January, with an average temperature of -9 to -4oC; the hottest month is July, with an average of 25oC.
+Around 75 percent of its annual precipitation occurs in summer, with the heaviest rainfall in July and August.
+
+According to the 2021 National Census data, in Beijing, there were 20845166 (95%) Han Chinese along with 1047929 (4.8%) people in other minority nationalities (e.g., Manchu, Hui ethnic, Mongolian ethnic).
+Mandarin Chinese is commonly spoken by all ethnic groups though many of the minority nationalities also have their own national languages, such as Mongolian language used by Mongolian ethnic.
+(4)
+
+Beijing is one of the birthplaces of Chinese Civilization and one of the five ancient capital cities in China.
+With but few interruptions, Beijing has been the capital of China for some eight centuries: including the capital of the State of Yan during the Western Zhou Dynasty (11th Century-771BC), the capital of Jin Dynasty (1153-1215), the capital of Yuan Dynasty (1271-1368), the capital of Ming Dynasty (1421-1644), and the capital of Qing Dynasty (1644-1912).
+In 1949, Beiping (former name of Beijing) was renamed Beijing and became the capital of the People’s Republic of China.
+Since then, it gradually develops into a modern metropolis.
+
+From the early 1950s to the reform and opening up, Beijing aimed to build a modernized industrial base, and the secondary industry became the dominant industry in economic development.
+In 1954, the proportion of the secondary industry was 44.1%, exceeding the tertiary industry for the first time, and in 1978, the proportion reached 71%.
+Since the 1980s, Beijing has vigorously developed the tertiary industry, and the proportion of the tertiary industry once again exceeded that of the secondary industry in 1994, and the proportion of the tertiary industry exceeded 60% in 1998, 70% in 2005, and 80% in 2016, reaching 84% in 2022, making it the city's economic "leader".
+According to the statistical communiqué on the National Economy and Social Development of Beijing in 2022 the top three sectors in terms of absolute volume of GDP are finance (19.7%), information transmission, software and information technology services (17.9%) and industry (12.1%).
+
+Beijing has various types of residential areas, ranging from traditional courtyard houses (siheyuan) in hutongs (narrow alleyways) to modern apartment buildings, gated residential complexes and detached houses.
+Household composition varies, ranging from single individuals and couples to families with children and multi-generational households.
+Notably, it is a strong tradition for grandparents to be involved in grandchildren care and household tasks.
+In big cities, such as Beijing, the involvement of grandparents in grandchild care is especially helpful since it relieves the high-pressure of a two-career family.
+BTW, China fully implemented the “two-child-per-family” policy in 2016, there are usually one or two children per family now in Beijing.
+
+Parental socialization goals in Beijing (as well as in other cities) align with broader Chinese Confucianism cultural norms and typically emphasize the following seven developmental goals for children: Gaining knowledge, internalizing social norms, being modest about success and ashamed of failure, displaying self-restraint and filial piety, and maintaining harmonious relationships with others.
+Education and learning are seen as very important aspects of children’s lives.
+For primary school children in Beijing, parents (also the education system) especially emphasize on academic achievement.
+Moreover, with China’s growing exposure to western values, autonomy has been promoted by current educationalists during the last decade, and is especially emphasized in developed cities such as Beijing.
+As to parental education levels, according to the data of 2020 population census, the average years of schooling for permanent population in Beijing aged 15 and above is 12.64 years, and among whom 48% have university degree (15 years of education and above).
+So, the percentage for the parents holding a university degree should be much higher than 48%.
+
+It’s common that parents spend large parts of the day away from home and children are cared for externally.
+Between 2 and 3 years of age young children can attend nurseries (very few nurseries accept children as young as 1.5-year-old).
+Nurseries are largely commercialized and non-subsidized.
+Starting at age 3, children can attend either publicly subsidized kindergarten or private kindergarten.
+Children move on to primary school at six.
+Public primary education is free and compulsory.
+There are also private primary schools that cater to other groups, such as international primary schools that serve families catering to the expatriate community and families seeking an international education, as well as those who want to get prepared for studying abroad later.
+The samples of the current study were drawn from public kindergarten and public primary school.
+
+Children growing up in Beijing have a high exposure to technology.
+Smartphones and other touchscreen devices are prevalent in most families in Beijing and are used widely for education, communication, and entertainment.
+In 2022, almost every Chinese netizen accessed the internet via mobile devices and Beijing has been fully covered by ultrafast 5G signals.
+
+95% of the sampled Children were recruited from local public kindergarten and primary school.
+We firstly introduced the experiment to the heads of the kindergarten/school.
+Once getting their permission, we asked the teachers to help send the printed letter (information about the study, informed consent, as well as the five questions) to the parents.
+And a Mandarin speaking research assistant then tested kids whose parents signed the informed consent in a separate room in the kindergarten/school.
+A few of the youngest kids (5% of total) were recruited by directly introducing the experiment to the parents who we personally knew and tested the kids either in a separate room at our institute or at their home.
+
+**References and further readings:**
+
+* https://english.beijing.gov.cn/beijinginfo/index.html
+* https://www.chinadiscovery.com/beijing-tours/maps/beijing-districts-map.html
+* https://www.britannica.com/place/Beijing/Landscape; http://english.igsnrr.cas.cn/eocg/moc/200704/t20070409_8626.html
+* http://us.mofcom.gov.cn/article/aboutchina/202011/20201103012649.shtml
+* http://tjj.beijing.gov.cn/EnglishSite/
+* Binah-Pollak, A. (2014). Discourses and practices of child-rearing in China: The bio-power of parenting in Beijing. China Information, 28(1), 27-45. doi:10.1177/0920203x13517617
+* Chen, F., & Liu, G. (2011). The Health Implications of Grandparents Caring for Grandchildren in China. The Journals of Gerontology: Series B, 67B(1), 99-112. doi:10.1093/geronb/gbr132
+* Chen, F., Short, S.
+E., & Entwisle, B.
+(2000).
+The impact of grandparental proximity on maternal childcare in China.
+Population Research and Policy Review, 19(6), 571-590.
+doi:10.1023/A:1010618302144
+* Luo, R., Tamis-LeMonda, C.
+S., & Song, L.
+(2013).
+Chinese parents’ goals and practices in early childhood.
+Early Childhood Research Quarterly, 28(4), 843-857.
+doi:https://doi.org/10.1016/j.ecresq.2013.08.001
+* Nyland, B., Zeng, X., Nyland, C., & Tran, L. (2009). grandparents as educators and carers in China. Journal of Early Childhood Research, 7(1), 46-57. doi:10.1177/1476718x08098353
+* Xu, H.
+(2019).
+Physical and mental health of Chinese grandparents caring for grandchildren and great-grandparents.
+Social Science & Medicine, 229, 106-116.
+doi:https://doi.org/10.1016/j.socscimed.2018.05.047
+* Zhu, N., Chang, L.
+(2019).
+Education and Parenting in China.
+In: Sorbring, E., Lansford, J.
+(eds) School Systems, Parent Behavior, and Academic Achievement.
+Young People and Learning Processes in School and Everyday Life, vol 3.
+Springer, Cham.
+https://doi.org/10.1007/978-3-030-28277-6_2
+
+### Buenos Aires (Argentina) - Location
+
+**References and further readings:**
+
+* ...
+
 ### Chimfunshi (Sambia) - Location
+
+Chimfunshi wildlife orphanage is an NGO providing a home for about 150 chimpanzees.
+The sanctuary is located in the Copperbelt region in the northern part of Zambia close to DRC border.
+The chimpanzees are housed in eight different enclosures; each of an area up to 121.5Ha.
+The Sanctuary provides housing, medical care and education for the employees and their families which are in total about 300 people living in 5 different compounds around Chimfunshi.
+
+Chimfunshi itself was founded in 1983 by David and Sheila Siddle who lived in Zambia since the 1950’s.
+In the past years they rehabilitated chimpanzees who were confiscated from poachers and from obsolete zoos and circuses worldwide.
+Today the sanctuary is managed by a Board of Trustees to ensure the long-term sustainability.
+
+Throughout the year Zambia has a mainly humid subtropical climate with a dry winter.
+There are three seasons.
+The rather cool dry season which lasts from May to August.
+A short hot dry season which is followed by a hot and humid rainy season from Novmeber to April.
+Overall, the temperatures are relatively mild due to the altitude of the country in the north but can be cold in winter.
+The sanctuary is nestled by woodland, savanna and situated near the Kafue river.
+
+The country has about 18 Million inhabitants.
+The population consists mostly of Bantu-speaking groups whereby Bemba is the largest ethnicity and the most spoken language beside Chewa, Tonga and Lozi.
+English which is the country's official language, is only spoken by about 2% of the population as a first language.
+For people with high education levels English is the most commonly used second language.
+Complex patterns of migrations created a broad linguistic and cultural variety.
+Due to the big mining industry, the population in the Copperbelt area consists of people from all parts of Zambia and even from neighboring countries.
+
+Zambia is mainly a Christian country (Protestant, Romanic Catholic, Jehovah’s Witnesses and some fundamentalists churches) but due to the Asian community, Hindus and Muslim are represented as well.
+The northeast and northwest part of Zambia is still strongly influenced by cultural traditions of the Congo basin.
+Zambian people still value traditional norms within their families, villages and clans.
+Such norms, ideals and morals are for example  mutual respect and reciprocity.
+
+The main sectors of the economy in Zambia is agriculture and copper mining and smelting especially in the northern Copperbelt region.
+Despite these large copper deposits, Zambia is one of the poorest countries in the world.
+Three quarters of the poor live in rural areas.
+As in other African countries there is a strong trend of movement from rural arears to urban centers whereby men migrate more often and women remain behind in villages.
+The housing style in rural areas vary a lot by ethnic group.
+Overall, mud and thatch, brick, or other materials are used for construction.
+
+People working at Chimfunshi wildlife orphanage are living in compounds.
+These are little settlements made of stone houses with corrugated iron roofs, a well to access clean water, solar systems for electricity and often little gardens to grow crops and/or keeping farm animals (e.g.
+chickens).
+
+Since independence day Zambia invested a lot in education.
+By now schooling is compulsory for 7- to 14-year-olds.
+Primary school lasts for 7 years and the secondary level for 5 years.
+The Twampane School at Chimfunshi was founded in 2011 to give the children of Chimfunshi employees the opportunity to attend school upto grade 9th.
+Almost 120 of the students live in the Chimfunshi area, the others come from the surrounding farms and settlements, thus the schools provides education for about 220 students.
+Children who perform well at school are enabled due to sponsorship programs to attend a secondary school.
+Furthermore, Chimfunshi offers children in the final grades on-site vocational training and further education.
+(9)
+Depending on the financial possibilities of the families, electrical devices with touch screens such as smartphones or laptops are available.
+Many still use cellphones and do not own a smartphone, which also makes access to such electronic devices more difficult for some children or even households.
+
+Before a study can be conducted in Chimfunshi, it must be presented to the Scientific Advisory Board of Chimfunshi.
+The board members and the sanctuary directress deliberate and decide whether a study can be carried out or not.
+Once these formalities have been clarified, the parents are approached with the help of an on-site assistant.
+The study program is explained to each family which are interested to participate in one way or the other in a study.
+Participation is recorded in writing and can be revoked by the parents at any time.
+Depending on the study, recruitment takes place in cooperation with the school teachers.
+(11)
+
+**References and further readings:**
+
+* https://chimfunshiwildlife.org/
+* https://www.britannica.com/place/Zambia/Education
+* https://legendsandlegaciesofafrica.org/sheilasiddle.php
 
@@
 
+**References and further readings:**
+
+* ...
+
 ### Khwe (Namibia) - Ethnic group
+
+**References and further readings:**
+
+* ...
+
+### Leipzig (Germany) - Location
+
+Leipzig is a medium-sized city located in the east of Germany with a population of approximately 620,000.
+It serves as a significant urban center within the state of Saxony.
+Geographically, leipzig is situated in the southernmost part of the North German Plain.
+
+The city landscape is characterized by urban and suburban areas, with parks, squares, and historical buildings.
+Leipzig has an oceanic climate with continental influence.
+Winters are cold (average temperature around 1°C) and summers warm (average temperature around 19°C).
+
+The majority of inhabitants of Leipzig are German, many of which have moved from other parts of Germany.
+Around 17% of the population have a migration background.
+The largest groups of migrants come from Syria, Ukraine, and the Russian Federation.
+In comparison to more rural areas in the region, Leipzig has a larger proportion of inhabitants with a migration background and is generally seen as more liberal and progressive.
+German is the primary language spoken in Leipzig.
+Additionally, due to its role as a major educational and cultural center, English and other foreign languages are also spoken by a significant portion of the population.
+
+Historically, Leipzig gained prominence as a trade city during the Middle Ages and later became a major center of the Enlightenment and the arts in the 18th and 19th centuries.
+Following World War II, Leipzig was part of the socialist German Democratic Republic.
+Leipzig played a crucial role in the Peaceful Revolution of 1989, which ultimately led to the fall of the Berlin Wall and the reunification of Germany.
+
+Leipzig has been a market economy for centuries.
+It has a modern and diversified economy that encompasses various sectors, such as manufacturing, services, and creative industries.
+The city is known for its trade fairs, music, and publishing industries.
+
+The city has a combination of apartment buildings, detached houses, and residential complexes.
+Household composition varies, ranging from single individuals and couples to families with children and multi-generational households.
+Children mostly live in nuclear families with one or two children and their caregivers.
+
+Parental socialization goals in Leipzig align with broader German cultural norms and typically emphasize the importance of children’s independence, psychological autonomy, self-confidence and assertiveness.
+Education and learning are seen as important aspects of children’s lives.
+Parental education levels are generally very high; adults have at least nine years of formal schooling and high school and university degrees are very widespread.
+
+Parents spend large parts of the day away from home, and the majority of children are cared for externally: starting at nine months of age, children can attend nurseries, moving on to kindergarten at three and primary school around six.
+Institutional childcare is provided by the city and financially subsidized; institutionalized primary education is free and compulsory.
+
+Children growing up in Leipzig have a high exposure to technology.
+Smartphones and other touchscreen devices are prevalent in most families and educational institutions, reflecting the widespread use of digital technology for communication, entertainment, and information retrieval.
+
+Children were recruited via a database of children whose parents expressed interest in participating in studies of child development.
+They were tested in a separate room in their kindergartens by a German-speaking research assistant.
+
+**References and further readings:**
+
+* City website for demographic information: https://english.leipzig.de
+* Otto, H., & Keller, H. (2016). Is there something like German parenting. Contemporary Parenting: a Global Perspective, 81-94.
+
+### Malatya (Turkey) - Location
+
+Malatya is a big city located in the Eastern Anatolia region of Turkey with a population of approximately 800,000.
+Due to its strong economy based on agriculture, it is one of the biggest cities in eastern Turkey.
+
+The city landscape is characterized by mostly urban and some rural areas.
+Malatya has a temperate continental climate with very cold winters (average temperature around -3°C) and very hot summers (average temperature around 33°C).
+
+The population of Malatya is diverse which include inhabitants with Turkish, Kurdish, Circassian, Armenian, and Zaza origins.
+Malatya is also a multilingual city.
+Although the dominant language is Turkish, around 40% of the population speaks Kurdish.
+
+Malatya has a long history since the Hittite times. It has also been significant location for the Roman Empire, Byzantine Empire, and Ottoman Empire.
+
+Malatya’s economy depends on agriculture, and it is famous for apricot production. Recently, Malatya has also undergone some industrial development such as textile manufacturing.
+
+The urban area of Malatya consists of apartment buildings.
+Household composition usually involves families with children and multi-generational households.
+Children live both in nuclear families (with parents and siblings) and in extended families (nuclear family and a set of grandparents).
+Parental socialization in Malatya aligns with broader Turkish cultural norms, and typically emphasize the importance of children’s interdependence, value of family.
+Education and learning are seen as important aspects of children’s lives.
+Parental education levels are generally above the average of Turkey; with most adults have high school or university degrees.
+
+Fathers spend large parts of the day away from home, and the majority of children are cared at home by their mothers and grandparents until they start formal schooling at the age 7.
+Primary education is free and compulsory.
+
+Children growing up in Malatya have some exposure to technology.
+Smartphones and other touchscreen devices are somewhat prevalent in most families, reflecting the widespread use of digital technology for communication.
+
+Children were recruited through nurseries and schools who expressed interest in participating research.
+They were tested in a separate room in their nurseries/school kindergartens by a Turkish-speaking research assistant.
+Some children were also tested in parks and outdoor areas.
+
+### Nyabyeya (Uganda) - Location
+
+Nyabyeya Forestry College is situated in the Masindi district of western Uganda, approximately 25 km from Masindi Town and 240 km from Kampala, the capital city.
+The college is adjacent to Budongo Tropical High Forest and 8 km from Budongo conservation field station, where primatologists study wild-ranging chimpanzees.
+The college draws its sample from the surrounding villages, including Marram, Kyempunu, Nyabigoma, Nyabyeya 1 and 2 and Trading Center, Nyakafunjo, and Kyamasuka.
+
+Nyabyeya is located on a green, gently sloping area behind Nyabyeya Hill and is characterized by tropical vegetation and a savanna climate, characterized by daytime temperatures reaching 32°C/90°F and cooler nights at 17°C/63°F.
+The region observes two distinct agricultural seasons - a wet season from late March to June and August to November, followed by a dry season from early December to March.
+
+The studied villages are culturally very diverse and house ethnic groups such as Bantu, Luo, Nilotics, and Nilo-Hamites.
+Spoken languages depend on the tribe and include Alur, Lugbara, Runyoro, lendu, kakwa, Acholi, Langi, Luganda, Logo, Kebu, madi, and many others.
+Kiswahili and English often serve as a common ground.
+For this study, children who understand Kiswahili were invited.
+
+During the Second World War, many Polish refugees were brought to Uganda and located in Bunyoro on the fringes of Budongo Forest at Nyabyeya.
+When the refugees were evacuated after World War II ended, the forestry college was transferred into the facilities the Polish refugees had left behind.
+It now serves as an educational institute conducting training in Forestry, Agroforestry, Biomass Energy Technologies, and beekeeping.
+
+The community predominantly practices subsistence farming, cultivating crops like maize, cassava, sweet potatoes, and beans.
+Wealthier families sometimes keep goats, pigs, chickens, or ducks.
+Additionally, sugarcane and coffee cultivation contribute significantly to the local economy, with the Kinyara Sugar Company playing a pivotal role in sugarcane harvesting.
+Living conditions in the community are characterized by extended families residing together, with an average of 10 people under one roof.
+While temporary round mud huts are common, permanent houses are found in the trading center of Nyabyeya.
+Most people in the community live by hand to mouth, and parents (especially women) work hard to provide the basics for their household members.
+
+Parental socialization goals vary, with limited guidance for children in some instances, leading to very independent lives at a young age.
+Cultural practices include the belief in producing many children as a sign of respect, with specific tribes attaching wealth to the number of daughters.
+Twins are highly honored, and rituals are performed to welcome them.
+Often, young children take care of their siblings and carry them around on their backs.
+Children start working early, for example, by helping their parents with farming or cow herding.
+Often, families cannot afford school materials for their children and struggle to provide regular food.
+Early marriages and teenage pregnancies often result in girls leaving school earlier.
+
+Parental education levels are generally low, with many parents above 50 having only primary education.
+The education system faces challenges such as inadequate school supplies, leading to high dropout rates.
+Children start primary school at ages 5-7, and secondary education runs for four years, with options to pursue advanced levels.
+
+The community exhibits low exposure to technology, with smartphones and touchscreen devices considered luxuries.
+Limited internet usage and power supply challenges contribute to this low adoption.
+However, technology is more prevalent in institutions like Nyabyeya Forestry College.
+Participating families were recruited by the local research assistants, for example, via personal contact, visiting them at home, or calling them.
+Families were invited to the Nyabyeya Forestry College (transport offered via boda boda (motorcycle)), and children participated in a quiet room in the College.
+
+**References and further readings:**
+
+* Budongo Conservation Field Station: http://www.budongo.org/
+* Holden, E., Buryn-Weitzel, J.
+C., Atim, S., Biroch, H., Donnellan, E., Graham, K.
+E., Hoffman, M., Jurua, M., Knapper, C.
+V., Lahiff, N.
+J., Marshall, S., Paricia, J., Tusiime, F., Wilke, C., Majid, A., & Slocombe, K.
+E.
+(2022).
+Maternal attitudes and behaviours differentially shape infant early life experience: A cross cultural study.
+PLOS ONE, 17(12), e0278378.
+https://doi.org/10.1371/journal.pone.0278378
+
+### Ocuilan (Mexico) - Location
+
+Ocuilan is a municipality located in the centre south of Mexico with a population of 36,223 inhabitants, distributed in 48 towns in an area of 344.84 km2  inside the Mexican State.
+(Ocuilan, n.d.) Geographically Ocuilan has an altitude of between 1000 to 2,600 m situated 80 km south of Mexico City.
+(INEGI,2010)
+
+The communities in Ocuilan are distributed on a mountain range called Trans-Mexican volcanic Belt surrounded by valleys and mountains, the climate is semi-humid with summer rains, and average temperatures vary between 8C and 22C throughout the year.
+The higher elevations have mixed pine forests with more tropical vegetation in the lowlands.
+The distribution of the land is 31.91% agriculture, 0.48% urban zone and the rest forest.
+(INEGI,2010)
+
+Historically, the municipality of Ocuilan was occupied by three different towns: Tlahuicas, Mazahuas, and Ocuiltecos.
+Besides being in the same territory, they had their own language, religion, and customs until the arrival of the Mexica people.
+Within 100 years, the Mexica dominated the area.
+The territory was under Mexican control until the arrival of the Spanish kingdom, which took advantage of the discontent of the towns dominated under the Aztec Empire.
+The Spanish kingdom allied itself with those towns and waged war on the Aztec Empire, succeeding in taking the Mexica capital on 13 August 1521.
+Although there was some resistance, all the towns within what is now the State of Mexico fell to the Spaniards shortly thereafter.
+(Edo Mex, 2018)
+
+During the period of Spanish control, the municipality of  Ocuilan was primarily characterized by agricultural activities.
+The presence of missionary friars played an important role in the dissemination of catholic religion and the Spanish language.
+(Edo Mex, 2018)  Over the course of the conquest, the Spanish language gradually gained prominence, but it is still possible to find indigenous languages like Tlahuica, Nahualt and Mazahua among the inhabitants.
+(Ocuilan, n.d.)
+
+Following the attainment of Mexican independence, Ocuilan continued to be a farming area and also emerged as an important religious centre, attracting pilgrims from various regions of Mexico.
+During the Mexican Revolution, the locality assumed significance as a stronghold of the Zapatistas which played an essential role in the enactment of the Political Constitution of 1917.
+In the subsequent decades, political stability, economic development, and population growth in the State of Mexico.
+(Edo Mex, 2018)   Nowadays, livestock farming and trout rearing stand as the dominant economic pursuits in Ocuilan.
+(Ocuilan, n.d.)
+
+Demographically, the average household in Ocuilan comprises 4.1 inhabitants, (Ocuilan, n.d.)  primarily adhering to a nuclear family structure characterized by an authoritative rearing model.
+Parents assume a proactive role in establishing parental control, emphasizing the enforcement of rules and disciplinary measures (Delfín-Ruiz et al., 2021).
+The parent's education level generally extends to the middle school level, while the prevailing family values involve the mother's engagement in domestic responsibilities and the father's participation in occupational pursuits.
+
+Regarding education, children in Ocuilan typically start their day by attending kindergarten between 8 am to 12 pm.
+Afterwards, mothers or other family members take care of the children as formal childcare options are limited.
+Consequently, children typically begin their early schooling experience at around 3 years of age.
+
+In terms of technology, approximately  77.9% of households possess at least one screen device, whereas access to the Internet is available to only  22.7% of households.
+Consequently, while a significant proportion of children have experienced digital technology a considerable segment lacks exposure and accessibility to such resources.
+(Ocuilan, n.d.)
+
+For the study, we first obtained permission from Mexican school authorities to visit local kindergartens.
+Next, we contacted parents and invited them to take part in the research.
+The evaluation of interested children was then carried out in a separate area within their own kindergartens, overseen by a Spanish-speaking research assistant.
+
+**References and further readings:**
+
+* Compendio de información geográfica municipal 2010.
+Instituto Nacional de Estadística, Geografía e Informática INEGI (2010).
+Retrieved 3 August  2023, from https://en.www.inegi.org.mx/app/biblioteca/ficha.html?upc=702825293031
+* Delfín-Ruiz, C., Orozco, C. S., & Guzmán, R. C. (2021). Caracterización de los roles familiares y su impacto en las familias de México. Revista de Ciencias Sociales, 27.
+* Ocuilan: Economy, employment, equity, quality of life, education, health and public safety. (n.d.). Data México. Retrieved 13 May 2023, from https://datamexico.org/en/profile/geo/ocuilan
+* Historia del Estado de Mexico. (2018) Gobierno del Estado de México Edo Mex (2018).  Retrieved 13 May 2023  from  https://edomex.gob.mx/historia_edomex
+
+### Plymouth (UK) - Location
+
+**References and further readings:**
+
+* ...
+
+### Pune (India) - Location
+
+**References and further readings:**
+
+* ...
+
+### Stanford (USA) - Location
+
+The sample was drawn from a children’s museum in San Jose, California located in the western United States of America.
+San Jose is a large city with a population of approximately 983,000 people and geographically is within the Santa Clara Valley in the southern part of the Bay Area, California.
+
+The city is a large metropolitan area with urban and suburban areas bordered by mountain ranges to the east and west.
+The land is characterized by bay flats and hills with several rivers running through the city.
+San Jose’s climate is described as mild, semi-arid, and mediterranean.
+A wet season typically occurs between November and March with combined rainfall and an average daytime temperature of 50 degrees Fahrenheit.
+A dry season occurs between March and November where precipitation is minimal and the average daytime temperature is 70 degrees Fahrenheit.
+
+According to the most recent census data, the 3 largest groups by Race are Asian (Non-Hispanic) (37%), White (Non-hispanic) (25%) and Hispanic (31%).
+40% of residents immigrated to the United States, with most residents originating from Mexico, Philippines, and China.
+Although English is the primary language used, more than half (58%) of people also speak a language other than English at home, including Spanish (20%), Chinese (7%), Tagalog (3%), Vietnamese (2%), and other Asian & Pacific Islander languages (19%).
+
+San Jose was originally home to the Tamien people of the Ohlone from around 4000 BC.
+Around 1777 the Tamien people were displaced and enslaved, and San Jose became the first town in the Spanish colony Nueva California.
+San Jose would eventually become the first incorporated city and state capital when California became a state in the United States of America following the Mexican-American War.
+
+San Jose historically is a large farming community with a major industry in food processing and agriculture.
+The Valley was especially known for its tree nuts, berries, and orchard fruits.
+The city soon became a hub for the manufacturing of electric machinery and motor vehicles, and would eventually become the modern technological hub that it is today.
+San Jose is presently centered in “Silicon Valley”, a global center for technological innovation and entrepreneurs.
+
+The city has a combination of apartment buildings, detached houses, and residential complexes.
+Household composition varies, ranging from single individuals and couples to families with children and multi-generational households.
+Children mostly live in nuclear families with one or two children and their caregivers.
+
+Parental socialization goals in California typically emphasize tolerance, individualism, diversity, personal fulfillment, and holistic autonomy, but vary greatly as a result of its diverse populus.
+Education and learning are seen as important aspects of children’s lives.
+Parental education levels are generally very high; many adults have a graduate degree, and most adults have at least 12 years of formal schooling and a 4-year college degree.
+
+It is common for parents to spend large parts of the day away from home, and typically rely on external care including family, nannies, and daycare for childcare.
+Daycares are largely commercialized and non-subsidized.
+Starting around age 2, children can begin attending preschool.
+At age 5, children can enter kindergarten in publicly subsidized schools and move on to primary school at age 6.
+While public primary education is typically free and compulsory, around 15% of children in San Jose are enrolled in private, non-subsidized institutions for primary school.
+
+Children in San Jose have high exposure to technology.
+Nearly all households in San Jose have a computer (97%), with 93% of households having a broadband internet subscription.
+Smartphones and other touchscreen devices are used in most families and are used widely for education, communication, and entertainment.
+
+Children were recruited in person at a children’s museum in San Jose.
+Participants were randomly solicited from patrons visiting the children’s museum.
+Parents were given information about the study activity and consented before beginning the study.
+Children completed the study in a separate research room centrally located in the museum.
+
+**References and further readings:**
+
+* Miller, Miguel (1999).
+Climate of San Jose, NOAA Technical Memorandum, retrieved 22 September 2023 from: https://www.wrh.noaa.gov/mtr/sfd_sjc_climate/sjc/SJC_CLIMATE3.php#:~:text=San%20Jose%20%3Ds%20latitude%20and,total%20falls%20within%20this%20period.
+* Quick Facts: San Jose City, California (2022). United States Census Bureau, retrieved 22 September 2023 from: https://www.census.gov/quickfacts/fact/table/sanjosecitycalifornia/PST045222
+* San Jose, California Population 2023 (2023). World Population Review, retrieved 22 September 2023 from: https://worldpopulationreview.com/us-cities/san-jose-ca-population
+* San Jose Demographics and Diversity (2023). San Jose, retrieved 22 September 2023 from: https://www.sanjose.org/meetings/quick-guides/san-jose-demographics-and-diversity
+* Wilcox, W. D., Wang, W. (2020). State of Contradiction: Progressive Family Culture, Traditional Family Structure in California, Institute for Family Studies, retrieved 22 September 2023 from:
+https://ifstudies.org/blog/state-of-contradiction-progressive-family-culture-traditional-family-structure-in-california
 
@@
 
-### Leipzig (Germany) - Location
+**References and further readings:**
 
-### Akure (Nigeria) - Location
+* ...
 
-### Plymouth (UK) - Location
+```{r figpred2, include = T, fig.align = "center", fig.cap = "Household demographics by community.
+Vertical lines show individual data points with minimal horizontal jitter to avoid overplotting.", out.width="100%"}
 
-### Stanford (USA) - Location
+dempred <- data%>%
+  group_by(community,continent)%>%
+  mutate(older_children = children - 1 - younger_children)%>%
+  distinct(subjid, .keep_all = T)%>%
+  select(subjid, community, continent, older_children,children, younger_children, household)%>%
+  pivot_longer(names_to = "dem", values_to = "value", cols = c(older_children,children, younger_children, household))%>%
+  mutate(dem = recode(dem,
+                      older_children = "older children",
+                            younger_children = "younger children"),
+         dem = factor(dem, levels = c("household", "children", "older children", "younger children")))%>%
+  ggplot(aes(y = community, x = value))+
+  facet_grid(continent~dem, scales = "free", space = "free_y")+
+  geom_density_ridges(
+    jittered_points = TRUE,
+    position = position_points_jitter(width = 0.25, height = 0),
+    point_shape = '|',  point_alpha = 1, alpha = 0.7,
+  )+
+ # geom_density_ridges(
+ #    col = "white",
+ #    jittered_points = TRUE, quantile_lines = TRUE, scale = 0.9, alpha = 0.7,
+ #    vline_size = 1, vline_color = "red",
+ #    point_size = 0.4, point_alpha = 1,
+ #    position = position_raincloud(adjust_vlines = TRUE)
+ #  )
+  labs(x = "No. of individuals", y= "")+
+  #geom_jitter(alpha = .1, width = 0.1, height = 0.1)+
+  theme_few()
 
-### Ocuilan (Mexico) - Location
+ggsave(plot = dempred, "../visuals/dempred.png", height = 8, width = 14, scale = 1.1)
 
-### Beijing (China) - Location
-
-### Buenos Aires (Argentina) - Location
-
-### Pune (India) - Location
-
-### Auckland (New Zealand) - Location
-
-### Malatya (Turkey) - Location
-
-### Bandongo (Rep. Congo) - Ethnic group
-
-### Bayaka (Rep. Congo) - Ethnic group
-
-### Nyabyeya (Uganda) - Location
+knitr::include_graphics("../visuals/dempred.png")
+```
 
@@
 
-## Design
-
 ## Setup and Procedure
 
-The task was implemented as a browser-based interactive picture book.
+The task was implemented as a browser-based interactive picture book using `HTML` and `JavaScript`.
 Participants saw animated agents on a touch screen device, listened to pre-recorded audio instructions and responded by touching the screen.
@@
 
-Figure X shows a screenshot from the task.
+Figure \@ref(fig:task) shows a screenshot from the task.
 The task was introduced verbally by the assistant as the balloon game in which the participant would play with other children to find a balloon.
@@
 On each trial, we recorded the exact x-coordinate of the participant's touch.
+
+```{r figagents, include = T, fig.align = "center", fig.cap = "Screenshot from the task.
+The scene depicts the choice phase in a test trial.
+Participants had to use the gaze of the agent to locate the balloon and click on the hedge where they thought the balloon was.", out.width="80%"}
+knitr::include_graphics("../visuals/task.png")
+```
 
@@
 They were meant to show young adults and represent the diversity in appearance prevalent in the local population.
-See section [agents](#agents)) for all faces used in the study.
+Figure \@ref(fig:figagents) shows the agents that were used in the study.
+Some agents were used in multiple cultural settings.
+All agents had the same underlying eye-geometry (size of the pupil and the iris) and only differed in superficial features.
+
+```{r figagents, include = T, fig.align = "center", fig.cap = "Agents used in the task. Some agents were used for multiple cultural settings", out.width="100%"}
+knitr::include_graphics("../visuals/agents.png")
+```
 
 ## Questionnaire
+
+The parents of children who participated in the task were asked to fill out a short questionnaire with the following questions (English version):
+
+* Is there a device with a screen in your household? (answer: "yes" or "no")
+* Does your child have experience with touchscreens? (answer: "yes" or "no")
+* How many people live in your household (people residing and sleeping in one place e.g., a house)? (answer: number)
+* How many children live in your household? (answer: number)
+* How many children in your household are younger than the child participating in the study? (answer: number)
+
+The questions were translated to parents native language by a native speaker.
+In The number of older children living in the same household was computed by subtracting one (the child taking the test) and the number of younger children from the total number of children.
+Whenever parents were not able to read or write (most relevant for Chimfunshi, BaYaka, Bandongo, Khwe, Ha||om), research assistants asked the question and recorded the answer.
 
@@
 
-## Script
+## Voice-over script
 
-### Welcome (before the start of the task):
+### Welcome (before the start of the task)
 
@@
 
-### Goodbye
+### Goodbye (after the last test trial)
 
 The children are super happy after playing. Thanks a lot for your help! See you soon and goodbye!
-
-## Agents
-
-Figure
 

### 2024-01-19 analysis/gafo-cc-analysis.Rmd
prep model run in cluster

@@
 ```{r}
+exclude <- read_csv("../data/gafo-cc-clean-data.csv")%>%
+  filter(children == younger_children, trialnr == 1)%>%
+  pull(subjid)
+
 mdata <- read_csv("../data/gafo-cc-clean-data.csv")%>%
   ungroup()%>%
+  filter(!subjid %in% exclude)%>%
   mutate(older_children = children - 1 - younger_children)%>%
@@
 
-fixef(bm_octs_rand)
+fixef(bm_octs_fix)
 ```
@@
 bm_trial_base <- brm(click ~ targetcentralityx + ageinyears + (targetcentralityx|subjid)+ (ageinyears + targetcentralityx |community),
+                              data   = mdata%>%na.omit(), 
+                              family = Gamma(link = "log"),
+                              warmup = 2000, 
+                              iter   = 6000, 
+                              chains = 4, 
+                              cores  = 4,
+                              threads = threading(8),
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")%>%
+  add_criterion(., c("waic","loo"))
+
+saveRDS(bm_trial_base, "../saves/bm_trial_base.rds")
+
+bm_trial_pred <- brm(click ~ targetcentralityx + ageinyears + touchscreen + older_children + (targetcentralityx|subjid)+ (ageinyears + touchscreen + older_children + targetcentralityx |community),
                               data   = mdata, 
@@
 
-bm_trial_pred <- brm(click ~ targetcentralityx + ageinyears + touchscreen + older_children + (targetcentralityx|subjid)+ (ageinyears + touchscreen + older_children |community),
-                              data   = mdata, 
-                              family = Gamma(link = "log"),
-                              warmup = 2000, 
-                              iter   = 6000, 
-                              chains = 4, 
-                              cores  = 4,
-                              threads = threading(8),
-             control = list(adapt_delta = 0.95),
-             backend = "cmdstanr")%>%
-  add_criterion(., c("waic","loo"))
+saveRDS(bm_trial_pred, "../saves/bm_trial_pred.rds")
+
+loo_compare(bm_trial_base,
+            bm_trial_pred
+            )%>%as_tibble(rownames = "model")
+
+fixef(bm_trial_pred)
+```
+
+```{r}
+draws <- bind_rows(
+as_draws_df(bm_trial_pred)%>%
+  select(contains("children"))%>%
+  select(contains("children"))%>%
+  select(-contains("sd"))%>%
+  select(-contains("cor"))%>%
+  pivot_longer(cols = contains("children]"), names_to = "community", values_to = "value")%>%
+  mutate(post = value + b_older_children, 
+         community = str_remove(community, "r_community"),
+         community = str_remove(community, ",older_children]"),
+         community = str_remove(community, "\\["))%>%
+  select(community, post)%>%
+  mutate(type = "older_children"),
+
+as_draws_df(bm_trial_pred)%>%
+  select(contains("touchscreen"))%>%
+  select(contains("touchscreen"))%>%
+  select(-contains("sd"))%>%
+  select(-contains("cor"))%>%
+  pivot_longer(cols = contains("touchscreen1]"), names_to = "community", values_to = "value")%>%
+  mutate(post = value + b_touchscreen1, 
+         community = str_remove(community, "r_community"),
+         community = str_remove(community, ",touchscreen1]"),
+         community = str_remove(community, "\\["))%>%
+  select(community, post)%>%
+  mutate(type = "touchscreen"),
+
+as_draws_df(bm_trial_pred)%>%
+  select(contains("ageinyears"))%>%
+  select(contains("ageinyears"))%>%
+  select(-contains("sd"))%>%
+  select(-contains("cor"))%>%
+  pivot_longer(cols = contains("ageinyears]"), names_to = "community", values_to = "value")%>%
+  mutate(post = value + b_ageinyears, 
+         community = str_remove(community, "r_community"),
+         community = str_remove(community, ",ageinyears]"),
+         community = str_remove(community, "\\["))%>%
+  select(community, post)%>%
+  mutate(type = "ageinyears"),
+
+as_draws_df(bm_trial_pred)%>%
+  select(contains("targetcentralityx"))%>%
+  select(contains("targetcentralityx"))%>%
+  select(-contains("sd"))%>%
+  select(-contains("cor"))%>%
+  select(-contains("subjid"))%>%
+  pivot_longer(cols = contains("targetcentralityx]"), names_to = "community", values_to = "value")%>%
+  mutate(post = value + b_targetcentralityx, 
+         community = str_remove(community, "r_community"),
+         community = str_remove(community, ",targetcentralityx]"),
+         community = str_remove(community, "\\["))%>%
+  select(community, post)%>%
+  mutate(type = "targetcentrality")
+
+)
+
+pdraws <- draws%>%
+  mutate(continent = ifelse(
+    community %in% c("leipzig", "plymouth"), "Europe", 
+    ifelse(
+      community %in% c("akure", "hai||om", "khwe", "chimfunshi", "bandongo", "bayaka", "windhoek", "uganda"), "Africa",
+      ifelse(community %in% c("stanford", "mexico", "buenos_aires"), "America",
+             ifelse(community %in% c("india", "beijing", "turkey"), "Asia", "Oceania"))
+    )
+  ))%>%
+  mutate(continent = factor(continent, levels = c("America", "Africa", "Europe", "Asia", "Oceania"), ordered = T))%>%
+  mutate(community = recode(community,
+                            akure = "Akure (Nigeria)",
+                            leipzig = "Leipzig (Germany)",
+                            `hai||om` = "Hai||om (Namibia)",
+                            khwe = "Khwe (Namibia)",
+                            windhoek = "Windhoek (Namibia)",
+                            stanford = "Stanford (USA)",
+                            chimfunshi = "Chimfunshi (Sambia)",
+                            mexico = "Ocuilan (Mexico)",
+                            plymouth = "Plymouth (UK)",
+                            beijing = "Beijing (China)", 
+                            india = "Pune (India)",
+                            buenos_aires = "Buenos Aires (Argentina)",
+                            auckland = "Auckland (New Zealand)",
+                            turkey = "Malatya (Turkey)",
+                            bandongo = "Bandongo (Rep. Congo)",
+                            bayaka = "Bayaka (Rep. Congo)", 
+                            uganda = "Nyabyeya (Uganda)"))
+
+saveRDS(pdraws, "../saves/pdraws.rds")
+
+pdraws <- readRDS("../saves/pdraws.rds")
+
+ggplot(pdraws, aes(x= post, y = community))+
+  #geom_density_ridges(rel_min_height = 0.005, col = "black", alpha = .75, fill = NA)+
+  geom_density_ridges(rel_min_height = 0.005, col = "white", alpha = .75, fill = "grey")+
+  geom_vline(xintercept = 0, lty = 3)+
+  facet_grid(continent~type, scales = "free", space = "free_y")+
+  #stat_pointinterval(size = 0.1)+
+  #xlim(-0.15, 0.1)+
+  theme_minimal()+
+  theme(panel.border = element_rect(colour = "black", fill=NA, size = .5))
+
 ```
@@
 
-bm_base <- brm(click ~ targetcentralityx + ageinyears + (trialnr + targetcentralityx|subjid),
+bm_null <- brm(click ~ targetcentralityx + (trialnr + targetcentralityx|subjid),
                               data   = mdata, 
@@
 
-bm_cult_x_age <- brm(click ~ targetcentralityx + ageinyears + (trialnr + targetcentralityx|subjid)+ (ageinyears |community),
+bm_cult_x_age <- brm(click ~ targetcentralityx + ageinyears + (trialnr + targetcentralityx|subjid)+ (ageinyears + targetcentralityx |community),
                               data   = mdata, 

### 2024-01-19 analysis/gafo-cc-analysis.Rmd
prep merge

@@
                               data   = mdata%>%na.omit(), 
-                              family = Gamma(link = "log"),
+                              family = lognormal(),
                               warmup = 2000, 
@@
                               data   = mdata, 
-                              family = Gamma(link = "log"),
+                              family = lognormal(),
                               warmup = 2000, 
@@
   mutate(community = recode(community,
-                            akure = "Akure (Nigeria)",
-                            leipzig = "Leipzig (Germany)",
-                            `hai||om` = "Hai||om (Namibia)",
-                            khwe = "Khwe (Namibia)",
-                            windhoek = "Windhoek (Namibia)",
-                            stanford = "Stanford (USA)",
-                            chimfunshi = "Chimfunshi (Sambia)",
-                            mexico = "Ocuilan (Mexico)",
-                            plymouth = "Plymouth (UK)",
-                            beijing = "Beijing (China)", 
-                            india = "Pune (India)",
-                            buenos_aires = "Buenos Aires (Argentina)",
-                            auckland = "Auckland (New Zealand)",
-                            turkey = "Malatya (Turkey)",
-                            bandongo = "Bandongo (Rep. Congo)",
-                            bayaka = "Bayaka (Rep. Congo)", 
-                            uganda = "Nyabyeya (Uganda)"))
+                            akure = "akure (nigeria)",
+                            leipzig = "leipzig (germany)",
+                            `hai||om` = "hai||om (namibia)",
+                            khwe = "khwe (namibia)",
+                            windhoek = "windhoek (namibia)",
+                            stanford = "stanford (usa)",
+                            chimfunshi = "chimfunshi (sambia)",
+                            mexico = "ocuilan (mexico)",
+                            plymouth = "plymouth (uk)",
+                            beijing = "beijing (china)", 
+                            india = "pune (india)",
+                            buenos_aires = "buenos aires (argentina)",
+                            auckland = "auckland (new zealand)",
+                            turkey = "malatya (turkey)",
+                            bandongo = "bandongo (rep. congo)",
+                            bayaka = "bayaka (rep. congo)", 
+                            uganda = "nyabyeya (uganda)"))
 
@@
 
-bm_null <- brm(click ~ targetcentralityx + (trialnr + targetcentralityx|subjid),
+bm_null <- brm(click ~ targetcentralityx + (targetcentralityx|subjid),
                               data   = mdata, 
-                              family = Gamma(link = "log"),
+                              family = lognormal(),
                               warmup = 2000, 
@@
 
-bm_cult <- brm(click ~ targetcentralityx + ageinyears + (trialnr + targetcentralityx|subjid)+ (1 |community),
+bm_age <- brm(click ~ targetcentralityx + ageinyears + (targetcentralityx|subjid),
                               data   = mdata, 
-                              family = Gamma(link = "log"),
+                              family = lognormal(),
                               warmup = 2000, 
@@
 
-bm_cult_x_age <- brm(click ~ targetcentralityx + ageinyears + (trialnr + targetcentralityx|subjid)+ (ageinyears + targetcentralityx |community),
+bm_cult <- brm(click ~ targetcentralityx + (targetcentralityx|subjid)+ (targetcentralityx |community),
                               data   = mdata, 
-                              family = Gamma(link = "log"),
+                              family = lognormal(),
                               warmup = 2000, 
@@
 
-```
-
-```{r}
-six_fold_cross_validation <- function(data, m1, m2, m3, repeats) {
+bm_cult_age <- brm(click ~ targetcentralityx + ageinyears + (targetcentralityx|subjid)+ (ageinyears + targetcentralityx |community),
+                              data   = mdata, 
+                              family = lognormal(),
+                              warmup = 2000, 
+                              iter   = 6000, 
+                              chains = 4, 
+                              cores  = 4,
+                              threads = threading(8),
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")
+```
+
+```{r}
+six_fold_cross_validation <- function(data, m1, m2, m3, m4, repeats) {
 
@@
 #Prepare results DF
-  results <- tibble(m1_score=numeric(), m2_score=numeric() , m3_score=numeric(), m3_beats_m2=logical(), m3_beats_m1=logical(), m2_beats_m1=logical(), m1 = character(), m2 = character(), m3 = character())
+  results <- tibble(
+    m1_score=numeric(), 
+    m2_score=numeric() , 
+    m3_score=numeric(),
+    m4_score=numeric(),
+
+    m4_beats_m3=logical(),
+    m4_beats_m2=logical(),
+    m4_beats_m1=logical(),
+
+    m3_beats_m2=logical(),
+    m3_beats_m1=logical(),
+
+    m2_beats_m1=logical(),
+
+    m1 = character(), 
+    m2 = character(),
+    m3 = character(),
+    m4 = character())
 
@@
   # Split dataset into 6 bins
-  bin_data <- data%>%group_by(community) %>% mutate(bin = rep(1:6, length.out = n()))
+  bin_data <- data%>%group_by(community)%>%distinct(subjid) %>% mutate(bin = rep(1:6, length.out = n()))
 
@@
     # Train models
-    up_m1 <- update(m1, newdata=training_data, cores=4,backend = "cmdstanr")
-    up_m2 <- update(m2, newdata=training_data, cores=4,backend = "cmdstanr")
-    up_m3 <- update(m3, newdata=training_data, cores=4,backend = "cmdstanr")
+    up_m1 <- update(m1, newdata=training_data, cores=4, threads = threading(8),backend = "cmdstanr")
+    up_m2 <- update(m2, newdata=training_data, cores=4, threads = threading(8),backend = "cmdstanr")
+    up_m3 <- update(m3, newdata=training_data, cores=4, threads = threading(8),backend = "cmdstanr")
+    up_m4 <- update(m4, newdata=training_data, cores=4, threads = threading(8),backend = "cmdstanr")
 
@@
     preds_m3 <- posterior_predict(up_m3, newdata=testing_data, allow_new_levels=TRUE, sample_new_levels="gaussian")
+    preds_m4 <- posterior_predict(up_m4, newdata=testing_data, allow_new_levels=TRUE, sample_new_levels="gaussian")
 
     # Evaluate predictive accuracy
-  score_m1 <- mean(sqrt(colMeans((testing_data$mean_click - t(preds_m1))**2)))
-  score_m2 <- mean(sqrt(colMeans((testing_data$mean_click - t(preds_m2))**2)))
-  score_m3 <- mean(sqrt(colMeans((testing_data$mean_click - t(preds_m3))**2)))
+  score_m1 <- mean(sqrt(colMeans((testing_data$click - t(preds_m1))**2)))
+  score_m2 <- mean(sqrt(colMeans((testing_data$click - t(preds_m2))**2)))
+  score_m3 <- mean(sqrt(colMeans((testing_data$click - t(preds_m3))**2)))
+  score_m4 <- mean(sqrt(colMeans((testing_data$click - t(preds_m4))**2)))
 
@@
   m3_name <-  as.character(substitute(m3))
+  m4_name <-  as.character(substitute(m4))
 
     # Record results
-    results <- add_row(results,
+    results <- add_row(repeats = i,
+                       fold = j, 
+                       results,
                        m1_score = score_m1, 
@@
                        m3_score = score_m3,
+                       m4_score = score_m4,
+
+                       m4_beats_m3 = m4_score < m3_score,
+                       m4_beats_m2 = m4_score < m2_score,
+                       m4_beats_m1 = m4_score < m1_score,
+
                        m3_beats_m2 = m3_score < m2_score,
@@
                        m2_beats_m1 = m2_score < m1_score,
+
                        m1  = m1_name, 
                        m2 = m2_name, 
-                       m3 = m3_name)
+                       m3 = m3_name,
+                       m4 = m4_name)
  }
@@
 ```{r}
-cv_cult <- six_fold_cross_validation(scdata, bm_base, bm_cult, bm_cult_x_age, 2)
-```
-
-## Test for
+cv_cult <- six_fold_cross_validation(mdata, bm_null, bm_cult, bm_age, bm_cult_age, bm_cult_x_age, 2)
+```
+
+```{r}
+mean(cv_cult$m4_beats_m1)
+```

### 2024-01-19 analysis/gafo-cc-analysis.Rmd

@@
   mutate(community = recode(community,
-                            akure = "akure (nigeria)",
-                            leipzig = "leipzig (germany)",
-                            `hai||om` = "hai||om (namibia)",
-                            khwe = "khwe (namibia)",
-                            windhoek = "windhoek (namibia)",
-                            stanford = "stanford (usa)",
-                            chimfunshi = "chimfunshi (sambia)",
-                            mexico = "ocuilan (mexico)",
-                            plymouth = "plymouth (uk)",
-                            beijing = "beijing (china)", 
-                            india = "pune (india)",
-                            buenos_aires = "buenos aires (argentina)",
-                            auckland = "auckland (new zealand)",
-                            turkey = "malatya (turkey)",
-                            bandongo = "bandongo (rep. congo)",
-                            bayaka = "bayaka (rep. congo)", 
-                            uganda = "nyabyeya (uganda)"))
+                            akure = "Akure (Nigeria)",
+                            leipzig = "Leipzig (Germany)",
+                            `hai||om` = "Hai||om (Namibia)",
+                            khwe = "Khwe (Namibia)",
+                            windhoek = "Windhoek (Namibia)",
+                            stanford = "Stanford (USA)",
+                            chimfunshi = "Chimfunshi (Sambia)",
+                            mexico = "Ocuilan (Mexico)",
+                            plymouth = "Plymouth (UK)",
+                            beijing = "Beijing (China)", 
+                            india = "Pune (India)",
+                            buenos_aires = "Buenos Aires (Argentina)",
+                            auckland = "Auckland (New Zealand)",
+                            turkey = "Malatya (Turkey)",
+                            bandongo = "Bandongo (Rep. Congo)",
+                            bayaka = "Bayaka (Rep. Congo)", 
+                            uganda = "Nyabyeya (Uganda)"))
 

### 2024-01-23 paper/paper.tex
prep merge

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\centering\begin{threeparttable}}
%   {\end{threeparttable}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

\makeatletter
\usepackage{etoolbox}
\patchcmd{\maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{keywords\newline\indent Word count: X}
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Unity in diversity: Children from 17 communities process gaze in similar ways},
  pdfauthor={Manuel Bohn1,2, Julia Prein1,2, \ldots\ldots, \& Daniel B. M. Haun2},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Unity in diversity: Children from 17 communities process gaze in similar ways}
\author{Manuel Bohn\textsuperscript{1,2}, Julia Prein\textsuperscript{1,2}, \ldots{}\textsuperscript{\ldots{}}, \& Daniel B. M. Haun\textsuperscript{2}}
\date{}

\shorttitle{Gaze-following across 17 communities}

\authornote{

Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

Enter author note here.

The authors made the following contributions. Manuel Bohn: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Julia Prein: Conceptualization, Methodology, Writing - Review \& Editing; \ldots{}: Conceptualization, Methodology, Writing - Review \& Editing; Daniel B. M. Haun: Conceptualization, Writing - Review \& Editing.

Correspondence concerning this article should be addressed to Manuel Bohn, Postal address. E-mail: \href{mailto:my@email.com}{\nolinkurl{my@email.com}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute of Psychology in Education, Leuphana University Lüneburg\\\textsuperscript{2} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology}

\abstract{%
Understanding gaze is critical for human social interaction. In a comprehensive cross-cultural study spanning five continents and 17 distinct cultural contexts, we examined the development of gaze understanding among preschoolers using a single reliable task tailored to each cultural setting. Our data provides evidence that children worldwide process gaze in the same way. Key performance signatures of a computational model that sees gaze following as a form of social vector estimation were found in all communities. Additionally, we found a subtle yet cross-culturally consistent relationship between children's environments and their ability to understand gaze. These results highlight the cross-cultural robustness of core social cognitive skills, as well as similarities in the developmental process, suggesting that fundamental aspects of social cognition and interaction emerge and develop in comparable ways globally and hence are a bedrock of human social cognition.
}

\begin{document}
\maketitle

Social cognition is a defining aspect of the human species (\emph{1}--\emph{3}). It is supposed to enable unique forms of communication and cooperation that underlie cumulative cultural evolution and the formation of complex societies (\emph{4}--\emph{6}). The eyes are the proverbial window to the mind and the starting point for a majority of social reasoning processes (\emph{7}). Gaze is used to infer the focus of visual attention, which is a critical aspect of coordinated activities, including communication and cooperation (\emph{8}, \emph{9}). The ability to follow gaze emerges early in childhood (\emph{10}--\emph{12}) and individual differences in children's gaze following ability predict later life outcomes, most notably, later communicative abilities (\emph{13}, \emph{14}). Underlying this narrative is the wide-held assumption that gaze following is fundamental to human social cognition and, therefore, works and develops in the same way across human societies despite substantial variation in developmental contexts. This claim, however, lacks a solid empirical foundation.

We conducted a large-scale cross-cultural study on the development of gaze-following abilities to study potentially universal processing signatures and their development. Previous developmental studies focused on the onset of gaze following in infancy (\emph{15}, \emph{16}). The XXXX participants (age ) in the study lived in 17 different communities spread over five continents. The countries from which data was contributed to the study represented 46\% of the world's population. Communities covered a broad spectrum of geographical locations, social and political systems, languages, and subsistence styles (Fig. \ref{fig:fig1}).

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{../visuals/fig1}

}

\caption{(B) Screenshot from the task. The scene depicts the choice phase in a test trial. Participants had to use the gaze of the agent to locate the balloon and click on the hedge where they thought the balloon was. Agents, audio recordings and backgrounds were adpated to each cultural setting.}\label{fig:fig1}
\end{figure}

\begin{table}

\caption{\label{tab:tab1}Participant demographics.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lllllll}
\toprule
Continent & Country & Community & N(male) & Age (range) & Language & Touchscreen\\
\midrule
America & Argentina & Buenos Aires & 105 (53) & 4.72 (3.00 - 6.96) & Spanish (Rioplatense) & 0.90\\
 & Mexico & Ocuilan & 125 (61) & 4.97 (2.57 - 6.95) & Spanish (Mexican) & 0.77\\
 & USA & Stanford & 100 (56) & 5.00 (2.52 - 7.90) & English (American) & 0.98\\
Africa & Namibia & Hai||om & 60 (38) & 5.85 (2.74 - 8.34) & Hai||om & 0.05\\
 &  & Khwe & 59 (24) & 5.84 (3.38 - 8.63) & Khwedam & 0.19\\
\addlinespace
 &  & Windhoek & 41 (18) & 5.68 (2.66 - 8.66) & English (Nigerian) & 0.95\\
 & Nigeria & Akure & 114 (53) & 5.07 (2.57 - 7.33) & English (Nigerian) & 0.91\\
 & Rep. Congo & BaYaka & 28 (12) & 7.86 (3.94 - 10.56) & BaYaka & 1.00\\
 &  & Bandongo & 30 (11) & 7.45 (3.50 - 10.95) & Lingala & 1.00\\
 & Sambia & Chimfunshi & 22 (5) & 5.98 (2.88 - 8.00) & Bemba & 0.14\\
\addlinespace
 & Uganda & Nyabyeya & 51 (27) & 5.41 (3.27 - 8.21) & Swahili & 0.49\\
Europe & Germany & Leipzig & 100 (48) & 4.88 (2.53 - 6.95) & German & 0.89\\
 & UK & Plymouth & 70 (30) & 6.02 (2.38 - 8.94) & English (British) & 0.99\\
Asia & China & Beijing & 123 (62) & 5.47 (2.69 - 8.48) & Mandarin & 0.95\\
 & India & Pune & 155 (75) & 6.14 (3.06 - 8.83) & English (Indian) / Marathi & 0.92\\
\addlinespace
 & Turkey & Malatya & 85 (40) & 5.02 (2.75 - 7.12) & Turkish & 1.00\\
Oceania & New Zealand & Auckland & 43 (19) & 5.14 (2.81 - 8.75) & English (New Zealand) & 0.95\\
\bottomrule
\end{tabular}}
\end{table}

We used an animated picture book tablet task in which participants were asked to locate a hidden object based on observing an agent's gaze. Children watched a balloon disappear behind a hedge. An agent followed the trajectory of the balloon with their eyes. The key dependent variable was the precision with which children located the agent's focus of attention, that is, the deviation between where the agent looked (where the object was) and where the child thought the agent looked. We adapted visuals and audio instructions specifically to each of the 17 communities (Fig. 1). Previous work demonstrated excellent individual-level measurement properties for this task (\emph{17}). Thus, in addition to group-level trends, we were able to investigate individual-level variation.

As the first step, we investigated developmental gains. Across all 17 communities, we found a substantial increase in average levels of precision with age (range: \(\beta_{min}\) = , 95\% CrI () to \(\beta_{max}\) = ()). There were marked differences between communities: urban communities around the globe showed higher levels of precision compared to rural communities. We return to this result below. However, differences between communities were small compared to differences between individuals: communities did not form homogeneous clusters but largely overlapping distributions in that some individuals from communities with a lower average level of precision (e.g.~) performed better compared to some individuals from a setting with a very high average level of precision. Furthermore, in all communities, some 4-year-olds outperformed children two years older than them.

Consistent developmental gains alone cannot inform us about the cognitive processes children use when locating the agent's focus of attention. Recent computational work modeled gaze following as social vector estimation (\emph{18}). When observing the eyes, onlookers estimate a vector from the center of the eye through the pupil. The focus of attention is the location wherever the estimated vectors from both eyes hit a surface (Fig. XX). The estimation process is not perfect, but each individual has a systematic level of uncertainty, which is conceptualized as the cause of individual differences. Importantly, this process model predicts a clear performance signature in our cross-cultural gaze following task: Trials in which the agent looks further away from the center (i.e.~to the left or right side of the screen) should result in lower levels of precision, compared to trials in which the agent looks closer to the middle. This prediction is best understood by considering a similar phenomenon: pointing a torch light to a flat surface. The width of the light beam represents each individual's level of uncertainty in vector estimation. When the torch is directed straight down, the light beam is concentrated in a relatively small area. When the torch is rotated to the side, the light from one half of the cone must travel further than the light from the other half to reach the surface. As a consequence, the light is spread over a wider area.

The processing signature was clearly visible across all 17 communities. Precision decreased when the agent looked at locations further away from the center (fixed effect: \(\beta\) = (), community-level effects: Fig. 2). Visualization of the data showed the predicted u-shaped pattern in all communities. These results indicate a universal cognitive process used by children in all communities. There is, however, an alternative way in which the u = shaped pattern might arise: it would also arise when participants ignored the agent's gaze and instead always selected the middle of the screen (center bias). To rule out this alternative explanation, we directly compared three cognitive models that made different assumptions about how participants' responses were generated: the focal vector-based gaze estimation model described above, a center-bias model where participants always select the center, and a random guessing model where participants select random locations. For every community, we found overwhelming support for the gaze estimation model (min \(BF_{10}\) \textless{} 1000 for comparisons with both alternative models). Taken together, children from all 17 communities processed gaze in similar ways.

What is left to explain are the marked community- and individual-level differences. In addition to the gaze-following task, caregivers filled out a small questionnaire about children's access to screen-based technology and the composition of their households. On an individual level, we found that across communities, children with access to touchscreen devices had higher levels of precision (fixed effect: \(\beta\) = (), community-level effects: Fig. 2). On a community level, we also saw that average performance was lowest in the communities in which touchscreen devices were the least frequent (Fig. 3). Thus, methodological factors likely explained the marked differences between communities.

On an individual level, other factors likely generated individual differences because there was substantial variation even in communities where almost all children had access to touchscreens. Previous work suggested that social cognition develops in social interaction (\emph{19}--\emph{21}), in particular, with older siblings (\emph{22}, \emph{23}). We found tentative support for this idea in the form of a small but consistent effect in the direction that participants living together with more children older than themselves had slightly higher levels of precision (fixed effect: \(\beta\) = (), community-level effects: Fig. 2).

Following and understanding gaze is a foundational building block of human social cognition (\emph{8}, \emph{9}). A substantial body of work has explored the developmental onset of gaze following in a few selected cultural settings (\emph{10}--\emph{12}, \emph{15}, \emph{16}). The data reported here provides evidence that children all over the world process gaze in the same way. Key performance signatures of a model that sees gaze following as a form of social vector estimation were found in the data of all 17 distinct cultural communities. The cognitive processes underlying gaze following are thus likely to be rooted in humans' evolved cognitive architecture, which is -- presumably -- later refined during social interaction. The phylogenetic roots of these processes might possibly lie much deeper as primates from a wide range of species follow gaze (\emph{24}--\emph{26}). Yet, if they also show the same processing signatures has yet to be explored.

There are important limitations to this study. The methodological factors that influenced performance might have overshadowed individual and community-level differences that originate from other sources. Importantly, this does not affect our interpretation of the data as evidence for shared cognitive processing because the key processing signatures were present in all communities. The role that social interaction plays as a potential driver of development and source of individual differences is vastly under-explored in the current study. The small effect of the exposure to older children does not indicate which aspects of social interaction enhance gaze processing. Naturalistic data directly recording social interactions across communities would offer crucial information to close this explanatory gap. Recent work in the field of language acquisition has shown how technological innovations can be used to close this explanatory gap.

The evidence presented here holds far-reaching implications. Our work pioneers a methodological approach that introduces solid individual-level measurement to the cross-cultural study of cognitive development. As such, it serves as a blueprint for future research on a broad spectrum of cognitive abilities. Most importantly, this study offers a much-needed empirical foundation for theories on human nature. The finding that children from diverse cultures deploy similar cognitive processes in interpreting gaze points to an evolutionary basis of basic social cognition, which is refined during development, presumably through social interaction.

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\leavevmode\vadjust pre{\hypertarget{ref-tomasello2005understanding}{}}%
\CSLLeftMargin{1. }%
\CSLRightInline{M. Tomasello, M. Carpenter, J. Call, T. Behne, H. Moll, Understanding and sharing intentions: The origins of cultural cognition. \emph{Behavioral and Brain Sciences} \textbf{28}, 675--691 (2005).}

\leavevmode\vadjust pre{\hypertarget{ref-laland2021understanding}{}}%
\CSLLeftMargin{2. }%
\CSLRightInline{K. Laland, A. Seed, Understanding human cognitive uniqueness. \emph{Annual Review of Psychology} \textbf{72}, 689--716 (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-wellman2014making}{}}%
\CSLLeftMargin{3. }%
\CSLRightInline{H. M. Wellman, \emph{Making Minds: How Theory of Mind Develops} (Oxford University Press, 2014).}

\leavevmode\vadjust pre{\hypertarget{ref-henrich2016secret}{}}%
\CSLLeftMargin{4. }%
\CSLRightInline{J. Henrich, \emph{The Secret of Our Success: How Culture Is Driving Human Evolution, Domesticating Our Species, and Making Us Smarter} (princeton University press, 2016).}

\leavevmode\vadjust pre{\hypertarget{ref-tomasello2003makes}{}}%
\CSLLeftMargin{5. }%
\CSLRightInline{M. Tomasello, H. Rakoczy, What makes human cognition unique? From individual to shared to collective intentionality. \emph{Mind \& language} \textbf{18}, 121--147 (2003).}

\leavevmode\vadjust pre{\hypertarget{ref-legare2019development}{}}%
\CSLLeftMargin{6. }%
\CSLRightInline{C. H. Legare, The development of cumulative cultural learning. \emph{Annual Review of Developmental Psychology} \textbf{1}, 119--147 (2019).}

\leavevmode\vadjust pre{\hypertarget{ref-shepherd2010following}{}}%
\CSLLeftMargin{7. }%
\CSLRightInline{S. V. Shepherd, Following gaze: Gaze-following behavior as a window into social cognition. \emph{Frontiers in integrative neuroscience} \textbf{4}, 5 (2010).}

\leavevmode\vadjust pre{\hypertarget{ref-tomasello2007reliance}{}}%
\CSLLeftMargin{8. }%
\CSLRightInline{M. Tomasello, B. Hare, H. Lehmann, J. Call, Reliance on head versus eyes in the gaze following of great apes and human infants: The cooperative eye hypothesis. \emph{Journal of human evolution} \textbf{52}, 314--320 (2007).}

\leavevmode\vadjust pre{\hypertarget{ref-scaife1975capacity}{}}%
\CSLLeftMargin{9. }%
\CSLRightInline{M. Scaife, J. S. Bruner, The capacity for joint visual attention in the infant. \emph{Nature} \textbf{253}, 265--266 (1975).}

\leavevmode\vadjust pre{\hypertarget{ref-tang2023slow}{}}%
\CSLLeftMargin{10. }%
\CSLRightInline{Y. Tang, M. R. Gonzalez, G. O. Deák, The slow emergence of gaze-and point-following: A longitudinal study of infants from 4 to 12 months. \emph{Developmental Science}, e13457 (2023).}

\leavevmode\vadjust pre{\hypertarget{ref-gredeback2010development}{}}%
\CSLLeftMargin{11. }%
\CSLRightInline{G. Gredebäck, L. Fikke, A. Melinder, The development of joint visual attention: A longitudinal study of gaze following during interactions with mothers and strangers. \emph{Developmental science} \textbf{13}, 839--848 (2010).}

\leavevmode\vadjust pre{\hypertarget{ref-byers2021development}{}}%
\CSLLeftMargin{12. }%
\CSLRightInline{K. Byers-Heinlein, R. K.-Y. Tsui, D. Van Renswoude, A. K. Black, R. Barr, A. Brown, M. Colomer, S. Durrant, A. Gampe, N. Gonzalez-Gomez, others, The development of gaze following in monolingual and bilingual infants: A multi-laboratory study. \emph{Infancy} \textbf{26}, 4--38 (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-brooks2005development}{}}%
\CSLLeftMargin{13. }%
\CSLRightInline{R. Brooks, A. N. Meltzoff, The development of gaze following and its relation to language. \emph{Developmental science} \textbf{8}, 535--543 (2005).}

\leavevmode\vadjust pre{\hypertarget{ref-carpenter1998social}{}}%
\CSLLeftMargin{14. }%
\CSLRightInline{M. Carpenter, K. Nagell, M. Tomasello, G. Butterworth, C. Moore, Social cognition, joint attention, and communicative competence from 9 to 15 months of age. \emph{Monographs of the society for research in child development}, i--174 (1998).}

\leavevmode\vadjust pre{\hypertarget{ref-hernik2019infant}{}}%
\CSLLeftMargin{15. }%
\CSLRightInline{M. Hernik, T. Broesch, Infant gaze following depends on communicative signals: An eye-tracking study of 5-to 7-month-olds in vanuatu. \emph{Developmental science} \textbf{22}, e12779 (2019).}

\leavevmode\vadjust pre{\hypertarget{ref-callaghan2011early}{}}%
\CSLLeftMargin{16. }%
\CSLRightInline{T. Callaghan, H. Moll, H. Rakoczy, F. Warneken, U. Liszkowski, T. Behne, M. Tomasello, W. A. Collins, Early social cognition in three cultural contexts. \emph{Monographs of the society for research in child development}, i--142 (2011).}

\leavevmode\vadjust pre{\hypertarget{ref-prein2023tango}{}}%
\CSLLeftMargin{17. }%
\CSLRightInline{J. C. Prein, S. Kalinke, D. B. Haun, M. Bohn, TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults. \emph{Behavior Research Methods}, 1--17 (2023).}

\leavevmode\vadjust pre{\hypertarget{ref-prein2023variation}{}}%
\CSLLeftMargin{18. }%
\CSLRightInline{J. C. Prein, L. Maurits, A. Werwach, D. B. M. Haun, M. Bohn, Variation in gaze understanding across the life span: {A} process-level perspective. \emph{{PsyArXiv}}, doi: \href{https://doi.org/10.31234/osf.io/dy73a}{10.31234/osf.io/dy73a} (2023).}

\leavevmode\vadjust pre{\hypertarget{ref-barresi1996intentional}{}}%
\CSLLeftMargin{19. }%
\CSLRightInline{J. Barresi, C. Moore, Intentional relations and social understanding. \emph{Behavioral and brain sciences} \textbf{19}, 107--122 (1996).}

\leavevmode\vadjust pre{\hypertarget{ref-perner1994theory}{}}%
\CSLLeftMargin{20. }%
\CSLRightInline{J. Perner, T. Ruffman, S. R. Leekam, Theory of mind is contagious: You catch it from your sibs. \emph{Child Development} \textbf{65}, 1228--1238 (1994).}

\leavevmode\vadjust pre{\hypertarget{ref-rakoczy2022foundations}{}}%
\CSLLeftMargin{21. }%
\CSLRightInline{H. Rakoczy, Foundations of theory of mind and its development in early childhood. \emph{Nature Reviews Psychology} \textbf{1}, 223--235 (2022).}

\leavevmode\vadjust pre{\hypertarget{ref-lewis1996social}{}}%
\CSLLeftMargin{22. }%
\CSLRightInline{C. Lewis, N. H. Freeman, C. Kyriakidou, K. Maridaki-Kassotaki, D. M. Berridge, Social influences on false belief access: Specific sibling influences or general apprenticeship? \emph{Child development} \textbf{67}, 2930--2947 (1996).}

\leavevmode\vadjust pre{\hypertarget{ref-ruffman1998older}{}}%
\CSLLeftMargin{23. }%
\CSLRightInline{T. Ruffman, J. Perner, M. Naito, L. Parkin, W. A. Clements, Older (but not younger) siblings facilitate false belief understanding. \emph{Developmental psychology} \textbf{34}, 161 (1998).}

\leavevmode\vadjust pre{\hypertarget{ref-rosati2009looking}{}}%
\CSLLeftMargin{24. }%
\CSLRightInline{A. G. Rosati, B. Hare, Looking past the model species: Diversity in gaze-following skills across primates. \emph{Current opinion in neurobiology} \textbf{19}, 45--51 (2009).}

\leavevmode\vadjust pre{\hypertarget{ref-tomasello1998five}{}}%
\CSLLeftMargin{25. }%
\CSLRightInline{M. Tomasello, J. Call, B. Hare, Five primate species follow the visual gaze of conspecifics. \emph{Animal behaviour} \textbf{55}, 1063--1069 (1998).}

\leavevmode\vadjust pre{\hypertarget{ref-itakura2004gaze}{}}%
\CSLLeftMargin{26. }%
\CSLRightInline{S. Itakura, Gaze-following and joint visual attention in nonhuman animals, \emph{Japanese Psychological Research}. \textbf{46} (2004)pp. 216--226.}

\end{CSLReferences}

\end{document}

### 2024-01-23 paper/paper.tex
advance paper

@@
 \resizebox{\linewidth}{!}{
-\begin{tabular}[t]{lllllll}
+\begin{tabular}[t]{llllllll}
 \toprule
-Continent & Country & Community & N(male) & Age (range) & Language & Touchscreen\\
+Continent & Country & Community & N(male) & Age (range) & Language & Market integration & Touchscreen\\
 \midrule
-America & Argentina & Buenos Aires & 105 (53) & 4.72 (3.00 - 6.96) & Spanish (Rioplatense) & 0.90\\
- & Mexico & Ocuilan & 125 (61) & 4.97 (2.57 - 6.95) & Spanish (Mexican) & 0.77\\
- & USA & Stanford & 100 (56) & 5.00 (2.52 - 7.90) & English (American) & 0.98\\
-Africa & Namibia & Hai||om & 60 (38) & 5.85 (2.74 - 8.34) & Hai||om & 0.05\\
- &  & Khwe & 59 (24) & 5.84 (3.38 - 8.63) & Khwedam & 0.19\\
+America & Argentina & Buenos Aires & 105 (53) & 4.72 (3.00 - 6.96) & Spanish (Rioplatense) & high & 0.90\\
+ & Mexico & Ocuilan & 125 (61) & 4.97 (2.57 - 6.95) & Spanish (Mexican) & medium & 0.77\\
+ & USA & Stanford & 100 (56) & 5.00 (2.52 - 7.90) & English (American) & high & 0.98\\
+Africa & Namibia & Hai||om & 60 (38) & 5.85 (2.74 - 8.34) & Hai||om & low & 0.05\\
+ &  & Khwe & 59 (24) & 5.84 (3.38 - 8.63) & Khwedam & low & 0.19\\
 \addlinespace
- &  & Windhoek & 41 (18) & 5.68 (2.66 - 8.66) & English (Nigerian) & 0.95\\
- & Nigeria & Akure & 114 (53) & 5.07 (2.57 - 7.33) & English (Nigerian) & 0.91\\
- & Rep. Congo & BaYaka & 28 (12) & 7.86 (3.94 - 10.56) & BaYaka & 1.00\\
- &  & Bandongo & 30 (11) & 7.45 (3.50 - 10.95) & Lingala & 1.00\\
- & Sambia & Chimfunshi & 22 (5) & 5.98 (2.88 - 8.00) & Bemba & 0.14\\
+ &  & Windhoek & 41 (18) & 5.68 (2.66 - 8.66) & English (Nigerian) & high & 0.95\\
+ & Nigeria & Akure & 114 (53) & 5.07 (2.57 - 7.33) & English (Nigerian) & high & 0.91\\
+ & Rep. Congo & BaYaka & 28 (12) & 7.86 (3.94 - 10.56) & BaYaka & low & 0.00\\
+ &  & Bandongo & 30 (11) & 7.45 (3.50 - 10.95) & Lingala & low & 0.00\\
+ & Sambia & Chimfunshi & 22 (5) & 5.98 (2.88 - 8.00) & Bemba & medium & 0.14\\
 \addlinespace
- & Uganda & Nyabyeya & 51 (27) & 5.41 (3.27 - 8.21) & Swahili & 0.49\\
-Europe & Germany & Leipzig & 100 (48) & 4.88 (2.53 - 6.95) & German & 0.89\\
- & UK & Plymouth & 70 (30) & 6.02 (2.38 - 8.94) & English (British) & 0.99\\
-Asia & China & Beijing & 123 (62) & 5.47 (2.69 - 8.48) & Mandarin & 0.95\\
- & India & Pune & 155 (75) & 6.14 (3.06 - 8.83) & English (Indian) / Marathi & 0.92\\
+ & Uganda & Nyabyeya & 51 (27) & 5.41 (3.27 - 8.21) & Swahili & medium & 0.49\\
+Europe & Germany & Leipzig & 100 (48) & 4.88 (2.53 - 6.95) & German & high & 0.89\\
+ & UK & Plymouth & 70 (30) & 6.02 (2.38 - 8.94) & English (British) & high & 0.99\\
+Asia & China & Beijing & 123 (62) & 5.47 (2.69 - 8.48) & Mandarin & high & 0.95\\
+ & India & Pune & 155 (75) & 6.14 (3.06 - 8.83) & English (Indian) / Marathi & high & 0.92\\
 \addlinespace
- & Turkey & Malatya & 85 (40) & 5.02 (2.75 - 7.12) & Turkish & 1.00\\
-Oceania & New Zealand & Auckland & 43 (19) & 5.14 (2.81 - 8.75) & English (New Zealand) & 0.95\\
+ & Turkey & Malatya & 85 (40) & 5.02 (2.75 - 7.12) & Turkish & high & 1.00\\
+Oceania & New Zealand & Auckland & 43 (19) & 5.14 (2.81 - 8.75) & English (New Zealand) & high & 0.95\\
 \bottomrule
@@
 Across all 17 communities, we found a substantial increase in average levels of precision with age (range: \(\beta_{min}\) = , 95\% CrI () to \(\beta_{max}\) = ()).
-There were marked differences between communities: urban communities around the globe showed higher levels of precision compared to rural communities.
-We return to this result below.
-However, differences between communities were small compared to differences between individuals: communities did not form homogeneous clusters but largely overlapping distributions in that some individuals from communities with a lower average level of precision (e.g.~) performed better compared to some individuals from a setting with a very high average level of precision.
-Furthermore, in all communities, some 4-year-olds outperformed children two years older than them.
+There were marked differences between communities: highly market-integrated communities around the globe showed higher levels of precision compared to less market-integrated communities.
+However, we think that these results are better explained by exposure to technology than market integration.
+We discuss them in more detail below.
+Differences between communities were small compared to differences between individuals: communities did not form homogeneous clusters but largely overlapping distributions in that some individuals from communities with a lower average level of precision performed better compared to some individuals from a setting with a very high average level of precision.
+Furthermore, in all communities, some 4-year-olds outperformed children two years older than them (see Fig.
+\ref{fig:fig2}).
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.75\linewidth]{../visuals/pvis_pred}
+
+}
+
+\caption{A) Developmental trajectories by cultural settings.
+Transparent dots show aggregated data for each individual.
+The color dentoes the different cultural settings.
+The developmental trajectories are predicted based on a model of the data aggregated for each participant.
+B) Performance by screen section and cultural setting.
+Each bin covers 1/10th of the screen.
+Points show means and eroor bars 95\% confidence intervals for the data within that bin aggregated across participants.}\label{fig:fig2}
+\end{figure}
 

### 2024-01-23 analysis/gafo-cc-visuals.Rmd
add model effects

--- 2023-09-19 analysis/gafo-cc-visuals.Rmd
@@
 library(brms)
+library(cowplot)
 ```
@@
 data <- read_csv("../data/gafo-cc-clean-data.csv")%>%
+  mutate(continent = ifelse(
+    community %in% c("leipzig", "plymouth"), "Europe", 
+    ifelse(
+      community %in% c("akure", "hai||om", "khwe", "chimfunshi", "bandongo", "bayaka", "windhoek", "uganda"), "Africa",
+      ifelse(community %in% c("stanford", "mexico", "buenos_aires"), "America",
+             ifelse(community %in% c("india", "beijing", "turkey"), "Asia", "Oceania"))
+    )
+  ))%>%
+  mutate(continent = factor(continent, levels = c("America", "Africa", "Europe", "Asia", "Oceania"), ordered = T))%>%
   mutate(community = recode(community,
-                            akure = "akure (nigeria)",
-                            leipzig = "leipzig (germany)",
-                            `hai||om` = "hai||om (namibia)",
-                            khwe = "khwe (namibia)",
-                            windhoek = "windhoek (namibia)",
-                            stanford = "stanford (usa)",
-                            chimfunshi = "chimfunshi (sambia)",
-                            mexico = "ocuilan (mexico)",
-                            plymouth = "plymouth (uk)",
-                            beijing = "beijing (china)", 
-                            india = "pune (india)",
-                            buenos_aires = "buenos aires (argentina)",
-                            auckland = "auckland (new zealand)",
-                            turkey = "malatya (turkey)"))
+                            akure = "Akure (Nigeria)",
+                            leipzig = "Leipzig (Germany)",
+                            `hai||om` = "Hai||om (Namibia)",
+                            khwe = "Khwe (Namibia)",
+                            windhoek = "Windhoek (Namibia)",
+                            stanford = "Stanford (USA)",
+                            chimfunshi = "Chimfunshi (Sambia)",
+                            mexico = "Ocuilan (Mexico)",
+                            plymouth = "Plymouth (UK)",
+                            beijing = "Beijing (China)", 
+                            india = "Pune (India)",
+                            buenos_aires = "Buenos Aires (Argentina)",
+                            auckland = "Auckland (New Zealand)",
+                            turkey = "Malatya (Turkey)",
+                            bandongo = "Bandongo (Rep. Congo)",
+                            bayaka = "BaYaka (Rep. Congo)", 
+                            uganda = "Nyabyeya (Uganda)"))
+```
+```{r}
+# Population of the countries involved
+(1394016000 + 1426093184 + 332639104	+ 214028304	+ 128649568 + 82017512 + 80159664 + 65761116 + 45479120 + 2630073	 + 43252968	 + 4925477	+ 17426624) /
+8078229894 # proportion of world population
+
 ```
@@
 data%>%
-  group_by(community)%>%
+  group_by(continent, community)%>%
   summarise(n= n_distinct(subjid))
@@
 data%>%
-  group_by(community,subjid, ageinyears)%>%
+  group_by(continent, community,subjid, ageinyears)%>%
   summarise(impr = mean(abs(clickdistfromtargetcenterx)))%>%
@@
   ylim(0,1000)+
-  facet_wrap(~community)+
+  facet_wrap(~continent)+
+  #facet_wrap(~community)+
   labs(x = "Age (in years)", y ="Imprecision (average click distance from target)")+
@@
   #group_by(community, targetposition, age_group)%>%
-  group_by(community, targetposition)%>%
+  group_by(continent, community, targetposition)%>%
   tidyboot_mean(col= abs(clickdistfromtargetcenterx))
@@
   scale_color_manual(name = "Community", values = colors)+
-  #facet_grid(~age_group)+
+  facet_grid(~continent)+
   ylim(0,1000)+
@@
 ggsave("../visuals/target_position_site.png", width = 8, height = 6, bg = "white")
+```
+
+```{r}
+ptp%>%
+  select(community, targetposition, mean)%>%
+  pivot_wider(names_from = targetposition, values_from = mean)%>%
+  mutate(t1_vs_t10 = `1` - `10`,
+         t2_vs_t9 = `2` - `9`,
+         t3_vs_t8 = `3` - `8`,
+         t4_vs_t7 = `4` - `7`,
+         t5_vs_t6 = `5` - `6`)%>%
+  select(community, t1_vs_t10, t2_vs_t9, t3_vs_t8, t4_vs_t7, t5_vs_t6)%>%
+  pivot_longer(names_to = "side_bias", values_to = "value", cols = c(t1_vs_t10, t2_vs_t9, t3_vs_t8, t4_vs_t7, t5_vs_t6))%>%
+  mutate(side_bias = factor(side_bias, levels = c("t1_vs_t10", "t2_vs_t9", "t3_vs_t8", "t4_vs_t7", "t5_vs_t6")))%>%
+  ggplot(., aes(y = side_bias, x = value, col = community))+
+    geom_vline(xintercept = 0, lty = 3, alpha = 0.75)+
+    scale_color_manual(name = "Community", values = colors)+
+    geom_point()+
+    geom_path(aes(group = community))+
+    labs(x = "Side bias (pos = better performance on right)", y = "Target position")+
+    theme_minimal()
 ```
@@
   mutate(click = abs(clickdistfromtargetcenterx))%>%
-  group_by(subjid, community, ageinyears)%>%
+  group_by(subjid, continent,community, ageinyears)%>%
   summarise(mean_click = mean(click))%>%
@@
 ndata <- ddata%>%
-  distinct(community, ageinyears)
+  distinct(continent, community, ageinyears)
 
@@
 ggplot()+
+  geom_point(data = ddata, aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
   geom_smooth(data = post, aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
   theme_minimal()+
-  geom_point(data = ddata, aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.5)+
   scale_fill_manual(name = "Community", values = colors)+
   scale_color_manual(name = "Community", values = colors)+
-  labs(x = "Age", y="Imprecision")#+
-  facet_wrap(~community)+guides(col = "none", fill = "none")
+  labs(x = "Age", y="Imprecision")+
+  theme(legend.position = "right")+
+  facet_wrap(~continent, nrow = 2)#+guides(col = "none", fill = "none")
 ```
@@
 
+```{r}
+am <- ggplot()+
+  geom_point(data = ddata%>%filter(continent == "America"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
+  geom_smooth(data = post%>%filter(continent == "America"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
+  theme_few()+
+  scale_fill_colorblind(name = "")+
+  scale_color_colorblind(name = "")+
+  labs(x = "Age", y="Imprecision")+
+  scale_x_continuous(limits = c(2,10))+
+  scale_y_continuous(limits = c(0,1000))+
+  theme(legend.position = c(0.7, 0.9), legend.background = element_blank(),axis.title.x = element_blank())+
+  facet_wrap(~continent, nrow = 1)#+guides(col = "none", fill = "none")
+
+af <- ggplot()+
+  geom_point(data = ddata%>%filter(continent == "Africa"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
+  geom_smooth(data = post%>%filter(continent == "Africa"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
+  theme_few()+
+  scale_fill_colorblind(name = "")+
+  scale_color_colorblind(name = "")+
+  labs(x = "Age", y="Imprecision")+
+    scale_x_continuous(limits = c(2,10))+
+  scale_y_continuous(limits = c(0,1000))+
+  theme(legend.position = "right", legend.background = element_blank(), axis.title.y = element_blank(), axis.ticks.y = element_blank())+
+  facet_wrap(~continent, nrow = 1)#+guides(col = "none", fill = "none")
+
+eu <- ggplot()+
+  geom_point(data = ddata%>%filter(continent == "Europe"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
+  geom_smooth(data = post%>%filter(continent == "Europe"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
+  theme_few()+
+  scale_fill_colorblind(name = "")+
+  scale_color_colorblind(name = "")+
+  labs(x = "Age", y="Imprecision")+
+    scale_x_continuous(limits = c(2,10))+
+  scale_y_continuous(limits = c(0,1000))+
+  theme(legend.position = c(0.7, 0.9), legend.background = element_blank(), axis.title.y = element_blank(), axis.ticks.y = element_blank(),
+        axis.title.x = element_blank())+
+  facet_wrap(~continent, nrow = 1)#+guides(col = "none", fill = "none")
+
+as <- ggplot()+
+  geom_point(data = ddata%>%filter(continent == "Asia"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
+  geom_smooth(data = post%>%filter(continent == "Asia"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
+  theme_few()+
+  scale_fill_colorblind(name = "")+
+  scale_color_colorblind(name = "")+
+  labs(x = "Age", y="Imprecision")+
+    scale_x_continuous(limits = c(2,10))+
+  scale_y_continuous(limits = c(0,1000))+
+  theme(legend.position = c(0.7, 0.9), legend.background = element_blank(), axis.title.y = element_blank(), axis.ticks.y = element_blank(),
+        axis.title.x = element_blank())+
+  facet_wrap(~continent, nrow = 1)#+guides(col = "none", fill = "none")
+
+oc <- ggplot()+
+  geom_point(data = ddata%>%filter(continent == "Oceania"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
+  geom_smooth(data = post%>%filter(continent == "Oceania"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
+  theme_few()+
+  scale_fill_colorblind(name = "")+
+  scale_color_colorblind(name = "")+
+  labs(x = " ", y="Imprecision")+
+    scale_x_continuous(limits = c(2,10))+
+  scale_y_continuous(limits = c(0,1000))+
+  theme(legend.position = c(0.7, 0.9), legend.background = element_blank(), )+
+  facet_wrap(~continent, nrow = 1)#+guides(col = "none", fill = "none")
+```
+
+```{r}
+plot_grid(
+  plot_grid(am, eu, as,  nrow = 1),
+  plot_grid(oc, af, NULL, rel_widths = c(0.975,1.45, 0.55), nrow = 1), nrow = 2, rel_heights = c(1,1.1) )
+```
+```{r}
+ggsave("../visuals/dev_con.png", width = 14, height = 8, bg = "white", scale = 1)
+```
+
+# Predictors
+
+```{r}
+pred_agg_i <- data%>%
+  mutate(older_children = children - 1 - younger_children)%>%
+  group_by(community, subjid)%>%
+  summarise(screen = mean(screen, na.rm = T),
+            touchscreen = mean(touchscreen, na.rm = T), 
+            older_children = mean(older_children, na.rm = T), 
+            household = mean(household, na.rm = T))
+
+pred_agg_g <- data%>%
+  mutate(older_children = children - 1 - younger_children)%>%
+  group_by(community)%>%
+  summarise(screen = mean(screen, na.rm = T),
+            touchscreen = mean(touchscreen, na.rm = T), 
+            older_children = mean(older_children, na.rm = T), 
+            household = mean(household, na.rm = T))%>%
+  pivot_longer(names_to = "dem", values_to = "value", cols = c(screen, touchscreen, older_children, household))
+
+pred_agg_g%>%
+  filter(dem == "screen" | dem == "touchscreen")%>%
+  ggplot(aes(y = community, x = dem, fill = value))+
+  geom_point(pch = 22, size = 5, stroke = 0)+
+  scale_fill_viridis_c()
+
+pred_agg_g%>%
+  filter(dem == "household" | dem == "older_children")%>%
+  ggplot(aes(y = community, x = dem, fill = value))+
+  geom_point(pch = 22, size = 5, stroke = 0)+
+  scale_fill_viridis_c()
+
+```
+
+```{r}
+pred_agg_perf <- data%>%
+  mutate(older_children = children - 1 - younger_children)%>%
+  group_by(community)%>%
+  summarise(screen = mean(screen, na.rm = T),
+            touchscreen = mean(touchscreen, na.rm = T), 
+            older_children = mean(older_children, na.rm = T), 
+            household = mean(household, na.rm = T), 
+            perf = mean(abs(clickdistfromtargetcenterx)))
+
+ggplot(pred_agg_perf, aes(x = perf, y = touchscreen))+
+  geom_point()
+```
+
 # Map
@@
 world <- map_data("world")
-
 ```
@@
                             auckland = "New Zealand",
-                            turkey = "Turkey"))%>%
+                            turkey = "Turkey",
+                            bandongo = "Republic of Congo",
+                            bayaka = "Republic of Congo", 
+                         uganda = "Uganda"))%>%
   mutate(loc_lat = recode(community,
@@
                             auckland = -36.850146242932965,
-                          turkey = 38.35501382975052))%>%
+                            turkey = 38.35501382975052, 
+                            bandongo = 2.062200395167898,
+                            bayaka = 3.5404910412941893, 
+                            uganda = 1.6766777415592256))%>%
     mutate(loc_long = recode(community,
@@
                             auckland = 174.7651647587945, 
-                            turkey = 38.33313216647862))%>%
+                            turkey = 38.33313216647862, 
+                            bandongo = 17.000644575618752,
+                            bayaka = 17.88784692818756,
+                            uganda = 31.549794624310884))%>%
   group_by(community, loc_lat, loc_long, region)%>%
@@
   coord_map("moll")+
-  geom_polygon(aes(fill = fill)) +
+  geom_polygon(aes(fill = fill), col = "white", linewidth = 0.05) +
   scale_fill_manual(breaks = c("out", "in"), values = c("grey", "#DBD56E"), guide = "none")+
   new_scale("fill") +
-  geom_point(pch = 21, data = data_map, aes(x = loc_long, y = loc_lat, fill = Participants), col = "black", inherit.aes = F, size = 2.5, stroke = 0.5)+
+  geom_point(pch = 21, data = data_map, aes(x = loc_long, y = loc_lat, fill = Participants), col = "black", inherit.aes = F, size = 4, stroke = 0.5)+
   #scale_fill_distiller(palette ="RdBu", direction = -1) + # or direction=1
@@
   plain+
-  theme(legend.position = c(0.15, 0.25), legend.background = element_blank())
+  theme(legend.position = c(0.2, 0.25), legend.background = element_blank())
 ```
 ```{r}
-ggsave("../visuals/map.png", width = 12, height = 6, bg = "white")
+ggsave("../visuals/map.png", width = 8, height = 4, bg = "white", scale = 1.3)
 ```

### 2024-01-23 paper/paper.Rmd
update plots

@@
 ---
-title             : "The title"
-shorttitle        : "Title"
+title             : "Unity in diversity: Children from 17 diverse communities process gaze in similar ways"
+shorttitle        : "Gaze-following across 17 communities"
 
 author: 
-  - name          : "First Author"
-    affiliation   : "1"
+  - name          : "Manuel Bohn"
+    affiliation   : "1,2"
     corresponding : yes    # Define only one corresponding author
@@
       - "Writing - Review & Editing"
-  - name          : "Ernst-August Doelle"
+  - name          : "Julia Prein"
     affiliation   : "1,2"
     role:
+      - "Conceptualization"
+      - "Methodology"
       - "Writing - Review & Editing"
-      - "Supervision"
+  - name          : "..."
+    affiliation   : "..."
+    role:
+      - "Conceptualization"
+      - "Methodology"
+      - "Writing - Review & Editing"
+  - name          : "Daniel B. M. Haun"
+    affiliation   : "2"
+    role:
+      - "Conceptualization"
+      - "Writing - Review & Editing"
 
@@
   - id            : "1"
-    institution   : "Wilhelm-Wundt-University"
+    institution   : "Institute of Psychology in Education, Leuphana University Lüneburg"
   - id            : "2"
-    institution   : "Konstanz Business School"
+    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology"
 
@@
 abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
-  One or two sentences to put the results into a more **general context**.
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
-
-  <!-- https://tinyurl.com/ybremelq -->
+  Understanding gaze is critical for human social interaction.
+In a comprehensive cross-cultural study spanning five continents and 17 distinct cultural contexts, we examined the development of gaze understanding among preschoolers using a single reliable task tailored to each cultural setting.
+Our data provides evidence that children worldwide process gaze in the same way.
+Key performance signatures of a computational model that sees gaze following as a form of social vector estimation were found in all communities.
+Additionally, we found a subtle yet cross-culturally consistent relationship between children's environments and their ability to understand gaze.
+These results highlight the cross-cultural robustness of core social cognitive skills, as well as similarities in the developmental process, suggesting that fundamental aspects of social cognition and interaction emerge and develop in comparable ways globally and hence are a bedrock of human social cognition.
 
@@
 
-bibliography      : "r-references.bib"
+bibliography      : "library.bib"
 csl: science.csl
@@
 library("papaja")
-r_refs("r-references.bib")
+library(tidyverse)
+library(knitr)
+library(kableExtra)
 ```
@@
 set.seed(42)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
+knitr::opts_chunk$set(cache.extra = knitr::rand_seed, message = F, warning = F)
+options(knitr.kable.NA = '')
 ```
 
-Participants in the study lived in 17 different communities spread over five continents.
-Taken together, the countries from which data was contributed to the study represent 46% of the world's population.
+```{r data}
+data <- read_csv("../data/gafo-cc-clean-data.csv")%>%
+  mutate(continent = ifelse(
+    community %in% c("leipzig", "plymouth"), "Europe", 
+    ifelse(
+      community %in% c("akure", "hai||om", "khwe", "chimfunshi", "bandongo", "bayaka", "windhoek", "uganda"), "Africa",
+      ifelse(community %in% c("stanford", "mexico", "buenos_aires"), "America",
+             ifelse(community %in% c("india", "beijing", "turkey"), "Asia", "Oceania"))
+    )
+  ))%>%
+  mutate(continent = factor(continent, levels = c("America", "Africa", "Europe", "Asia", "Oceania"), ordered = T))%>%
+  mutate(community = recode(community,
+                            akure = "Akure (Nigeria)",
+                            leipzig = "Leipzig (Germany)",
+                            `hai||om` = "Hai||om (Namibia)",
+                            khwe = "Khwe (Namibia)",
+                            windhoek = "Windhoek (Namibia)",
+                            stanford = "Stanford (USA)",
+                            chimfunshi = "Chimfunshi (Sambia)",
+                            mexico = "Ocuilan (Mexico)",
+                            plymouth = "Plymouth (UK)",
+                            beijing = "Beijing (China)", 
+                            india = "Pune (India)",
+                            buenos_aires = "Buenos Aires (Argentina)",
+                            auckland = "Auckland (New Zealand)",
+                            turkey = "Malatya (Turkey)",
+                            bandongo = "Bandongo (Rep. Congo)",
+                            bayaka = "BaYaka (Rep. Congo)", 
+                            uganda = "Nyabyeya (Uganda)"))
+```
 
-# Results
+Social cognition is a defining aspect of the human species [@tomasello2005understanding; @laland2021understanding; @wellman2014making].
+It is supposed to enable unique forms of communication and cooperation that underlie cumulative cultural evolution and the formation of complex societies [@henrich2016secret; @tomasello2003makes; @legare2019development].
+The eyes are the proverbial window to the mind and the starting point for a majority of social reasoning processes [@shepherd2010following].
+Gaze is used to infer the focus of visual attention, which is a critical aspect of coordinated activities, including communication and cooperation [@tomasello2007reliance; @scaife1975capacity].
+The ability to follow gaze emerges early in childhood [@tang2023slow; @gredeback2010development; @byers2021development] and individual differences in children's gaze following ability predict later life outcomes, most notably, later communicative abilities [@brooks2005development; @carpenter1998social].
+Underlying this narrative is the wide-held assumption that gaze following is fundamental to human social cognition and, therefore, works and develops in the same way across human societies despite substantial variation in developmental contexts.
+This claim, however, lacks a solid empirical foundation.
 
-# Discussion
+We conducted a large-scale cross-cultural study on the development of gaze-following abilities to study potentially universal processing signatures and their development.
+Previous developmental studies focused on the onset of gaze following in infancy [@hernik2019infant; @callaghan2011early].
+The `r n_distinct(data$subjid)` participants in the study lived in 17 different communities spread over five continents (Fig.
+\@ref(fig:fig1)A, Tab.
+\@ref(tab:tab1)).
+The countries from which data was contributed to the study represented 46 % of the world's population.
+Communities covered a broad spectrum of geographical locations, social and political systems, languages, and subsistence styles (see Supplemental Materials).
 
-# Methods
+```{r fig1, include = T, fig.align = "center", fig.cap = "(B) Screenshot from the task.
+The scene depicts the choice phase in a test trial.
+Participants had to use the gaze of the agent to locate the balloon and click on the hedge where they thought the balloon was.
+Agents, audio recordings and backgrounds were adpated to each cultural setting.", out.width="100%"}
+knitr::include_graphics("../visuals/fig1.png")
+```
 
-## Participants
+```{r tab1, echo=F}
+tba1 <- data %>%
+  separate(community, into = c("community", "country"), sep = " \\(")%>%
+  mutate(country = str_remove(country, "\\("),
+         country = str_remove(country, "\\)"))%>%
+  distinct(subjid, .keep_all = T)%>%
+  group_by(community, country, continent)%>%
+  summarise(N = n_distinct(subjid), 
+            m = sum(sex == "m", na.rm = T), 
+            mean_age = mean(ageinyears),
+            min_age = min(ageinyears), 
+            max_age = max(ageinyears), 
+            touchscreen = mean(touchscreen, na.rm = T))%>%
+  mutate_if(is.numeric, format, digits = 2, nsmall = 2)%>%
+  mutate(age = paste0(mean_age, " (", min_age, " - ", max_age, ")"))%>%
+  mutate(N = paste0(N, " (", m,")"))%>%
+  select(-c(mean_age, min_age, max_age))%>%
+  arrange(continent, country)%>%
+  group_by(continent) %>%
+  mutate(continent = replace(continent, duplicated(continent), " ")) %>%
+  ungroup %>%
+  mutate(country = replace(country, duplicated(country), " "))%>%
+  mutate(language = c("Spanish (Rioplatense)", "Spanish (Mexican)", "English (American)", "Hai||om", "Khwedam", "English (Nigerian)", "English (Nigerian)", "BaYaka", "Lingala", "Bemba", "Swahili", "German", "English (British)", "Mandarin", "English (Indian) / Marathi", "Turkish", "English (New Zealand)"),
+           market_integration = c("high", "medium", "high", "low", "low", "high", "high", "low", "low", "medium", "medium", "high", "high", "high", "high", "high", "high"))%>%
+  select(continent, country, community, N, age, language, market_integration, touchscreen)
 
-## Material
+kableExtra::kable(tba1,
+             col.names = linebreak(c("Continent", "Country", "Community", "N(male)", "Age (range)", "Language", "Market integration","Touchscreen")),
+             caption = "Participant demographics.", 
+             format="latex", booktabs=TRUE
+             )%>% 
+  kable_styling(latex_options="scale_down")
+```
 
-## Procedure
+We used an animated picture book tablet task in which participants were asked to locate a hidden object based on observing an agent's gaze.
+Children watched a balloon disappear behind a hedge.
+An agent followed the trajectory of the balloon with their eyes (Fig.
+\@ref(fig:fig1)B).
+The key dependent variable was the precision with which children located the agent's focus of attention, that is, the deviation between where the agent looked (where the object was) and where the child thought the agent looked.
+We adapted visuals and audio instructions specifically to each of the 17 communities.
+Previous work demonstrated excellent individual-level measurement properties for this task [@prein2023tango].
+Thus, in addition to group-level trends, we were able to investigate individual-level variation.
 
-## Data analysis
-We used `r cite_r("r-references.bib")` for all our analyses.
+```{r}
+post_agg <- readRDS("../saves/post_agg.rds")
+post_fix <- readRDS("../saves/cult_age_fix.rds")
+
+```
+
+As the first step, we investigated developmental gains.
+Across all 17 communities, we found a substantial increase in average levels of precision with age (fixed effect: $\beta$ = `r post_fix%>%filter(term == "ageinyears")%>%pull(Estimate)`, 95% HDI (`r post_fix%>%filter(term == "ageinyears")%>%pull(Q2.5)` - `r post_fix%>%filter(term == "ageinyears")%>%pull(Q97.5)`); range of community-level effects: $\beta_{min}$ = `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%tail(1)%>%pull(mean)`, 95% HDI (`r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%tail(1)%>%pull(lci)` - `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%tail(1)%>%pull(uci)`) to $\beta_{max}$ = `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%head(1)%>%pull(mean)`, 95% HDI (`r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%head(1)%>%pull(lci)` - `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%head(1)%>%pull(uci)`).
+There were marked differences between communities: highly market-integrated communities around the globe showed higher levels of precision compared to less market-integrated communities.
+However, we believe that these results are better explained by exposure to technology than market integration.
+We discuss them in more detail below.
+Differences between communities were small compared to differences between individuals: communities did not form homogeneous clusters but largely overlapping distributions in that some individuals from communities with a lower average level of precision performed better compared to some individuals from a setting with a very high average level of precision.
+Furthermore, in all communities, some 4-year-olds outperformed children two years older than them (see Fig.
+\@ref(fig:fig2)A).
+
+```{r fig2, include = T, fig.align = "center", fig.cap = "A) Developmental trajectories by cultural settings.
+Transparent dots show aggregated data for each individual.
+The color dentoes the different cultural settings.
+The developmental trajectories are predicted based on a model of the data aggregated for each participant.
+B) Performance by screen section and cultural setting.
+Each bin covers 1/10th of the screen.
+Points show means and eroor bars 95\\% confidence intervals for the data within that bin aggregated across participants.", out.width="75%"}
+knitr::include_graphics("../visuals/pvis_pred.png")
+```
+
+Consistent developmental gains alone cannot inform us about the cognitive processes children use when locating the agent's focus of attention.
+Recent computational work modeled gaze following as social vector estimation [@prein2023variation].
+When observing the eyes, onlookers estimate a vector from the center of the eye through the pupil.
+The focus of attention is the location wherever the estimated vectors from both eyes hit a surface (Fig.
+\@ref(fig:fig1)C).
+The estimation process is not perfect, but each individual has a systematic level of uncertainty, which is conceptualized as the cause of individual differences.
+Importantly, this process model predicts a clear performance signature in our cross-cultural gaze following task: Trials in which the agent looks further away from the center (i.e.
+to the left or right side of the screen) should result in lower levels of precision, compared to trials in which the agent looks closer to the middle.
+This prediction is best understood by considering a similar phenomenon: pointing a torch light to a flat surface.
+The width of the light beam represents each individual's level of uncertainty in vector estimation.
+When the torch is directed straight down, the light beam is concentrated in a relatively small area.
+When the torch is rotated to the side, the light from one half of the cone must travel further than the light from the other half to reach the surface.
+As a consequence, the light is spread over a wider area.
+
+The processing signature was clearly visible across all 17 communities.
+Precision decreased when the agent looked at locations further away from the center (fixed effect: $\beta$ = `r post_fix%>%filter(term == "targetcentralityx")%>%pull(Estimate)`, 95% HDI (`r post_fix%>%filter(term == "targetcentralitx")%>%pull(Q2.5)` - `r post_fix%>%filter(term == "targetcentralityx")%>%pull(Q97.5)`); range of community-level effects: $\beta_{min}$ = `r post_agg%>%filter(type == "targetcentrality")%>%arrange(mean)%>%tail(1)%>%pull(mean)`, 95% HDI (`r post_agg%>%filter(type == "targetcentrality")%>%arrange(mean)%>%tail(1)%>%pull(lci)` - `r post_agg%>%filter(type == "targetcentrality")%>%arrange(mean)%>%tail(1)%>%pull(uci)`) to $\beta_{max}$ = `r post_agg%>%filter(type == "targetcentrality")%>%arrange(mean)%>%head(1)%>%pull(mean)`, 95% HDI (`r post_agg%>%filter(type == "targetcentrality")%>%arrange(mean)%>%head(1)%>%pull(lci)` - `r post_agg%>%filter(type == "targetcentrality")%>%arrange(mean)%>%head(1)%>%pull(uci)`).
+Visualization of the data showed the predicted u-shaped pattern in all communities (see Fig.
+\@ref(fig:fig2)B).
+These results indicate a universal cognitive process used by children in all communities.
+There is, however, an alternative way in which the u = shaped pattern might arise: it would also arise when participants ignored the agent's gaze and instead always selected the middle of the screen (center bias).
+To rule out this alternative explanation, we directly compared three cognitive models that made different assumptions about how participants' responses were generated: the focal vector-based gaze estimation model described above, a center-bias model where participants always select the center, and a random guessing model where participants select random locations.
+For every community, we found overwhelming support for the gaze estimation model (min $BF_{10}$ < 1000 for comparisons with both alternative models).
+Taken together, children from all 17 communities processed gaze in similar ways.
+
+```{r}
+pred_est <- readRDS("../saves/pred_est.rds")
+```
+
+What is left to explain are the marked community- and individual-level differences.
+In addition to the gaze-following task, caregivers filled out a small questionnaire about children's access to screen-based technology and the composition of their households.
+On an individual level, we found that across communities, children with access to touchscreen devices had higher levels of precision ($\beta$ = `r pred_est%>%filter(term == "touchscreen1")%>%pull(Estimate)`, SE = `r pred_est%>%filter(term == "touchscreen1")%>%pull(Est.Error)`, 95% CrI = `r pred_est%>%filter(term == "touchscreen1")%>%pull(Q2.5)` - `r pred_est%>%filter(term == "touchscreen1")%>%pull(Q97.5)`).
+On a community level, we also saw that average performance was lowest in the communities in which touchscreen devices were the least frequent (Fig.
+\@ref(fig:fig3)).
+Thus, methodological factors likely explained the marked differences between communities.
+
+```{r fig3, include = T, fig.align = "center", fig.cap = "Correlation between performance in the gaze-following task and the exposure to touchscreens on a cultural setting-level.
+Realtive imprecision accounts for differences in age between settings in that it corresponds to the random intercept estimate for each setting in a model predicting performance by age.", out.width="50%"}
+knitr::include_graphics("../visuals/pcomtc.png")
+```
+
+On an individual level, other factors likely generated individual differences because there was substantial variation even in communities where almost all children had access to touchscreens.
+Previous work suggested that social cognition develops in social interaction [@barresi1996intentional; @perner1994theory; @rakoczy2022foundations], in particular, with older siblings [@lewis1996social; @ruffman1998older].
+We found tentative support for this idea in the form of a small but consistent effect in the direction that participants living together with more children older than themselves had slightly higher levels of precision ($\beta$ = `r pred_est%>%filter(term == "older_children")%>%pull(Estimate)`, SE = `r pred_est%>%filter(term == "older_children")%>%pull(Est.Error)`, 95% CrI = `r pred_est%>%filter(term == "older_children")%>%pull(Q2.5)` - `r pred_est%>%filter(term == "older_children")%>%pull(Q97.5)`).
+
+Following and understanding gaze is a foundational building block of human social cognition [@tomasello2007reliance; @scaife1975capacity].
+A substantial body of work has explored the developmental onset of gaze following in a few selected cultural settings [@tang2023slow; @gredeback2010development; @byers2021development; @hernik2019infant; @callaghan2011early].
+The data reported here provides evidence that children all over the world process gaze in the same way.
+Key performance signatures of a model that sees gaze following as a form of social vector estimation were found in the data of all 17 distinct cultural communities.
+The cognitive processes underlying gaze following are thus likely to be rooted in humans' evolved cognitive architecture, which is -- presumably -- later refined during social interaction.
+The phylogenetic roots of these processes might possibly lie much deeper as primates from a wide range of species follow gaze [@rosati2009looking; @tomasello1998five; @itakura2004gaze].
+Yet, if they also show the same processing signatures has yet to be explored.
+
+There are important limitations to this study.
+The methodological factors that influenced performance might have overshadowed individual and community-level differences that originate from other sources.
+Importantly, this does not affect our interpretation of the data as evidence for shared cognitive processing because the key processing signatures were present in all communities.
+The role that social interaction plays as a potential driver of development and source of individual differences is vastly under-explored in the current study.
+The small effect of the exposure to older children does not indicate which aspects of social interaction enhance gaze processing.
+Naturalistic data directly recording social interactions across communities would offer crucial information to close this explanatory gap.
+Recent work in the field of language acquisition has shown how technological innovations can be used to close this explanatory gap.
+
+The evidence presented here holds far-reaching implications.
+Our work pioneers a methodological approach that introduces solid individual-level measurement to the cross-cultural study of cognitive development.
+As such, it serves as a blueprint for future research on a broad spectrum of cognitive abilities.
+Most importantly, this study offers a much-needed empirical foundation for theories on human nature.
+The finding that children from diverse cultures deploy similar cognitive processes in interpreting gaze points to an evolutionary basis of basic social cognition, which is refined during development, presumably through social interaction.
 

### 2024-01-23 paper/paper.tex
update plots

@@
 As the first step, we investigated developmental gains.
-Across all 17 communities, we found a substantial increase in average levels of precision with age (range: \(\beta_{min}\) = , 95\% CrI () to \(\beta_{max}\) = ()).
+Across all 17 communities, we found a substantial increase in average levels of precision with age (fixed effect: \(\beta\) = -0.30, 95\% HDI (-0.39 - -0.21); range of community-level effects: \(\beta_{min}\) = -0.06, 95\% HDI (-0.17 - 0.06) to \(\beta_{max}\) = -0.58, 95\% HDI (-0.69 - -0.46).
 There were marked differences between communities: highly market-integrated communities around the globe showed higher levels of precision compared to less market-integrated communities.
@@
 Furthermore, in all communities, some 4-year-olds outperformed children two years older than them (see Fig.
-\ref{fig:fig2}).
+\ref{fig:fig2}A).
 
@@
 The processing signature was clearly visible across all 17 communities.
-Precision decreased when the agent looked at locations further away from the center (fixed effect: \(\beta\) = (), community-level effects: Fig.
-2).
-Visualization of the data showed the predicted u-shaped pattern in all communities.
+Precision decreased when the agent looked at locations further away from the center (fixed effect: \(\beta\) = 0.48, 95\% HDI ( - 0.54); range of community-level effects: \(\beta_{min}\) = 0.58, 95\% HDI (0.51 - 0.66) to \(\beta_{max}\) = 0.22, 95\% HDI (0.05 - 0.38).
+Visualization of the data showed the predicted u-shaped pattern in all communities (see Fig.
+\ref{fig:fig2}B).
 These results indicate a universal cognitive process used by children in all communities.
@@
 In addition to the gaze-following task, caregivers filled out a small questionnaire about children's access to screen-based technology and the composition of their households.
-On an individual level, we found that across communities, children with access to touchscreen devices had higher levels of precision (fixed effect: \(\beta\) = (), community-level effects: Fig.
-2).
+On an individual level, we found that across communities, children with access to touchscreen devices had higher levels of precision (\(\beta\) = -0.14, SE = 0.04, 95\% CrI = -0.22 - -0.07).
 On a community level, we also saw that average performance was lowest in the communities in which touchscreen devices were the least frequent (Fig.
-3).
+\ref{fig:fig3}).
 Thus, methodological factors likely explained the marked differences between communities.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.5\linewidth]{../visuals/pcomtc}
+
+}
+
+\caption{Correlation between performance in the gaze-following task and the exposure to touchscreens on a cultural setting-level.
+Realtive imprecision accounts for differences in age between settings in that it corresponds to the random intercept estimate for each setting in a model predicting performance by age.}\label{fig:fig3}
+\end{figure}
 
@@
 Previous work suggested that social cognition develops in social interaction (\emph{19}--\emph{21}), in particular, with older siblings (\emph{22}, \emph{23}).
-We found tentative support for this idea in the form of a small but consistent effect in the direction that participants living together with more children older than themselves had slightly higher levels of precision (fixed effect: \(\beta\) = (), community-level effects: Fig.
-2).
+We found tentative support for this idea in the form of a small but consistent effect in the direction that participants living together with more children older than themselves had slightly higher levels of precision (\(\beta\) = -0.01, SE = 0.01, 95\% CrI = -0.04 - 0.01).
 

### 2024-01-29 analysis/gafo-cc-data-processing.Rmd
prep merge

@@
 
-unique(tidy_data_namibia$subjID)
+```
+
+```{r}
+# quality checks
+
+# range of click distance: min = 0; max = 1920
+range(abs(tidy_data_namibia$clickDistFromTargetCenterX)) #
+
+# number of trials: everyone should have more than 4 trials.
+tidy_data_namibia%>%group_by(subjID)%>%filter(voiceover == F, trialType == "test")%>%summarise(n = n())%>%filter(n<5)
+
 ```
@@
     ageInYears = as.numeric(difftime(test_date,BirthDate, units = "days")/365.25),
+    Children = ifelse(subjID == "W0000023", 2, Children)
   ) %>%
@@
 ```{r}
+# quality checks
+
+# check for typos in subject names, is there a data file for every child in the demographics spreadsheet?
+tidy_demographics_namibia%>%
+  filter(!subjid %in% tidy_data_namibia$subjID)
+
+# range of ages: should not be below 2.5
+range(tidy_demographics_namibia$ageinyears)
+
+# screen and touchscreen should only be 0 or 1 
+unique(tidy_demographics_namibia$screen) 
+unique(tidy_demographics_namibia$touchscreen)
+
+# children should at least be 1 (the tested child) 
+tidy_demographics_namibia%>%filter(children < 1)
+# household should at least be 2 (the tested child and one adult) 
+tidy_demographics_namibia%>%filter(household < 2) 
+# household should be larger than children
+tidy_demographics_namibia%>%filter(children >= household) 
+# youngerchildren should be fewer than children
+tidy_demographics_namibia%>%filter(youngerchildren >= children)
+
+exclude_namib <- tidy_demographics_namibia%>%filter(children >= household) %>% pull(subjid)
+
+```
+
+```{r}
 data_namibia <- tidy_demographics_namibia%>%
   left_join(tidy_data_namibia%>%rename_all(tolower),by = c("subjid"))%>%
+  filter(!subjid %in% exclude_namib)%>%
   distinct(subjid, trialnr, .keep_all = T)
@@
 ```{r}
-data_namibia%>%
-  filter(community == "windhoek")%>%
-  mutate(age_group = substr(ageinyears, 1,1))%>%
-  #group_by(age_group)%>%
-  summarise(n = n_distinct(subjid))
-
-data_namibia%>%
-  filter(community == "windhoek")%>%
-  group_by(ageinyears)%>%
-  summarise(n= n_distinct(subjid))%>%
-  ggplot(aes(x = ageinyears, y = ""))+
-  geom_count(alpha = .5)+
-  xlim(2.5, 8)+
-  theme_bw()
+# did a child get lost on the way?
+n_distinct(tidy_demographics_namibia$subjid) == (n_distinct(data_namibia$subjid) + length(exclude_namib))
 ```
@@
 
+```{r}
+# quality checks
+
+# range of click distance: min = 0; max = 1920
+range(abs(tidy_data_leipzig$clickDistFromTargetCenterX)) #
+
+# number of trials: everyone should have more than 4 trials.
+tidy_data_leipzig%>%group_by(subjID)%>%filter(voiceover == F, trialType == "test")%>%summarise(n = n())%>%filter(n<5)
+
+```
+
 ```{r demographics}
@@
 ```{r}
+# quality checks
+
+# check for typos in subject names
 tidy_demographics_leipzig%>%
   filter(!subjid %in% tidy_data_leipzig$subjID)
+
+# range of ages: should not be below 2.5
+range(tidy_demographics_leipzig$ageinyears)
+
+# screen and touchscreen should only be 0 or 1 or NA
+unique(tidy_demographics_leipzig$screen) 
+unique(tidy_demographics_leipzig$touchscreen)
+
+# children should at least be 1 (the tested child) 
+tidy_demographics_leipzig%>%filter(children < 1)
+# household should at least be 2 (the tested child and one adult) 
+tidy_demographics_leipzig%>%filter(household < 2) 
+# household should be larger than children
+tidy_demographics_leipzig%>%filter(children >= household) 
+# youngerchildren should be fewer than children
+tidy_demographics_leipzig%>%filter(younger_children >= children) 
 ```
@@
   distinct(subjid, trialnr, .keep_all = TRUE)
-
-```
-
-```{r}
-data_leipzig%>%
-  group_by(subjid)%>%
-  summarise(n())
-
-data_leipzig%>%
-  #group_by(subjid)%>%
-  summarise(n = n_distinct(subjid))
-
-data_leipzig%>%
-  mutate(age_group = substr(ageinyears, 1, 1))%>%
-  select(subjid, sex, age_group, screen, touchscreen, household, children, younger_children)%>%
-  na.omit()%>%
-  group_by(age_group, sex)%>%
-  summarise(n = n_distinct(subjid))
-
-data_leipzig%>%
-  mutate(age_group = substr(ageinyears, 1, 1))%>%
-  select(subjid, sex, age_group, screen, touchscreen, household, children, younger_children)%>%
-  na.omit()%>%
-  group_by(age_group)%>%
-  summarise(n = n_distinct(subjid))
+```
+
+```{r}
+# did a child get lost on the way?
+n_distinct(tidy_demographics_leipzig$subjid) <= (n_distinct(tidy_data_leipzig$subjID))
 ```
@@
 
+```{r}
+# quality checks
+
+# range of click distance: min = 0; max = 1920
+range(abs(tidy_data_nigeria$clickDistFromTargetCenterX)) #
+
+# number of trials: everyone should have more than 4 trials.
+tidy_data_nigeria%>%group_by(subjID)%>%filter(voiceover == F, trialType == "test")%>%summarise(n = n())%>%filter(n<5)
+
+```
+
 ```{r demographics}
@@
 ```{r}
+# quality checks
+
+# check for typos in subject names
+tidy_demographics_nigeria%>%
+  filter(!subjid %in% tidy_data_nigeria$subjID)
+
+# range of ages: should not be below 2.5
+range(tidy_demographics_nigeria$ageinyears)
+
+# screen and touchscreen should only be 0 or 1 or NA
+unique(tidy_demographics_nigeria$screen) 
+unique(tidy_demographics_nigeria$touchscreen)
+
+# children should at least be 1 (the tested child) 
+tidy_demographics_nigeria%>%filter(children < 1)
+# household should at least be 2 (the tested child and one adult) 
+tidy_demographics_nigeria%>%filter(household < 2) 
+# household should be larger than children
+tidy_demographics_nigeria%>%filter(children >= household) 
+# younger children should be fewer than children
+tidy_demographics_nigeria%>%filter(younger_children >= children)
+
+exclude_niger <- tidy_demographics_nigeria%>%filter(younger_children >= children) %>% pull(subjid)
+```
+
+```{r}
 data_nigeria <- tidy_demographics_nigeria%>%
   left_join(tidy_data_nigeria%>%rename_all(tolower),by = c("subjid"))%>%
+  filter(!subjid %in% exclude_niger)%>%
   mutate(location = community,
@@
   distinct(subjid, trialnr, .keep_all = TRUE)
+```
+
+```{r}
+# did a child get lost on the way?
+n_distinct(tidy_demographics_nigeria$subjid) == (n_distinct(data_nigeria$subjid) + length(exclude_niger))
 ```
@@
 ```{r}
-tidy_data_zambia%>%
-  summarise(n = n_distinct(subjID))
+# quality checks
+
+# range of click distance: min = 0; max = 1920
+range(abs(tidy_data_zambia$clickDistFromTargetCenterX)) #
+
+# number of trials: everyone should have more than 4 trials.
+tidy_data_zambia%>%group_by(subjID)%>%filter(voiceover == F, trialType == "test")%>%summarise(n = n())%>%filter(n<5)
+
 ```
@@
 ```{r}
+# quality checks
+
+# check for typos in subject names
+tidy_demographics_zambia%>%
+  filter(!subjid %in% tidy_data_zambia$subjID)
+
+# range of ages: should not be below 2.5
+range(tidy_demographics_zambia$ageinyears)
+
+# screen and touchscreen should only be 0 or 1 or NA
+unique(tidy_demographics_zambia$screen) 
+unique(tidy_demographics_zambia$touchscreen)
+
+# children should at least be 1 (the tested child) 
+tidy_demographics_zambia%>%filter(children < 1)
+# household should at least be 2 (the tested child and one adult) 
+tidy_demographics_zambia%>%filter(household < 2) 
+# household should be larger than children
+tidy_demographics_zambia%>%filter(children >= household) 
+# younger children should be fewer than children
+tidy_demographics_zambia%>%filter(younger_children >= children) 
+```
+
+```{r}
 data_zambia <- tidy_demographics_zambia%>%
@@
 
+```{r}
+# did a child get lost on the way?
+n_distinct(tidy_demographics_zambia$subjid) <= (n_distinct(data_zambia$subjid))
+```
+
 # Stanford
@@
 ```{r}
-data_stanford <- read.csv("../../raw_data/gafo-cc/stanford/tidy_data_extra.csv")%>%
+raw_data_stanford <- read.csv("../../raw_data/gafo-cc/stanford/tidy_data_extra.csv")%>%
   mutate(subjID = paste0("S",subjID),
@@
 ```{r}
-data_stanford%>%
-  mutate(age_group = substr(ageinyears, 1,1))%>%
-  group_by(age_group)%>%
-  summarise(n = n_distinct(subjid))
-
+# quality checks
+
+# range of click distance: min = 0; max = 1920
+range(abs(raw_data_stanford$clickdistfromtargetcenterx)) #
+
+# number of trials: everyone should have more than 4 trials.
+raw_data_stanford%>%group_by(subjid)%>%filter(voiceover == F, trialtype == "test")%>%summarise(n = n())%>%filter(n<5)
+
+```
+
+```{r}
+# quality checks
+
+# range of ages: should not be below 2.5
+range(raw_data_stanford$ageinyears)
+
+# screen and touchscreen should only be 0 or 1 or NA
+unique(raw_data_stanford$screen) 
+unique(raw_data_stanford$touchscreen)
+
+# children should at least be 1 (the tested child) 
+raw_data_stanford%>%filter(children < 1)
+# household should at least be 2 (the tested child and one adult) 
+raw_data_stanford%>%filter(household < 2) 
+# household should be larger than children
+raw_data_stanford%>%filter(children >= household) 
+# youngerchildren should be fewer than children
+raw_data_stanford%>%filter(younger_children >= children)
+
+exclude_stanf <- raw_data_stanford%>%filter(children >= household)%>%distinct(subjid)%>%pull(subjid)
+```
+
+```{r}
+data_stanford <- raw_data_stanford%>%
+  filter(!subjid %in% exclude_stanf)
 ```
@@
   distinct(subjID, trialNr, .keep_all = T)#%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
-
-unique(raw_data_plymouth$subjID)
-```
-
-```{r}
-tidy_data_plymouth%>%
-  filter(trialType == "test")%>%
-  group_by(subjID)%>%
-  summarise(n = n())
-
-tidy_data_plymouth%>%
-  filter(trialType == "test")%>%
-  summarise(n = n_distinct(subjID))
-
-tidy_data_plymouth%>%
-  filter(subjID == "uksch002")
+```
+
+```{r}
+# quality checks
+
+# range of click distance: min = 0; max = 1920
+range(abs(tidy_data_plymouth$clickDistFromTargetCenterX)) #
+
+# number of trials: everyone should have more than 4 trials.
+tidy_data_plymouth%>%group_by(subjID)%>%filter(voiceover == F, trialType == "test")%>%summarise(n = n())%>%filter(n<5)
+
 ```
@@
   )%>%
-  filter(tested == "yes")
+  filter(tested == "yes", subjid != "uksch057")
 
@@
 ```{r}
+# quality checks
+
+# check for typos in subject names
+tidy_demographics_plymouth%>%
+  filter(!subjid %in% tidy_data_plymouth$subjID)
+
+# range of ages: should not be below 2.5
+range(tidy_demographics_plymouth$ageinyears)
+
+# screen and touchscreen should only be 0 or 1 or NA
+unique(tidy_demographics_plymouth$screen) 
+unique(tidy_demographics_plymouth$touchscreen)
+
+# children should at least be 1 (the tested child) 
+tidy_demographics_plymouth%>%filter(children < 1)
+# household should at least be 2 (the tested child and one adult) 
+tidy_demographics_plymouth%>%filter(household < 2) 
+# household should be larger than children
+tidy_demographics_plymouth%>%filter(children >= household) 
+# youngerchildren should be fewer than children
+tidy_demographics_plymouth%>%filter(younger_children >= children) 
+```
+
+```{r}
 data_plymouth <- tidy_demographics_plymouth%>%
@@
   distinct(subjid, trialnr, .keep_all = TRUE)
-
-data_plymouth%>%
-  #mutate(age_group = substr(ageinyears, 1,1))%>%
-  #group_by(age)%>%
-  summarise(n = n_distinct(subjid))
-
-data_plymouth%>%
-  group_by(age)%>%
-  summarise(n())
-
- data_plymouth%>%
-   filter(is.na(durationanimationballoontotal))
 ```
@@
 ```{r}
-tidy_data_mex%>%
-  summarise(n = n_distinct(subjID))
+# quality checks
+
+# range of click distance: min = 0; max = 1920
+range(abs(tidy_data_mex$clickDistFromTargetCenterX)) #
+
+# number of trials: everyone should have more than 4 trials.
+tidy_data_mex%>%group_by(subjID)%>%filter(voiceover == F, trialType == "test")%>%summarise(n = n())%>%filter(n<5)
+
 ```
@@
   filter(!is.na(lastname))%>%
-  mutate(birth_date = ifelse(birth_date == 29042017, 20170429, birth_date))
+  mutate(birth_date = ifelse(birth_date == 29042017, 20170429, birth_date), 
+         subjid = ifelse(subjid == "Mexva37", "Mexva037", subjid),
+         subjid = ifelse(subjid == "Mexva51", "Mexva051", subjid), 
+         children = ifelse(subjid == "Mexli040", children + 1, children),
+         children = ifelse(subjid == "Mexli064", children + 1, children))
 
@@
   select(-c(name, lastname, test_date, birth_date, comment))%>%
-  filter(!is.na(ageinyears))
-
+  filter(!is.na(ageinyears))%>%
+  mutate(household = household + children)
+
+```
+
+```{r}
+# quality checks
+
+# check for typos in subject names
+tidy_demographics_mex%>%
+  filter(!subjid %in% tidy_data_mex$subjID)
+
+# range of ages: should not be below 2.5
+range(tidy_demographics_mex$ageinyears)
+
+# screen and touchscreen should only be 0 or 1 or NA
+unique(tidy_demographics_mex$screen) 
+unique(tidy_demographics_mex$touchscreen)
+
+# children should at least be 1 (the tested child) 
+tidy_demographics_mex%>%filter(children < 1)
+# household should at least be 2 (the tested child and one adult) 
+tidy_demographics_mex%>%filter(household < 2) 
+# household should be larger than children
+tidy_demographics_mex%>%filter(children >= household) 
+# youngerchildren should be fewer than children
+tidy_demographics_mex%>%filter(younger_children >= children) 
 ```
@@
   distinct(subjid, trialnr, .keep_all = TRUE)
-
-data_mex%>%summarise(n = n_distinct(subjid))
-
-```
+```
+
 ```{r}
@@
 
-#unique(tidy_data_leipzig$subjID)
-
-tidy_data_china%>%
-  filter(subjID == "china077")
-
-n_distinct(tidy_data_china$subjID)
-
-tidy_data_china%>%
-  group_by(subjID)%>%
-  summarise(n())
+```
+
+```{r}
+# quality checks
+
+# range of click distance: min = 0; max = 1920
+range(abs(tidy_data_china$clickDistFromTargetCenterX)) #
+
+# number of trials: everyone should have more than 4 trials.
+tidy_data_china%>%group_by(subjID)%>%filter(voiceover == F, trialType == "test")%>%summarise(n = n())%>%filter(n<5)
+
 ```
@@
 
+```
+
+```{r}
+# quality checks
+
+# check for typos in subject names
 tidy_demographics_china%>%
-  arrange(ageinyears)
+  filter(!subjid %in% tidy_data_china$subjID)
+
+# range of ages: should not be below 2.5
+range(tidy_demographics_china$ageinyears)
+
+# screen and touchscreen should only be 0 or 1 or NA
+unique(tidy_demographics_china$screen) 
+unique(tidy_demographics_china$touchscreen)
+
+# children should at least be 1 (the tested child) 
+tidy_demographics_china%>%filter(children < 1)
+# household should at least be 2 (the tested child and one adult) 
+tidy_demographics_china%>%filter(household < 2) 
+# household should be larger than children
+tidy_demographics_china%>%filter(children >= household) 
+# youngerchildren should be fewer than children
+tidy_demographics_china%>%filter(younger_children >= children) 
 ```
@@
   distinct(subjid, trialnr, .keep_all = TRUE)
-
-data_china%>%
-  #mutate(age_group = substr(ageinyears, 1,1))%>%
-  #group_by(age_group)%>%
-  summarise(n = n_distinct(subjid))
-
-data_china%>%
-  group_by(subjid)%>%
-  summarise(n())
-
 ```
@@
 ```{r}
-tidy_data_arg%>%
-  summarise(n = n_distinct(subjID))
-
-tidy_data_arg%>%
-  group_by(subjID)%>%
-  summarise(n = n())
+# quality checks
+
+# range of click distance: min = 0; max = 1920
+range(abs(tidy_data_arg$clickDistFromTargetCenterX)) #
+
+# number of trials: everyone should have more than 4 trials.
+tidy_data_arg%>%group_by(subjID)%>%filter(voiceover == F, trialType == "test")%>%summarise(n = n())%>%filter(n<5)
+
 ```
@@
 
+```
+
+```{r}
+# quality checks
+
+# check for typos in subject names
 tidy_demographics_arg%>%
-  filter(ageinyears < 2)
-```
-
-```{r}
-raw_demographics_arg%>%
-  filter(!id %in% tidy_data_arg$subjID)
-
-tidy_data_arg%>%
-  filter(!subjID %in% raw_demographics_arg$id)
+  filter(!subjid %in% tidy_data_arg$subjID)
+
+# range of ages: should not be below 2.5
+range(tidy_demographics_arg$ageinyears)
+
+# screen and touchscreen should only be 0 or 1 or NA
+unique(tidy_demographics_arg$screen) 
+unique(tidy_demographics_arg$touchscreen)
+
+# children should at least be 1 (the tested child) 
+tidy_demographics_arg%>%filter(children < 1)
+# household should at least be 2 (the tested child and one adult) 
+tidy_demographics_arg%>%filter(household < 2) 
+# household should be larger than children
+tidy_demographics_arg%>%filter(children >= household) 
+# youngerchildren should be fewer than children
+tidy_demographics_arg%>%filter(younger_children >= children) 
 ```
@@
   distinct(subjid, trialnr, .keep_all = TRUE)
-
-data_arg%>%
-  group_by(community)%>%
-  summarise(n = n_distinct(subjid))
-
-data_arg%>%
-  group_by(subjid)%>%
-  summarise(n = n())
 ```
@@
 ```{r}
-tidy_data_ind%>%
-  summarise(n = n_distinct(subjID))
-
-tidy_data_ind%>%
-  group_by(subjID)%>%
-  summarise(n = n())
+# quality checks
+
+# range of click distance: min = 0; max = 1920
+range(abs(tidy_data_ind$clickDistFromTargetCenterX)) #
+
+# number of trials: everyone should have more than 4 trials.
+tidy_data_ind%>%group_by(subjID)%>%filter(voiceover == F, trialType == "test")%>%summarise(n = n())%>%filter(n<5)
 
@@
 ```{r }
-raw_demographics_ind <- read_xlsx("../../../../../../Cloud/QuantEx/Gafo-cc/data/india/gafo-cc-india-participants.xlsx", sheet = 1)
+raw_demographics_ind <- read_xlsx("../../../../../../Cloud/QuantEx/Gafo-cc/data/india/Gafo_Corrected.xlsx", sheet = 1)
 
@@
   )  %>%
-  select(-c(first_name, last_name, test_date, birth_date, comment))%>%
+  select(-c(test_date, birth_date, comment))%>%
   filter(!is.na(ageinyears))%>%
@@
 ```{r}
+# quality checks
+
+# check for typos in subject names
+tidy_demographics_ind%>%
+  filter(!subjid %in% tidy_data_ind$subjID)
+
+# range of ages: should not be below 2.5
+range(tidy_demographics_ind$ageinyears)
+
+# screen and touchscreen should only be 0 or 1 or NA
+unique(tidy_demographics_ind$screen) 
+unique(tidy_demographics_ind$touchscreen)
+
+# children should at least be 1 (the tested child) 
+tidy_demographics_ind%>%filter(children < 1)
+# household should at least be 2 (the tested child and one adult) 
+tidy_demographics_ind%>%filter(household < 2) 
+# household should be larger than children
+tidy_demographics_ind%>%filter(children >= household) 
+# youngerchildren should be fewer than children
+tidy_demographics_ind%>%filter(younger_children >= children)
+
+exclude_ind <- c(tidy_demographics_ind%>%filter(children >= household) %>% pull(subjid),
+                 tidy_demographics_ind%>%filter(younger_children >= children)%>% pull(subjid))
+
+```
+
+```{r}
 data_ind <- tidy_demographics_ind%>%
+  filter(!subjid %in%exclude_ind)%>%
   left_join(tidy_data_ind%>%rename_all(tolower),by = c("subjid"))%>%
@@
   distinct(subjid, trialnr, .keep_all = TRUE)
-
-data_ind%>%
-  group_by(subjid)%>%
-  summarise(n = n())
-
 ```
@@
 ```{r}
-tidy_data_nz%>%
-  #filter(trialType == "test")%>%
-  group_by(subjID)%>%
-  summarise(n = n())
-
-tidy_data_nz%>%
-  filter(trialType == "test")%>%
-  summarise(n = n_distinct(subjID))
-
-tidy_data_nz%>%
-  filter(subjID == "uksch002")
+# quality checks
+
+# range of click distance: min = 0; max = 1920
+range(abs(tidy_data_nz$clickDistFromTargetCenterX)) #
+
+# number of trials: everyone should have more than 4 trials.
+tidy_data_nz%>%group_by(subjID)%>%filter(voiceover == F, trialType == "test")%>%summarise(n = n())%>%filter(n<5)
+
 ```
@@
   read_xlsx("../../../../../../Cloud/QuantEx/Gafo-cc/data/new_zealand/gafo-cc-new-zealand-participants.xlsx", sheet = 1)
-  )
+  )%>%
+  filter(id != "NZ000001")
 
@@
 ```{r}
+# quality checks
+
+# check for typos in subject names
+tidy_demographics_nz%>%
+  filter(!subjid %in% tidy_data_nz$subjID)
+
+# range of ages: should not be below 2.5
+range(tidy_demographics_leipzig$ageinyears)
+
+# screen and touchscreen should only be 0 or 1 or NA
+unique(tidy_demographics_leipzig$screen) 
+unique(tidy_demographics_leipzig$touchscreen)
+
+# children should at least be 1 (the tested child) 
+tidy_demographics_leipzig%>%filter(children < 1)
+# household should at least be 2 (the tested child and one adult) 
+tidy_demographics_leipzig%>%filter(household < 2) 
+# household should be larger than children
+tidy_demographics_leipzig%>%filter(children >= household) 
+# youngerchildren should be fewer than children
+tidy_demographics_leipzig%>%filter(younger_children >= children) 
+```
+
+```{r}
 data_nz <- tidy_demographics_nz%>%
-  filter(subjid != "NZ000001")%>%
   left_join(tidy_data_nz%>%rename_all(tolower),by = c("subjid"))%>%
   distinct(subjid, trialnr, .keep_all = TRUE)
-
-data_nz%>%
-  #mutate(age_group = substr(ageinyears, 1,1))%>%
-  #group_by(age)%>%
-  summarise(n = n_distinct(subjid))
-
-# data_nz%>%
-#   group_by(age)%>%
-#   summarise(n())
 ```
@@
 ```{r}
-tidy_data_tur%>%
-  summarise(n = n_distinct(subjID))
-
-tidy_data_tur%>%
-  group_by(subjID)%>%
-  summarise(n = n())
-
-unique(tidy_data_tur$subjID)
+# quality checks
+
+# range of click distance: min = 0; max = 1920
+range(abs(tidy_data_tur$clickDistFromTargetCenterX)) #
+
+# number of trials: everyone should have more than 4 trials.
+tidy_data_tur%>%group_by(subjID)%>%filter(voiceover == F, trialType == "test")%>%summarise(n = n())%>%filter(n<5)
+
 ```
@@
 
+```
+
+```{r}
+# quality checks
+
+# check for typos in subject names
+tidy_demographics_tur%>%
+  filter(!subjid %in% tidy_data_tur$subjID)
+
+# range of ages: should not be below 2.5
+range(tidy_demographics_tur$ageinyears)
+
+# screen and touchscreen should only be 0 or 1 or NA
+unique(tidy_demographics_tur$screen) 
+unique(tidy_demographics_tur$touchscreen)
+
+# children should at least be 1 (the tested child) 
+tidy_demographics_tur%>%filter(children < 1)
+# household should at least be 2 (the tested child and one adult) 
+tidy_demographics_tur%>%filter(household < 2) 
+# household should be larger than children
+tidy_demographics_tur%>%filter(children >= household) 
+# youngerchildren should be fewer than children
+tidy_demographics_tur%>%filter(younger_children >= children) 
 ```
@@
                      "ASYAA200" = "TUR00003"))
-
-data_tur%>%
-  group_by(subjid)%>%
-  summarise(n = n())
-
-data_tur%>%
-  mutate(age_group = substr(ageinyears, 1,1))%>%
-  group_by(age_group)%>%
-  summarise(n = n_distinct(subjid))
-
 ```
@@
 tidy_data_cong <- raw_data_cong %>%
-
+  mutate(subjID = ifelse(subjID == "BD000063", "BY000063", subjID))%>%
   # convert all character vectors into factors
@@
     sample = as.factor("na"),
-    studytype = as.factor("vali"),
+    studytype = as.factor("vali")
   ) %>%select(-touchScreen)#%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
@@
 ```{r}
-tidy_data_cong%>%
-  summarise(n = n_distinct(subjID))
-
-tidy_data_cong%>%
-  group_by(subjID)%>%
-  summarise(n = n())
+# quality checks
+
+# range of click distance: min = 0; max = 1920
+range(abs(tidy_data_cong$clickDistFromTargetCenterX)) #
+
+# number of trials: everyone should have more than 4 trials.
+tidy_data_cong%>%group_by(subjID)%>%filter(voiceover == F, trialType == "test")%>%summarise(n = n())%>%filter(n<5)
 
@@
 ```{r}
+# quality checks
+
+# check for typos in subject names
+tidy_demographics_cong%>%
+  filter(!subjid %in% tidy_data_cong$subjID)
+# one child has no data, no idea where it is
+
+# range of ages: should not be below 2.5
+range(tidy_demographics_cong$ageinyears)
+
+# screen and touchscreen should only be 0 or 1 or NA
+unique(tidy_demographics_cong$screen) 
+unique(tidy_demographics_cong$touchscreen)
+
+# children should at least be 1 (the tested child) 
+tidy_demographics_cong%>%filter(children < 1)
+# household should at least be 2 (the tested child and one adult) 
+tidy_demographics_cong%>%filter(household < 2) 
+# household should be larger than children
+tidy_demographics_cong%>%filter(children >= household) 
+# youngerchildren should be fewer than children
+tidy_demographics_cong%>%filter(younger_children >= children) 
+```
+
+```{r}
 data_cong <- tidy_demographics_cong%>%
@@
   distinct(subjid, trialnr, .keep_all = TRUE)
-
-data_cong%>%
-  group_by(subjid)%>%
-  summarise(n = n())
-
-data_cong%>%
-  group_by(subjid)%>%
-  summarise(n = n(), 
-            mean = mean(abs(clickdistfromtargetcenterx)))
-
 ```
@@
   distinct(subjID, trialNr, .keep_all = T)#%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
-
-unique(tidy_data_uganda$subjID)
-```
-
-```{r}
-tidy_data_uganda%>%
-  filter(trialType == "test")%>%
-  group_by(subjID)%>%
-  summarise(n = n())
-
-tidy_data_uganda%>%
-  filter(trialType == "test")%>%
-  summarise(n = n_distinct(subjID))
+```
+
+```{r}
+# quality checks
+
+# range of click distance: min = 0; max = 1920
+range(abs(tidy_data_uganda$clickDistFromTargetCenterX)) #
+
+# number of trials: everyone should have more than 4 trials.
+tidy_data_uganda%>%group_by(subjID)%>%filter(voiceover == F, trialType == "test")%>%summarise(n = n())%>%filter(n<5)
 
@@
 ```{r}
+# quality checks
+
+# check for typos in subject names
+tidy_demographics_uganda%>%
+  filter(!subjid %in% tidy_data_uganda$subjID)
+
+# one child is missing: ugand041
+
+# range of ages: should not be below 2.5
+range(tidy_demographics_uganda$ageinyears)
+
+# screen and touchscreen should only be 0 or 1 or NA
+unique(tidy_demographics_uganda$screen) 
+unique(tidy_demographics_uganda$touchscreen)
+
+# children should at least be 1 (the tested child) 
+tidy_demographics_uganda%>%filter(children < 1)
+# household should at least be 2 (the tested child and one adult) 
+tidy_demographics_uganda%>%filter(household < 2) 
+# household should be larger than children
+tidy_demographics_uganda%>%filter(children >= household) 
+# youngerchildren should be fewer than children
+tidy_demographics_uganda%>%filter(younger_children >= children)
+
+exclude_uganda <- tidy_demographics_uganda%>%filter(younger_children >= children) %>% pull(subjid)
+```
+
+```{r}
 data_uganda <- tidy_demographics_uganda%>%
   left_join(tidy_data_uganda%>%rename_all(tolower),by = c("subjid"))%>%
+  filter(!subjid %in% exclude_uganda)%>%
   distinct(subjid, trialnr, .keep_all = TRUE)
-
-data_uganda%>%
-  mutate(age_group = substr(ageinyears, 1,1))%>%
-  group_by(age_group)%>%
-  summarise(n = n_distinct(subjid))
-
 ```
@@
 )%>%
-  #mutate(community = paste0("c",as.character(as.numeric(as.factor(community)))))%>%
+  mutate(community = paste0("c",as.character(as.numeric(as.factor(community)))))%>%
   filter(trialtype == "test",
@@
 merge_raw_data%>%
-  filter(children < younger_children, trialnr == 1)
+  filter(children <= younger_children, trialnr == 1)
 
@@
 methods_data <- merge_raw_data%>%
-  select(subjid, community, age_group, ageinyears, trialnr, targetposition,targetcentralityx, clickdistfromtargetcenterx)%>%
-  filter(ageinyears > 1)
+  select(subjid, community, age_group, ageinyears, trialtype, voiceover, trialnr, targetposition,targetcentralityx, clickdistfromtargetcenterx)
 

### 2024-01-29 paper/supplement.Rmd
prep merge

@@
 ---
-title: "Unity in diversity: Children from 17 communities process gaze in similar ways"
+title: "Unity in diversity: shared basic social-cognitive processing in children from from 17 diverse communities"
 subtitle: "Supplementary material"
@@
 library(ggthemes)
+library(ggpubr)
 library(tidyboot)
+library(tidybayes)
 library(maps)
@@
 library(papaja)
+library(coda)
+library(ggrepel)
 
@@
 
+set.seed(1337)
 ```
@@
 
-A total of `r sum(as.numeric(demtab$N))` children between `r round(min(data$ageinyears), 2)` and `r round(max(data$ageinyears), 2)` provided data for the study.
-Children lived in `r n_distinct(data$community)` different communities, located in `r n_distinct(data$country)` different countries.
-Table \@ref(tab:demtable) gives the sample size per community together with some basic demographic information.
-Additional children were recruited but did not contribute data to the study.
-The recruitment strategy varied from community to community and we therefore cannot provide detailed information about the number of children that were excluded.
-All children who contributed at least five valid data points were included in the final sample.
-We did not exclude any participants for performance reasons.
-A detailed description of each site and the way children were recruited can be found below.
-
 ```{r}
@@
 
-```{r figpred1, include = T, fig.align = "center", fig.cap = "Age distribution (left) and prevalence of different types of technology by community.
+```{r figpred1, include = T, fig.align = "center", fig.cap = "A) Age distribution and B) prevalence of different types of technology by community.
 Left: dots show individual data points.
-Right: color shows the proportion of children with access to screens or touchscreens."}
-techpred <- plot_grid(page, ppred, align = "h", rel_widths = c(1, 0.5))
-
-ggsave(plot = techpred, "../visuals/techpred.png", height = 10, width = 10, scale = 1)
+Right: color shows the proportion of children with access to screens or touchscreens.", out.width="100%"}
+techpred <- plot_grid(page, ppred, rel_widths = c(1, 0.5),align = "h", labels = c("A", "B"))
+
+ggsave(plot = techpred, "../visuals/techpred.png",  height = 7, width = 10, scale = 1)
 
@@
 ```
+
+A total of `r sum(as.numeric(demtab$N))` children between `r round(min(data$ageinyears), 2)` and `r round(max(data$ageinyears), 2)` provided data for the study.
+Children lived in `r n_distinct(data$community)` different communities, located in `r n_distinct(data$country)` different countries.
+Table \@ref(tab:demtable) gives the sample size per community together with some basic demographic information.
+Figure \@ref(fig:figpred1)A shows the age distribution in each setting.
+Additional children were recruited but did not contribute data to the study.
+The recruitment strategy varied from community to community and we therefore cannot provide detailed information about the number of children that were excluded.
+All children who contributed at least four valid data points were included in the final sample.
+We did not exclude any participants for performance reasons.
+A detailed description of each site and the way children were recruited can be found below.
 
@@
 Its average annual temperature is 11 to 14oC.
-The coldest month in Beijing is January, with an average temperature of -9 to -4oC; the hottest month is July, with an average of 25oC.
+The coldest month in Beijing is January, with an average temperature of -9 to -4°C; the hottest month is July, with an average of 25°C.
 Around 75 percent of its annual precipitation occurs in summer, with the heaviest rainfall in July and August.
@@
 In big cities, such as Beijing, the involvement of grandparents in grandchild care is especially helpful since it relieves the high-pressure of a two-career family.
-BTW, China fully implemented the “two-child-per-family” policy in 2016, there are usually one or two children per family now in Beijing.
+Since China fully implemented the “two-child-per-family” policy in 2016, there are now usually one or two children per family in Beijing.
 
@@
 Smartphones and other touchscreen devices are prevalent in most families in Beijing and are used widely for education, communication, and entertainment.
-In 2022, almost every Chinese netizen accessed the internet via mobile devices and Beijing has been fully covered by ultrafast 5G signals.
+In 2022, almost every Chinese citizen accessed the internet via mobile devices and Beijing has been fully covered by ultra fast 5G signals.
 
@@
 Three quarters of the poor live in rural areas.
-As in other African countries there is a strong trend of movement from rural arears to urban centers whereby men migrate more often and women remain behind in villages.
+As in other African countries there is a strong trend of movement from rural areas to urban centers whereby men migrate more often and women remain behind in villages.
 The housing style in rural areas vary a lot by ethnic group.
@@
 Additionally, sugarcane and coffee cultivation contribute significantly to the local economy, with the Kinyara Sugar Company playing a pivotal role in sugarcane harvesting.
+
 Living conditions in the community are characterized by extended families residing together, with an average of 10 people under one roof.
@@
 
-Ocuilan is a municipality located in the centre south of Mexico with a population of 36,223 inhabitants, distributed in 48 towns in an area of 344.84 km2  inside the Mexican State.
-(Ocuilan, n.d.) Geographically Ocuilan has an altitude of between 1000 to 2,600 m situated 80 km south of Mexico City.
+Ocuilan is a municipality located in the centre south of Mexico with a population of 36,223 inhabitants, distributed in 48 towns in an area of 344.84 km2  inside the Mexican State (Ocuilan, n.d.).
+Geographically Ocuilan has an altitude of between 1000 to 2,600 m situated 80 km south of Mexico City.
 (INEGI,2010)
@@
 
-dempred <- data%>%
-  group_by(community,continent)%>%
-  mutate(older_children = children - 1 - younger_children)%>%
-  distinct(subjid, .keep_all = T)%>%
-  select(subjid, community, continent, older_children,children, younger_children, household)%>%
-  pivot_longer(names_to = "dem", values_to = "value", cols = c(older_children,children, younger_children, household))%>%
-  mutate(dem = recode(dem,
-                      older_children = "older children",
-                            younger_children = "younger children"),
-         dem = factor(dem, levels = c("household", "children", "older children", "younger children")))%>%
-  ggplot(aes(y = community, x = value))+
-  facet_grid(continent~dem, scales = "free", space = "free_y")+
-  geom_density_ridges(
-    jittered_points = TRUE,
-    position = position_points_jitter(width = 0.25, height = 0),
-    point_shape = '|',  point_alpha = 1, alpha = 0.7,
-  )+
+# dempred <- data%>%
+#   group_by(community,continent)%>%
+#   mutate(older_children = children - 1 - younger_children)%>%
+#   distinct(subjid, .keep_all = T)%>%
+#   select(subjid, community, continent, older_children,children, younger_children, household)%>%
+#   pivot_longer(names_to = "dem", values_to = "value", cols = c(older_children,children, younger_children, household))%>%
+#   mutate(dem = recode(dem,
+#                       older_children = "older children",
+#                             younger_children = "younger children"),
+#          dem = factor(dem, levels = c("household", "children", "older children", "younger children")))%>%
+#   ggplot(aes(y = community, x = value))+
+#   facet_grid(continent~dem, scales = "free", space = "free_y")+
 #   geom_density_ridges(
- #    col = "white",
- #    jittered_points = TRUE, quantile_lines = TRUE, scale = 0.9, alpha = 0.7,
- #    vline_size = 1, vline_color = "red",
- #    point_size = 0.4, point_alpha = 1,
- #    position = position_raincloud(adjust_vlines = TRUE)
- #  )
-  labs(x = "No. of individuals", y= "")+
-  #geom_jitter(alpha = .1, width = 0.1, height = 0.1)+
-  theme_few()
-
-ggsave(plot = dempred, "../visuals/dempred.png", height = 8, width = 14, scale = 1.1)
+#     jittered_points = TRUE,
+#     position = position_points_jitter(width = 0.25, height = 0),
+#     point_shape = '|',  point_alpha = 1, alpha = 0.7,
+#   )+
+#  # geom_density_ridges(
+#  #    col = "white",
+#  #    jittered_points = TRUE, quantile_lines = TRUE, scale = 0.9, alpha = 0.7,
+#  #    vline_size = 1, vline_color = "red",
+#  #    point_size = 0.4, point_alpha = 1,
+#  #    position = position_raincloud(adjust_vlines = TRUE)
+#  #  )
+#   labs(x = "No. of individuals", y= "")+
+#   #geom_jitter(alpha = .1, width = 0.1, height = 0.1)+
+#   theme_few()
+# 
+# ggsave(plot = dempred, "../visuals/dempred.png", height = 8, width = 14, scale = 1.1)
 
@@
 
-```{r figagents, include = T, fig.align = "center", fig.cap = "Screenshot from the task.
+```{r figtask, include = T, fig.align = "center", fig.cap = "Screenshot from the task.
 The scene depicts the choice phase in a test trial.
@@
 Participants simply had to touch the visible balloon.
-In fam2 trials, the trajectory of the balloon was visible but it landed behind a small barrier (usually a hedge - see Figure XXB).
+In fam2 trials, the trajectory of the balloon was visible but it landed behind a small barrier (usually a hedge - see Figure \@ref(fig:task)).
 Thus, participants needed to touch the hedge where they saw the balloon land.
@@
 
+We analysed the data in three steps.
+First, we tested whether there was substantial cross-cultural variation in performance.
+Second, we looked for signatures in the data that informed the hypothesis that children processed gaze in the same way across cultural settings.
+Finally, we related performance in the task (on an individual level) to aspects of everyday experience, in particular the exposure to screen-based technology and social interaction (approximated by household composition).
+
+We used Bayesian Regression models fit in `R` [] using the package `brms` [@burkner2019bayesian] for all analyses except the cognitive models, which were implemented in the probabilistic programming language `webppl` [@dippl].
+For regression models, we used the default priors built in to `brms`.
+The dependent variable in all regression models was imprecision, that is, the absolute distance between the true location of the balloon (to x-coordinate of its center) and the location where the participant touched the screen.
+We used a Log-normal distribution to model the data because the natural lower bound for imprecision is zero and the data was right skewed with a long tail to the right.
+Numeric predictors that entered the models were scaled to have a mean of zero and a standard deviation of 1.
+For each model we ran four chains with 6000 iterations, removing the first 2000 for burn-in.
+All models had converging chains (Rhat values < 1.01).
+Details specific to each analysis can be found below.
+The analysis code can be found in the online repository associated with the study (link).
+
+We pre-registered an analysis plan at https://osf.io/tdsvc.
+The analyses reported below follow the same logical as the pre-registered analyses but they differ substantially in detail.
+The main difference lies in the random effects structure we used in the models.
+In the pre-registration, we did not include random slopes for target centrality (i.e.
+the distance of the location where the balloon landed from the center of the screen), neither within subject nor within cultural setting.
+Instead, we included random slopes for trial within subject.
+We decided to change this and remove random slopes for trial but include them for target centrality.
+The reasons were as follows: trail effects in the sense of learning across trials were unlikely because participants did not receive differential feedback.
+Furthermore, in multiple studies with the same task since the registration we never found any trial effects [@prein2023tango; @prein2023variation].
+We therefore removed trial from the models completely to reduce model complexity.
+On the other hand, we included random slopes for target centrality to be able to look at cross-cultural variation.
+The cognitive model was not mentioned in the pre-registration because it is a more recent development [see @prein2023variation].
+
+## Cross-cultural variation
+
+As a first step, we investigated cross-cultural variation in performance.
+As stated in the pre-registration, this can be problematic when including random intercepts for participant and cultural setting at the same time.
+Participants are fully nested within cultural setting.
+If there was an effect of cultural setting, we would expect participant random intercepts to cluster by cultural setting.
+This clustering would appear whether or not cultural setting would be included in the model as a random effect or not -- the only difference would be if the participant random intercepts are estimated as a deviation from a grand intercept or a culture-specific one.
+Standard metrics such as `WAIC` or `LOO` would penalize the model with additional intercept for cultural setting for having additional parameters that do not help to improve predictive accuracy.
+
+To get around this problem, we used a cross-validation procedure [see e.g., @stengelin2023children].
+For each cultural setting we randomly sampled a data set that was 5/6 the size of the full data set (training data).
+Then we fit the model to this training data and used the estimated model parameters to predict the remaining 1/6 of the data (testing data).
+We then compared the model predictions from the different models by computing the mean difference between the true and predicted imprecision, over all trials in the testing data set.
+This approach gets around the problem mentioned in above because the model predicts a new dataset for which the individual random intercepts are unknown.
+Clustering by culture could therefore only be predicted by a model that included culture as a predictor.
+We repeated the cross-validation procedure 100 times and counted which model performed best most often.
+
+We compared the following models (`brms` notation):
+
+`null`:
+* `imprecision ~ age + target_centrality + (target_centrality | participant)`
+
+`culture`:
+* `imprecision ~ age + target_centrality + (target_centrality | participant) + (target_centrality | culture)`
+
+`culture_age`: 
+* `imprecision ~ age + target_centrality + (target_centrality | participant) + (age + target_centrality | culture)`
+
+```{r}
+mdata <- data%>%
+  ungroup()%>%
+  mutate(older_children = children - 1 - younger_children)%>%
+  mutate(ageinyears = scale(ageinyears),
+         targetcentralityx = scale(targetcentralityx),
+         trialnr = scale(trialnr),
+         touchscreen = factor(touchscreen),
+         screen = factor(screen),
+         click = abs(clickdistfromtargetcenterx))
+```
+
+```{r}
+bm_null <- brm(click ~ ageinyears + targetcentralityx + (trialnr + targetcentralityx|subjid),
+                              data   = mdata,
+                              family = lognormal(),
+                              warmup = 2000,
+                              iter   = 6000,
+                              chains = 4,
+                              cores  = 4,
+                              threads = threading(8),
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")
+
+saveRDS(bm_null, "../saves/bm_cv_null.rds")
+
+bm_cult <- brm(click ~ ageinyears + targetcentralityx + (trialnr + targetcentralityx|subjid)+ (1 |community),
+                              data   = mdata,
+                              family = lognormal(),
+                              warmup = 2000,
+                              iter   = 6000,
+                              chains = 4,
+                              cores  = 4,
+                              threads = threading(8),
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")
+
+saveRDS(bm_cult, "../saves/bm_cv_cult.rds")
+
+bm_cult_age <- brm(click ~ ageinyears + targetcentralityx + (trialnr + targetcentralityx|subjid)+ (ageinyears + targetcentralityx |community),
+                              data   = mdata,
+                              family = lognormal(),
+                              warmup = 2000,
+                              iter   = 6000,
+                              chains = 4,
+                              cores  = 4,
+                              threads = threading(8),
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr")
+
+saveRDS(bm_cult_age, "../saves/bm_cv_cult_age.rds")
+
+fixef(bm_cult_age)%>%as_tibble(rownames = "term")%>%mutate_if(is.numeric, round, 2)%>%saveRDS(.,"../saves/cult_age_fix.rds")
+
+```
+
+```{r}
+six_fold_cross_validation <- function(data, m1, m2, m3, m4, repeats) {
+
+  N_ids = n_distinct(data$subjid)
+#Prepare results DF
+  results <- tibble(
+    m1_score=numeric(), 
+    m2_score=numeric(), 
+    m3_score=numeric(), 
+    #m4_score=numeric(),
+
+    #m4_beats_m3=logical(), 
+    #m4_beats_m2=logical(), 
+    #m4_beats_m1=logical(), 
+    m3_beats_m2=logical(), 
+    m3_beats_m1=logical(), 
+    m2_beats_m1=logical(),
+
+    m1 = character(), 
+    m2 = character(), 
+    m3 = character(),
+    #m4 = character()
+    )
+
+#Repeat the whole shebang several times
+  for(i in 1:repeats) {
+
+  # Split dataset into 6 bins
+  bin_data <- data%>%distinct(community, subjid)%>%group_by(community) %>% mutate(bin = rep(1:6, length.out = n()))
+
+for(j in 1:6) {
+    # Use bin j as "hold out" data
+    testing_ids <- bin_data%>%filter(bin == j)%>%pull(subjid)
+    training_ids <- bin_data%>%filter(bin != j)%>%pull(subjid)
+    # Safety check - is partition complete and disjoint?
+    stopifnot(length(testing_ids) + length(training_ids) == N_ids)
+    stopifnot(length(intersect(testing_ids, training_ids)) == 0)
+# Create two separate dataframes
+    testing_data <- filter(data, subjid %in% testing_ids)
+    training_data <- filter(data, subjid %in% training_ids)
+
+    # Train models
+    up_m1 <- update(m1, newdata=training_data, cores=4,backend = "cmdstanr", threads = threading(8))
+    up_m2 <- update(m2, newdata=training_data, cores=4,backend = "cmdstanr", threads = threading(8))
+    up_m3 <- update(m3, newdata=training_data, cores=4,backend = "cmdstanr", threads = threading(8))
+    #up_m4 <- update(m4, newdata=training_data, cores=4,backend = "cmdstanr", threads = threading(8))
+
+    # Sample predictions
+    preds_m1 <- posterior_predict(up_m1, newdata=testing_data, allow_new_levels=TRUE, sample_new_levels="gaussian")
+    preds_m2 <- posterior_predict(up_m2, newdata=testing_data, allow_new_levels=TRUE, sample_new_levels="gaussian")
+    preds_m3 <- posterior_predict(up_m3, newdata=testing_data, allow_new_levels=TRUE, sample_new_levels="gaussian")
+    #preds_m4 <- posterior_predict(up_m4, newdata=testing_data, allow_new_levels=TRUE, sample_new_levels="gaussian")
+
+    # Evaluate predictive accuracy
+  score_m1 <- mean(sqrt(colMeans((testing_data$click - t(preds_m1))**2)))
+  score_m2 <- mean(sqrt(colMeans((testing_data$click - t(preds_m2))**2)))
+  score_m3 <- mean(sqrt(colMeans((testing_data$click - t(preds_m3))**2)))
+  #score_m4 <- mean(sqrt(colMeans((testing_data$click - t(preds_m4))**2)))
+
+  m1_name <-  as.character(substitute(m1))
+  m2_name <-  as.character(substitute(m2))
+  m3_name <-  as.character(substitute(m3))
+  #m4_name <-  as.character(substitute(m4))
+
+    # Record results
+    results <- add_row(results,
+
+                       repeats = i, 
+                       bin = j,
+
+                       m1_score = score_m1,
+                       m2_score = score_m2,
+                       m3_score = score_m3,
+                       #m4_score = score_m4,
+
+                       # m4_beats_m3 = m4_score < m3_score,
+                       # m4_beats_m2 = m4_score < m2_score,
+                       # m4_beats_m2 = m4_score < m1_score,
+                       m3_beats_m2 = m3_score < m2_score,
+                       m3_beats_m1 = m3_score < m1_score,
+                       m2_beats_m1 = m2_score < m1_score,
+
+                       m1  = m1_name,
+                       m2 = m2_name,
+                       m3 = m3_name,
+                       #m4 = m4_name
+                       )
+ }
+  }
+  return(results)
+}
+```
+
+```{r}
+cv_cult <- six_fold_cross_validation(scdata, bm_base, bm_cult, bm_cult_age, 1)
+```
+
+We pre-registered the inclusion of additional models which did not include age as a predictor.
+To reduce computational demands and given that we did not implement this approach to determine the effect of age, we decided to leave these models out so that all models included age as a predictor.
+The main questions were, therefore, whether there were systematic absolute (model `culture`) or also developmental (model `culture_age`) differences between cultural settings.
+
+The results showed that the `culture_age` model made, by far, the best predictions and outperformed the `culture` model in `r mean(cv_cult$m3_beats_m2)*100`% and the `null` model in `r mean(cv_cult$m3_beats_m1)*100`% of cases.
+Furthermore, the `culture` model outperformed the `null` model in `r mean(cv_cult$m2_beats_m1)*100` % of cases.
+This suggests that there were substantial absolute and developmental differences between cultural settings (see Figure \@ref(fig:figdev)A).
+
+## Processing signatures
+
+In the second analysis focused on signatures in the data that suggest that children in all cultural settings use similar cognitive processes to infer the location of the balloon.
+The first -- weaker -- signature was simply an increase in performance with age.
+The second -- stronger -- signature was a strong effect of target centrality.
+That is, the further away from the center the balloon lands, the more imprecise should participants be.
+This second signature is derived from the model by the cognitive model introduced in @prein2023variation.
+It predicts that trials in which the agent looks further away from the center (i.e.
+to the left or right side of the screen) result in higher levels of imprecision compared to trials in which the agent looks closer to the middle.
+
+This prediction is best understood by considering a similar phenomenon: pointing a torch light to a flat surface.
+The width of the light beam represents each individual's level of uncertainty in vector estimation and is represented in the model as a normal distribution around the true gaze vector with a participant specific standard deviation.
+On each trial, the model assumes that the participant samples a vector from this distribution to infer the location of the balloon.
+The smaller the standard deviation -- -- the narrower the light beam --, the more precise on average the participant is.
+Now, when the torch is directed straight down, the light beam is concentrated in a relatively small area.
+When the torch is rotated to the side, the the light from one half of the cone must travel further than the light from the other half to reach the surface.
+As a consequence, the light is spread over a wider area.
+This is true no matter how wide the cone (how large the standard deviation) is.
+
+```{r}
+draws <- bind_rows(
+as_draws_df(bm_cult_age)%>%
+  select(contains("ageinyears"))%>%
+  select(contains("ageinyears"))%>%
+  select(-contains("sd"))%>%
+  select(-contains("cor"))%>%
+  pivot_longer(cols = contains("ageinyears]"), names_to = "community", values_to = "value")%>%
+  mutate(post = value + b_ageinyears,
+         community = str_remove(community, "r_community"),
+         community = str_remove(community, ",ageinyears]"),
+         community = str_remove(community, "\\["))%>%
+  select(community, post)%>%
+  mutate(type = "ageinyears"),
+
+as_draws_df(bm_cult_age)%>%
+  select(contains("targetcentralityx"))%>%
+  select(contains("targetcentralityx"))%>%
+  select(-contains("sd"))%>%
+  select(-contains("cor"))%>%
+  select(-contains("subjid"))%>%
+  pivot_longer(cols = contains("targetcentralityx]"), names_to = "community", values_to = "value")%>%
+  mutate(post = value + b_targetcentralityx,
+         community = str_remove(community, "r_community"),
+         community = str_remove(community, ",targetcentralityx]"),
+         community = str_remove(community, "\\["))%>%
+  select(community, post)%>%
+  mutate(type = "targetcentrality")
+)%>%
+  mutate(community = str_replace(community, "\\.", " "),
+         community= str_remove(site,"\\."))
+
+pdraws <- draws%>%
+  mutate(community = recode(community, 
+                            "Auckland (NewZealand)" = "Auckland (New Zealand)",
+                            "BaYaka (Rep.Congo)" = "BaYaka (Rep. Congo)",
+                            "Bandongo (Rep.Congo)" = "Bandongo (Rep. Congo)",
+                            "Buenos Aires(Argentina)" = "Buenos Aires (Argentina)"))%>%
+  left_join(data%>%distinct(community, continent))%>%
+  mutate(continent = factor(continent, levels = c("America", "Africa", "Europe", "Asia", "Oceania"), ordered = T))
+
+saveRDS(pdraws, "../saves/pdraws.rds")
+
+post_agg <- pdraws%>%
+  group_by(community, type)%>%
+  summarise(mean = mean(post),
+            lci = hdi_lower(post),
+            uci = hdi_upper(post))
+
+saveRDS(post_agg, "../saves/post_agg.rds")
+```
+
+```{r figpreds, include = T, fig.align = "center", fig.cap = "Posterior distributions of model estimates for the poredictor variables by cultural setting.", out.width="100%"}
+
+pdraws <- readRDS("../saves/pdraws.rds")%>%
+  mutate(type = recode(type,
+                       ageinyears = "Age",
+                       targetcentrality = "Target centrality"),
+         type = factor(type, levels = c("Age","Target centrality")))
+
+ppred <- ggplot(pdraws, aes(x= post, y = community))+
+
+  geom_density_ridges(col = "white", alpha = .75, fill = "grey")+
+  geom_vline(xintercept = 0, lty = 3)+
+  facet_grid(continent~type, scales = "free", space = "free_y")+
+  #stat_pointinterval(size = 0.1)+
+  #xlim(-0.15, 0.1)+
+  labs(x = "Posterior model estimate", y= "")+
+  theme_few()+
+  theme( strip.text.y.right = element_text(angle = 0))
+
+ggsave(plot = ppred, "../visuals/pred.png", height = 6, width = 12, scale = 1)
+
+knitr::include_graphics("../visuals/pred.png")
+
+```
+
+To test these predictions, we inspected the parameter estimates for age and target centrality in the "winning" `culture_age` model described in the previous sections.
+We found strong main effects of age ($\beta$ = ) and target centrality ($\beta$ =).
+Figure \@ref(fig:figpreds) visualizes the posterior distributions for each cultural setting and shows that -- despite variation in strength -- there was a strong effect of age and target centrality in all cultural settings.
+
+Another way to look at these signatures is to visualize the group-level developmental trajectories and the aggregated performance at different areas of the screen.
+Figure \@ref(fig:figdev)A shows that children got more precise with age in all cultural settings.
+Figure \@ref(fig:figdev)B shows the expected u-shaped pattern: the closer the balloon lands to the center of the screen (bins 5 and 6) the more precise children are in all cultural settings.
+
+```{r}
+devdata <- data%>%
+  mutate(click = abs(clickdistfromtargetcenterx))%>%
+  group_by(subjid, continent,community, ageinyears)%>%
+  summarise(mean_click = mean(click))%>%
+  ungroup()%>%
+  mutate(ageinyears = ageinyears - min(ageinyears))
+
+bm_dev <- brm(mean_click ~ ageinyears + (ageinyears |community),
+                              data   = devdata,
+                              family = lognormal(),
+                              warmup = 2000,
+                              iter   = 4000,
+                              chains = 4,
+                              cores  = 4,
+             control = list(adapt_delta = 0.95))
+
+ndata <- devdata%>%
+  distinct(continent, community, ageinyears)
+
+post <- fitted(bm_dev, newdata = ndata, re_formula =~(ageinyears|community))%>%
+  as_tibble() %>%
+  bind_cols(ndata)%>%
+  mutate(ageinyears = ageinyears + min(data$ageinyears))
+```
+
+```{r}
+tc_agg_data<- data%>%
+  mutate(targetposition = factor(targetposition, levels = c(1:10)))%>%
+  group_by(continent, community, targetposition)%>%
+  tidyboot_mean(col= abs(clickdistfromtargetcenterx))
+
+tam <- tc_agg_data%>%
+  filter(continent == "America")%>%
+  ggplot(., aes(x = targetposition, y = mean, col = community))+
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
+  labs(x = "", y = "")+
+  scale_color_colorblind(name = "", guide = "none")+
+  facet_grid(continent~.)+
+  ylim(0,1000)+
+  theme_few()
+
+taf <- tc_agg_data%>%
+  filter(continent == "Africa")%>%
+  ggplot(., aes(x = targetposition, y = mean, col = community))+
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
+  labs(x = "", y = "")+
+  scale_color_colorblind(name = "", guide = "none")+
+  facet_grid(continent~.)+
+  ylim(0,1000)+
+  theme_few()
+
+teu <- tc_agg_data%>%
+  filter(continent == "Europe")%>%
+  ggplot(., aes(x = targetposition, y = mean, col = community))+
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
+  labs(x = "", y = "")+
+  scale_color_colorblind(name = "", guide = "none")+
+  facet_grid(continent~.)+
+  ylim(0,1000)+
+  theme_few()
+
+tas <- tc_agg_data%>%
+  filter(continent == "Asia")%>%
+  ggplot(., aes(x = targetposition, y = mean, col = community))+
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
+  labs(x = "", y = "")+
+  scale_color_colorblind(name = "", guide = "none")+
+  facet_grid(continent~.)+
+  ylim(0,1000)+
+  theme_few()
+
+toc <- tc_agg_data%>%
+  filter(continent == "Oceania")%>%
+  ggplot(., aes(x = targetposition, y = mean, col = community))+
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
+  labs(x = "Target position (binned)", y = "")+
+  scale_color_colorblind(name = "", guide = "none")+
+  facet_grid(continent~.)+
+  ylim(0,1000)+
+  theme_few()
+
+```
+
+```{r}
+am <- ggplot()+
+  geom_point(data = mdata%>%filter(continent == "America"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
+  geom_smooth(data = post%>%filter(continent == "America"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
+  theme_few()+
+  scale_fill_colorblind(name = "")+
+  scale_color_colorblind(name = "")+
+  labs(x = "", y="Imprecision")+
+  scale_x_continuous(limits = c(2,10))+
+  scale_y_continuous(limits = c(0,1000))+
+  facet_grid(continent~.)+
+  theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))
+
+af <- ggplot()+
+  geom_point(data = mdata%>%filter(continent == "Africa"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
+  geom_smooth(data = post%>%filter(continent == "Africa"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
+  theme_few()+
+  scale_fill_colorblind(name = "")+
+  scale_color_colorblind(name = "")+
+  labs(x = "", y="")+
+    scale_x_continuous(limits = c(2,10))+
+  scale_y_continuous(limits = c(0,1000))+
+  facet_grid(continent~.)+
+  theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))
+
+eu <- ggplot()+
+  geom_point(data = mdata%>%filter(continent == "Europe"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
+  geom_smooth(data = post%>%filter(continent == "Europe"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
+  theme_few()+
+  scale_fill_colorblind(name = "")+
+  scale_color_colorblind(name = "")+
+  labs(x = "", y="")+
+    scale_x_continuous(limits = c(2,10))+
+  scale_y_continuous(limits = c(0,1000))+
+  facet_grid(continent~.)+
+  theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))
+
+as <- ggplot()+
+  geom_point(data = mdata%>%filter(continent == "Asia"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
+  geom_smooth(data = post%>%filter(continent == "Asia"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
+  theme_few()+
+  scale_fill_colorblind(name = "")+
+  scale_color_colorblind(name = "")+
+  labs(x = "", y="")+
+    scale_x_continuous(limits = c(2,10))+
+  scale_y_continuous(limits = c(0,1000))+
+  facet_grid(continent~.)+
+  theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))
+
+oc <- ggplot()+
+  geom_point(data = mdata%>%filter(continent == "Oceania"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
+  geom_smooth(data = post%>%filter(continent == "Oceania"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
+  theme_few()+
+  scale_fill_colorblind(name = "")+
+  scale_color_colorblind(name = "")+
+  labs(x = "Age", y="")+
+    scale_x_continuous(limits = c(2,10))+
+  scale_y_continuous(limits = c(0,1000))+
+  facet_grid(continent~.)+
+  theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))
+```
+
+```{r figdev, include = T, fig.align = "center", fig.cap = "A) Developmental trajectories by cultural settings.
+Transparent dots show aggregated data for each individual.
+The color dentoes the different cultural settings.
+The developmental trajectories are predicted based on a model of the data aggregated for each participant.
+B) Performance by screen section and cultural setting.
+Each bin covers 1/10th of the screen.
+Points show means and eroor bars 95\\% confidence intervals for the data within that bin aggregated across participants.", out.width="100%"}
+# plot_grid(
+#   plot_grid(am, tam, nrow = 1, align = "h", rel_widths = c(2,1)),
+#   plot_grid(af, taf, nrow = 1, align = "h", rel_widths = c(2,1)),
+#   plot_grid(eu, teu, nrow = 1, align = "h", rel_widths = c(2,1)),
+#   plot_grid(as, tas, nrow = 1, align = "h", rel_widths = c(2,1)),
+#   plot_grid(oc, toc, nrow = 1, align = "h", rel_widths = c(2,1)),
+#   align = "v",
+#   ncol = 1
+#   )
+
+pvis_pred <- plot_grid(
+  plot_grid(am, af, eu, as,oc, ncol = 1, align = "v"),
+  plot_grid(tam, taf, teu, tas,toc, ncol = 1, align = "v"),
+  nrow = 1,
+  labels = c("A","B"),
+  rel_widths = c(1.75,1)
+)
+
+ggsave(plot = pvis_pred, "../visuals/pvis_pred.png", height = 10, width = 6, scale = 1.5)
+
+knitr::include_graphics("../visuals/pvis_pred.png")
+
+```
+
+### Cognitive model
+
+The u-shaped pattern reported above may also arise if participants did not process the agent's gaze at all but only selected the middle of the screen.
+In such a scenario, the further away the balloon lands from the center, the further away it is from the center and the participant's click.
+This would also result in a u-shaped pattern and a strong effect of target centrality.
+It would not, however, predict a developmental improvement in performance.
+Nevertheless, we wanted to quantify the evidence in favor of the vector-based gaze estimation model compared to this alternative center-bias model.
+We also added a random guessing model to the comparison according to which participants also ignored the agents gaze but simply touched random locations on the screen.
+
+The vector-based gaze estimation model has been described in detail in @prein2023variation.
+In brief, the it inversely models the process generating clicks based on observed eye movements.
+Formally, the model is defined as:
+
+\begin{equation}
+    P(\theta | x_c, \alpha_l, \alpha_r) \propto P(x_c | \alpha_l, \alpha_r, \theta)P(\theta)
+\end{equation}
+
+Here, $\theta$ represents an individual's cognitive ability to locate the focus of the agent's attention, $x_c$ represents the clicked coordinate, and $\alpha_l$ and $\alpha_r$ correspond to the left and right pupil angles (each defined as the angle between a line connecting the center of the eye to the pupil and a line extended vertically downward from the center of the eye).
+
+The basic assumption in this model is that participants click on the screen location where they think the agent is looking.
+The true eye angles ($\alpha_l$ and $\alpha_r$) are not directly observable and are estimated with noise, yielding $\hat{\alpha_l}$ and $\hat{\alpha_r}$.
+
+Each click $x_c$ implies a "matched pair" of estimated pupil angles $\hat{\alpha_l}$ and $\hat{\alpha_r}$, with the constraint that the lines extended along those two angles meet at the precise location of where the target is believed to be.
+As a consequence, we can rewrite the likelihood function of the model as:
+
+\begin{equation}
+P(x_c | \alpha_l, \alpha_r, \theta) \propto P(\hat{\alpha_l}, \hat{\alpha_r} | \alpha_l, \alpha_r, \theta) P(x_c)
+\end{equation}
+
+$P(x_c)$ is a prior over potential target locations.
+Because the target was last visible in the screen and because the agent was located in the center, we assumed that participants have an a priori expectation that the target will land close to the middle.
+We estimated the strength of this center bias (i.e., the standard deviation of a Normal distribution around the screen center) based on the data: $P(x_c) \sim \mathcal{N}(960, \sigma^p)$.
+
+The primary inferential task for participants is therefore to estimate the pupil angles ($\hat{\alpha_l}$ and $\hat{\alpha_r}$), i.e., to sample from the term $P(\hat{\alpha_l}, \hat{\alpha_r} | \alpha_l, \alpha_r, \theta)$.
+Here, we assumed that the pair of estimated pupil angles were sampled from a probability distribution which is the product of two Normal distributions of equal variance, $\sigma_v$, centered on the true pupil angles:
+
+\begin{equation}
+P(\hat{\alpha_l}, \hat{\alpha_r} | \alpha_l, \alpha_r, \theta) \propto \phi(\hat{\alpha}_l ; \alpha_l, \sigma_v)\phi(\hat{\alpha}_r ; \alpha_r, \sigma_v),
+\end{equation}
+
+Here, $\sigma_v$ plays a crucial role in determining the accuracy with which participants estimate pupil angles.
+Smaller values of $\sigma_v$ result in a narrow distribution around the pupil angle, making clicks far away from the target less likely.
+Conversely, larger values for $\sigma_v$ lead to a wider distribution, making clicks far away from the target more likely.
+To circle back to the analogy introduced above, $\sigma_v$ corresponds to the width of the light beam.
+Thus, the goal of the model was to estimate participant-specific values for $\sigma_v$: $\sigma_{v_i}$.
+These participant specific values were sampled from a normal distribution centered around the value we expected for a child given their age ($age_i$): $\sigma_{v_i} \sim e^{\mathcal{N}(\sigma_{v_{age}}, \sigma^{\sigma_{v_{age}}}})$.
+(Values were exponentiated to always be positive).
+$\sigma_{v_{age}}$ in turn was defined via a simple regression model: $\sigma_{v_{age}} = \beta_0^{\sigma_{v_{age}}} + age_i \cdot \beta_1^{\sigma_{v_{age}}}$.
+Where $\beta_0^{\sigma_{v_{age}}}$ and $\beta_1^{\sigma_{v_{age}}}$ represent the population-level intercept and slope that together describe a curve that represents the average developmental pattern.
+
+To summarize, the model assumes that participant's clicks are generated by a process that relies on noisy estimates of the agent's gaze direction.
+The precision, with which the gaze direction is estimated, varies between participants and increases with development.
+
+The two alternative models assume that participants ignore the agent's gaze completely, instead they are assumed to follow simple heuristics.
+According to the center bias model they always try to click in the center of the screen: $P(x_c) \sim \mathcal{N}(960, 160)$.
+(960 is the x-coordinate of the center and 160 is the width of the balloon).
+According to the random guessing model, they randomly click coordinates on the screen: $P(x_c) \sim \mathcal{U}(0, 1920)$.
+
+All models were run separately for each cultural setting.
+The code to run the models can be found in the associated online repository.
+We also refer to this source for information on the prior distributions for all model parameters.
+
+We compared models based on the marginal likelihood of the data for each model, which represents the likelihood of the data while averaging over the prior distribution on parameters.
+The pair-wise ratio of marginal likelihoods for two models is known as the Bayes Factor.
+Bayes Factors are a quantitative measure of the predictive quality of a model, taking into account the possible values of the model parameters weighted by their prior probabilities.
+The incorporation of the prior distribution over parameters in the averaging process implicitly considers model complexity: models with more parameters typically exhibit broader prior distributions over parameter values and broader prior distribution can attenuate the potential gains in predictive accuracy that a model with more parameters might otherwise achieve [@lee2014bayesian].
+
+Table \@ref(tab:bftable) shows the Bayes Factors in favor of the vector-based gaze estimation model for each cultural setting.
+The evidence in favor of the gaze model compared to the two alternative models was clear (all BF > 1 000 000 000 000 000).
+This result clearly rules out that the u-shaped pattern in the data was the result of participants always clicking the center instead of following gaze.
+
+```{r bftable, echo=F}
+bf <- readRDS("../model/output/bf_comparison.rds")%>%
+  mutate_if(is.numeric, format, digits = 2, nsmall = 2)
+
+knitr::kable(bf,
+             col.names = c("Community", "log(BF~gaze,center~)", "log(BF~gaze,guess~)"),
+             caption = "Log Bayes Factors in favor of the gaze model compared to two alternative models.", 
+             )
+```
+
+## Experiential predictors
+
+```{r}
+scdata <- mdata%>%
+  group_by(subjid, community, ageinyears, touchscreen, household, children, younger_children)%>%
+  summarise(mean_click = mean(click))%>%
+  mutate(older_children = children - 1 - younger_children)%>%
+  ungroup()%>%
+  group_by(community)%>%
+  mutate(
+         household = scale(household), 
+         children = scale(children), 
+         older_children = scale(older_children),
+         younger_children = scale(younger_children)
+         )%>%
+  na.omit()
+
+bm_pred_null <- brm(mean_click ~ ageinyears + (ageinyears |community), 
+                              data   = scdata, 
+                              family = lognormal(),
+                              warmup = 2000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr",
+             threads = threading(2)
+             )%>%
+  add_criterion(., c("waic","loo"))
+
+bm_pred_tc <- brm(mean_click ~ ageinyears + touchscreen + (ageinyears |community), 
+                              data   = scdata, 
+                              family = lognormal(),
+                              warmup = 2000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr",
+             threads = threading(2))%>%
+  add_criterion(., c("waic","loo"))
+
+bm_pred_tc_hh <- brm(mean_click ~ ageinyears + touchscreen + household + (ageinyears |community), 
+                              data   = scdata, 
+                              family = lognormal(),
+                              warmup = 2000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr",
+             threads = threading(2)
+             )%>%
+  add_criterion(., c("waic","loo"))
+
+bm_pred_tc_c <- brm(mean_click ~ ageinyears + touchscreen + children + (ageinyears |community), 
+                              data   = scdata, 
+                              family = lognormal(),
+                              warmup = 2000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr",
+             threads = threading(2)
+             )%>%
+  add_criterion(., c("waic","loo"))
+
+bm_pred_tc_yc <- brm(mean_click ~ ageinyears + touchscreen + younger_children + (ageinyears |community), 
+                              data   = scdata, 
+                              family = lognormal(),
+                              warmup = 2000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr",
+             threads = threading(2)
+             )%>%
+  add_criterion(., c("waic","loo"))
+
+bm_pred_tc_oc <- brm(mean_click ~ ageinyears + touchscreen + older_children + (ageinyears |community), 
+                              data   = scdata, 
+                              family = lognormal(),
+                              warmup = 2000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr",
+             threads = threading(2)
+             )%>%
+  add_criterion(., c("waic","loo"))
+
+bm_pred_tc_oc_rand <- brm(mean_click ~ ageinyears + touchscreen + older_children + (touchscreen + older_children + ageinyears |community), 
+                              data   = scdata, 
+                              family = lognormal(),
+                              warmup = 2000, 
+                              iter   = 4000, 
+                              chains = 4, 
+                              cores  = 4,
+             control = list(adapt_delta = 0.95),
+             backend = "cmdstanr",
+             threads = threading(2)
+             )%>%
+  add_criterion(., c("waic","loo"))
+```
+
+```{r}
+model_comp <- loo_compare(bm_pred_null, bm_pred_tc, bm_pred_tc_hh, bm_pred_tc_oc,bm_pred_tc_yc, bm_pred_tc_c, bm_pred_tc_oc_rand,
+            criterion = "waic"
+            )%>%
+  as_tibble(rownames = "model")%>%
+  left_join(model_weights(bm_pred_null, bm_pred_tc, bm_pred_tc_hh, bm_pred_tc_oc,bm_pred_tc_yc, bm_pred_tc_c, bm_pred_tc_oc_rand, criterion = "waic")%>%
+              as_tibble(rownames = "model")
+  )%>%
+  mutate_if(is.numeric, round, 2)
+
+saveRDS(model_comp, "../saves/model_comp.rds")
+
+model_comp <- readRDS("../saves/model_comp.rds")
+```
+
+The final analysis focused on whether we could predict performance in the task by aspects of everyday experience.
+For the ease of model fitting, we aggregated the data for each participant so that models predicted the average imprecision across trials^[@prein2023variation showed that the performance mean is nearly perfectly correlated with $\sigma_v$.
+When re-running the winning model on the trial-by-trial data, the results were qualitatively and quantitatively identical.].
+The aspects we could focus on were limited to the questions we asked in the questionnaire.
+That is, we analysed the effects of exposure to technology and household composition.
+
+We asked about children's exposure to screens as well as touchscreens.
+These two variables were largely redundant (see Figure Figure \@ref(fig:figpred1)B) and so we included only one of them in the model.
+We chose the availability of a touchscreen as a predictor because the task itself was presented on a touchscreen.
+We expected (and pre-registered) that children with exposure to touchscreens would perform better.
+
+For household composition, we asked for the total number of people in the household, the number of children and the number of younger children.
+Based on this, we also computed the number of older children living in the household.
+We did not pre-register this, but decided to also include this variable because prior work on advanced forms of social cognition has suggested that the presence of older siblings is slightly more predictive of development compared to other aspects of household composition [e.g., @lewis1996social; @ruffman1998older; but see @peterson2003opening].
+We think that gaze following improves though practice during social interaction.
+Particularly supportive, we believe, are situations in which it is difficult to infer the goals and intentions of another person based on other information sources (e.g., language or context).
+In such situations, children have to pay closer attention to the interaction partner and use their gaze to make such inferences.
+We are well aware that the numbers in the questionnaire are very far removed from these forms of social interaction.
+Thus, at best, they are a very coarse approximation.
+As a consequence, we do not expect there to be a very strong link between the two.
+We sincerely hope that future work will be able to directly assess children's social interactions.
+We standardized each predictor *within* each culture before fitting the models.
+Thus, the interpretation of the coefficient is the gain in precision for living e.g., in a larger household relative to other children from the same cultural settings.
+
+We compared models in a Bayesian model comparison.
+Models were compared based on the difference in expected log pointwise predictive density (ELPD) computed via the widely applicable information criterion (`WAIC`) and the standard error of that difference (SE).
+As pre-registered, we fit a separate model for each aspect of household composition.
+We compared the following models.
+
+`null`:
+* `mean_imprecision ~ age + (age | culture)`
+
+`touchscreen`:
+* `mean_imprecision ~ touchscreen + age + (age | culture)`
+
+`household`:
+* `mean_imprecision ~ household + touchscreen + age + (age | culture)`
+
+`children`:
+* `mean_imprecision ~ children + touchscreen + age + (age | culture)`
+
+`younger_children`:
+* `mean_imprecision ~ younger_children + touchscreen + age + (age | culture)`
+
+`older_children`:
+* `mean_imprecision ~ older_children + touchscreen + age + (age | culture)`
+
+```{r predcomptable, echo=F}
+pred_mocel_comp <- readRDS("../saves/model_comp.rds")%>%
+  mutate_if(is.numeric, format, digits = 2, nsmall = 2)%>%
+  select(model, elpd_diff, se_diff, waic, se_waic, value)%>%
+  mutate(model = recode(model, 
+                        bm_pred_null = "null",
+                        bm_pred_tc_oc = "older_children",
+                        bm_pred_tc = "touchscreen",
+                        bm_pred_tc_hh = "household",
+                        bm_pred_tc_c = "children",
+                        bm_pred_tc_yc = "younger_children",
+                        bm_pred_tc_oc_rand = "older_children (by culture)"))
+
+knitr::kable(pred_mocel_comp,
+             col.names = c("Model", "WAIC", "SE","diffWAIC", "diffSE", "Weight"),
+             caption = "Model comparison based on WAIC for experiential predictor models.", 
+             )
+```
+
+Table \@ref(tab:predcomptable) shows that the model predicting average imprecision by the expose of touchscreens and the number of older children living in the household performed best.
+However, the difference between the models, in particular those with different demographic predictors, was very small, suggesting that household composition contributed only little to explaining differences between individuals.
+Thus, we caution against an overly strong interpretation of the results.
+To test whether there was variation across cultural settings in the importance of these predictors, we added a model to the comparison that allowed these predictors to vary by cultural setting:
+
+`older_children (by culture)`:
+* `mean_imprecision ~ older_children + touchscreen + age + (older_children + touchscreen + age | culture)`
+
+```{r}
+pred_est <- fixef(bm_pred_tc_oc)%>%
+  as_tibble(rownames = "term")%>%
+  mutate_if(is.numeric,round, 2)
+
+saveRDS(pred_est, "../saves/pred_est.rds")
+
+pred_est <- readRDS("../saves/pred_est.rds")
+```
+
+Table \@ref(tab:predcomptable) shows that this model preformed relatively poor, suggesting that there was little variation across cultural settings in how the predictors influenced performance.
+When inspecting the estimates within the winning model, we saw that children with exposure to touchscreens performed better compared to children without exposure ($\beta$ = `r pred_est%>%filter(term == "touchscreen1")%>%pull(Estimate)`, SE = `r pred_est%>%filter(term == "touchscreen1")%>%pull(Est.Error)`, 95% CrI = `r pred_est%>%filter(term == "touchscreen1")%>%pull(Q2.5)` - `r pred_est%>%filter(term == "touchscreen1")%>%pull(Q97.5)`).
+Children with more older children living in the same household also tended to perform better ($\beta$ = `r pred_est%>%filter(term == "older_children")%>%pull(Estimate)`, SE = `r pred_est%>%filter(term == "older_children")%>%pull(Est.Error)`, 95% CrI = `r pred_est%>%filter(term == "older_children")%>%pull(Q2.5)` - `r pred_est%>%filter(term == "older_children")%>%pull(Q97.5)`).
+
+```{r}
+ptc_com <- ranef(bm_pred_null)$community[, ,1]%>%as_tibble(rownames = "community")%>%
+  left_join(data%>%group_by(community)%>%summarise(touchscreen = mean(touchscreen, na.rm = T)))
+
+saveRDS(ptc_com, "../saves/ptc_com.rds")
+
+ptc_com <- readRDS("../saves/ptc_com.rds")
+
+pcomtc <- ggplot(ptc_com,aes(x = touchscreen, y = Estimate))+
+  stat_cor(aes(x = touchscreen, y = Estimate,label = paste(..r.label..)),inherit.aes = F,r.accuracy = 0.01, cor.coef.name = "r",label.y = 0.85)+
+  geom_point(alpha = .75, pch = 1)+
+  geom_smooth(method = "lm", col = "firebrick", alpha = .25)+
+  labs(x = "Touchscreen exposure", y = "Relative imprecision (age corrected)")+
+  geom_text_repel(aes(label = community), size = 3, min.segment.length = 0, segment.curvature = -0.1)+
+  theme_few()
+
+ggsave(plot = pcomtc, "../visuals/pcomtc.png", height = 4, width = 5, scale = 1.5)
+```
+
 # Appendix

### 2024-01-29 paper/paper.Rmd
update fig1

@@
 
-```{r fig1, include = T, fig.align = "center", fig.cap = "(B) Screenshot from the task.
+```{r fig1, include = T, fig.align = "center", fig.cap = "(A) Data collection sites.
+Points show approximate geographical location of the data collection sites, coloring shows the sample sizes.
+(B) Screenshot from the task.
 The scene depicts the choice phase in a test trial.
 Participants had to use the gaze of the agent to locate the balloon and click on the hedge where they thought the balloon was.
-Agents, audio recordings and backgrounds were adpated to each cultural setting.", out.width="100%"}
+Agents, audio recordings and backgrounds were adpated to each cultural setting.
+(C) Graphical illustration of the cognitive model.
+Individuals infer the target of an agent's attention by estimating a vector based on the position of the pupils within the eyes.
+This process is noisy, illustrated by the different vectors.
+Individuals differ in their level of precision (indicated by alpha).
+Regardless of the level of precision, the further out the target lands, the less precise the model predicts individuals to be.", out.width="75%"}
 knitr::include_graphics("../visuals/fig1.png")

### 2024-01-29 paper/paper.tex
update fig1

@@
 \hypersetup{
-  pdftitle={Unity in diversity: Children from 17 communities process gaze in similar ways},
+  pdftitle={Unity in diversity: Children from 17 diverse communities process gaze in similar ways},
   pdfauthor={Manuel Bohn1,2, Julia Prein1,2, \ldots\ldots, \& Daniel B. M. Haun2},
@@
 
-\title{Unity in diversity: Children from 17 communities process gaze in similar ways}
+\title{Unity in diversity: Children from 17 diverse communities process gaze in similar ways}
 \author{Manuel Bohn\textsuperscript{1,2}, Julia Prein\textsuperscript{1,2}, \ldots{}\textsuperscript{\ldots{}}, \& Daniel B. M. Haun\textsuperscript{2}}
@@
 Previous developmental studies focused on the onset of gaze following in infancy (\emph{15}, \emph{16}).
-The XXXX participants (age ) in the study lived in 17 different communities spread over five continents.
-The countries from which data was contributed to the study represented 46\% of the world's population.
-Communities covered a broad spectrum of geographical locations, social and political systems, languages, and subsistence styles (Fig.
-\ref{fig:fig1}).
+The 1311 participants in the study lived in 17 different communities spread over five continents (Fig.
+\ref{fig:fig1}A, Tab.
+\ref{tab:tab1}).
+The countries from which data was contributed to the study represented 46 \% of the world's population.
+Communities covered a broad spectrum of geographical locations, social and political systems, languages, and subsistence styles (see Supplemental Materials).
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{../visuals/fig1}
+{\centering \includegraphics[width=0.75\linewidth]{../visuals/fig1}
 
@@
 
-\caption{(B) Screenshot from the task.
+\caption{(A) Data collection sites.
+Points show approximate geographical location of the data collection sites, coloring shows the sample sizes.
+(B) Screenshot from the task.
 The scene depicts the choice phase in a test trial.
 Participants had to use the gaze of the agent to locate the balloon and click on the hedge where they thought the balloon was.
-Agents, audio recordings and backgrounds were adpated to each cultural setting.}\label{fig:fig1}
+Agents, audio recordings and backgrounds were adpated to each cultural setting.
+(C) Graphical illustration of the cognitive model.
+Individuals infer the target of an agent's attention by estimating a vector based on the position of the pupils within the eyes.
+This process is noisy, illustrated by the different vectors.
+Individuals differ in their level of precision (indicated by alpha).
+Regardless of the level of precision, the further out the target lands, the less precise the model predicts individuals to be.}\label{fig:fig1}
 \end{figure}
@@
 Children watched a balloon disappear behind a hedge.
-An agent followed the trajectory of the balloon with their eyes.
+An agent followed the trajectory of the balloon with their eyes (Fig.
+\ref{fig:fig1}B).
 The key dependent variable was the precision with which children located the agent's focus of attention, that is, the deviation between where the agent looked (where the object was) and where the child thought the agent looked.
-We adapted visuals and audio instructions specifically to each of the 17 communities (Fig.
-1).
+We adapted visuals and audio instructions specifically to each of the 17 communities.
 Previous work demonstrated excellent individual-level measurement properties for this task (\emph{17}).
@@
 There were marked differences between communities: highly market-integrated communities around the globe showed higher levels of precision compared to less market-integrated communities.
-However, we think that these results are better explained by exposure to technology than market integration.
+However, we believe that these results are better explained by exposure to technology than market integration.
 We discuss them in more detail below.
@@
 The focus of attention is the location wherever the estimated vectors from both eyes hit a surface (Fig.
-XX).
+\ref{fig:fig1}C).
 The estimation process is not perfect, but each individual has a systematic level of uncertainty, which is conceptualized as the cause of individual differences.

### 2024-01-30 paper/paper.Rmd
update paper

@@
 Agents, audio recordings and backgrounds were adpated to each cultural setting.
-(C) Graphical illustration of the cognitive model.
+(C) Drawings used as agents across cultural settings.
+(D) Graphical illustration of the cognitive model.
 Individuals infer the target of an agent's attention by estimating a vector based on the position of the pupils within the eyes.
@@
 Individuals differ in their level of precision (indicated by alpha).
-Regardless of the level of precision, the further out the target lands, the less precise the model predicts individuals to be.", out.width="75%"}
+For a given level of precision, the further out the target lands, the less precise the model predicts individuals to be.
+Solid and transparent dots show simualted means and individual data points to illustrate the predicted effect of target position.", out.width="75%"}
 knitr::include_graphics("../visuals/fig1.png")
@@
 As the first step, we investigated developmental gains.
-Across all 17 communities, we found a substantial increase in average levels of precision with age (fixed effect: $\beta$ = `r post_fix%>%filter(term == "ageinyears")%>%pull(Estimate)`, 95% HDI (`r post_fix%>%filter(term == "ageinyears")%>%pull(Q2.5)` - `r post_fix%>%filter(term == "ageinyears")%>%pull(Q97.5)`); range of community-level effects: $\beta_{min}$ = `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%tail(1)%>%pull(mean)`, 95% HDI (`r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%tail(1)%>%pull(lci)` - `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%tail(1)%>%pull(uci)`) to $\beta_{max}$ = `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%head(1)%>%pull(mean)`, 95% HDI (`r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%head(1)%>%pull(lci)` - `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%head(1)%>%pull(uci)`).
-There were marked differences between communities: highly market-integrated communities around the globe showed higher levels of precision compared to less market-integrated communities.
-However, we believe that these results are better explained by exposure to technology than market integration.
-We discuss them in more detail below.
-Differences between communities were small compared to differences between individuals: communities did not form homogeneous clusters but largely overlapping distributions in that some individuals from communities with a lower average level of precision performed better compared to some individuals from a setting with a very high average level of precision.
-Furthermore, in all communities, some 4-year-olds outperformed children two years older than them (see Fig.
+Across all 17 communities, we found a substantial increase in average levels of precision with age (fixed effect in Bayesian regression model [@burkner2019bayesian]: $\beta$ = `r post_fix%>%filter(term == "ageinyears")%>%pull(Estimate)`, 95% HDI (`r post_fix%>%filter(term == "ageinyears")%>%pull(Q2.5)` - `r post_fix%>%filter(term == "ageinyears")%>%pull(Q97.5)`); range of community-level effects in model: $\beta_{min}$ = `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%tail(1)%>%pull(mean)`, 95% HDI (`r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%tail(1)%>%pull(lci)` - `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%tail(1)%>%pull(uci)`) to $\beta_{max}$ = `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%head(1)%>%pull(mean)`, 95% HDI (`r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%head(1)%>%pull(lci)` - `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%head(1)%>%pull(uci)`).
+Nevertheless, there were also marked differences between communities (see Fig.
+\@ref(fig:fig2)A).
+In a cross-validation procedure, in which we trained a regression model on a subset of the data (training data) to later predict the held out data (testing data) [@stengelin2023children], we found that a model that assumed cross-cultural variation to outperform simple models in 100% of cases (see Supplemental Material).
+At first glance, it seems that highly market-integrated communities around the globe showed higher levels of precision compared to less market-integrated communities (see Tab.
+\@ref(tab:tab1)).
+However, believe that these results are better understood in terms of exposure to technology and we discuss them in more detail below.
+Furthermore, average differences between communities were small compared to differences between individuals: communities did not form homogeneous clusters but largely overlapping distributions in that some individuals from communities with a lower average level of precision performed better compared to some individuals from a setting with a very high average level of precision.
+Similarly, in all communities, some 4-year-olds outperformed children two years older than them (see Fig.
 \@ref(fig:fig2)A).
@@
 To rule out this alternative explanation, we directly compared three cognitive models that made different assumptions about how participants' responses were generated: the focal vector-based gaze estimation model described above, a center-bias model where participants always select the center, and a random guessing model where participants select random locations.
-For every community, we found overwhelming support for the gaze estimation model (min $BF_{10}$ < 1000 for comparisons with both alternative models).
+For every community, we found overwhelming support for the gaze estimation model (min $BF_{10}$ > 1000 for comparisons with both alternative models).
 Taken together, children from all 17 communities processed gaze in similar ways.
@@
 Previous work suggested that social cognition develops in social interaction [@barresi1996intentional; @perner1994theory; @rakoczy2022foundations], in particular, with older siblings [@lewis1996social; @ruffman1998older].
-We found tentative support for this idea in the form of a small but consistent effect in the direction that participants living together with more children older than themselves had slightly higher levels of precision ($\beta$ = `r pred_est%>%filter(term == "older_children")%>%pull(Estimate)`, SE = `r pred_est%>%filter(term == "older_children")%>%pull(Est.Error)`, 95% CrI = `r pred_est%>%filter(term == "older_children")%>%pull(Q2.5)` - `r pred_est%>%filter(term == "older_children")%>%pull(Q97.5)`).
+We found tentative support for this idea in the form of a small but consistent effect in the direction that participants living together with more children older than themselves (relative to other children from the same setting) had slightly higher levels of precision ($\beta$ = `r pred_est%>%filter(term == "older_children")%>%pull(Estimate)`, SE = `r pred_est%>%filter(term == "older_children")%>%pull(Est.Error)`, 95% CrI = `r pred_est%>%filter(term == "older_children")%>%pull(Q2.5)` - `r pred_est%>%filter(term == "older_children")%>%pull(Q97.5)`).
 
 Following and understanding gaze is a foundational building block of human social cognition [@tomasello2007reliance; @scaife1975capacity].
-A substantial body of work has explored the developmental onset of gaze following in a few selected cultural settings [@tang2023slow; @gredeback2010development; @byers2021development; @hernik2019infant; @callaghan2011early].
+A substantial body of work has explored the developmental onset of gaze following in a few selected cultural settings [@moore2008development; @tang2023slow; @gredeback2010development; @byers2021development; @hernik2019infant; @callaghan2011early].
 The data reported here provides evidence that children all over the world process gaze in the same way.
 Key performance signatures of a model that sees gaze following as a form of social vector estimation were found in the data of all 17 distinct cultural communities.
-The cognitive processes underlying gaze following are thus likely to be rooted in humans' evolved cognitive architecture, which is -- presumably -- later refined during social interaction.
-The phylogenetic roots of these processes might possibly lie much deeper as primates from a wide range of species follow gaze [@rosati2009looking; @tomasello1998five; @itakura2004gaze].
+The cognitive processes underlying gaze following are thus likely to be rooted in humans' evolved cognitive architecture, which is -- presumably -- later refined during social interaction [@astor2020social; @movellan2002development; @senju2015early].
+The phylogenetic roots of these processes might possibly lie much deeper as primates from a wide range of species follow gaze [@rosati2009looking; @tomasello1998five; @itakura2004gaze; @kano2014cross].
 Yet, if they also show the same processing signatures has yet to be explored.
@@
 Naturalistic data directly recording social interactions across communities would offer crucial information to close this explanatory gap.
-Recent work in the field of language acquisition has shown how technological innovations can be used to close this explanatory gap.
+Recent work in the field of language acquisition has shown how technological innovations can be used to close this explanatory gap [@bergelson2023everyday; @donnelly2021longitudinal].
 

### 2024-01-31 paper/supplement.Rmd
update supllement

@@
                             stanford = "Stanford (USA)",
-                            chimfunshi = "Chimfunshi (Sambia)",
+                            chimfunshi = "Chimfunshi (Zambia)",
                             mexico = "Ocuilan (Mexico)",
@@
                             auckland = "Auckland (New Zealand)",
-                            turkey = "Malatya (Turkey)",
+                            turkey = "Malatya (Türkiye)",
                             bandongo = "Bandongo (Rep. Congo)",
@@
 Figure \@ref(fig:figpred1)A shows the age distribution in each setting.
+For some children, the exact birthday was unknown.
+In such cases, we set the birthday to the 30th of June of the year that would make them fall into the reported age category.
 Additional children were recruited but did not contribute data to the study.
 The recruitment strategy varied from community to community and we therefore cannot provide detailed information about the number of children that were excluded.
-All children who contributed at least four valid data points were included in the final sample.
+All children who contributed at least four valid data points were included in the final sample, however, we excluded children when parents did not fill out the questionnaire correctly (e.g., when the number of children living in the household was reported to be larger than the household itself or when the number of children reported to live in the household equaled the number of children younger than the child being tested).
+Twelve children had to be excluded for one of these reasons (one from Akure, two from Stanford, seven from Pune and two from Windhoek).
 We did not exclude any participants for performance reasons.
@@
 
-# dempred <- data%>%
-#   group_by(community,continent)%>%
-#   mutate(older_children = children - 1 - younger_children)%>%
-#   distinct(subjid, .keep_all = T)%>%
-#   select(subjid, community, continent, older_children,children, younger_children, household)%>%
-#   pivot_longer(names_to = "dem", values_to = "value", cols = c(older_children,children, younger_children, household))%>%
-#   mutate(dem = recode(dem,
-#                       older_children = "older children",
-#                             younger_children = "younger children"),
-#          dem = factor(dem, levels = c("household", "children", "older children", "younger children")))%>%
-#   ggplot(aes(y = community, x = value))+
-#   facet_grid(continent~dem, scales = "free", space = "free_y")+
+dempred <- data%>%
+  group_by(community,continent)%>%
+  mutate(older_children = children - 1 - younger_children)%>%
+  distinct(subjid, .keep_all = T)%>%
+  select(subjid, community, continent, older_children,children, younger_children, household)%>%
+  pivot_longer(names_to = "dem", values_to = "value", cols = c(older_children,children, younger_children, household))%>%
+  mutate(dem = recode(dem,
+                      older_children = "older children",
+                            younger_children = "younger children"),
+         dem = factor(dem, levels = c("household", "children", "older children", "younger children")))%>%
+  ggplot(aes(y = community, x = value))+
+  facet_grid(continent~dem, scales = "free", space = "free_y")+
+  geom_density_ridges(
+    jittered_points = TRUE,
+    position = position_points_jitter(width = 0.25, height = 0),
+    point_shape = '|',  point_alpha = 1, alpha = 0.7,
+  )+
  # geom_density_ridges(
-#     jittered_points = TRUE,
-#     position = position_points_jitter(width = 0.25, height = 0),
-#     point_shape = '|',  point_alpha = 1, alpha = 0.7,
-#   )+
-#  # geom_density_ridges(
-#  #    col = "white",
-#  #    jittered_points = TRUE, quantile_lines = TRUE, scale = 0.9, alpha = 0.7,
-#  #    vline_size = 1, vline_color = "red",
-#  #    point_size = 0.4, point_alpha = 1,
-#  #    position = position_raincloud(adjust_vlines = TRUE)
-#  #  )
-#   labs(x = "No. of individuals", y= "")+
-#   #geom_jitter(alpha = .1, width = 0.1, height = 0.1)+
-#   theme_few()
-# 
-# ggsave(plot = dempred, "../visuals/dempred.png", height = 8, width = 14, scale = 1.1)
+ #    col = "white",
+ #    jittered_points = TRUE, quantile_lines = TRUE, scale = 0.9, alpha = 0.7,
+ #    vline_size = 1, vline_color = "red",
+ #    point_size = 0.4, point_alpha = 1,
+ #    position = position_raincloud(adjust_vlines = TRUE)
+ #  )
+  labs(x = "No. of individuals", y= "")+
+  #geom_jitter(alpha = .1, width = 0.1, height = 0.1)+
+  theme_few()
+
+ggsave(plot = dempred, "../visuals/dempred.png", height = 8, width = 14, scale = 1.1)
 
@@
   ungroup()%>%
-  mutate(older_children = children - 1 - younger_children)%>%
-  mutate(ageinyears = scale(ageinyears),
-         targetcentralityx = scale(targetcentralityx),
-         trialnr = scale(trialnr),
-         touchscreen = factor(touchscreen),
-         screen = factor(screen),
+  mutate(ageinyears = as.numeric(scale(ageinyears)),
+         targetcentralityx = as.numeric(scale(targetcentralityx)),
          click = abs(clickdistfromtargetcenterx))
+
+#write_csv(mdata,"../data/mdata.csv")
 ```
@@
 ```{r}
-bm_null <- brm(click ~ ageinyears + targetcentralityx + (trialnr + targetcentralityx|subjid),
-                              data   = mdata,
-                              family = lognormal(),
-                              warmup = 2000,
-                              iter   = 6000,
-                              chains = 4,
-                              cores  = 4,
-                              threads = threading(8),
-             control = list(adapt_delta = 0.95),
-             backend = "cmdstanr")
-
-saveRDS(bm_null, "../saves/bm_cv_null.rds")
-
-bm_cult <- brm(click ~ ageinyears + targetcentralityx + (trialnr + targetcentralityx|subjid)+ (1 |community),
-                              data   = mdata,
-                              family = lognormal(),
-                              warmup = 2000,
-                              iter   = 6000,
-                              chains = 4,
-                              cores  = 4,
-                              threads = threading(8),
-             control = list(adapt_delta = 0.95),
-             backend = "cmdstanr")
-
-saveRDS(bm_cult, "../saves/bm_cv_cult.rds")
-
-bm_cult_age <- brm(click ~ ageinyears + targetcentralityx + (trialnr + targetcentralityx|subjid)+ (ageinyears + targetcentralityx |community),
-                              data   = mdata,
-                              family = lognormal(),
-                              warmup = 2000,
-                              iter   = 6000,
-                              chains = 4,
-                              cores  = 4,
-                              threads = threading(8),
-             control = list(adapt_delta = 0.95),
-             backend = "cmdstanr")
-
-saveRDS(bm_cult_age, "../saves/bm_cv_cult_age.rds")
-
-fixef(bm_cult_age)%>%as_tibble(rownames = "term")%>%mutate_if(is.numeric, round, 2)%>%saveRDS(.,"../saves/cult_age_fix.rds")
+# bm_null <- brm(click ~ ageinyears + targetcentralityx + (targetcentralityx|subjid),
+#                               data   = mdata,
+#                               family = lognormal(),
+#                               warmup = 2000,
+#                               iter   = 6000,
+#                               chains = 4,
+#                               cores  = 4,
+#                               threads = threading(8),
+#              control = list(adapt_delta = 0.95),
+#              backend = "cmdstanr")
+# 
+# saveRDS(bm_null, "../saves/bm_cv_null.rds")
+# 
+# 
+# bm_cult <- brm(click ~ ageinyears + targetcentralityx + (targetcentralityx|subjid)+ (targetcentralityx |community),
+#                               data   = mdata,
+#                               family = lognormal(),
+#                               warmup = 2000,
+#                               iter   = 6000,
+#                               chains = 4,
+#                               cores  = 4,
+#                               threads = threading(8),
+#              control = list(adapt_delta = 0.95),
+#              backend = "cmdstanr")
+# 
+# saveRDS(bm_cult, "../saves/bm_cv_cult.rds")
+# 
+# bm_cult_age <- brm(click ~ ageinyears + targetcentralityx + (targetcentralityx|subjid)+ (ageinyears + targetcentralityx |community),
+#                               data   = mdata,
+#                               family = lognormal(),
+#                               warmup = 2000,
+#                               iter   = 6000,
+#                               chains = 4,
+#                               cores  = 4,
+#                               threads = threading(8),
+#              control = list(adapt_delta = 0.95),
+#              backend = "cmdstanr")
+# 
+# saveRDS(bm_cult_age, "../saves/bm_cv_cult_age.rds")
+# 
+# fixef(bm_cult_age)%>%as_tibble(rownames = "term")%>%mutate_if(is.numeric, round, 2)%>%saveRDS(.,"../saves/cult_age_fix.rds")
 
@@
 ```{r}
-six_fold_cross_validation <- function(data, m1, m2, m3, m4, repeats) {
-
-  N_ids = n_distinct(data$subjid)
-#Prepare results DF
-  results <- tibble(
-    m1_score=numeric(), 
-    m2_score=numeric(), 
-    m3_score=numeric(), 
-    #m4_score=numeric(),
-
-    #m4_beats_m3=logical(), 
-    #m4_beats_m2=logical(), 
-    #m4_beats_m1=logical(), 
-    m3_beats_m2=logical(), 
-    m3_beats_m1=logical(), 
-    m2_beats_m1=logical(),
-
-    m1 = character(), 
-    m2 = character(), 
-    m3 = character(),
-    #m4 = character()
-    )
-
-#Repeat the whole shebang several times
-  for(i in 1:repeats) {
-
-  # Split dataset into 6 bins
-  bin_data <- data%>%distinct(community, subjid)%>%group_by(community) %>% mutate(bin = rep(1:6, length.out = n()))
-
-for(j in 1:6) {
-    # Use bin j as "hold out" data
-    testing_ids <- bin_data%>%filter(bin == j)%>%pull(subjid)
-    training_ids <- bin_data%>%filter(bin != j)%>%pull(subjid)
-    # Safety check - is partition complete and disjoint?
-    stopifnot(length(testing_ids) + length(training_ids) == N_ids)
-    stopifnot(length(intersect(testing_ids, training_ids)) == 0)
-# Create two separate dataframes
-    testing_data <- filter(data, subjid %in% testing_ids)
-    training_data <- filter(data, subjid %in% training_ids)
-
-    # Train models
-    up_m1 <- update(m1, newdata=training_data, cores=4,backend = "cmdstanr", threads = threading(8))
-    up_m2 <- update(m2, newdata=training_data, cores=4,backend = "cmdstanr", threads = threading(8))
-    up_m3 <- update(m3, newdata=training_data, cores=4,backend = "cmdstanr", threads = threading(8))
-    #up_m4 <- update(m4, newdata=training_data, cores=4,backend = "cmdstanr", threads = threading(8))
-
-    # Sample predictions
-    preds_m1 <- posterior_predict(up_m1, newdata=testing_data, allow_new_levels=TRUE, sample_new_levels="gaussian")
-    preds_m2 <- posterior_predict(up_m2, newdata=testing_data, allow_new_levels=TRUE, sample_new_levels="gaussian")
-    preds_m3 <- posterior_predict(up_m3, newdata=testing_data, allow_new_levels=TRUE, sample_new_levels="gaussian")
-    #preds_m4 <- posterior_predict(up_m4, newdata=testing_data, allow_new_levels=TRUE, sample_new_levels="gaussian")
-
-    # Evaluate predictive accuracy
-  score_m1 <- mean(sqrt(colMeans((testing_data$click - t(preds_m1))**2)))
-  score_m2 <- mean(sqrt(colMeans((testing_data$click - t(preds_m2))**2)))
-  score_m3 <- mean(sqrt(colMeans((testing_data$click - t(preds_m3))**2)))
-  #score_m4 <- mean(sqrt(colMeans((testing_data$click - t(preds_m4))**2)))
-
-  m1_name <-  as.character(substitute(m1))
-  m2_name <-  as.character(substitute(m2))
-  m3_name <-  as.character(substitute(m3))
-  #m4_name <-  as.character(substitute(m4))
-
-    # Record results
-    results <- add_row(results,
-
-                       repeats = i, 
-                       bin = j,
-
-                       m1_score = score_m1,
-                       m2_score = score_m2,
-                       m3_score = score_m3,
-                       #m4_score = score_m4,
-
-                       # m4_beats_m3 = m4_score < m3_score,
-                       # m4_beats_m2 = m4_score < m2_score,
-                       # m4_beats_m2 = m4_score < m1_score,
-                       m3_beats_m2 = m3_score < m2_score,
-                       m3_beats_m1 = m3_score < m1_score,
-                       m2_beats_m1 = m2_score < m1_score,
-
-                       m1  = m1_name,
-                       m2 = m2_name,
-                       m3 = m3_name,
-                       #m4 = m4_name
-                       )
- }
-  }
-  return(results)
-}
-```
-
-```{r}
-cv_cult <- six_fold_cross_validation(scdata, bm_base, bm_cult, bm_cult_age, 1)
+# script for cross validation can be found in  `../scripts/cross_validation.R`
+# cross validation is run in script `../scripts/run_cross_validation.R`, here we only load the saved output
+cv_cult <- readRDS("../saves/cross_validation_result.rds")
 ```
@@
 This is true no matter how wide the cone (how large the standard deviation) is.
+A formal definition of the model can be found below.
 
 ```{r}
-draws <- bind_rows(
-as_draws_df(bm_cult_age)%>%
-  select(contains("ageinyears"))%>%
-  select(contains("ageinyears"))%>%
-  select(-contains("sd"))%>%
-  select(-contains("cor"))%>%
-  pivot_longer(cols = contains("ageinyears]"), names_to = "community", values_to = "value")%>%
-  mutate(post = value + b_ageinyears,
-         community = str_remove(community, "r_community"),
-         community = str_remove(community, ",ageinyears]"),
-         community = str_remove(community, "\\["))%>%
-  select(community, post)%>%
-  mutate(type = "ageinyears"),
-
-as_draws_df(bm_cult_age)%>%
-  select(contains("targetcentralityx"))%>%
-  select(contains("targetcentralityx"))%>%
-  select(-contains("sd"))%>%
-  select(-contains("cor"))%>%
-  select(-contains("subjid"))%>%
-  pivot_longer(cols = contains("targetcentralityx]"), names_to = "community", values_to = "value")%>%
-  mutate(post = value + b_targetcentralityx,
-         community = str_remove(community, "r_community"),
-         community = str_remove(community, ",targetcentralityx]"),
-         community = str_remove(community, "\\["))%>%
-  select(community, post)%>%
-  mutate(type = "targetcentrality")
-)%>%
-  mutate(community = str_replace(community, "\\.", " "),
-         community= str_remove(site,"\\."))
-
-pdraws <- draws%>%
-  mutate(community = recode(community, 
-                            "Auckland (NewZealand)" = "Auckland (New Zealand)",
-                            "BaYaka (Rep.Congo)" = "BaYaka (Rep. Congo)",
-                            "Bandongo (Rep.Congo)" = "Bandongo (Rep. Congo)",
-                            "Buenos Aires(Argentina)" = "Buenos Aires (Argentina)"))%>%
-  left_join(data%>%distinct(community, continent))%>%
-  mutate(continent = factor(continent, levels = c("America", "Africa", "Europe", "Asia", "Oceania"), ordered = T))
-
-saveRDS(pdraws, "../saves/pdraws.rds")
-
-post_agg <- pdraws%>%
-  group_by(community, type)%>%
-  summarise(mean = mean(post),
-            lci = hdi_lower(post),
-            uci = hdi_upper(post))
-
-saveRDS(post_agg, "../saves/post_agg.rds")
+# draws <- bind_rows(
+# as_draws_df(bm_cult_age)%>%
+#   select(contains("ageinyears"))%>%
+#   select(contains("ageinyears"))%>%
+#   select(-contains("sd"))%>%
+#   select(-contains("cor"))%>%
+#   pivot_longer(cols = contains("ageinyears]"), names_to = "community", values_to = "value")%>%
+#   mutate(post = value + b_ageinyears,
+#          community = str_remove(community, "r_community"),
+#          community = str_remove(community, ",ageinyears]"),
+#          community = str_remove(community, "\\["))%>%
+#   select(community, post)%>%
+#   mutate(type = "ageinyears"),
+# 
+# as_draws_df(bm_cult_age)%>%
+#   select(contains("targetcentralityx"))%>%
+#   select(contains("targetcentralityx"))%>%
+#   select(-contains("sd"))%>%
+#   select(-contains("cor"))%>%
+#   select(-contains("subjid"))%>%
+#   pivot_longer(cols = contains("targetcentralityx]"), names_to = "community", values_to = "value")%>%
+#   mutate(post = value + b_targetcentralityx,
+#          community = str_remove(community, "r_community"),
+#          community = str_remove(community, ",targetcentralityx]"),
+#          community = str_remove(community, "\\["))%>%
+#   select(community, post)%>%
+#   mutate(type = "targetcentrality")
+# )%>%
+#   mutate(community = str_replace(community, "\\.", " "),
+#          community= str_remove(community,"\\."))
+# 
+# pdraws <- draws%>%
+#   mutate(community = recode(community,
+#                             "Auckland (NewZealand)" = "Auckland (New Zealand)",
+#                             "BaYaka (Rep.Congo)" = "BaYaka (Rep. Congo)",
+#                             "Bandongo (Rep.Congo)" = "Bandongo (Rep. Congo)",
+#                             "Buenos Aires(Argentina)" = "Buenos Aires (Argentina)"))%>%
+#   left_join(data%>%distinct(community, continent))%>%
+#   mutate(continent = factor(continent, levels = c("America", "Africa", "Europe", "Asia", "Oceania"), ordered = T))
+# 
+# saveRDS(pdraws, "../saves/pdraws.rds")
+# 
+# post_agg <- pdraws%>%
+#   group_by(community, type)%>%
+#   summarise(mean = mean(post),
+#             lci = hdi_lower(post),
+#             uci = hdi_upper(post))
+# 
+# saveRDS(post_agg, "../saves/post_agg.rds")
 ```
@@
 
+```{r}
+fixef_cult_age <- readRDS("../saves/cult_age_fix.rds")
+```
+
 To test these predictions, we inspected the parameter estimates for age and target centrality in the "winning" `culture_age` model described in the previous sections.
-We found strong main effects of age ($\beta$ = ) and target centrality ($\beta$ =).
-Figure \@ref(fig:figpreds) visualizes the posterior distributions for each cultural setting and shows that -- despite variation in strength -- there was a strong effect of age and target centrality in all cultural settings.
+We found strong main effects of age ($\beta$ = `r fixef_cult_age%>%filter(term == "ageinyears")%>%pull(Estimate)`, SE = `r fixef_cult_age%>%filter(term == "ageinyears")%>%pull(Est.Error)`, 95% CrI = `r fixef_cult_age%>%filter(term == "ageinyears")%>%pull(Q2.5)` - `r fixef_cult_age%>%filter(term == "ageinyears")%>%pull(Q97.5)`) and target centrality ($\beta$ =`r fixef_cult_age%>%filter(term == "targetcentralityx")%>%pull(Estimate)`, SE = `r fixef_cult_age%>%filter(term == "targetcentralityx")%>%pull(Est.Error)`, 95% CrI = `r fixef_cult_age%>%filter(term == "targetcentralityx")%>%pull(Q2.5)` - `r fixef_cult_age%>%filter(term == "targetcentralityx")%>%pull(Q97.5)`).
+Figure \@ref(fig:figpreds) visualizes the posterior distributions for each cultural setting and shows that -- despite variation in strength -- there was a substantial effect of age and target centrality in all cultural settings.
 
@@
 Figure \@ref(fig:figdev)A shows that children got more precise with age in all cultural settings.
-Figure \@ref(fig:figdev)B shows the expected u-shaped pattern: the closer the balloon lands to the center of the screen (bins 5 and 6) the more precise children are in all cultural settings.
+Figure \@ref(fig:figdev)B shows the u-shaped pattern predicted by the cognitive model: the closer the balloon lands to the center of the screen (bins 5 and 6) the more precise children are in all cultural settings.
 
@@
 am <- ggplot()+
-  geom_point(data = mdata%>%filter(continent == "America"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
+  geom_point(data = devdata%>%filter(continent == "America"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
   geom_smooth(data = post%>%filter(continent == "America"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
@@
 af <- ggplot()+
-  geom_point(data = mdata%>%filter(continent == "Africa"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
+  geom_point(data = devdata%>%filter(continent == "Africa"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
   geom_smooth(data = post%>%filter(continent == "Africa"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
@@
 eu <- ggplot()+
-  geom_point(data = mdata%>%filter(continent == "Europe"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
+  geom_point(data = devdata%>%filter(continent == "Europe"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
   geom_smooth(data = post%>%filter(continent == "Europe"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
@@
 as <- ggplot()+
-  geom_point(data = mdata%>%filter(continent == "Asia"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
+  geom_point(data = devdata%>%filter(continent == "Asia"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
   geom_smooth(data = post%>%filter(continent == "Asia"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
@@
 oc <- ggplot()+
-  geom_point(data = mdata%>%filter(continent == "Oceania"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
+  geom_point(data = devdata%>%filter(continent == "Oceania"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
   geom_smooth(data = post%>%filter(continent == "Oceania"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
@@
 The evidence in favor of the gaze model compared to the two alternative models was clear (all BF > 1 000 000 000 000 000).
-This result clearly rules out that the u-shaped pattern in the data was the result of participants always clicking the center instead of following gaze.
+This result rules out that the u-shaped pattern in the data was the result of participants always clicking the center instead of following gaze.
 
@@
 bf <- readRDS("../model/output/bf_comparison.rds")%>%
-  mutate_if(is.numeric, format, digits = 2, nsmall = 2)
+  mutate_if(is.numeric, format, digits = 2, nsmall = 2)%>%
+  mutate(community = recode(community,
+                            nigeria = "Akure (Nigeria)",
+                            leipzig = "Leipzig (Germany)",
+                            `hai||om` = "Hai||om (Namibia)",
+                            khwe = "Khwe (Namibia)",
+                            windhoek = "Windhoek (Namibia)",
+                            stanford = "Stanford (USA)",
+                            chimfunshi = "Chimfunshi (Zambia)",
+                            mexico = "Ocuilan (Mexico)",
+                            plymouth = "Plymouth (UK)",
+                            china = "Beijing (China)", 
+                            india = "Pune (India)",
+                            argentina = "Buenos Aires (Argentina)",
+                            auckland = "Auckland (New Zealand)",
+                            turkey = "Malatya (Türkiye)",
+                            bandongo = "Bandongo (Rep. Congo)",
+                            bayaka = "BaYaka (Rep. Congo)", 
+                            uganda = "Nyabyeya (Uganda)"))
 
@@
 ```{r}
-scdata <- mdata%>%
-  group_by(subjid, community, ageinyears, touchscreen, household, children, younger_children)%>%
-  summarise(mean_click = mean(click))%>%
-  mutate(older_children = children - 1 - younger_children)%>%
-  ungroup()%>%
-  group_by(community)%>%
-  mutate(
-         household = scale(household), 
-         children = scale(children), 
-         older_children = scale(older_children),
-         younger_children = scale(younger_children)
-         )%>%
-  na.omit()
-
-bm_pred_null <- brm(mean_click ~ ageinyears + (ageinyears |community), 
-                              data   = scdata, 
-                              family = lognormal(),
-                              warmup = 2000, 
-                              iter   = 4000, 
-                              chains = 4, 
-                              cores  = 4,
-             control = list(adapt_delta = 0.95),
-             backend = "cmdstanr",
-             threads = threading(2)
-             )%>%
-  add_criterion(., c("waic","loo"))
-
-bm_pred_tc <- brm(mean_click ~ ageinyears + touchscreen + (ageinyears |community), 
-                              data   = scdata, 
-                              family = lognormal(),
-                              warmup = 2000, 
-                              iter   = 4000, 
-                              chains = 4, 
-                              cores  = 4,
-             control = list(adapt_delta = 0.95),
-             backend = "cmdstanr",
-             threads = threading(2))%>%
-  add_criterion(., c("waic","loo"))
-
-bm_pred_tc_hh <- brm(mean_click ~ ageinyears + touchscreen + household + (ageinyears |community), 
-                              data   = scdata, 
-                              family = lognormal(),
-                              warmup = 2000, 
-                              iter   = 4000, 
-                              chains = 4, 
-                              cores  = 4,
-             control = list(adapt_delta = 0.95),
-             backend = "cmdstanr",
-             threads = threading(2)
-             )%>%
-  add_criterion(., c("waic","loo"))
-
-bm_pred_tc_c <- brm(mean_click ~ ageinyears + touchscreen + children + (ageinyears |community), 
-                              data   = scdata, 
-                              family = lognormal(),
-                              warmup = 2000, 
-                              iter   = 4000, 
-                              chains = 4, 
-                              cores  = 4,
-             control = list(adapt_delta = 0.95),
-             backend = "cmdstanr",
-             threads = threading(2)
-             )%>%
-  add_criterion(., c("waic","loo"))
-
-bm_pred_tc_yc <- brm(mean_click ~ ageinyears + touchscreen + younger_children + (ageinyears |community), 
-                              data   = scdata, 
-                              family = lognormal(),
-                              warmup = 2000, 
-                              iter   = 4000, 
-                              chains = 4, 
-                              cores  = 4,
-             control = list(adapt_delta = 0.95),
-             backend = "cmdstanr",
-             threads = threading(2)
-             )%>%
-  add_criterion(., c("waic","loo"))
-
-bm_pred_tc_oc <- brm(mean_click ~ ageinyears + touchscreen + older_children + (ageinyears |community), 
-                              data   = scdata, 
-                              family = lognormal(),
-                              warmup = 2000, 
-                              iter   = 4000, 
-                              chains = 4, 
-                              cores  = 4,
-             control = list(adapt_delta = 0.95),
-             backend = "cmdstanr",
-             threads = threading(2)
-             )%>%
-  add_criterion(., c("waic","loo"))
-
-bm_pred_tc_oc_rand <- brm(mean_click ~ ageinyears + touchscreen + older_children + (touchscreen + older_children + ageinyears |community), 
-                              data   = scdata, 
-                              family = lognormal(),
-                              warmup = 2000, 
-                              iter   = 4000, 
-                              chains = 4, 
-                              cores  = 4,
-             control = list(adapt_delta = 0.95),
-             backend = "cmdstanr",
-             threads = threading(2)
-             )%>%
-  add_criterion(., c("waic","loo"))
+# scdata <- mdata%>%
+#   group_by(subjid, community, ageinyears, touchscreen, household, children, younger_children)%>%
+#   summarise(mean_click = mean(click))%>%
+#   ungroup()%>%
+#   group_by(community)%>%
+#   mutate(
+#          household = scale(household),
+#          children = scale(children),
+#          younger_children = scale(younger_children)
+#          )%>%
+#   na.omit()
+# 
+# bm_pred_null <- brm(mean_click ~ ageinyears + (ageinyears |community),
+#                               data   = scdata,
+#                               family = lognormal(),
+#                               warmup = 2000,
+#                               iter   = 4000,
+#                               chains = 4,
+#                               cores  = 4,
+#              control = list(adapt_delta = 0.95),
+#              backend = "cmdstanr",
+#              threads = threading(8)
+#              )%>%
+#   add_criterion(., c("waic","loo"))
+# 
+# bm_pred_tc <- brm(mean_click ~ ageinyears + touchscreen + (ageinyears |community),
+#                               data   = scdata,
+#                               family = lognormal(),
+#                               warmup = 2000,
+#                               iter   = 4000,
+#                               chains = 4,
+#                               cores  = 4,
+#              control = list(adapt_delta = 0.95),
+#              backend = "cmdstanr",
+#              threads = threading(8))%>%
+#   add_criterion(., c("waic","loo"))
+# 
+# bm_pred_tc_hh <- brm(mean_click ~ ageinyears + touchscreen + household + (ageinyears |community),
+#                               data   = scdata,
+#                               family = lognormal(),
+#                               warmup = 2000,
+#                               iter   = 4000,
+#                               chains = 4,
+#                               cores  = 4,
+#              control = list(adapt_delta = 0.95),
+#              backend = "cmdstanr",
+#              threads = threading(8)
+#              )%>%
+#   add_criterion(., c("waic","loo"))
+# 
+# 
+# bm_pred_tc_c <- brm(mean_click ~ ageinyears + touchscreen + children + (ageinyears |community),
+#                               data   = scdata,
+#                               family = lognormal(),
+#                               warmup = 2000,
+#                               iter   = 4000,
+#                               chains = 4,
+#                               cores  = 4,
+#              control = list(adapt_delta = 0.95),
+#              backend = "cmdstanr",
+#              threads = threading(8)
+#              )%>%
+#   add_criterion(., c("waic","loo"))
+# 
+# bm_pred_tc_yc <- brm(mean_click ~ ageinyears + touchscreen + younger_children + (ageinyears |community),
+#                               data   = scdata,
+#                               family = lognormal(),
+#                               warmup = 2000,
+#                               iter   = 4000,
+#                               chains = 4,
+#                               cores  = 4,
+#              control = list(adapt_delta = 0.95),
+#              backend = "cmdstanr",
+#              threads = threading(8)
+#              )%>%
+#   add_criterion(., c("waic","loo"))
+# 
+# bm_pred_tc_rand <- brm(mean_click ~ ageinyears + touchscreen + (touchscreen + ageinyears |community),
+#                               data   = scdata,
+#                               family = lognormal(),
+#                               warmup = 2000,
+#                               iter   = 4000,
+#                               chains = 4,
+#                               cores  = 4,
+#              control = list(adapt_delta = 0.95),
+#              backend = "cmdstanr",
+#              threads = threading(8)
+#              )%>%
+#   add_criterion(., c("waic","loo"))
 ```
@@
 ```{r}
-model_comp <- loo_compare(bm_pred_null, bm_pred_tc, bm_pred_tc_hh, bm_pred_tc_oc,bm_pred_tc_yc, bm_pred_tc_c, bm_pred_tc_oc_rand,
-            criterion = "waic"
-            )%>%
-  as_tibble(rownames = "model")%>%
-  left_join(model_weights(bm_pred_null, bm_pred_tc, bm_pred_tc_hh, bm_pred_tc_oc,bm_pred_tc_yc, bm_pred_tc_c, bm_pred_tc_oc_rand, criterion = "waic")%>%
-              as_tibble(rownames = "model")
-  )%>%
-  mutate_if(is.numeric, round, 2)
-
-saveRDS(model_comp, "../saves/model_comp.rds")
+# model_comp <- loo_compare(bm_pred_null, bm_pred_tc, bm_pred_tc_hh, bm_pred_tc_yc, bm_pred_tc_c, bm_pred_tc_rand,
+#             criterion = "waic"
+#             )%>%
+#   as_tibble(rownames = "model")%>%
+#   left_join(model_weights(bm_pred_null, bm_pred_tc, bm_pred_tc_hh, bm_pred_tc_yc, bm_pred_tc_c, bm_pred_tc_rand, criterion = "waic")%>%
+#               as_tibble(rownames = "model")
+#   )%>%
+#   mutate_if(is.numeric, round, 2)
+# 
+# saveRDS(model_comp, "../saves/model_comp.rds")
 
@@
 We asked about children's exposure to screens as well as touchscreens.
-These two variables were largely redundant (see Figure Figure \@ref(fig:figpred1)B) and so we included only one of them in the model.
+These two variables were largely redundant (see Figure \@ref(fig:figpred1)B) and so we included only one of them in the model.
 We chose the availability of a touchscreen as a predictor because the task itself was presented on a touchscreen.
@@
 For household composition, we asked for the total number of people in the household, the number of children and the number of younger children.
-Based on this, we also computed the number of older children living in the household.
-We did not pre-register this, but decided to also include this variable because prior work on advanced forms of social cognition has suggested that the presence of older siblings is slightly more predictive of development compared to other aspects of household composition [e.g., @lewis1996social; @ruffman1998older; but see @peterson2003opening].
-We think that gaze following improves though practice during social interaction.
-Particularly supportive, we believe, are situations in which it is difficult to infer the goals and intentions of another person based on other information sources (e.g., language or context).
-In such situations, children have to pay closer attention to the interaction partner and use their gaze to make such inferences.
-We are well aware that the numbers in the questionnaire are very far removed from these forms of social interaction.
-Thus, at best, they are a very coarse approximation.
-As a consequence, we do not expect there to be a very strong link between the two.
-We sincerely hope that future work will be able to directly assess children's social interactions.
 We standardized each predictor *within* each culture before fitting the models.
@@
 * `mean_imprecision ~ younger_children + touchscreen + age + (age | culture)`
-
-`older_children`:
-* `mean_imprecision ~ older_children + touchscreen + age + (age | culture)`
 
@@
                         bm_pred_null = "null",
-                        bm_pred_tc_oc = "older_children",
                         bm_pred_tc = "touchscreen",
@@
                         bm_pred_tc_yc = "younger_children",
-                        bm_pred_tc_oc_rand = "older_children (by culture)"))
+                        bm_pred_tc_rand = "touchscreen (by culture)"))
 
@@
 
-Table \@ref(tab:predcomptable) shows that the model predicting average imprecision by the expose of touchscreens and the number of older children living in the household performed best.
-However, the difference between the models, in particular those with different demographic predictors, was very small, suggesting that household composition contributed only little to explaining differences between individuals.
-Thus, we caution against an overly strong interpretation of the results.
-To test whether there was variation across cultural settings in the importance of these predictors, we added a model to the comparison that allowed these predictors to vary by cultural setting:
-
-`older_children (by culture)`:
-* `mean_imprecision ~ older_children + touchscreen + age + (older_children + touchscreen + age | culture)`
+Table \@ref(tab:predcomptable) shows that the model predicting average imprecision by the availability of touchscreens performed best and better than any of the models including a predictor referring to household composition.
+However, the difference between the models was very small, suggesting that they are largely equivalent, and, for the sake of consistency, we therefore inspected the posterior estimates for household composition predictors nevertheless.
+
+To test whether there was variation across cultural settings in the importance of the availability of touchscreens, we added a model to the comparison that allowed this predictors to vary by cultural setting:
+
+`touchscreen (by culture)`:
+* `mean_imprecision ~ touchscreen + age + (touchscreen + age | culture)`
 
 ```{r}
-pred_est <- fixef(bm_pred_tc_oc)%>%
-  as_tibble(rownames = "term")%>%
-  mutate_if(is.numeric,round, 2)
-
-saveRDS(pred_est, "../saves/pred_est.rds")
+# pred_est <- fixef(bm_pred_tc)%>%
+#   as_tibble(rownames = "term")%>%
+#   mutate_if(is.numeric,round, 2)
+# 
+# saveRDS(pred_est, "../saves/pred_est.rds")
 
@@
 
-Table \@ref(tab:predcomptable) shows that this model preformed relatively poor, suggesting that there was little variation across cultural settings in how the predictors influenced performance.
+Table \@ref(tab:predcomptable) shows that this model preformed relatively poor, suggesting that there was little variation across cultural settings in how the availability of touchscreens influenced performance.
+
 When inspecting the estimates within the winning model, we saw that children with exposure to touchscreens performed better compared to children without exposure ($\beta$ = `r pred_est%>%filter(term == "touchscreen1")%>%pull(Estimate)`, SE = `r pred_est%>%filter(term == "touchscreen1")%>%pull(Est.Error)`, 95% CrI = `r pred_est%>%filter(term == "touchscreen1")%>%pull(Q2.5)` - `r pred_est%>%filter(term == "touchscreen1")%>%pull(Q97.5)`).
-Children with more older children living in the same household also tended to perform better ($\beta$ = `r pred_est%>%filter(term == "older_children")%>%pull(Estimate)`, SE = `r pred_est%>%filter(term == "older_children")%>%pull(Est.Error)`, 95% CrI = `r pred_est%>%filter(term == "older_children")%>%pull(Q2.5)` - `r pred_est%>%filter(term == "older_children")%>%pull(Q97.5)`).
-
-```{r}
-ptc_com <- ranef(bm_pred_null)$community[, ,1]%>%as_tibble(rownames = "community")%>%
-  left_join(data%>%group_by(community)%>%summarise(touchscreen = mean(touchscreen, na.rm = T)))
-
-saveRDS(ptc_com, "../saves/ptc_com.rds")
+Figure \@ref(fig:figtcagg) shows that there was a very strong correlation between touchscreen availability and performance on a cultural setting-level as well.
+To account for age differences between settings in this analysis, we used random intercept estimates for each setting from a model predicting performance by age.
+Thus, the values on the y-axis in Figure \@ref(fig:figtcagg) represent the deviation from the grand intercept for each setting for age = 0 (i.e., the mean given the centering procedure we applied before fitting the model).
+
+When inspecting the posterior estimates for the different predictors referring to household composition, the overall pattern was consistent with the interpretation that social interactions, in particular with older children and adults, support the development of gaze following.
+However, all estimates wwere very small and not reliably different from zero ($\beta$ = `r pred_est%>%filter(term == "older_children")%>%pull(Estimate)`, SE = `r pred_est%>%filter(term == "older_children")%>%pull(Est.Error)`, 95% CrI = `r pred_est%>%filter(term == "older_children")%>%pull(Q2.5)` - `r pred_est%>%filter(term == "older_children")%>%pull(Q97.5)`).
+We think the reason for this lack of a strong association is a lack of resolution: household composition is very far removed from the factors that previous work has suggested to be related to the development of gaze following in younger children, such as attachment quality or the importance of gaze in early communicative interactions [@astor2020social; @movellan2002development; @senju2015early].
+We hope that future work can increase the resolution with which everyday experiences in children from diverse cultural settings are recorded to compare the drivers behind development as we observe it.
+
+```{r figtcagg, include = T, fig.align = "center", fig.cap = "Correlation between performance in the gaze-following task and the exposure to touchscreens on a cultural setting-level.
+Realtive imprecision accounts for differences in age between settings in that it corresponds to the random intercept estimate for each setting in a model predicting performance by age.", out.width="50%"}
+# ptc_com <- ranef(bm_pred_null)$community[, ,1]%>%as_tibble(rownames = "community")%>%
+#   left_join(data%>%group_by(community)%>%summarise(touchscreen = mean(touchscreen, na.rm = T)))
+# 
+# saveRDS(ptc_com, "../saves/ptc_com.rds")
 
@@
 ggsave(plot = pcomtc, "../visuals/pcomtc.png", height = 4, width = 5, scale = 1.5)
+
+knitr::include_graphics("../visuals/pcomtc.png")
 ```

### 2024-01-31 scripts/cross_validation.R

@@ -1,0 +1,68 @@
+six_fold_cross_validation <- function(data, m1, m2, m3, repeats) {
+  
+  
+  N_ids = n_distinct(data$subjid)
+  #Prepare results DF
+  
+  #Repeat the whole shebang several times
+  for(i in 1:repeats) {
+    
+    # Split dataset into 6 bins
+    bin_data <- data%>%distinct(community, subjid)%>%group_by(community) %>% mutate(bin = rep(sample(c(1:6),size = 6,replace = FALSE), length.out = n()))
+    
+    for(j in 1:6) {
+      # Use bin j as "hold out" data
+      testing_ids <- bin_data%>%filter(bin == j)%>%pull(subjid)
+      training_ids <- bin_data%>%filter(bin != j)%>%pull(subjid)
+      # Safety check - is partition complete and disjoint?
+      stopifnot(length(testing_ids) + length(training_ids) == N_ids)
+      stopifnot(length(intersect(testing_ids, training_ids)) == 0)
+      # Create two separate dataframes
+      testing_data <- filter(data, subjid %in% testing_ids)
+      training_data <- filter(data, subjid %in% training_ids)
+      
+      # Train models
+      up_m1 <- update(m1, newdata=training_data, cores=4,backend = "cmdstanr", threads = threading(8))
+      up_m2 <- update(m2, newdata=training_data, cores=4,backend = "cmdstanr", threads = threading(8))
+      up_m3 <- update(m3, newdata=training_data, cores=4,backend = "cmdstanr", threads = threading(8))
+      
+      
+      # Sample predictions
+      preds_m1 <- posterior_predict(up_m1, newdata=testing_data, allow_new_levels=TRUE, sample_new_levels="gaussian")
+      preds_m2 <- posterior_predict(up_m2, newdata=testing_data, allow_new_levels=TRUE, sample_new_levels="gaussian")
+      preds_m3 <- posterior_predict(up_m3, newdata=testing_data, allow_new_levels=TRUE, sample_new_levels="gaussian")
+      
+      # Evaluate predictive accuracy
+      score_m1 <- mean(sqrt(colMeans((testing_data$click - t(preds_m1))**2)))
+      score_m2 <- mean(sqrt(colMeans((testing_data$click - t(preds_m2))**2)))
+      score_m3 <- mean(sqrt(colMeans((testing_data$click - t(preds_m3))**2)))
+      
+      m1_name <-  as.character(substitute(m1))
[…]

### 2024-01-31 paper/paper.Rmd
update supplement

@@
       community %in% c("akure", "hai||om", "khwe", "chimfunshi", "bandongo", "bayaka", "windhoek", "uganda"), "Africa",
-      ifelse(community %in% c("stanford", "mexico", "buenos_aires"), "America",
+      ifelse(community %in% c("stanford", "mexico", "buenos_aires"), "Americas",
              ifelse(community %in% c("india", "beijing", "turkey"), "Asia", "Oceania"))
@@
   ))%>%
-  mutate(continent = factor(continent, levels = c("America", "Africa", "Europe", "Asia", "Oceania"), ordered = T))%>%
+  mutate(continent = factor(continent, levels = c("Americas", "Africa", "Europe", "Asia", "Oceania"), ordered = T))%>%
   mutate(community = recode(community,
@@
 
+Based on this, we also computed the number of older children living in the household.
+We did not pre-register this, but decided to also include this variable because prior work on advanced forms of social cognition has suggested that the presence of older siblings is slightly more predictive of development compared to other aspects of household composition [e.g., @lewis1996social; @ruffman1998older; but see @peterson2003opening].
+We think that gaze following improves though practice during social interaction.
+Particularly supportive, we believe, are situations in which it is difficult to infer the goals and intentions of another person based on other information sources (e.g., language or context).
+In such situations, children have to pay closer attention to the interaction partner and use their gaze to make such inferences.
+We are well aware that the numbers in the questionnaire are very far removed from these forms of social interaction.
+Thus, at best, they are a very coarse approximation.
+As a consequence, we do not expect there to be a very strong link between the two.
+We sincerely hope that future work will be able to directly assess children's social interactions.
+
 On an individual level, other factors likely generated individual differences because there was substantial variation even in communities where almost all children had access to touchscreens.

### 2024-02-05 paper/supplement.Rmd
update supplement

@@
 ---
-title: "Unity in diversity: shared basic social-cognitive processing in children from from 17 diverse communities"
-subtitle: "Supplementary material"
+title: "Unity in diversity: Children from 17 diverse communities process gaze in similar ways"
+subtitle: "Supplemental material"
 author: "..."
@@
 library(ggrepel)
+library(knitr)
+library(kableExtra)
 
@@
 knitr::opts_chunk$set(echo=F, warning=FALSE, message=FALSE, size="small")
+options(knitr.kable.NA = '')
 
@@
 
-in the section [site descriptions](#site-descriptions)
+This docuemnt provides a detailed overview of the participants and methods of the in the section [site descriptions](#site-descriptions)
 
@@
 
-knitr::kable(demtab,
+kableExtra::kable(demtab,
              col.names = c("Community", "Country", "Continent", "N", "Sex (male)", "Age (range)"),
               caption = "Participant demographics.", 
-             #ote = "Column age shows mean and range in paranthesis.", digits = 2, align = "l"
+             format="latex", booktabs=TRUE
              )
@@
 
-```{r figpred1, include = T, fig.align = "center", fig.cap = "A) Age distribution and B) prevalence of different types of technology by community.
-Left: dots show individual data points.
-Right: color shows the proportion of children with access to screens or touchscreens.", out.width="100%"}
-techpred <- plot_grid(page, ppred, rel_widths = c(1, 0.5),align = "h", labels = c("A", "B"))
-
-ggsave(plot = techpred, "../visuals/techpred.png",  height = 7, width = 10, scale = 1)
-
-knitr::include_graphics("../visuals/techpred.png")
-
-```
-
 A total of `r sum(as.numeric(demtab$N))` children between `r round(min(data$ageinyears), 2)` and `r round(max(data$ageinyears), 2)` provided data for the study.
@@
 * New Zealand Census 2018 for Auckland Region: https://www.stats.govt.nz/tools/2018-census-place-summaries/auckland-region#population-and-dwellings
+
+```{r figpred1, include = T, fig.align = "center", fig.cap = "A) Age distribution and B) prevalence of different types of technology by community.
+Left: dots show individual data points.
+Right: color shows the proportion of children with access to screens or touchscreens.", out.width="100%"}
+# techpred <- plot_grid(page, ppred, rel_widths = c(1, 0.5),align = "h", labels = c("A", "B"))
+# 
+# ggsave(plot = techpred, "../visuals/techpred.png",  height = 7, width = 10, scale = 1)
+
+knitr::include_graphics("../visuals/techpred.png")
+
+```
 
@@
 ```{r figpred2, include = T, fig.align = "center", fig.cap = "Household demographics by community.
-Vertical lines show individual data points with minimal horizontal jitter to avoid overplotting.", out.width="100%"}
-
-dempred <- data%>%
-  group_by(community,continent)%>%
-  mutate(older_children = children - 1 - younger_children)%>%
-  distinct(subjid, .keep_all = T)%>%
-  select(subjid, community, continent, older_children,children, younger_children, household)%>%
-  pivot_longer(names_to = "dem", values_to = "value", cols = c(older_children,children, younger_children, household))%>%
-  mutate(dem = recode(dem,
-                      older_children = "older children",
-                            younger_children = "younger children"),
-         dem = factor(dem, levels = c("household", "children", "older children", "younger children")))%>%
-  ggplot(aes(y = community, x = value))+
-  facet_grid(continent~dem, scales = "free", space = "free_y")+
-  geom_density_ridges(
-    jittered_points = TRUE,
-    position = position_points_jitter(width = 0.25, height = 0),
-    point_shape = '|',  point_alpha = 1, alpha = 0.7,
-  )+
- # geom_density_ridges(
- #    col = "white",
- #    jittered_points = TRUE, quantile_lines = TRUE, scale = 0.9, alpha = 0.7,
- #    vline_size = 1, vline_color = "red",
- #    point_size = 0.4, point_alpha = 1,
- #    position = position_raincloud(adjust_vlines = TRUE)
- #  )
-  labs(x = "No. of individuals", y= "")+
-  #geom_jitter(alpha = .1, width = 0.1, height = 0.1)+
-  theme_few()
-
-ggsave(plot = dempred, "../visuals/dempred.png", height = 8, width = 14, scale = 1.1)
+Points show individual data points with minimal vertical and horizontal jitter to avoid overplotting.
+Red points show means with 95\\% CI.", out.width="100%"}
+
+# dempred <- data%>%
+#   group_by(community,continent)%>%
+#   distinct(subjid, .keep_all = T)%>%
+#   select(subjid, community, continent, children, younger_children, household)%>%
+#   pivot_longer(names_to = "dem", values_to = "value", cols = c(children, younger_children, household))%>%
+#   mutate(dem = recode(dem,
+#                       younger_children = "younger children"),
+#          dem = factor(dem, levels = c("household", "children", "younger children")))%>%
+#   ggplot(aes(y = value, x = community))+
+#   facet_grid(dem~continent, scales = "free", space = "free_x")+
+#   geom_jitter(width = 0.2, height = 0.1, alpha = 0.1)+
+#   geom_pointrange(data = dempred_agg, aes(ymin = ci_lower, ymax = ci_upper, y = mean), col = "firebrick")+
+#   theme_few()+
+#   labs(y = "No. of individuals", x= "")+
+#   theme(axis.text.x = element_text(angle = 55, vjust = 1, hjust=1))
+# 
+# ggsave(plot = dempred, "../visuals/dempred.png", height = 6, width = 12, scale = 1)
 
 knitr::include_graphics("../visuals/dempred.png")
+
 ```
@@
 ## Setup and Procedure
+
+```{r task, include = T, fig.align = "center", fig.cap = "Screenshot from the task.
+The scene depicts the choice phase in a test trial.
+Participants had to use the gaze of the agent to locate the balloon and click on the hedge where they thought the balloon was.", out.width="80%"}
+knitr::include_graphics("../visuals/task.png")
+```
 
@@
 On each trial, we recorded the exact x-coordinate of the participant's touch.
-
-```{r figtask, include = T, fig.align = "center", fig.cap = "Screenshot from the task.
-The scene depicts the choice phase in a test trial.
-Participants had to use the gaze of the agent to locate the balloon and click on the hedge where they thought the balloon was.", out.width="80%"}
-knitr::include_graphics("../visuals/task.png")
-```
 
@@
 
-We used Bayesian Regression models fit in `R` [] using the package `brms` [@burkner2019bayesian] for all analyses except the cognitive models, which were implemented in the probabilistic programming language `webppl` [@dippl].
+We used Bayesian Regression models fit in `R` [@r] using the package `brms` [@burkner2019bayesian] for all analyses except the cognitive models, which were implemented in the probabilistic programming language `webppl` [@dippl].
 For regression models, we used the default priors built in to `brms`.
@@
 `null`:
+
 * `imprecision ~ age + target_centrality + (target_centrality | participant)`
@@
 `culture`:
+
 * `imprecision ~ age + target_centrality + (target_centrality | participant) + (target_centrality | culture)`
@@
 `culture_age`:
+
 * `imprecision ~ age + target_centrality + (target_centrality | participant) + (age + target_centrality | culture)`
@@
 ```{r}
-mdata <- data%>%
-  ungroup()%>%
-  mutate(ageinyears = as.numeric(scale(ageinyears)),
-         targetcentralityx = as.numeric(scale(targetcentralityx)),
-         click = abs(clickdistfromtargetcenterx))
+# mdata <- data%>%
+#   ungroup()%>%
+#   mutate(ageinyears = as.numeric(scale(ageinyears)),
+#          targetcentralityx = as.numeric(scale(targetcentralityx)),
+#          click = abs(clickdistfromtargetcenterx))
 
@@
 #   left_join(data%>%distinct(community, continent))%>%
-#   mutate(continent = factor(continent, levels = c("America", "Africa", "Europe", "Asia", "Oceania"), ordered = T))
+#   mutate(continent = factor(continent, levels = c("Americas", "Africa", "Europe", "Asia", "Oceania"), ordered = T))
 # 
@@
 
-pdraws <- readRDS("../saves/pdraws.rds")%>%
-  mutate(type = recode(type,
-                       ageinyears = "Age",
-                       targetcentrality = "Target centrality"),
-         type = factor(type, levels = c("Age","Target centrality")))
-
-ppred <- ggplot(pdraws, aes(x= post, y = community))+
-
-  geom_density_ridges(col = "white", alpha = .75, fill = "grey")+
-  geom_vline(xintercept = 0, lty = 3)+
-  facet_grid(continent~type, scales = "free", space = "free_y")+
-  #stat_pointinterval(size = 0.1)+
-  #xlim(-0.15, 0.1)+
-  labs(x = "Posterior model estimate", y= "")+
-  theme_few()+
-  theme( strip.text.y.right = element_text(angle = 0))
-
-ggsave(plot = ppred, "../visuals/pred.png", height = 6, width = 12, scale = 1)
+# pdraws <- readRDS("../saves/pdraws.rds")%>%
+#   mutate(type = recode(type,
+#                        ageinyears = "Age",
+#                        targetcentrality = "Target centrality"),
+#          type = factor(type, levels = c("Age","Target centrality")))
+# 
+# 
+# 
+# ppred <- ggplot(pdraws, aes(x= post, y = community))+
+# 
+#   geom_density_ridges(col = "white", alpha = .75, fill = "grey")+
+#   geom_vline(xintercept = 0, lty = 3)+
+#   facet_grid(continent~type, scales = "free", space = "free_y")+
+#   #stat_pointinterval(size = 0.1)+
+#   #xlim(-0.15, 0.1)+
+#   labs(x = "Posterior model estimate", y= "")+
+#   theme_few()+
+#   theme( strip.text.y.right = element_text(angle = 0))
+# 
+# 
+# ggsave(plot = ppred, "../visuals/pred.png", height = 6, width = 12, scale = 1)
 
@@
 ```{r}
-devdata <- data%>%
-  mutate(click = abs(clickdistfromtargetcenterx))%>%
-  group_by(subjid, continent,community, ageinyears)%>%
-  summarise(mean_click = mean(click))%>%
-  ungroup()%>%
-  mutate(ageinyears = ageinyears - min(ageinyears))
-
-bm_dev <- brm(mean_click ~ ageinyears + (ageinyears |community),
-                              data   = devdata,
-                              family = lognormal(),
-                              warmup = 2000,
-                              iter   = 4000,
-                              chains = 4,
-                              cores  = 4,
-             control = list(adapt_delta = 0.95))
-
-ndata <- devdata%>%
-  distinct(continent, community, ageinyears)
-
-post <- fitted(bm_dev, newdata = ndata, re_formula =~(ageinyears|community))%>%
-  as_tibble() %>%
-  bind_cols(ndata)%>%
-  mutate(ageinyears = ageinyears + min(data$ageinyears))
+# devdata <- data%>%
+#   mutate(click = abs(clickdistfromtargetcenterx))%>%
+#   group_by(subjid, continent,community, ageinyears)%>%
+#   summarise(mean_click = mean(click))%>%
+#   ungroup()%>%
+#   mutate(ageinyears = ageinyears - min(ageinyears))
+# 
+# bm_dev <- brm(mean_click ~ ageinyears + (ageinyears |community),
+#                               data   = devdata,
+#                               family = lognormal(),
+#                               warmup = 2000,
+#                               iter   = 4000,
+#                               chains = 4,
+#                               cores  = 4,
+#              control = list(adapt_delta = 0.95))
+# 
+# 
+# ndata <- devdata%>%
+#   distinct(continent, community, ageinyears)
+# 
+# 
+# post <- fitted(bm_dev, newdata = ndata, re_formula =~(ageinyears|community))%>%
+#   as_tibble() %>%
+#   bind_cols(ndata)%>%
+#   mutate(ageinyears = ageinyears + min(data$ageinyears))
 ```
@@
 ```{r}
-tc_agg_data<- data%>%
-  mutate(targetposition = factor(targetposition, levels = c(1:10)))%>%
-  group_by(continent, community, targetposition)%>%
-  tidyboot_mean(col= abs(clickdistfromtargetcenterx))
-
-tam <- tc_agg_data%>%
-  filter(continent == "America")%>%
-  ggplot(., aes(x = targetposition, y = mean, col = community))+
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
-  labs(x = "", y = "")+
-  scale_color_colorblind(name = "", guide = "none")+
-  facet_grid(continent~.)+
-  ylim(0,1000)+
-  theme_few()
-
-taf <- tc_agg_data%>%
-  filter(continent == "Africa")%>%
-  ggplot(., aes(x = targetposition, y = mean, col = community))+
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
-  labs(x = "", y = "")+
-  scale_color_colorblind(name = "", guide = "none")+
-  facet_grid(continent~.)+
-  ylim(0,1000)+
-  theme_few()
-
-teu <- tc_agg_data%>%
-  filter(continent == "Europe")%>%
-  ggplot(., aes(x = targetposition, y = mean, col = community))+
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
-  labs(x = "", y = "")+
-  scale_color_colorblind(name = "", guide = "none")+
-  facet_grid(continent~.)+
-  ylim(0,1000)+
-  theme_few()
-
-tas <- tc_agg_data%>%
-  filter(continent == "Asia")%>%
-  ggplot(., aes(x = targetposition, y = mean, col = community))+
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
-  labs(x = "", y = "")+
-  scale_color_colorblind(name = "", guide = "none")+
-  facet_grid(continent~.)+
-  ylim(0,1000)+
-  theme_few()
-
-toc <- tc_agg_data%>%
-  filter(continent == "Oceania")%>%
-  ggplot(., aes(x = targetposition, y = mean, col = community))+
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
-  labs(x = "Target position (binned)", y = "")+
-  scale_color_colorblind(name = "", guide = "none")+
-  facet_grid(continent~.)+
-  ylim(0,1000)+
-  theme_few()
+# tc_agg_data<- data%>%
+#   mutate(targetposition = factor(targetposition, levels = c(1:10)))%>%
+#   group_by(continent, community, targetposition)%>%
+#   tidyboot_mean(col= abs(clickdistfromtargetcenterx))
+# 
+# 
+# tam <- tc_agg_data%>%
+#   filter(continent == "Americas")%>%
+#   ggplot(., aes(x = targetposition, y = mean, col = community))+
+#   geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
+#   labs(x = "", y = "")+
+#   scale_color_colorblind(name = "", guide = "none")+
+#   facet_grid(continent~.)+
+#   ylim(0,1000)+
+#   theme_few()
+# 
+# taf <- tc_agg_data%>%
+#   filter(continent == "Africa")%>%
+#   ggplot(., aes(x = targetposition, y = mean, col = community))+
+#   geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
+#   labs(x = "", y = "")+
+#   scale_color_colorblind(name = "", guide = "none")+
+#   facet_grid(continent~.)+
+#   ylim(0,1000)+
+#   theme_few()
+# 
+# teu <- tc_agg_data%>%
+#   filter(continent == "Europe")%>%
+#   ggplot(., aes(x = targetposition, y = mean, col = community))+
+#   geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
+#   labs(x = "", y = "")+
+#   scale_color_colorblind(name = "", guide = "none")+
+#   facet_grid(continent~.)+
+#   ylim(0,1000)+
+#   theme_few()
+# 
+# tas <- tc_agg_data%>%
+#   filter(continent == "Asia")%>%
+#   ggplot(., aes(x = targetposition, y = mean, col = community))+
+#   geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
+#   labs(x = "", y = "")+
+#   scale_color_colorblind(name = "", guide = "none")+
+#   facet_grid(continent~.)+
+#   ylim(0,1000)+
+#   theme_few()
+# 
+# toc <- tc_agg_data%>%
+#   filter(continent == "Oceania")%>%
+#   ggplot(., aes(x = targetposition, y = mean, col = community))+
+#   geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
+#   labs(x = "Target position (binned)", y = "")+
+#   scale_color_colorblind(name = "", guide = "none")+
+#   facet_grid(continent~.)+
+#   ylim(0,1000)+
+#   theme_few()
 
@@
 ```{r}
-am <- ggplot()+
-  geom_point(data = devdata%>%filter(continent == "America"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
-  geom_smooth(data = post%>%filter(continent == "America"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
-  theme_few()+
-  scale_fill_colorblind(name = "")+
-  scale_color_colorblind(name = "")+
-  labs(x = "", y="Imprecision")+
-  scale_x_continuous(limits = c(2,10))+
-  scale_y_continuous(limits = c(0,1000))+
-  facet_grid(continent~.)+
-  theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))
-
-af <- ggplot()+
-  geom_point(data = devdata%>%filter(continent == "Africa"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
-  geom_smooth(data = post%>%filter(continent == "Africa"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
-  theme_few()+
-  scale_fill_colorblind(name = "")+
-  scale_color_colorblind(name = "")+
-  labs(x = "", y="")+
-    scale_x_continuous(limits = c(2,10))+
-  scale_y_continuous(limits = c(0,1000))+
-  facet_grid(continent~.)+
-  theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))
-
-eu <- ggplot()+
-  geom_point(data = devdata%>%filter(continent == "Europe"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
-  geom_smooth(data = post%>%filter(continent == "Europe"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
-  theme_few()+
-  scale_fill_colorblind(name = "")+
-  scale_color_colorblind(name = "")+
-  labs(x = "", y="")+
-    scale_x_continuous(limits = c(2,10))+
-  scale_y_continuous(limits = c(0,1000))+
-  facet_grid(continent~.)+
-  theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))
-
-as <- ggplot()+
-  geom_point(data = devdata%>%filter(continent == "Asia"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
-  geom_smooth(data = post%>%filter(continent == "Asia"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
-  theme_few()+
-  scale_fill_colorblind(name = "")+
-  scale_color_colorblind(name = "")+
-  labs(x = "", y="")+
-    scale_x_continuous(limits = c(2,10))+
-  scale_y_continuous(limits = c(0,1000))+
-  facet_grid(continent~.)+
-  theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))
-
-oc <- ggplot()+
-  geom_point(data = devdata%>%filter(continent == "Oceania"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
-  geom_smooth(data = post%>%filter(continent == "Oceania"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
-  theme_few()+
-  scale_fill_colorblind(name = "")+
-  scale_color_colorblind(name = "")+
-  labs(x = "Age", y="")+
-    scale_x_continuous(limits = c(2,10))+
-  scale_y_continuous(limits = c(0,1000))+
-  facet_grid(continent~.)+
-  theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))
+# am <- ggplot()+
+#   geom_point(data = devdata%>%filter(continent == "Americas"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
+#   geom_smooth(data = post%>%filter(continent == "Americas"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
+#   theme_few()+
+#   scale_fill_colorblind(name = "")+
+#   scale_color_colorblind(name = "")+
+#   labs(x = "", y="Imprecision")+
+#   scale_x_continuous(limits = c(2,10))+
+#   scale_y_continuous(limits = c(0,1000))+
+#   facet_grid(continent~.)+
+#   theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))
+# 
+# af <- ggplot()+
+#   geom_point(data = devdata%>%filter(continent == "Africa"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
+#   geom_smooth(data = post%>%filter(continent == "Africa"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
+#   theme_few()+
+#   scale_fill_colorblind(name = "")+
+#   scale_color_colorblind(name = "")+
+#   labs(x = "", y="")+
+#     scale_x_continuous(limits = c(2,10))+
+#   scale_y_continuous(limits = c(0,1000))+
+#   facet_grid(continent~.)+
+#   theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))
+# 
+# eu <- ggplot()+
+#   geom_point(data = devdata%>%filter(continent == "Europe"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
+#   geom_smooth(data = post%>%filter(continent == "Europe"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
+#   theme_few()+
+#   scale_fill_colorblind(name = "")+
+#   scale_color_colorblind(name = "")+
+#   labs(x = "", y="")+
+#     scale_x_continuous(limits = c(2,10))+
+#   scale_y_continuous(limits = c(0,1000))+
+#   facet_grid(continent~.)+
+#   theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))
+# 
+# as <- ggplot()+
+#   geom_point(data = devdata%>%filter(continent == "Asia"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
+#   geom_smooth(data = post%>%filter(continent == "Asia"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
+#   theme_few()+
+#   scale_fill_colorblind(name = "")+
+#   scale_color_colorblind(name = "")+
+#   labs(x = "", y="")+
+#     scale_x_continuous(limits = c(2,10))+
+#   scale_y_continuous(limits = c(0,1000))+
+#   facet_grid(continent~.)+
+#   theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))
+# 
+# oc <- ggplot()+
+#   geom_point(data = devdata%>%filter(continent == "Oceania"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
+#   geom_smooth(data = post%>%filter(continent == "Oceania"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
+#   theme_few()+
+#   scale_fill_colorblind(name = "")+
+#   scale_color_colorblind(name = "")+
+#   labs(x = "Age", y="")+
+#     scale_x_continuous(limits = c(2,10))+
+#   scale_y_continuous(limits = c(0,1000))+
+#   facet_grid(continent~.)+
+#   theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))
 ```
@@
 Each bin covers 1/10th of the screen.
-Points show means and eroor bars 95\\% confidence intervals for the data within that bin aggregated across participants.", out.width="100%"}
-# plot_grid(
-#   plot_grid(am, tam, nrow = 1, align = "h", rel_widths = c(2,1)),
-#   plot_grid(af, taf, nrow = 1, align = "h", rel_widths = c(2,1)),
-#   plot_grid(eu, teu, nrow = 1, align = "h", rel_widths = c(2,1)),
-#   plot_grid(as, tas, nrow = 1, align = "h", rel_widths = c(2,1)),
-#   plot_grid(oc, toc, nrow = 1, align = "h", rel_widths = c(2,1)),
-#   align = "v",
-#   ncol = 1
+Points show means and eroor bars 95\\% confidence intervals for the data within that bin aggregated across participants.", out.width="75%"}
+
+# pvis_pred <- plot_grid(
+#   plot_grid(am, af, eu, as,oc, ncol = 1, align = "v"),
+#   plot_grid(tam, taf, teu, tas,toc, ncol = 1, align = "v"),
+#   nrow = 1,
+#   labels = c("A","B"),
+#   rel_widths = c(1.75,1)
 # )
-
-pvis_pred <- plot_grid(
-  plot_grid(am, af, eu, as,oc, ncol = 1, align = "v"),
-  plot_grid(tam, taf, teu, tas,toc, ncol = 1, align = "v"),
-  nrow = 1,
-  labels = c("A","B"),
-  rel_widths = c(1.75,1)
-)
-
-ggsave(plot = pvis_pred, "../visuals/pvis_pred.png", height = 10, width = 6, scale = 1.5)
-
+# 
+# ggsave(plot = pvis_pred, "../visuals/pvis_pred.png", height = 10, width = 6, scale = 1.5)
+# 
 knitr::include_graphics("../visuals/pvis_pred.png")
@@
 
-knitr::kable(bf,
-             col.names = c("Community", "log(BF~gaze,center~)", "log(BF~gaze,guess~)"),
+kableExtra::kable(bf,
+             col.names = c("Community", "log(BF\\textsubscript{gaze,center})", "log(BF\\textsubscript{gaze,guess})"),
              caption = "Log Bayes Factors in favor of the gaze model compared to two alternative models.",
+             format="latex", booktabs=TRUE, escape = F
              )
@@
 We compared models in a Bayesian model comparison.
-Models were compared based on the difference in expected log pointwise predictive density (ELPD) computed via the widely applicable information criterion (`WAIC`) and the standard error of that difference (SE).
+Models were compared based on the difference in expected log pointwise predictive density (`ELPD`) computed via the widely applicable information criterion (`WAIC`) and the standard error of that difference (SE).
 As pre-registered, we fit a separate model for each aspect of household composition.
@@
 `null`:
+
 * `mean_imprecision ~ age + (age | culture)`
@@
 `touchscreen`:
+
 * `mean_imprecision ~ touchscreen + age + (age | culture)`
@@
 `household`:
+
 * `mean_imprecision ~ household + touchscreen + age + (age | culture)`
@@
 `children`:
+
 * `mean_imprecision ~ children + touchscreen + age + (age | culture)`
@@
 `younger_children`:
+
 * `mean_imprecision ~ younger_children + touchscreen + age + (age | culture)`
@@
                         bm_pred_tc_c = "children",
-                        bm_pred_tc_yc = "younger_children",
+                        bm_pred_tc_yc = "younger children",
                         bm_pred_tc_rand = "touchscreen (by culture)"))
 
-knitr::kable(pred_mocel_comp,
-             col.names = c("Model", "WAIC", "SE","diffWAIC", "diffSE", "Weight"),
-             caption = "Model comparison based on WAIC for experiential predictor models.", 
+kableExtra::kable(pred_mocel_comp,
+             col.names = c("Model","diff\\textsubscript{WAIC}", "diff\\textsubscript{SE}", "WAIC", "SE", "Weight"),
+             caption = "Log Bayes Factors in favor of the gaze model compared to two alternative models.",
+             format="latex", booktabs=TRUE, escape = F
              )
+
 ```
@@
 Table \@ref(tab:predcomptable) shows that the model predicting average imprecision by the availability of touchscreens performed best and better than any of the models including a predictor referring to household composition.
-However, the difference between the models was very small, suggesting that they are largely equivalent, and, for the sake of consistency, we therefore inspected the posterior estimates for household composition predictors nevertheless.
+However, the difference between the models was very small (`ELPD` < 1, see Table \@ref(tab:predcomptable)), suggesting that they are largely equivalent, and, for the sake of consistency, we therefore inspected the posterior estimates for household composition predictors nevertheless.
 
@@
 `touchscreen (by culture)`:
+
 * `mean_imprecision ~ touchscreen + age + (touchscreen + age | culture)`
@@
 Table \@ref(tab:predcomptable) shows that this model preformed relatively poor, suggesting that there was little variation across cultural settings in how the availability of touchscreens influenced performance.
-
-When inspecting the estimates within the winning model, we saw that children with exposure to touchscreens performed better compared to children without exposure ($\beta$ = `r pred_est%>%filter(term == "touchscreen1")%>%pull(Estimate)`, SE = `r pred_est%>%filter(term == "touchscreen1")%>%pull(Est.Error)`, 95% CrI = `r pred_est%>%filter(term == "touchscreen1")%>%pull(Q2.5)` - `r pred_est%>%filter(term == "touchscreen1")%>%pull(Q97.5)`).
+When inspecting the estimates within the winning model, we saw that children with exposure to touchscreens performed better compared to children without exposure ($\beta$ = `r pred_est%>%filter(term == "touchscreen")%>%pull(Estimate)`, SE = `r pred_est%>%filter(term == "touchscreen")%>%pull(Est.Error)`, 95% CrI = `r pred_est%>%filter(term == "touchscreen")%>%pull(Q2.5)` - `r pred_est%>%filter(term == "touchscreen")%>%pull(Q97.5)`).
 Figure \@ref(fig:figtcagg) shows that there was a very strong correlation between touchscreen availability and performance on a cultural setting-level as well.
-To account for age differences between settings in this analysis, we used random intercept estimates for each setting from a model predicting performance by age.
+To account for age differences between settings in this analysis, we used random intercept estimates for each setting from a model predicting performance by age (the `null` model mentioned above).
 Thus, the values on the y-axis in Figure \@ref(fig:figtcagg) represent the deviation from the grand intercept for each setting for age = 0 (i.e., the mean given the centering procedure we applied before fitting the model).
@@
 When inspecting the posterior estimates for the different predictors referring to household composition, the overall pattern was consistent with the interpretation that social interactions, in particular with older children and adults, support the development of gaze following.
-However, all estimates wwere very small and not reliably different from zero ($\beta$ = `r pred_est%>%filter(term == "older_children")%>%pull(Estimate)`, SE = `r pred_est%>%filter(term == "older_children")%>%pull(Est.Error)`, 95% CrI = `r pred_est%>%filter(term == "older_children")%>%pull(Q2.5)` - `r pred_est%>%filter(term == "older_children")%>%pull(Q97.5)`).
+However, all estimates were very small and not reliably different from zero.
 We think the reason for this lack of a strong association is a lack of resolution: household composition is very far removed from the factors that previous work has suggested to be related to the development of gaze following in younger children, such as attachment quality or the importance of gaze in early communicative interactions [@astor2020social; @movellan2002development; @senju2015early].
@@
 
-ptc_com <- readRDS("../saves/ptc_com.rds")
-
-pcomtc <- ggplot(ptc_com,aes(x = touchscreen, y = Estimate))+
-  stat_cor(aes(x = touchscreen, y = Estimate,label = paste(..r.label..)),inherit.aes = F,r.accuracy = 0.01, cor.coef.name = "r",label.y = 0.85)+
-  geom_point(alpha = .75, pch = 1)+
-  geom_smooth(method = "lm", col = "firebrick", alpha = .25)+
-  labs(x = "Touchscreen exposure", y = "Relative imprecision (age corrected)")+
-  geom_text_repel(aes(label = community), size = 3, min.segment.length = 0, segment.curvature = -0.1)+
-  theme_few()
-
-ggsave(plot = pcomtc, "../visuals/pcomtc.png", height = 4, width = 5, scale = 1.5)
+# ptc_com <- readRDS("../saves/ptc_com.rds")
+# 
+# pcomtc <- ggplot(ptc_com,aes(x = touchscreen, y = Estimate))+
+#   stat_cor(aes(x = touchscreen, y = Estimate,label = paste(..r.label..)),inherit.aes = F,r.accuracy = 0.01, cor.coef.name = "r",label.y = 0.85)+
+#   geom_point(alpha = .75, pch = 1)+
+#   geom_smooth(method = "lm", col = "firebrick", alpha = .25)+
+#   labs(x = "Touchscreen exposure", y = "Relative imprecision (age corrected)")+
+#   geom_text_repel(aes(label = community), size = 3, min.segment.length = 0, segment.curvature = -0.1)+
+#   theme_few()
+# 
+# ggsave(plot = pcomtc, "../visuals/pcomtc.png", height = 4, width = 5, scale = 1.5)
 

### 2024-02-28 analysis/gafo-cc-visuals.Rmd
run inward click model on cluster

@@
 library(cowplot)
+library(png)
+library(ggimage)
+library(ggridges)
 ```
@@
                             uganda = "Nyabyeya (Uganda)"))
+
 ```
@@
 ggsave("../visuals/target_position_site.png", width = 8, height = 6, bg = "white")
+```
+
+```{r}
+im <- readPNG("../visuals/gazemodel-cc-center.png")
+im2 <- matrix(rgb(im[,,1],im[,,2],im[,,3], im[,,4] * 0.5), nrow=dim(im)[1])
+
+sim_dat <- tibble(
+  targetposition = factor(c(1:10)), 
+  mean = c(550,350,225, 150 , 100, 100, 150,225,350,550),
+  sd = c(seq(100,50, length.out = 5), seq(50, 100, length.out = 5)),
+  col = c("no","no","no","no","yes","yes","no","no","no","no")
+)%>%
+  expand_grid(id = as.character(c(1:50)))%>%
+  rowwise()%>%
+  mutate(impr = rnorm(1, mean, sd))
+
+ggplot(sim_dat, aes(x = targetposition, y= mean, col = col))+
+  background_image(im2) + 
+  geom_point(size = 3)+
+  geom_jitter(aes(y = impr), alpha = 0.1, width = 0.1)+
+  scale_color_manual(values = c("black", "firebrick"), guide = "none")+
+  ylim(0, 1000)+
+  labs(x = "Target position (binned)", y = "Imprecision")+
+  theme_few()
+
+ggsave("../visuals/target_position_model_center.png", width = 6.8, height = 4)
+
+im3 <- readPNG("../visuals/gazemodel-cc-side.png")
+im4 <- matrix(rgb(im3[,,1],im3[,,2],im3[,,3], im3[,,4] * 0.5), nrow=dim(im3)[1])
+
+sim_dat2 <- tibble(
+  targetposition = factor(c(1:10)), 
+  mean = c(550,350,225, 150 , 100, 100, 150,225,350,550),
+  sd = c(seq(100,50, length.out = 5), seq(50, 100, length.out = 5)),
+  col = c("yes","no","no","no","no","no","no","no","no","yes")
+)%>%
+  expand_grid(id = as.character(c(1:50)))%>%
+  rowwise()%>%
+  mutate(impr = rnorm(1, mean, sd))
+
+ggplot(sim_dat2, aes(x = targetposition, y= mean, col = col))+
+  background_image(im4) + 
+  geom_point(size = 3)+
+  geom_jitter(aes(y = impr), alpha = 0.1, width = 0.1)+
+  scale_color_manual(values = c("black", "firebrick"), guide = "none")+
+  ylim(0, 1000)+
+  labs(x = "Target position (binned)", y = "Imprecision")+
+  theme_few()
+
+ggsave("../visuals/target_position_model_edge.png", width = 6.8, height = 4)
 ```
@@
 
-ggplot()+
+ndata_all <- ddata%>%
+  distinct(ageinyears)
+
+post_all <- fitted(bm_base, newdata = ndata_all, re_formula = NA)%>%
+  as_tibble() %>%
+  bind_cols(ndata_all)%>%
+  mutate(ageinyears = ageinyears + min(data$ageinyears))
+
+pagg_dev <- ggplot()+
   geom_point(data = ddata, aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
-  geom_smooth(data = post, aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
-  theme_minimal()+
-  scale_fill_manual(name = "Community", values = colors)+
-  scale_color_manual(name = "Community", values = colors)+
+  #geom_smooth(data = post, aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .1, size = 0)+
+  #geom_line(data = post, aes(x = ageinyears, y = Estimate, fill =community, col = community), stat = "identity", alpha = .4)+
+  geom_smooth(data = post_all, aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5), stat = "identity", alpha = 0.5, col = "#555555", size = 1.5)+
+  theme_few()+
+    scale_x_continuous(limits = c(2,10))+
+  scale_y_continuous(limits = c(0,1000))+
+  scale_fill_manual(name = "Community", values = colors, guide = "none")+
+  scale_color_manual(name = "Community", values = colors, guide = "none")+
   labs(x = "Age", y="Imprecision")+
-  theme(legend.position = "right")+
-  facet_wrap(~continent, nrow = 2)#+guides(col = "none", fill = "none")
+  theme(legend.position = "right")
 ```
@@
 ```{r}
-ggsave("../visuals/dev.png", width = 12, height = 8, bg = "white")
+pind <- ggplot()+ 
+ geom_point(data = ddata, aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
+  geom_smooth(data = post, aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
+  theme_few()+
+  scale_fill_manual(name = "Community", values = colors, guide = "none")+
+  scale_color_manual(name = "color", values = colors, guide = "none")+
+  labs(x = "Age", y="Imprecision")+
+  scale_x_continuous(limits = c(2,10))+
+  scale_y_continuous(limits = c(0,1000))+
+  theme(legend.position = c(0.7, 0.9), legend.background = element_blank(),axis.title.x = element_blank(), axis.title.y = element_blank(), axis.ticks.y = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.text.y = element_blank())+
+  facet_wrap(~community, nrow = 3)#+guides(col = "none", fill = "none")
+```
+
+```{r}
+plot_grid(
+  pagg_dev, pind, rel_widths = c(1,1.5), align = "h"
+)
+```
+
+```{r}
+ggsave("../visuals/dev2.png", width = 12, height = 4, bg = "white", scale = 1.25)
+```
+
+```{r}
+tc_ind<- data%>%
+  mutate(targetposition = factor(targetposition, levels = c(1:10)))%>%
+  group_by(community, subjid, targetposition)%>%
+  summarise(mean = mean(abs(clickdistfromtargetcenterx)))
+
+tc_agg<- data%>%
+  mutate(targetposition = factor(targetposition, levels = c(1:10)))%>%
+  group_by(targetposition)%>%
+  tidyboot_mean(col= abs(clickdistfromtargetcenterx))
+
+tc_com<- data%>%
+  mutate(targetposition = factor(targetposition, levels = c(1:10)))%>%
+  group_by(community, targetposition)%>%
+  tidyboot_mean(col= abs(clickdistfromtargetcenterx))
+
+ptagg <- ggplot()+
+  geom_jitter(data = tc_ind, aes(x = targetposition, y = mean, col = community), alpha = .05, height = 0, width = 0.2)+
+  geom_pointrange(data =tc_agg, aes(x = targetposition, y = mean, ymin = ci_lower, ymax = ci_upper),pch = "-", col = "#555555", size = 3, stroke = 1.5, linewidth = 2)+
+  #geom_pointrange(data =tc_com, aes(x = targetposition, y = mean, ymin = ci_lower, ymax = ci_upper, col = community),pch = 1, alpha = 0.2, position = position_dodge(width = 0.25))+
+  labs(x = "Target position (binned)", y = "Imprecision")+
+  scale_color_manual(name = "", guide = "none", values = colors)+
+  ylim(0,1000)+
+  theme_few()
+
+ptind <- ggplot()+
+  geom_pointrange(data =tc_com, aes(x = targetposition, y = mean, ymin = ci_lower, ymax = ci_upper, col = community),pch = "-", size = 1)+
+  labs(x = "", y = "")+
+  scale_color_manual(name = "", guide = "none", values = colors)+
+  ylim(0,1000)+
+  theme_few()+
+  theme(legend.position = c(0.7, 0.9), legend.background = element_blank(),axis.title.x = element_blank(), axis.title.y = element_blank(), axis.ticks.y = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.text.y = element_blank())+
+  facet_wrap(~community, nrow = 3)#+guides(col = "none", fill = "none")
+```
+```{r}
+plot_grid(
+  ptagg, ptind, rel_widths = c(1,1.5), align = "h"
+)
+```
+
+```{r}
+ggsave("../visuals/tc2.png", width = 12, height = 4, bg = "white", scale = 1.25)
+```
+
+```{r}
+plot_grid(
+plot_grid(
+  pagg_dev, pind, rel_widths = c(1,1.5), align = "h", axis = "bt",labels = c("A", "B")
+),
+plot_grid(
+  ptagg, ptind, rel_widths = c(1,1.5), align = "h", axis = "bt", labels = c("C", "D")
+), nrow = 2, align = "v"
+)
+```
+```{r}
+ggsave("../visuals/fig2_alt2.png", width = 12, height = 8, bg = "white", scale = 1.25)
 ```
@@
   geom_point()
+```
+
+# Inward clicks
+
+```{r}
+
+iclick = data%>%
+  group_by(community, targetposition)%>%
+  summarise(click_dist_mean = mean(clickdistfromtargetcenterx))
+  mutate(click_dist_mean = ifelse(targetposition< 6, -click_dist_mean, click_dist_mean))
+
+piclick <- data%>%
+  mutate(fill1 = ifelse(targetcenterx < 960, -clickdistfromtargetcenterx, clickdistfromtargetcenterx), 
+         fill = ifelse(fill1 < 0, "yes", "no"))%>%
+  ggplot(aes(x = clickdistfromtargetcenterx, y = community))+
+  #geom_density_ridges(data = .%>%filter(fill == "yes"), alpha = 0.5, col = NA, fill = "#85AD00",bandwidth = 200)+
+  #geom_density_ridges(data = .%>%filter(fill == "no"), alpha = 0.5, col = NA, fill = "grey",bandwidth = 200)+
+  geom_density_ridges(alpha = .75,  bandwidth = 200, fill = "grey", col = "white")+
+  geom_vline(xintercept = 0, lty = 1, size = 1)+
+  facet_grid(~factor(targetposition))+
+  labs(x = "Click distance from target", y = "")+
+  scale_x_continuous(breaks = c(0), limits = c(-1500, 1500))+
+  scale_y_discrete(limits=rev)+
+  #scale_fill_manual(values = c("grey","#85AD00"))+
+  scale_color_manual(name = "", guide = "none", values = colors)+
+  geom_point(data = iclick, aes(x = click_dist_mean, y = community), col = "firebrick", size = 1, stroke = 1)+
+  theme_few()
+```
+
+```{r}
+plot_grid(
+plot_grid(
+  pagg_dev, pind, rel_widths = c(1,1.5), align = "h", axis = "bt",labels = c("A", "B")
+),
+plot_grid(
+  ptagg, ptind, rel_widths = c(1,1.5), align = "h", axis = "bt", labels = c("C", "D")
+), 
+piclick,
+nrow = 3, align = "v", rel_heights = c(1,1, 0.6)
+)
+```
+
+```{r}
+ggsave("../visuals/fig2_alt3.png", width = 12, height = 10, bg = "white", scale = 1.4)
 ```
@@
 ```
+
+```{r}
+world <- map_data("world")
+```
+
+```{r}
+gWorld <- world%>%
+  filter(region != "Antarctica")%>%
+  mutate(fill = ifelse(region %in% c("Turkey", "Germany", "Kenya"), "out", "in"))%>% 
+  filter(! long > 180)
+```
+
+```{r}
+ggplot(data = gWorld%>%filter(! long  < -30, long < 60,  lat > -40, lat < 70 ), mapping = aes(x = long, y = lat, group = group)) + 
+  coord_map("moll")+
+  geom_polygon(aes(fill = fill), col = NA, linewidth = 0) +
+  scale_fill_manual(breaks = c("out", "in"), values = c( "black", "#f2f2f2"), guide = "none")+
+  plain
+
+library(rworldmap)
+cont <- map_data(coastsCoarse)
+plot(coastsCoarse)
+```
+
+```{r}
+ggsave("../../../../../../Desktop/map.png", width = 4, height = 4, scale = 1.3)
+```
+
+```{r}
+gWorld2 <- world%>%
+  filter(region != "Antarctica")%>%
+  mutate(fill = ifelse(region %in% c("Turkey", "Germany", "Kenya", "USA", "Mexico", "Argentina", "Colombia", "Morocco", "Nigeria", "Namibia", "India", "China", "Malaysia", "Australia", "Zambia", "Japan", "Spain", "UK", "Republic of Congo", "Sweden", "Turkmenistan"), "out", "in"))%>%
+  filter(! long > 180)
+```
+
+```{r}
+ggplot(data = gWorld2, mapping = aes(x = long, y = lat, group = group)) + 
+  coord_map("moll")+
+  geom_polygon(aes(fill = fill), col = NA, linewidth = 0) +
+  scale_fill_manual(breaks = c("out", "in"), values = c( "#DBD56E", "grey"), guide = "none")+
+  plain
+```
+
+```{r}
+ggsave("../../../../../../Desktop/map2.png", width = 12, height = 8, scale = 1)
+```

### 2024-03-14 analysis/gafo-cc-model.Rmd
finalize model comparison

@@
 #   saveRDS("../model/output/mexico_model_comparison.rds")
-
- mexico_model_comparison <- readRDS("../model/output/mexico_model_comparison.rds")
+# 
+#  mexico_model_comparison <- readRDS("../model/output/mexico_model_comparison.rds")
 ```
@@
 #      fread("../model/output/akure_model_comparison_chain4.csv"),
-#      fread("../model/output/akure_model_comparison_chain5.csv"),
+#      fread("../model/output/akure_model_comparison_chain52.csv"),
 #      fread("../model/output/akure_model_comparison_chain6.csv")
@@
 #   saveRDS("../model/output/bandongo_model_comparison.rds")
-
+# 
 bandongo_model_comparison <- readRDS("../model/output/bandongo_model_comparison.rds")
@@
 ```{r, message=FALSE, warning=F}
-khwe_model_comparison <- rbindlist(
-  list(
-    fread("../model/output/khwe_model_comparison_chain1.csv"),
-    fread("../model/output/khwe_model_comparison_chain2.csv"),
-    fread("../model/output/khwe_model_comparison_chain3.csv"),
-    fread("../model/output/khwe_model_comparison_chain4.csv"),
-    fread("../model/output/khwe_model_comparison_chain5.csv"),
-    fread("../model/output/khwe_model_comparison_chain6.csv")
-  ), use.names=TRUE)%>%
-  group_by(chain, iteration, model)%>%
-  summarise(like = sum(loglike))%>%
-  mutate(community = "khwe")%>%
-  saveRDS("../model/output/khwe_model_comparison.rds")
+# khwe_model_comparison <- rbindlist(
+#   list(
+#     fread("../model/output/khwe_model_comparison_chain1.csv"),
+#     fread("../model/output/khwe_model_comparison_chain2.csv"),
+#     fread("../model/output/khwe_model_comparison_chain3.csv"),
+#     fread("../model/output/khwe_model_comparison_chain4.csv"),
+#     fread("../model/output/khwe_model_comparison_chain5.csv"),
+#     fread("../model/output/khwe_model_comparison_chain6.csv")
+#   ), use.names=TRUE)%>%
+#   group_by(chain, iteration, model)%>%
+#   summarise(like = sum(loglike))%>%
+#   mutate(community = "khwe")%>%
+#   saveRDS("../model/output/khwe_model_comparison.rds")
 
@@
 ```{r, message=FALSE, warning=F}
-plymouth_model_comparison <- rbindlist(
-  list(
-    fread("../model/output/plymouth_model_comparison_chain1.csv"),
-    fread("../model/output/plymouth_model_comparison_chain2.csv"),
-    fread("../model/output/plymouth_model_comparison_chain3.csv"),
-    fread("../model/output/plymouth_model_comparison_chain4.csv"),
-    fread("../model/output/plymouth_model_comparison_chain5.csv"),
-    fread("../model/output/plymouth_model_comparison_chain6.csv")
-  ), use.names=TRUE)%>%
-  group_by(chain, iteration, model)%>%
-  summarise(like = sum(loglike))%>%
-  mutate(community = "plymouth")%>%
-  saveRDS("../model/output/plymouth_model_comparison.rds")
+# plymouth_model_comparison <- rbindlist(
+#   list(
+#     fread("../model/output/plymouth_model_comparison_chain1.csv"),
+#     fread("../model/output/plymouth_model_comparison_chain2.csv"),
+#     fread("../model/output/plymouth_model_comparison_chain3.csv"),
+#     fread("../model/output/plymouth_model_comparison_chain4.csv"),
+#     fread("../model/output/plymouth_model_comparison_chain5.csv"),
+#     fread("../model/output/plymouth_model_comparison_chain6.csv")
+#   ), use.names=TRUE)%>%
+#   group_by(chain, iteration, model)%>%
+#   summarise(like = sum(loglike))%>%
+#   mutate(community = "plymouth")%>%
+#   saveRDS("../model/output/plymouth_model_comparison.rds")
 
@@
 ```{r, message=FALSE, warning=F}
-stanford_model_comparison <- rbindlist(
-  list(
-    fread("../model/output/stanford_model_comparison_chain1.csv"),
-    fread("../model/output/stanford_model_comparison_chain2.csv"),
-    fread("../model/output/stanford_model_comparison_chain3.csv"),
-    fread("../model/output/stanford_model_comparison_chain4.csv"),
-    fread("../model/output/stanford_model_comparison_chain5.csv"),
-    fread("../model/output/stanford_model_comparison_chain6.csv")
-  ), use.names=TRUE)%>%
-  group_by(chain, iteration, model)%>%
-  summarise(like = sum(loglike))%>%
-  mutate(community = "stanford")%>%
-  saveRDS("../model/output/stanford_model_comparison.rds")
+# stanford_model_comparison <- rbindlist(
+#   list(
+#     fread("../model/output/stanford_model_comparison_chain1.csv"),
+#     fread("../model/output/stanford_model_comparison_chain2.csv"),
+#     fread("../model/output/stanford_model_comparison_chain3.csv"),
+#     fread("../model/output/stanford_model_comparison_chain4.csv"),
+#     fread("../model/output/stanford_model_comparison_chain5.csv"),
+#     fread("../model/output/stanford_model_comparison_chain6.csv")
+#   ), use.names=TRUE)%>%
+#   group_by(chain, iteration, model)%>%
+#   summarise(like = sum(loglike))%>%
+#   mutate(community = "stanford")%>%
+#   saveRDS("../model/output/stanford_model_comparison.rds")
 
@@
 ```{r, message=FALSE, warning=F}
-turkey_model_comparison <- rbindlist(
-  list(
-    fread("../model/output/turkey_model_comparison_chain1.csv"),
-    fread("../model/output/turkey_model_comparison_chain2.csv"),
-    fread("../model/output/turkey_model_comparison_chain3.csv"),
-    fread("../model/output/turkey_model_comparison_chain4.csv"),
-    fread("../model/output/turkey_model_comparison_chain5.csv"),
-    fread("../model/output/turkey_model_comparison_chain6.csv")
-  ), use.names=TRUE)%>%
-  group_by(chain, iteration, model)%>%
-  summarise(like = sum(loglike))%>%
-  mutate(community = "turkey")%>%
-  saveRDS("../model/output/turkey_model_comparison.rds")
+# turkey_model_comparison <- rbindlist(
+#   list(
+#     fread("../model/output/turkey_model_comparison_chain1.csv"),
+#     fread("../model/output/turkey_model_comparison_chain2.csv"),
+#     fread("../model/output/turkey_model_comparison_chain3.csv"),
+#     fread("../model/output/turkey_model_comparison_chain4.csv"),
+#     fread("../model/output/turkey_model_comparison_chain5.csv"),
+#     fread("../model/output/turkey_model_comparison_chain6.csv")
+#   ), use.names=TRUE)%>%
+#   group_by(chain, iteration, model)%>%
+#   summarise(like = sum(loglike))%>%
+#   mutate(community = "turkey")%>%
+#   saveRDS("../model/output/turkey_model_comparison.rds")
 
@@
 
+## uganda
+
+```{r, message=FALSE, warning=F}
+# uganda_model_comparison <- rbindlist(
+#   list(
+#     fread("../model/output/uganda_model_comparison_chain1.csv"),
+#     fread("../model/output/uganda_model_comparison_chain2.csv"),
+#     fread("../model/output/uganda_model_comparison_chain31.csv"),
+#     fread("../model/output/uganda_model_comparison_chain4.csv"),
+#     fread("../model/output/uganda_model_comparison_chain5.csv"),
+#     fread("../model/output/uganda_model_comparison_chain61.csv")
+#   ), use.names=TRUE)%>%
+#   group_by(chain, iteration, model)%>%
+#   summarise(like = sum(loglike))%>%
+#   mutate(community = "uganda")%>%
+#   saveRDS("../model/output/uganda_model_comparison.rds")
+
+uganda_model_comparison <- readRDS("../model/output/uganda_model_comparison.rds")
+```
+
+```{r}
+uganda_model_comparison%>%
+  group_by(community, model,chain)%>%
+  summarise(margllh = logSumExp(like), 
+            n = n_distinct(iteration))%>%
+  pivot_wider(names_from = model, values_from = margllh)
+```
+
 ## windhoek
@@
 ```{r, message=FALSE, warning=F}
-windhoek_model_comparison <- rbindlist(
-  list(
-    fread("../model/output/windhoek_model_comparison_chain1.csv"),
-    fread("../model/output/windhoek_model_comparison_chain2.csv"),
-    fread("../model/output/windhoek_model_comparison_chain3.csv"),
-    fread("../model/output/windhoek_model_comparison_chain4.csv"),
-    fread("../model/output/windhoek_model_comparison_chain5.csv"),
-    fread("../model/output/windhoek_model_comparison_chain6.csv")
-  ), use.names=TRUE)%>%
-  group_by(chain, iteration, model)%>%
-  summarise(like = sum(loglike))%>%
-  mutate(community = "windhoek")%>%
-  saveRDS("../model/output/windhoek_model_comparison.rds")
+# windhoek_model_comparison <- rbindlist(
+# list(
+#   fread("../model/output/windhoek_model_comparison_chain1.csv"),
+#   fread("../model/output/windhoek_model_comparison_chain2.csv"),
+#   fread("../model/output/windhoek_model_comparison_chain3.csv"),
+#   fread("../model/output/windhoek_model_comparison_chain4.csv"),
+#   fread("../model/output/windhoek_model_comparison_chain5.csv"),
+#   fread("../model/output/windhoek_model_comparison_chain6.csv")
+# ), use.names=TRUE)%>%
+# group_by(chain, iteration, model)%>%
+# summarise(like = sum(loglike))%>%
+# mutate(community = "windhoek")%>%
+# saveRDS("../model/output/windhoek_model_comparison.rds")
 
@@
   turkey_model_comparison,
-  windhoek_model_comparison
+  windhoek_model_comparison,
+  uganda_model_comparison
 ) %>%

### 2024-03-14 analysis/gafo-cc-visuals.Rmd

@@
 library(ggridges)
+library(ggside)
 ```
@@
 ```
+
+# talk plots
+
+```{r}
+meand <- ddata%>%
+  filter(community %in% c("Leipzig (Germany)", "Akure (Nigeria)", "Malatya (Turkey)"))%>%
+  group_by(community)%>%
+  tidyboot_mean(col = mean_click)
+
+ggplot()+
+  #geom_point(data = ddata%>%filter(community %in% c("Akure (Nigeria)")), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
+    geom_point(data = ddata%>%filter(community %in% c("Leipzig (Germany)", "Akure (Nigeria)", "Malatya (Turkey)")), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
+  #geom_smooth(data = post%>%filter(community %in% c("Akure (Nigeria)")), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
+    geom_smooth(data = post%>%filter(community %in% c("Leipzig (Germany)",  "Akure (Nigeria)", "Malatya (Turkey)")), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
+  #geom_ysidedensity(data = ddata%>%filter(community %in% c("Akure (Nigeria)")), aes(y = mean_click, fill = community),col = "white",alpha = 0.5)+
+    #geom_ysidedensity(data = ddata%>%filter(community %in% c("Leipzig (Germany)",  "Akure (Nigeria)", "Malatya (Turkey)")), aes(y = mean_click, fill = community),col = "white",alpha = 0.5)+
+  geom_ysidepoint(data = meand, aes(y =mean, col = community, x = community), pch = 4, orientation = "x", size = 2, stroke = 2)+
+  geom_ysidesegment(data = meand, aes(y =ci_lower, yend = ci_upper , col = community, x = community, xend = community), size = 1)+
+  theme_classic()+
+    scale_x_continuous(limits = c(2,9))+
+  scale_y_continuous(limits = c(0,1000))+
+  scale_fill_colorblind(name = "Community", guide = "none")+
+  scale_color_colorblind(name = "Community", guide = "none")+
+  labs(x = "Age", y="Cognitive measure (Imprecision)")+
+  theme(legend.position = "right")+
+  theme(#panel.border = element_rect(color = "black",fill = NA,size = .25),
+        ggside.panel.border = element_blank(),
+        ggside.panel.scale.y = .25,
+        #axis.title.x = element_text(hjust = 0.2),
+        legend.position = c(0.85,0.3),
+        legend.background = element_blank())+
+  theme_ggside_void()
+```
+
+```{r}
+ggsave("../../../../../../Desktop/dev4.png", width = 10, height = 6, scale = 1)
+```

### 2024-03-14 paper/paper.tex

@@
 Previous developmental studies focused on the onset of gaze following in infancy (\emph{15}, \emph{16}).
-The 1311 participants in the study lived in 17 different communities spread over five continents (Fig.
+The 1377 participants in the study lived in 17 different communities spread over five continents (Fig.
 \ref{fig:fig1}A, Tab.
@@
 Individuals differ in their level of precision (indicated by alpha).
-Regardless of the level of precision, the further out the target lands, the less precise the model predicts individuals to be.}\label{fig:fig1}
+For a given level of precision, the further out the target lands, the less precise the model predicts individuals to be.
+Solid and transparent dots show simualted means and individual data points to illustrate the predicted effect of target position.}\label{fig:fig1}
 \end{figure}
@@
 America & Argentina & Buenos Aires & 105 (53) & 4.72 (3.00 - 6.96) & Spanish (Rioplatense) & high & 0.90\\
- & Mexico & Ocuilan & 125 (61) & 4.97 (2.57 - 6.95) & Spanish (Mexican) & medium & 0.77\\
- & USA & Stanford & 100 (56) & 5.00 (2.52 - 7.90) & English (American) & high & 0.98\\
+ & Mexico & Ocuilan & 127 (63) & 4.96 (2.57 - 6.95) & Spanish (Mexican) & medium & 0.77\\
+ & USA & Stanford & 98 (54) & 4.99 (2.52 - 7.90) & English (American) & high & 0.98\\
 Africa & Namibia & Hai||om & 60 (38) & 5.85 (2.74 - 8.34) & Hai||om & low & 0.05\\
@@
 \addlinespace
- &  & Windhoek & 41 (18) & 5.68 (2.66 - 8.66) & English (Nigerian) & high & 0.95\\
- & Nigeria & Akure & 114 (53) & 5.07 (2.57 - 7.33) & English (Nigerian) & high & 0.91\\
- & Rep. Congo & BaYaka & 28 (12) & 7.86 (3.94 - 10.56) & BaYaka & low & 0.00\\
+ &  & Windhoek & 39 (17) & 5.69 (2.66 - 8.66) & English (Nigerian) & high & 0.95\\
+ & Nigeria & Akure & 114 (54) & 5.07 (2.57 - 7.33) & English (Nigerian) & high & 0.91\\
+ & Rep. Congo & BaYaka & 29 (13) & 7.80 (3.94 - 10.56) & BaYaka & low & 0.00\\
  &  & Bandongo & 30 (11) & 7.45 (3.50 - 10.95) & Lingala & low & 0.00\\
- & Sambia & Chimfunshi & 22 (5) & 5.98 (2.88 - 8.00) & Bemba & medium & 0.14\\
+ & Uganda & Nyabyeya & 125 (62) & 5.94 (2.67 - 8.92) & Bemba & medium & 0.34\\
 \addlinespace
- & Uganda & Nyabyeya & 51 (27) & 5.41 (3.27 - 8.21) & Swahili & medium & 0.49\\
+ & Zambia & Chimfunshi & 22 (5) & 5.98 (2.88 - 8.00) & Swahili & medium & 0.14\\
 Europe & Germany & Leipzig & 100 (48) & 4.88 (2.53 - 6.95) & German & high & 0.89\\
@@
 Asia & China & Beijing & 123 (62) & 5.47 (2.69 - 8.48) & Mandarin & high & 0.95\\
- & India & Pune & 155 (75) & 6.14 (3.06 - 8.83) & English (Indian) / Marathi & high & 0.92\\
+ & India & Pune & 148 (73) & 6.14 (3.06 - 8.83) & English (Indian) / Marathi & high & 0.93\\
 \addlinespace
- & Turkey & Malatya & 85 (40) & 5.02 (2.75 - 7.12) & Turkish & high & 1.00\\
+ & Türkiye & Malatya & 85 (40) & 5.02 (2.75 - 7.12) & Turkish & high & 1.00\\
 Oceania & New Zealand & Auckland & 43 (19) & 5.14 (2.81 - 8.75) & English (New Zealand) & high & 0.95\\
@@
 As the first step, we investigated developmental gains.
-Across all 17 communities, we found a substantial increase in average levels of precision with age (fixed effect: \(\beta\) = -0.30, 95\% HDI (-0.39 - -0.21); range of community-level effects: \(\beta_{min}\) = -0.06, 95\% HDI (-0.17 - 0.06) to \(\beta_{max}\) = -0.58, 95\% HDI (-0.69 - -0.46).
-There were marked differences between communities: highly market-integrated communities around the globe showed higher levels of precision compared to less market-integrated communities.
-However, we believe that these results are better explained by exposure to technology than market integration.
-We discuss them in more detail below.
-Differences between communities were small compared to differences between individuals: communities did not form homogeneous clusters but largely overlapping distributions in that some individuals from communities with a lower average level of precision performed better compared to some individuals from a setting with a very high average level of precision.
-Furthermore, in all communities, some 4-year-olds outperformed children two years older than them (see Fig.
+Across all 17 communities, we found a substantial increase in average levels of precision with age (fixed effect in Bayesian regression model (\emph{18}): \(\beta\) = -0.30, 95\% HDI (-0.40 - -0.21); range of community-level effects in model: \(\beta_{min}\) = -0.06, 95\% HDI (-0.17 - 0.06) to \(\beta_{max}\) = -0.59, 95\% HDI (-0.70 - -0.47).
+Nevertheless, there were also marked differences between communities (see Fig.
+\ref{fig:fig2}A).
+In a cross-validation procedure, in which we trained a regression model on a subset of the data (training data) to later predict the held out data (testing data) (\emph{19}), we found that a model that assumed cross-cultural variation to outperform simple models in 100\% of cases (see Supplemental Material).
+At first glance, it seems that highly market-integrated communities around the globe showed higher levels of precision compared to less market-integrated communities (see Tab.
+\ref{tab:tab1}).
+However, believe that these results are better understood in terms of exposure to technology and we discuss them in more detail below.
+Furthermore, average differences between communities were small compared to differences between individuals: communities did not form homogeneous clusters but largely overlapping distributions in that some individuals from communities with a lower average level of precision performed better compared to some individuals from a setting with a very high average level of precision.
+Similarly, in all communities, some 4-year-olds outperformed children two years older than them (see Fig.
 \ref{fig:fig2}A).
@@
 Consistent developmental gains alone cannot inform us about the cognitive processes children use when locating the agent's focus of attention.
-Recent computational work modeled gaze following as social vector estimation (\emph{18}).
+Recent computational work modeled gaze following as social vector estimation (\emph{20}).
 When observing the eyes, onlookers estimate a vector from the center of the eye through the pupil.
@@
 The processing signature was clearly visible across all 17 communities.
-Precision decreased when the agent looked at locations further away from the center (fixed effect: \(\beta\) = 0.48, 95\% HDI ( - 0.54); range of community-level effects: \(\beta_{min}\) = 0.58, 95\% HDI (0.51 - 0.66) to \(\beta_{max}\) = 0.22, 95\% HDI (0.05 - 0.38).
+Precision decreased when the agent looked at locations further away from the center (fixed effect: \(\beta\) = 0.47, 95\% HDI ( - 0.54); range of community-level effects: \(\beta_{min}\) = 0.58, 95\% HDI (0.51 - 0.66) to \(\beta_{max}\) = 0.16, 95\% HDI (-0.01 - 0.34).
 Visualization of the data showed the predicted u-shaped pattern in all communities (see Fig.
@@
 To rule out this alternative explanation, we directly compared three cognitive models that made different assumptions about how participants' responses were generated: the focal vector-based gaze estimation model described above, a center-bias model where participants always select the center, and a random guessing model where participants select random locations.
-For every community, we found overwhelming support for the gaze estimation model (min \(BF_{10}\) \textless{} 1000 for comparisons with both alternative models).
+For every community, we found overwhelming support for the gaze estimation model (min \(BF_{10}\) \textgreater{} 1000 for comparisons with both alternative models).
 Taken together, children from all 17 communities processed gaze in similar ways.
@@
 In addition to the gaze-following task, caregivers filled out a small questionnaire about children's access to screen-based technology and the composition of their households.
-On an individual level, we found that across communities, children with access to touchscreen devices had higher levels of precision (\(\beta\) = -0.14, SE = 0.04, 95\% CrI = -0.22 - -0.07).
+On an individual level, we found that across communities, children with access to touchscreen devices had higher levels of precision (\(\beta\) = , SE = , 95\% CrI = - ).
 On a community level, we also saw that average performance was lowest in the communities in which touchscreen devices were the least frequent (Fig.
@@
 
+Based on this, we also computed the number of older children living in the household.
+We did not pre-register this, but decided to also include this variable because prior work on advanced forms of social cognition has suggested that the presence of older siblings is slightly more predictive of development compared to other aspects of household composition (e.g., \emph{21}, \emph{22}, but see \emph{23}).
+We think that gaze following improves though practice during social interaction.
+Particularly supportive, we believe, are situations in which it is difficult to infer the goals and intentions of another person based on other information sources (e.g., language or context).
+In such situations, children have to pay closer attention to the interaction partner and use their gaze to make such inferences.
+We are well aware that the numbers in the questionnaire are very far removed from these forms of social interaction.
+Thus, at best, they are a very coarse approximation.
+As a consequence, we do not expect there to be a very strong link between the two.
+We sincerely hope that future work will be able to directly assess children's social interactions.
+
 On an individual level, other factors likely generated individual differences because there was substantial variation even in communities where almost all children had access to touchscreens.
-Previous work suggested that social cognition develops in social interaction (\emph{19}--\emph{21}), in particular, with older siblings (\emph{22}, \emph{23}).
-We found tentative support for this idea in the form of a small but consistent effect in the direction that participants living together with more children older than themselves had slightly higher levels of precision (\(\beta\) = -0.01, SE = 0.01, 95\% CrI = -0.04 - 0.01).
+Previous work suggested that social cognition develops in social interaction (\emph{24}--\emph{26}), in particular, with older siblings (\emph{21}, \emph{22}).
+We found tentative support for this idea in the form of a small but consistent effect in the direction that participants living together with more children older than themselves (relative to other children from the same setting) had slightly higher levels of precision (\(\beta\) = , SE = , 95\% CrI = - ).
 
 Following and understanding gaze is a foundational building block of human social cognition (\emph{8}, \emph{9}).
-A substantial body of work has explored the developmental onset of gaze following in a few selected cultural settings (\emph{10}--\emph{12}, \emph{15}, \emph{16}).
+A substantial body of work has explored the developmental onset of gaze following in a few selected cultural settings (\emph{10}--\emph{12}, \emph{15}, \emph{16}, \emph{27}).
 The data reported here provides evidence that children all over the world process gaze in the same way.
 Key performance signatures of a model that sees gaze following as a form of social vector estimation were found in the data of all 17 distinct cultural communities.
-The cognitive processes underlying gaze following are thus likely to be rooted in humans' evolved cognitive architecture, which is -- presumably -- later refined during social interaction.
-The phylogenetic roots of these processes might possibly lie much deeper as primates from a wide range of species follow gaze (\emph{24}--\emph{26}).
+The cognitive processes underlying gaze following are thus likely to be rooted in humans' evolved cognitive architecture, which is -- presumably -- later refined during social interaction (\emph{28}--\emph{30}).
+The phylogenetic roots of these processes might possibly lie much deeper as primates from a wide range of species follow gaze (\emph{31}--\emph{34}).
 Yet, if they also show the same processing signatures has yet to be explored.
@@
 Naturalistic data directly recording social interactions across communities would offer crucial information to close this explanatory gap.
-Recent work in the field of language acquisition has shown how technological innovations can be used to close this explanatory gap.
+Recent work in the field of language acquisition has shown how technological innovations can be used to close this explanatory gap (\emph{35}, \emph{36}).
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-burkner2019bayesian}{}}%
+\CSLLeftMargin{18. }%
+\CSLRightInline{P.-C. Bürkner, Bayesian item response modeling in r with brms and stan. \emph{arXiv preprint arXiv:1905.09501} (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-stengelin2023children}{}}%
+\CSLLeftMargin{19. }%
+\CSLRightInline{R. Stengelin, R. Ball, L. Maurits, P. Kanngiesser, D. B. Haun, Children over-imitate adults and peers more than puppets. \emph{Developmental Science} \textbf{26}, e13303 (2023).}
+
 \leavevmode\vadjust pre{\hypertarget{ref-prein2023variation}{}}%
-\CSLLeftMargin{18. }%
+\CSLLeftMargin{20. }%
 \CSLRightInline{J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-barresi1996intentional}{}}%
-\CSLLeftMargin{19. }%
-\CSLRightInline{J. Barresi, C. Moore, Intentional relations and social understanding. \emph{Behavioral and brain sciences} \textbf{19}, 107--122 (1996).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-perner1994theory}{}}%
-\CSLLeftMargin{20. }%
-\CSLRightInline{J. Perner, T. Ruffman, S. R. Leekam, Theory of mind is contagious: You catch it from your sibs. \emph{Child Development} \textbf{65}, 1228--1238 (1994).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rakoczy2022foundations}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-lewis1996social}{}}%
 \CSLLeftMargin{21. }%
-\CSLRightInline{H. Rakoczy, Foundations of theory of mind and its development in early childhood. \emph{Nature Reviews Psychology} \textbf{1}, 223--235 (2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-lewis1996social}{}}%
-\CSLLeftMargin{22. }%
 \CSLRightInline{C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ruffman1998older}{}}%
-\CSLLeftMargin{23. }%
+\CSLLeftMargin{22. }%
 \CSLRightInline{T.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-peterson2003opening}{}}%
+\CSLLeftMargin{23. }%
+\CSLRightInline{C.
+Peterson, V.
+Slaughter, Opening windows into the mind: Mothers' preferences for mental state explanations and children's theory of mind.
+\emph{Cognitive Development} \textbf{18}, 399--429 (2003).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-barresi1996intentional}{}}%
+\CSLLeftMargin{24. }%
+\CSLRightInline{J. Barresi, C. Moore, Intentional relations and social understanding. \emph{Behavioral and brain sciences} \textbf{19}, 107--122 (1996).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-perner1994theory}{}}%
+\CSLLeftMargin{25. }%
+\CSLRightInline{J. Perner, T. Ruffman, S. R. Leekam, Theory of mind is contagious: You catch it from your sibs. \emph{Child Development} \textbf{65}, 1228--1238 (1994).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rakoczy2022foundations}{}}%
+\CSLLeftMargin{26. }%
+\CSLRightInline{H. Rakoczy, Foundations of theory of mind and its development in early childhood. \emph{Nature Reviews Psychology} \textbf{1}, 223--235 (2022).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-moore2008development}{}}%
+\CSLLeftMargin{27. }%
+\CSLRightInline{C. Moore, The development of gaze following. \emph{Child Development Perspectives} \textbf{2}, 66--70 (2008).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-astor2020social}{}}%
+\CSLLeftMargin{28. }%
+\CSLRightInline{K.
+Astor, M.
+Lindskog, L.
+Forssman, B.
+Kenward, M.
+Fransson, A.
+Skalkidou, A.
+Tharner, J.
+Cassé, G.
+Gredebäck, Social and emotional contexts predict the development of gaze following in early infancy.
+\emph{Royal Society open science} \textbf{7}, 201178 (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-movellan2002development}{}}%
+\CSLLeftMargin{29. }%
+\CSLRightInline{J.
+R.
+Movellan, J.
+S.
+Watson, {``The development of gaze following as a bayesian systems identification problem''} in \emph{Proceedings 2nd International Conference on Development and Learning.
+ICDL 2002} (IEEE, 2002), pp.
+34--40.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-senju2015early}{}}%
+\CSLLeftMargin{30. }%
+\CSLRightInline{A.
+Senju, A.
+Vernetti, N.
+Ganea, K.
+Hudry, L.
+Tucker, T.
+Charman, M.
+H.
+Johnson, Early social experience affects the development of eye gaze processing.
+\emph{Current Biology} \textbf{25}, 3086--3091 (2015).}
+
 \leavevmode\vadjust pre{\hypertarget{ref-rosati2009looking}{}}%
-\CSLLeftMargin{24. }%
+\CSLLeftMargin{31. }%
 \CSLRightInline{A. G. Rosati, B. Hare, Looking past the model species: Diversity in gaze-following skills across primates. \emph{Current opinion in neurobiology} \textbf{19}, 45--51 (2009).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-tomasello1998five}{}}%
-\CSLLeftMargin{25. }%
+\CSLLeftMargin{32. }%
 \CSLRightInline{M. Tomasello, J. Call, B. Hare, Five primate species follow the visual gaze of conspecifics. \emph{Animal behaviour} \textbf{55}, 1063--1069 (1998).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-itakura2004gaze}{}}%
-\CSLLeftMargin{26. }%
+\CSLLeftMargin{33. }%
 \CSLRightInline{S. Itakura, Gaze-following and joint visual attention in nonhuman animals, \emph{Japanese Psychological Research}. \textbf{46} (2004)pp. 216--226.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kano2014cross}{}}%
+\CSLLeftMargin{34. }%
+\CSLRightInline{F.
+Kano, J.
+Call, Cross-species variation in gaze following and conspecific preference among great apes, human infants and adults.
+\emph{Animal Behaviour} \textbf{91}, 137--150 (2014).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bergelson2023everyday}{}}%
+\CSLLeftMargin{35. }%
+\CSLRightInline{E.
+Bergelson, M.
+Soderstrom, I.-C.
+Schwarz, C.
+F.
+Rowland, N.
+Ramirez-Esparza, L.
+R.
+Hamrick, E.
+Marklund, M.
+Kalashnikova, A.
+Guez, M.
+Casillas, others, Everyday language input and production in 1,001 children from six continents.
+\emph{Proceedings of the National Academy of Sciences} \textbf{120}, e2300671120 (2023).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-donnelly2021longitudinal}{}}%
+\CSLLeftMargin{36. }%
+\CSLRightInline{S.
+Donnelly, E.
+Kidd, The longitudinal relationship between conversational turn-taking and vocabulary growth in early language development.
+\emph{Child Development} \textbf{92}, 609--625 (2021).}
 

### 2024-03-14 paper/supplement.Rmd

@@
 library(kableExtra)
+library(pals)
+library(RColorBrewer)
 
@@
 ```
+```{r}
+qual_col_pals = brewer.pal.info[brewer.pal.info$colorblind == TRUE,]
+col_vector = unlist(mapply(brewer.pal, qual_col_pals$maxcolors, rownames(qual_col_pals)))
+colors=kelly(n=n_distinct(data$community)+1)
+colors <- colors[ !colors == '#F2F3F4']
+```
 
@@
 ```{r}
-page <- data%>%
-  group_by(community,continent)%>%
-  distinct(subjid, .keep_all = T)%>%
-  mutate(dens = approxfun(density(ageinyears))(ageinyears))%>%
-  ggplot(aes(y = community, x = ageinyears))+
-  facet_grid(continent~., scales = "free", space = "free_y")+
-  geom_density_ridges(
-    jittered_points = TRUE,
-    position = position_points_jitter(width = 0, height = 0),
-    point_shape = '|',  point_alpha = 0.5, alpha = 0.7,
-  )+
-  labs(x = "Age (in years)", y= "")+
-  theme_few()+
-  theme(strip.background = element_blank(),strip.text.y = element_blank())
-
-pred_agg_i <- data%>%
-  mutate(older_children = children - 1 - younger_children)%>%
-  group_by(community, subjid)%>%
-  summarise(screen = mean(screen, na.rm = T),
-            touchscreen = mean(touchscreen, na.rm = T),
-            older_children = mean(older_children, na.rm = T),
-            household = mean(household, na.rm = T))
-
-pred_agg_g <- data%>%
-  mutate(older_children = children - 1 - younger_children)%>%
-  group_by(community, continent)%>%
-  summarise(screen = mean(screen, na.rm = T),
-            touchscreen = mean(touchscreen, na.rm = T),
-            older_children = mean(older_children, na.rm = T),
-            younger_children = mean(younger_children, na.rm = T),
-            children = mean(children, na.rm = T),
-            household = mean(household, na.rm = T))%>%
-  pivot_longer(names_to = "dem", values_to = "value", cols = c(screen, touchscreen, older_children,children, younger_children, household))
-
-ppred <- pred_agg_g%>%
-  filter(dem == "screen" | dem == "touchscreen")%>%
-  ggplot(aes(y = community, x = dem, fill = value))+
-  geom_point(pch = 22, size = 10, stroke = 0)+
-  facet_grid(continent~., scales = "free", space = "free_y")+
-  labs(x = "", y= "")+
-  scale_fill_viridis_c(name = "Prevalence")+
-  theme_few()+
-  scale_x_discrete(guide = guide_axis(n.dodge = 2))+
-  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), strip.text.y.right = element_text(angle = 0))
+# page <- data%>%
+#   group_by(community,continent)%>%
+#   distinct(subjid, .keep_all = T)%>%
+#   mutate(dens = approxfun(density(ageinyears))(ageinyears))%>%
+#   ggplot(aes(y = community, x = ageinyears))+
+#   #facet_grid(continent~., scales = "free", space = "free_y")+
+#   geom_density_ridges(
+#     jittered_points = TRUE,
+#     position = position_points_jitter(width = 0, height = 0),
+#     point_shape = '|',  point_alpha = 0.5, alpha = 0.7,
+#   )+
+#   labs(x = "Age (in years)", y= "")+
+#   theme_few()+
+#   theme(strip.background = element_blank(),strip.text.y = element_blank())
+# 
+# pred_agg_i <- data%>%
+#   mutate(older_children = children - 1 - younger_children)%>%
+#   group_by(community, subjid)%>%
+#   summarise(screen = mean(screen, na.rm = T),
+#             touchscreen = mean(touchscreen, na.rm = T),
+#             older_children = mean(older_children, na.rm = T),
+#             household = mean(household, na.rm = T))
+# 
+# pred_agg_g <- data%>%
+#   mutate(older_children = children - 1 - younger_children)%>%
+#   group_by(community, continent)%>%
+#   summarise(screen = mean(screen, na.rm = T),
+#             touchscreen = mean(touchscreen, na.rm = T),
+#             older_children = mean(older_children, na.rm = T),
+#             younger_children = mean(younger_children, na.rm = T),
+#             children = mean(children, na.rm = T),
+#             household = mean(household, na.rm = T))%>%
+#   pivot_longer(names_to = "dem", values_to = "value", cols = c(screen, touchscreen, older_children,children, younger_children, household))
+# 
+# ppred <- pred_agg_g%>%
+#   filter(dem == "screen" | dem == "touchscreen")%>%
+#   ggplot(aes(y = community, x = dem, fill = value))+
+#   geom_point(pch = 22, size = 10, stroke = 0)+
+#   #facet_grid(continent~., scales = "free", space = "free_y")+
+#   labs(x = "", y= "")+
+#   scale_fill_viridis_c(name = "Prevalence")+
+#   theme_few()+
+#   scale_x_discrete(guide = guide_axis(n.dodge = 2))+
+#   theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), strip.text.y.right = element_text(angle = 0))
 ```
@@
 
+Akure is situated in the Ondo State in southwest Nigeria. About 800,000 people live in this medium-sized city, and most of them are from the nearby urban and rural areas.
+
+There are two different seasons in Akure's tropical climate: the wet season, which runs from April to October, and the dry season, which runs from November to March.
+Rich vegetation, including deep forests and productive agriculture, is what defines the city.
+
+Akure's natural surroundings are enhanced by the abundant vegetation that includes dense forests, beautiful farmlands, and vivid flora, which is fostered by the climate and fertile soils.
+
+Akure boasts a diverse populace, representing a cultural mosaic where the Yoruba, Igbo, and Hausa communities coexist harmoniously.
+While the Yoruba ethnicity predominates, English serves as a widely spoken language alongside the native tongue.
+
+Over centuries, Akure has cultivated a sense of unity among its residents, transcending ethnic boundaries and nurturing a strong community spirit grounded in mutual respect and cooperation.
+This communal ethos extends from familial bonds – encompassing both nuclear and extended families – to broader social networks within neighborhoods, workplaces, and religious congregations.
+Akure's evolution from a traditional Yoruba kingdom to a thriving urban metropolis is deeply embedded in history and has a rich cultural legacy.
+The landscape is dotted with evidence of old kingdoms and communities, highlighting the city's lasting influence and crucial role in the history of the area.
+
+The primary industry of Akure is agriculture, with a large number of residents working in a variety of farming-related fields including agricultural cultivation, animal husbandry, and the extraction of palm oil.
+In addition to providing for livelihoods, this traditional subsistence approach maintains cultural customs and connections to the land, tying communities to their agricultural origins.
+
+The variety of architectural styles and types of homes found in the city are reflected in the housing landscape.
+Akure offers a diverse range of housing options, including modern urban dwellings scattered across the city and ancient mud-brick homes tucked away in rural hamlets.
+These housing options can accommodate nuclear families, extended kin networks, and communal living arrangements.
+
+A set of fundamental principles that are deeply embedded in the fabric of Akure society define parenting there.
+Parents are essential in passing on cultural legacy and forming the identities of future generations because they emphasize reverence for elders, community cohesion, and the value of education.
+Cultural festivals, ceremonies, and rite of passage serve as platforms for imparting values and fostering social cohesion within the community.
+
+The differences in parents' educational attainment in Akure are a reflection of their socioeconomic status and differences in access to formal education.
+Childcare practices often involve extended family members, particularly grandparents, who play significant roles in nurturing and guiding children.
+The city is home to a wide range of educational institutions including public and private schools, that provide extensive curriculum that incorporate standard academic disciplines along with enrichment and cultural education initiatives.
+
+Akure has embraced technology in recent years, with a notable increase in digital adoption, especially among its younger population.
+The widespread availability of reasonably priced smartphones and other touchscreen devices has contributed to the growing integration of technology into everyday life, affecting both urban and peri-urban areas.
+This technological revolution has changed social interactions and cultural dynamics within the community by democratizing access to information, communication, and entertainment.
+
+For this study, participants were recruited from churches during Sunday services and residences during community visits within the city of Akure, ensuring a wide representation of its vibrant population.
+
 **References and further readings:**
 
-* ...
+* ttps://worldpopulationreview.com/world-cities/akure-population
 
@@
 
+Buenos Aires is the capital of Argentina and located in the North-East of the country, on the shores of the Rio de la Plata.
+Administratively, the city is autonomous (Autonomous City of Buenos Aires) and has a separate administration from the surrounding Province of Buenos Aires.
+The city has a population of about 3 million inhabitants and the larger metropolitan area of about 15 million inhabitants.
+The majority of the population are either of European descent or of mixed descent, and about 2% of the population is of indigenous descent (e.g., Quechua, Guaraní, Mapuche, Aymara).
+Spanish is the predominant language in Buenos Aires, and the local dialect is known as Rioplatense Spanish.
+
+The city has a humid, subtropical climate and has generally mild weather.
+The average temperatures range from 11 degrees Celsius (July) to 25 degrees (January), but heat waves are common during the summer months (December to February).
+
+Buenos Aires was first established during Spanish colonization in the 16th century and was involved in trans-Atlantic trade when it became the capital of the Viceroyalty of Rio de la Plata (1776).
+The War of Independence against the Spanish crown lasted from 1810 to 1816 and was followed by an internal civil war between federalists and centralists over the constitution of the nation state.
+In the present day, Argentina is a presidential federal republic and Buenos Aires is its political and cultural center.
+
+Moreover, the city is the commercial, financial, and industrial hub of Argentina and a major site for tourism.
+Buenos Aires has a market economy and the main economic activities center on the service sector (e.g.
+finance, commerce, tourism, social services) and, to some extent, manufacturing.
+The city contributes about 20% to the Gross Domestic Product of Argentina.
+Most people in Buenos Aires live in apartment buildings, but informal settlements have been growing over the last decades.
+Argentina has experienced one of the highest inflation rates in the world in the past years and poverty has been steadily increasing—though poverty rates in the city of Buenos Aires tend to be lower than in the surrounding Buenos Aires Province.
+
+Commonly, children grow up in nuclear families, but ties with extended family tend to be strong.
+Generally, family and closeness to family are important cultural values in Argentina.
+Traditionally, female caregivers had a central role in the family, but this has been undergoing change in recent years, particularly, in middle-class families, with male caregivers taking on caring responsibilities, too.
+Argentina was the first country in South America to legalize same-sex marriage in 2010 and Buenos Aires in particular is perceived as progressive and liberal city.
+Some parenting values in middle-class families in Argentina, such as being responsive to the child and providing stimulating encounters, are similar to countries such as the U.S.
+or France.
+Caregivers tend to control their children’s schedules/activities, but children do not necessarily perceive this control as negative and caregivers are more permissive with younger children.
+
+Caregivers in the current sample mostly came from a middle-class background and usually had completed tertiary education.
+In Argentina, children attend nursery/kindergarten from two to three years of age with the last year of kindergarten, from age 5, being compulsory.
+Children attend primary school from age 6 years and secondary school from age 12 (secondary school lasts 5 or 6 years).
+Children are schooled in Spanish and usually learn a second language (usually English) from the age of 9.
+Children in Indigenous communities in other Argentinian Provinces (e.g.
+Salta Province, Formosa Province) will often speak their respective Indigenous language (e.g.
+Wichí) as their primary language and schools often rely on bilingual teaching assistants to help during schools lessons (that are predominantly taught in Spanish).
+Smartphones, tablets, and computers are common, and children are exposed to these devices from early on.
+Children were recruited from one local kindergarten by sending out information letters and consent forms to parents.
+Children who had parental consent to take part in the study were tested in Spanish in a quiet room in their kindergarten by a local experimenter.
+
 **References and further readings:**
 
-* ...
+* de Minzi, M.
+C.
+R., Lemos, V., Rubilar, J.
+V.
+(2014).
+Argentine culture and parenting styles in Parenting Across Cultures: Childrearing, Motherhood and Fatherhood in Non-Western Cultures, Ed.
+Selin, H., Springer, 277–292.
+
+* Bornstein, M. H. (1996). Ideas about parenting in Argentina, France, and the United States. International Journal of Behavioural Development, 19, 347–368.
+
+* Buenos Aires Cuidad. Useful information on Buenos Aires. Retrieved from: https://buenosaires.gob.ar/solarcities/en/conoce-buenos-aires
+
+* Benitez, J.
+(2022).
+Moving on up?
+The downside of the high life in Buenos Aires social housing.
+The Sociological Review.
+Retrieved from: https://thesociologicalreview.org/magazine/october-2022/verticality/moving-on-up/
+
+* Giménez, J.
+(2023).
+La pobreza aumentó al 40.1% en el primer semestre de 2023 y afecta al 56.2% de los niños.
+Retrieved from: https://chequeado.com/el-explicador/la-pobreza-aumento-al-401-en-el-primer-semestre-de-2023-y-afecta-al-562-de-los-ninos/
+
+* Instituto Nacional de Estadística y Censos, Censo Nacional de Población, Hogares y Viviendas (2022). Retrieved from: https://www.indec.gob.ar/indec/web/Nivel4-Tema-2-41-135
 
@@
 Chimfunshi wildlife orphanage is an NGO providing a home for about 150 chimpanzees.
-The sanctuary is located in the Copperbelt region in the northern part of Zambia close to DRC border.
+The sanctuary is located in the Copperbelt region in the northern part of Zambia close to the DRC border.
 The chimpanzees are housed in eight different enclosures; each of an area up to 121.5Ha.
-The Sanctuary provides housing, medical care and education for the employees and their families which are in total about 300 people living in 5 different compounds around Chimfunshi.
+The Sanctuary provides education, housing and medical care for the employees and their families which are in total about 300 people living in 5 different compounds around Chimfunshi.
 
@@
 In the past years they rehabilitated chimpanzees who were confiscated from poachers and from obsolete zoos and circuses worldwide.
-Today the sanctuary is managed by a Board of Trustees to ensure the long-term sustainability.
-
-Throughout the year Zambia has a mainly humid subtropical climate with a dry winter.
-There are three seasons.
-The rather cool dry season which lasts from May to August.
-A short hot dry season which is followed by a hot and humid rainy season from Novmeber to April.
-Overall, the temperatures are relatively mild due to the altitude of the country in the north but can be cold in winter.
-The sanctuary is nestled by woodland, savanna and situated near the Kafue river.
-
-The country has about 18 Million inhabitants.
-The population consists mostly of Bantu-speaking groups whereby Bemba is the largest ethnicity and the most spoken language beside Chewa, Tonga and Lozi.
-English which is the country's official language, is only spoken by about 2% of the population as a first language.
-For people with high education levels English is the most commonly used second language.
-Complex patterns of migrations created a broad linguistic and cultural variety.
-Due to the big mining industry, the population in the Copperbelt area consists of people from all parts of Zambia and even from neighboring countries.
-
-Zambia is mainly a Christian country (Protestant, Romanic Catholic, Jehovah’s Witnesses and some fundamentalists churches) but due to the Asian community, Hindus and Muslim are represented as well.
-The northeast and northwest part of Zambia is still strongly influenced by cultural traditions of the Congo basin.
-Zambian people still value traditional norms within their families, villages and clans.
-Such norms, ideals and morals are for example  mutual respect and reciprocity.
-
-The main sectors of the economy in Zambia is agriculture and copper mining and smelting especially in the northern Copperbelt region.
-Despite these large copper deposits, Zambia is one of the poorest countries in the world.
-Three quarters of the poor live in rural areas.
-As in other African countries there is a strong trend of movement from rural areas to urban centers whereby men migrate more often and women remain behind in villages.
-The housing style in rural areas vary a lot by ethnic group.
-Overall, mud and thatch, brick, or other materials are used for construction.
-
-People working at Chimfunshi wildlife orphanage are living in compounds.
-These are little settlements made of stone houses with corrugated iron roofs, a well to access clean water, solar systems for electricity and often little gardens to grow crops and/or keeping farm animals (e.g.
-chickens).
-
-Since independence day Zambia invested a lot in education.
-By now schooling is compulsory for 7- to 14-year-olds.
-Primary school lasts for 7 years and the secondary level for 5 years.
-The Twampane School at Chimfunshi was founded in 2011 to give the children of Chimfunshi employees the opportunity to attend school upto grade 9th.
-Almost 120 of the students live in the Chimfunshi area, the others come from the surrounding farms and settlements, thus the schools provides education for about 220 students.
-Children who perform well at school are enabled due to sponsorship programs to attend a secondary school.
-Furthermore, Chimfunshi offers children in the final grades on-site vocational training and further education.
-(9)
-Depending on the financial possibilities of the families, electrical devices with touch screens such as smartphones or laptops are available.
-Many still use cellphones and do not own a smartphone, which also makes access to such electronic devices more difficult for some children or even households.
-
-Before a study can be conducted in Chimfunshi, it must be presented to the Scientific Advisory Board of Chimfunshi.
-The board members and the sanctuary directress deliberate and decide whether a study can be carried out or not.
-Once these formalities have been clarified, the parents are approached with the help of an on-site assistant.
-The study program is explained to each family which are interested to participate in one way or the other in a study.
-Participation is recorded in writing and can be revoked by the parents at any time.
-Depending on the study, recruitment takes place in cooperation with the school teachers.
-(11)
+To ensure long-term sustainability, the sanctuary is managed by a Board of Trustees.
+
+Zambia experiences a predominantly subtropical climate.
+The temperatures throughout the year are relatively mild but can be cold in winter due to the altitude of the country in the north.
+The countries’ climate oscillates between a cool dry season (May to August) followed by a short hot and dry season which turns into a hot and humid rainy season lasting from November to April.
+The sanctuary is nestled amidst woodland and savanna, close to the Kafue River.
+
+The country, with approximately 18 million inhabitants, consists of a diverse population primarily composed of Bantu-speaking groups.
+Among these, the Bemba ethnicity stands out as the largest, accompanied by other significant groups such as Chewa, Tonga, and Lozi.
+While English serves as the official language, it is spoken natively by only around 2% of the population.
+However, for those with higher education levels, English becomes the predominant second language.
+The patterns of migrations has contributed to a rich tapestry of linguistic and cultural diversity across the nation., Due to a robust mining industry in the Copperbelt region, the population hailing from various corners of Zambia and even neighboring countries.
+
+Zambia, predominantly a Christian nation, encompasses a diverse religious landscape.
+Due to the presence of an Asian community, Hindu and Muslim are represented beside the Christian denominations including Protestant, Roman Catholic, Jehovah’s Witnesses, and various fundamentalist churches.
+Cultural traditions from the Congo basin significantly influence the northeast and northwest regions of Zambia.
+Despite modernization, Zambian society continues to uphold traditional norms within families, villages, and clans.
+These enduring values emphasize mutual respect and reciprocity as cornerstones of communal harmony.
+
+Agriculture and copper mining and smelting, particularly in the northern Copperbelt region, are the primary sectors of Zambia’s economy.
+Despite the abundance of copper deposits, Zambia ranks among the world’s poorest nations.
+The majority of the impoverished, three-fourths to be precise, reside in rural areas.
+Similar to other African nations, there’s a pronounced trend of migration from rural to urban areas, with men migrating more frequently while women often stay back in the villages.
+The architectural style in rural areas significantly differs across ethnic groups, with construction materials ranging from mud and thatch to brick and other resources.
+
+People employed at the Chimfunshi wildlife orphanage reside in compounds.
+These compounds are small communities comprised of stone houses topped with corrugated iron roofs.
+They feature wells for clean water access, solar systems for power, and frequently, small gardens for crop cultivation and/or livestock rearing, such as chickens.
+
+Since its Independence Day, Zambia has made significant investments in education.
+Currently, education is mandatory for children aged 7 to 14.
+The educational system is structured with a 7-year primary school program followed by a 5-year secondary level.
+In 2011, the Twampane School was established at Chimfunshi, providing the children of its employees the chance to pursue education up to the 9th grade.
+Approximately 120 students reside within the Chimfunshi area, while the rest commute from nearby farms and settlements, bringing the total student population to around 220.
+Sponsorship programs are in place to support academically outstanding students in attending secondary school.
+Additionally, Chimfunshi provides on-site vocational training and further education for students in the final grades.
+
+The availability of touchscreen electronic devices like smartphones or laptops depends on each family’s financial capacity.
+While many still utilize cellphones, the lack of smartphone ownership can pose challenges in accessing such devices for some children or households.
+
+Prior to initiating a study at Chimfunshi, it must first be submitted to the Chimfunshi Scientific Advisory Board.
+The board members, along with the sanctuary directress, review and determine the feasibility of the proposed study.
+Once the necessary formalities are sorted, an on-site assistant assists in reaching out to the parents.
+The study program is explained to each family expressing interest in participating in the study.
+Written consent is obtained for participation, which can be withdrawn by the parents at any point.
+Depending on the nature of the study, the recruitment process is carried out in collaboration with the school teachers.
 
@@
 
+The Hai||om are an indigenous group primarily living in the areas in and around the Etosha Pan of northern Namibia.
+In the current research, participants were recruited in small communities of 150 to 300 people in the Oshikoto and Otjozondjupa regions.
+
+They live in a dry Savannah of northern Namibia, characterized by the arid Namib Desert and the fringes of the Kalahari.
+The climate is hot and dry, with average temperatures exceeding 30°C and unsteady and minimal rainfall during summer.
+Vegetation is sparse, consisting mainly of drought-resistant shrubs and grasses with bloom of edible and non-edible plants during rain season.
+
+The Hai||om (i.e., treesleepers), also referred to as Heikum or Hai//om, speak Hai||om, which belongs to the Khoekhoe language family often recognized for containing distinct consonants (i.e., “click” sounds).
+Local dialects (i.e., =Ākhoe) differ across communities.
+They traditionally lived in small, semi-nomadic bands, loosely organized around kinship ties and shared leadership roles.
+Like many other forager communities of southern Africa, the Hai||om value egalitarianism, autonomy, and sharing on demand as foundational schemas organizing their social structure.
+
+The Hai||om are the indigenous people of the Etosha pan, have been living in this area for centuries.
+During the colonial era and German and South-African occupation of their lands, the Hai||om faced forced relocation from Etosha to the neighboring farmlands.
+The dispossession of their traditional lands together with political and societal discrimination continue having lasting impact on their communities and livelihoods.
+
+Traditionally, the Hai||om have been hunter-gatherers, relying on their vast knowledge of the desert environment to find food and water.
+They utilized a variety of techniques for hunting and gathering, including tracking, digging, and setting traps.
+They exhibited a semi-nomadic lifestyle, taking advantage of seasonal  resource availability.
+This self-sufficient lifestyle has been impacted by factors like climate change and government programs, but many Hai||om continue to practice traditional subsistence activities whenever possible.
+Today, the rural Hai||om communities participating in the current research practice a mixed subsistence combining seasonal and occasional farm work, small-scale gardening and animal husbandry, foraging, but also rely on government food programs.
+
+Most of the Hai||om families participating in this research house in small huts constructed from branches, corrugated iron, and animal dung.
+These dwellings are easily portable and household mobility remains high in these communities.
+Household composition is flexible, with extended families often living together and individuals moving between and within  communities based on kinship ties and resource availability.
+
+Hai||om child-rearing emphasizes autonomy, egalitarianism, cooperation, and sharing on demand as foundational schemas.
+Children are actively involved in daily activities from a young age, learning essential skills primarily through observation and participation, rather than direct pedagogy.
+Parents also instill cultural knowledge and values through storytelling and traditional practices.
+
+Due to their historical marginalization and remote location, access to formal education remains challenging for many Hai||om communities.
+In one community, children have access to a primary school from age 6 onward, whereas in the other community, children need to travel about 35km to access the next school.
+In both communities, dropout rates are reported low by teachers, likely due to multiple reasons, such as cultural mismatches between often authoritarian teaching styles and foreign learning content at schools, children’s autonomy in deciding on their learning environments, and secondary schools being located far away from their home communities.
+Traditional knowledge transfer remains vital, with elders playing a significant role in childcare and education.
+At the same time, children spend considerable amounts of their daily lives in mixed-age peer groups, which present important learning contexts for these children.
+Children learn through practical experience and participation in daily activities alongside adults and peers.
+
+Exposure to technology, particularly smartphones and other touchscreen devices, is highly limited among the Hai||om due to their remote location and traditional lifestyle.
+Electricity is available through solar panels at schools, farm houses, and few households, but the importance of electricity in people’s lives remains minimal.
+Some individuals, particularly younger generations, may have some exposure to technology through interactions with outsiders or limited access to shared devices, such as cellphones.
+
+It is important to note that this depiction provides an overview on the communities participating in the current research and does not reflect the diversity of livelihoods among urban-dwelling Hai||om people more generally.
+Their experiences and adaptations vary depending on individual circumstances and ongoing socio-economic changes.
+
+Children were recruited from their homes as part of a long term research project taking place in these communities.
+They were later tested in quiet locations either at the school building or vacant spaces in their communities.
+Testing was done by male adult experimenters and a research team known to the communities for about 8 years.
+The research was approved by the Max Planck Research Ethics Council, the Namibian Commission on Research Science and Technology (Permit Number RPIV01112021), the Namibian San Council, and the Ministry of Education, Arts and Culture of the Republic of Namibia.
+The study also adhered to guidelines for best practice in cross-cultural research (Bruno et al., 2022).
+Children received small amounts of candy as a compensation for their participation.
+
 **References and further readings:**
 
-* ...
+* Bruno, D., Pope-Caldwell, S.
+M., Haberl, K., Hanus, D., Haun, D., Leisterer-Peoples, S., Mauritz, S., Neldner, K., Sibilsky, A., & Stengelin, R.
+(2022).
+Ethical guidelines for good practice in cross-cultural research.
+Leipzig: Department of Comparative Cultural Psychology, Max Planck Institute for evolutionary anthropology.
+
+* Dieckmann, U. (2012). Born in Etosha: Living and learning in the wild. Legal Assistance Centre.
+
+* Dieckmann, U., Thiem, M., Dirkx, E., Hays, J., Legal Assistance Centre (Namibia), & Desert Research Foundation of Namibia (Eds.).
+(2014).
+Scraping the pot: San in Namibia two decades after independence.
+Land, Environment and Development Project of the Legal Assistance Centre and Desert Research Foundation of Namibia.
+
+* Friederich, R., & Lempp, H. (2014). Etosha: Hai||om heartland: ancient hunter-gatherers and their environment. Namibia Publishing House (Pty) Ltd.
+
+* Widlok, T. (1999). Living on Mangetti: “Bushman” Autonomy and Namibian Independence. Oxford University Press.
 
@@
 
+The Khwe (also referred to as Khoe, Khwedam, or Barakhoena) people reside in their ancestral lands within today’s Bwabwata National Park in northwestern Namibia and the bordering regions in Angola and Botswana.
+There is also a Khwe community in today’s South Africa that has moved there while Namibia became independent in 1990.
+The current research was conducted in the Namibian Zambezi region which is home to numerous small Khwe communities.
+There are an estimated 3,000 to 5,000 Khwe residing in Bwabwata as of today.
+
+Due to its sub-tropical climate, inhabitants of Bwabwata National Park experience hot and humid summers, whereas other seasons are much more characterized by a hot and dry climate.
+Bwabwata is a dual-use National Park in which wild animals, including large predators, elephants, and other animals native to the Zambezi region roam freely around the Khwe and Hambukushu settlements in the Park.
+
+The Khwe people speak Khwedam, which is part of the larger Khoe-Kwadi language spectrum.
+They traditionally lived in small, semi-nomadic bands with leadership based on a combination of age and experience.
+Today, people live in rural communities of varying size, ranging from one-household settlements to settlements of up to 600 people.
+Larger settlements have access to schools, medical centers, police stations, and small shops.
+
+The Khwe of Bwabwata are the indigenous people of the region and have resided in the area for centuries.
+They faced similar historical injustices as other indigenous groups of Southern Africa, such as the Hai||om, resulting from colonization and political marginalization.
+This includes, but is not limited to, colonial dispossession, forced relocation, and the neglect of their traditional leadership systems.
+These continue to have lasting impacts on their community and land rights until today.
+
+Traditionally, the Khwe lived as hunter-gatherers, relying on their extensive knowledge of the environment to hunt game, gather bushfood, and find water.
+This self-sufficient way of life has been impacted by various factors, including the migration of Hambukushu (Bantu) communities to the area, German colonization and South African occupation, governmental resettlement programs, and other environmental changes.
+Today, Khwe people are no more allowed to leave their settlements freely as part of the anti-poaching regulations of the dual-use National Park.
+However, traditional subsistence activities continue being an integral part of the cultural identity of many Khwe people.
+Their traditional subsistence is today supplemented with wage labor, seasonal harvesting programs, small-scale gardening and animal husbandry, as well as governmental and non-governmental support.
+
+Household composition is flexible, with extended families often residing together and individuals moving between groups based on kinship ties and resource availability.
+Before Namibian independence, the South African Military Forces had multiple camps in the region due to its proximity to the Angolan border.
+After independence, Khwe communities increasingly settled in the residential infrastructure they had left behind.
+Other communities live in small huts made of wood, dung, corrugated iron, and other building materials.
+
+Similar to the Hai||om, Khwe child-rearing emphasizes autonomy, egalitarianism as well as strong norms on cooperation and demand sharing.
+Children actively participate in daily activities from a young age, learning essential hunting, gathering, and survival skills through observation and participation.
+Parents also transmit cultural knowledge and values through storytelling and traditional practices.
+
+Access to formal education has been historically limited for the Khwe of Bwabwata due to their remote location and marginalization.
+As of today, formalized education presents a two-edged sword as it is perceived by many as an important opportunity for social improvement, while also contributing to the erosion of cultural and environmental knowledge and skills.
+In the community sampled here, children do have access to a local kindergarten and a combined school.
+Many learners attending school did not experience kindergarten education as they grew up in the smaller communities surrounding this larger settlement.
+Especially in early childhood, traditional knowledge transfer and parenting practices remain crucial, with elders playing a significant role in childcare and education.
+Children learn through practical experience and participation in daily activities alongside adults.
+Additionally, recent initiatives aim to improve access to formal education within the national park.
+
+Exposure to technology, particularly smartphones and other touchscreen devices, is generally limited among the Khwe of Bwabwata also due to their remote location, economic hardships, and lack of access to electricity.
+However, similar to the Hai||om, the level of access can vary depending on proximity to towns and settlements.
+Some individuals, especially younger generations, may have some exposure through interactions with external communities or shared devices.
+
+It is important to note that this is only an approximate depiction of the situation faced by the communities participating in the current research.
+It does by no means give credit to the diversity of livelihoods among the Khwe people more generally.
+Their experiences and adaptations vary depending on individual circumstances and ongoing socio-economic changes.
+
+Children were recruited for a long-term research project after consulting with community elders and representatives.
+The project was conducted in local schools or kindergartens and received necessary approvals from relevant ethical bodies in Namibia and Germany: The Max Planck Research Ethics Council, the Namibian Commission on Research Science and Technology (Permit Number RPIV01112021), the Namibian San Council, and the Ministry of Education, Arts and Culture of the Republic of Namibia.
+Self-commitment regarding research ethics aligned with departmental guidelines for best practice in cross-cultural research (Bruno et al., 2022).
+Testing was carried out by a male adult from the community alongside a familiar research team.
+The study adhered to strict ethical guidelines for cross-cultural research, and children received small tokens of appreciation for their participation.
+
 **References and further readings:**
 
-* ...
+* Dieckmann, U., Thiem, M., Dirkx, E., Hays, J., Legal Assistance Centre (Namibia), & Desert Research Foundation of Namibia (Eds.).
+(2014).
+Scraping the pot: San in Namibia two decades after independence.
+Land, Environment and Development Project of the Legal Assistance Centre and Desert Research Foundation of Namibia.
+
+* Nkengbeza, D., Kangumu, B., & Sibuku, C.
+(2021).
+The Perceptions of the KHWE (San) Community at Bwabwata on the Importance and Influence of Formal Education (SSRN Scholarly Paper 3886443).
+https://papers.ssrn.com/abstract=3886443
+
+* Koot, S., Beek, W. V., & Diemer, J. (2016). The Khwe of Namibia. Foragers between Game, Tourism, and Politics. Anthropos, 111(2), 497–512. https://doi.org/10.5771/0257-9774-2016-2-497
+
+* Paksi, A.
+(2019).
+‘We live in a modern time’: : Local perceptions of traditional knowledge and formal education among a Namibian San community.
+Hunter Gatherer Research, 5(1–2), 119–151.
+https://doi.org/10.3828/hgr.2019.6
+
+* Paksi, A.
+(2020).
+‘Surviving Development’: Rural development interventions, protected area management, and formal education with the Khwe San in Bwabwata National Park, Namibia.
+Faculty of Social Sciences, University of Helsinki.
 
@@
 It serves as a significant urban center within the state of Saxony.
-Geographically, leipzig is situated in the southernmost part of the North German Plain.
+Geographically, Leipzig is situated in the southernmost part of the North German Plain.
 
@@
 
-* City website for demographic information: https://english.leipzig.de
+* City website for demographic information: https://english.Leipzig.de
 * Otto, H., & Keller, H. (2016). Is there something like German parenting. Contemporary Parenting: a Global Perspective, 81-94.
@@
 
+Plymouth is a coastal city in the South West of England with a population of more than 260,000 inhabitants.
+About 91% of the population was born in the UK and of those born outside of the UK, the largest proportion comes from the EU (4.5%).
+95% of residents identified as White, 2.3% as Asian, and 1% as Black.
+English is the predominant language spoken in the city.
+
+The city has a temperate oceanic climate with average temperatures ranging from 4 to 20 degrees Celsius.
+Winters are generally mild, and temperatures rarely drop below zero degrees.
+Rain is frequent and highest in autumn and winter.
+
+The area was first settled in the Bronze Age.
+Plymouth is situated at the meeting point of two rivers (river Tamar, river Plym) and has a large natural harbour.
+Due to its location, the city has served as a shipping port and naval harbour throughout history.
+It played an important role in the Spanish-British war in the 16th century and was a departure port for settlers bound for North America in the early 17th century.
+Due to its importance as a naval port, the city was heavily bombed during the 2nd World War and most of the city center needed to be re-build post-war.
+
+In the present day, Plymouth is home to a major dockyard and the biggest naval base in Western Europe.
+The largest employers are the defence industry and the armed forces, the university, the national health service as well as maritime businesses.
+Tourism, particularly in the summer months, is another source of income.
+The city has some areas of very high deprivation (among the 1% of most deprived areas in England) and the median income (33k) is slightly below the UK median (35k).
+
+The city has a large waterfront area and several harbours and docks, and there is a large inner-city park.
+Housing in the city mostly consists of terraced and semi-detached houses with few multi-storey buildings.
+Children mostly grow up in nuclear families.
+Children in the current study came mostly from middle class families.
+In Western middle-class families care-giving is usually child-centered and parents are responsive to children’s needs and wishes.
+Autonomy and independence are valued but, compared to countries such as Germany, children are somewhat less independent.
+As the UK is a multicultural country (and multiculturalism is increasing), parenting values are heterogenous—though the population in Plymouth, as compared to the rest of the UK, is less heterogenous and predominantly White British.
+
+The UK has one of the highest childcare costs in Europe (52% of median female earnings).
+Nurseries will offer places for children from 3 months of age, but currently the government only subsidizes childcare from three years of age (caregivers receive 15 hours of free nursery care for three- and four-year-olds).
+Primary school starts at age 5 years, and secondary school at age 11 to 12 and lasts until 18 years.
+Education is compulsory in the UK, but children do not have to attend school and can be homeschooled instead.
+
+Children are exposed to technology from early on, including mobile phones and other touch screen devices.
+Children were mostly recruited through a local primary school and some additional children were recruited through personal contacts of one of the experimenters.
+Parents received information letters and consent forms.
+Experimenters also visited the school during drop off times in the morning to answer any questions parents may have had.
+Only children whose parents had consented to their participation took part in the study.
+In the school setting, two experimenters usually conducted the study in parallel in quiet rooms in the school.
+Some children who were recruited through personal contacts participated in the study online, facilitated by one experimenter.
+
 **References and further readings:**
 
-* ...
+* Bozicevic, L., Hill, J., Chandra, P.
+S., Omirou, A., Holla, C., Wright, N., & Sharp, H.
+(2023).
+Cross-cultural differences in early caregiving: levels of mind-mindedness and instruction in UK and India.
+Frontiers in Child and Adolescent Psychiatry, 2, 1124883-1124883.
+
+* Kagitcibasi, C. (2017). Family, self, and human development across cultures: Theory and applications. Routledge.
+
+* Pearson, E., & Rao, N. (2003). Socialization goals, parenting practices, and peer competence in Chinese and English preschoolers. Early Child Development and Care, 173(1), 131-146.
+
+* Plymouth City Council, Understanding Our Communities. Retrieved from: https://www.plymouth.gov.uk/understanding-our-communities
+
+* Mubashar, L.
+(2023).
+'Childcare puzzle': Which countries in Europe have the highest and lowest childcare costs?
+Retrieved from: https://www.euronews.com/next/2023/03/06/childcare-puzzle-which-countries-in-europe-have-the-highest-and-lowest-childcare-costs
 
@@
 
+Pune is located in the state of Maharashtra in western India.
+The city’s total area is 15.642 square kilometres and the municipal corporation area covers 518 square kilometers.
+It lies on the western margin of the Deccan plateau at an altitude of 1840 feet.
+It is on the leeward side of the Sahyadri mountain range which forms a barrier with the Arabian Sea.
+The population within city limits is 4.5 million while including the metro population, it stands at 7.1 million.
+Pune is one of the largest information technology hubs in India and is also an important automobile and manufacturing hub.
+Sixty-two percent of the population in Pune is under the age of 30.
+The top three industries that offer employment are automotive, manufacturing and information technology and start-ups.
+Automobile industries such as Tata Motors, Jaguar, Renault, Volkswagen, General motors, Skoda, Force motors, Kinetic motors  and Mercedes-Benz have their manufacturing plants in Chakan, an industrial area around Pune.
+Cummins, a leading manufacturer of diesel and natural gas engines as well as JCB, the farm equipment company are other renowned investors.
+The manufacturing industry provides employment to over 600,000 people while the IT sector employs over 350,000 people.
+About 2.2 million migrant workers are employed in the automobile, construction and medium scale manufacturing industries.
+
+Pune is referred to as the ‘Oxford of the East’ because of its reputed educational institutions and is also considered to be one of the most livable cities in India.
+The literacy rate in Pune is 86.15%.
+As a result of rapid industrialization since the 1960s, a large number of people moved to Pune.
+Since there was inadequate housing to meet the demand, there was an increase in the number of slum dwellers.
+Nearly half of the slum dwellers do not have in-house toilets and 10% do not have electricity.
+Pune experiences a tropical wet and dry climate with average temperatures ranging between 20 and 28 degrees Celsius.
+Summer, monsoon and winter are the three main seasons with May being the hottest month.
+During summer, i.e.
+mid-March to mid-June, temperatures can go as high as 42 degrees Celsius.
+Monsoon lasts from June to October with most of the annual rainfall of 722mm falling between June and September with July being the wettest month.
+In the months of December and January, temperatures remain around 29 degrees Celsius with overnight temperatures dropping to below 12 degrees.
+
+During the 18th century, Pune was part of the Maratha empire and seat of the Peshwas.
+Besides it has been ruled by dynasties such as the Rashtrakutas, Ahmednagar Sultanate, Mughals and Adil Shahi dynasty.
+The modern city of Pune is comprised of many distinct neighbourhoods.
+These include ‘peths’ [Marathi for locality] on the eastern bank of the Mutha river and the cantonment areas of Khadki and Camp.
+Pune is considered to be the cultural capital of Maharashtra with emphasis on education, arts and crafts, music and theater.
+The most common language spoken is Marathi.
+Hinduism is the major religion practiced by just under 80% of the population.
+Other religions practised are Islam, Buddhism, Jainism, Christianity, Sikhism and Zoroastrianism.
+Food is made of sorghum and pearl millets with a fairly large consumption of coconut, garlic and green chillies to spice up the food.
+
+Children in Pune normally enter school between the ages of 2.5 and 3.5.
+The school leaving exam is taken between the ages of 17 and 18.
+Grades 11th and 12th (equivalent to AS and A levels in the UK) may be attended in school or ‘junior college’ with the latter offering education up to the postgraduate level.
+Following a school day, it is not uncommon for children to attend tuition or focussed coaching in sports or arts.
+Most households will have at least one mobile phone as well as a laptop so children are exposed to technology fairly early.
+
+Children are taught to address their elders (either in English or the equivalent term in a local language) as ‘older brother/sister’, ‘uncle’, ‘aunty’ or ‘grandmother’/’grandfather’ even if they are not relatives.
+This is considered to be respectful.
+At times, children touch the feet of elders as a sign of respect.
+Parents encourage their children to visit family and friends particularly during festivals.
+For the current study, recruitment took place via personal contacts.
+Both schools have participated in previous research projects and the researcher is on the management committee of one of the schools.
+The researcher was given a separate quiet room to carry out testing.
+Normally, after one child finished the task, he or she would send their classmate who had volunteered for the project.
+In the case of very young children, the researcher would the children personally from their respective class and ensure that they were handed back to their teachers upon completion.
+
 **References and further readings:**
 
-* ...
+* https://en.wikipedia.org/wiki/Pune
+* https://www.iimb.ac.in/turn_turn/pune-industrial-workforce.php
+* https://pune.gov.in/culture-heritage/
+* https://www.bbc.com/travel/article/20181028-an-indian-city-with-audacious-attitude
 
@@
 The land is characterized by bay flats and hills with several rivers running through the city.
-San Jose’s climate is described as mild, semi-arid, and mediterranean.
+San Jose’s climate is described as mild, semi-arid, and Mediterranean.
 A wet season typically occurs between November and March with combined rainfall and an average daytime temperature of 50 degrees Fahrenheit.
@@
 
-Parental socialization goals in California typically emphasize tolerance, individualism, diversity, personal fulfillment, and holistic autonomy, but vary greatly as a result of its diverse populus.
+Parental socialization goals in California typically emphasize tolerance, individualism, diversity, personal fulfillment, and holistic autonomy, but vary greatly as a result of its diverse populous.
 Education and learning are seen as important aspects of children’s lives.
@@
 
+# dempred_agg <- data%>%
+#   group_by(community)%>%
+#   distinct(subjid, .keep_all = T)%>%
+#   select(subjid, community, continent, children, younger_children, household)%>%
+#   pivot_longer(names_to = "dem", values_to = "value", cols = c(children, younger_children, household))%>%
+#     mutate(dem = recode(dem,
+#                       younger_children = "younger children"),
+#          dem = factor(dem, levels = c("household", "children", "younger children")))%>%
+#   group_by(community, dem)%>%
+#   na.omit()%>%
+#   tidyboot_mean(col = value)
+#   
+# 
 # dempred <- data%>%
-#   group_by(community,continent)%>%
+#   group_by(community)%>%
 #   distinct(subjid, .keep_all = T)%>%
@@
 #   ggplot(aes(y = value, x = community))+
-#   facet_grid(dem~continent, scales = "free", space = "free_x")+
+#   facet_grid(dem~., scales = "free", space = "free_x")+
 #   geom_jitter(width = 0.2, height = 0.1, alpha = 0.1)+
@@
 # 
-# ggsave(plot = dempred, "../visuals/dempred.png", height = 6, width = 12, scale = 1)
+# ggsave(plot = dempred, "../visuals/dempred.png", height = 6, width = 10, scale = 1)
 
@@
 First, we tested whether there was substantial cross-cultural variation in performance.
-Second, we looked for signatures in the data that informed the hypothesis that children processed gaze in the same way across cultural settings.
+Second, we looked for signatures in the data that children processed gaze in the same way across cultural settings.
 Finally, we related performance in the task (on an individual level) to aspects of everyday experience, in particular the exposure to screen-based technology and social interaction (approximated by household composition).
 
-We used Bayesian Regression models fit in `R` [@r] using the package `brms` [@burkner2019bayesian] for all analyses except the cognitive models, which were implemented in the probabilistic programming language `webppl` [@dippl].
+We used Bayesian Regression models fit in `R` [@r] using the package `brms` [@burkner2017brms] for all analyses except the cognitive models, which were implemented in the probabilistic programming language `webppl` [@dippl].
 For regression models, we used the default priors built in to `brms`.
 The dependent variable in all regression models was imprecision, that is, the absolute distance between the true location of the balloon (to x-coordinate of its center) and the location where the participant touched the screen.
-We used a Log-normal distribution to model the data because the natural lower bound for imprecision is zero and the data was right skewed with a long tail to the right.
+We used a Log-normal distribution to model the data because the natural lower bound for imprecision is zero and the data was right skewed with a long tail.
 Numeric predictors that entered the models were scaled to have a mean of zero and a standard deviation of 1.
-For each model we ran four chains with 6000 iterations, removing the first 2000 for burn-in.
+For each model we collected 6000 samples from four chains, removing the first 2000 for burn-in.
 All models had converging chains (Rhat values < 1.01).
@@
 We pre-registered an analysis plan at https://osf.io/tdsvc.
-The analyses reported below follow the same logical as the pre-registered analyses but they differ substantially in detail.
+The analyses reported below follow the same logic as the pre-registered analyses but they differ substantially in detail.
 The main difference lies in the random effects structure we used in the models.
@@
 Furthermore, in multiple studies with the same task since the registration we never found any trial effects [@prein2023tango; @prein2023variation].
-We therefore removed trial from the models completely to reduce model complexity.
+We therefore removed trial from the models completely.
 On the other hand, we included random slopes for target centrality to be able to look at cross-cultural variation.
@@
 
-## Cross-cultural variation
+0## Cross-cultural variation
 
@@
 
-The results showed that the `culture_age` model made, by far, the best predictions and outperformed the `culture` model in `r mean(cv_cult$m3_beats_m2)*100`% and the `null` model in `r mean(cv_cult$m3_beats_m1)*100`% of cases.
-Furthermore, the `culture` model outperformed the `null` model in `r mean(cv_cult$m2_beats_m1)*100` % of cases.
+The results showed that the `culture_age` model made, by far, the best predictions and outperformed the `culture` model in `r round(mean(cv_cult$m3_beats_m2),2)*100`% and the `null` model in `r round(mean(cv_cult$m3_beats_m1),2)*100`% of cases.
+Furthermore, the `culture` model outperformed the `null` model in `r round(mean(cv_cult$m2_beats_m1),2)*100` % of cases.
 This suggests that there were substantial absolute and developmental differences between cultural settings (see Figure \@ref(fig:figdev)A).
@@
 In the second analysis focused on signatures in the data that suggest that children in all cultural settings use similar cognitive processes to infer the location of the balloon.
-The first -- weaker -- signature was simply an increase in performance with age.
+The first -- somewhat weaker -- signature was simply an increase in performance with age.
 The second -- stronger -- signature was a strong effect of target centrality.
@@
 
-This prediction is best understood by considering a similar phenomenon: pointing a torch light to a flat surface.
+These prediction is best understood by considering a similar phenomenon: pointing a torch light to a flat surface.
 The width of the light beam represents each individual's level of uncertainty in vector estimation and is represented in the model as a normal distribution around the true gaze vector with a participant specific standard deviation.
@@
 # ppred <- ggplot(pdraws, aes(x= post, y = community))+
-# 
 #   geom_density_ridges(col = "white", alpha = .75, fill = "grey")+
 #   geom_vline(xintercept = 0, lty = 3)+
-#   facet_grid(continent~type, scales = "free", space = "free_y")+
+#   facet_grid(~type, scales = "free", space = "free_y")+
 #   #stat_pointinterval(size = 0.1)+
@@
 # 
+# ndata_all <- devdata%>%
+#   distinct(ageinyears)
+# 
+# post_all <- fitted(bm_dev, newdata = ndata_all, re_formula = NA)%>%
+#   as_tibble() %>%
+#   bind_cols(ndata_all)%>%
+#   mutate(ageinyears = ageinyears + min(data$ageinyears))
 # 
@@
 ```{r}
-# tc_agg_data<- data%>%
+# pagg_dev <- ggplot()+
+#   geom_point(data = devdata, aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
+#   geom_smooth(data = post_all, aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5), stat = "identity", alpha = 0.5, col = "#555555", size = 1.5)+
+#   theme_few()+
+#     scale_x_continuous(limits = c(2,10))+
+#   scale_y_continuous(limits = c(0,1000))+
+#   scale_fill_manual(name = "Community", values = colors, guide = "none")+
+#   scale_color_manual(name = "Community", values = colors, guide = "none")+
+#   labs(x = "Age", y="Imprecision")+
+#   theme(legend.position = "right")
+# 
+# pind <- ggplot()+ 
+#  geom_point(data = devdata, aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
+#   geom_smooth(data = post, aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
+#   theme_few()+
+#   scale_fill_manual(name = "Community", values = colors, guide = "none")+
+#   scale_color_manual(name = "color", values = colors, guide = "none")+
+#   labs(x = "Age", y="Imprecision")+
+#   scale_x_continuous(limits = c(2,10))+
+#   scale_y_continuous(limits = c(0,1000))+
+#   theme(legend.position = c(0.7, 0.9), legend.background = element_blank(),axis.title.x = element_blank(), axis.title.y = element_blank(), axis.ticks.y = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.text.y = element_blank())+
+#   facet_wrap(~community, nrow = 3)
+
+```
+
+```{r}
+# tc_ind<- data%>%
 #   mutate(targetposition = factor(targetposition, levels = c(1:10)))%>%
-#   group_by(continent, community, targetposition)%>%
+#   group_by(community, subjid, targetposition)%>%
+#   summarise(mean = mean(abs(clickdistfromtargetcenterx)))
+# 
+# tc_agg<- data%>%
+#   mutate(targetposition = factor(targetposition, levels = c(1:10)))%>%
+#   group_by(targetposition)%>%
 #   tidyboot_mean(col= abs(clickdistfromtargetcenterx))
 # 
-# 
-# tam <- tc_agg_data%>%
-#   filter(continent == "Americas")%>%
-#   ggplot(., aes(x = targetposition, y = mean, col = community))+
-#   geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
-#   labs(x = "", y = "")+
-#   scale_color_colorblind(name = "", guide = "none")+
-#   facet_grid(continent~.)+
+# tc_com<- data%>%
+#   mutate(targetposition = factor(targetposition, levels = c(1:10)))%>%
+#   group_by(community, targetposition)%>%
+#   tidyboot_mean(col= abs(clickdistfromtargetcenterx))
+# 
+# 
+# 
+# ptagg <- ggplot()+
+#   geom_jitter(data = tc_ind, aes(x = targetposition, y = mean, col = community), alpha = .05, height = 0, width = 0.2)+
+#   geom_pointrange(data =tc_agg, aes(x = targetposition, y = mean, ymin = ci_lower, ymax = ci_upper),pch = "-", col = "#555555", size = 3, stroke = 1.5, linewidth = 2)+
+#   labs(x = "Target position (binned)", y = "Imprecision")+
+#   scale_color_manual(name = "", guide = "none", values = colors)+
 #   ylim(0,1000)+
@@
 # 
-# taf <- tc_agg_data%>%
-#   filter(continent == "Africa")%>%
-#   ggplot(., aes(x = targetposition, y = mean, col = community))+
-#   geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
+# 
+# ptind <- ggplot()+
+#   geom_pointrange(data =tc_com, aes(x = targetposition, y = mean, ymin = ci_lower, ymax = ci_upper, col = community),pch = "-", size = 1)+
 #   labs(x = "", y = "")+
-#   scale_color_colorblind(name = "", guide = "none")+
-#   facet_grid(continent~.)+
+#   scale_color_manual(name = "", guide = "none", values = colors)+
 #   ylim(0,1000)+
-#   theme_few()
-# 
-# teu <- tc_agg_data%>%
-#   filter(continent == "Europe")%>%
-#   ggplot(., aes(x = targetposition, y = mean, col = community))+
-#   geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
-#   labs(x = "", y = "")+
-#   scale_color_colorblind(name = "", guide = "none")+
-#   facet_grid(continent~.)+
-#   ylim(0,1000)+
-#   theme_few()
-# 
-# tas <- tc_agg_data%>%
-#   filter(continent == "Asia")%>%
-#   ggplot(., aes(x = targetposition, y = mean, col = community))+
-#   geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
-#   labs(x = "", y = "")+
-#   scale_color_colorblind(name = "", guide = "none")+
-#   facet_grid(continent~.)+
-#   ylim(0,1000)+
-#   theme_few()
-# 
-# toc <- tc_agg_data%>%
-#   filter(continent == "Oceania")%>%
-#   ggplot(., aes(x = targetposition, y = mean, col = community))+
-#   geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
-#   labs(x = "Target position (binned)", y = "")+
-#   scale_color_colorblind(name = "", guide = "none")+
-#   facet_grid(continent~.)+
-#   ylim(0,1000)+
-#   theme_few()
-
-```
-
-```{r}
-# am <- ggplot()+
-#   geom_point(data = devdata%>%filter(continent == "Americas"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
-#   geom_smooth(data = post%>%filter(continent == "Americas"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
 #   theme_few()+
-#   scale_fill_colorblind(name = "")+
-#   scale_color_colorblind(name = "")+
-#   labs(x = "", y="Imprecision")+
-#   scale_x_continuous(limits = c(2,10))+
-#   scale_y_continuous(limits = c(0,1000))+
-#   facet_grid(continent~.)+
-#   theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))
-# 
-# af <- ggplot()+
-#   geom_point(data = devdata%>%filter(continent == "Africa"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
-#   geom_smooth(data = post%>%filter(continent == "Africa"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
-#   theme_few()+
-#   scale_fill_colorblind(name = "")+
-#   scale_color_colorblind(name = "")+
-#   labs(x = "", y="")+
-#     scale_x_continuous(limits = c(2,10))+
-#   scale_y_continuous(limits = c(0,1000))+
-#   facet_grid(continent~.)+
-#   theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))
-# 
-# eu <- ggplot()+
-#   geom_point(data = devdata%>%filter(continent == "Europe"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
-#   geom_smooth(data = post%>%filter(continent == "Europe"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
-#   theme_few()+
-#   scale_fill_colorblind(name = "")+
-#   scale_color_colorblind(name = "")+
-#   labs(x = "", y="")+
-#     scale_x_continuous(limits = c(2,10))+
-#   scale_y_continuous(limits = c(0,1000))+
-#   facet_grid(continent~.)+
-#   theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))
-# 
-# as <- ggplot()+
-#   geom_point(data = devdata%>%filter(continent == "Asia"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
-#   geom_smooth(data = post%>%filter(continent == "Asia"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
-#   theme_few()+
-#   scale_fill_colorblind(name = "")+
-#   scale_color_colorblind(name = "")+
-#   labs(x = "", y="")+
-#     scale_x_continuous(limits = c(2,10))+
-#   scale_y_continuous(limits = c(0,1000))+
-#   facet_grid(continent~.)+
-#   theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))
-# 
-# oc <- ggplot()+
-#   geom_point(data = devdata%>%filter(continent == "Oceania"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
-#   geom_smooth(data = post%>%filter(continent == "Oceania"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
-#   theme_few()+
-#   scale_fill_colorblind(name = "")+
-#   scale_color_colorblind(name = "")+
-#   labs(x = "Age", y="")+
-#     scale_x_continuous(limits = c(2,10))+
-#   scale_y_continuous(limits = c(0,1000))+
-#   facet_grid(continent~.)+
-#   theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))
-```
-
-```{r figdev, include = T, fig.align = "center", fig.cap = "A) Developmental trajectories by cultural settings.
-Transparent dots show aggregated data for each individual.
-The color dentoes the different cultural settings.
+#   theme(legend.position = c(0.7, 0.9), legend.background = element_blank(),axis.title.x = element_blank(), axis.title.y = element_blank(), axis.ticks.y = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.text.y = element_blank())+
+#   facet_wrap(~community, nrow = 3)
+```
+
+```{r figdev, include = T, fig.align = "center", fig.cap = "A) Developmental trajectory across and B) by community.
 The developmental trajectories are predicted based on a model of the data aggregated for each participant.
-B) Performance by screen section and cultural setting.
+C) Performance by screen section across and D) by community.
 Each bin covers 1/10th of the screen.
-Points show means and eroor bars 95\\% confidence intervals for the data within that bin aggregated across participants.", out.width="75%"}
+Points show means, and error bars 95% confidence intervals for the data within that bin aggregated across participants.
+Transparent dots in A) and C) show aggregated data for each individual.", out.width="100%"}
 
 # pvis_pred <- plot_grid(
-#   plot_grid(am, af, eu, as,oc, ncol = 1, align = "v"),
-#   plot_grid(tam, taf, teu, tas,toc, ncol = 1, align = "v"),
-#   nrow = 1,
-#   labels = c("A","B"),
-#   rel_widths = c(1.75,1)
+# plot_grid(
+#   pagg_dev, pind, rel_widths = c(1,1.5), align = "h", axis = "bt",labels = c("A", "B")
+# ),
+# plot_grid(
+#   ptagg, ptind, rel_widths = c(1,1.5), align = "h", axis = "bt", labels = c("C", "D")
+# ), nrow = 2, align = "v"
 # )
 # 
-# ggsave(plot = pvis_pred, "../visuals/pvis_pred.png", height = 10, width = 6, scale = 1.5)
-# 
+# ggsave(plot = pvis_pred, "../visuals/pvis_pred.png", width = 12, height = 8, bg = "white", scale = 1.25)
+
 knitr::include_graphics("../visuals/pvis_pred.png")
@@
 
-The u-shaped pattern reported above may also arise if participants did not process the agent's gaze at all but only selected the middle of the screen.
-In such a scenario, the further away the balloon lands from the center, the further away it is from the center and the participant's click.
-This would also result in a u-shaped pattern and a strong effect of target centrality.
-It would not, however, predict a developmental improvement in performance.
-Nevertheless, we wanted to quantify the evidence in favor of the vector-based gaze estimation model compared to this alternative center-bias model.
+The u-shaped pattern reported above may also arise if participants did not process the agent's gaze at all but only selected the middle of the screen or selected random locations.
+When only selecting the middle, the further away the balloon lands from the center, the further away it is from the center and the participant's click.
+When randomly selecting locations, the maximal imprecision is smaller when the target lands in the center (max: half screen width) compared to when it lands on the edge (max: full screen width).
+As a consequence, both alternative accounts would  result in a u-shaped pattern and a strong effect of target centrality.
+They would not, however, predict a developmental improvement in performance.
+Nevertheless, we wanted to quantify the evidence in favor of the vector-based gaze estimation model compared to these alternative center bias and random guessing models.
 We also added a random guessing model to the comparison according to which participants also ignored the agents gaze but simply touched random locations on the screen.
@@
 #   labs(x = "Touchscreen exposure", y = "Relative imprecision (age corrected)")+
-#   geom_text_repel(aes(label = community), size = 3, min.segment.length = 0, segment.curvature = -0.1)+
 #   theme_few()
 # 
-# ggsave(plot = pcomtc, "../visuals/pcomtc.png", height = 4, width = 5, scale = 1.5)
+# ggsave(plot = pcomtc, "../visuals/pcomtc.png", height = 4, width = 5, scale = 1.2)
 

### 2024-03-15 analysis/gafo-cc-visuals.Rmd
add missing site descriptions to supplement

@@
   ylim(0, 1000)+
-  labs(x = "Target position (binned)", y = "Imprecision")+
+  labs(x = "Target position (binned)", y = "Imprecision (simulated)")+
   theme_few()

### 2024-03-15 paper/paper.Rmd
add missing site descriptions to supplement

--- 2024-01-30 paper/paper.Rmd
@@
 ---
-title             : "Unity in diversity: Children from 17 diverse communities process gaze in similar ways"
+title             : "A cross-cultural universal of human social cognition: Children from 17 diverse communities process gaze in similar ways"
 shorttitle        : "Gaze-following across 17 communities"
@@
 author: 
-  - name          : "Manuel Bohn"
-    affiliation   : "1,2"
+  - name          : "Manuel Bohn (ORCID: 0000-0001-6006-1348)"
+    affiliation   : "1,2,*"
     corresponding : yes    # Define only one corresponding author
-    address       : "Postal address"
-    email         : "my@email.com"
+    address       : "Universitätsallee 1, 21335 Lüneburg, Germany"
+    email         : "manuel.bohn@leuphana.de"
     role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
       - "Conceptualization"
+      - "Methodology"
+      - "Formal Analysis"
       - "Writing - Original Draft Preparation"
       - "Writing - Review & Editing"
-  - name          : "Julia Prein"
-    affiliation   : "1,2"
+  - name          : "Julia Prein (ORCID: 0000-0002-3154-6167)"
+    affiliation   : "1,2,*"
     role:
@@
       - "Methodology"
+      - "Software"
+      - "Investigation"
       - "Writing - Review & Editing"
-  - name          : "..."
-    affiliation   : "..."
+  - name          : "Agnes Ayikoru"
+    affiliation   : "3"
+    role:
+      - "Investigation"
+  - name          : "Florian M. Bednarski (ORCID: 0000-0003-4384-4791)"
+    affiliation   : "4"
+    role:
+      - "Investigation"
+      - "Writing - Review & Editing" 
+  - name          : "Ardain Dzabatou"
+    affiliation   : "5"
+    role:
+      - "Investigation"
+  - name          : "Michael C. Frank (ORCID: 0000-0002-7551-4378)"
+    affiliation   : "6"
+    role:
+      - "Investigation"
+      - "Writing - Review & Editing"
+  - name          : "Annette M. E. Henderson (ORCID: 0000-0003-4384-4791)"
+    affiliation   : "4"
+    role:
+      - "Investigation"
+      - "Writing - Review & Editing"      
+  - name          : "Joan Isabella"
+    affiliation   : "3"
+    role:
+     - "Investigation" 
+  - name          : "Josefine Kalbitz"
+    affiliation   : "2"
+    role:
+      - "Investigation"
+      - "Writing - Review & Editing"
+  - name          : "Patricia Kanngiesser (ORCID:0000-0003-1068-3725)"
+    affiliation   : "7"
+    role:
+      - "Investigation"
+      - "Writing - Review & Editing" 
+  - name          : "Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733)"
+    affiliation   : "8"
+    role:
+      - "Investigation"
+      - "Writing - Review & Editing" 
+  - name          : "Bahar Köymen (ORCID: 0000-0001-5126-8240)"
+    affiliation   : "9"
+    role:
+      - "Investigation"
+      - "Writing - Review & Editing"  
+  - name          : "Maira V. Manrique-Hernandez"
+    affiliation   : "2"
+    role:
+      - "Investigation"
+  - name          : "Shirley Magazi (ORCID: 0009-0006-0479-9800)"
+    affiliation   : "10"
+    role:
+      - "Investigation"
+  - name          : "Lizbeth Mújica-Manrique"
+    affiliation   : "2"
+    role:
+      - "Investigation"
+      - "Writing - Review & Editing" 
+  - name          : "Julia Ohlendorf"
+    affiliation   : "2"
+    role:
+      - "Investigation"
+  - name          : "Damilola Olaoba"
+    affiliation   : "2"
+    role:
+     - "Investigation"
+  - name          : "Wesley R. Pieters (ORCID:0000-0002-6152-249X)"
+    affiliation   : "10"
+    role:
+      - "Investigation"
+      - "Writing - Review & Editing" 
+  - name          : "Sarah Pope-Caldwell"
+    affiliation   : "2"
+    role:
+     - "Investigation"    
+  - name          : "Katie Slocombe (ORCID: 0000-0002-7310-1887)"
+    affiliation   : "11"
+    role:
+     - "Investigation"
+  - name          : "Robert Z. Sparks (ORCID: 0000-0001-7545-0522)"
+    affiliation   : "6"
+    role:
+      - "Investigation"
+  - name          : "Jahnavi Sunderarajan"
+    affiliation   : "2"
+    role:
+      - "Investigation"
+  - name          : "Wilson Vieira"
+    affiliation   : "2"
+    role:
+     - "Investigation"
+  - name          : "Zhen Zhang (ORCID: 0000-0001-9300-0920)"
+    affiliation   : "12"
+    role:
+      - "Investigation"
+      - "Writing - Review & Editing"   
+  - name          : "Yufei Zong (ORCID: 0009-0000-5012-0244)"
+    affiliation   : "12"
+    role:
+      - "Investigation"
+      - "Writing - Review & Editing"
+  - name          : "Roman Stengelin (ORCID: 0000-0003-2212-4613)"
+    affiliation   : "2,10"
     role:
@@
       - "Methodology"
+      - "Investigation"
       - "Writing - Review & Editing" 
@@
       - "Conceptualization"
+      - "Funding acquisition"
       - "Writing - Review & Editing"
@@
     institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology"
+  - id            : "3"
+    institution   : "Budongo Conservation Field Station"
+  - id            : "4"
+    institution   : "School of Psychology, University of Auckland"
+  - id            : "5"
+    institution   : "Université Marien Ngouabi"
+  - id            : "6"
+    institution   : "Department of Psychology, Stanford University"
+  - id            : "7"
+    institution   : "School of Psychology, University of Plymouth"
+  - id            : "8"
+    institution   : "Department of Psychology, Koç University"
+  - id            : "9"
+    institution   : "Division of Psychology, Communication, and Human Neuroscience, University of Manchester"   
+  - id            : "10"
+    institution   : "Department of Psychology and Social Work, University of Namibia"
+  - id            : "11"
+    institution   : "Department of Psychology, University of York"
+  - id            : "12"
+    institution   : "CAS Key Laboratory of Behavioral Science, Institute of Psychology, Chinese Academy of Sciences"
+  - id            : "*"
+    institution   : "joint first author"
 
 authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-  Enter author note here.
+   The authors would like to thank Luke Maurits for statistical advice.
+Manuel Bohn was supported by a Jacobs Foundation Research Fellowship (2022-1484-00).
+We are gratful to thank all children and caregivers for participating in the study.
 
 abstract: |
-  Understanding gaze is critical for human social interaction.
-In a comprehensive cross-cultural study spanning five continents and 17 distinct cultural contexts, we examined the development of gaze understanding among preschoolers using a single reliable task tailored to each cultural setting.
-Our data provides evidence that children worldwide process gaze in the same way.
-Key performance signatures of a computational model that sees gaze following as a form of social vector estimation were found in all communities.
-Additionally, we found a subtle yet cross-culturally consistent relationship between children's environments and their ability to understand gaze.
-These results highlight the cross-cultural robustness of core social cognitive skills, as well as similarities in the developmental process, suggesting that fundamental aspects of social cognition and interaction emerge and develop in comparable ways globally and hence are a bedrock of human social cognition.
+  Theoretical accounts assume that key features of human social cognition are universal.
+Here we focus on gaze following, the bedrock of social interactions and coordinated activities, to test this claim.
+In this comprehensive cross-cultural study spanning five continents and 17 distinct cultural communities, we examined the development of gaze following in early childhood.
+We identified key processing signatures through a computational model that assumes that participants follow an individual’s gaze by estimating a vector emanating from the eye-center through the pupil.
+Using a single reliable touchscreen-based task, we found these signatures in all communities, suggesting that children worldwide processed gaze in highly similar ways.
+Additionally, we found a cross-culturally consistent relationship between children’s exposure to touchscreens and their performance in the task, which also explained absolute differences between communities.
+These results provide strong evidence for a universal process underlying a foundational socio-cognitive ability in humans that can be reliably inferred even in the presence of cultural variation in overt behavior.
 
@@
 classoption       : "man"
-output            : papaja::apa6_pdf
+output            : papaja::apa6_doc
 ---
@@
                             stanford = "Stanford (USA)",
-                            chimfunshi = "Chimfunshi (Sambia)",
-                            mexico = "Ocuilan (Mexico)",
+                            chimfunshi = "Chimfunshi (Zambia)",
+                            mexico = "Ocuilan (México)",
                             plymouth = "Plymouth (UK)",
@@
 
-Social cognition is a defining aspect of the human species [@tomasello2005understanding; @laland2021understanding; @wellman2014making].
-It is supposed to enable unique forms of communication and cooperation that underlie cumulative cultural evolution and the formation of complex societies [@henrich2016secret; @tomasello2003makes; @legare2019development].
-The eyes are the proverbial window to the mind and the starting point for a majority of social reasoning processes [@shepherd2010following].
-Gaze is used to infer the focus of visual attention, which is a critical aspect of coordinated activities, including communication and cooperation [@tomasello2007reliance; @scaife1975capacity].
-The ability to follow gaze emerges early in childhood [@tang2023slow; @gredeback2010development; @byers2021development] and individual differences in children's gaze following ability predict later life outcomes, most notably, later communicative abilities [@brooks2005development; @carpenter1998social].
-Underlying this narrative is the wide-held assumption that gaze following is fundamental to human social cognition and, therefore, works and develops in the same way across human societies despite substantial variation in developmental contexts.
-This claim, however, lacks a solid empirical foundation.
+Human socio-cognitive skills enable unique forms of communication and cooperation that provide a bedrock for cumulative culture and the formation of complex societies  [@tomasello2020adaptive; @laland2021understanding; @wellman2014making; @henrich2016secret; @tomasello2003makes; @legare2019development; @heyes2018cognitive].
+The eyes are the proverbial "window to the mind" and eye gaze is essential for many social reasoning processes  [@shepherd2010following; @doherty2006development].
+Others’ eye gaze is used to infer their focus of visual attention, which is a critical aspect of coordinated activities, including communication and cooperation [@tomasello2007reliance; @scaife1975capacity].
+The ability to follow gaze emerges early in childhood [@tang2023slow; @gredeback2010development; @byers2021development; @del2019developmental] and individual differences in children’s gaze-following ability predict later life outcomes, most notably, communicative abilities [@brooks2005development; @carpenter1998social].
+Difficulties with gaze following have been linked to developmental disorders, including Autism [@itier2009neural].
 
-We conducted a large-scale cross-cultural study on the development of gaze-following abilities to study potentially universal processing signatures and their development.
-Previous developmental studies focused on the onset of gaze following in infancy [@hernik2019infant; @callaghan2011early].
-The `r n_distinct(data$subjid)` participants in the study lived in 17 different communities spread over five continents (Fig.
+There is a widely-held assumption, that, despite substantial variation in developmental contexts, gaze-following works and develops in the same way across human societies [@tomasello2019becoming].
+However, this view is seemingly at odds with the substantial diversity in socio-cognitive development that cross-cultural studies have revealed [@miller2018contributions; @wellman2014making; @mayer2013synchrony; @dixson2018scaling; @taumoepeau2019cross].
+One potential source for this paradox lies in the reliance on aggregated measures in cross-cultural studies.
+Absolute differences in mean performance across communities are interpreted as a signal of different underlying cognitive processes.
+In this study, we resolve this paradox by instead focusing on processing signatures that can be investigated independently of absolute community-level differences.
+This allows us to directly evaluate the empirical foundation of claims about universal features of human social cognition.
+To this end, we conducted a pre-registered, large-scale, cross-cultural study on the development of gaze-following abilities to study potentially universal processing signatures.
+These signatures were derived from a computational model that assumes that participants follow gaze by estimating a vector emanating from the eye center through the pupil [@prein2023variation].
+
+The `r n_distinct(data$subjid)` participants who took part in the study lived in 17 different communities across 14 countries and five continents (Fig.
 \@ref(fig:fig1)A, Tab.
 \@ref(tab:tab1)).
-The countries from which data was contributed to the study represented 46 % of the world's population.
+These countries represent ~46% of the world’s population.
 Communities covered a broad spectrum of geographical locations, social and political systems, languages, and subsistence styles (see Supplemental Materials).
+This diversity allowed us to overcome the common pitfall of cross-cultural studies that largely compared urban communities from the global north to rural communities from the global south [@barrett2020towards].
 
 ```{r fig1, include = T, fig.align = "center", fig.cap = "(A) Data collection sites.
-Points show approximate geographical location of the data collection sites, coloring shows the sample sizes.
+Points show the approximate geographical location of the data collection sites, coloring shows the sample sizes.
 (B) Screenshot from the task.
 The scene depicts the choice phase in a test trial.
-Participants had to use the gaze of the agent to locate the balloon and click on the hedge where they thought the balloon was.
-Agents, audio recordings and backgrounds were adpated to each cultural setting.
+Participants had to use the gaze of the agent to locate the balloon and click on the location on the hedge where they thought the balloon was.
+Agents, audio recordings and backgrounds were adapted to each cultural setting.
 (C) Drawings used as agents across cultural settings.
 (D) Graphical illustration of the cognitive model.
-Individuals infer the target of an agent's attention by estimating a vector based on the position of the pupils within the eyes.
-This process is noisy, illustrated by the different vectors.
-Individuals differ in their level of precision (indicated by alpha).
-For a given level of precision, the further out the target lands, the less precise the model predicts individuals to be.
-Solid and transparent dots show simualted means and individual data points to illustrate the predicted effect of target position.", out.width="75%"}
+Individuals infer the target of an agent’s attention by estimating a vector based on the position of the pupils within the eyes.
+This process is noisy, illustrated by the different vectors (transparent lines).
+Individuals differ in their level of precision (indicated by sigma).
+For a given level of precision, the closer the  target lands to the left or the right, the less precise the model predicts individuals to be.
+Solid and transparent dots show simulated means and individual data points to illustrate the predicted effect of target position.", out.width="75%"}
 knitr::include_graphics("../visuals/fig1.png")
@@
 
-```{r tab1, echo=F}
+```{r tab1, include = T}
 tba1 <- data %>%
@@
   group_by(continent) %>%
-  mutate(continent = replace(continent, duplicated(continent), " ")) %>%
-  ungroup %>%
+  mutate(continent = as.character(continent),
+         continent = replace(continent, duplicated(continent), " ")) %>%
+  ungroup() %>%
   mutate(country = replace(country, duplicated(country), " "))%>%
-  mutate(language = c("Spanish (Rioplatense)", "Spanish (Mexican)", "English (American)", "Hai||om", "Khwedam", "English (Nigerian)", "English (Nigerian)", "BaYaka", "Lingala", "Bemba", "Swahili", "German", "English (British)", "Mandarin", "English (Indian) / Marathi", "Turkish", "English (New Zealand)"),
+  mutate(language = c("Spanish (Rioplatense)", "Spanish (Mexican)", "English (American)", "Hai||om", "Khwedam", "English (Nigerian)*", "English (Nigerian)", "BaYaka", "Lingala", "Swahili", "Bemba", "German", "English (British)", "Mandarin", "English (Indian) / Marathi", "Turkish", "English (New Zealand)"),
            market_integration = c("high", "medium", "high", "low", "low", "high", "high", "low", "low", "medium", "medium", "high", "high", "high", "high", "high", "high"))%>%
@@
 
-kableExtra::kable(tba1,
+apa_table(tba1,
           col.names = linebreak(c("Continent", "Country", "Community", "N(male)", "Age (range)", "Language", "Market integration","Touchscreen")),
           caption = "Participant demographics.",
-             format="latex", booktabs=TRUE
-             )%>% 
-  kable_styling(latex_options="scale_down")
+          #align = paste0("m{", 1/(ncol(tba1) + 1), "\\linewidth}"),
+          longtable = TRUE,
+          note = "*Local collaborators and piloting suggested that Nigerian English is suitable for Windhoek as well.",
+          escape=TRUE)
 ```
 
-We used an animated picture book tablet task in which participants were asked to locate a hidden object based on observing an agent's gaze.
+We used an animated picture book tablet task in which participants had to locate a hidden object based on observing an agent’s gaze.
 Children watched a balloon disappear behind a hedge.
@@
 \@ref(fig:fig1)B).
-The key dependent variable was the precision with which children located the agent's focus of attention, that is, the deviation between where the agent looked (where the object was) and where the child thought the agent looked.
+The key dependent variable was the (im)precision with which children located the agent’s focus of attention, that is, the deviation between where the agent looked (where the object was) and the child’s response.
 We adapted visuals and audio instructions specifically to each of the 17 communities.
-Previous work demonstrated excellent individual-level measurement properties for this task [@prein2023tango].
-Thus, in addition to group-level trends, we were able to investigate individual-level variation.
+Previous work demonstrated excellent individual-level measurement properties for this task in a German sample [@prein2023tango].
 
@@
 
-As the first step, we investigated developmental gains.
-Across all 17 communities, we found a substantial increase in average levels of precision with age (fixed effect in Bayesian regression model [@burkner2019bayesian]: $\beta$ = `r post_fix%>%filter(term == "ageinyears")%>%pull(Estimate)`, 95% HDI (`r post_fix%>%filter(term == "ageinyears")%>%pull(Q2.5)` - `r post_fix%>%filter(term == "ageinyears")%>%pull(Q97.5)`); range of community-level effects in model: $\beta_{min}$ = `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%tail(1)%>%pull(mean)`, 95% HDI (`r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%tail(1)%>%pull(lci)` - `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%tail(1)%>%pull(uci)`) to $\beta_{max}$ = `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%head(1)%>%pull(mean)`, 95% HDI (`r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%head(1)%>%pull(lci)` - `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%head(1)%>%pull(uci)`).
+As the first step, we investigated developmental improvements, that is, how children become more precise at estimating the target location with age.
+Across all 17 communities, we found a substantial increase in average levels of precision with age (fixed effect in Bayesian regression model [@burkner2019bayesian]: $\beta$ = `r post_fix%>%filter(term == "ageinyears")%>%pull(Estimate)`, 95% HDI (`r post_fix%>%filter(term == "ageinyears")%>%pull(Q2.5)` - `r post_fix%>%filter(term == "ageinyears")%>%pull(Q97.5)`); range of community-level (random) effects: $\beta_{min}$ = `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%tail(1)%>%pull(mean)`, 95% HDI (`r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%tail(1)%>%pull(lci)` - `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%tail(1)%>%pull(uci)`) to $\beta_{max}$ = `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%head(1)%>%pull(mean)`, 95% HDI (`r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%head(1)%>%pull(lci)` - `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%head(1)%>%pull(uci)`).
+
+```{r}
+cv_cult <- readRDS("../saves/cross_validation_result.rds")
+```
+
 Nevertheless, there were also marked differences between communities (see Fig.
 \@ref(fig:fig2)A).
-In a cross-validation procedure, in which we trained a regression model on a subset of the data (training data) to later predict the held out data (testing data) [@stengelin2023children], we found that a model that assumed cross-cultural variation to outperform simple models in 100% of cases (see Supplemental Material).
-At first glance, it seems that highly market-integrated communities around the globe showed higher levels of precision compared to less market-integrated communities (see Tab.
-\@ref(tab:tab1)).
-However, believe that these results are better understood in terms of exposure to technology and we discuss them in more detail below.
-Furthermore, average differences between communities were small compared to differences between individuals: communities did not form homogeneous clusters but largely overlapping distributions in that some individuals from communities with a lower average level of precision performed better compared to some individuals from a setting with a very high average level of precision.
+In a six-fold cross-validation procedure, we trained a regression model on a subset of the data (training data) to later predict the held-out data (testing data) [@stengelin2023children].
+We found that a model assuming cross-cultural variation in average performance as well as cross-cultural variation in developmental trajectories outperformed simpler models – assuming no variation in the shape of developmental trajectories or nor variation between settings at all – in `r round(mean(cv_cult$m3_beats_m2),2)*100`% of cases (see Supplemental Material).
+At first glance, it seems that highly market-integrated communities around the globe showed higher levels of precision compared to less market-integrated communities (compare Tab.
+\@ref(tab:tab1) and Fig.
+\@ref(fig:fig2)A).
+However, numerous alternative groupings (e.g., average levels of education or average household size) are possible and, instead, these results could be best understood in terms of exposure to touch-screen devices; a finding we discuss in more detail below.
+Importantly, average differences in precision between communities were small compared to differences between individuals: communities did not form homogeneous clusters but largely overlapping distributions in that some individuals from communities with a lower average level of precision performed better compared to some individuals from a setting with a very high average level of precision.
 Similarly, in all communities, some 4-year-olds outperformed children two years older than them (see Fig.
 \@ref(fig:fig2)A).
+The lack of adequate individual-level measurement instruments  in previous large-scale developmental cross-cultural studies made it impossible to contrast these perspectives.
+The substantial overlap between communities found here speaks against categorical differences in gaze following and is suggestive of a similar underlying process.
+However, consistent developmental improvements alone cannot inform us about the cognitive processes children use when locating the agent’s focus of attention.
 
-```{r fig2, include = T, fig.align = "center", fig.cap = "A) Developmental trajectories by cultural settings.
-Transparent dots show aggregated data for each individual.
-The color dentoes the different cultural settings.
+```{r fig2, include = T, fig.align = "center", fig.cap = "A) Developmental trajectory across and B) by community.
 The developmental trajectories are predicted based on a model of the data aggregated for each participant.
-B) Performance by screen section and cultural setting.
+C) Performance by screen section across and D) by community.
 Each bin covers 1/10th of the screen.
-Points show means and eroor bars 95\\% confidence intervals for the data within that bin aggregated across participants.", out.width="75%"}
+Points show means, and error bars 95% confidence intervals for the data within that bin aggregated across participants.
+Transparent dots in A) and C) show aggregated data for each individual.", out.width="100%"}
 knitr::include_graphics("../visuals/pvis_pred.png")
@@
 
-Consistent developmental gains alone cannot inform us about the cognitive processes children use when locating the agent's focus of attention.
 Recent computational work modeled gaze following as social vector estimation [@prein2023variation].
-When observing the eyes, onlookers estimate a vector from the center of the eye through the pupil.
-The focus of attention is the location wherever the estimated vectors from both eyes hit a surface (Fig.
-\@ref(fig:fig1)C).
-The estimation process is not perfect, but each individual has a systematic level of uncertainty, which is conceptualized as the cause of individual differences.
-Importantly, this process model predicts a clear performance signature in our cross-cultural gaze following task: Trials in which the agent looks further away from the center (i.e.
-to the left or right side of the screen) should result in lower levels of precision, compared to trials in which the agent looks closer to the middle.
+When observing the eyes, onlookers estimate a vector emanating from the center of the eye that runs through the pupil.
+The focus of attention is the location where the estimated vectors from both eyes hit a surface (Fig.
+\@ref(fig:fig1)D).
+It is assumed that this estimation process has some uncertainty and that individuals vary in their level of uncertainty.
+As a consequence, even though individuals use the same general process, they might differ in their absolute levels of precision.
+Crucially, this process model predicts a clear performance signature in our gaze following task: Trials in which the agent looks further away from the center (i.e.
+to the left or right side of the screen) should result in lower levels of precision compared to trials in which the agent looks closer to the middle.
 This prediction is best understood by considering a similar phenomenon: pointing a torch light to a flat surface.
-The width of the light beam represents each individual's level of uncertainty in vector estimation.
+The width of the light beam represents each individual’s level of uncertainty in vector estimation.
 When the torch is directed straight down, the light beam is concentrated in a relatively small area.
 When the torch is rotated to the side, the light from one half of the cone must travel further than the light from the other half to reach the surface.
-As a consequence, the light is spread over a wider area.
+As a consequence, the light is spread over a wider area (see Fig.
+\@ref(fig:fig1)D).
 
-The processing signature was clearly visible across all 17 communities.
-Precision decreased when the agent looked at locations further away from the center (fixed effect: $\beta$ = `r post_fix%>%filter(term == "targetcentralityx")%>%pull(Estimate)`, 95% HDI (`r post_fix%>%filter(term == "targetcentralitx")%>%pull(Q2.5)` - `r post_fix%>%filter(term == "targetcentralityx")%>%pull(Q97.5)`); range of community-level effects: $\beta_{min}$ = `r post_agg%>%filter(type == "targetcentrality")%>%arrange(mean)%>%tail(1)%>%pull(mean)`, 95% HDI (`r post_agg%>%filter(type == "targetcentrality")%>%arrange(mean)%>%tail(1)%>%pull(lci)` - `r post_agg%>%filter(type == "targetcentrality")%>%arrange(mean)%>%tail(1)%>%pull(uci)`) to $\beta_{max}$ = `r post_agg%>%filter(type == "targetcentrality")%>%arrange(mean)%>%head(1)%>%pull(mean)`, 95% HDI (`r post_agg%>%filter(type == "targetcentrality")%>%arrange(mean)%>%head(1)%>%pull(lci)` - `r post_agg%>%filter(type == "targetcentrality")%>%arrange(mean)%>%head(1)%>%pull(uci)`).
+This processing signature was clearly visible across all 17 communities.
+Precision decreased when the agent looked at locations further away from the center (fixed effect: $\beta$ = `r post_fix%>%filter(term == "targetcentralityx")%>%pull(Estimate)`, 95% HDI (`r post_fix%>%filter(term == "targetcentralityx")%>%pull(Q2.5)` - `r post_fix%>%filter(term == "targetcentralityx")%>%pull(Q97.5)`); range of community-level effects: $\beta_{min}$ = `r post_agg%>%filter(type == "targetcentrality")%>%arrange(mean)%>%tail(1)%>%pull(mean)`, 95% HDI (`r post_agg%>%filter(type == "targetcentrality")%>%arrange(mean)%>%tail(1)%>%pull(lci)` - `r post_agg%>%filter(type == "targetcentrality")%>%arrange(mean)%>%tail(1)%>%pull(uci)`) to $\beta_{max}$ = `r post_agg%>%filter(type == "targetcentrality")%>%arrange(mean)%>%head(1)%>%pull(mean)`, 95% HDI (`r post_agg%>%filter(type == "targetcentrality")%>%arrange(mean)%>%head(1)%>%pull(lci)` - `r post_agg%>%filter(type == "targetcentrality")%>%arrange(mean)%>%head(1)%>%pull(uci)`).
 Visualization of the data showed the predicted u-shaped pattern in all communities (see Fig.
@@
 These results indicate a universal cognitive process used by children in all communities.
-There is, however, an alternative way in which the u = shaped pattern might arise: it would also arise when participants ignored the agent's gaze and instead always selected the middle of the screen (center bias).
-To rule out this alternative explanation, we directly compared three cognitive models that made different assumptions about how participants' responses were generated: the focal vector-based gaze estimation model described above, a center-bias model where participants always select the center, and a random guessing model where participants select random locations.
-For every community, we found overwhelming support for the gaze estimation model (min $BF_{10}$ > 1000 for comparisons with both alternative models).
+There are, however, alternative ways in which the u-shaped pattern might arise: if participants ignored the agent’s gaze and instead always selected the middle of the screen (center bias) or randomly select locations (random guessing), precision would also decrease when the balloon lands further away from the center.
+To rule out these alternative explanations, we compared three cognitive models that made different assumptions about how participants’ responses were generated: the focal vector-based gaze estimation model described above, a center-bias model where participants always select the center, and a random guessing model where participants select random locations.
+For every community, we found overwhelming support for the gaze estimation model (min $BF_{10}$ > 100 000 for comparisons with both alternative models).
 Taken together, children from all 17 communities processed gaze in similar ways.
@@
 
-What is left to explain are the marked community- and individual-level differences.
-In addition to the gaze-following task, caregivers filled out a small questionnaire about children's access to screen-based technology and the composition of their households.
-On an individual level, we found that across communities, children with access to touchscreen devices had higher levels of precision ($\beta$ = `r pred_est%>%filter(term == "touchscreen1")%>%pull(Estimate)`, SE = `r pred_est%>%filter(term == "touchscreen1")%>%pull(Est.Error)`, 95% CrI = `r pred_est%>%filter(term == "touchscreen1")%>%pull(Q2.5)` - `r pred_est%>%filter(term == "touchscreen1")%>%pull(Q97.5)`).
-On a community level, we also saw that average performance was lowest in the communities in which touchscreen devices were the least frequent (Fig.
-\@ref(fig:fig3)).
-Thus, methodological factors likely explained the marked differences between communities.
+```{r}
+ptc_com <- readRDS("../saves/ptc_com.rds")
 
-```{r fig3, include = T, fig.align = "center", fig.cap = "Correlation between performance in the gaze-following task and the exposure to touchscreens on a cultural setting-level.
-Realtive imprecision accounts for differences in age between settings in that it corresponds to the random intercept estimate for each setting in a model predicting performance by age.", out.width="50%"}
-knitr::include_graphics("../visuals/pcomtc.png")
+pttest <- cor.test(ptc_com$Estimate, ptc_com$touchscreen)
 ```
 
-On an individual level, other factors likely generated individual differences because there was substantial variation even in communities where almost all children had access to touchscreens.
-Previous work suggested that social cognition develops in social interaction [@barresi1996intentional; @perner1994theory; @rakoczy2022foundations], in particular, with older siblings [@lewis1996social; @ruffman1998older].
-We found tentative support for this idea in the form of a small but consistent effect in the direction that participants living together with more children older than themselves (relative to other children from the same setting) had slightly higher levels of precision ($\beta$ = `r pred_est%>%filter(term == "older_children")%>%pull(Estimate)`, SE = `r pred_est%>%filter(term == "older_children")%>%pull(Est.Error)`, 95% CrI = `r pred_est%>%filter(term == "older_children")%>%pull(Q2.5)` - `r pred_est%>%filter(term == "older_children")%>%pull(Q97.5)`).
+Next, we looked at factors that could explain community- and individual-level variation.
+In addition to the gaze-following task, caregivers responded to a short questionnaire about children’s access to screen-based technology and household composition.
+On an individual level, we found that children with access to touchscreen devices had higher levels of precision ($\beta$ = `r pred_est%>%filter(term == "touchscreen")%>%pull(Estimate)`, SE = `r pred_est%>%filter(term == "touchscreen")%>%pull(Est.Error)`, 95% CrI = `r pred_est%>%filter(term == "touchscreen")%>%pull(Q2.5)` - `r pred_est%>%filter(term == "touchscreen")%>%pull(Q97.5)`).
+This effect was consistent across communities in that allowing the effect of access to touchscreens to vary across communities did not improve model fit (see Supplemental Materials).
+On a community level, we also saw that average performance was lowest in communities in which touchscreen devices were the least frequent (community-level correlation between age-corrected imprecision and proportion of children with access to touchscreens: *r* = `r round(pttest$estimate,2)`, 95% CI = `r round(pttest$conf.int[1],2)` - `r round(pttest$conf.int[2],2)`).
+Thus, familiarity with the device used for data collection likely explains variation between communities.
+The most likely explanation for this effect is that children with more touchscreen experience were better at task handling and thus more likely to precisely touch the location they inferred the agent to look at.
+
+```{r}
+cor_dat <- data%>%
+  group_by(subjid, children)%>%
+  summarise(click = mean(abs(clickdistfromtargetcenterx)))
+
+ctest <- cor.test(cor_dat$children, cor_dat$click)
+```
+
+However, there was substantial variation between individuals that could not be explained by differential exposures to touch screens alone.
+For example, in Malatya (Türkyie) where 100% of children had access to touch screens there was still substantial variation between individuals (see Fig.
+1B).
+This strongly indicates that other factors likely contributed to individual differences.
+Social interaction has been highlighted as an important driver of social-cognitive development [e.g., @tomasello2019becoming; @carpendale2020makes; @barresi1996intentional; @perner1994theory; @rakoczy2022foundations] and thus we hypothesized (and pre-registered) that more opportunities for social interaction -- approximated by living in larger households with more children -- would be associated with higher levels of precision.
+At first glance, the opposite seemed to be the case: there was a substantial zero-order correlation between the number of children living in the household and average imprecision (`r round(ctest$estimate,2)`, 95% CI = `r round(ctest$conf.int[1],2)` - `r round(ctest$conf.int[2],2)`) suggesting that having more opportunities for social interactions was related to poorer performance.
+However, this correlation is spurious and reflects a confounding of household composition with exposure to technology on a community level.
+When predicting performance by relative opportunities for social interactions within a community -- while accounting for absolute differences and the prevalence of touchscreens -- we found no strong associations between any of the demographic indicators and performance (see Supplemental Material).
+The reason for an absence of such an association may be a lack of resolution: household composition is very far removed from the factors that previous work has suggested to be related to the development of gaze following in younger children, such as attachment quality or the use of gaze in early communicative interactions [@astor2020social; @movellan2002development; @senju2015early].
+Future work could increase the resolution with which everyday experiences in children from diverse communities are recorded to compare the drivers behind development as we observe it.
+Recent work in the field of language acquisition has shown how technological innovations allowed for direct recording of social interactions across communities which can be used to close this explanatory gap [@bergelson2023everyday; @donnelly2021longitudinal].
 
 Following and understanding gaze is a foundational building block of human social cognition [@tomasello2007reliance; @scaife1975capacity].
-A substantial body of work has explored the developmental onset of gaze following in a few selected cultural settings [@moore2008development; @tang2023slow; @gredeback2010development; @byers2021development; @hernik2019infant; @callaghan2011early].
-The data reported here provides evidence that children all over the world process gaze in the same way.
-Key performance signatures of a model that sees gaze following as a form of social vector estimation were found in the data of all 17 distinct cultural communities.
-The cognitive processes underlying gaze following are thus likely to be rooted in humans' evolved cognitive architecture, which is -- presumably -- later refined during social interaction [@astor2020social; @movellan2002development; @senju2015early].
+A substantial body of work has explored the developmental onset of gaze following in a few selected cultural communities [@moore2008development; @tang2023slow; @gredeback2010development; @byers2021development].
+The data reported here provides strong evidence that children from a large and diverse set of communities process others’ gaze in similar ways.
+We found key performance signatures of a model treating gaze following as a form of social vector estimation across all 17 communities.
+With the focus on individual-level processing signatures, the study goes beyond previous studies on gaze following – focused on the onset of gaze following in infancy [@hernik2019infant; @callaghan2011early] – as well as comprehensive cross-cultural studies that compared average developmental trajectories [@house2020universal; @van2018development; @blake2015ontogeny; @kanngiesser2022children].
+
+The cognitive processes underlying gaze following might be rooted in humans’ evolved cognitive architecture, which is -- presumably -- later refined during social (i.e., cultural) interaction [@astor2020social; @movellan2002development; @senju2015early].
 The phylogenetic roots of these processes might possibly lie much deeper as primates from a wide range of species follow gaze [@rosati2009looking; @tomasello1998five; @itakura2004gaze; @kano2014cross].
-Yet, if they also show the same processing signatures has yet to be explored.
+Yet, similarities in overt behavior do not imply the same underlying cognitive processes.
+The present study defines clear performance signatures that can be explored in other species to test such evolutionary hypotheses.
 
-There are important limitations to this study.
-The methodological factors that influenced performance might have overshadowed individual and community-level differences that originate from other sources.
-Importantly, this does not affect our interpretation of the data as evidence for shared cognitive processing because the key processing signatures were present in all communities.
-The role that social interaction plays as a potential driver of development and source of individual differences is vastly under-explored in the current study.
-The small effect of the exposure to older children does not indicate which aspects of social interaction enhance gaze processing.
-Naturalistic data directly recording social interactions across communities would offer crucial information to close this explanatory gap.
-Recent work in the field of language acquisition has shown how technological innovations can be used to close this explanatory gap [@bergelson2023everyday; @donnelly2021longitudinal].
+Our study combined precise individual-level cognitive measurement and individual-level assessment of experience (here: touchscreen exposure) in a large and diverse sample to directly investigate the impact of specific cultural experiences on developmental outcomes.
+Instead of establishing universality by maximizing the cultural distance between two or three tested communities [@norenzayan2005psychological], this large-scale cross-cultural approach treats children’s cultural experience at scale, shedding light on the big “middle ground” of children’s cultural experience [@barrett2020towards].
 
-The evidence presented here holds far-reaching implications.
-Our work pioneers a methodological approach that introduces solid individual-level measurement to the cross-cultural study of cognitive development.
-As such, it serves as a blueprint for future research on a broad spectrum of cognitive abilities.
-Most importantly, this study offers a much-needed empirical foundation for theories on human nature.
-The finding that children from diverse cultures deploy similar cognitive processes in interpreting gaze points to an evolutionary basis of basic social cognition, which is refined during development, presumably through social interaction.
+In sum, our work pioneers an approach that introduces computational modeling and precise individual-level measurement to the cross-cultural study of cognitive development.
+This approach allowed us to test for universals in the human cognitive architecture rather than just overt behavior.
+As such, it can serve as a blueprint for future research on a broad spectrum of cognitive abilities and offers a much-needed empirical foundation for theories on the nature of the human mind.
+Children from diverse cultures deploy similar cognitive processes in interpreting gaze, pointing to a universal foundation of basic social cognition, which is refined during development.
 

### 2024-03-15 paper/paper.tex
add missing site descriptions to supplement

@@
 \hypersetup{
-  pdftitle={Unity in diversity: Children from 17 diverse communities process gaze in similar ways},
-  pdfauthor={Manuel Bohn1,2, Julia Prein1,2, \ldots\ldots, \& Daniel B. M. Haun2},
+  pdftitle={A cross-cultural universal of human social cognition: Children from 17 diverse communities process gaze in similar ways},
+  pdfauthor={Manuel Bohn (ORCID: 0000-0001-6006-1348)1,2,*, Julia Prein (ORCID: 0000-0002-3154-6167)1,2,*, Agnes Ayikoru3, Florian M.
+Bednarski (ORCID: 0000-0003-4384-4791)4, Ardain Dzabatou5, Michael C.
+Frank (ORCID: 0000-0002-7551-4378)6, Annette M.
+E.
+Henderson (ORCID: 0000-0003-4384-4791)4, Joan Isabella3, Josefine Kalbitz2, Patricia Kanngiesser (ORCID:0000-0003-1068-3725)7, Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733)8, Bahar Köymen (ORCID: 0000-0001-5126-8240)9, Maira V.
+Manrique-Hernandez2, Shirley Magazi (ORCID: 0009-0006-0479-9800)10, Lizbeth Mújica-Manrique2, Julia Ohlendorf2, Damilola Olaoba2, Wesley R.
+Pieters (ORCID:0000-0002-6152-249X)10, Sarah Pope-Caldwell2, Katie Slocombe (ORCID: 0000-0002-7310-1887)11, Robert Z.
+Sparks (ORCID: 0000-0001-7545-0522)6, Jahnavi Sunderarajan2, Wilson Vieira2, Zhen Zhang (ORCID: 0000-0001-9300-0920)12, Yufei Zong (ORCID: 0009-0000-5012-0244)12, Roman Stengelin (ORCID: 0000-0003-2212-4613)2,10, \& Daniel B.
+M.
+Haun2},
   pdflang={en-EN},
@@
 
-\title{Unity in diversity: Children from 17 diverse communities process gaze in similar ways}
-\author{Manuel Bohn\textsuperscript{1,2}, Julia Prein\textsuperscript{1,2}, \ldots{}\textsuperscript{\ldots{}}, \& Daniel B. M. Haun\textsuperscript{2}}
+\title{A cross-cultural universal of human social cognition: Children from 17 diverse communities process gaze in similar ways}
+\author{Manuel Bohn (ORCID: 0000-0001-6006-1348)\textsuperscript{1,2,*}, Julia Prein (ORCID: 0000-0002-3154-6167)\textsuperscript{1,2,*}, Agnes Ayikoru\textsuperscript{3}, Florian M.
+Bednarski (ORCID: 0000-0003-4384-4791)\textsuperscript{4}, Ardain Dzabatou\textsuperscript{5}, Michael C.
+Frank (ORCID: 0000-0002-7551-4378)\textsuperscript{6}, Annette M.
+E.
+Henderson (ORCID: 0000-0003-4384-4791)\textsuperscript{4}, Joan Isabella\textsuperscript{3}, Josefine Kalbitz\textsuperscript{2}, Patricia Kanngiesser (ORCID:0000-0003-1068-3725)\textsuperscript{7}, Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733)\textsuperscript{8}, Bahar Köymen (ORCID: 0000-0001-5126-8240)\textsuperscript{9}, Maira V.
+Manrique-Hernandez\textsuperscript{2}, Shirley Magazi (ORCID: 0009-0006-0479-9800)\textsuperscript{10}, Lizbeth Mújica-Manrique\textsuperscript{2}, Julia Ohlendorf\textsuperscript{2}, Damilola Olaoba\textsuperscript{2}, Wesley R.
+Pieters (ORCID:0000-0002-6152-249X)\textsuperscript{10}, Sarah Pope-Caldwell\textsuperscript{2}, Katie Slocombe (ORCID: 0000-0002-7310-1887)\textsuperscript{11}, Robert Z.
+Sparks (ORCID: 0000-0001-7545-0522)\textsuperscript{6}, Jahnavi Sunderarajan\textsuperscript{2}, Wilson Vieira\textsuperscript{2}, Zhen Zhang (ORCID: 0000-0001-9300-0920)\textsuperscript{12}, Yufei Zong (ORCID: 0009-0000-5012-0244)\textsuperscript{12}, Roman Stengelin (ORCID: 0000-0003-2212-4613)\textsuperscript{2,10}, \& Daniel B.
+M.
+Haun\textsuperscript{2}}
 \date{}
@@
 
-Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-Enter author note here.
+The authors would like to thank Luke Maurits for statistical advice.
+Manuel Bohn was supported by a Jacobs Foundation Research Fellowship (2022-1484-00).
+We are greatful to thank all children and caregivers for participating in the study.
 
 The authors made the following contributions.
-Manuel Bohn: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Julia Prein: Conceptualization, Methodology, Writing - Review \& Editing; \ldots{}: Conceptualization, Methodology, Writing - Review \& Editing; Daniel B.
+Manuel Bohn (ORCID: 0000-0001-6006-1348): Conceptualization, Methodology, Formal Analysis, Writing - Original Draft Preparation, Writing - Review \& Editing; Julia Prein (ORCID: 0000-0002-3154-6167): Conceptualization, Methodology, Software, Investigation, Writing - Review \& Editing; Agnes Ayikoru: Investigation; Florian M.
+Bednarski (ORCID: 0000-0003-4384-4791): Investigation, Writing - Review \& Editing; Ardain Dzabatou: Investigation; Michael C.
+Frank (ORCID: 0000-0002-7551-4378): Investigation, Writing - Review \& Editing; Annette M.
+E.
+Henderson (ORCID: 0000-0003-4384-4791): Investigation, Writing - Review \& Editing; Joan Isabella: Investigation; Josefine Kalbitz: Investigation, Writing - Review \& Editing; Patricia Kanngiesser (ORCID:0000-0003-1068-3725): Investigation, Writing - Review \& Editing; Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733): Investigation, Writing - Review \& Editing; Bahar Köymen (ORCID: 0000-0001-5126-8240): Investigation, Writing - Review \& Editing; Maira V.
+Manrique-Hernandez: Investigation; Shirley Magazi (ORCID: 0009-0006-0479-9800): Investigation; Lizbeth Mújica-Manrique: Investigation, Writing - Review \& Editing; Julia Ohlendorf: Investigation; Damilola Olaoba: Investigation; Wesley R.
+Pieters (ORCID:0000-0002-6152-249X): Investigation, Writing - Review \& Editing; Sarah Pope-Caldwell: Investigation; Katie Slocombe (ORCID: 0000-0002-7310-1887): Investigation; Robert Z.
+Sparks (ORCID: 0000-0001-7545-0522): Investigation; Jahnavi Sunderarajan: Investigation; Wilson Vieira: Investigation; Zhen Zhang (ORCID: 0000-0001-9300-0920): Investigation, Writing - Review \& Editing; Yufei Zong (ORCID: 0009-0000-5012-0244): Investigation, Writing - Review \& Editing; Roman Stengelin (ORCID: 0000-0003-2212-4613): Conceptualization, Methodology, Investigation, Writing - Review \& Editing; Daniel B.
 M.
-Haun: Conceptualization, Writing - Review \& Editing.
+Haun: Conceptualization, Funding acquisition, Writing - Review \& Editing.
 
-Correspondence concerning this article should be addressed to Manuel Bohn, Postal address. E-mail: \href{mailto:my@email.com}{\nolinkurl{my@email.com}}
+Correspondence concerning this article should be addressed to Manuel Bohn (ORCID: 0000-0001-6006-1348), Universitätsallee 1, 21335 Lüneburg, Germany.
+E-mail: \href{mailto:manuel.bohn@leuphana.de}{\nolinkurl{manuel.bohn@leuphana.de}}
 
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute of Psychology in Education, Leuphana University Lüneburg\\\textsuperscript{2} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute of Psychology in Education, Leuphana University Lüneburg\\\textsuperscript{2} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology\\\textsuperscript{3} Budongo Conservation Field Station\\\textsuperscript{4} School of Psychology, University of Auckland\\\textsuperscript{5} Université Marien Ngouabi\\\textsuperscript{6} Department of Psychology, Stanford University\\\textsuperscript{7} School of Psychology, University of Plymouth\\\textsuperscript{8} Department of Psychology, Koç University\\\textsuperscript{9} Division of Psychology, Communication, and Human Neuroscience, University of Manchester\\\textsuperscript{10} Department of Psychology and Social Work, University of Namibia\\\textsuperscript{11} Department of Psychology, University of York\\\textsuperscript{12} CAS Key Laboratory of Behavioral Science, Institute of Psychology, Chinese Academy of Sciences\\\textsuperscript{*} joint first author}
 
 \abstract{%
-Understanding gaze is critical for human social interaction.
-In a comprehensive cross-cultural study spanning five continents and 17 distinct cultural contexts, we examined the development of gaze understanding among preschoolers using a single reliable task tailored to each cultural setting.
-Our data provides evidence that children worldwide process gaze in the same way.
-Key performance signatures of a computational model that sees gaze following as a form of social vector estimation were found in all communities.
-Additionally, we found a subtle yet cross-culturally consistent relationship between children's environments and their ability to understand gaze.
-These results highlight the cross-cultural robustness of core social cognitive skills, as well as similarities in the developmental process, suggesting that fundamental aspects of social cognition and interaction emerge and develop in comparable ways globally and hence are a bedrock of human social cognition.
+Theoretical accounts assume that key features of human social cognition are universal.
+Here we focus on gaze following, the bedrock of social interactions and coordinated activities, to test this claim.
+In this comprehensive cross-cultural study spanning five continents and 17 distinct cultural communities, we examined the development of gaze following in early childhood.
+We identified key processing signatures through a computational model that assumes that participants follow an individual's gaze by estimating a vector emanating from the eye-center through the pupil.
+Using a single reliable touchscreen-based task, we found these signatures in all communities, suggesting that children worldwide processed gaze in highly similar ways.
+Additionally, we found a cross-culturally consistent relationship between children's exposure to touchscreens and their performance in the task, which also explained absolute differences between communities.
+These results provide strong evidence for a universal process underlying a foundational socio-cognitive ability in humans that can be reliably inferred even in the presence of cultural variation in overt behavior.
 }
@@
 
-Social cognition is a defining aspect of the human species (\emph{1}--\emph{3}).
-It is supposed to enable unique forms of communication and cooperation that underlie cumulative cultural evolution and the formation of complex societies (\emph{4}--\emph{6}).
-The eyes are the proverbial window to the mind and the starting point for a majority of social reasoning processes (\emph{7}).
-Gaze is used to infer the focus of visual attention, which is a critical aspect of coordinated activities, including communication and cooperation (\emph{8}, \emph{9}).
-The ability to follow gaze emerges early in childhood (\emph{10}--\emph{12}) and individual differences in children's gaze following ability predict later life outcomes, most notably, later communicative abilities (\emph{13}, \emph{14}).
-Underlying this narrative is the wide-held assumption that gaze following is fundamental to human social cognition and, therefore, works and develops in the same way across human societies despite substantial variation in developmental contexts.
-This claim, however, lacks a solid empirical foundation.
+Human socio-cognitive skills enable unique forms of communication and cooperation that provide a bedrock for cumulative culture and the formation of complex societies (\emph{1}--\emph{7}).
+The eyes are the proverbial ``window to the mind'' and eye gaze is essential for many social reasoning processes (\emph{8}, \emph{9}).
+Others' eye gaze is used to infer their focus of visual attention, which is a critical aspect of coordinated activities, including communication and cooperation (\emph{10}, \emph{11}).
+The ability to follow gaze emerges early in childhood (\emph{12}--\emph{15}) and individual differences in children's gaze-following ability predict later life outcomes, most notably, communicative abilities (\emph{16}, \emph{17}).
+Difficulties with gaze following have been linked to developmental disorders, including Autism (\emph{18}).
 
-We conducted a large-scale cross-cultural study on the development of gaze-following abilities to study potentially universal processing signatures and their development.
-Previous developmental studies focused on the onset of gaze following in infancy (\emph{15}, \emph{16}).
-The 1377 participants in the study lived in 17 different communities spread over five continents (Fig.
+There is a widely-held assumption, that, despite substantial variation in developmental contexts, gaze-following works and develops in the same way across human societies (\emph{19}).
+However, this view is seemingly at odds with the substantial diversity in socio-cognitive development that cross-cultural studies have revealed (\emph{3}, \emph{20}--\emph{23}).
+One potential source for this paradox lies in the reliance on aggregated measures in cross-cultural studies.
+Absolute differences in mean performance across communities are interpreted as a signal of different underlying cognitive processes.
+In this study, we resolve this paradox by instead focusing on processing signatures that can be investigated independently of absolute community-level differences.
+This allows us to directly evaluate the empirical foundation of claims about universal features of human social cognition.
+To this end, we conducted a pre-registered, large-scale, cross-cultural study on the development of gaze-following abilities to study potentially universal processing signatures.
+These signatures were derived from a computational model that assumes that participants follow gaze by estimating a vector emanating from the eye center through the pupil (\emph{24}).
+
+The 1377 participants who took part in the study lived in 17 different communities across 14 countries and five continents (Fig.
 \ref{fig:fig1}A, Tab.
 \ref{tab:tab1}).
-The countries from which data was contributed to the study represented 46 \% of the world's population.
+These countries represent \textasciitilde46\% of the world's population.
 Communities covered a broad spectrum of geographical locations, social and political systems, languages, and subsistence styles (see Supplemental Materials).
+This diversity allowed us to overcome the common pitfall of cross-cultural studies that largely compared urban communities from the global north to rural communities from the global south (\emph{25}).
 
@@
 \caption{(A) Data collection sites.
-Points show approximate geographical location of the data collection sites, coloring shows the sample sizes.
+Points show the approximate geographical location of the data collection sites, coloring shows the sample sizes.
 (B) Screenshot from the task.
 The scene depicts the choice phase in a test trial.
-Participants had to use the gaze of the agent to locate the balloon and click on the hedge where they thought the balloon was.
-Agents, audio recordings and backgrounds were adpated to each cultural setting.
+Participants had to use the gaze of the agent to locate the balloon and click on the location on the hedge where they thought the balloon was.
+Agents, audio recordings and backgrounds were adapted to each cultural setting.
 (C) Drawings used as agents across cultural settings.
 (D) Graphical illustration of the cognitive model.
-Individuals infer the target of an agent's attention by estimating a vector based on the position of the pupils within the eyes.
-This process is noisy, illustrated by the different vectors.
-Individuals differ in their level of precision (indicated by alpha).
-For a given level of precision, the further out the target lands, the less precise the model predicts individuals to be.
-Solid and transparent dots show simualted means and individual data points to illustrate the predicted effect of target position.}\label{fig:fig1}
+Individuals infer the target of an agent’s attention by estimating a vector based on the position of the pupils within the eyes.
+This process is noisy, illustrated by the different vectors (transparent lines).
+Individuals differ in their level of precision (indicated by sigma).
+For a given level of precision, the closer the  target lands to the left or the right, the less precise the model predicts individuals to be.
+Solid and transparent dots show simulated means and individual data points to illustrate the predicted effect of target position.}\label{fig:fig1}
 \end{figure}
 
-\begin{table}
+\begin{center}
+\begin{ThreePartTable}
 
-\caption{\label{tab:tab1}Participant demographics.}
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}[t]{llllllll}
+\begin{TableNotes}[para]
+\normalsize{\textit{Note.} *Local collaborators and piloting suggested that Nigerian English is suitable for Windhoek as well.}
+\end{TableNotes}
+
+\begin{longtable}{m{0.111111111111111\linewidth}m{0.111111111111111\linewidth}m{0.111111111111111\linewidth}m{0.111111111111111\linewidth}m{0.111111111111111\linewidth}m{0.111111111111111\linewidth}m{0.111111111111111\linewidth}m{0.111111111111111\linewidth}}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
+\caption{\label{tab:tab1}Participant demographics.}\\
 \toprule
@@
 \midrule
-America & Argentina & Buenos Aires & 105 (53) & 4.72 (3.00 - 6.96) & Spanish (Rioplatense) & high & 0.90\\
- & Mexico & Ocuilan & 127 (63) & 4.96 (2.57 - 6.95) & Spanish (Mexican) & medium & 0.77\\
+\endfirsthead
+\caption*{\normalfont{Table \ref{tab:tab1} continued}}\\
+\toprule
+Continent & Country & Community & N(male) & Age (range) & Language & Market integration & Touchscreen\\
+\midrule
+\endhead
+Americas & Argentina & Buenos Aires & 105 (53) & 4.72 (3.00 - 6.96) & Spanish (Rioplatense) & high & 0.90\\
+ & México & Ocuilan & 127 (63) & 4.96 (2.57 - 6.95) & Spanish (Mexican) & medium & 0.77\\
  & USA & Stanford & 98 (54) & 4.99 (2.52 - 7.90) & English (American) & high & 0.98\\
@@
  &  & Khwe & 59 (24) & 5.84 (3.38 - 8.63) & Khwedam & low & 0.19\\
-\addlinespace
  &  & Windhoek & 39 (17) & 5.69 (2.66 - 8.66) & English (Nigerian) & high & 0.95\\
- & Nigeria & Akure & 114 (54) & 5.07 (2.57 - 7.33) & English (Nigerian) & high & 0.91\\
+ & Nigeria & Akure & 114 (54) & 5.07 (2.57 - 7.33) & English (Nigerian)* & high & 0.91\\
  & Rep. Congo & BaYaka & 29 (13) & 7.80 (3.94 - 10.56) & BaYaka & low & 0.00\\
  &  & Bandongo & 30 (11) & 7.45 (3.50 - 10.95) & Lingala & low & 0.00\\
- & Uganda & Nyabyeya & 125 (62) & 5.94 (2.67 - 8.92) & Bemba & medium & 0.34\\
-\addlinespace
- & Zambia & Chimfunshi & 22 (5) & 5.98 (2.88 - 8.00) & Swahili & medium & 0.14\\
+ & Uganda & Nyabyeya & 125 (62) & 5.94 (2.67 - 8.92) & Swahili & medium & 0.34\\
+ & Zambia & Chimfunshi & 22 (5) & 5.98 (2.88 - 8.00) & Bemba & medium & 0.14\\
 Europe & Germany & Leipzig & 100 (48) & 4.88 (2.53 - 6.95) & German & high & 0.89\\
@@
  & India & Pune & 148 (73) & 6.14 (3.06 - 8.83) & English (Indian) / Marathi & high & 0.93\\
-\addlinespace
  & Türkiye & Malatya & 85 (40) & 5.02 (2.75 - 7.12) & Turkish & high & 1.00\\
@@
 \bottomrule
-\end{tabular}}
-\end{table}
+\addlinespace
+\insertTableNotes
+\end{longtable}
 
-We used an animated picture book tablet task in which participants were asked to locate a hidden object based on observing an agent's gaze.
+\end{ThreePartTable}
+\end{center}
+
+We used an animated picture book tablet task in which participants had to locate a hidden object based on observing an agent's gaze.
 Children watched a balloon disappear behind a hedge.
@@
 \ref{fig:fig1}B).
-The key dependent variable was the precision with which children located the agent's focus of attention, that is, the deviation between where the agent looked (where the object was) and where the child thought the agent looked.
+The key dependent variable was the (im)precision with which children located the agent's focus of attention, that is, the deviation between where the agent looked (where the object was) and the child's response.
 We adapted visuals and audio instructions specifically to each of the 17 communities.
-Previous work demonstrated excellent individual-level measurement properties for this task (\emph{17}).
-Thus, in addition to group-level trends, we were able to investigate individual-level variation.
+Previous work demonstrated excellent individual-level measurement properties for this task in a German sample (\emph{26}).
 
-As the first step, we investigated developmental gains.
-Across all 17 communities, we found a substantial increase in average levels of precision with age (fixed effect in Bayesian regression model (\emph{18}): \(\beta\) = -0.30, 95\% HDI (-0.40 - -0.21); range of community-level effects in model: \(\beta_{min}\) = -0.06, 95\% HDI (-0.17 - 0.06) to \(\beta_{max}\) = -0.59, 95\% HDI (-0.70 - -0.47).
+As the first step, we investigated developmental improvements, that is, how children become more precise at estimating the target location with age.
+Across all 17 communities, we found a substantial increase in average levels of precision with age (fixed effect in Bayesian regression model (\emph{27}): \(\beta\) = -0.30, 95\% HDI (-0.40 - -0.21); range of community-level (random) effects: \(\beta_{min}\) = -0.06, 95\% HDI (-0.18 - 0.05) to \(\beta_{max}\) = -0.59, 95\% HDI (-0.71 - -0.48).
+
 Nevertheless, there were also marked differences between communities (see Fig.
 \ref{fig:fig2}A).
-In a cross-validation procedure, in which we trained a regression model on a subset of the data (training data) to later predict the held out data (testing data) (\emph{19}), we found that a model that assumed cross-cultural variation to outperform simple models in 100\% of cases (see Supplemental Material).
-At first glance, it seems that highly market-integrated communities around the globe showed higher levels of precision compared to less market-integrated communities (see Tab.
-\ref{tab:tab1}).
-However, believe that these results are better understood in terms of exposure to technology and we discuss them in more detail below.
-Furthermore, average differences between communities were small compared to differences between individuals: communities did not form homogeneous clusters but largely overlapping distributions in that some individuals from communities with a lower average level of precision performed better compared to some individuals from a setting with a very high average level of precision.
+In a six-fold cross-validation procedure, we trained a regression model on a subset of the data (training data) to later predict the held-out data (testing data) (\emph{28}).
+We found that a model assuming cross-cultural variation in average performance as well as cross-cultural variation in developmental trajectories outperformed simpler models -- assuming no variation in the shape of developmental trajectories or nor variation between settings at all -- in 98\% of cases (see Supplemental Material).
+At first glance, it seems that highly market-integrated communities around the globe showed higher levels of precision compared to less market-integrated communities (compare Tab.
+\ref{tab:tab1} and Fig.
+\ref{fig:fig2}A).
+However, numerous alternative groupings (e.g., average levels of education or average household size) are possible and, instead, these results could be best understood in terms of exposure to touch-screen devices; a finding we discuss in more detail below.
+Importantly, average differences in precision between communities were small compared to differences between individuals: communities did not form homogeneous clusters but largely overlapping distributions in that some individuals from communities with a lower average level of precision performed better compared to some individuals from a setting with a very high average level of precision.
 Similarly, in all communities, some 4-year-olds outperformed children two years older than them (see Fig.
 \ref{fig:fig2}A).
+The lack of adequate individual-level measurement instruments in previous large-scale developmental cross-cultural studies made it impossible to contrast these perspectives.
+The substantial overlap between communities found here speaks against categorical differences in gaze following and is suggestive of a similar underlying process.
+However, consistent developmental improvements alone cannot inform us about the cognitive processes children use when locating the agent's focus of attention.
 
@@
 
-{\centering \includegraphics[width=0.75\linewidth]{../visuals/pvis_pred}
+{\centering \includegraphics[width=1\linewidth]{../visuals/pvis_pred}
 
@@
 
-\caption{A) Developmental trajectories by cultural settings.
-Transparent dots show aggregated data for each individual.
-The color dentoes the different cultural settings.
+\caption{A) Developmental trajectory across and B) by community.
 The developmental trajectories are predicted based on a model of the data aggregated for each participant.
-B) Performance by screen section and cultural setting.
+C) Performance by screen section across and D) by community.
 Each bin covers 1/10th of the screen.
-Points show means and eroor bars 95\% confidence intervals for the data within that bin aggregated across participants.}\label{fig:fig2}
+Points show means, and error bars 95\% confidence intervals for the data within that bin aggregated across participants.
+Transparent dots in A) and C) show aggregated data for each individual.}\label{fig:fig2}
 \end{figure}
 
-Consistent developmental gains alone cannot inform us about the cognitive processes children use when locating the agent's focus of attention.
-Recent computational work modeled gaze following as social vector estimation (\emph{20}).
-When observing the eyes, onlookers estimate a vector from the center of the eye through the pupil.
-The focus of attention is the location wherever the estimated vectors from both eyes hit a surface (Fig.
-\ref{fig:fig1}C).
-The estimation process is not perfect, but each individual has a systematic level of uncertainty, which is conceptualized as the cause of individual differences.
-Importantly, this process model predicts a clear performance signature in our cross-cultural gaze following task: Trials in which the agent looks further away from the center (i.e.~to the left or right side of the screen) should result in lower levels of precision, compared to trials in which the agent looks closer to the middle.
+Recent computational work modeled gaze following as social vector estimation (\emph{24}).
+When observing the eyes, onlookers estimate a vector emanating from the center of the eye that runs through the pupil.
+The focus of attention is the location where the estimated vectors from both eyes hit a surface (Fig.
+\ref{fig:fig1}D).
+It is assumed that this estimation process has some uncertainty and that individuals vary in their level of uncertainty.
+As a consequence, even though individuals use the same general process, they might differ in their absolute levels of precision.
+Crucially, this process model predicts a clear performance signature in our gaze following task: Trials in which the agent looks further away from the center (i.e.~to the left or right side of the screen) should result in lower levels of precision compared to trials in which the agent looks closer to the middle.
 This prediction is best understood by considering a similar phenomenon: pointing a torch light to a flat surface.
@@
 When the torch is rotated to the side, the light from one half of the cone must travel further than the light from the other half to reach the surface.
-As a consequence, the light is spread over a wider area.
+As a consequence, the light is spread over a wider area (see Fig.
+\ref{fig:fig1}D).
 
-The processing signature was clearly visible across all 17 communities.
-Precision decreased when the agent looked at locations further away from the center (fixed effect: \(\beta\) = 0.47, 95\% HDI ( - 0.54); range of community-level effects: \(\beta_{min}\) = 0.58, 95\% HDI (0.51 - 0.66) to \(\beta_{max}\) = 0.16, 95\% HDI (-0.01 - 0.34).
+This processing signature was clearly visible across all 17 communities.
+Precision decreased when the agent looked at locations further away from the center (fixed effect: \(\beta\) = 0.47, 95\% HDI ( - 0.54); range of community-level effects: \(\beta_{min}\) = 0.58, 95\% HDI (0.51 - 0.66) to \(\beta_{max}\) = 0.16, 95\% HDI (-0.01 - 0.33).
 Visualization of the data showed the predicted u-shaped pattern in all communities (see Fig.
@@
 These results indicate a universal cognitive process used by children in all communities.
-There is, however, an alternative way in which the u = shaped pattern might arise: it would also arise when participants ignored the agent's gaze and instead always selected the middle of the screen (center bias).
-To rule out this alternative explanation, we directly compared three cognitive models that made different assumptions about how participants' responses were generated: the focal vector-based gaze estimation model described above, a center-bias model where participants always select the center, and a random guessing model where participants select random locations.
-For every community, we found overwhelming support for the gaze estimation model (min \(BF_{10}\) \textgreater{} 1000 for comparisons with both alternative models).
+There are, however, alternative ways in which the u-shaped pattern might arise: if participants ignored the agent's gaze and instead always selected the middle of the screen (center bias) or randomly select locations (random guessing), precision would also decrease when the balloon lands further away from the center.
+To rule out these alternative explanations, we compared three cognitive models that made different assumptions about how participants' responses were generated: the focal vector-based gaze estimation model described above, a center-bias model where participants always select the center, and a random guessing model where participants select random locations.
+For every community, we found overwhelming support for the gaze estimation model (min \(BF_{10}\) \textgreater{} 100 000 for comparisons with both alternative models).
 Taken together, children from all 17 communities processed gaze in similar ways.
 
-What is left to explain are the marked community- and individual-level differences.
-In addition to the gaze-following task, caregivers filled out a small questionnaire about children's access to screen-based technology and the composition of their households.
-On an individual level, we found that across communities, children with access to touchscreen devices had higher levels of precision (\(\beta\) = , SE = , 95\% CrI = - ).
-On a community level, we also saw that average performance was lowest in the communities in which touchscreen devices were the least frequent (Fig.
-\ref{fig:fig3}).
-Thus, methodological factors likely explained the marked differences between communities.
+Next, we looked at factors that could explain community- and individual-level variation.
+In addition to the gaze-following task, caregivers responded to a short questionnaire about children's access to screen-based technology and household composition.
+On an individual level, we found that children with access to touchscreen devices had higher levels of precision (\(\beta\) = -0.14, SE = 0.04, 95\% CrI = -0.21 - -0.07).
+This effect was consistent across communities in that allowing the effect of access to touchscreens to vary across communities did not improve model fit (see Supplemental Materials).
+On a community level, we also saw that average performance was lowest in communities in which touchscreen devices were the least frequent (community-level correlation between age-corrected imprecision and proportion of children with access to touchscreens: \emph{r} = -0.90, 95\% CI = -0.96 - -0.74).
+Thus, familiarity with the device used for data collection likely explains variation between communities.
+The most likely explanation for this effect is that children with more touchscreen experience were better at task handling and thus more likely to precisely touch the location they inferred the agent to look at.
 
-\begin{figure}
+However, there was substantial variation between individuals that could not be explained by differential exposures to touch screens alone.
+For example, in Malatya (Türkyie) where 100\% of children had access to touch screens there was still substantial variation between individuals (see Fig.
+1B).
+This strongly indicates that other factors likely contributed to individual differences.
+Social interaction has been highlighted as an important driver of social-cognitive development (e.g., \emph{19}, \emph{29}--\emph{32}) and thus we hypothesized (and pre-registered) that more opportunities for social interaction -- approximated by living in larger households with more children -- would be associated with higher levels of precision.
+At first glance, the opposite seemed to be the case: there was a substantial zero-order correlation between the number of children living in the household and average imprecision (0.27, 95\% CI = 0.22 - 0.32) suggesting that having more opportunities for social interactions was related to poorer performance.
+However, this correlation is spurious and reflects a confounding of household composition with exposure to technology on a community level.
+When predicting performance by relative opportunities for social interactions within a community -- while accounting for absolute differences and the prevalence of touchscreens -- we found no strong associations between any of the demographic indicators and performance (see Supplemental Material).
+The reason for an absence of such an association may be a lack of resolution: household composition is very far removed from the factors that previous work has suggested to be related to the development of gaze following in younger children, such as attachment quality or the use of gaze in early communicative interactions (\emph{33}--\emph{35}).
+Future work could increase the resolution with which everyday experiences in children from diverse communities are recorded to compare the drivers behind development as we observe it.
+Recent work in the field of language acquisition has shown how technological innovations allowed for direct recording of social interactions across communities which can be used to close this explanatory gap (\emph{36}, \emph{37}).
 
-{\centering \includegraphics[width=0.5\linewidth]{../visuals/pcomtc}
+Following and understanding gaze is a foundational building block of human social cognition (\emph{10}, \emph{11}).
+A substantial body of work has explored the developmental onset of gaze following in a few selected cultural communities (\emph{12}--\emph{14}, \emph{38}).
+The data reported here provides strong evidence that children from a large and diverse set of communities process others' gaze in similar ways.
+We found key performance signatures of a model treating gaze following as a form of social vector estimation across all 17 communities.
+With the focus on individual-level processing signatures, the study goes beyond previous studies on gaze following -- focused on the onset of gaze following in infancy (\emph{39}, \emph{40}) -- as well as comprehensive cross-cultural studies that compared average developmental trajectories (\emph{41}--\emph{44}).
 
-}
+The cognitive processes underlying gaze following might be rooted in humans' evolved cognitive architecture, which is -- presumably -- later refined during social (i.e., cultural) interaction (\emph{33}--\emph{35}).
+The phylogenetic roots of these processes might possibly lie much deeper as primates from a wide range of species follow gaze (\emph{45}--\emph{48}).
+Yet, similarities in overt behavior do not imply the same underlying cognitive processes.
+The present study defines clear performance signatures that can be explored in other species to test such evolutionary hypotheses.
 
-\caption{Correlation between performance in the gaze-following task and the exposure to touchscreens on a cultural setting-level.
-Realtive imprecision accounts for differences in age between settings in that it corresponds to the random intercept estimate for each setting in a model predicting performance by age.}\label{fig:fig3}
-\end{figure}
+Our study combined precise individual-level cognitive measurement and individual-level assessment of experience (here: touchscreen exposure) in a large and diverse sample to directly investigate the impact of specific cultural experiences on developmental outcomes.
+Instead of establishing universality by maximizing the cultural distance between two or three tested communities (\emph{49}), this large-scale cross-cultural approach treats children's cultural experience at scale, shedding light on the big ``middle ground'' of children's cultural experience (\emph{25}).
 
-Based on this, we also computed the number of older children living in the household.
-We did not pre-register this, but decided to also include this variable because prior work on advanced forms of social cognition has suggested that the presence of older siblings is slightly more predictive of development compared to other aspects of household composition (e.g., \emph{21}, \emph{22}, but see \emph{23}).
-We think that gaze following improves though practice during social interaction.
-Particularly supportive, we believe, are situations in which it is difficult to infer the goals and intentions of another person based on other information sources (e.g., language or context).
-In such situations, children have to pay closer attention to the interaction partner and use their gaze to make such inferences.
-We are well aware that the numbers in the questionnaire are very far removed from these forms of social interaction.
-Thus, at best, they are a very coarse approximation.
-As a consequence, we do not expect there to be a very strong link between the two.
-We sincerely hope that future work will be able to directly assess children's social interactions.
-
-On an individual level, other factors likely generated individual differences because there was substantial variation even in communities where almost all children had access to touchscreens.
-Previous work suggested that social cognition develops in social interaction (\emph{24}--\emph{26}), in particular, with older siblings (\emph{21}, \emph{22}).
-We found tentative support for this idea in the form of a small but consistent effect in the direction that participants living together with more children older than themselves (relative to other children from the same setting) had slightly higher levels of precision (\(\beta\) = , SE = , 95\% CrI = - ).
-
-Following and understanding gaze is a foundational building block of human social cognition (\emph{8}, \emph{9}).
-A substantial body of work has explored the developmental onset of gaze following in a few selected cultural settings (\emph{10}--\emph{12}, \emph{15}, \emph{16}, \emph{27}).
-The data reported here provides evidence that children all over the world process gaze in the same way.
-Key performance signatures of a model that sees gaze following as a form of social vector estimation were found in the data of all 17 distinct cultural communities.
-The cognitive processes underlying gaze following are thus likely to be rooted in humans' evolved cognitive architecture, which is -- presumably -- later refined during social interaction (\emph{28}--\emph{30}).
-The phylogenetic roots of these processes might possibly lie much deeper as primates from a wide range of species follow gaze (\emph{31}--\emph{34}).
-Yet, if they also show the same processing signatures has yet to be explored.
-
-There are important limitations to this study.
-The methodological factors that influenced performance might have overshadowed individual and community-level differences that originate from other sources.
-Importantly, this does not affect our interpretation of the data as evidence for shared cognitive processing because the key processing signatures were present in all communities.
-The role that social interaction plays as a potential driver of development and source of individual differences is vastly under-explored in the current study.
-The small effect of the exposure to older children does not indicate which aspects of social interaction enhance gaze processing.
-Naturalistic data directly recording social interactions across communities would offer crucial information to close this explanatory gap.
-Recent work in the field of language acquisition has shown how technological innovations can be used to close this explanatory gap (\emph{35}, \emph{36}).
-
-The evidence presented here holds far-reaching implications.
-Our work pioneers a methodological approach that introduces solid individual-level measurement to the cross-cultural study of cognitive development.
-As such, it serves as a blueprint for future research on a broad spectrum of cognitive abilities.
-Most importantly, this study offers a much-needed empirical foundation for theories on human nature.
-The finding that children from diverse cultures deploy similar cognitive processes in interpreting gaze points to an evolutionary basis of basic social cognition, which is refined during development, presumably through social interaction.
+In sum, our work pioneers an approach that introduces computational modeling and precise individual-level measurement to the cross-cultural study of cognitive development.
+This approach allowed us to test for universals in the human cognitive architecture rather than just overt behavior.
+As such, it can serve as a blueprint for future research on a broad spectrum of cognitive abilities and offers a much-needed empirical foundation for theories on the nature of the human mind.
+Children from diverse cultures deploy similar cognitive processes in interpreting gaze, pointing to a universal foundation of basic social cognition, which is refined during development.
 
@@
 \begin{CSLReferences}{0}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-tomasello2005understanding}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-tomasello2020adaptive}{}}%
 \CSLLeftMargin{1. }%
-\CSLRightInline{M.
-Tomasello, M.
-Carpenter, J.
-Call, T.
-Behne, H.
-Moll, Understanding and sharing intentions: The origins of cultural cognition.
-\emph{Behavioral and Brain Sciences} \textbf{28}, 675--691 (2005).}
+\CSLRightInline{M. Tomasello, The adaptive origins of uniquely human sociality. \emph{Philosophical Transactions of the Royal Society B} \textbf{375}, 20190493 (2020).}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-heyes2018cognitive}{}}%
+\CSLLeftMargin{7. }%
+\CSLRightInline{C. Heyes, \emph{Cognitive Gadgets} (Harvard University Press, 2018).}
+
 \leavevmode\vadjust pre{\hypertarget{ref-shepherd2010following}{}}%
-\CSLLeftMargin{7. }%
+\CSLLeftMargin{8. }%
 \CSLRightInline{S. V. Shepherd, Following gaze: Gaze-following behavior as a window into social cognition. \emph{Frontiers in integrative neuroscience} \textbf{4}, 5 (2010).}
 
+\leavevmode\vadjust pre{\hypertarget{ref-doherty2006development}{}}%
+\CSLLeftMargin{9. }%
+\CSLRightInline{M. J. Doherty, The development of mentalistic gaze understanding. \emph{Infant and Child Development} \textbf{15}, 179--186 (2006).}
+
 \leavevmode\vadjust pre{\hypertarget{ref-tomasello2007reliance}{}}%
-\CSLLeftMargin{8. }%
+\CSLLeftMargin{10. }%
 \CSLRightInline{M.
@@
 Call, Reliance on head versus eyes in the gaze following of great apes and human infants: The cooperative eye hypothesis.
-\emph{Journal of human evolution} \textbf{52}, 314--320 (2007).}
+\emph{Journal of Human Evolution} \textbf{52}, 314--320 (2007).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-scaife1975capacity}{}}%
-\CSLLeftMargin{9. }%
+\CSLLeftMargin{11. }%
 \CSLRightInline{M. Scaife, J. S. Bruner, The capacity for joint visual attention in the infant. \emph{Nature} \textbf{253}, 265--266 (1975).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-tang2023slow}{}}%
-\CSLLeftMargin{10. }%
+\CSLLeftMargin{12. }%
 \CSLRightInline{Y. Tang, M. R. Gonzalez, G. O. Deák, The slow emergence of gaze-and point-following: A longitudinal study of infants from 4 to 12 months. \emph{Developmental Science}, e13457 (2023).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-gredeback2010development}{}}%
-\CSLLeftMargin{11. }%
+\CSLLeftMargin{13. }%
 \CSLRightInline{G.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-byers2021development}{}}%
-\CSLLeftMargin{12. }%
+\CSLLeftMargin{14. }%
 \CSLRightInline{K.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-del2019developmental}{}}%
+\CSLLeftMargin{15. }%
+\CSLRightInline{T. Del Bianco, T. Falck-Ytter, E. Thorup, G. Gredebäck, The developmental origins of gaze-following in human infants. \emph{Infancy} \textbf{24}, 433--454 (2019).}
+
 \leavevmode\vadjust pre{\hypertarget{ref-brooks2005development}{}}%
-\CSLLeftMargin{13. }%
+\CSLLeftMargin{16. }%
 \CSLRightInline{R. Brooks, A. N. Meltzoff, The development of gaze following and its relation to language. \emph{Developmental science} \textbf{8}, 535--543 (2005).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-carpenter1998social}{}}%
-\CSLLeftMargin{14. }%
+\CSLLeftMargin{17. }%
 \CSLRightInline{M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-hernik2019infant}{}}%
-\CSLLeftMargin{15. }%
+\leavevmode\vadjust pre{\hypertarget{ref-itier2009neural}{}}%
+\CSLLeftMargin{18. }%
+\CSLRightInline{R. J. Itier, M. Batty, Neural bases of eye and gaze processing: The core of social cognition. \emph{Neuroscience \& Biobehavioral Reviews} \textbf{33}, 843--863 (2009).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-tomasello2019becoming}{}}%
+\CSLLeftMargin{19. }%
+\CSLRightInline{M. Tomasello, \emph{Becoming Human: A Theory of Ontogeny} (Harvard University Press, 2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-miller2018contributions}{}}%
+\CSLLeftMargin{20. }%
+\CSLRightInline{J. G. Miller, M. Wice, N. Goyal, Contributions and challenges of cultural research on the development of social cognition. \emph{Developmental Review} \textbf{50}, 65--76 (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-mayer2013synchrony}{}}%
+\CSLLeftMargin{21. }%
+\CSLRightInline{A.
+Mayer, B.
+E.
+Träuble, Synchrony in the onset of mental state understanding across cultures?
+A study among children in samoa.
+\emph{International Journal of Behavioral Development} \textbf{37}, 21--28 (2013).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-dixson2018scaling}{}}%
+\CSLLeftMargin{22. }%
+\CSLRightInline{H.
+G.
+Dixson, A.
+F.
+Komugabe-Dixson, B.
+J.
+Dixson, J.
+Low, Scaling theory of mind in a small-scale society: A case study from vanuatu.
+\emph{Child Development} \textbf{89}, 2157--2175 (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-taumoepeau2019cross}{}}%
+\CSLLeftMargin{23. }%
 \CSLRightInline{M.
-Hernik, T.
-Broesch, Infant gaze following depends on communicative signals: An eye-tracking study of 5-to 7-month-olds in vanuatu.
-\emph{Developmental science} \textbf{22}, e12779 (2019).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-callaghan2011early}{}}%
-\CSLLeftMargin{16. }%
-\CSLRightInline{T.
-Callaghan, H.
-Moll, H.
-Rakoczy, F.
-Warneken, U.
-Liszkowski, T.
-Behne, M.
-Tomasello, W.
-A.
-Collins, Early social cognition in three cultural contexts.
-\emph{Monographs of the society for research in child development}, i--142 (2011).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-prein2023tango}{}}%
-\CSLLeftMargin{17. }%
-\CSLRightInline{J.
-C.
-Prein, S.
-Kalinke, D.
-B.
-Haun, M.
-Bohn, TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults.
-\emph{Behavior Research Methods}, 1--17 (2023).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-burkner2019bayesian}{}}%
-\CSLLeftMargin{18. }%
-\CSLRightInline{P.-C. Bürkner, Bayesian item response modeling in r with brms and stan. \emph{arXiv preprint arXiv:1905.09501} (2019).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-stengelin2023children}{}}%
-\CSLLeftMargin{19. }%
-\CSLRightInline{R. Stengelin, R. Ball, L. Maurits, P. Kanngiesser, D. B. Haun, Children over-imitate adults and peers more than puppets. \emph{Developmental Science} \textbf{26}, e13303 (2023).}
+Taumoepeau, S.
+Sadeghi, A.
+Nobilo, Cross-cultural differences in children's theory of mind in iran and new zealand: The role of caregiver mental state talk.
+\emph{Cognitive Development} \textbf{51}, 32--45 (2019).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-prein2023variation}{}}%
-\CSLLeftMargin{20. }%
+\CSLLeftMargin{24. }%
 \CSLRightInline{J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-lewis1996social}{}}%
-\CSLLeftMargin{21. }%
-\CSLRightInline{C.
-Lewis, N.
-H.
-Freeman, C.
-Kyriakidou, K.
-Maridaki-Kassotaki, D.
-M.
-Berridge, Social influences on false belief access: Specific sibling influences or general apprenticeship?
-\emph{Child development} \textbf{67}, 2930--2947 (1996).}
+\leavevmode\vadjust pre{\hypertarget{ref-barrett2020towards}{}}%
+\CSLLeftMargin{25. }%
+\CSLRightInline{H. C. Barrett, Towards a cognitive science of the human: Cross-cultural approaches and their urgency. \emph{Trends in Cognitive Sciences} \textbf{24}, 620--638 (2020).}
 
-\leavevmode\vadjust pre{\hypertarget{ref-ruffman1998older}{}}%
-\CSLLeftMargin{22. }%
-\CSLRightInline{T.
-Ruffman, J.
-Perner, M.
-Naito, L.
-Parkin, W.
-A.
-Clements, Older (but not younger) siblings facilitate false belief understanding.
-\emph{Developmental psychology} \textbf{34}, 161 (1998).}
+\leavevmode\vadjust pre{\hypertarget{ref-prein2023tango}{}}%
+\CSLLeftMargin{26. }%
+\CSLRightInline{J.
+C.
+Prein, S.
+Kalinke, D.
+B.
+Haun, M.
+Bohn, TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults.
+\emph{Behavior Research Methods}, 1--17 (2023).}
 
-\leavevmode\vadjust pre{\hypertarget{ref-peterson2003opening}{}}%
-\CSLLeftMargin{23. }%
-\CSLRightInline{C.
-Peterson, V.
-Slaughter, Opening windows into the mind: Mothers' preferences for mental state explanations and children's theory of mind.
-\emph{Cognitive Development} \textbf{18}, 399--429 (2003).}
+\leavevmode\vadjust pre{\hypertarget{ref-burkner2019bayesian}{}}%
+\CSLLeftMargin{27. }%
+\CSLRightInline{P.-C. Bürkner, Bayesian item response modeling in r with brms and stan. \emph{arXiv preprint arXiv:1905.09501} (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-stengelin2023children}{}}%
+\CSLLeftMargin{28. }%
+\CSLRightInline{R. Stengelin, R. Ball, L. Maurits, P. Kanngiesser, D. B. Haun, Children over-imitate adults and peers more than puppets. \emph{Developmental Science} \textbf{26}, e13303 (2023).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-carpendale2020makes}{}}%
+\CSLLeftMargin{29. }%
+\CSLRightInline{J. Carpendale, C. Lewis, \emph{What Makes Us Human: How Minds Develop Through Social Interactions} (Routledge, 2020).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-barresi1996intentional}{}}%
-\CSLLeftMargin{24. }%
+\CSLLeftMargin{30. }%
 \CSLRightInline{J. Barresi, C. Moore, Intentional relations and social understanding. \emph{Behavioral and brain sciences} \textbf{19}, 107--122 (1996).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-perner1994theory}{}}%
-\CSLLeftMargin{25. }%
+\CSLLeftMargin{31. }%
 \CSLRightInline{J. Perner, T. Ruffman, S. R. Leekam, Theory of mind is contagious: You catch it from your sibs. \emph{Child Development} \textbf{65}, 1228--1238 (1994).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-rakoczy2022foundations}{}}%
-\CSLLeftMargin{26. }%
+\CSLLeftMargin{32. }%
 \CSLRightInline{H. Rakoczy, Foundations of theory of mind and its development in early childhood. \emph{Nature Reviews Psychology} \textbf{1}, 223--235 (2022).}
 
-\leavevmode\vadjust pre{\hypertarget{ref-moore2008development}{}}%
-\CSLLeftMargin{27. }%
-\CSLRightInline{C. Moore, The development of gaze following. \emph{Child Development Perspectives} \textbf{2}, 66--70 (2008).}
-
 \leavevmode\vadjust pre{\hypertarget{ref-astor2020social}{}}%
-\CSLLeftMargin{28. }%
+\CSLLeftMargin{33. }%
 \CSLRightInline{K.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-movellan2002development}{}}%
-\CSLLeftMargin{29. }%
+\CSLLeftMargin{34. }%
 \CSLRightInline{J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-senju2015early}{}}%
-\CSLLeftMargin{30. }%
+\CSLLeftMargin{35. }%
 \CSLRightInline{A.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-rosati2009looking}{}}%
-\CSLLeftMargin{31. }%
-\CSLRightInline{A. G. Rosati, B. Hare, Looking past the model species: Diversity in gaze-following skills across primates. \emph{Current opinion in neurobiology} \textbf{19}, 45--51 (2009).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-tomasello1998five}{}}%
-\CSLLeftMargin{32. }%
-\CSLRightInline{M. Tomasello, J. Call, B. Hare, Five primate species follow the visual gaze of conspecifics. \emph{Animal behaviour} \textbf{55}, 1063--1069 (1998).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-itakura2004gaze}{}}%
-\CSLLeftMargin{33. }%
-\CSLRightInline{S. Itakura, Gaze-following and joint visual attention in nonhuman animals, \emph{Japanese Psychological Research}. \textbf{46} (2004)pp. 216--226.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kano2014cross}{}}%
-\CSLLeftMargin{34. }%
-\CSLRightInline{F.
-Kano, J.
-Call, Cross-species variation in gaze following and conspecific preference among great apes, human infants and adults.
-\emph{Animal Behaviour} \textbf{91}, 137--150 (2014).}
-
 \leavevmode\vadjust pre{\hypertarget{ref-bergelson2023everyday}{}}%
-\CSLLeftMargin{35. }%
+\CSLLeftMargin{36. }%
 \CSLRightInline{E.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-donnelly2021longitudinal}{}}%
-\CSLLeftMargin{36. }%
+\CSLLeftMargin{37. }%
 \CSLRightInline{S.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-moore2008development}{}}%
+\CSLLeftMargin{38. }%
+\CSLRightInline{C. Moore, The development of gaze following. \emph{Child Development Perspectives} \textbf{2}, 66--70 (2008).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hernik2019infant}{}}%
+\CSLLeftMargin{39. }%
+\CSLRightInline{M.
+Hernik, T.
+Broesch, Infant gaze following depends on communicative signals: An eye-tracking study of 5-to 7-month-olds in vanuatu.
+\emph{Developmental science} \textbf{22}, e12779 (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-callaghan2011early}{}}%
+\CSLLeftMargin{40. }%
+\CSLRightInline{T.
+Callaghan, H.
+Moll, H.
+Rakoczy, F.
+Warneken, U.
+Liszkowski, T.
+Behne, M.
+Tomasello, W.
+A.
+Collins, Early social cognition in three cultural contexts.
+\emph{Monographs of the society for research in child development}, i--142 (2011).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-house2020universal}{}}%
+\CSLLeftMargin{41. }%
+\CSLRightInline{B.
+R.
+House, P.
+Kanngiesser, H.
+C.
+Barrett, T.
+Broesch, S.
+Cebioglu, A.
+N.
+Crittenden, A.
+Erut, S.
+Lew-Levy, C.
+Sebastian-Enesco, A.
+M.
+Smith, others, Universal norm psychology leads to societal diversity in prosocial behaviour and development.
+\emph{Nature Human Behaviour} \textbf{4}, 36--44 (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-van2018development}{}}%
+\CSLLeftMargin{42. }%
+\CSLRightInline{E.
+J.
+Van Leeuwen, E.
+Cohen, E.
+Collier-Baker, C.
+J.
+Rapold, M.
+Schäfer, S.
+Schütte, D.
+B.
+Haun, The development of human social learning across seven societies.
+\emph{Nature Communications} \textbf{9}, 2076 (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-blake2015ontogeny}{}}%
+\CSLLeftMargin{43. }%
+\CSLRightInline{P.
+R.
+Blake, K.
+McAuliffe, J.
+Corbit, T.
+C.
+Callaghan, O.
+Barry, A.
+Bowie, L.
+Kleutsch, K.
+Kramer, E.
+Ross, H.
+Vongsachang, others, The ontogeny of fairness in seven societies.
+\emph{Nature} \textbf{528}, 258--261 (2015).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kanngiesser2022children}{}}%
+\CSLLeftMargin{44. }%
+\CSLRightInline{P.
+Kanngiesser, M.
+Schäfer, E.
+Herrmann, H.
+Zeidler, D.
+Haun, M.
+Tomasello, Children across societies enforce conventional norms but in culturally variable ways.
+\emph{Proceedings of the National Academy of Sciences} \textbf{119}, e2112521118 (2022).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rosati2009looking}{}}%
+\CSLLeftMargin{45. }%
+\CSLRightInline{A. G. Rosati, B. Hare, Looking past the model species: Diversity in gaze-following skills across primates. \emph{Current opinion in neurobiology} \textbf{19}, 45--51 (2009).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-tomasello1998five}{}}%
+\CSLLeftMargin{46. }%
+\CSLRightInline{M. Tomasello, J. Call, B. Hare, Five primate species follow the visual gaze of conspecifics. \emph{Animal behaviour} \textbf{55}, 1063--1069 (1998).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-itakura2004gaze}{}}%
+\CSLLeftMargin{47. }%
+\CSLRightInline{S. Itakura, Gaze-following and joint visual attention in nonhuman animals, \emph{Japanese Psychological Research}. \textbf{46} (2004)pp. 216--226.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kano2014cross}{}}%
+\CSLLeftMargin{48. }%
+\CSLRightInline{F.
+Kano, J.
+Call, Cross-species variation in gaze following and conspecific preference among great apes, human infants and adults.
+\emph{Animal Behaviour} \textbf{91}, 137--150 (2014).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-norenzayan2005psychological}{}}%
+\CSLLeftMargin{49. }%
+\CSLRightInline{A. Norenzayan, S. J. Heine, Psychological universals: What are they and how can we know? \emph{Psychological Bulletin} \textbf{131}, 763 (2005).}
+
 \end{CSLReferences}

### 2024-03-15 paper/supplement.Rmd
add missing site descriptions to supplement

@@
 
-Akure is situated in the Ondo State in southwest Nigeria. About 800,000 people live in this medium-sized city, and most of them are from the nearby urban and rural areas.
+Akure is situated in the Ondo State in southwest Nigeria. About 800,000 people live in this medium-sized city. Most inhabitants moved from the nearby urban and rural areas to Akure.
 
@@
 
-Akure's natural surroundings are enhanced by the abundant vegetation that includes dense forests, beautiful farmlands, and vivid flora, which is fostered by the climate and fertile soils.
-
-Akure boasts a diverse populace, representing a cultural mosaic where the Yoruba, Igbo, and Hausa communities coexist harmoniously.
+Akure's natural surroundings are enhanced by the abundant vegetation that includes dense forests, farmlands, and vivid flora, which is fostered by the climate and fertile soils.
+
+Akure boasts a diverse populace, representing a cultural mosaic where the Yoruba, Igbo, and Hausa communities coexist.
 While the Yoruba ethnicity predominates, English serves as a widely spoken language alongside the native tongue.
@@
 The climate is defined as either oceanic (Cfb) or subtropical (NIWA).
-Temperatures are mild throughout the year, with an average temperature of 23.7 during summer and 14.7 during winter months.
+Temperatures are mild throughout the year, with an average temperature of 23.7°C during summer and 14.7°C during winter months.
 
@@
 
-Education levels are generally good in Auckland.
-18.6% of the population hold a Bachelor's Degree.
-Interestingly about 9.1% move overseas for their secondary education.
-Parenting and childcare practises are comparable to other western cultures, with some adjustments being implemented in recent years to include more Māori cultural practises in education programs.
+Education levels are generally high in Auckland.
+18.6% of the population hold a Bachelor's degree.
+Interestingly, about 9.1% move overseas for their secondary education.
+Parenting and childcare practices are comparable to other western cultures, with some adjustments being implemented in recent years to include more Māori cultural practices in education programs.
 Such as starting the day or specific activities | hui with Karakia, a form of incantation to ensure a favorable outcome to important events and undertakings.
@@
 Aotearoa is an industrialized nation, nearly everybody has a smartphone and uses technology in their everyday life.
-Many administrative processes are very much digitized.
+Many administrative processes are digitized.
 There is no perceived mistrust towards technology and new developments are generally embraced with great interest.
@@
 
-### Bandongo (Rep. Congo) - Ethnic group
+### Bandongo and BaYaka (Rep. Congo) - Ethnic groups
+
+Both BaYaka and Bandongo populations live (seasonally) in a remote village located in the Likouala region of the Republic of the Congo.
+The Republic of the Congo is located in the central-western part of sub-Saharan Africa along the equator.
+The Likouala department is located in the country's north, in the Congo River Basin, bordering the Central African Republic and the Democratic Republic of Congo.
+The region's climate is tropical, with temperatures ranging from 34°C to 23°C yearly and 148.73 mm of rainfall yearly (Weather and Climate, 2024).
+The dry season starts from December until March, with a mild, rainy season from April until August.
+Heavier rains happen between September and November.
+
+The village is inhabited by approximately 300 BaYaka and 300 Bandongo people (estimates from 2019).
+The BaYaka and Bandongo people have co-inhabited the rainforests of the Congo basin for approximately 3.000 years (Takeuchi, 2014) and have developed inter-ethnic kin (or patronage) and commercial relationships with one another (Lewis, 2002).
+Despite this historical coexistence, each cultural group has distinct means of subsistence and speaks their own language; for the Bandongo, this is Bondongo (Bantu C142); for the BaYaka, this is Yaka (C104); although Lingala (Bantu C36d) is often used as lingua-franca between groups) (Hammarström, 2019).
+The BaYaka are one of many hunter-gatherer societies living in the Congo Basin (Bahuchet, 2017).
+Like many other hunter-gatherer groups in the world, the BaYaka are egalitarian (Boyette & Hewlett, 2017; Woodburn, 1982), follow an autonomy foundational schema (Boyette & Hewlett, 2017), share resources and parental care (Lewis, 2016) and are characterized by an immediate-return economy with an absence of food storage techniques (Lewis, 2002).
+The BaYaka forage for food items in the forests they inhabit while supplementing their diets with some agricultural items (Boyette et al., 2020; Kitanishi, 1995).
+The Bandongo mainly rely on fishing and agriculture to obtain their nutrition (Komatsu, 1998).
+Although the Bandongo also practice hunting to some extent, it is mainly directed to smaller game species, often sourced with the intent to sell, while BaYaka focus on a wider range of species and bigger game for subsistence (Fa et al., 2016).
+BaYaka and Bandongo groups sometimes collaborate in their subsistence activities, such as hunting and fishing (Jang & Boyette, 2021; Kandza et al., 2023).
+Contrary to BaYaka, Bandongo live in a stratified and hierarchical society characterized by wealth accumulation and authority (Boyette et al., 2018).
+
+In the forest camps, the BaYaka inhabit temporary houses (called mongulo or ekuta, depending on the region) built with Marantaceae leaves, lianas, palm tree leaves, etc.
+(see Lewis, 2002).
+These structures are occupied by several family members (usually, but not always, grandparents, parents, and their children).
+Older children may sometimes build their own ekuta, where they sleep alone or with other children.
+The area of forest camps varies, but usually they are small, leading to ekutas being built relatively close to each other (Lew-Levy et al., 2020).
+In the village, BaYaka tend to live in unoccupied Bandongo houses or build their own houses with branches and adobe.
+Bandongo families build permanent habitation with very clear delimitations, usually consisting of a house where the family lives and a kitchen, both built with adobe and thatch roofs (Boyette et al., 2018).
+Households in the village are usually organized based on patrilineal families.
+
+In BaYaka and Bandongo communities, children acquire information through teaching and observational learning from adults and other children (Boyette & Hewlett, 2017; Lew-Levy et al., 2020).
+However, the types of teaching may differ between the two groups.
+Due to their focus on individual autonomy, BaYaka has been reported to show lower levels of direct instruction compared to farmer groups (Boyette & Hewlett, 2017).
+Both communities show alloparental care for children, but while BaYaka caregiving encompasses members of both sexes and different ages within the community, Bandongo alloparenting is provided mainly by women belonging to the extended family of the children (Boyette et al., 2018, 2020).
+
+BaYaka children have limited to no exposure to formal education, and the same is true for most BaYaka parents.
+Bandongo children often attend primary school in the village.
+Some of those children choose to continue into higher levels of education, usually up to high school, in nearby towns.
+It is likely that the parents of the children tested completed at least primary school, but we did not directly ask them in this study.
+
+In the village where this research was conducted, BaYaka and Bandongo people have limited access to market goods or electronic technology.
+BaYaka, in particular, may only have access to the goods brought by the market boat every two weeks (e.g., radios, flip-flops, machetes, torches) or those available through commercial exchange with their Bandongo neighbors.
+However, the Bandongo often have more access to commercial items when visiting nearby towns.
+Although exposure to display screens is rare, the research team found a television used communally by the village people in 2023 (time of data collection).
+A smaller television was found in a BaYaka camp in 2022 (the television belonged to a Bandongo man).
+No touchscreen device has been observed to be used by either community outside of a research setting.
+
+Children from both communities were recruited after their parents or guardians provided explicit informed consent.
+The experiment was conducted in the research house, which has a central location in the village.
+Before experimentation, children’s consent was requested, at which point, children were free to opt out of participating.
+Children were paired with a same-cultural group experimenter.
+Children had the experiment presented in their primary spoken languages; for BaYaka, this was Yaka, and for Bandongo, this was Lingala.
+Children received pre-recorded instructions from the testing computer, as well as some additional instructions, reiterating the recordings when needed.
 
@@
 
-* ...
-
-### Bayaka (Rep. Congo) - Ethnic group
-
-**References and further readings:**
-
-* ...
+* Bahuchet, S. (2017). Cultural diversity of African pygmies. In Hunter-gatherers of the Congo Basin (pp. 1-30). Routledge.
+Boyette, A.
+H., & Hewlett, B.
+S.
+(2017).
+Autonomy, Equality, and Teaching among Aka Foragers and Ngandu Farmers of the Congo Basin.
+Human Nature, 28(3), 289–322.
+https://doi.org/10.1007/s12110-017-9294-y
+* Boyette, A.
+H., Lew-Levy, S., & Gettler, L.
+T.
+(2018).
+Dimensions of Fatherhood in a Congo Basin Village: A Multimethod Analysis of Intracultural Variation in Men’s Parenting and Its Relevance for Child Health.
+Current Anthropology, 59(6), 839–847.
+https://doi.org/10.1086/700717
+* Boyette, A.
+H., Lew‐Levy, S., Sarma, M.
+S., Valchy, M., & Gettler, L.
+T.
+(2020).
+Fatherhood, egalitarianism, and child health in two small‐scale societies in the Republic of the Congo.
+American Journal of Human Biology, 32(4).
+https://doi.org/10.1002/ajhb.23342
+* Fa, J.
+E., Olivero, J., Farfán, M.
+A., Lewis, J., Yasuoka, H., Noss, A., Hattori, S., Hirai, M., Kamgaing, T.
+O.
+W., Carpaneto, G., Germi, F., Márquez, A.
+L., Duarte, J., Duda, R., Gallois, S., Riddell, M., & Nasi, R.
+(2016).
+Differences between Pygmy and Non-Pygmy Hunting in Congo Basin Forests.
+PLOS ONE, 11(9), e0161703.
+https://doi.org/10.1371/journal.pone.0161703
+* Hammarström, H. (2019). An inventory of Bantu languages. In The Bantu languages (pp. 17-78). Routledge.
+* Jang, H., & Boyette, A.
+H.
+(2021).
+Observations of Cooperative Pond Fishing by the Bayaka and Bantu People in the Flooded Forest of the Northern Republic of Congo (2).
+The Center for African Area Studies, Kyoto University.
+https://doi.org/10.34548/asm.41.2.1
+* Kandza, V.
+H., Jang, H., Ntamboudila, F.
+K., Lew-Levy, S., & Boyette, A.
+H.
+(2023).
+Intergroup Cooperation in Shotgun Hunting Among BaYaka Foragers and Yambe Farmers from the Republic of the Congo.
+Human Nature, 34(2), 153–176.
+https://doi.org/10.1007/s12110-023-09448-0
+* Kitanishi, K.
+(1995).
+Seasonal Changes in the Subsistence Activities and Food Intake of the Aka Hunter-Gatherers in Northeastern Congo (2).
+The Center for African Area Studies, Kyoto University.
+https://doi.org/10.14989/68133
+* Lewis, J.
+(2002).
+Forest hunter-gatherers and their world: A study of the Mbendjele Yaka pygmies of Congo-Brazzaville and their secular and religious activities and representations (Doctoral dissertation, University of London).
+* Lewis, J.
+(2016).
+Play, music, and taboo in the reproduction of an egalitarian society.
+Social learning and innovation in contemporary hunter-gatherers: Evolutionary and ethnographic perspectives, 147-158.
+* Lew-Levy, S., Kissler, S.
+M., Boyette, A.
+H., Crittenden, A.
+N., Mabulla, I.
+A., & Hewlett, B.
+S.
+(2020).
+Who teaches children to forage?
+Exploring the primacy of child-to-child teaching among Hadza and BaYaka Hunter-Gatherers of Tanzania and Congo.
+Evolution and Human Behavior, 41(1), 12–22.
+https://doi.org/10.1016/j.evolhumbehav.2019.07.003
+* Takeuchi, K. (2014). In: Barry S. Hewlett ed. Hunter-Gatherers of the Congo Basin: Cultures, Histories and Biology of Arican Pygmies, 2014. Transaction Publishers, New Brunswick.
+* Weather and Climate. (2024). Https://weatherandclimate.com/republic-of-the-congo/likouala/impfondo.
+* Woodburn, J. (1982). Egalitarian Societies. Man, 17(3), 431. https://doi.org/10.2307/2801707
 
@@
 Beijing, a municipality directly under the Central Government, is the capital of the People's Republic of China and the country's political, economic, cultural and transportation center as well as a famous historic city and a modern international city.
-Beijing covers an area of 16,410.54 square kilometers (sq.km) with a population of 21,843,000 in 2022.
+Beijing covers an area of 16 410 54 km^2^ with a population of 21 843 000 in 2022.
 Beijing ranked second in Chinese cities in terms of GDP in 2022.
@@
 Beijing has a temperate, continental monsoonal climate, characterized by short spring and autumns, hot and rainy summers, and cold and dry winters.
-Its average annual temperature is 11 to 14oC.
+Its average annual temperature is 11 to 14°C.
 The coldest month in Beijing is January, with an average temperature of -9 to -4°C; the hottest month is July, with an average of 25°C.
@@
 
-According to the 2021 National Census data, in Beijing, there were 20845166 (95%) Han Chinese along with 1047929 (4.8%) people in other minority nationalities (e.g., Manchu, Hui ethnic, Mongolian ethnic).
+According to the 2021 National Census data, in Beijing, there were 20 845 166 (95%) Han Chinese along with 1 047 929 (4.8%) people in other minority nationalities (e.g., Manchu, Hui ethnic, Mongolian ethnic).
 Mandarin Chinese is commonly spoken by all ethnic groups though many of the minority nationalities also have their own national languages, such as Mongolian language used by Mongolian ethnic.
@@
 Beijing is one of the birthplaces of Chinese Civilization and one of the five ancient capital cities in China.
-With but few interruptions, Beijing has been the capital of China for some eight centuries: including the capital of the State of Yan during the Western Zhou Dynasty (11th Century-771BC), the capital of Jin Dynasty (1153-1215), the capital of Yuan Dynasty (1271-1368), the capital of Ming Dynasty (1421-1644), and the capital of Qing Dynasty (1644-1912).
+With but few interruptions, Beijing has been the capital of China for some eight centuries: including the capital of the State of Yan during the Western Zhou Dynasty (11th Century - 771 BCE), the capital of Jin Dynasty (1153 - 1215), the capital of Yuan Dynasty (1271 - 1368), the capital of Ming Dynasty (1421-1644), and the capital of Qing Dynasty (1644 - 1912).
 In 1949, Beiping (former name of Beijing) was renamed Beijing and became the capital of the People’s Republic of China.
@@
 It’s common that parents spend large parts of the day away from home and children are cared for externally.
-Between 2 and 3 years of age young children can attend nurseries (very few nurseries accept children as young as 1.5-year-old).
+Between 2 and 3 years of age young children can attend nurseries (very few nurseries accept children as young as 1.5 years old).
 Nurseries are largely commercialized and non-subsidized.
@@
 The city has a humid, subtropical climate and has generally mild weather.
-The average temperatures range from 11 degrees Celsius (July) to 25 degrees (January), but heat waves are common during the summer months (December to February).
+The average temperatures range from 11°C (July) to 25°C (January), but heat waves are common during the summer months (December to February).
 
@@
 The sanctuary is located in the Copperbelt region in the northern part of Zambia close to the DRC border.
-The chimpanzees are housed in eight different enclosures; each of an area up to 121.5Ha.
+The chimpanzees are housed in eight different enclosures; each of an area up to 121.5ha.
 The Sanctuary provides education, housing and medical care for the employees and their families which are in total about 300 people living in 5 different compounds around Chimfunshi.
@@
 The current research was conducted in the Namibian Zambezi region which is home to numerous small Khwe communities.
-There are an estimated 3,000 to 5,000 Khwe residing in Bwabwata as of today.
+There are an estimated 3 000 to 5 000 Khwe residing in Bwabwata as of today.
 
@@
 
-Leipzig is a medium-sized city located in the east of Germany with a population of approximately 620,000.
+Leipzig is a medium-sized city located in the east of Germany with a population of approximately 620 000.
 It serves as a significant urban center within the state of Saxony.
@@
 
-Malatya is a big city located in the Eastern Anatolia region of Turkey with a population of approximately 800,000.
+Malatya is a big city located in the Eastern Anatolia region of Turkey with a population of approximately 800 000.
 Due to its strong economy based on agriculture, it is one of the biggest cities in eastern Turkey.
@@
 
-Nyabyeya is located on a green, gently sloping area behind Nyabyeya Hill and is characterized by tropical vegetation and a savanna climate, characterized by daytime temperatures reaching 32°C/90°F and cooler nights at 17°C/63°F.
+Nyabyeya is located on a green, gently sloping area behind Nyabyeya Hill and is characterized by tropical vegetation and a savanna climate, characterized by daytime temperatures reaching 32°C/90°F and cooler nights at 17°C.
 The region observes two distinct agricultural seasons - a wet season from late March to June and August to November, followed by a dry season from early December to March.
@@
 * Budongo Conservation Field Station: http://www.budongo.org/
+
 * Holden, E., Buryn-Weitzel, J.
@@
 
-Ocuilan is a municipality located in the centre south of Mexico with a population of 36,223 inhabitants, distributed in 48 towns in an area of 344.84 km2  inside the Mexican State (Ocuilan, n.d.).
-Geographically Ocuilan has an altitude of between 1000 to 2,600 m situated 80 km south of Mexico City.
+Ocuilan is a municipality located in the centre south of Mexico with a population of 36,223 inhabitants, distributed in 48 towns in an area of 344.84 km^2^  inside the Mexican State (Ocuilan, n.d.).
+Geographically Ocuilan has an altitude of between 1000 to 2 600 m situated 80 km south of Mexico City.
 (INEGI,2010)
@@
 
-Plymouth is a coastal city in the South West of England with a population of more than 260,000 inhabitants.
+Plymouth is a coastal city in the South West of England with a population of more than 260 000 inhabitants.
 About 91% of the population was born in the UK and of those born outside of the UK, the largest proportion comes from the EU (4.5%).
@@
 
-The city has a temperate oceanic climate with average temperatures ranging from 4 to 20 degrees Celsius.
-Winters are generally mild, and temperatures rarely drop below zero degrees.
+The city has a temperate oceanic climate with average temperatures ranging from 4 to 20°C.
+Winters are generally mild, and temperatures rarely drop below 0°C.
 Rain is frequent and highest in autumn and winter.
@@
 Pune is located in the state of Maharashtra in western India.
-The city’s total area is 15.642 square kilometres and the municipal corporation area covers 518 square kilometers.
+The city’s total area is 15.642 km^2^ and the municipal corporation area covers 518 km^2^.
 It lies on the western margin of the Deccan plateau at an altitude of 1840 feet.
@@
 Cummins, a leading manufacturer of diesel and natural gas engines as well as JCB, the farm equipment company are other renowned investors.
-The manufacturing industry provides employment to over 600,000 people while the IT sector employs over 350,000 people.
+The manufacturing industry provides employment to over 600 000 people while the IT sector employs over 350 000 people.
 About 2.2 million migrant workers are employed in the automobile, construction and medium scale manufacturing industries.
@@
 Nearly half of the slum dwellers do not have in-house toilets and 10% do not have electricity.
-Pune experiences a tropical wet and dry climate with average temperatures ranging between 20 and 28 degrees Celsius.
+Pune experiences a tropical wet and dry climate with average temperatures ranging between 20 and 28°C.
 Summer, monsoon and winter are the three main seasons with May being the hottest month.
 During summer, i.e.
-mid-March to mid-June, temperatures can go as high as 42 degrees Celsius.
+mid-March to mid-June, temperatures can go as high as 42°C.
 Monsoon lasts from June to October with most of the annual rainfall of 722mm falling between June and September with July being the wettest month.
-In the months of December and January, temperatures remain around 29 degrees Celsius with overnight temperatures dropping to below 12 degrees.
+In the months of December and January, temperatures remain around 29°C with overnight temperatures dropping to below 12°C.
 
@@
 San Jose’s climate is described as mild, semi-arid, and Mediterranean.
-A wet season typically occurs between November and March with combined rainfall and an average daytime temperature of 50 degrees Fahrenheit.
-A dry season occurs between March and November where precipitation is minimal and the average daytime temperature is 70 degrees Fahrenheit.
+A wet season typically occurs between November and March with combined rainfall and an average daytime temperature of 50°F.
+A dry season occurs between March and November where precipitation is minimal and the average daytime temperature is 70°F.
 
@@
 
+Windhoek is the capital city of Namibia and is situated in the Khomas region, in the central part of the country, at an elevation of 1700 m above sea level, with a total space of 645 km^2^.
+The Khomas region is further divided into 10 constituencies: John Pandeni, Katutura Central, Katutura East, Khomasdal, Moses //Garoeb, Samora Machel, Tobias Hainyeko, Windhoek East, Windhoek Rural and Windhoek West.
+The recent 2023 census indicates that the population of the Khomas region grew by 30.8%; from 342 141 in 2011 to 494 605 in 2023.
+
+The urban part of the Khomas region is commonly known as Windhoek, made up of the nine constituencies of the region.
+Windhoek rural is the rural part of the Khomas region on the outskirts of Windhoek.
+According to the recent 2023 census, Windhoek has a population of 486 169 (250 142 female and 236 027 male) and a population density of 94.9 persons per km^2^ (total area of 5124.2043 km^2^).
+
+The name Windhoek is derived from the Afrikaans meaning „windy corner“.
+The former spelling at the beginning of the German colonial time “Windhuk” is not in use anymore.
+From its beginnings as a small settlement in the late 19th century, Windhoek has grown into a diverse and multi-ethnic community, home to a multitude of languages and cultures, including Nama, Owambo, Damara, Herero, Germans, Afrikaans, and British communities.
+Windhoek is the dominant economic and political centre of Namibia, accounting for more than 50% of the country’s manufacturing activity, over 80% of its finance and business services, and two-thirds of its community and social services.
+Inherited from the colonial and apartheid era, the city maintains its distinctive dual spatial structure.
+The city is made up of three parts: the central part consisting of the central business district (CBD); the east, south and west consisting of various suburbs housing people from primarily middle and upper socio-economic households; and the northern and north-western part of the city where more than 70% of the Windhoek population lives on 25% of the land in crowded formal and informal settlements.
+CBD is modern and thriving with light industrial areas to the north and south.
+In the center of the CBD are government offices, courts, banks, the main post office, business centers, hotels, and new modern shopping malls and supermarkets; a blend of high and low-rise modern buildings.
+
+The current study was conducted in Cimbebasia, a suburb situated in Southern Windhoek falling within the Windhoek West constituency.
+According to the recent 2023 census, the total population of Windhoek West is 59 907.
+The household population is 56 297 with a total of 17 132 households and an average of 3.3 persons per household and a population density of 287.9 persons per km^2^ of which the area is 208.08 km^2^.
+
+English serves as the primary medium of instruction within the educational system, but children often grow up with significant exposure to other indigenous languages like Herero and Damara within their communities.
+Socialization goals and parenting goals reflect that of urban communities in the Global South emphasizing “communal psychological autonomy and relatedness” (Keller & Kaertner, 2013).
+Children in such communities spend a significant portion of their time on activities related to school, family, and leisure with peers and siblings.
+Children’s exposure to smartphones, tablets, and computers begins at a relatively early age, mirroring a global trend in urban middle-class communities.
+
+Participants came from predominantly middle-class communities and were tested at local Sunday schools (at churches) and at educational institutions.
+
 **References and further readings:**
 
-* ...
+* Corbett, J. 45 Facts About Windhoek. https://facts.net/world/cities/45-facts-about-windhoek/
+
+* Gentz, S., Chouinard, L.
+J., & Ruiz-Casares, M.
+(2022).
+Time use and time use satisfaction: An examination of children’s out of school activities in Namibia.
+Journal of the British Academy, 10s2, 59–82.
+https://doi.org/10.5871/jba/010s2.059
+
+* Hamatui, N., & Beynon, C.
+(2017).
+Particulate matter and respiratory symptoms among adults living in Windhoek, Namibia: a cross sectional descriptive study.
+International journal of environmental research and public health, 14(2).
+
+* Keller, H., & Kärtner, J. (2013). Development: The cultural solution of universal developmental tasks. Advances in Culture and Psychology, 3, 63–116.
+
+* Namibia Statistics Agency. 2023 Census, Windhoek, Namibia. https://census.nsa.org.na
+
+* Pendleton, W., & Nickanor, N. (2016). The State of Food Insecuritity in Windhoek, Namibia (No. 14). Southern African Migration Programme.
 

### 2024-03-19 supplement/supplement.Rmd
clean repo

--- 2024-03-15 paper/supplement.Rmd
@@
     number_sections: false
-bibliography: library.bib
-#csl: pnas.csl
+bibliography: ../paper/library.bib
+csl: science.csl
 header-includes:

### 2024-03-19 paper/paper.Rmd
clean repo

@@
      - "Investigation"
+     - "Writing - Review & Editing"
   - name          : "Robert Z. Sparks (ORCID: 0000-0001-7545-0522)"
@@
       - "Investigation"
-      - "Writing - Review & Editing"
   - name          : "Roman Stengelin (ORCID: 0000-0003-2212-4613)"
-    affiliation   : "2,10"
+    affiliation   : "2,10,+"
     role:
@@
       - "Writing - Review & Editing" 
-  - name          : "Daniel B. M. Haun"
-    affiliation   : "2"
+  - name          : "Daniel B. M. Haun (ORCID: 0000-0002-3262-645X)"
+    affiliation   : "2,+"
     role:
@@
     institution   : "joint first author"
+  - id            : "+"
+    institution   : "joint last author"
 
@@
 We are gratful to thank all children and caregivers for participating in the study.
+We thank the Max Planck Society for the Advancement fo Science.
 
@@
 Using a single reliable touchscreen-based task, we found these signatures in all communities, suggesting that children worldwide processed gaze in highly similar ways.
-Additionally, we found a cross-culturally consistent relationship between children’s exposure to touchscreens and their performance in the task, which also explained absolute differences between communities.
+Absolute differences in performance between groups are accounted for by a cross-culturally consistent relationship between children’s exposure to touchscreens and their performance in the task.
 These results provide strong evidence for a universal process underlying a foundational socio-cognitive ability in humans that can be reliably inferred even in the presence of cultural variation in overt behavior.
@@
 Others’ eye gaze is used to infer their focus of visual attention, which is a critical aspect of coordinated activities, including communication and cooperation [@tomasello2007reliance; @scaife1975capacity].
-The ability to follow gaze emerges early in childhood [@tang2023slow; @gredeback2010development; @byers2021development; @del2019developmental] and individual differences in children’s gaze-following ability predict later life outcomes, most notably, communicative abilities [@brooks2005development; @carpenter1998social].
+The ability to follow gaze emerges early in childhood [@tang2023slow; @gredeback2010development; @byers2021development; @del2019developmental], and individual differences in children’s gaze-following ability predict later life outcomes, most notably communicative abilities [@brooks2005development; @carpenter1998social].
 Difficulties with gaze following have been linked to developmental disorders, including Autism [@itier2009neural].
 
-There is a widely-held assumption, that, despite substantial variation in developmental contexts, gaze-following works and develops in the same way across human societies [@tomasello2019becoming].
+There is a widely held assumption that, despite substantial variation in developmental contexts, gaze-following works and develops in the same way across human societies [@tomasello2019becoming].
 However, this view is seemingly at odds with the substantial diversity in socio-cognitive development that cross-cultural studies have revealed [@miller2018contributions; @wellman2014making; @mayer2013synchrony; @dixson2018scaling; @taumoepeau2019cross].
@@
 Communities covered a broad spectrum of geographical locations, social and political systems, languages, and subsistence styles (see Supplemental Materials).
-This diversity allowed us to overcome the common pitfall of cross-cultural studies that largely compared urban communities from the global north to rural communities from the global south [@barrett2020towards].
+This diversity allowed us to overcome the common pitfall of cross-cultural studies that compare urban communities from the global north to rural communities from the global south [@barrett2020towards].
 
@@
 Points show the approximate geographical location of the data collection sites, coloring shows the sample sizes.
-(B) Screenshot from the task.
-The scene depicts the choice phase in a test trial.
-Participants had to use the gaze of the agent to locate the balloon and click on the location on the hedge where they thought the balloon was.
+(B) Screenshots from the task.
+Screenshots from the task.
+The upper scene depicts the start and the lower the choice phase in a test trial.
+Participants had to use the gaze of the agent to locate the balloon and touch the location on the hedge where they thought the balloon was.
 Agents, audio recordings and backgrounds were adapted to each cultural setting.
@@
 Individuals differ in their level of precision (indicated by sigma).
-For a given level of precision, the closer the  target lands to the left or the right, the less precise the model predicts individuals to be.
+For a given level of precision, the further the target lands from the centre of the screen, the less precise the model predicts individuals to be.
 Solid and transparent dots show simulated means and individual data points to illustrate the predicted effect of target position.", out.width="75%"}
-knitr::include_graphics("../visuals/fig1.png")
+knitr::include_graphics("../figures/fig1.png")
 ```
@@
   mutate(country = replace(country, duplicated(country), " "))%>%
-  mutate(language = c("Spanish (Rioplatense)", "Spanish (Mexican)", "English (American)", "Hai||om", "Khwedam", "English (Nigerian)*", "English (Nigerian)", "BaYaka", "Lingala", "Swahili", "Bemba", "German", "English (British)", "Mandarin", "English (Indian) / Marathi", "Turkish", "English (New Zealand)"),
-           market_integration = c("high", "medium", "high", "low", "low", "high", "high", "low", "low", "medium", "medium", "high", "high", "high", "high", "high", "high"))%>%
-  select(continent, country, community, N, age, language, market_integration, touchscreen)
+  mutate(language = c("Spanish (Rioplatense)", "Spanish (Mexican)", "English (American)", "Hai||om", "Khwedam", "English (Nigerian)2", "English (Nigerian)", "BaYaka", "Lingala", "Kiswahili", "Bemba", "German", "English (British)", "Mandarin", "English (Indian) / Marathi", "Turkish", "English (New Zealand)"))%>%
+  select(continent, country, community, N, age, language, touchscreen)
 
 apa_table(tba1,
-          col.names = linebreak(c("Continent", "Country", "Community", "N(male)", "Age (range)", "Language", "Market integration","Touchscreen")),
+          col.names = linebreak(c("Continent", "Country", "Community", "N(male)", "Age (range)", "Language", "Touchscreen exposure1")),
           caption = "Participant demographics.",
@@
           longtable = TRUE,
-          note = "*Local collaborators and piloting suggested that Nigerian English is suitable for Windhoek as well.",
+          note = "1 Proportion of participants who have access to touchscreens according to parental questionnaire.
+2 Local collaborators and piloting suggested that Nigerian English is suitable for Windhoek as well.",
           escape=TRUE)
@@
 The key dependent variable was the (im)precision with which children located the agent’s focus of attention, that is, the deviation between where the agent looked (where the object was) and the child’s response.
-We adapted visuals and audio instructions specifically to each of the 17 communities.
+We adapted visuals and audio instructions specifically for each of the 17 communities.
 Previous work demonstrated excellent individual-level measurement properties for this task in a German sample [@prein2023tango].
@@
 In a six-fold cross-validation procedure, we trained a regression model on a subset of the data (training data) to later predict the held-out data (testing data) [@stengelin2023children].
+This procedure was repeated 100 times.
 We found that a model assuming cross-cultural variation in average performance as well as cross-cultural variation in developmental trajectories outperformed simpler models – assuming no variation in the shape of developmental trajectories or nor variation between settings at all – in `r round(mean(cv_cult$m3_beats_m2),2)*100`% of cases (see Supplemental Material).
-At first glance, it seems that highly market-integrated communities around the globe showed higher levels of precision compared to less market-integrated communities (compare Tab.
-\@ref(tab:tab1) and Fig.
-\@ref(fig:fig2)A).
-However, numerous alternative groupings (e.g., average levels of education or average household size) are possible and, instead, these results could be best understood in terms of exposure to touch-screen devices; a finding we discuss in more detail below.
+There are numerous ways in which communities could be grouped that would fall in line with these absolute differences (e.g., market integration, average levels of education, or average household size).
+However, we deliberately want to avoid any such overly simplistic explanation.
+Instead, we think these results can be best understood in terms of exposure to touch-screen devices;; a finding we discuss in more detail below.
 Importantly, average differences in precision between communities were small compared to differences between individuals: communities did not form homogeneous clusters but largely overlapping distributions in that some individuals from communities with a lower average level of precision performed better compared to some individuals from a setting with a very high average level of precision.
@@
 The lack of adequate individual-level measurement instruments  in previous large-scale developmental cross-cultural studies made it impossible to contrast these perspectives.
-The substantial overlap between communities found here speaks against categorical differences in gaze following and is suggestive of a similar underlying process.
+The substantial overlap between communities found here speaks against categorical differences in gaze following and is suggestive of a universal underlying process.
 However, consistent developmental improvements alone cannot inform us about the cognitive processes children use when locating the agent’s focus of attention.
@@
 The developmental trajectories are predicted based on a model of the data aggregated for each participant.
-C) Performance by screen section across and D) by community.
+C) Performance by target location on the screen across, and D) by community.
 Each bin covers 1/10th of the screen.
@@
 Transparent dots in A) and C) show aggregated data for each individual.", out.width="100%"}
-knitr::include_graphics("../visuals/pvis_pred.png")
+knitr::include_graphics("../figures/pvis_pred.png")
 ```
@@
 As a consequence, even though individuals use the same general process, they might differ in their absolute levels of precision.
-Crucially, this process model predicts a clear performance signature in our gaze following task: Trials in which the agent looks further away from the center (i.e.
-to the left or right side of the screen) should result in lower levels of precision compared to trials in which the agent looks closer to the middle.
+Crucially, this process model predicts a clear performance signature in our gaze following task: Trials in which the agent looks further away from the center should result in lower levels of precision compared to trials in which the agent looks closer to the center.
 This prediction is best understood by considering a similar phenomenon: pointing a torch light to a flat surface.
@@
 These results indicate a universal cognitive process used by children in all communities.
-There are, however, alternative ways in which the u-shaped pattern might arise: if participants ignored the agent’s gaze and instead always selected the middle of the screen (center bias) or randomly select locations (random guessing), precision would also decrease when the balloon lands further away from the center.
+There are, however, alternative ways in which the u-shaped pattern might arise: if participants ignored the agent’s gaze and instead always selected the middle of the screen (center bias) or randomly selected locations (random guessing), precision would also decrease when the balloon lands further away from the center.
 To rule out these alternative explanations, we compared three cognitive models that made different assumptions about how participants’ responses were generated: the focal vector-based gaze estimation model described above, a center-bias model where participants always select the center, and a random guessing model where participants select random locations.
@@
 However, there was substantial variation between individuals that could not be explained by differential exposures to touch screens alone.
-For example, in Malatya (Türkyie) where 100% of children had access to touch screens there was still substantial variation between individuals (see Fig.
+For example, in Malatya (Türkyie) where 100% of children had access to touchscreens there was still substantial variation between individuals (see Fig.
 1B).
@@
 Social interaction has been highlighted as an important driver of social-cognitive development [e.g., @tomasello2019becoming; @carpendale2020makes; @barresi1996intentional; @perner1994theory; @rakoczy2022foundations] and thus we hypothesized (and pre-registered) that more opportunities for social interaction -- approximated by living in larger households with more children -- would be associated with higher levels of precision.
-At first glance, the opposite seemed to be the case: there was a substantial zero-order correlation between the number of children living in the household and average imprecision (`r round(ctest$estimate,2)`, 95% CI = `r round(ctest$conf.int[1],2)` - `r round(ctest$conf.int[2],2)`) suggesting that having more opportunities for social interactions was related to poorer performance.
-However, this correlation is spurious and reflects a confounding of household composition with exposure to technology on a community level.
 When predicting performance by relative opportunities for social interactions within a community -- while accounting for absolute differences and the prevalence of touchscreens -- we found no strong associations between any of the demographic indicators and performance (see Supplemental Material).
-The reason for an absence of such an association may be a lack of resolution: household composition is very far removed from the factors that previous work has suggested to be related to the development of gaze following in younger children, such as attachment quality or the use of gaze in early communicative interactions [@astor2020social; @movellan2002development; @senju2015early].
-Future work could increase the resolution with which everyday experiences in children from diverse communities are recorded to compare the drivers behind development as we observe it.
+Whilst household size was a useful proxy for regular social interaction opportunities, the measure does not directly measure the factors that previous work has suggested to be related to the development of gaze following in younger children, such as attachment quality or the use of gaze in early communicative interactions [@astor2020social; @movellan2002development; @senju2015early].
+Future work could increase the resolution with which everyday experiences in children from diverse communities are recorded to compare the drivers behind social-cognitive development as we observe it.
 Recent work in the field of language acquisition has shown how technological innovations allowed for direct recording of social interactions across communities which can be used to close this explanatory gap [@bergelson2023everyday; @donnelly2021longitudinal].
@@
 
-The cognitive processes underlying gaze following might be rooted in humans’ evolved cognitive architecture, which is -- presumably -- later refined during social (i.e., cultural) interaction [@astor2020social; @movellan2002development; @senju2015early].
+The cognitive processes underlying gaze following might be rooted in humans’ evolved cognitive architecture, which is -- presumably -- later refined during social interaction [@astor2020social; @movellan2002development; @senju2015early].
 The phylogenetic roots of these processes might possibly lie much deeper as primates from a wide range of species follow gaze [@rosati2009looking; @tomasello1998five; @itakura2004gaze; @kano2014cross].

### 2024-03-19 supplement/supplement.Rmd
clean repo

@@
 # 
-# ggsave(plot = techpred, "../visuals/techpred.png",  height = 7, width = 10, scale = 1)
-
-knitr::include_graphics("../visuals/techpred.png")
+# ggsave(plot = techpred, "../figures/techpred.png",  height = 7, width = 10, scale = 1)
+
+knitr::include_graphics("../figures/techpred.png")
 
@@
 # 
-# ggsave(plot = dempred, "../visuals/dempred.png", height = 6, width = 10, scale = 1)
-
-knitr::include_graphics("../visuals/dempred.png")
+# ggsave(plot = dempred, "../figures/dempred.png", height = 6, width = 10, scale = 1)
+
+knitr::include_graphics("../figures/dempred.png")
 
@@
 Participants had to use the gaze of the agent to locate the balloon and click on the hedge where they thought the balloon was.", out.width="80%"}
-knitr::include_graphics("../visuals/task.png")
+knitr::include_graphics("../figures/task.png")
 ```
@@
 ```{r figagents, include = T, fig.align = "center", fig.cap = "Agents used in the task. Some agents were used for multiple cultural settings", out.width="100%"}
-knitr::include_graphics("../visuals/agents.png")
+knitr::include_graphics("../figures/agents.png")
 ```
@@
 # 
-# ggsave(plot = ppred, "../visuals/pred.png", height = 6, width = 12, scale = 1)
-
-knitr::include_graphics("../visuals/pred.png")
+# ggsave(plot = ppred, "../figures/pred.png", height = 6, width = 12, scale = 1)
+
+knitr::include_graphics("../figures/pred.png")
 
@@
 # 
-# ggsave(plot = pvis_pred, "../visuals/pvis_pred.png", width = 12, height = 8, bg = "white", scale = 1.25)
-
-knitr::include_graphics("../visuals/pvis_pred.png")
+# ggsave(plot = pvis_pred, "../figures/pvis_pred.png", width = 12, height = 8, bg = "white", scale = 1.25)
+
+knitr::include_graphics("../figures/pvis_pred.png")
 
@@
 # 
-# ggsave(plot = pcomtc, "../visuals/pcomtc.png", height = 4, width = 5, scale = 1.2)
-
-knitr::include_graphics("../visuals/pcomtc.png")
+# ggsave(plot = pcomtc, "../figures/pcomtc.png", height = 4, width = 5, scale = 1.2)
+
+knitr::include_graphics("../figures/pcomtc.png")
 ```

### 2024-03-24 paper/paper.Rmd
update repo

@@
 ---
-title             : "A cross-cultural universal of human social cognition: Children from 17 diverse communities process gaze in similar ways"
+title             : "A universal of human social cognition: Children from 17 communities process gaze in similar ways"
 shorttitle        : "Gaze-following across 17 communities"

### 2024-04-03 supplement/supplement.Rmd
update paper for submission

@@
 ---
-title: "Unity in diversity: Children from 17 diverse communities process gaze in similar ways"
+title: "A universal of human social cognition: Children from 17 communities process gaze in similar ways"
 subtitle: "Supplemental material"
-author: "..."
+author:
+  - Manuel Bohn
+  - Julia Prein
+  - Agnes Ayikoru
+  - Florian M. Bednarski
+  - Ardain Dzabatou
+  - Michael C. Frank 
+  - Annette M. E. Henderson 
+  - Joan Isabella
+  - Josefine Kalbitz 
+  - Patricia Kanngiesser
+  - Dilara Keşşafoğlu
+  - Bahar Köymen
+  - Maira V. Manrique-Hernandez 
+  - Shirley Magazi
+  - Lizbeth Mújica-Manrique
+  - Julia Ohlendorf
+  - Damilola Olaoba
+  - Wesley R. Pieters
+  - Sarah Pope-Caldwell
+  - Katie Slocombe
+  - Robert Z. Sparks
+  - Jahnavi Sunderarajan
+  - Wilson Vieira
+  - Zhen Zhang
+  - Yufei Zong
+  - Roman Stengelin
+  - Daniel B. M. Haun
 output: 
   bookdown::pdf_document2:
+    toc: yes 
+    number_sections: false    
+  bookdown::word_document2:
     toc: yes 
@@
 
-# Overview
-
-This docuemnt provides a detailed overview of the participants and methods of the in the section [site descriptions](#site-descriptions)
-
 # Participants
@@
 A total of `r sum(as.numeric(demtab$N))` children between `r round(min(data$ageinyears), 2)` and `r round(max(data$ageinyears), 2)` provided data for the study.
-Children lived in `r n_distinct(data$community)` different communities, located in `r n_distinct(data$country)` different countries.
+Children lived in `r n_distinct(data$community)` different communities, located in `r n_distinct(demtab$country)` different countries.
 Table \@ref(tab:demtable) gives the sample size per community together with some basic demographic information.
+The recruitment strategy for each community is reported in the respective site descriptions.
 Figure \@ref(fig:figpred1)A shows the age distribution in each setting.
@@
 In such cases, we set the birthday to the 30th of June of the year that would make them fall into the reported age category.
-Additional children were recruited but did not contribute data to the study.
-The recruitment strategy varied from community to community and we therefore cannot provide detailed information about the number of children that were excluded.
-All children who contributed at least four valid data points were included in the final sample, however, we excluded children when parents did not fill out the questionnaire correctly (e.g., when the number of children living in the household was reported to be larger than the household itself or when the number of children reported to live in the household equaled the number of children younger than the child being tested).
-Twelve children had to be excluded for one of these reasons (one from Akure, two from Stanford, seven from Pune and two from Windhoek).
+
+Data from children was only included in the study when they contributed at least four valid test trials.
+We also excluded the data from children with a diagnosed developmental disorder.
+In sum, in addition to the sample size reported above, 74 additional children participated in the study but did not contribute data.
+The main reasons for exclusion were: contribution of less than four valid test trials, technical failures, and missing or implausible demographic information (e.g., when the number of children living in the household was reported to be larger than the household itself or when the number of children reported to live in the household equaled the number of children younger than the child being tested).
 We did not exclude any participants for performance reasons.
-A detailed description of each site and the way children were recruited can be found below.
+A detailed description of each site and the way children were recruited can be found in the respective site description.
+
+```{r figpred1, include = T, fig.align = "center", fig.cap = "A) Age distribution and B) prevalence of different types of technology by community.
+Left: dots show individual data points.
+Right: color shows the proportion of children with access to screens or touchscreens.", out.width="100%"}
+# techpred <- plot_grid(page, ppred, rel_widths = c(1, 0.5),align = "h", labels = c("A", "B"))
+# 
+# ggsave(plot = techpred, "../figures/techpred.png",  height = 7, width = 10, scale = 1)
+
+knitr::include_graphics("../figures/techpred.png")
+
+```
 
@@
 
-Akure is situated in the Ondo State in southwest Nigeria. About 800,000 people live in this medium-sized city. Most inhabitants moved from the nearby urban and rural areas to Akure.
+Akure is situated in the Ondo State in southwest Nigeria. About 800 000 people live in this medium-sized city. Most inhabitants moved from the nearby urban and rural areas to Akure.
 
 There are two different seasons in Akure's tropical climate: the wet season, which runs from April to October, and the dry season, which runs from November to March.
-Rich vegetation, including deep forests and productive agriculture, is what defines the city.
+Rich vegetation, including deep forests and productive agriculture, defines the city.
 
@@
 This communal ethos extends from familial bonds – encompassing both nuclear and extended families – to broader social networks within neighborhoods, workplaces, and religious congregations.
-Akure's evolution from a traditional Yoruba kingdom to a thriving urban metropolis is deeply embedded in history and has a rich cultural legacy.
-The landscape is dotted with evidence of old kingdoms and communities, highlighting the city's lasting influence and crucial role in the history of the area.
+Akure's evolution from a traditional Yoruba kingdom to a thriving urban metropolis is deeply embedded in history and has a rich cultural legacy, highlighting the city's lasting influence and crucial role in the history of the area.
 
@@
 
-The variety of architectural styles and types of homes found in the city are reflected in the housing landscape.
 Akure offers a diverse range of housing options, including modern urban dwellings scattered across the city and ancient mud-brick homes tucked away in rural hamlets.
@@
 
-A set of fundamental principles that are deeply embedded in the fabric of Akure society define parenting there.
 Parents are essential in passing on cultural legacy and forming the identities of future generations because they emphasize reverence for elders, community cohesion, and the value of education.
@@
 The median age in the Auckland region was 34.7 years.
-181,194 Māori people with a median age of 24.9 years were counted in the 2018 census.
+181 194 Māori people with a median age of 24.9 years were counted in the 2018 census.
 Overall the population is composed of 53.5% European, 28.2% Asian, 15.5% Pacific Peoples, 11.5% Māori, 2.3% Middle Eastern / Latin American / African and 1.1% Other ethnicity.
@@
 Māori peoples arrived in Auckland | Tāmaki Makaurau around 1350 from other Pacific Islands.
-Before the arrival of European New Zealanders | Pākehā New Zealand was populated by about 20,000 Māori.
+Before the arrival of European New Zealanders | Pākehā New Zealand was populated by about 20 000 Māori.
 Aotearoa was colonized by the Dutch and British Empires in the 18th Century.
@@
 
-51.9% of the people in Auckland are employed full time, with an unemployment rate of 4.1% and 30.4% not in the labor force (i.e.
-retirees).
+51.9% of the people in Auckland are employed full time, with an unemployment rate of 4.1% and 30.4% retirees.
 The main occupations are professionals (25.9%) and managers (18.1%) with only 5.9% operating machinery and 7.9% laborers.
-The people of Auckland are part of a service society with a median income of 34,400NZD and 19.8% of the population earning more than 70,000NZD.
+The people of Auckland are part of a service society with a median income of 34 400NZD and 19.8% of the population earning more than 70 000NZD.
 
@@
 Success is determined by career paths, income and general success in professional and private aspects of life.
-Sport plays a central role in most aspects of society.
 The role of sports is viewed as essential for living a healthy and successful life and as such is a central part in education programs.
@@
 Parenting and childcare practices are comparable to other western cultures, with some adjustments being implemented in recent years to include more Māori cultural practices in education programs.
-Such as starting the day or specific activities | hui with Karakia, a form of incantation to ensure a favorable outcome to important events and undertakings.
-(see Literature for further information on early childhood education in New Zealand.)
+Such as starting the day or specific activities | hui with Karakia, a form of incantation to ensure a favorable outcome to important events and undertakings (see Literature for further information on early childhood education in New Zealand).
 
@@
 For this study we reached out to early childcare centers and schools.
-Two early childcare centers and one primary school agree to participate.
+Two early childcare centers and one primary school agreed to participate.
 Some additional children were tested during home visit sessions.
@@
 
-```{r figpred1, include = T, fig.align = "center", fig.cap = "A) Age distribution and B) prevalence of different types of technology by community.
-Left: dots show individual data points.
-Right: color shows the proportion of children with access to screens or touchscreens.", out.width="100%"}
-# techpred <- plot_grid(page, ppred, rel_widths = c(1, 0.5),align = "h", labels = c("A", "B"))
-# 
-# ggsave(plot = techpred, "../figures/techpred.png",  height = 7, width = 10, scale = 1)
-
-knitr::include_graphics("../figures/techpred.png")
-
-```
-
 ### Bandongo and BaYaka (Rep. Congo) - Ethnic groups
@@
 The Likouala department is located in the country's north, in the Congo River Basin, bordering the Central African Republic and the Democratic Republic of Congo.
-The region's climate is tropical, with temperatures ranging from 34°C to 23°C yearly and 148.73 mm of rainfall yearly (Weather and Climate, 2024).
+The region's climate is tropical, with temperatures ranging from 23°C to 34°C yearly and 148.73 mm of rainfall yearly (Weather and Climate, 2024).
 The dry season starts from December until March, with a mild, rainy season from April until August.
@@
 The village is inhabited by approximately 300 BaYaka and 300 Bandongo people (estimates from 2019).
-The BaYaka and Bandongo people have co-inhabited the rainforests of the Congo basin for approximately 3.000 years (Takeuchi, 2014) and have developed inter-ethnic kin (or patronage) and commercial relationships with one another (Lewis, 2002).
+The BaYaka and Bandongo people have co-inhabited the rain forests of the Congo basin for approximately 3.000 years (Takeuchi, 2014) and have developed inter-ethnic kin (or patronage) and commercial relationships with one another (Lewis, 2002).
 Despite this historical coexistence, each cultural group has distinct means of subsistence and speaks their own language; for the Bandongo, this is Bondongo (Bantu C142); for the BaYaka, this is Yaka (C104); although Lingala (Bantu C36d) is often used as lingua-franca between groups) (Hammarström, 2019).
@@
 In the village, BaYaka tend to live in unoccupied Bandongo houses or build their own houses with branches and adobe.
-Bandongo families build permanent habitation with very clear delimitations, usually consisting of a house where the family lives and a kitchen, both built with adobe and thatch roofs (Boyette et al., 2018).
+Bandongo families build permanent habitation with very clear delimitation, usually consisting of a house where the family lives and a kitchen, both built with adobe and thatch roofs (Boyette et al., 2018).
 Households in the village are usually organized based on patrilineal families.
@@
 
-Beijing, a municipality directly under the Central Government, is the capital of the People's Republic of China and the country's political, economic, cultural and transportation center as well as a famous historic city and a modern international city.
+Beijing, a municipality directly under the Central Government, is the capital of the People's Republic of China and the country's political, economic, cultural and transportation center.
 Beijing covers an area of 16 410 54 km^2^ with a population of 21 843 000 in 2022.
@@
 
-95% of the sampled Children were recruited from local public kindergarten and primary school.
+95% of the sampled children were recruited from local public kindergarten and primary school.
 We firstly introduced the experiment to the heads of the kindergarten/school.
 Once getting their permission, we asked the teachers to help send the printed letter (information about the study, informed consent, as well as the five questions) to the parents.
-And a Mandarin speaking research assistant then tested kids whose parents signed the informed consent in a separate room in the kindergarten/school.
+A Mandarin speaking research assistant then tested kids whose parents signed the informed consent in a separate room in the kindergarten/school.
 A few of the youngest kids (5% of total) were recruited by directly introducing the experiment to the parents who we personally knew and tested the kids either in a separate room at our institute or at their home.
@@
 Most people in Buenos Aires live in apartment buildings, but informal settlements have been growing over the last decades.
-Argentina has experienced one of the highest inflation rates in the world in the past years and poverty has been steadily increasing—though poverty rates in the city of Buenos Aires tend to be lower than in the surrounding Buenos Aires Province.
+Argentina has experienced one of the highest inflation rates in the world in the past years and poverty has been steadily increasing — though poverty rates in the city of Buenos Aires tend to be lower than in the surrounding Buenos Aires Province.
 
@@
 Argentina was the first country in South America to legalize same-sex marriage in 2010 and Buenos Aires in particular is perceived as progressive and liberal city.
-Some parenting values in middle-class families in Argentina, such as being responsive to the child and providing stimulating encounters, are similar to countries such as the U.S.
-or France.
+Some parenting values in middle-class families in Argentina, such as being responsive to the child and providing stimulating encounters, are similar to western countries.
 Caregivers tend to control their children’s schedules/activities, but children do not necessarily perceive this control as negative and caregivers are more permissive with younger children.
@@
 
-### Chimfunshi (Sambia) - Location
+### Chimfunshi (Zambia) - Location
 
@@
 The sanctuary is located in the Copperbelt region in the northern part of Zambia close to the DRC border.
-The chimpanzees are housed in eight different enclosures; each of an area up to 121.5ha.
 The Sanctuary provides education, housing and medical care for the employees and their families which are in total about 300 people living in 5 different compounds around Chimfunshi.
@@
 However, for those with higher education levels, English becomes the predominant second language.
-The patterns of migrations has contributed to a rich tapestry of linguistic and cultural diversity across the nation., Due to a robust mining industry in the Copperbelt region, the population hailing from various corners of Zambia and even neighboring countries.
+The patterns of migrations have contributed to a rich tapestry of linguistic and cultural diversity across the nation.
+Due to a robust mining industry in the Copperbelt region, the population hails from various corners of Zambia and even neighboring countries.
 
@@
 They traditionally lived in small, semi-nomadic bands, loosely organized around kinship ties and shared leadership roles.
-Like many other forager communities of southern Africa, the Hai||om value egalitarianism, autonomy, and sharing on demand as foundational schemas organizing their social structure.
 
@@
 In one community, children have access to a primary school from age 6 onward, whereas in the other community, children need to travel about 35km to access the next school.
-In both communities, dropout rates are reported low by teachers, likely due to multiple reasons, such as cultural mismatches between often authoritarian teaching styles and foreign learning content at schools, children’s autonomy in deciding on their learning environments, and secondary schools being located far away from their home communities.
+In both communities, school attendance rates are reported low by teachers, likely due to multiple reasons, such as cultural mismatches between often authoritarian teaching styles and foreign learning content at schools, children’s autonomy in deciding on their learning environments, and secondary schools being located far away from their home communities.
 Traditional knowledge transfer remains vital, with elders playing a significant role in childcare and education.
@@
 
-Exposure to technology, particularly smartphones and other touchscreen devices, is generally limited among the Khwe of Bwabwata also due to their remote location, economic hardships, and lack of access to electricity.
+Exposure to technology, particularly smartphones and other touchscreen devices, is generally limited among the Khwe of Bwabwata, also due to their remote location, economic hardships, and lack of access to electricity.
 However, similar to the Hai||om, the level of access can vary depending on proximity to towns and settlements.
@@
 
-### Malatya (Turkey) - Location
-
-Malatya is a big city located in the Eastern Anatolia region of Turkey with a population of approximately 800 000.
-Due to its strong economy based on agriculture, it is one of the biggest cities in eastern Turkey.
+### Malatya (Türkiye) - Location
+
+Malatya is a big city located in the Eastern Anatolia region of Türkiye with a population of approximately 800 000.
+Due to its strong economy based on agriculture, it is one of the biggest cities in eastern Türkiye.
 
@@
 Children live both in nuclear families (with parents and siblings) and in extended families (nuclear family and a set of grandparents).
-Parental socialization in Malatya aligns with broader Turkish cultural norms, and typically emphasize the importance of children’s interdependence, value of family.
+Parental socialization in Malatya aligns with broader Turkish cultural norms, and typically emphasize the importance of children’s interdependence and the value of family.
 Education and learning are seen as important aspects of children’s lives.
-Parental education levels are generally above the average of Turkey; with most adults have high school or university degrees.
+Parental education levels are generally above the average of Türkiye; with most adults have high school or university degrees.
 
@@
 Nyabyeya Forestry College is situated in the Masindi district of western Uganda, approximately 25 km from Masindi Town and 240 km from Kampala, the capital city.
-The college is adjacent to Budongo Tropical High Forest and 8 km from Budongo conservation field station, where primatologists study wild-ranging chimpanzees.
-The college draws its sample from the surrounding villages, including Marram, Kyempunu, Nyabigoma, Nyabyeya 1 and 2 and Trading Center, Nyakafunjo, and Kyamasuka.
-
-Nyabyeya is located on a green, gently sloping area behind Nyabyeya Hill and is characterized by tropical vegetation and a savanna climate, characterized by daytime temperatures reaching 32°C/90°F and cooler nights at 17°C.
+The college is adjacent to Budongo Forest and 8 km from Budongo Conservation Field Station, where primatologists study habituated wild chimpanzees.
+The sample were invited to participate at the college from the surrounding villages, including Marram, Kyempunu, Nyabigoma, Nyabyeya 1 and 2 and Trading Center, Nyakafunjo, and Kyamasuka.
+
+Nyabyeya village is characterized by tropical vegetation and a savanna climate, characterized by daytime temperatures reaching 32°C and cooler nights at 17°C.
 The region observes two distinct agricultural seasons - a wet season from late March to June and August to November, followed by a dry season from early December to March.
 
-The studied villages are culturally very diverse and house ethnic groups such as Bantu, Luo, Nilotics, and Nilo-Hamites.
-Spoken languages depend on the tribe and include Alur, Lugbara, Runyoro, lendu, kakwa, Acholi, Langi, Luganda, Logo, Kebu, madi, and many others.
+The studied villages are culturally very diverse and are home to different ethnic groups including Bantu, Luo, Nilotics, and Nilo-Hamites.
+Spoken languages depend on the tribe and include Alur, Lugbara, Runyoro, Lendu, Kakwa, Acholi, Langi, Luganda, Logo, Kebu, Madi, and many others.
 Kiswahili and English often serve as a common ground.
-For this study, children who understand Kiswahili were invited.
+For this study, children who understood Kiswahili were invited.
 
@@
 
-The community predominantly practices subsistence farming, cultivating crops like maize, cassava, sweet potatoes, and beans.
+The local communities predominantly practices subsistence farming, cultivating crops like maize, cassava, sweet potatoes, and beans.
 Wealthier families sometimes keep goats, pigs, chickens, or ducks.
 Additionally, sugarcane and coffee cultivation contribute significantly to the local economy, with the Kinyara Sugar Company playing a pivotal role in sugarcane harvesting.
-
-Living conditions in the community are characterized by extended families residing together, with an average of 10 people under one roof.
-While temporary round mud huts are common, permanent houses are found in the trading center of Nyabyeya.
-Most people in the community live by hand to mouth, and parents (especially women) work hard to provide the basics for their household members.
-
-Parental socialization goals vary, with limited guidance for children in some instances, leading to very independent lives at a young age.
+Salaried work is rare and many households struggle to provide essentials, including food, health care, and school materials for family members.
+
+Living conditions in the community are characterized by extended families residing together, with an average of 10 people in each household.
+Households tend to inhabit several buildings within a compound, with buildings made from traditional materials (wood and mud walls; straw roof) or bricks with metal roofing.
+
+Parental socialization goals vary, but a previous sample of mothers from these communities valued relational socialization goals over autonomous goals (Holden et al., 2022).
 Cultural practices include the belief in producing many children as a sign of respect, with specific tribes attaching wealth to the number of daughters.
@@
 Often, young children take care of their siblings and carry them around on their backs.
-Children start working early, for example, by helping their parents with farming or cow herding.
-Often, families cannot afford school materials for their children and struggle to provide regular food.
-Early marriages and teenage pregnancies often result in girls leaving school earlier.
-
-Parental education levels are generally low, with many parents above 50 having only primary education.
-The education system faces challenges such as inadequate school supplies, leading to high dropout rates.
-Children start primary school at ages 5-7, and secondary education runs for four years, with options to pursue advanced levels.
+Children start to help their parents with chores from an early age (collecting fire wood or water, tending crops or animal care).
+
+School is not mandatory and parental education levels in these communities is  generally low, with a minority of mothers in the Holden et al (2022) sample having any secondary level education.
+The education system faces challenges such as overcrowding and lack of resources, leading to high dropout rates.
+Children start primary school at ages 5-9, and secondary education runs for four years, with options to pursue advanced levels.
+Lack of sanitary products to allow attendance of school during menstruation, early marriages and teenage pregnancies often result in girls performing worse than boys and leaving school earlier.
 
 The community exhibits low exposure to technology, with smartphones and touchscreen devices considered luxuries.
-Limited internet usage and power supply challenges contribute to this low adoption.
+Limited internet access and power supply challenges contribute to this low adoption.
 However, technology is more prevalent in institutions like Nyabyeya Forestry College.
 Participating families were recruited by the local research assistants, for example, via personal contact, visiting them at home, or calling them.
-Families were invited to the Nyabyeya Forestry College (transport offered via boda boda (motorcycle)), and children participated in a quiet room in the College.
+Families were invited to participate at the Nyabyeya Forestry College (transport offered via boda boda (motorcycle taxi)), and children participated in a quiet room in the College.
 
@@
 
-Ocuilan is a municipality located in the centre south of Mexico with a population of 36,223 inhabitants, distributed in 48 towns in an area of 344.84 km^2^  inside the Mexican State (Ocuilan, n.d.).
-Geographically Ocuilan has an altitude of between 1000 to 2 600 m situated 80 km south of Mexico City.
-(INEGI,2010)
-
-The communities in Ocuilan are distributed on a mountain range called Trans-Mexican volcanic Belt surrounded by valleys and mountains, the climate is semi-humid with summer rains, and average temperatures vary between 8C and 22C throughout the year.
+Ocuilan is a municipality located in the center south of Mexico with a population of 36 223 inhabitants, distributed in 48 towns in an area of 344.84 km^2^ inside the Mexican State (Ocuilan, n.d.).
+Geographically, Ocuilan has an altitude of between 1000 to 2600 m situated 80 km south of Mexico City (INEGI, 2010).
+
+The communities in Ocuilan are distributed on a mountain range called Trans-Mexican volcanic Belt surrounded by valleys and mountains, the climate is semi-humid with summer rains, and average temperatures vary between 8°C and 22°C throughout the year.
 The higher elevations have mixed pine forests with more tropical vegetation in the lowlands.
-The distribution of the land is 31.91% agriculture, 0.48% urban zone and the rest forest.
-(INEGI,2010)
+The distribution of the land is 31.91% agriculture, 0.48% urban zone and the rest forest (INEGI,2010).
 
@@
 The Spanish kingdom allied itself with those towns and waged war on the Aztec Empire, succeeding in taking the Mexica capital on 13 August 1521.
-Although there was some resistance, all the towns within what is now the State of Mexico fell to the Spaniards shortly thereafter.
-(Edo Mex, 2018)
-
+Although there was some resistance, all the towns within what is now the State of Mexico fell to the Spaniards shortly thereafter (Edo Mex, 2018).
 During the period of Spanish control, the municipality of Ocuilan was primarily characterized by agricultural activities.
-The presence of missionary friars played an important role in the dissemination of catholic religion and the Spanish language.
-(Edo Mex, 2018)  Over the course of the conquest, the Spanish language gradually gained prominence, but it is still possible to find indigenous languages like Tlahuica, Nahualt and Mazahua among the inhabitants.
-(Ocuilan, n.d.)
-
-Following the attainment of Mexican independence, Ocuilan continued to be a farming area and also emerged as an important religious centre, attracting pilgrims from various regions of Mexico.
-During the Mexican Revolution, the locality assumed significance as a stronghold of the Zapatistas which played an essential role in the enactment of the Political Constitution of 1917.
-In the subsequent decades, political stability, economic development, and population growth in the State of Mexico.
-(Edo Mex, 2018)   Nowadays, livestock farming and trout rearing stand as the dominant economic pursuits in Ocuilan.
-(Ocuilan, n.d.)
-
-Demographically, the average household in Ocuilan comprises 4.1 inhabitants, (Ocuilan, n.d.)  primarily adhering to a nuclear family structure characterized by an authoritative rearing model.
+The presence of missionary friars played an important role in the dissemination of catholic religion and the Spanish language (Edo Mex, 2018).
+Over the course of the conquest, the Spanish language gradually gained prominence, but it is still possible to find indigenous languages like Tlahuica, Nahualt and Mazahua among the inhabitants (Ocuilan, n.d.).
+
+Following the attainment of Mexican independence, Ocuilan continued to be a farming area and also emerged as an important religious center, attracting pilgrims from various regions of Mexico.
+During the Mexican Revolution, Ocuilan assumed significance as a stronghold of the Zapatistas which played an essential role in the enactment of the Political Constitution of 1917.
+The subsequent decades brought political stability, economic development, and population growth in the State of Mexico (Edo Mex, 2018).
+Nowadays, livestock farming and trout rearing are the dominant economic pursuits in Ocuilan (Ocuilan, n.d.).
+
+Demographically, the average household in Ocuilan comprises 4.1 inhabitants, (Ocuilan, n.d.), primarily adhering to a nuclear family structure characterized by an authoritative rearing model.
 Parents assume a proactive role in establishing parental control, emphasizing the enforcement of rules and disciplinary measures (Delfín-Ruiz et al., 2021).
@@
 
-Regarding education, children in Ocuilan typically start their day by attending kindergarten between 8 am to 12 pm.
+Children in Ocuilan typically begin their early schooling experience at around 3 years of age and attend kindergarten between 8 am to 12 pm.
 Afterwards, mothers or other family members take care of the children as formal childcare options are limited.
-Consequently, children typically begin their early schooling experience at around 3 years of age.
 
 In terms of technology, approximately 77.9% of households possess at least one screen device, whereas access to the Internet is available to only 22.7% of households.
-Consequently, while a significant proportion of children have experienced digital technology a considerable segment lacks exposure and accessibility to such resources.
-(Ocuilan, n.d.)
-
-For the study, we first obtained permission from Mexican school authorities to visit local kindergartens.
+Consequently, while a significant proportion of children have experienced digital technology a considerable segment of the population lacks exposure and accessibility to such resources (Ocuilan, n.d.).
+
+For this study, we first obtained permission from Mexican school authorities to visit local kindergartens.
 Next, we contacted parents and invited them to take part in the research.
-The evaluation of interested children was then carried out in a separate area within their own kindergartens, overseen by a Spanish-speaking research assistant.
+Data of interested children was then collected in a separate area within their own kindergartens, overseen by a Spanish-speaking research assistant.
 
@@
 Children in the current study came mostly from middle class families.
-In Western middle-class families care-giving is usually child-centered and parents are responsive to children’s needs and wishes.
+In Western middle-class families, care-giving is usually child-centered and parents are responsive to children’s needs and wishes.
 Autonomy and independence are valued but, compared to countries such as Germany, children are somewhat less independent.
-As the UK is a multicultural country (and multiculturalism is increasing), parenting values are heterogenous—though the population in Plymouth, as compared to the rest of the UK, is less heterogenous and predominantly White British.
+As the UK is a multicultural country (and multiculturalism is increasing), parenting values are heterogeneous — though the population in Plymouth, as compared to the rest of the UK, is less heterogeneous and predominantly White British.
 
@@
 The population within city limits is 4.5 million while including the metro population, it stands at 7.1 million.
+
+Pune experiences a tropical wet and dry climate with average temperatures ranging between 20 and 28°C.
+Summer, monsoon and winter are the three main seasons with May being the hottest month.
+During summer, i.e., mid-March to mid-June, temperatures can go as high as 42°C.
+Monsoon lasts from June to October with most of the annual rainfall of 722mm falling between June and September with July being the wettest month.
+In the months of December and January, temperatures remain around 29°C with overnight temperatures dropping to below 12°C.
+
+Pune is considered to be the cultural capital of Maharashtra with emphasis on education, arts and crafts, music and theater.
+The most common language spoken is Marathi.
+Hinduism is the major religion practiced by just under 80% of the population.
+Other religions practiced are Islam, Buddhism, Jainism, Christianity, Sikhism and Zoroastrianism.
+Food is made of sorghum and pearl millets with a fairly large consumption of coconut, garlic and green chillies to spice up the food.
+Pune is referred to as the ‘Oxford of the East’ because of its reputed educational institutions and is also considered to be one of the most livable cities in India.
+The literacy rate in Pune is 86.15%.
+
 Pune is one of the largest information technology hubs in India and is also an important automobile and manufacturing hub.
@@
 The top three industries that offer employment are automotive, manufacturing and information technology and start-ups.
-Automobile industries such as Tata Motors, Jaguar, Renault, Volkswagen, General motors, Skoda, Force motors, Kinetic motors  and Mercedes-Benz have their manufacturing plants in Chakan, an industrial area around Pune.
-Cummins, a leading manufacturer of diesel and natural gas engines as well as JCB, the farm equipment company are other renowned investors.
+Automobile industries have their manufacturing plants in Chakan, an industrial area around Pune.
+A leading manufacturer of diesel and natural gas engines as well as a farm equipment company are other renowned investors.
 The manufacturing industry provides employment to over 600 000 people while the IT sector employs over 350 000 people.
@@
 
-Pune is referred to as the ‘Oxford of the East’ because of its reputed educational institutions and is also considered to be one of the most livable cities in India.
-The literacy rate in Pune is 86.15%.
+During the 18th century, Pune was part of the Maratha empire and seat of the Peshwas.
+Besides, it has been ruled by dynasties such as the Rashtrakutas, Ahmednagar Sultanate, Mughals and Adil Shahi dynasty.
+The modern city of Pune is comprised of many distinct neighbourhoods.
+These include ‘peths’ [Marathi for locality] on the eastern bank of the Mutha river and the cantonment areas of Khadki and Camp.
 As a result of rapid industrialization since the 1960s, a large number of people moved to Pune.
@@
 Nearly half of the slum dwellers do not have in-house toilets and 10% do not have electricity.
-Pune experiences a tropical wet and dry climate with average temperatures ranging between 20 and 28°C.
-Summer, monsoon and winter are the three main seasons with May being the hottest month.
-During summer, i.e.
-mid-March to mid-June, temperatures can go as high as 42°C.
-Monsoon lasts from June to October with most of the annual rainfall of 722mm falling between June and September with July being the wettest month.
-In the months of December and January, temperatures remain around 29°C with overnight temperatures dropping to below 12°C.
-
-During the 18th century, Pune was part of the Maratha empire and seat of the Peshwas.
-Besides it has been ruled by dynasties such as the Rashtrakutas, Ahmednagar Sultanate, Mughals and Adil Shahi dynasty.
-The modern city of Pune is comprised of many distinct neighbourhoods.
-These include ‘peths’ [Marathi for locality] on the eastern bank of the Mutha river and the cantonment areas of Khadki and Camp.
-Pune is considered to be the cultural capital of Maharashtra with emphasis on education, arts and crafts, music and theater.
-The most common language spoken is Marathi.
-Hinduism is the major religion practiced by just under 80% of the population.
-Other religions practised are Islam, Buddhism, Jainism, Christianity, Sikhism and Zoroastrianism.
-Food is made of sorghum and pearl millets with a fairly large consumption of coconut, garlic and green chillies to spice up the food.
+
+Children are taught to address their elders (either in English or the equivalent term in a local language) as ‘older brother/sister’, ‘uncle’, ‘aunty’ or ‘grandmother’/’grandfather’ even if they are not relatives.
+This is considered to be respectful.
+At times, children touch the feet of elders as a sign of respect.
+Parents encourage their children to visit family and friends particularly during festivals.
 
@@
 Following a school day, it is not uncommon for children to attend tuition or focussed coaching in sports or arts.
+
 Most households will have at least one mobile phone as well as a laptop so children are exposed to technology fairly early.
 
-Children are taught to address their elders (either in English or the equivalent term in a local language) as ‘older brother/sister’, ‘uncle’, ‘aunty’ or ‘grandmother’/’grandfather’ even if they are not relatives.
-This is considered to be respectful.
-At times, children touch the feet of elders as a sign of respect.
-Parents encourage their children to visit family and friends particularly during festivals.
 For the current study, recruitment took place via personal contacts.
@@
 The sample was drawn from a children’s museum in San Jose, California located in the western United States of America.
-San Jose is a large city with a population of approximately 983,000 people and geographically is within the Santa Clara Valley in the southern part of the Bay Area, California.
+San Jose is a large city with a population of approximately 983 000 people and geographically is within the Santa Clara Valley in the southern part of the Bay Area, California.
 
@@
 
-Parental socialization goals in California typically emphasize tolerance, individualism, diversity, personal fulfillment, and holistic autonomy, but vary greatly as a result of its diverse populous.
+Parental socialization goals in California typically emphasize tolerance, individualism, diversity, personal fulfillment, and holistic autonomy, but vary greatly as a result of its diverse population.
 Education and learning are seen as important aspects of children’s lives.
@@
 English serves as the primary medium of instruction within the educational system, but children often grow up with significant exposure to other indigenous languages like Herero and Damara within their communities.
-Socialization goals and parenting goals reflect that of urban communities in the Global South emphasizing “communal psychological autonomy and relatedness” (Keller & Kaertner, 2013).
+Socialization and parenting goals reflect that of urban communities in the Global South emphasizing “communal psychological autonomy and relatedness” (Keller & Kaertner, 2013).
 Children in such communities spend a significant portion of their time on activities related to school, family, and leisure with peers and siblings.
@@
 * Pendleton, W., & Nickanor, N. (2016). The State of Food Insecuritity in Windhoek, Namibia (No. 14). Southern African Migration Programme.
+
+# Method
+
+We adapted the task developed by Prein and colleagues [@prein2023tango].
+We refer to the original publication for a detailed description of its development, implementation and psychometric evaluation (in Germany).
+Below, we give an overview and focus on the cross-cultural adaptation of the task.
+The task itself, including all the versions used in the study, can be accessed via the following website: https://ccp-odc.eva.mpg.de/tango-cc/
+
+## Setup and Procedure
+
+```{r task, include = T, fig.align = "center", fig.cap = "Screenshot from the task.
+The scene depicts the choice phase in a test trial.
+Participants had to use the gaze of the agent to locate the balloon and click on the hedge where they thought the balloon was.", out.width="80%"}
+knitr::include_graphics("../figures/task.png")
+```
+
+The task was implemented as a browser-based interactive picture book using `HTML` and `JavaScript`.
+Participants saw animated agents on a touch screen device, listened to pre-recorded audio instructions and responded by touching the screen.
+In all communities, a research assistant, fluent in the local language(s), guided the child through the task.
+
+Figure \@ref(fig:task) shows a screenshot from the task.
+The task was introduced verbally by the assistant as the balloon game in which the participant would play with other children to find a balloon.
+On each trial, participants saw an agent located in a window in the center of the screen.
+A balloon fell down from its starting position just below the agent.
+The agent's gaze followed the trajectory of the balloon.
+That is, the pupils and the iris were programmed to align with the center of the balloon.
+Once the balloon had landed on the ground, the agent was instructed to locate it, that is, to touch the location on the screen where they thought the balloon was.
+On each trial, we recorded the exact x-coordinate of the participant's touch.
+
+There were two types of familiarization trials.
+In fam1 trials, the balloon fell down and landed in plain sight.
+Participants simply had to touch the visible balloon.
+In fam2 trials, the trajectory of the balloon was visible but it landed behind a small barrier (a hedge - see Figure \@ref(fig:task)).
+Thus, participants needed to touch the hedge where they saw the balloon land.
+Next came test trials.
+Here, the barrier moved up and covered the balloon's trajectory.
+That is, participants only saw the agent's eyes move, but not the balloon.
+They had to infer the location of the balloon based on the agent's gaze direction.
+During fam1, fam2 and the first test trial, children heard voice overs commenting what happened on the screen.
+Critically, the agent was described as wanting to help the child and always looking at the balloon (see section [script](#appendix-script) for the English wording).
+
+Children completed one fam1 trial, two fam2 trials and 16 test trials.
+We excluded the first test trial from the analysis because of the voice-over.
+Thus, 15 test trials were used in the analysis below.
+
+Each child saw eight different agents, four male, four female.
+The agent changed from trial to trial, with alternating genders.
+A coin toss before the first trial decided whether the first agent was male or female.
+The order in which agents were shown was randomized with the constraint that all agents had to be shown once until an agent was shown again.
+The color of the balloon also changed from trial to trial in a random order, also with the constraint that all colors appeared once before any one was repeated.
+
+The location (x-coordinate) where the balloon landed was determined in the following way: The screen was divided in ten equally sized bins.
+On each trial, one of the bins was randomly selected and the exact x-coordinate was randomly chosen within that bin.
+Constraints were that the balloon landed in each bin equally often and the same bin appeared no more than twice in a row.
+
+All children were tested with a touch screen device with a size between 11 and 13 inch equipped with a webcam.
+The data was either stored locally or sent to a server.
+In addition to the behavioral data, we stored the webcam recording of the session for verification purposes.
+
+## Culture-specific adaptations
+
+The following components of the task were adapted to each cultural setting: voice-overs, agents, background.
+The voice overs were originally formulated in British English and German (see section [script](#script)).
+For each setting, they were first translated/adapted to the local language.
+In some cases (BaYaka and Bandongo), this was done by first translating them to French.
+The translations were done by native or near-native speakers.
+They were not exact translations of the original text but were adapted so that children from the respective community would understand them.
+For example, the word "hedge" in the British English version was changed to "bush" for the Nigerian English version to adjust for how children in the respective community would refer to the thing they saw.
+The content of each utterance was comparable across languages.
+
+The agents were drawn for each cultural setting in close collaboration with local researchers and/or research assistants.
+They were meant to show young adults and represent the diversity in appearance prevalent in the local population.
+Figure \@ref(fig:figagents) shows the agents that were used in the study.
+Some agents were used in multiple cultural settings.
+All agents had roughly the same underlying eye-geometry (size of the pupil and the iris) and only differed in superficial features.
+
+```{r figagents, include = T, fig.align = "center", fig.cap = "Agents used in the task. Some agents were used for multiple cultural settings", out.width="100%"}
+knitr::include_graphics("../figures/agents.png")
+```
+
+## Questionnaire
+
+The parents of children who participated in the task were asked to fill out a short questionnaire with the following questions (English version):
+
+* Is there a device with a screen in your household? (answer: "yes" or "no")
+* Does your child have experience with touchscreens? (answer: "yes" or "no")
+* How many people live in your household (people residing and sleeping in one place e.g., a house)? (answer: number)
+* How many children live in your household? (answer: number)
+* How many children in your household are younger than the child participating in the study? (answer: number)
+
+The questions were translated to parents’ native language by an assistant fluent in English and the parents’ language.
+Whenever parents were not able to read or write (most relevant for Chimfunshi, BaYaka, Bandongo, Khwe, Ha||om, Nyabyeya), research assistants asked the question and recorded the answer.
+Figure \@ref(fig:figpred2) summarizes the responses to the questions for each cultural setting.
 
@@
 
-# Method
-
-We adapted the task developed by Prein and colleagues [@prein2023tango].
-We refer to the original publication for a detailed description of its development, implementation and psychometric evaluation (in Germany).
-Below give an overview and focus on the cross-cultural adaptation of the task.
-The task itself, including all the versions used in the study, can be accessed via the following website: https://ccp-odc.eva.mpg.de/tango-cc/
-
-## Setup and Procedure
-
-```{r task, include = T, fig.align = "center", fig.cap = "Screenshot from the task.
-The scene depicts the choice phase in a test trial.
-Participants had to use the gaze of the agent to locate the balloon and click on the hedge where they thought the balloon was.", out.width="80%"}
-knitr::include_graphics("../figures/task.png")
-```
-
-The task was implemented as a browser-based interactive picture book using `HTML` and `JavaScript`.
-Participants saw animated agents on a touch screen device, listened to pre-recorded audio instructions and responded by touching the screen.
-In all communities, a research assistant, fluent in the local language(s), guided the child through the task.
-
-Figure \@ref(fig:task) shows a screenshot from the task.
-The task was introduced verbally by the assistant as the balloon game in which the participant would play with other children to find a balloon.
-On each trial, participants saw an agent located in a window in the center of the screen.
-A balloon fell down from its starting position just below the agent.
-The agent's gaze followed the trajectory of the balloon.
-That is, the pupils and the iris were programmed to align with the center of the balloon.
-Once the balloon had landed on the ground, the agent was instructed to locate it, that is, to touch the location on the screen where they thought the balloon was.
-On each trial, we recorded the exact x-coordinate of the participant's touch.
-
-There were two types of familiarization trials.
-In fam1 trials, the balloon fell down and landed in plain sight.
-Participants simply had to touch the visible balloon.
-In fam2 trials, the trajectory of the balloon was visible but it landed behind a small barrier (usually a hedge - see Figure \@ref(fig:task)).
-Thus, participants needed to touch the hedge where they saw the balloon land.
-Next came test trials.
-Here, the barrier moved up and covered the balloons trajectory.
-That is, participants only saw the agents eyes move, but not the balloon.
-They had to infer the location of the balloon based on the agent's gaze direction.
-During fam1, fam2 and the first test trial, children heard voice overs commenting what happened on the screen.
-Critically, the agent was described as wanting to help the child and to always look at the balloon (see section [script](#appendix-script) for the English wording).
-
-Children completed one fam1 trial, two fam2 trials and 16 test trials.
-We excluded the first test trial from the analysis because of the voice-over.
-Thus, 15 test trials were used in the analysis below.
-
-Each child saw eight different agents, four male, four female.
-The agent changed from trial to trail, with alternating genders.
-A coin toss before the first trial decided whether the first agent was male or female.
-The order in which agents were shown was randomized with the constraint that all agents had to be shown once until an agent was shown again.
-The color of the balloon also changed from trial to trial in a random order, also with the constraint that all colors appeared once before any one was repeated.
-
-The location (x-coordinate) where the balloon landed was determined in the following way: The screen was divided in ten equally sized bins.
-On each trial, one of the bins was randomly selected and the exact x-coordinate was randomly chosen within that bin.
-Constraints were that the balloon landed in each bin equally often and the same bin appeared no more than twice in a row.
-
-All children were tested with a touch screen device with a size between 11 and 13 inch equipped with a webcam.
-The data was either stored locally or sent to a server.
-In addition to the behavioral data, we stored the webcam recording of the session for verification purposes.
-
-## Culture-specific adaptations
-
-The following components of the task were adapted to each cultural settings: voice-overs, agents, background.
-The voice overs were originally formulated in British English and German (see section [script](#script)).
-For each setting, they were first translated/adapted to the local language.
-In some cases (BaYaka and Bandongo) this was done by first translating them to French.
-The translations were done by native or near-native speakers.
-They were not exact translations of the original text but were adapted so that children from the respective community would understand them.
-For example, the word "hedge" in the British English version  was changed to "bush" for the Nigerian English version to adjust for how children in the respective community would refer to the thing they saw.
-The content of each utterance was comparable across languages.
-
-The agents were drawn for each cultural setting in close collaboration with local researchers and/or research assistants.
-They were meant to show young adults and represent the diversity in appearance prevalent in the local population.
-Figure \@ref(fig:figagents) shows the agents that were used in the study.
-Some agents were used in multiple cultural settings.
-All agents had the same underlying eye-geometry (size of the pupil and the iris) and only differed in superficial features.
-
-```{r figagents, include = T, fig.align = "center", fig.cap = "Agents used in the task. Some agents were used for multiple cultural settings", out.width="100%"}
-knitr::include_graphics("../figures/agents.png")
-```
-
-## Questionnaire
-
-The parents of children who participated in the task were asked to fill out a short questionnaire with the following questions (English version):
-
-* Is there a device with a screen in your household? (answer: "yes" or "no")
-* Does your child have experience with touchscreens? (answer: "yes" or "no")
-* How many people live in your household (people residing and sleeping in one place e.g., a house)? (answer: number)
-* How many children live in your household? (answer: number)
-* How many children in your household are younger than the child participating in the study? (answer: number)
-
-The questions were translated to parents native language by a native speaker.
-In The number of older children living in the same household was computed by subtracting one (the child taking the test) and the number of younger children from the total number of children.
-Whenever parents were not able to read or write (most relevant for Chimfunshi, BaYaka, Bandongo, Khwe, Ha||om), research assistants asked the question and recorded the answer.
-
 # Analysis
@@
 For regression models, we used the default priors built in to `brms`.
-The dependent variable in all regression models was imprecision, that is, the absolute distance between the true location of the balloon (to x-coordinate of its center) and the location where the participant touched the screen.
+The dependent variable in all regression models was imprecision, that is, the absolute distance between the true location of the balloon (x-coordinate of its center) and the location where the participant touched the screen.
 We used a Log-normal distribution to model the data because the natural lower bound for imprecision is zero and the data was right skewed with a long tail.
 Numeric predictors that entered the models were scaled to have a mean of zero and a standard deviation of 1.
-For each model we collected 6000 samples from four chains, removing the first 2000 for burn-in.
+For each model, we collected 6000 samples from four chains, removing the first 2000 for burn-in.
 All models had converging chains (Rhat values < 1.01).
 Details specific to each analysis can be found below.
-The analysis code can be found in the online repository associated with the study (link).
+The analysis code can be found in the online repository associated with the study (https://github.com/ccp-eva/gafo-cc-analysis).
 
@@
 We decided to change this and remove random slopes for trial but include them for target centrality.
-The reasons were as follows: trail effects in the sense of learning across trials were unlikely because participants did not receive differential feedback.
+The reasons were as follows: trial effects in the sense of learning across trials were unlikely because participants did not receive differential feedback.
 Furthermore, in multiple studies with the same task since the registration we never found any trial effects [@prein2023tango; @prein2023variation].
@@
 
-0## Cross-cultural variation
+## Cross-cultural variation
 
@@
 To get around this problem, we used a cross-validation procedure [see e.g., @stengelin2023children].
-For each cultural setting we randomly sampled a data set that was 5/6 the size of the full data set (training data).
-Then we fit the model to this training data and used the estimated model parameters to predict the remaining 1/6 of the data (testing data).
+For each cultural setting, we randomly sampled a data set that was 5/6 the size of the full data set (training data).
+Then, we fit the model to this training data and used the estimated model parameters to predict the remaining 1/6 of the data (testing data).
 We then compared the model predictions from the different models by computing the mean difference between the true and predicted imprecision, over all trials in the testing data set.
-This approach gets around the problem mentioned in above because the model predicts a new dataset for which the individual random intercepts are unknown.
+This approach gets around the problem mentioned above because the model predicts a new data set for which the individual random intercepts are unknown.
 Clustering by culture could therefore only be predicted by a model that included culture as a predictor.
@@
 The results showed that the `culture_age` model made, by far, the best predictions and outperformed the `culture` model in `r round(mean(cv_cult$m3_beats_m2),2)*100`% and the `null` model in `r round(mean(cv_cult$m3_beats_m1),2)*100`% of cases.
-Furthermore, the `culture` model outperformed the `null` model in `r round(mean(cv_cult$m2_beats_m1),2)*100` % of cases.
+Furthermore, the `culture` model outperformed the `null` model in `r round(mean(cv_cult$m2_beats_m1),2)*100`% of cases.
 This suggests that there were substantial absolute and developmental differences between cultural settings (see Figure \@ref(fig:figdev)A).
@@
 
-In the second analysis focused on signatures in the data that suggest that children in all cultural settings use similar cognitive processes to infer the location of the balloon.
+The second analysis focused on signatures in the data that suggest that children in all cultural settings use similar cognitive processes to infer the location of the balloon.
 The first -- somewhat weaker -- signature was simply an increase in performance with age.
@@
 That is, the further away from the center the balloon lands, the more imprecise should participants be.
-This second signature is derived from the model by the cognitive model introduced in @prein2023variation.
-It predicts that trials in which the agent looks further away from the center (i.e.
-to the left or right side of the screen) result in higher levels of imprecision compared to trials in which the agent looks closer to the middle.
-
-These prediction is best understood by considering a similar phenomenon: pointing a torch light to a flat surface.
-The width of the light beam represents each individual's level of uncertainty in vector estimation and is represented in the model as a normal distribution around the true gaze vector with a participant specific standard deviation.
+This second signature is derived from the cognitive model introduced in @prein2023variation.
+It predicts that trials in which the agent looks further away from the center (i.e., to the left or right side of the screen) result in higher levels of imprecision compared to trials in which the agent looks closer to the middle.
+
+The cognitive model implemented gaze following as a social form of vector following, whereby participants estimate a gaze vector that connects the center of the agent's eye and the center of the pupil.
+The model's prediction about a centrality effect is best understood by considering a similar phenomenon: pointing a torch light to a flat surface.
+The width of the light beam represents each individual's level of uncertainty in vector estimation and is represented in the model as a Normal distribution around the true gaze vector with a participant specific standard deviation.
 On each trial, the model assumes that the participant samples a vector from this distribution to infer the location of the balloon.
-The smaller the standard deviation -- -- the narrower the light beam --, the more precise on average the participant is.
+The smaller the standard deviation -- the narrower the light beam --, the more precise on average the participant is.
 Now, when the torch is directed straight down, the light beam is concentrated in a relatively small area.
-When the torch is rotated to the side, the the light from one half of the cone must travel further than the light from the other half to reach the surface.
+When the torch is rotated to the side, the light from one half of the cone must travel further than the light from the other half to reach the surface.
 As a consequence, the light is spread over a wider area.
@@
 Nevertheless, we wanted to quantify the evidence in favor of the vector-based gaze estimation model compared to these alternative center bias and random guessing models.
-We also added a random guessing model to the comparison according to which participants also ignored the agents gaze but simply touched random locations on the screen.
 
 The vector-based gaze estimation model has been described in detail in @prein2023variation.
-In brief, the it inversely models the process generating clicks based on observed eye movements.
+In brief, it inversely models the process generating clicks based on observed eye movements.
 Formally, the model is defined as:
@@
 
-Here, $\sigma_v$ plays a crucial role in determining the accuracy with which participants estimate pupil angles.
+Here, $\sigma_v$ determines the level of accuracy with which participants estimated the pupil angles, and it is thus the component of the model that defines $\theta$.
 Smaller values of $\sigma_v$ result in a narrow distribution around the pupil angle, making clicks far away from the target less likely.
@@
 Thus, the goal of the model was to estimate participant-specific values for $\sigma_v$: $\sigma_{v_i}$.
-These participant specific values were sampled from a normal distribution centered around the value we expected for a child given their age ($age_i$): $\sigma_{v_i} \sim e^{\mathcal{N}(\sigma_{v_{age}}, \sigma^{\sigma_{v_{age}}}})$.
+These participant-specific values were sampled from a Normal distribution centered around the value we expected for a child given their age ($age_i$): $\sigma_{v_i} \sim e^{\mathcal{N}(\sigma_{v_{age}}, \sigma^{\sigma_{v_{age}}}})$.
 (Values were exponentiated to always be positive).
-$\sigma_{v_{age}}$ in turn was defined via a simple regression model: $\sigma_{v_{age}} = \beta_0^{\sigma_{v_{age}}} + age_i \cdot \beta_1^{\sigma_{v_{age}}}$.
+$\sigma_{v_{age}}$, in turn, was defined via a simple regression model: $\sigma_{v_{age}} = \beta_0^{\sigma_{v_{age}}} + age_i \cdot \beta_1^{\sigma_{v_{age}}}$.
 Where $\beta_0^{\sigma_{v_{age}}}$ and $\beta_1^{\sigma_{v_{age}}}$ represent the population-level intercept and slope that together describe a curve that represents the average developmental pattern.
@@
 The two alternative models assume that participants ignore the agent's gaze completely, instead they are assumed to follow simple heuristics.
-According to the center bias model they always try to click in the center of the screen: $P(x_c) \sim \mathcal{N}(960, 160)$.
+According to the center bias model, they always try to click in the center of the screen: $P(x_c) \sim \mathcal{N}(960, 160)$.
 (960 is the x-coordinate of the center and 160 is the width of the balloon).
@@
 The incorporation of the prior distribution over parameters in the averaging process implicitly considers model complexity: models with more parameters typically exhibit broader prior distributions over parameter values and broader prior distribution can attenuate the potential gains in predictive accuracy that a model with more parameters might otherwise achieve [@lee2014bayesian].
-
-Table \@ref(tab:bftable) shows the Bayes Factors in favor of the vector-based gaze estimation model for each cultural setting.
-The evidence in favor of the gaze model compared to the two alternative models was clear (all BF > 1 000 000 000 000 000).
-This result rules out that the u-shaped pattern in the data was the result of participants always clicking the center instead of following gaze.
 
@@
 
+Table \@ref(tab:bftable) shows the Bayes Factors in favor of the vector-based gaze estimation model for each cultural setting.
+The evidence in favor of the gaze model compared to the two alternative models was clear (all BF > 1 000 000 000 000 000).
+This result rules out that the u-shaped pattern in the data was the result of participants always clicking the center instead of following gaze.
+
 ## Experiential predictors
@@
 The final analysis focused on whether we could predict performance in the task by aspects of everyday experience.
-For the ease of model fitting, we aggregated the data for each participant so that models predicted the average imprecision across trials^[@prein2023variation showed that the performance mean is nearly perfectly correlated with $\sigma_v$.
+For the ease of model fitting, we aggregated the data for each participant so that models predicted the average imprecision across trials [@prein2023variation showed that the performance mean is nearly perfectly correlated with $\sigma_v$.
 When re-running the winning model on the trial-by-trial data, the results were qualitatively and quantitatively identical.].

### 2024-06-06 supplement/supplement.Rmd
update repo new submission

@@
 title: "A universal of human social cognition: Children from 17 communities process gaze in similar ways"
-subtitle: "Supplemental material"
+subtitle: "Supplementary Material"
 author:
@@
 Details specific to each analysis can be found below.
-The analysis code can be found in the online repository associated with the study (https://github.com/ccp-eva/gafo-cc-analysis).
-
-We pre-registered an analysis plan at https://osf.io/tdsvc.
+The analysis code can be found in the online repository associated with the study<!--[masked for peer review; see .zip file included]--> (https://github.com/ccp-eva/gafo-cc-analysis/).
+
+We pre-registered an analysis plan at <!--https://osf.io/tdsvc/?view_only=f404d66c967542f28ce4af16371f34e6-->https://osf.io/tdsvc.
 The analyses reported below follow the same logic as the pre-registered analyses but they differ substantially in detail.

### 2024-07-18 paper/paper.Rmd
correct spelling mistakes, update to APA 7

@@
 title             : "A universal of human social cognition: Children from 17 communities process gaze in similar ways"
-shorttitle        : "Gaze-following across 17 communities"
+shorttitle        : "gaze following across 17 communities"
 
 author: 
-  - name          : "Manuel Bohn (ORCID: 0000-0001-6006-1348)"
+  - name          : "Manuel Bohn"
     affiliation   : "1,2,*"
@@
       - "Writing - Review & Editing"
-  - name          : "Julia Prein (ORCID: 0000-0002-3154-6167)"
+  - name          : "Julia Christin Prein"
     affiliation   : "1,2,*"
@@
       - "Investigation"
-  - name          : "Florian M. Bednarski (ORCID: 0000-0003-4384-4791)"
+  - name          : "Florian M. Bednarski"
     affiliation   : "4"
@@
       - "Investigation"
-  - name          : "Michael C. Frank (ORCID: 0000-0002-7551-4378)"
+  - name          : "Michael C. Frank"
     affiliation   : "6"
@@
       - "Writing - Review & Editing"
-  - name          : "Annette M. E. Henderson (ORCID: 0000-0003-4384-4791)"
+  - name          : "Annette M. E. Henderson"
     affiliation   : "4"
@@
       - "Writing - Review & Editing"
-  - name          : "Patricia Kanngiesser (ORCID:0000-0003-1068-3725)"
+  - name          : "Patricia Kanngiesser"
     affiliation   : "7"
@@
       - "Writing - Review & Editing" 
-  - name          : "Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733)"
+  - name          : "Dilara Keşşafoğlu"
     affiliation   : "8"
@@
       - "Writing - Review & Editing" 
-  - name          : "Bahar Köymen (ORCID: 0000-0001-5126-8240)"
+  - name          : "Bahar Köymen"
     affiliation   : "9"
@@
       - "Investigation"
-  - name          : "Shirley Magazi (ORCID: 0009-0006-0479-9800)"
+  - name          : "Shirley Magazi"
     affiliation   : "10"
@@
      - "Investigation"
-  - name          : "Wesley R. Pieters (ORCID:0000-0002-6152-249X)"
+  - name          : "Wesley R. Pieters"
     affiliation   : "10"
@@
      - "Investigation"    
-  - name          : "Katie Slocombe (ORCID: 0000-0002-7310-1887)"
+  - name          : "Katie Slocombe"
     affiliation   : "11"
@@
      - "Writing - Review & Editing"
-  - name          : "Robert Z. Sparks (ORCID: 0000-0001-7545-0522)"
+  - name          : "Robert Z. Sparks"
     affiliation   : "6"
@@
      - "Investigation"
-  - name          : "Zhen Zhang (ORCID: 0000-0001-9300-0920)"
+  - name          : "Zhen Zhang"
     affiliation   : "12"
@@
       - "Writing - Review & Editing"   
-  - name          : "Yufei Zong (ORCID: 0009-0000-5012-0244)"
+  - name          : "Yufei Zong"
     affiliation   : "12"
@@
       - "Investigation"
-  - name          : "Roman Stengelin (ORCID: 0000-0003-2212-4613)"
+  - name          : "Roman Stengelin"
     affiliation   : "2,10,+"
@@
       - "Writing - Review & Editing" 
-  - name          : "Daniel B. M. Haun (ORCID: 0000-0002-3262-645X)"
+  - name          : "Daniel B. M. Haun"
     affiliation   : "2,+"
@@
 Manuel Bohn was supported by a Jacobs Foundation Research Fellowship (2022-1484-00).
-We are gratful to thank all children and caregivers for participating in the study.
-We thank the Max Planck Society for the Advancement fo Science.
+We are grateful to thank all children and caregivers for participating in the study.
+We thank the Max Planck Society for the Advancement of Science.
 
@@
 Here we focus on gaze following, the bedrock of social interactions and coordinated activities, to test this claim.
-In this comprehensive cross-cultural study spanning five continents and 17 distinct cultural communities, we examined the development of gaze following in early childhood.
-We identified key processing signatures through a computational model that assumes that participants follow an individual’s gaze by estimating a vector emanating from the eye-center through the pupil.
-Using a single reliable touchscreen-based task, we found these signatures in all communities, suggesting that children worldwide processed gaze in highly similar ways.
-Absolute differences in performance between groups are accounted for by a cross-culturally consistent relationship between children’s exposure to touchscreens and their performance in the task.
+In a comprehensive cross-cultural study spanning five continents and 17 distinct cultural communities, we examined the development of gaze following in early childhood.
+We identified key processing signatures through a computational model that assumes that participants follow an individual’s gaze by estimating a vector emanating from the eye center through the pupil.
+We found these signatures in all communities, suggesting that children worldwide processed gaze in highly similar ways.
+Absolute differences between groups were accounted for by a cross-culturally consistent relationship between children’s exposure to touchscreens and their performance in the task.
 These results provide strong evidence for a universal process underlying a foundational socio-cognitive ability in humans that can be reliably inferred even in the presence of cultural variation in overt behavior.
 
-keywords          : "keywords"
-wordcount         : "X"
-
 bibliography      : "library.bib"
-csl: science.csl
 
@@
 classoption       : "man"
-output            : papaja::apa6_doc
+csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
+documentclass     : "apa7"
+output            :
+  papaja::apa6_pdf:
+    latex_engine: xelatex
+    keep_tex: true
+editor_options    : 
+  markdown: 
+    wrap: sentence
+header-includes:
+  - \usepackage{amsmath}
+  - \usepackage{amssymb}
+  - \usepackage{unicode-math}
+  - \usepackage{setspace}
+  - \usepackage{libertine}
+  - \captionsetup[figure]{font={stretch=1}}
+  - |
+    \makeatletter
+    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+      {-1em}%
+      {\normalfont\normalsize\bfseries\typesectitle}}
+
+    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+      {-\z@\relax}%
+      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+    \makeatother
 ---
@@
 
+# Research Transparency Statement
+
+All authors declare no conflicts of interest.
+Preregistration: The hypotheses, methods and parts of the analysis plan were preregistered (<!-- https://osf.io/tdsvc/?view_only=f404d66c967542f28ce4af16371f34e6-->https://osf.io/tdsvc) on March 12th, 2022, prior to data collection which began on March 18th, 2022.
+Additional analysis and deviations from the preregistration are reported in the Supplementary Material.
+Materials: All study materials are publicly available <!--[masked for peer review] --> (https://ccp-odc.eva.mpg.de/tango-cc/).
+Data: All primary data are publicly available <!--[masked for peer review; see .zip file included--> (https://github.com/ccp-eva/gafo-cc-analysis/).
+Analysis scripts: All analysis scripts are publicly available <!--[masked for peer review; see .zip file included]--> (https://github.com/ccp-eva/gafo-cc-analysis/).
+
+# Introduction
+
 Human socio-cognitive skills enable unique forms of communication and cooperation that provide a bedrock for cumulative culture and the formation of complex societies  [@tomasello2020adaptive; @laland2021understanding; @wellman2014making; @henrich2016secret; @tomasello2003makes; @legare2019development; @heyes2018cognitive].
-The eyes are the proverbial "window to the mind" and eye gaze is essential for many social reasoning processes  [@shepherd2010following; @doherty2006development].
-Others’ eye gaze is used to infer their focus of visual attention, which is a critical aspect of coordinated activities, including communication and cooperation [@tomasello2007reliance; @scaife1975capacity].
-The ability to follow gaze emerges early in childhood [@tang2023slow; @gredeback2010development; @byers2021development; @del2019developmental], and individual differences in children’s gaze-following ability predict later life outcomes, most notably communicative abilities [@brooks2005development; @carpenter1998social].
-Difficulties with gaze following have been linked to developmental disorders, including Autism [@itier2009neural].
+The eyes are the proverbial "window to the mind" and eye gaze is essential for many social reasoning processes  [@shepherd2010following; @doherty2006development; @emery2000eyes].
+Others’ eye gaze is used to infer their focus of visual attention, which is a critical aspect of coordinated activities, including communication and cooperation [@tomasello2007reliance; @scaife1975capacity; @langton2000eyes; @rossano2012gaze; @richardson2005looking; @sebanz2006joint].
 
-There is a widely held assumption that, despite substantial variation in developmental contexts, gaze-following works and develops in the same way across human societies [@tomasello2019becoming].
-However, this view is seemingly at odds with the substantial diversity in socio-cognitive development that cross-cultural studies have revealed [@miller2018contributions; @wellman2014making; @mayer2013synchrony; @dixson2018scaling; @taumoepeau2019cross].
+The ability to follow gaze emerges early in development [@tang2023slow; @gredeback2010development; @byers2021development; @del2019developmental].
+The earliest signs of gaze following have been found in infants as young as four months [@astor2021gaze; @d1997demonstration].
+Initially, infants rely more on head direction than actual gaze direction [@michel2021effects; @lempers1977development].
+Throughout the first two years of life, children refine their abilities: they interpret gaze in mentalistic terms, for example, they follow gaze to locations outside their own visual field by moving around barriers [@moll200412].
+Importantly, individual differences in children’s gaze following abilities predict later life outcomes, most notably communicative abilities [@carpenter1998social].
+For example, gaze following at 10 months predicts language scores at 18 months of age [@brooks2005development].
+Difficulties with gaze following have been linked to developmental disorders, including Autism [@itier2009neural; @thorup2016altered; @thorup2018reduced].
+This work highlights the importance of gaze following as a foundational building block of human social interaction and its central place in theorizing.
+
+A central assumption in the theoretical and empirical work discussed above is that, despite substantial variation in developmental contexts, gaze following works and develops in the same way across human societies [@tomasello2019becoming].
+This assumption -- despite being central to many developmental theories -- is currently not supported by evidence.
+On the contrary, cross-cultural studies have revealed substantial diversity in socio-cognitive development [@miller2018contributions; @wellman2014making; @mayer2013synchrony; @dixson2018scaling; @taumoepeau2019cross].
+One of the very few cross-cultural studies also found differences in the likelihood to follow gaze between communities [@callaghan2011early].
+
 One potential source for this paradox lies in the reliance on aggregated measures in cross-cultural studies.
 Absolute differences in mean performance across communities are interpreted as a signal of different underlying cognitive processes.
-In this study, we resolve this paradox by instead focusing on processing signatures that can be investigated independently of absolute community-level differences.
+In the present study, we resolve this paradox by instead focusing on processing signatures that can be investigated independently of absolute community-level differences.
 This allows us to directly evaluate the empirical foundation of claims about universal features of human social cognition.
-To this end, we conducted a pre-registered, large-scale, cross-cultural study on the development of gaze-following abilities to study potentially universal processing signatures.
-These signatures were derived from a computational model that assumes that participants follow gaze by estimating a vector emanating from the eye center through the pupil [@prein2023variation].
+To this end, we conducted a pre-registered, large-scale, cross-cultural study on the development of gaze following abilities to study potentially universal processing signatures.
+
+The processing signatures were derived from a computational model that assumes that participants follow gaze by estimating a vector emanating from the eye center through the pupil [@prein2024variation].
+The key innovation of the model is that it explains how individuals may use the same cognitive process but still differ in their measured abilities.
+The process always involves estimating a vector but also involves a degree of uncertainty because the eye center is not directly observable.
+Individuals are assumed to differ in their level of uncertainty with which they estimate the vector which causes differences in their observable behavior.
+Importantly, the assumed process leaves a key signature in the data that is observable independent of the absolute level of performance.
+In the present study, we therefore focus on this signature instead of absolute levels of performance when evaluating the claim whether there is evidence for a universal cognitive mechanism underlying gaze following.
 
@@
 These countries represent ~46% of the world’s population.
-Communities covered a broad spectrum of geographical locations, social and political systems, languages, and subsistence styles (see Supplemental Materials).
-This diversity allowed us to overcome the common pitfall of cross-cultural studies that compare urban communities from the global north to rural communities from the global south [@barrett2020towards].
+Communities covered a broad spectrum of geographical locations, social and political systems, languages, and subsistence styles (see Supplementary Material).
+This diversity allowed us to overcome the common pitfall of cross-cultural studies that compare urban communities from the Global North to rural communities from the Global South [@barrett2020towards].
 
@@
 (B) Screenshots from the task.
-Screenshots from the task.
-The upper scene depicts the start and the lower the choice phase in a test trial.
+The upper scene depicts the start, and the lower scene depicts the choice phase in a test trial.
 Participants had to use the gaze of the agent to locate the balloon and touch the location on the hedge where they thought the balloon was.
-Agents, audio recordings and backgrounds were adapted to each cultural setting.
-(C) Drawings used as agents across cultural settings.
-(D) Graphical illustration of the cognitive model.
-Individuals infer the target of an agent’s attention by estimating a vector based on the position of the pupils within the eyes.
-This process is noisy, illustrated by the different vectors (transparent lines).
-Individuals differ in their level of precision (indicated by sigma).
-For a given level of precision, the further the target lands from the centre of the screen, the less precise the model predicts individuals to be.
-Solid and transparent dots show simulated means and individual data points to illustrate the predicted effect of target position.", out.width="75%"}
-knitr::include_graphics("../figures/fig1.png")
+Agents, audio recordings and backgrounds were adapted to each community.
+(C) Drawings used as agents across communities.", out.width="100%"}
+knitr::include_graphics("../figures/fig1_2.png")
 ```
@@
   mutate(country = replace(country, duplicated(country), " "))%>%
-  mutate(language = c("Spanish (Rioplatense)", "Spanish (Mexican)", "English (American)", "Hai||om", "Khwedam", "English (Nigerian)2", "English (Nigerian)", "BaYaka", "Lingala", "Kiswahili", "Bemba", "German", "English (British)", "Mandarin", "English (Indian) / Marathi", "Turkish", "English (New Zealand)"))%>%
+  mutate(language = c("Spanish (Rioplatense)", "Spanish (Mexican)", "English (American)", "Hai||om", "Khwedam", "English (Nigerian)2", "English (Nigerian)", "Yaka", "Lingala", "Kiswahili", "Bemba", "German", "English (British)", "Mandarin", "English (Indian) / Marathi", "Turkish", "English (New Zealand)"))%>%
   select(continent, country, community, N, age, language, touchscreen)
@@
 apa_table(tba1,
-          col.names = linebreak(c("Continent", "Country", "Community", "N(male)", "Age (range)", "Language", "Touchscreen exposure1")),
+          col.names = linebreak(c("Continent", "Country", "Community", "N (male)", "Age (range)", "Language", "Touchscreen exposure1")),
           caption = "Participant demographics.",
-          #align = paste0("m{", 1/(ncol(tba1) + 1), "\\linewidth}"),
+          align = paste0("m{", 1/(ncol(tba1) + 1), "\\linewidth}"),
           longtable = TRUE,
@@
 \@ref(fig:fig1)B).
-The key dependent variable was the (im)precision with which children located the agent’s focus of attention, that is, the deviation between where the agent looked (where the object was) and the child’s response.
+The key dependent variable was the (im)precision with which children located the agent’s focus of attention, that is, the deviation between where the agent looked (where the balloon was) and the child’s response.
 We adapted visuals and audio instructions specifically for each of the 17 communities.
-Previous work demonstrated excellent individual-level measurement properties for this task in a German sample [@prein2023tango].
+Previous work demonstrated excellent individual-level measurement properties for this task in a German sample [@prein2024tango].
 
@@
 
+# Methods
+
+## Participants
+
+```{r}
+demtab <- data %>%
+  separate(community, into = c("community", "country"), sep = " \\(")%>%
+  mutate(country = str_remove(country, "\\("),
+         country = str_remove(country, "\\)"))%>%
+  distinct(subjid, .keep_all = T)%>%
+  group_by(community, country, continent)%>%
+  summarise(N = n_distinct(subjid), 
+            m = sum(sex == "m", na.rm = T), 
+            mean_age = mean(ageinyears),
+            min_age = min(ageinyears), 
+            max_age = max(ageinyears))%>%
+  mutate_if(is.numeric, format, digits = 2, nsmall = 2)%>%
+  mutate(age = paste(mean_age, " (", min_age, " - ", max_age, ")"))%>%
+  select(-c(mean_age, min_age, max_age))%>%
+  arrange(continent)
+```
+
+A total of `r sum(as.numeric(demtab$N))` children between `r round(min(data$ageinyears), 2)` and `r round(max(data$ageinyears), 2)` years of age provided data for the study.
+Children lived in `r n_distinct(data$community)` different communities, located in `r n_distinct(demtab$country)` different countries.
+Table \@ref(tab:tab1) gives the sample size per community together with some basic demographic information.
+The recruitment strategy for each community is reported in the respective site descriptions.
+For some children, the exact birthday was unknown.
+In such cases, we set the birthday to the 30th of June of the year that would make them fall into the reported age category.
+
+Data from children was only included in the study when they contributed at least four valid test trials.
+We also excluded the data from children with a diagnosed developmental disorder.
+In sum, in addition to the sample size reported above, 74 additional children participated in the study but did not contribute data.
+The main reasons for exclusion were: contribution of less than four valid test trials, technical failures, and missing or implausible demographic information (e.g., when the number of children living in the household was reported to be larger than the household itself or when the number of children reported to live in the household equaled the number of children younger than the child being tested).
+We did not exclude any participants for performance reasons.
+A detailed description of each data collection site and the way children were recruited can be found in the Supplementary Material.
+
+## Setup and Procedure
+
+The task was implemented as a browser-based interactive picture book using `HTML`, `CSS`, and `JavaScript`.
+Participants saw animated agents on a touch screen device, listened to pre-recorded audio instructions and responded by touching the screen.
+In all communities, a research assistant, fluent in the local language(s), guided the child through the task.
+
+Figure \@ref(fig:fig1)B shows a screenshot from the task.
+The task was introduced verbally by the assistant as the balloon game in which the participant would play with other children to find a balloon.
+On each trial, participants saw an agent located in a window in the center of the screen.
+A balloon fell down from its starting position just below the agent.
+The agent's gaze followed the trajectory of the balloon.
+That is, the pupils and the iris were programmed to align with the center of the balloon.
+Once the balloon had landed on the ground, the agent was instructed to locate it, that is, to touch the location on the screen where they thought the balloon was.
+On each trial, we recorded the exact x-coordinate of the participant's touch.
+
+There were two types of training trials.
+In training 1 trials, the balloon fell down and landed in plain sight.
+Participants simply had to touch the visible balloon.
+In training 2 trials, the trajectory of the balloon was visible but it landed behind a small barrier (a hedge -- see Figure \@ref(fig:fig1)B).
+Thus, participants needed to touch the hedge where they saw the balloon land.
+Next came test trials.
+Here, the barrier moved up and covered the balloon's trajectory.
+That is, participants only saw the agent's eyes move, but not the balloon.
+They had to infer the location of the balloon based on the agent's gaze direction.
+During training 1, training 2 and the first test trial, children heard voice-overs commenting what happened on the screen.
+Critically, the agent was described as wanting to help the child and always looking at the balloon.
+
+Children completed one training 1, two training 2 trials and 16 test trials.
+We excluded the first test trial from the analysis because of the voice-over.
+Thus, 15 test trials were used in the analysis below.
+Each child saw eight different agents (four male, four female).
+The agent changed from trial to trial, with alternating genders.
+A coin toss before the first trial decided whether the first agent was male or female.
+The order in which agents were shown was randomized with the constraint that all agents had to be shown once until an agent was shown again.
+The color of the balloon also changed from trial to trial in a random order, also with the constraint that all colors appeared once before any one was repeated.
+
+The location (x-coordinate) where the balloon landed was determined in the following way: The screen was divided in ten equally sized bins.
+On each trial, one of the bins was randomly selected and the exact x-coordinate was randomly chosen within that bin.
+Constraints were that the balloon landed in each bin equally often and the same bin appeared no more than twice in a row.
+
+All children were tested with a touchscreen device with a size between 11 and 13 inch equipped with a webcam.
+The data was either stored locally or sent to a server.
+In addition to the behavioral data, we stored the webcam recording of the session for verification purposes.
+Community-specific adaptations were made by changing the visuals and the audio instructions (see Supplementary Material for details).
+
+In addition to the gaze following task, caregivers responded to a short questionnaire about children’s access to screens and touchscreens (binary answer) as well as the number of people, children and children younger than the focal child living in the household (numeric; see Supplementary Material for details).
+The numeric variables were scaled within community prior to inclusion into the regression models.
+
+# Analysis
+
+## Regression models
+
+We used Bayesian Regression models fit in `R` [@r] using the package `brms` [@burkner2017brms] for all analyses except the cognitive models (see below).
+We used default priors built into `brms`.
+The dependent variable in all regression models was imprecision, that is, the absolute distance between the true location of the balloon (x-coordinate of its center) and the location where the participant touched the screen.
+We used a Log-normal distribution to model the data because the natural lower bound for imprecision is zero and the data was right skewed with a long tail.
+Numeric predictors that entered the models were scaled to have a mean of zero and a standard deviation of 1.
+
+To analyse cross-cultural variation in performance, we used a cross-validation procedure [see e.g., @stengelin2023children].
+In the Supplementary Material we give a detailed justification of this approach.
+For each community, we randomly sampled a data set that was 5/6 the size of the full data set (training data).
+Then, we fit the model to this training data and used the estimated model parameters to predict the remaining 1/6 of the data (testing data).
+We then compared the model predictions from the different models by computing the mean difference between the true and predicted imprecision, over all trials in the testing data set.
+We repeated the cross-validation procedure 100 times and computed the percentage of cases in which one model outperformed the other.
+We compared three models: a null model assuming no systematic community-level variation, a model assuming variation between communities and a model assuming variation between communities and in developmental trajectories (see Supplementary Material for model equations).
+
+To evaluate the processing signatures predicted by the cognitive model that trials in which the balloon lands further away from the center lead to larger imprecision (see next section for details), we fit a model predicting imprecision by age and target centrality (distance of the landing position from the center in pixel/SVG units) with random intercepts for participant and community and random slopes for target centrality within participant and community (`brms` notation: `age + target_centrality + (target_centrality | participant) + (age + target_centrality | community)`).
+
+## Cognitive model
+
+Recent computational work modeled gaze following as social vector estimation [@prein2024variation].
+When following gaze, onlookers observe the location of the pupil within the eye and estimate a vector emanating from the center of the eye through the pupil.
+The focus of attention is the location where the estimated vectors from both eyes hit a surface (Fig.
+\@ref(fig:fig12)).
+It is assumed that this estimation process has some uncertainty because the center of the eye is not directly observable and that individuals vary in their level of uncertainty.
+As a consequence, even though individuals use the same general process, they might differ in their absolute levels of precision.
+Crucially, this process model predicts a clear performance signature in the gaze following task: Trials in which the agent looks further away from the center should result in lower levels of precision compared to trials in which the agent looks closer to the center.
+This prediction is best understood by considering a similar phenomenon: pointing a torch light to a flat surface.
+The width of the light beam represents each individual’s level of uncertainty in vector estimation.
+When the torch is directed straight down, the light beam is concentrated in a relatively small area.
+When the torch is rotated to the side, the light from one half of the cone must travel further than the light from the other half to reach the surface.
+As a consequence, the light is spread over a wider area (see Fig.
+\@ref(fig:fig12)).
+
+The model inversely models the process generating touches on the screen based on observed eye movements and is defined as:
+
+\begin{equation}
+    P(\theta | x_c, \alpha_l, \alpha_r) \propto P(x_c | \alpha_l, \alpha_r, \theta)P(\theta)
+\end{equation}
+
+Here, $\theta$ represents an individual's cognitive ability to locate the focus of the agent's attention, $x_c$ represents the touched coordinate, and $\alpha_l$ and $\alpha_r$ correspond to the left and right pupil angles (each defined as the angle between a line connecting the center of the eye to the pupil and a line extended vertically downward from the center of the eye).
+
+The basic assumption in this model is that participants touch on the screen location where they think the agent is looking.
+The true eye angles ($\alpha_l$ and $\alpha_r$) are not directly observable and are estimated with noise, yielding $\hat{\alpha_l}$ and $\hat{\alpha_r}$.
+
+Each touch $x_c$ implies a "matched pair" of estimated pupil angles $\hat{\alpha_l}$ and $\hat{\alpha_r}$, with the constraint that the lines extended along those two angles meet at the precise location of where the target is believed to be.
+As a consequence, we can rewrite the likelihood function of the model as:
+
+\begin{equation}
+P(x_c | \alpha_l, \alpha_r, \theta) \propto P(\hat{\alpha_l}, \hat{\alpha_r} | \alpha_l, \alpha_r, \theta) P(x_c)
+\end{equation}
+
+$P(x_c)$ is a prior over potential target locations.
+Because the target was last visible in the screen and because the agent was located in the center, we assumed that participants have an a priori expectation that the target will land close to the middle.
+We estimated the strength of this center bias (*i.e.,* the standard deviation of a Normal distribution around the screen center) based on the data: $P(x_c) \sim \mathcal{N}(960, \sigma^p)$.
+
+The primary inferential task for participants is therefore to estimate the pupil angles ($\hat{\alpha_l}$ and $\hat{\alpha_r}$), that is, to sample from the term $P(\hat{\alpha_l}, \hat{\alpha_r} | \alpha_l, \alpha_r, \theta)$.
+Here, we assumed that the pair of estimated pupil angles were sampled from a probability distribution which is the product of two Normal distributions of equal variance, $\sigma_v$, centered on the true pupil angles:
+
+\begin{equation}
+P(\hat{\alpha_l}, \hat{\alpha_r} | \alpha_l, \alpha_r, \theta) \propto \phi(\hat{\alpha}_l ; \alpha_l, \sigma_v)\phi(\hat{\alpha}_r ; \alpha_r, \sigma_v),
+\end{equation}
+
+Here, $\sigma_v$ determines the level of accuracy with which participants estimated the pupil angles, and it is thus the component of the model that defines $\theta$.
+Smaller values of $\sigma_v$ result in a narrow distribution around the pupil angle, making touches far away from the target less likely.
+Conversely, larger values for $\sigma_v$ lead to a wider distribution, making touches far away from the target more likely.
+To circle back to the analogy introduced above, $\sigma_v$ corresponds to the width of the light beam.
+Thus, the goal of the model was to estimate participant-specific values for $\sigma_v$: $\sigma_{v_i}$.
+For more details on how $\sigma_{v_i}$ was estimated, see the Supplementary Material.
+
+To summarize, the model assumes that participant's touches are generated by a process that relies on noisy estimates of the agent's gaze direction.
+The precision, with which the gaze direction is estimated, varies between participants and increases with development.
+
+As stated above, the key signature prediction of the model is that precision decreases when the balloon lands further away from the center.
+This pattern, however, also arises when participants ignore the agent's gaze completely and instead follow simple heuristics.
+We implemented these heuristics as alternative models and directly compared them to the gaze estimation model.
+According to the center bias model, participants always try to touch in the center of the screen: $P(x_c) \sim \mathcal{N}(960, 160)$ (960 is the x-coordinate of the center and 160 is the width of the balloon).
+According to the random guessing model, they randomly touch coordinates on the screen: $P(x_c) \sim \mathcal{U}(0, 1920)$.
+
+The cognitive models were implemented in the probabilistic programming language `webppl` [@dippl].
+All models were run separately for each community.
+Information on the prior distributions for all model parameters can be found in the associated online repository.
+We compared models based on the marginal likelihood of the data for each model, which represents the likelihood of the data while averaging over the prior distribution on parameters.
+The pair-wise ratio of marginal likelihoods for two models is known as the Bayes Factor.
+Bayes Factors are a quantitative measure of the predictive quality of a model, taking into account the possible values of the model parameters weighted by their prior probabilities.
+The incorporation of the prior distribution over parameters in the averaging process implicitly considers model complexity: models with more parameters typically exhibit broader prior distributions over parameter values and broader prior distribution can attenuate the potential gains in predictive accuracy that a model with more parameters might otherwise achieve [@lee2014bayesian].
+
+# Results
+
+## Cross-cultural variation in development
+
 As the first step, we investigated developmental improvements, that is, how children become more precise at estimating the target location with age.
-Across all 17 communities, we found a substantial increase in average levels of precision with age (fixed effect in Bayesian regression model [@burkner2019bayesian]: $\beta$ = `r post_fix%>%filter(term == "ageinyears")%>%pull(Estimate)`, 95% HDI (`r post_fix%>%filter(term == "ageinyears")%>%pull(Q2.5)` - `r post_fix%>%filter(term == "ageinyears")%>%pull(Q97.5)`); range of community-level (random) effects: $\beta_{min}$ = `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%tail(1)%>%pull(mean)`, 95% HDI (`r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%tail(1)%>%pull(lci)` - `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%tail(1)%>%pull(uci)`) to $\beta_{max}$ = `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%head(1)%>%pull(mean)`, 95% HDI (`r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%head(1)%>%pull(lci)` - `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%head(1)%>%pull(uci)`).
+Across all 17 communities, we found a substantial increase in average levels of precision with age (fixed effect of age: $\beta$ = `r post_fix%>%filter(term == "ageinyears")%>%pull(Estimate)`, 95% Credible Interval (CrI) (`r post_fix%>%filter(term == "ageinyears")%>%pull(Q2.5)` — `r post_fix%>%filter(term == "ageinyears")%>%pull(Q97.5)`); range of community-level (random) effects: $\beta_{min}$ = `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%tail(1)%>%pull(mean)`, 95% CrI (`r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%tail(1)%>%pull(lci)` — `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%tail(1)%>%pull(uci)`) to $\beta_{max}$ = `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%head(1)%>%pull(mean)`, 95% CrI (`r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%head(1)%>%pull(lci)` — `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%head(1)%>%pull(uci)`)).
 
@@
 \@ref(fig:fig2)A).
-In a six-fold cross-validation procedure, we trained a regression model on a subset of the data (training data) to later predict the held-out data (testing data) [@stengelin2023children].
-This procedure was repeated 100 times.
-We found that a model assuming cross-cultural variation in average performance as well as cross-cultural variation in developmental trajectories outperformed simpler models – assuming no variation in the shape of developmental trajectories or nor variation between settings at all – in `r round(mean(cv_cult$m3_beats_m2),2)*100`% of cases (see Supplemental Material).
-There are numerous ways in which communities could be grouped that would fall in line with these absolute differences (e.g., market integration, average levels of education, or average household size).
-However, we deliberately want to avoid any such overly simplistic explanation.
-Instead, we think these results can be best understood in terms of exposure to touch-screen devices;; a finding we discuss in more detail below.
-Importantly, average differences in precision between communities were small compared to differences between individuals: communities did not form homogeneous clusters but largely overlapping distributions in that some individuals from communities with a lower average level of precision performed better compared to some individuals from a setting with a very high average level of precision.
+The cross-validation procedure found that a model assuming cross-cultural variation in average performance as well as cross-cultural variation in developmental trajectories outperformed simpler models -- assuming no variation in the shape of developmental trajectories or no variation between settings at all -- in `r round(mean(cv_cult$m3_beats_m2),2)*100`% of cases.
+
+Average differences in precision between communities were small compared to differences between individuals: communities did not form homogeneous clusters but largely overlapping distributions in that some individuals from communities with a lower average level of precision performed better compared to some individuals from a setting with a very high average level of precision.
 Similarly, in all communities, some 4-year-olds outperformed children two years older than them (see Fig.
@@
 The lack of adequate individual-level measurement instruments in previous large-scale developmental cross-cultural studies made it impossible to contrast these perspectives.
-The substantial overlap between communities found here speaks against categorical differences in gaze following and is suggestive of a universal underlying process.
-However, consistent developmental improvements alone cannot inform us about the cognitive processes children use when locating the agent’s focus of attention.
 
@@
 
-Recent computational work modeled gaze following as social vector estimation [@prein2023variation].
-When observing the eyes, onlookers estimate a vector emanating from the center of the eye that runs through the pupil.
-The focus of attention is the location where the estimated vectors from both eyes hit a surface (Fig.
-\@ref(fig:fig1)D).
-It is assumed that this estimation process has some uncertainty and that individuals vary in their level of uncertainty.
-As a consequence, even though individuals use the same general process, they might differ in their absolute levels of precision.
-Crucially, this process model predicts a clear performance signature in our gaze following task: Trials in which the agent looks further away from the center should result in lower levels of precision compared to trials in which the agent looks closer to the center.
-This prediction is best understood by considering a similar phenomenon: pointing a torch light to a flat surface.
-The width of the light beam represents each individual’s level of uncertainty in vector estimation.
-When the torch is directed straight down, the light beam is concentrated in a relatively small area.
-When the torch is rotated to the side, the light from one half of the cone must travel further than the light from the other half to reach the surface.
-As a consequence, the light is spread over a wider area (see Fig.
-\@ref(fig:fig1)D).
+## Universal processing signatures
 
-This processing signature was clearly visible across all 17 communities.
-Precision decreased when the agent looked at locations further away from the center (fixed effect: $\beta$ = `r post_fix%>%filter(term == "targetcentralityx")%>%pull(Estimate)`, 95% HDI (`r post_fix%>%filter(term == "targetcentralityx")%>%pull(Q2.5)` - `r post_fix%>%filter(term == "targetcentralityx")%>%pull(Q97.5)`); range of community-level effects: $\beta_{min}$ = `r post_agg%>%filter(type == "targetcentrality")%>%arrange(mean)%>%tail(1)%>%pull(mean)`, 95% HDI (`r post_agg%>%filter(type == "targetcentrality")%>%arrange(mean)%>%tail(1)%>%pull(lci)` - `r post_agg%>%filter(type == "targetcentrality")%>%arrange(mean)%>%tail(1)%>%pull(uci)`) to $\beta_{max}$ = `r post_agg%>%filter(type == "targetcentrality")%>%arrange(mean)%>%head(1)%>%pull(mean)`, 95% HDI (`r post_agg%>%filter(type == "targetcentrality")%>%arrange(mean)%>%head(1)%>%pull(lci)` - `r post_agg%>%filter(type == "targetcentrality")%>%arrange(mean)%>%head(1)%>%pull(uci)`).
+```{r fig12, include = T, fig.align = "center", fig.cap = "Graphical illustration of the cognitive model.
+Individuals infer the target of an agent’s attention by estimating a vector based on the position of the pupils within the eyes.
+This process is noisy, illustrated by the different vectors (transparent lines).
+Individuals differ in their level of precision (indicated by sigma).
+For a given level of precision, the further the target lands from the center of the screen, the less precise the model predicts individuals to be.
+Solid and transparent dots show simulated means and individual data points to illustrate the predicted effect of target position.", out.width="100%"}
+knitr::include_graphics("../figures/fig1_3.png")
+```
+
+The key processing signature predicted by the cognitive model was that precision should decrease when the balloon landed further away from the center.
+This signature was clearly visible across all 17 communities (fixed effect for target centrality: $\beta$ = `r post_fix%>%filter(term == "targetcentralityx")%>%pull(Estimate)`, 95% CrI (`r post_fix%>%filter(term == "targetcentralityx")%>%pull(Q2.5)` — `r post_fix%>%filter(term == "targetcentralityx")%>%pull(Q97.5)`); range of community-level (random) effects: $\beta_{min}$ = `r post_agg%>%filter(type == "targetcentrality")%>%arrange(mean)%>%tail(1)%>%pull(mean)`, 95% CrI (`r post_agg%>%filter(type == "targetcentrality")%>%arrange(mean)%>%tail(1)%>%pull(lci)` — `r post_agg%>%filter(type == "targetcentrality")%>%arrange(mean)%>%tail(1)%>%pull(uci)`) to $\beta_{max}$ = `r post_agg%>%filter(type == "targetcentrality")%>%arrange(mean)%>%head(1)%>%pull(mean)`, 95% CrI (`r post_agg%>%filter(type == "targetcentrality")%>%arrange(mean)%>%head(1)%>%pull(lci)` — `r post_agg%>%filter(type == "targetcentrality")%>%arrange(mean)%>%head(1)%>%pull(uci)`)).
 Visualization of the data showed the predicted u-shaped pattern in all communities (see Fig.
 \@ref(fig:fig2)B).
-These results indicate a universal cognitive process used by children in all communities.
-There are, however, alternative ways in which the u-shaped pattern might arise: if participants ignored the agent’s gaze and instead always selected the middle of the screen (center bias) or randomly selected locations (random guessing), precision would also decrease when the balloon lands further away from the center.
-To rule out these alternative explanations, we compared three cognitive models that made different assumptions about how participants’ responses were generated: the focal vector-based gaze estimation model described above, a center-bias model where participants always select the center, and a random guessing model where participants select random locations.
-For every community, we found overwhelming support for the gaze estimation model (min $BF_{10}$ > 100 000 for comparisons with both alternative models).
-Taken together, children from all 17 communities processed gaze in similar ways.
+When we compared the focal vector-based gaze estimation model described above to the alternative center bias and random guessing models, we found overwhelming support for the gaze estimation model (min $BF_{10}$ > 100 000 for comparisons with both alternative models, see Supplementary Materials) in every community.
 
@@
 
-Next, we looked at factors that could explain community- and individual-level variation.
-In addition to the gaze-following task, caregivers responded to a short questionnaire about children’s access to screen-based technology and household composition.
-On an individual level, we found that children with access to touchscreen devices had higher levels of precision ($\beta$ = `r pred_est%>%filter(term == "touchscreen")%>%pull(Estimate)`, SE = `r pred_est%>%filter(term == "touchscreen")%>%pull(Est.Error)`, 95% CrI = `r pred_est%>%filter(term == "touchscreen")%>%pull(Q2.5)` - `r pred_est%>%filter(term == "touchscreen")%>%pull(Q97.5)`).
-This effect was consistent across communities in that allowing the effect of access to touchscreens to vary across communities did not improve model fit (see Supplemental Materials).
-On a community level, we also saw that average performance was lowest in communities in which touchscreen devices were the least frequent (community-level correlation between age-corrected imprecision and proportion of children with access to touchscreens: *r* = `r round(pttest$estimate,2)`, 95% CI = `r round(pttest$conf.int[1],2)` - `r round(pttest$conf.int[2],2)`).
+## Predictors of variation
+
+We used the caregiver questionnaire to explain community- and individual-level variation.
+On an individual level, we found that children with access to touchscreen devices had higher levels of precision ($\beta$ = `r pred_est%>%filter(term == "touchscreen")%>%pull(Estimate)`, SE = `r pred_est%>%filter(term == "touchscreen")%>%pull(Est.Error)`, 95% CrI = `r pred_est%>%filter(term == "touchscreen")%>%pull(Q2.5)` — `r pred_est%>%filter(term == "touchscreen")%>%pull(Q97.5)`).
+This effect was consistent across communities in that allowing the effect of access to touchscreens to vary across communities did not improve model fit (see Supplementary Material).
+On a community level, we also saw that average performance was lowest in communities in which touchscreen devices were the least frequent (community-level correlation between age-corrected imprecision and proportion of children with access to touchscreens: *r* = `r round(pttest$estimate,2)`, 95% CI = `r round(pttest$conf.int[1],2)` — `r round(pttest$conf.int[2],2)`).
 Thus, familiarity with the device used for data collection likely explains variation between communities.
-The most likely explanation for this effect is that children with more touchscreen experience were better at task handling and thus more likely to precisely touch the location they inferred the agent to look at.
+Children with more touchscreen experience were probably better at task handling and thus more likely to precisely touch the location they inferred the agent to look at.
 
@@
 
-However, there was substantial variation between individuals that could not be explained by differential exposures to touch screens alone.
-For example, in Malatya (Türkyie) where 100% of children had access to touchscreens there was still substantial variation between individuals (see Fig.
-1B).
+However, there was substantial variation between individuals that could not be explained by differential exposures to touchscreens alone.
+For example, in Malatya (Türkiye) where 100% of children had access to touchscreens there was still substantial variation between individuals (see Fig.\@ref(fig:fig1)B).
 This strongly indicates that other factors likely contributed to individual differences.
 Social interaction has been highlighted as an important driver of social-cognitive development [e.g., @tomasello2019becoming; @carpendale2020makes; @barresi1996intentional; @perner1994theory; @rakoczy2022foundations] and thus we hypothesized (and pre-registered) that more opportunities for social interaction -- approximated by living in larger households with more children -- would be associated with higher levels of precision.
-When predicting performance by relative opportunities for social interactions within a community -- while accounting for absolute differences and the prevalence of touchscreens -- we found no strong associations between any of the demographic indicators and performance (see Supplemental Material).
-Whilst household size was a useful proxy for regular social interaction opportunities, the measure does not directly measure the factors that previous work has suggested to be related to the development of gaze following in younger children, such as attachment quality or the use of gaze in early communicative interactions [@astor2020social; @movellan2002development; @senju2015early].
-Future work could increase the resolution with which everyday experiences in children from diverse communities are recorded to compare the drivers behind social-cognitive development as we observe it.
-Recent work in the field of language acquisition has shown how technological innovations allowed for direct recording of social interactions across communities which can be used to close this explanatory gap [@bergelson2023everyday; @donnelly2021longitudinal].
+When predicting performance by relative opportunities for social interactions within a community -- while accounting for absolute differences and the prevalence of touchscreens -- we found no strong associations between any of the demographic indicators and performance (see Supplementary Material).
 
-Following and understanding gaze is a foundational building block of human social cognition [@tomasello2007reliance; @scaife1975capacity].
+# Discussion
+
+Following and understanding gaze is a foundational building block of human social cognition [@tomasello2007reliance; @scaife1975capacity; @langton2000eyes; @rossano2012gaze; @richardson2005looking; @sebanz2006joint].
 A substantial body of work has explored the developmental onset of gaze following in a few selected cultural communities [@moore2008development; @tang2023slow; @gredeback2010development; @byers2021development].
 The data reported here provides strong evidence that children from a large and diverse set of communities process others’ gaze in similar ways.
-We found key performance signatures of a model treating gaze following as a form of social vector estimation across all 17 communities.
-With the focus on individual-level processing signatures, the study goes beyond previous studies on gaze following – focused on the onset of gaze following in infancy [@hernik2019infant; @callaghan2011early] – as well as comprehensive cross-cultural studies that compared average developmental trajectories [@house2020universal; @van2018development; @blake2015ontogeny; @kanngiesser2022children].
+We found key performance signatures predicted by a model treating gaze following as a form of social vector estimation process across all 17 communities.
+With the focus on individual-level processing signatures, the study goes beyond previous studies on gaze following -- focused on the onset of gaze following in infancy [@hernik2019infant; @callaghan2011early] -- as well as comprehensive cross-cultural studies that compared average developmental trajectories [@house2020universal; @van2018development; @blake2015ontogeny; @kanngiesser2022children].
 
@@
 Our study combined precise individual-level cognitive measurement and individual-level assessment of experience (here: touchscreen exposure) in a large and diverse sample to directly investigate the impact of specific cultural experiences on developmental outcomes.
-Instead of establishing universality by maximizing the cultural distance between two or three tested communities [@norenzayan2005psychological], this large-scale cross-cultural approach treats children’s cultural experience at scale, shedding light on the big “middle ground” of children’s cultural experience [@barrett2020towards].
+Instead of establishing universality by maximizing the cultural distance between two or three tested communities [@norenzayan2005psychological], this large-scale cross-cultural approach treats children’s cultural experience at scale, shedding light on the big "middle ground" of children’s cultural experience [@barrett2020towards].
+
+The study has important limitations.
+The fact that performance in the task was correlated with exposure to touchscreens might have overshadowed other sources of variation.
+However, we think it is in an important innovation that we were able to account for this effect.
+Most developmental cross-cultural studies do not even question the portability of their measurement instruments.
+Importantly, the key result that the processing signatures were seen in all communities, is immune to this finding.
+The potential that lies in the otherwise precise individual-level measurement that the task achieves is largely unexploited.
+The questionnaire items only offer a very coarse picture into children's actual lived experiences.
+Whilst household size was a useful proxy for regular social interaction opportunities, the measure does not directly measure the factors that previous work has suggested to be related to the development of gaze following in younger children, such as attachment quality or the use of gaze in early communicative interactions [@astor2020social; @movellan2002development; @senju2015early].
+Future work could increase the resolution with which everyday experiences in children from diverse communities are recorded to compare the drivers behind social-cognitive development as we observe it.
+Recent work in the field of language acquisition has shown how technological innovations allowed for direct recording of social interactions across communities which can be used to close this explanatory gap [@bergelson2023everyday; @donnelly2021longitudinal].
 
@@
 As such, it can serve as a blueprint for future research on a broad spectrum of cognitive abilities and offers a much-needed empirical foundation for theories on the nature of the human mind.
-Children from diverse cultures deploy similar cognitive processes in interpreting gaze, pointing to a universal foundation of basic social cognition, which is refined during development.
+Children from diverse communities deploy similar cognitive processes in interpreting gaze, pointing to a universal foundation of basic social cognition, which is refined during development.
 

### 2024-10-13 paper/paper.Rmd
paper reformat step 1

@@
                             uganda = "Nyabyeya (Uganda)"))
+
+data%>%
+  mutate(side = ifelse(targetcenterx < 960, "left", "right"),
+         error = ifelse(clickdistfromtargetcenterx < 0, "left", "right"))%>%
+  group_by(side)%>%
+  summarise(left_bias = mean(error == "left"),
+            right_bias = mean(error == "right"))
+
 ```
-
-# Research Transparency Statement
-
-All authors declare no conflicts of interest.
-Preregistration: The hypotheses, methods and parts of the analysis plan were preregistered (<!-- https://osf.io/tdsvc/?view_only=f404d66c967542f28ce4af16371f34e6-->https://osf.io/tdsvc) on March 12th, 2022, prior to data collection which began on March 18th, 2022.
-Additional analysis and deviations from the preregistration are reported in the Supplementary Material.
-Materials: All study materials are publicly available <!--[masked for peer review] --> (https://ccp-odc.eva.mpg.de/tango-cc/).
-Data: All primary data are publicly available <!--[masked for peer review; see .zip file included--> (https://github.com/ccp-eva/gafo-cc-analysis/).
-Analysis scripts: All analysis scripts are publicly available <!--[masked for peer review; see .zip file included]--> (https://github.com/ccp-eva/gafo-cc-analysis/).
 
@@
 Human socio-cognitive skills enable unique forms of communication and cooperation that provide a bedrock for cumulative culture and the formation of complex societies [@tomasello2020adaptive; @laland2021understanding; @wellman2014making; @henrich2016secret; @tomasello2003makes; @legare2019development; @heyes2018cognitive].
-The eyes are the proverbial "window to the mind" and eye gaze is essential for many social reasoning processes  [@shepherd2010following; @doherty2006development; @emery2000eyes].
+The eyes are the proverbial "window to the mind" and eye gaze is essential for many social reasoning processes [@shepherd2010following; @doherty2006development; @emery2000eyes; @frischen2007gaze].
 Others’ eye gaze is used to infer their focus of visual attention, which is a critical aspect of coordinated activities, including communication and cooperation [@tomasello2007reliance; @scaife1975capacity; @langton2000eyes; @rossano2012gaze; @richardson2005looking; @sebanz2006joint].
+During ontogeny, gaze following is an important aspect of many critical learning objectives that enable children to become functioning members of the society they grow up in, including language, social learning and joint action [@brownell2011early; @moore2008development; @brooks2005development; @carpenter1998social; @mundy2007attention; @stephenson2021gaze].
+Because of the central role gaze following plays during human ontogeny, it has been widely argued that gaze following has been a target of natural selection [@tomasello2007reliance; @kano2023evolution; @emery2000eyes; @clark2023white].
+This implies that the process by which humans use gaze direction to infer the focus of attention is universal.
+In this paper, we report a comprehensive cross-cultural study on the ontogeny of gaze following in which we shed light on the universal aspects of gaze following as well as sources of variation and their origins.
+
+## Ontogeny of gaze following
 
@@
 The earliest signs of gaze following have been found in infants as young as four months [@astor2021gaze; @d1997demonstration].
-Initially, infants rely more on head direction than actual gaze direction [@michel2021effects; @lempers1977development].
-Throughout the first two years of life, children refine their abilities: they interpret gaze in mentalistic terms, for example, they follow gaze to locations outside their own visual field by moving around barriers [@moll200412].
-Importantly, individual differences in children’s gaze following abilities predict later life outcomes, most notably communicative abilities [@carpenter1998social].
-For example, gaze following at 10 months predicts language scores at 18 months of age [@brooks2005development].
-Difficulties with gaze following have been linked to developmental disorders, including Autism [@itier2009neural; @thorup2016altered; @thorup2018reduced].
-This work highlights the importance of gaze following as a foundational building block of human social interaction and its central place in theorizing.
+Throughout the first two years of life, children refine their abilities: they interpret gaze in mentalistic terms [@butterworth1991minds; @deak2000effects], for example, they follow gaze to locations outside their own visual field by moving around barriers [@moll200412].
+Initially, children rely more on head direction than actual gaze direction [@michel2021effects].
+In fact, when head and gaze direction diverge, children fail to accurately locate the agent's focus of attention up until 19 months of age [@lempers1979young].
 
-A central assumption in the theoretical and empirical work discussed above is that, despite substantial variation in developmental contexts, gaze following works and develops in the same way across human societies [@tomasello2019becoming].
-This assumption -- despite being central to many developmental theories -- is currently not supported by evidence.
-On the contrary, cross-cultural studies have revealed substantial diversity in socio-cognitive development [@miller2018contributions; @wellman2014making; @mayer2013synchrony; @dixson2018scaling; @taumoepeau2019cross].
-One of the very few cross-cultural studies also found differences in the likelihood to follow gaze between communities [@callaghan2011early].
+From an evolutionary perspective, while many species are able to follow gaze based on head directions, uniquely human forms of joint action and communication require a more precise localization of other's attention and thus critically rely on gaze direction inferred from eye movements [@emery2000eyes; @hessels2020does].
+In a recent study, @prein2024variation studied the development of gaze following based on eye movements across from three years up until old age.
+They found particularly steep developmental improvements in the preschool years resulting in a relatively stable level of accuracy from ten years onward and a slight decrease starting around age 40.
 
-One potential source for this paradox lies in the reliance on aggregated measures in cross-cultural studies.
-Absolute differences in mean performance across communities are interpreted as a signal of different underlying cognitive processes.
-In the present study, we resolve this paradox by instead focusing on processing signatures that can be investigated independently of absolute community-level differences.
-This allows us to directly evaluate the empirical foundation of claims about universal features of human social cognition.
-To this end, we conducted a pre-registered, large-scale, cross-cultural study on the development of gaze following abilities to study potentially universal processing signatures.
+The studies reported thus far, all relied on data collected in western affluent settings.
+Such settings represent only a minority of the worlds population and are thus insufficient to make claims about universal aspects of human cognition [@nielsen2017persistent; @norenzayan2005psychological; @amir2020cross].
+Three studies with infants and children from traditionally underrepresented parts of the world (Bhutan, India, Peru, Vanuatu) find that children start gaze following (including head direction) at similar ages, the rates of gaze following, however, differed between cultural settings [@hernik2019infant; @astor2022maternal; @callaghan2011early].
 
-The processing signatures were derived from a computational model that assumes that participants follow gaze by estimating a vector emanating from the eye center through the pupil [@prein2024variation].
-The key innovation of the model is that it explains how individuals may use the same cognitive process but still differ in their measured abilities.
+Rates and accuracy of gaze following do not just differ between cultural settings; there is also substantial variation within settings.
+In fact, the pivotal role of gaze following in many uniquely human activities has been studied by relating individual differences in gaze following to other phenomena -- both cross-sectionally and longitudinally [@carpenter1998social; @brooks2015connecting].
+For example, gaze following at 10 months predicts language scores at 18 months of age [@brooks2005development; see also @macdonald2013eye].
+Furthermore, difficulties with gaze following have been linked to developmental disorders, including Autism [@itier2009neural; @thorup2016altered; @thorup2018reduced] and -- at least in some cultural contexts -- to maternal postpartum depression [astor2022maternal].
+Individual differences are also key to explaining the -- mainly social-interactional -- driving forces behind the development of gaze following.
+For example, it has been found that early attachment quality or the use of gaze in communicative interactions predict later rates of gaze following [@astor2020social; @movellan2002development; @senju2015early].
+
+## Cognitive universals and sources of variation
+
+The existence of variation in gaze following both within and between cultural settings raises the question of how to square these findings with the suggestion that gaze following is a fundamental building block of human social cognition and interaction and that eye movements are processed the same way in humans all over the world.
+Looking at other aspects of social cognition, one could easily make the argument that variation is the norm rather than the exception [see e.g., @miller2018contributions; @wellman2014making; @mayer2013synchrony; @dixson2018scaling; @taumoepeau2019cross].
+As a first step, answering this question requires data from many different cultural settings.
+In a second step, however, we need to a way of detecting universal processes in such data.
+The traditional approach is to compare some sort of aggregate measure (mean level of performance, average age of onset) across cultural settings.
+Absolute differences in mean performance across communities are interpreted as a signal of different underlying cognitive processes [see e.g., @house2020universal; @van2018development; @blake2015ontogeny; @kanngiesser2022children].
+No differences seemingly support the existence of a psychological universal.
+Such an approach, however, neglects the existence of within-cultural variation altogether [see also @gurven2018broadening].
+
+In the present study, we want to take a different approach for which we assume that universal processes and variation can co-exist [@kline2018variation; @greenfield2003cultural; @jensen2012bridging].
+Instead of starting with the outcome (performance in the task), we start with the process that generates the outcome.
+By defining this process, we make a proposal for the universal aspect of the process.
+At the same time, we define variable aspects in the process that generate individual differences.
+This allows us to define signatures that the process leaves behind that can be detected independent of absolute levels of performance.
+
+For gaze following, we can use the computational model proposed by @prein2024variation to derive such predictions.
+They formalized the widely-held view that gaze following involves estimating a vector emanating from the eye center through the pupil [@todorovic2006geometrical; @yaniv1990heuristics; @butterworth1991minds; @symons2004you].
+The key innovation of the model is that it explains how individuals may use the same  process but still differ in their measured abilities.
 The process always involves estimating a vector but also involves a degree of uncertainty because the eye center is not directly observable.
@@
 Importantly, the assumed process leaves a key signature in the data that is observable independent of the absolute level of performance.
-In the present study, we therefore focus on this signature instead of absolute levels of performance when evaluating the claim whether there is evidence for a universal cognitive mechanism underlying gaze following.
+In the present study, we therefore focus on this signature instead of absolute levels of performance when evaluating the claim whether there is evidence for a universal cognitive process underlying gaze following.
 
-The `r n_distinct(data$subjid)` participants who took part in the study lived in 17 different communities across 14 countries and five continents (Fig.
-\@ref(fig:fig1)A, Tab.
-\@ref(tab:tab1)).
-These countries represent ~46% of the world’s population.
-Communities covered a broad spectrum of geographical locations, social and political systems, languages, and subsistence styles (see Supplementary Material).
-This diversity allowed us to overcome the common pitfall of cross-cultural studies that compare urban communities from the Global North to rural communities from the Global South [@barrett2020towards].
+## The current study
+
+The present study had three goals.
+First, to collect a comprehensive data set and study the ontogeny of gaze following beyond infancy across cultures.
+To make this possible, we used a semi-standardized task that required minimal assistance from an experimenter and no behavioral coding.
+The task is an animated picture book presented on a tablet screen.
+Children watched a balloon disappear behind a hedge.
+An agent followed the trajectory of the balloon with their eyes (Figure \@ref(fig:fig1)B).
+The key dependent variable was (im)precision, that is, the deviation between where the agent looked (where the balloon was) and the child’s response.
+The task's flexible implementation as a browser-based web-app allowed us to quickly tailor its visual and audio content to each cultural setting (visuals and audio).
+The task has been psychometrically evaluated and has shown to yield reliable individual-level measurements across communities and across ages [@prein2024tango; @prein2024measuring].
+
+We collected data in 17 different communities across 14 countries and five continents.
+Communities covered a broad spectrum of geographical locations, social and political systems, languages, and subsistence styles.
+This diversity allowed us to overcome a common pitfall of cross-cultural studies that compare urban communities from the Global North to rural communities from the Global South [@barrett2020towards].
+We aimed for large sample sizes within each community to contrast within- and between cultural variation.
+Our expectation regarding the first goal was to see substantial variation across cultures but even more variation between individuals.
+In all communities, we expected performance to increase with age.
+
+The second goals was to look for signatures in the data of the universal gaze following process predicted by the model of @prein2024measuring.
+In the task, the hidden object is located on a horizontal plane at the lower end of the screen.
+The agent is located in the upper center of the screen (see Figure \@ref(fig:fig1)B).
+The model predicts trials in which the object is hidden further away from the center to be more difficult resulting in higher imprecision.
+The signature is thus a u-shaped relation between object location and imprecision (Figure \@ref(fig:fig12)).
+
+Finally, we sought to explain individual differences in gaze following precision by linking them to methodological aspects of the study as well as aggregate measures of children's everyday social experience.
+Experience with tablets and touch screens co-varied with community and we expected children more familiar with this medium to perform better.
+Previous work suggested that gaze following is refined in social interaction [@movellan2002development; @senju2015early].
+To approximate social interaction, we asked parents to fill out a questionnaire about household size and composition.
+We acknowledge that this measure approximates opportunities for social interaction in a rather crude way but we nevertheless expected children living in larger households and with more siblings (relative to their community) to be more accurate when following gaze.
 
@@
 
+## Preregistration
+
+The study design, the sampling strategy and the general analytic strategy were preregistered prior to data collection (https://osf.io/tdsvc).
+The final sample size was not preregistered because we did not know how many communities would participate when the study began.
+Instead, we stated the age range we intended to study in each community (3.0 to 5.9 years of age) along and that we planned to test 20 children per year bin.
+We achieved this goal for most ages in most communities, but not for all (see Supplementary Table 1).
+The analysis reported here deviated from the preregistration in the following ways: In the pre-registration, in the regression models, we did not include random slopes for target centrality (i.e.
+the distance of the location where the balloon landed from the center of the screen), neither within subject nor within cultural setting.
+Instead, we included random slopes for trial within subject.
+We decided to change this and remove random slopes for trial but include them for target centrality because trial effects in the sense of learning across trials were unlikely because participants did not receive differential feedback.
+Furthermore, multiple studies with the same task since the registration found no trial effects [@prein2024tango; @prein2024variation].
+On the other hand, we included random slopes for target centrality to be able to look at cross-cultural variation.
+The cognitive models were not mentioned in the pre-registration because it is a more recent development [@prein2024variation].
+
+## Open data and materials
+
+All study materials <!--[masked for peer review] --> (https://ccp-odc.eva.mpg.de/tango-cc/), primary data and analysis scripts are publicly available <!--[masked for peer review; see .zip file included--> (https://github.com/ccp-eva/gafo-cc-analysis/).
+
 ## Participants
@@
 A total of `r sum(as.numeric(demtab$N))` children between `r round(min(data$ageinyears), 2)` and `r round(max(data$ageinyears), 2)` years of age provided data for the study.
-Children lived in `r n_distinct(data$community)` different communities, located in `r n_distinct(demtab$country)` different countries.
-Table \@ref(tab:tab1) gives the sample size per community together with some basic demographic information.
-The recruitment strategy for each community is reported in the respective site descriptions.
+Children lived in `r n_distinct(data$community)` different communities, located in `r n_distinct(demtab$country)` different countries across five continents.
+Table \@ref(tab:tab1) gives the sample size per community together with basic demographic information and age.
 For some children, the exact birthday was unknown.
 In such cases, we set the birthday to the 30th of June of the year that would make them fall into the reported age category.
+We provide a detailed description of the sample characteristics, the study site and recruitment strategy for each community in the Supplementary Material.
 
@@
 
-## Setup and Procedure
+## Material and Procedure
 
@@
 In all communities, a research assistant, fluent in the local language(s), guided the child through the task.
+That is, the research assistant guided the child through the introduction and advanced the study from trial to trial.
 
@@
 On each trial, one of the bins was randomly selected and the exact x-coordinate was randomly chosen within that bin.
-Constraints were that the balloon landed in each bin equally often and the same bin appeared no more than twice in a row.
+Constraints were that the balloon landed in each bin once in the first ten trials and, for the remaining six test trials, it landed in a different om each trial.
+Thus, each bin appeared a no more than twice.
 
@@
 In addition to the gaze following task, caregivers responded to a short questionnaire about children’s access to screens and touchscreens (binary answer) as well as the number of people, children and children younger than the focal child living in the household (numeric; see Supplementary Material for details).
-The numeric variables were scaled within community prior to inclusion into the regression models.
 
@@
 
-## Regression models
+## Cross-cultural variation
 
-We used Bayesian Regression models fit in `R` [@r] using the package `brms` [@burkner2017brms] for all analyses except the cognitive models (see below).
+We used Bayesian Regression models fit in `R` [@r] using the package `brms` [@burkner2017brms].
 We used default priors built into `brms`.
@@
 
-To analyse cross-cultural variation in performance, we used a cross-validation procedure [see e.g., @stengelin2023children].
-In the Supplementary Material we give a detailed justification of this approach.
-For each community, we randomly sampled a data set that was 5/6 the size of the full data set (training data).
+The first analysis was focused on cross-cultural variation.
+Fixed effects in the model were age and target centrality (distance of the landing position from the center in pixel/SVG units).
+The latter term accounts for trial difficulty.
+Furthermore, we included participant as a random effect, with a random slope for target centrality.
+To assess cross-cultural variation, we compared three models.
+A null model without cultural setting as a predictor (`brms` notation: `imprecision ~ age + target_centrality + (target_centrality | participant)`), a model with cultural setting as a random intercept (`imprecision ~ age + target_centrality + (target_centrality | participant) + (target_centrality | community)`) and a model with cultural setting as a random intercept and an added random slope for age (`imprecision ~ age + target_centrality + (target_centrality | participant) + (age + target_centrality | community)`).
+Thus, the second model assumes that there is variation across cultures in average levels of precision and the third model assumes that there are additional cultural differences in the effect of age.
+
+As stated in the pre-registration, comparing these models could be problematic.
+Participants are fully nested within cultural setting.
+If there was an effect of cultural setting, we would expect participant random intercepts to cluster by cultural setting.
+This clustering would appear whether or not cultural setting would be included in the model as a random effect or not -- the only difference would be if the participant random intercepts were estimated as a deviation from a grand intercept or a culture-specific one.
+Standard metrics such as `WAIC` or `LOO` would penalize the model with additional intercept for cultural setting for having additional parameters that do not help to improve predictive accuracy.
+
+To get around this problem, we used a cross-validation procedure (see e.g., 6).
+For each cultural setting, we randomly sampled a data set that was 5/6 the size of the full data set (training data).
 Then, we fit the model to this training data and used the estimated model parameters to predict the remaining 1/6 of the data (testing data).
 We then compared the model predictions from the different models by computing the mean difference between the true and predicted imprecision, over all trials in the testing data set.
-We repeated the cross-validation procedure 100 times and computed the percentage of cases in which one model outperformed the other.
-We compared three models: a null model assuming no systematic community-level variation, a model assuming variation between communities and a model assuming variation between communities and in developmental trajectories (see Supplementary Material for model equations).
+This approach gets around the problem mentioned above because the model predicts a new data set for which the individual random intercepts are unknown.
+Clustering by culture could therefore only be predicted by a model that included culture as a predictor.
+We repeated the cross-validation procedure 100 times and counted which model performed best most often.
 
-To evaluate the processing signatures predicted by the cognitive model that trials in which the balloon lands further away from the center lead to larger imprecision (see next section for details), we fit a model predicting imprecision by age and target centrality (distance of the landing position from the center in pixel/SVG units) with random intercepts for participant and community and random slopes for target centrality within participant and community (`brms` notation: `age + target_centrality + (target_centrality | participant) + (age + target_centrality | community)`).
+## Processing signatures
 
-## Cognitive model
-
-Recent computational work modeled gaze following as social vector estimation [@prein2024variation].
-When following gaze, onlookers observe the location of the pupil within the eye and estimate a vector emanating from the center of the eye through the pupil.
+The processing signatures were derived from the model proposed by [@prein2024variation].
+The model sees gaze following as social vector estimation.
+When following gaze, onlookers observe the location (and movement) of the pupil within the eye and estimate a vector emanating from the center of the eye through the pupil.
 The focus of attention is the location where the estimated vectors from both eyes hit a surface (Fig.
 \@ref(fig:fig12)).
-It is assumed that this estimation process has some uncertainty because the center of the eye is not directly observable and that individuals vary in their level of uncertainty.
+It is assumed that this estimation process is not perfect but has some uncertainty because the center of the eye is not directly observable.
+Individual differences are conceptualized as differences in the level of uncertainty.
 As a consequence, even though individuals use the same general process, they might differ in their absolute levels of precision.
-Crucially, this process model predicts a clear performance signature in the gaze following task: Trials in which the agent looks further away from the center should result in lower levels of precision compared to trials in which the agent looks closer to the center.
+
+The process model predicts a clear performance signature in the data: trials in which the agent looks further away from the center should result in lower levels of precision compared to trials in which the agent looks closer to the center.
 This prediction is best understood by considering a similar phenomenon: pointing a torch light to a flat surface.
@@
 
-The model inversely models the process generating touches on the screen based on observed eye movements and is defined as:
+In the following, we give a brief mathematical description of the model. The model inversely models the process generating touches on the screen based on observed eye movements and is defined as:
 
@@
 
-Here, $\theta$ represents an individual's cognitive ability to locate the focus of the agent's attention, $x_c$ represents the touched coordinate, and $\alpha_l$ and $\alpha_r$ correspond to the left and right pupil angles (each defined as the angle between a line connecting the center of the eye to the pupil and a line extended vertically downward from the center of the eye).
+Here, $\theta$ represents an individual's level of precision in locating the focus of the agent's attention, $x_c$ represents the touched coordinate, and $\alpha_l$ and $\alpha_r$ correspond to the left and right pupil angles (each defined as the angle between a line connecting the center of the eye to the pupil and a line extended vertically downward from the center of the eye).
 
@@
 $P(x_c)$ is a prior over potential target locations.
-Because the target was last visible in the screen and because the agent was located in the center, we assumed that participants have an a priori expectation that the target will land close to the middle.
-We estimated the strength of this center bias (*i.e.,* the standard deviation of a Normal distribution around the screen center) based on the data: $P(x_c) \sim \mathcal{N}(960, \sigma^p)$.
+Because the target was last visible in the screen and because the agent was located in the center, we assumed that participants have an a priori expectation that the target will land closer to the middle.
+We estimated the strength of this center bias (i.e., the standard deviation of a Normal distribution around the screen center) based on the data: $P(x_c) \sim \mathcal{N}(960, \sigma^p)$.
 
@@
 
-Here, $\sigma_v$ determines the level of accuracy with which participants estimated the pupil angles, and it is thus the component of the model that defines $\theta$.
+Thus, $\sigma_v$ determines the level of accuracy with which participants estimated the pupil angles, and it is thus the component of the model that defines $\theta$.
 Smaller values of $\sigma_v$ result in a narrow distribution around the pupil angle, making touches far away from the target less likely.
@@
 
-To summarize, the model assumes that participant's touches are generated by a process that relies on noisy estimates of the agent's gaze direction.
-The precision, with which the gaze direction is estimated, varies between participants and increases with development.
+As stated above, the key signature prediction of the model is that precision decreases when the balloon lands further away from the center.
+To test this prediction, we fit a model predicting imprecision by age and target centrality with random intercepts for participant and community and random slopes for target centrality within participant and community (`imprecision ~ age + target_centrality + (target_centrality | participant) + (age + target_centrality | community)`).
+As stated above, the predictor target centrality captures the distance from the center so that a positive effect of target centrality (i.e.
+a positive estimate with a 95% CrI not overlapping with zero) would mean support for the processing signature.
+In addition, we visualized the data for each community and inspected the shape of the plot.
 
-As stated above, the key signature prediction of the model is that precision decreases when the balloon lands further away from the center.
-This pattern, however, also arises when participants ignore the agent's gaze completely and instead follow simple heuristics.
-We implemented these heuristics as alternative models and directly compared them to the gaze estimation model.
-According to the center bias model, participants always try to touch in the center of the screen: $P(x_c) \sim \mathcal{N}(960, 160)$ (960 is the x-coordinate of the center and 160 is the width of the balloon).
-According to the random guessing model, they randomly touch coordinates on the screen: $P(x_c) \sim \mathcal{U}(0, 1920)$.
+The same pattern, however, also arises when participants ignore the agent's gaze completely and instead follow simple heuristics.
+When participants always touch the center of the screen, regardless of where the agent is looking, trials in which the balloon lands further away from the center have a higher imprecision.
+When participants randomly touch a location on the screen -- again ignoring the agent's gaze -- the maximum imprecision for trials in which the balloon lands in the center is half the width of the screen.
+When the balloon lands on one of the far ends of the screen, the maximum imprecision is a full screen widths.
+Thus, across trials, the average imprecision is again higher when the balloon lands further away from the center, resulting in the same pattern as predicted by the model.
 
-The cognitive models were implemented in the probabilistic programming language `webppl` [@dippl].
-All models were run separately for each community.
+Even though these alternatives are unlikely because they assume that participants ignore the agent's gaze, we nevertheless want to rule them out as processes generating the data.
+Thus, we implemented the gaze model along with the two alternative models in the probabilistic programming language `webppl` [@dippl].
+The way the gaze model predicts the participants behavior has been described above.
+The center bias model predicts a participant's touch by sampling from a Normal distribution around the center of the screen $P(x_c) \sim \mathcal{N}(960, 160)$ (960 is the x-coordinate of the center and 160 is the width of the balloon).
+The random guessing model predicts participant's touch by sampling from a uniform distribution over all possible locations: $P(x_c) \sim \mathcal{U}(0, 1920)$.
 Information on the prior distributions for all model parameters can be found in the associated online repository.
-We compared models based on the marginal likelihood of the data for each model, which represents the likelihood of the data while averaging over the prior distribution on parameters.
+
+For each community, we compared models based on the marginal likelihood of the data for each model, which represents the likelihood of the data while averaging over the prior distribution on parameters.
 The pair-wise ratio of marginal likelihoods for two models is known as the Bayes Factor.
@@
 
+## Predictors of variation
+
+The final analysis focused on whether we could predict performance in the task by methodological aspects of the study and aggregate measures of everyday social experience.
+For the ease of model fitting, we aggregated the data for each participant so that models predicted the average imprecision across trials.
+This approach is justified because the mean is nearly perfectly correlated with a model-based estimate of a participant's ability [$\sigma_v$ in the model above, see @prein2024variation] and because the predictor variables did not vary within child.
+
+In the questionnaire, we asked about children’s exposure to screens as well as touchscreens.
+These two variables were largely redundant and so we included only one of them in the model.
+We chose the availability of a touchscreen as a predictor because the task itself was presented on a touchscreen.
+
+For household composition, we asked for the total number of people in the household, the number of children and the number of younger children.
+We standardized each predictor within each community before fitting the models.
+Thus, the interpretation of the coefficient is the gain in precision for living e.g., in a larger household relative to other children from the same community.
+
+We compared a null model (`mean_imprecision ~ age + (age | community)`) to a model including access to touchscreens only as a fixed effect (`mean_imprecision ~ touchscreen + age + (age | culture)`), a model in which the effect of access to touchscreens was also allowed to vary by community (`mean_imprecision ~ touchscreen + age + (touchscreen + age | culture)`) and a model for each of the household-based predictors (e.g., `mean_imprecision ~ household_size + touchscreen + age + (age | culture)`).
+Models were fit in `brms` and compared based on the difference in expected log pointwise predictive density (`ELPD`) computed via the widely applicable information criterion (`WAIC`) and the standard error of that difference (SE).
+We inspected the estimates for fixed effects in the winning model along with their 95% CrI.
+
+For a community-level perspective, we correlated the proportion of children with access to touchscreens with an age-corrected performance average for each community.
+To obtain the latter, extracted the random intercept estimates for community from the null model described above.
+Because the model also includes age as a fixed effect, these values reflect variation between communities once differences in age have been accounted for.
+
 # Results
-
-## Cross-cultural variation in development
-
-As the first step, we investigated developmental improvements, that is, how children become more precise at estimating the target location with age.
-Across all 17 communities, we found a substantial increase in average levels of precision with age (fixed effect of age: $\beta$ = `r post_fix%>%filter(term == "ageinyears")%>%pull(Estimate)`, 95% Credible Interval (CrI) (`r post_fix%>%filter(term == "ageinyears")%>%pull(Q2.5)` — `r post_fix%>%filter(term == "ageinyears")%>%pull(Q97.5)`); range of community-level (random) effects: $\beta_{min}$ = `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%tail(1)%>%pull(mean)`, 95% CrI (`r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%tail(1)%>%pull(lci)` — `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%tail(1)%>%pull(uci)`) to $\beta_{max}$ = `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%head(1)%>%pull(mean)`, 95% CrI (`r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%head(1)%>%pull(lci)` — `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%head(1)%>%pull(uci)`)).
 
@@
 
-Nevertheless, there were also marked differences between communities (see Fig.
-\@ref(fig:fig2)A).
-The cross-validation procedure found that a model assuming cross-cultural variation in average performance as well as cross-cultural variation in developmental trajectories outperformed simpler models -- assuming no variation in the shape of developmental trajectories or no variation between settings at all -- in `r round(mean(cv_cult$m3_beats_m2),2)*100`% of cases.
+## Cross-cultural variation in development
 
-Average differences in precision between communities were small compared to differences between individuals: communities did not form homogeneous clusters but largely overlapping distributions in that some individuals from communities with a lower average level of precision performed better compared to some individuals from a setting with a very high average level of precision.
-Similarly, in all communities, some 4-year-olds outperformed children two years older than them (see Fig.
-\@ref(fig:fig2)A).
-The lack of adequate individual-level measurement instruments in previous large-scale developmental cross-cultural studies made it impossible to contrast these perspectives.
+There were marked differences between communities (see Figure \@ref(fig:fig2)A).
+The cross-validation procedure found that a model assuming cross-cultural variation in average performance as well as developmental trajectories outperformed simpler models in `r round(mean(cv_cult$m3_beats_m1),2)*100`% (no variation in developmental trajectories) and `r round(mean(cv_cult$m3_beats_m2),2)*100`% (no variation between communities at all) of cases, respectively.
+Nevertheless, average differences in precision between communities were small compared to differences between individuals: communities did not form homogeneous clusters but largely overlapping distributions in that some individuals from communities with a lower average level of precision performed better compared to some individuals from a setting with a very high average level of precision.
+Similarly, in all communities, some 4-year-olds outperformed children two years older than them (see Figure \@ref(fig:fig2)A).
 
-```{r fig2, include = T, fig.align = "center", fig.cap = "A) Developmental trajectory across and B) by community.
+Next, we investigated developmental gains, that is, the extent to which children become more precise at estimating the target location with age.
+Across all 17 communities, we found a substantial increase in average levels of precision with age (fixed effect of age: $\beta$ = `r post_fix%>%filter(term == "ageinyears")%>%pull(Estimate)`, 95% Credible Interval (CrI) (`r post_fix%>%filter(term == "ageinyears")%>%pull(Q2.5)` — `r post_fix%>%filter(term == "ageinyears")%>%pull(Q97.5)`); range of community-level (random) effects: $\beta_{min}$ = `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%tail(1)%>%pull(mean)`, 95% CrI (`r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%tail(1)%>%pull(lci)` — `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%tail(1)%>%pull(uci)`) to $\beta_{max}$ = `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%head(1)%>%pull(mean)`, 95% CrI (`r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%head(1)%>%pull(lci)` — `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%head(1)%>%pull(uci)`)).
+
+```{r fig2, include = T, fig.cap = "A) Developmental trajectory across and B) by community.
 The developmental trajectories are predicted based on a model of the data aggregated for each participant.
@@
 Each bin covers 1/10th of the screen.
-Points show means, and error bars 95% confidence intervals for the data within that bin aggregated across participants.
+Points show means, and error bars 95\\% confidence intervals for the data within that bin aggregated across participants.
 Transparent dots in A) and C) show aggregated data for each individual.", out.width="100%"}
@@
 
-## Universal processing signatures
+## Processing signatures
 
@@
 This signature was clearly visible across all 17 communities (fixed effect for target centrality: $\beta$ = `r post_fix%>%filter(term == "targetcentralityx")%>%pull(Estimate)`, 95% CrI (`r post_fix%>%filter(term == "targetcentralityx")%>%pull(Q2.5)` — `r post_fix%>%filter(term == "targetcentralityx")%>%pull(Q97.5)`); range of community-level (random) effects: $\beta_{min}$ = `r post_agg%>%filter(type == "targetcentrality")%>%arrange(mean)%>%tail(1)%>%pull(mean)`, 95% CrI (`r post_agg%>%filter(type == "targetcentrality")%>%arrange(mean)%>%tail(1)%>%pull(lci)` — `r post_agg%>%filter(type == "targetcentrality")%>%arrange(mean)%>%tail(1)%>%pull(uci)`) to $\beta_{max}$ = `r post_agg%>%filter(type == "targetcentrality")%>%arrange(mean)%>%head(1)%>%pull(mean)`, 95% CrI (`r post_agg%>%filter(type == "targetcentrality")%>%arrange(mean)%>%head(1)%>%pull(lci)` — `r post_agg%>%filter(type == "targetcentrality")%>%arrange(mean)%>%head(1)%>%pull(uci)`)).
-Visualization of the data showed the predicted u-shaped pattern in all communities (see Fig.
+
+Visualization of the data also showed the predicted u-shaped pattern in all communities (see Fig.
 \@ref(fig:fig2)B).
-When we compared the focal vector-based gaze estimation model described above to the alternative center bias and random guessing models, we found overwhelming support for the gaze estimation model (min $BF_{10}$ > 100 000 for comparisons with both alternative models, see Supplementary Materials) in every community.
+The visualization also showed that the u is not symmetric.
+Instead, imprecision seemed to be higher when the target lands on the left side of the screen.
+
+To rule out alternative explanations, we compared the focal vector-based gaze estimation model described above to the alternative center bias and random guessing models, we found overwhelming support for the gaze estimation model (min $BF_{10}$ > 100 000 for comparisons with both alternative models, see Supplementary Materials) in every community.
 
@@
 pred_est <- readRDS("../saves/pred_est.rds")
+
+pred_est_sc <- readRDS("../saves/pred_est_sc.rds")
 ```
@@
 
+```{r}
+pred_model_comp <- readRDS("../saves/model_comp.rds")%>%
+  mutate_if(is.numeric, format, digits = 2, nsmall = 2)%>%
+  select(model, elpd_diff, se_diff, waic, se_waic, value)%>%
+  mutate(model = recode(model, 
+                        bm_pred_null = "null",
+                        bm_pred_tc = "touchscreen",
+                        bm_pred_tc_hh = "household",
+                        bm_pred_tc_c = "children",
+                        bm_pred_tc_yc = "younger children",
+                        bm_pred_tc_rand = "touchscreen (by culture)"))
+```
+
 ## Predictors of variation
 
-We used the caregiver questionnaire to explain community- and individual-level variation.
-On an individual level, we found that children with access to touchscreen devices had higher levels of precision ($\beta$ = `r pred_est%>%filter(term == "touchscreen")%>%pull(Estimate)`, SE = `r pred_est%>%filter(term == "touchscreen")%>%pull(Est.Error)`, 95% CrI = `r pred_est%>%filter(term == "touchscreen")%>%pull(Q2.5)` — `r pred_est%>%filter(term == "touchscreen")%>%pull(Q97.5)`).
-This effect was consistent across communities in that allowing the effect of access to touchscreens to vary across communities did not improve model fit (see Supplementary Material).
-On a community level, we also saw that average performance was lowest in communities in which touchscreen devices were the least frequent (community-level correlation between age-corrected imprecision and proportion of children with access to touchscreens: *r* = `r round(pttest$estimate,2)`, 95% CI = `r round(pttest$conf.int[1],2)` — `r round(pttest$conf.int[2],2)`).
-Thus, familiarity with the device used for data collection likely explains variation between communities.
-Children with more touchscreen experience were probably better at task handling and thus more likely to precisely touch the location they inferred the agent to look at.
+```{r predcomptable, echo=F}
+pred_model_comp <- readRDS("../saves/model_comp.rds")%>%
+  mutate_if(is.numeric, format, digits = 2, nsmall = 2)%>%
+  select(model, elpd_diff, se_diff, waic, se_waic, value)%>%
+  mutate(model = recode(model, 
+                        bm_pred_null = "null",
+                        bm_pred_tc = "touchscreen",
+                        bm_pred_tc_hh = "touchscreen + household",
+                        bm_pred_tc_c = "touchscreen + children",
+                        bm_pred_tc_yc = "touchscreen + younger children",
+                        bm_pred_tc_rand = "touchscreen (by culture)"))
+
+kableExtra::kable(pred_model_comp,
+             col.names = c("Model","diff\\textsubscript{WAIC}", "diff\\textsubscript{SE}", "WAIC", "SE\\textsubscript{WAIC}", "Weight"),
+             caption = "comparison of models predicting individual-level variation.",
+             format="latex", booktabs=TRUE, escape = F
+             )
+
+```
+
+The model comparison favored the model including touchscreen as a fixed effect (no variation between communities) with no additional predictors capturing aspects of household composition (see Table \@ref(tab:predcomptable)).
+Children with access to touchscreen devices had higher levels of precision ($\beta$ = `r pred_est%>%filter(term == "touchscreen")%>%pull(Estimate)`, 95% CrI = `r pred_est%>%filter(term == "touchscreen")%>%pull(Q2.5)` — `r pred_est%>%filter(term == "touchscreen")%>%pull(Q97.5)`).
+This effect was consistent across communities in that allowing the effect of access to touchscreens to vary across communities did not improve model fit.
+
+On a community level, average performance was lowest in communities in which touchscreen devices were the least frequent (community-level correlation between age-corrected imprecision and proportion of children with access to touchscreens: *r* = `r round(pttest$estimate,2)`, 95% CI = `r round(pttest$conf.int[1],2)` — `r round(pttest$conf.int[2],2)`).
+
+Table \@ref(tab:predcomptable) shows that differences between models were small (`ELPD` < 1), suggesting that they were largely equivalent.
+For the sake of consistency, we also inspected the posterior estimates for household composition predictors, none of which had a 95% CrI excluding zero (household size: $\beta$ = `r pred_est_sc%>%filter(term == "household")%>%pull(Estimate)`, 95% CrI = `r pred_est_sc%>%filter(term == "household")%>%pull(Q2.5)` — `r pred_est_sc%>%filter(term == "household")%>%pull(Q97.5)`; children size: $\beta$ = `r pred_est_sc%>%filter(term == "children")%>%pull(Estimate)`, 95% CrI = `r pred_est_sc%>%filter(term == "children")%>%pull(Q2.5)` — `r pred_est_sc%>%filter(term == "children")%>%pull(Q97.5)`; younger children: $\beta$ = `r pred_est_sc%>%filter(term == "younger_children")%>%pull(Estimate)`, 95% CrI = `r pred_est_sc%>%filter(term == "younger_children")%>%pull(Q2.5)` — `r pred_est_sc%>%filter(term == "younger_children")%>%pull(Q97.5)`).
 
@@
 
-However, there was substantial variation between individuals that could not be explained by differential exposures to touchscreens alone.
-For example, in Malatya (Türkiye) where 100% of children had access to touchscreens there was still substantial variation between individuals (see Fig.\@ref(fig:fig1)B).
-This strongly indicates that other factors likely contributed to individual differences.
-Social interaction has been highlighted as an important driver of social-cognitive development [e.g., @tomasello2019becoming; @carpendale2020makes; @barresi1996intentional; @perner1994theory; @rakoczy2022foundations] and thus we hypothesized (and pre-registered) that more opportunities for social interaction -- approximated by living in larger households with more children -- would be associated with higher levels of precision.
-When predicting performance by relative opportunities for social interactions within a community -- while accounting for absolute differences and the prevalence of touchscreens -- we found no strong associations between any of the demographic indicators and performance (see Supplementary Material).
-
 # Discussion
@@
 With the focus on individual-level processing signatures, the study goes beyond previous studies on gaze following -- focused on the onset of gaze following in infancy [@hernik2019infant; @callaghan2011early] -- as well as comprehensive cross-cultural studies that compared average developmental trajectories [@house2020universal; @van2018development; @blake2015ontogeny; @kanngiesser2022children].
+
+Cultural settings are not homogeneous clusters but greatly overlap.
+
+alternative models not really alternative processes - motor noise model predicts no u-shaped pattern.
+
+The effect of touchscreen exposure wuggests that familiarity with the device used for data collection explains variation between communities.
+Children with more touchscreen experience were probably better at task handling and thus more likely to precisely touch the location they inferred the agent to look at.
+However, there was substantial variation between individuals that could not be explained by differential exposures to touchscreens alone.
+For example, in Malatya (Türkiye) where 100% of children had access to touchscreens there was still substantial variation between individuals (see Fig.\@ref(fig:fig1)B).
+This strongly indicates that other factors likely contributed to individual differences.
+
+Social interaction has been highlighted as an important driver of social-cognitive development [e.g., @tomasello2019becoming; @carpendale2020makes; @barresi1996intentional; @perner1994theory; @rakoczy2022foundations] and thus we hypothesized (and pre-registered) that more opportunities for social interaction -- approximated by living in larger households with more children -- would be associated with higher levels of precision.
+When predicting performance by relative opportunities for social interactions within a community -- while accounting for absolute differences and the prevalence of touchscreens -- we found no strong associations between any of the demographic indicators and performance (see Supplementary Material).
 

### 2024-10-16 paper/paper.Rmd
long version first draft

@@
 title             : "A universal of human social cognition: Children from 17 communities process gaze in similar ways"
-shorttitle        : "gaze following across 17 communities"
+shorttitle        : "Gaze following across 17 communities"
 
@@
 
-data%>%
-  mutate(side = ifelse(targetcenterx < 960, "left", "right"),
-         error = ifelse(clickdistfromtargetcenterx < 0, "left", "right"))%>%
-  group_by(side)%>%
-  summarise(left_bias = mean(error == "left"),
-            right_bias = mean(error == "right"))
-
 ```
@@
 Others’ eye gaze is used to infer their focus of visual attention, which is a critical aspect of coordinated activities, including communication and cooperation [@tomasello2007reliance; @scaife1975capacity; @langton2000eyes; @rossano2012gaze; @richardson2005looking; @sebanz2006joint].
-During ontogeny, gaze following is an important aspect of many critical learning objectives that enable children to become functioning members of the society they grow up in, including language, social learning and joint action [@brownell2011early; @moore2008development; @brooks2005development; @carpenter1998social; @mundy2007attention; @stephenson2021gaze].
+During ontogeny, gaze following is an important aspect of many critical learning objectives that enable children to become functioning members of the society they grow up in, including language, social learning and cooperation [@brownell2011early; @moore2008development; @brooks2005development; @carpenter1998social; @mundy2007attention; @stephenson2021gaze].
 Because of the central role gaze following plays during human ontogeny, it has been widely argued that gaze following has been a target of natural selection [@tomasello2007reliance; @kano2023evolution; @emery2000eyes; @clark2023white].
@@
 The earliest signs of gaze following have been found in infants as young as four months [@astor2021gaze; @d1997demonstration].
-Throughout the first two years of life, children refine their abilities: they interpret gaze in mentalistic terms [@butterworth1991minds; @deak2000effects], for example, they follow gaze to locations outside their own visual field by moving around barriers [@moll200412].
+Throughout the first two years of life, children refine their abilities: they begin to interpret gaze in mentalistic terms [@butterworth1991minds; @deak2000effects], for example, they follow gaze to locations outside their own visual field by moving around barriers [@moll200412].
 Initially, children rely more on head direction than actual gaze direction [@michel2021effects].
-In fact, when head and gaze direction diverge, children fail to accurately locate the agent's focus of attention up until 19 months of age [@lempers1979young].
+When head and gaze direction diverge, children often fail to accurately locate the agent's focus of attention up until 19 months of age [@lempers1979young].
 
 From an evolutionary perspective, while many species are able to follow gaze based on head directions, uniquely human forms of joint action and communication require a more precise localization of other's attention and thus critically rely on gaze direction inferred from eye movements [@emery2000eyes; @hessels2020does].
-In a recent study, @prein2024variation studied the development of gaze following based on eye movements across from three years up until old age.
+In a recent study, @prein2024variation studied the development of gaze following based on eye movements from three years up until old age.
 They found particularly steep developmental improvements in the preschool years resulting in a relatively stable level of accuracy from ten years onward and a slight decrease starting around age 40.
 
-The studies reported thus far, all relied on data collected in western affluent settings.
-Such settings represent only a minority of the worlds population and are thus insufficient to make claims about universal aspects of human cognition [@nielsen2017persistent; @norenzayan2005psychological; @amir2020cross].
-Three studies with infants and children from traditionally underrepresented parts of the world (Bhutan, India, Peru, Vanuatu) find that children start gaze following (including head direction) at similar ages, the rates of gaze following, however, differed between cultural settings [@hernik2019infant; @astor2022maternal; @callaghan2011early].
+The studies reported thus far, relied on data collected in western affluent settings.
+Such settings represent only a minority of the worlds population and are thus insufficient to make claims about universal aspects of human cognition [@nielsen2017persistent; @norenzayan2005psychological; @amir2020cross; @barrett2020towards].
+Three studies with infants and children from traditionally underrepresented parts of the world (Bhutan, India, Peru, Vanuatu) find that even though children start gaze following (gaze and head direction combined) at similar ages, the rates of gaze following differ between cultural settings [@hernik2019infant; @astor2022maternal; @callaghan2011early].
 
@@
 In fact, the pivotal role of gaze following in many uniquely human activities has been studied by relating individual differences in gaze following to other phenomena -- both cross-sectionally and longitudinally [@carpenter1998social; @brooks2015connecting].
-For example, gaze following at 10 months predicts language scores at 18 months of age [@brooks2005development; see also @macdonald2013eye].
+For example, gaze following at 10 months predicts language scores at 18 months of age [@brooks2005development; @macdonald2013eye].
 Furthermore, difficulties with gaze following have been linked to developmental disorders, including Autism [@itier2009neural; @thorup2016altered; @thorup2018reduced] and -- at least in some cultural contexts -- to maternal postpartum depression [astor2022maternal].
@@
 As a first step, answering this question requires data from many different cultural settings.
-In a second step, however, we need to a way of detecting universal processes in such data.
+In a second step, however, we need a way of detecting universal processes in such data.
 The traditional approach is to compare some sort of aggregate measure (mean level of performance, average age of onset) across cultural settings.
-Absolute differences in mean performance across communities are interpreted as a signal of different underlying cognitive processes [see e.g., @house2020universal; @van2018development; @blake2015ontogeny; @kanngiesser2022children].
-No differences seemingly support the existence of a psychological universal.
+Absolute differences between communities are interpreted as a signal of different underlying cognitive processes while no differences are taken to support the existence of a psychological universal [@house2020universal; @van2018development; @blake2015ontogeny; @kanngiesser2022children].
 Such an approach, however, neglects the existence of within-cultural variation altogether [see also @gurven2018broadening].
@@
 Instead of starting with the outcome (performance in the task), we start with the process that generates the outcome.
-By defining this process, we make a proposal for the universal aspect of the process.
-At the same time, we define variable aspects in the process that generate individual differences.
+By defining this process, we make a proposal for the universal aspects of the process.
+At the same time, we define variable aspects that generate individual differences.
 This allows us to define signatures that the process leaves behind that can be detected independent of absolute levels of performance.
@@
 For gaze following, we can use the computational model proposed by @prein2024variation to derive such predictions.
-They formalized the widely-held view that gaze following involves estimating a vector emanating from the eye center through the pupil [@todorovic2006geometrical; @yaniv1990heuristics; @butterworth1991minds; @symons2004you].
+They formalized the widely-held view that gaze following involves estimating some sort of vector emanating from the eye center through the pupil [@todorovic2006geometrical; @yaniv1990heuristics; @butterworth1991minds; @symons2004you].
 The key innovation of the model is that it explains how individuals may use the same process but still differ in their measured abilities.
@@
 Individuals are assumed to differ in their level of uncertainty with which they estimate the vector which causes differences in their observable behavior.
-Importantly, the assumed process leaves a key signature in the data that is observable independent of the absolute level of performance.
+Importantly, the general vector estimation process leaves a key signature in the data that is detectable independent of the absolute level of performance.
 In the present study, we therefore focus on this signature instead of absolute levels of performance when evaluating the claim whether there is evidence for a universal cognitive process underlying gaze following.
@@
 The task's flexible implementation as a browser-based web-app allowed us to quickly tailor its visual and audio content to each cultural setting (visuals and audio).
-The task has been psychometrically evaluated and has shown to yield reliable individual-level measurements across communities and across ages [@prein2024tango; @prein2024measuring].
+The task has been psychometrically evaluated and has shown to yield reliable individual-level measurements across communities and ages [@prein2024tango; @prein2024measuring].
 
@@
 Our expectation regarding the first goal was to see substantial variation across cultures but even more variation between individuals.
-In all communities, we expected performance to increase with age.
+In all communities, we expected performance to improve with age.
 
 The second goals was to look for signatures in the data of the universal gaze following process predicted by the model of @prein2024measuring.
-In the task, the hidden object is located on a horizontal plane at the lower end of the screen.
+In the task, the hidden object lands on a horizontal plane at the lower end of the screen.
 The agent is located in the upper center of the screen (see Figure \@ref(fig:fig1)B).
-The model predicts trials in which the object is hidden further away from the center to be more difficult resulting in higher imprecision.
+The model predicts that trials in which the object is hidden further away from the center to be more difficult, resulting in higher imprecision.
 The signature is thus a u-shaped relation between object location and imprecision (Figure \@ref(fig:fig12)).
@@
 To approximate social interaction, we asked parents to fill out a questionnaire about household size and composition.
-We acknowledge that this measure approximates opportunities for social interaction in a rather crude way but we nevertheless expected children living in larger households and with more siblings (relative to their community) to be more accurate when following gaze.
+We acknowledge that this measure approximates opportunities for social interaction in a rather coarse way but we nevertheless expected children living in larger households and with more siblings (relative to their community) to be more accurate when following gaze.
 
@@
 
+```{r}
+side_bias <- data%>%
+  mutate(side = ifelse(targetcenterx < 960, "left", "right"),
+         error = ifelse(clickdistfromtargetcenterx < 0, "left", "right"))%>%
+  group_by(side)%>%
+  summarise(left_bias = mean(error == "left"),
+            right_bias = mean(error == "right"))
+```
+
 Visualization of the data also showed the predicted u-shaped pattern in all communities (see Fig.
@@
 The visualization also showed that the u is not symmetric.
-Instead, imprecision seemed to be higher when the target lands on the left side of the screen.
+Instead, imprecision was higher when the target landed on the left side of the screen.
 
@@
 Following and understanding gaze is a foundational building block of human social cognition [@tomasello2007reliance; @scaife1975capacity; @langton2000eyes; @rossano2012gaze; @richardson2005looking; @sebanz2006joint].
-A substantial body of work has explored the developmental onset of gaze following in a few selected cultural communities [@moore2008development; @tang2023slow; @gredeback2010development; @byers2021development].
-The data reported here provides strong evidence that children from a large and diverse set of communities process others’ gaze in similar ways.
-We found key performance signatures predicted by a model treating gaze following as a form of social vector estimation process across all 17 communities.
-With the focus on individual-level processing signatures, the study goes beyond previous studies on gaze following -- focused on the onset of gaze following in infancy [@hernik2019infant; @callaghan2011early] -- as well as comprehensive cross-cultural studies that compared average developmental trajectories [@house2020universal; @van2018development; @blake2015ontogeny; @kanngiesser2022children].
+A substantial body of work has explored the developmental onset of gaze following in early infancy and in a few selected cultural communities [@moore2008development; @tang2023slow; @gredeback2010development; @byers2021development].
+The study reported here presents comparable data (i.e.
+collected via the same task with minimal superficial adjustments) on the development of gaze following in young children from 17 communities from five continents.
+We found substantial variation between cultural settings, both in average levels as well as the steepness of developmental trajectories.
+In that, however, individual-level variation greatly outweighed community-level variation.
+Despite this variation, we found evidence that the basic process of gaze following is the same across communities: we found key performance signatures predicted by a model conceptualizing gaze following as a form of social vector estimation in all communities.
+Individual-differences in gaze following were related to children's exposure to touchscreens but not to aggregate measures of opportunities for social interaction (i.e.
+household composition).
+This study provides evidence for a putative universal in basic social cognition and presents a new approach to studying cognitive processing in light of cross-cultural and individual variation.
 
-Cultural settings are not homogeneous clusters but greatly overlap.
+The task we used has good individual-level measurement properties across cultures [@prein2024measuring].
+This puts us in the position to contrast individual-level variability with community-level variability instead of dismissing the former as noise.
+The obvious pattern here was that cultural settings did not form homogeneous clusters but greatly overlapping distributions.
+That is, variation in the average developmental trajectories was small compared to variation between-individuals, both within communities and across them.
+Some individuals from the community with the highest average level of imprecision outperformed individuals from the community with the lowest average.
+Thus, the explanatory power of of community-level variables might be limited.
 
-alternative models not really alternative processes - motor noise model predicts no u-shaped pattern.
+On the face of it, a community-level perspective on the results points to a urban vs.
+rural divide in the data.
+Importantly, our sample included urban settings from the Global North and South so that geographic location and living conditions were only partly confounded (we did not collect data in rural settings in the Global North).
+Case in point is Namibia, where we collected data in both types of settings with results mirroring the overall pattern.
+In previous work, such differences were often attributed to specific community-level differences in everyday experience that come with urbanization [e.g., @amir2020developmental; @mavridis2020development].
+However, correlations identified this way remain speculative because urban and rural settings differ in a myriad of ways.
+Furthermore, this approach neglects within-community variation in everyday experience [@bohn2024understanding].
+It is often chosen because the measures used are not suited to reliably quantify individual-level variation.
+Given the good measurement properties of our task and the individual-level assessment via the parental questionnaire, we were able to directly link aspects of experience and cognitive development, omitting the intermediate community-level.
 
-The effect of touchscreen exposure wuggests that familiarity with the device used for data collection explains variation between communities.
+We investigated both methodological and household composition as potential predictors.
+Familiarity with the device used for data collection explained variation between communities.
 Children with more touchscreen experience were probably better at task handling and thus more likely to precisely touch the location they inferred the agent to look at.
-However, there was substantial variation between individuals that could not be explained by differential exposures to touchscreens alone.
-For example, in Malatya (Türkiye) where 100% of children had access to touchscreens there was still substantial variation between individuals (see Fig.\@ref(fig:fig1)B).
+Importantly, the model comparison showed that this relation did not vary substantially across communities.
+The effect, however, did not explain all variation between individuals.
+For example, in Malatya (Türkiye) where 100% of children had access to touchscreens there was still substantial variation between individuals.
 This strongly indicates that other factors likely contributed to individual differences.
 
-Social interaction has been highlighted as an important driver of social-cognitive development [e.g., @tomasello2019becoming; @carpendale2020makes; @barresi1996intentional; @perner1994theory; @rakoczy2022foundations] and thus we hypothesized (and pre-registered) that more opportunities for social interaction -- approximated by living in larger households with more children -- would be associated with higher levels of precision.
-When predicting performance by relative opportunities for social interactions within a community -- while accounting for absolute differences and the prevalence of touchscreens -- we found no strong associations between any of the demographic indicators and performance (see Supplementary Material).
+Social-interactional variables have been linked to the development of gaze following in previous work [@astor2020social; @movellan2002development; @senju2015early].
+Consequently, we predicted that opportunities for social interaction -- approximated by household size and composition -- would be linked to performance in the task while accounting for absolute differences and the prevalence of touchscreens.
+This was not the case.
+Yet, this result does not provide strong evidence for the absence of a relation between social-interactional variables and the development of gaze following, instead, we think it suggests that a more fine-grained approach is necessary to identify the relevant aspects of social interaction.
 
-The cognitive processes underlying gaze following might be rooted in humans’ evolved cognitive architecture, which is -- presumably -- later refined during social interaction [@astor2020social; @movellan2002development; @senju2015early].
+Despite substantial variation, we found the expected processing signatures in the data from all communities.
+Alternative accounts for how this pattern might have arisen did not explain the data well.
+However, these alternative approaches did not present viable alternative theoretical accounts for how participants followed gaze and why they differed from one another because they assumed that participants ignore gaze altogether.
+An alternative account involving the use of gaze cues would be that participants do not differ in the precision with which they estimate the gaze vector but that they differ only in the precision with which they touch the inferred location on the screen.
+This alternative -- motor noise -- account, however, would not predict the effect of target centrality and the u-shaped relation between target location and precision because motor noise should lead to normally distributed touches around the inferred location.
+Thus, we take the results as support for the idea of a universal process that is well-approximated by the model.
+This cognitive process might be rooted in humans’ evolved cognitive architecture, which is later refined during ontogeny.
 The phylogenetic roots of these processes might possibly lie much deeper as primates from a wide range of species follow gaze [@rosati2009looking; @tomasello1998five; @itakura2004gaze; @kano2014cross].
@@
 
-Our study combined precise individual-level cognitive measurement and individual-level assessment of experience (here: touchscreen exposure) in a large and diverse sample to directly investigate the impact of specific cultural experiences on developmental outcomes.
-Instead of establishing universality by maximizing the cultural distance between two or three tested communities [@norenzayan2005psychological], this large-scale cross-cultural approach treats children’s cultural experience at scale, shedding light on the big "middle ground" of children’s cultural experience [@barrett2020towards].
+An unexpected result was that imprecision was higher on the left compared to the right side of the screen.
+One candidate explanation for this pattern might be the dominance -- despite variation -- of right-handedness across cultures [@papadatou2020human].
+As of now, this is mere speculation and future research should investigate the origins of this pattern in more detail.
 
-The study has important limitations.
+The study has further limitations.
 The fact that performance in the task was correlated with exposure to touchscreens might have overshadowed other sources of variation.
@@
 Most developmental cross-cultural studies do not even question the portability of their measurement instruments.
-Importantly, the key result that the processing signatures were seen in all communities, is immune to this finding.
-The potential that lies in the otherwise precise individual-level measurement that the task achieves is largely unexploited.
-The questionnaire items only offer a very coarse picture into children's actual lived experiences.
-Whilst household size was a useful proxy for regular social interaction opportunities, the measure does not directly measure the factors that previous work has suggested to be related to the development of gaze following in younger children, such as attachment quality or the use of gaze in early communicative interactions [@astor2020social; @movellan2002development; @senju2015early].
+Importantly, the key result that the processing signatures were evident in all communities, is immune to this finding.
+The potential that lies in the precise individual-level measurement that our task achieves was largely unexploited.
+As mentioned above, the questionnaire items only offered a very coarse picture into children's actual lived experiences.
 Future work could increase the resolution with which everyday experiences in children from diverse communities are recorded to compare the drivers behind social-cognitive development as we observe it.
@@
 In sum, our work pioneers an approach that introduces computational modeling and precise individual-level measurement to the cross-cultural study of cognitive development.
-This approach allowed us to test for universals in the human cognitive architecture rather than just overt behavior.
-As such, it can serve as a blueprint for future research on a broad spectrum of cognitive abilities and offers a much-needed empirical foundation for theories on the nature of the human mind.
-Children from diverse communities deploy similar cognitive processes in interpreting gaze, pointing to a universal foundation of basic social cognition, which is refined during development.
+This approach allowed us to identify potential universals in the human cognitive architecture rather than just overt behavior.
+As such, it can serve as a blueprint for future research on a broad spectrum of cognitive abilities.
+Finally, the study provides a much-needed empirical foundation for theories on the nature of the human mind.
+Children from diverse communities deploy similar cognitive processes in interpreting gaze, pointing to a universal foundation of basic social cognition.
 

### 2024-10-16 paper/paper.tex
long version first draft

--- 2024-01-29 paper/paper.tex
@@
 \documentclass[
-  man,floatsintext]{apa6}
+  man,floatsintext]{apa7}
 \usepackage{amsmath,amssymb}
@@
 {}{\PatchFailed}
-\keywords{keywords\newline\indent Word count: X}
 \usepackage{lineno}
@@
 \usepackage{csquotes}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{unicode-math}
+\usepackage{setspace}
+\usepackage{libertine}
+\captionsetup[figure]{font={stretch=1}}
+\makeatletter
+\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-1em}%
+  {\normalfont\normalsize\bfseries\typesectitle}}
+
+\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-\z@\relax}%
+  {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+\makeatother
 \ifLuaTeX
@@
 \hypersetup{
-  pdftitle={Unity in diversity: Children from 17 diverse communities process gaze in similar ways},
-  pdfauthor={Manuel Bohn1,2, Julia Prein1,2, \ldots\ldots, \& Daniel B. M. Haun2},
+  pdftitle={A universal of human social cognition: Children from 17 communities process gaze in similar ways},
+  pdfauthor={Manuel Bohn1,2,*, Julia Christin Prein1,2,*, Agnes Ayikoru3, Florian M.
+Bednarski4, Ardain Dzabatou5, Michael C.
+Frank6, Annette M.
+E.
+Henderson4, Joan Isabella3, Josefine Kalbitz2, Patricia Kanngiesser7, Dilara Keşşafoğlu8, Bahar Köymen9, Maira V.
+Manrique-Hernandez2, Shirley Magazi10, Lizbeth Mújica-Manrique2, Julia Ohlendorf2, Damilola Olaoba2, Wesley R.
+Pieters10, Sarah Pope-Caldwell2, Katie Slocombe11, Robert Z.
+Sparks6, Jahnavi Sunderarajan2, Wilson Vieira2, Zhen Zhang12, Yufei Zong12, Roman Stengelin2,10,+, \& Daniel B.
+M.
+Haun2,+},
   pdflang={en-EN},
-  pdfkeywords={keywords},
   hidelinks,
@@
 
-\title{Unity in diversity: Children from 17 diverse communities process gaze in similar ways}
-\author{Manuel Bohn\textsuperscript{1,2}, Julia Prein\textsuperscript{1,2}, \ldots{}\textsuperscript{\ldots{}}, \& Daniel B. M. Haun\textsuperscript{2}}
+\title{A universal of human social cognition: Children from 17 communities process gaze in similar ways}
+\author{Manuel Bohn\textsuperscript{1,2,*}, Julia Christin Prein\textsuperscript{1,2,*}, Agnes Ayikoru\textsuperscript{3}, Florian M.
+Bednarski\textsuperscript{4}, Ardain Dzabatou\textsuperscript{5}, Michael C.
+Frank\textsuperscript{6}, Annette M.
+E.
+Henderson\textsuperscript{4}, Joan Isabella\textsuperscript{3}, Josefine Kalbitz\textsuperscript{2}, Patricia Kanngiesser\textsuperscript{7}, Dilara Keşşafoğlu\textsuperscript{8}, Bahar Köymen\textsuperscript{9}, Maira V.
+Manrique-Hernandez\textsuperscript{2}, Shirley Magazi\textsuperscript{10}, Lizbeth Mújica-Manrique\textsuperscript{2}, Julia Ohlendorf\textsuperscript{2}, Damilola Olaoba\textsuperscript{2}, Wesley R.
+Pieters\textsuperscript{10}, Sarah Pope-Caldwell\textsuperscript{2}, Katie Slocombe\textsuperscript{11}, Robert Z.
+Sparks\textsuperscript{6}, Jahnavi Sunderarajan\textsuperscript{2}, Wilson Vieira\textsuperscript{2}, Zhen Zhang\textsuperscript{12}, Yufei Zong\textsuperscript{12}, Roman Stengelin\textsuperscript{2,10,+}, \& Daniel B.
+M.
+Haun\textsuperscript{2,+}}
 \date{}
 
-\shorttitle{Gaze-following across 17 communities}
+\shorttitle{Gaze following across 17 communities}
 
@@
 
-Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-Enter author note here.
+The authors would like to thank Luke Maurits for statistical advice.
+Manuel Bohn was supported by a Jacobs Foundation Research Fellowship (2022-1484-00).
+We are grateful to thank all children and caregivers for participating in the study.
+We thank the Max Planck Society for the Advancement of Science.
 
 The authors made the following contributions.
-Manuel Bohn: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Julia Prein: Conceptualization, Methodology, Writing - Review \& Editing; \ldots{}: Conceptualization, Methodology, Writing - Review \& Editing; Daniel B.
+Manuel Bohn: Conceptualization, Methodology, Formal Analysis, Writing - Original Draft Preparation, Writing - Review \& Editing; Julia Christin Prein: Conceptualization, Methodology, Software, Investigation, Writing - Review \& Editing; Agnes Ayikoru: Investigation; Florian M.
+Bednarski: Investigation, Writing - Review \& Editing; Ardain Dzabatou: Investigation; Michael C.
+Frank: Investigation, Writing - Review \& Editing; Annette M.
+E.
+Henderson: Investigation, Writing - Review \& Editing; Joan Isabella: Investigation; Josefine Kalbitz: Investigation, Writing - Review \& Editing; Patricia Kanngiesser: Investigation, Writing - Review \& Editing; Dilara Keşşafoğlu: Investigation, Writing - Review \& Editing; Bahar Köymen: Investigation, Writing - Review \& Editing; Maira V.
+Manrique-Hernandez: Investigation; Shirley Magazi: Investigation; Lizbeth Mújica-Manrique: Investigation, Writing - Review \& Editing; Julia Ohlendorf: Investigation; Damilola Olaoba: Investigation; Wesley R.
+Pieters: Investigation, Writing - Review \& Editing; Sarah Pope-Caldwell: Investigation; Katie Slocombe: Investigation, Writing - Review \& Editing; Robert Z.
+Sparks: Investigation; Jahnavi Sunderarajan: Investigation; Wilson Vieira: Investigation; Zhen Zhang: Investigation, Writing - Review \& Editing; Yufei Zong: Investigation; Roman Stengelin: Conceptualization, Methodology, Investigation, Writing - Review \& Editing; Daniel B.
 M.
-Haun: Conceptualization, Writing - Review \& Editing.
+Haun: Conceptualization, Funding acquisition, Writing - Review \& Editing.
 
-Correspondence concerning this article should be addressed to Manuel Bohn, Postal address. E-mail: \href{mailto:my@email.com}{\nolinkurl{my@email.com}}
+Correspondence concerning this article should be addressed to Manuel Bohn, Universitätsallee 1, 21335 Lüneburg, Germany.
+E-mail: \href{mailto:manuel.bohn@leuphana.de}{\nolinkurl{manuel.bohn@leuphana.de}}
 
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute of Psychology in Education, Leuphana University Lüneburg\\\textsuperscript{2} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute of Psychology in Education, Leuphana University Lüneburg\\\textsuperscript{2} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology\\\textsuperscript{3} Budongo Conservation Field Station\\\textsuperscript{4} School of Psychology, University of Auckland\\\textsuperscript{5} Université Marien Ngouabi\\\textsuperscript{6} Department of Psychology, Stanford University\\\textsuperscript{7} School of Psychology, University of Plymouth\\\textsuperscript{8} Department of Psychology, Koç University\\\textsuperscript{9} Division of Psychology, Communication, and Human Neuroscience, University of Manchester\\\textsuperscript{10} Department of Psychology and Social Work, University of Namibia\\\textsuperscript{11} Department of Psychology, University of York\\\textsuperscript{12} CAS Key Laboratory of Behavioral Science, Institute of Psychology, Chinese Academy of Sciences\\\textsuperscript{*} joint first author\\\textsuperscript{+} joint last author}
 
 \abstract{%
-Understanding gaze is critical for human social interaction.
-In a comprehensive cross-cultural study spanning five continents and 17 distinct cultural contexts, we examined the development of gaze understanding among preschoolers using a single reliable task tailored to each cultural setting.
-Our data provides evidence that children worldwide process gaze in the same way.
-Key performance signatures of a computational model that sees gaze following as a form of social vector estimation were found in all communities.
-Additionally, we found a subtle yet cross-culturally consistent relationship between children's environments and their ability to understand gaze.
-These results highlight the cross-cultural robustness of core social cognitive skills, as well as similarities in the developmental process, suggesting that fundamental aspects of social cognition and interaction emerge and develop in comparable ways globally and hence are a bedrock of human social cognition.
+Theoretical accounts assume that key features of human social cognition are universal.
+Here we focus on gaze following, the bedrock of social interactions and coordinated activities, to test this claim.
+In a comprehensive cross-cultural study spanning five continents and 17 distinct cultural communities, we examined the development of gaze following in early childhood.
+We identified key processing signatures through a computational model that assumes that participants follow an individual's gaze by estimating a vector emanating from the eye center through the pupil.
+We found these signatures in all communities, suggesting that children worldwide processed gaze in highly similar ways.
+Absolute differences between groups were accounted for by a cross-culturally consistent relationship between children's exposure to touchscreens and their performance in the task.
+These results provide strong evidence for a universal process underlying a foundational socio-cognitive ability in humans that can be reliably inferred even in the presence of cultural variation in overt behavior.
 }
@@
 
-Social cognition is a defining aspect of the human species (\emph{1}--\emph{3}).
-It is supposed to enable unique forms of communication and cooperation that underlie cumulative cultural evolution and the formation of complex societies (\emph{4}--\emph{6}).
-The eyes are the proverbial window to the mind and the starting point for a majority of social reasoning processes (\emph{7}).
-Gaze is used to infer the focus of visual attention, which is a critical aspect of coordinated activities, including communication and cooperation (\emph{8}, \emph{9}).
-The ability to follow gaze emerges early in childhood (\emph{10}--\emph{12}) and individual differences in children's gaze following ability predict later life outcomes, most notably, later communicative abilities (\emph{13}, \emph{14}).
-Underlying this narrative is the wide-held assumption that gaze following is fundamental to human social cognition and, therefore, works and develops in the same way across human societies despite substantial variation in developmental contexts.
-This claim, however, lacks a solid empirical foundation.
+\begin{verbatim}
+## # A tibble: 2 x 3
+##   side  left_bias right_bias
+##   <chr>     <dbl>      <dbl>
+## 1 left      0.170      0.830
+## 2 right     0.754      0.246
+\end{verbatim}
 
-We conducted a large-scale cross-cultural study on the development of gaze-following abilities to study potentially universal processing signatures and their development.
-Previous developmental studies focused on the onset of gaze following in infancy (\emph{15}, \emph{16}).
-The 1311 participants in the study lived in 17 different communities spread over five continents (Fig.
-\ref{fig:fig1}A, Tab.
-\ref{tab:tab1}).
-The countries from which data was contributed to the study represented 46 \% of the world's population.
-Communities covered a broad spectrum of geographical locations, social and political systems, languages, and subsistence styles (see Supplemental Materials).
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
+
+Human socio-cognitive skills enable unique forms of communication and cooperation that provide a bedrock for cumulative culture and the formation of complex societies (Henrich, 2016; Heyes, 2018; Laland \& Seed, 2021; Legare, 2019; Tomasello, 2020; Tomasello \& Rakoczy, 2003; Wellman, 2014).
+The eyes are the proverbial ``window to the mind'' and eye gaze is essential for many social reasoning processes (Doherty, 2006; Emery, 2000; Frischen et al., 2007; Shepherd, 2010).
+Others' eye gaze is used to infer their focus of visual attention, which is a critical aspect of coordinated activities, including communication and cooperation (Langton et al., 2000; Richardson \& Dale, 2005; Rossano, 2012; Scaife \& Bruner, 1975; Sebanz et al., 2006; Tomasello et al., 2007).
+During ontogeny, gaze following is an important aspect of many critical learning objectives that enable children to become functioning members of the society they grow up in, including language, social learning and joint action (Brooks \& Meltzoff, 2005; Brownell, 2011; Carpenter et al., 1998; Moore, 2008; Mundy \& Newell, 2007; Stephenson et al., 2021).
+Because of the central role gaze following plays during human ontogeny, it has been widely argued that gaze following has been a target of natural selection (Clark et al., 2023; Emery, 2000; Kano, 2023; Tomasello et al., 2007).
+This implies that the process by which humans use gaze direction to infer the focus of attention is universal.
+In this paper, we report a comprehensive cross-cultural study on the ontogeny of gaze following in which we shed light on the universal aspects of gaze following as well as sources of variation and their origins.
+
+\hypertarget{ontogeny-of-gaze-following}{%
+\subsection{Ontogeny of gaze following}\label{ontogeny-of-gaze-following}}
+
+The ability to follow gaze emerges early in development (Byers-Heinlein et al., 2021; Del Bianco et al., 2019; Gredebäck et al., 2010; Tang et al., 2023).
+The earliest signs of gaze following have been found in infants as young as four months (Astor et al., 2021; D'Entremont et al., 1997).
+Throughout the first two years of life, children refine their abilities: they interpret gaze in mentalistic terms (Butterworth \& Jarrett, 1991; Deák et al., 2000), for example, they follow gaze to locations outside their own visual field by moving around barriers (Moll \& Tomasello, 2004).
+Initially, children rely more on head direction than actual gaze direction (Michel et al., 2021).
+In fact, when head and gaze direction diverge, children fail to accurately locate the agent's focus of attention up until 19 months of age (Lempers, 1979).
+
+From an evolutionary perspective, while many species are able to follow gaze based on head directions, uniquely human forms of joint action and communication require a more precise localization of other's attention and thus critically rely on gaze direction inferred from eye movements (Emery, 2000; Hessels, 2020).
+In a recent study, Prein, Maurits, et al.
+(2024) studied the development of gaze following based on eye movements across from three years up until old age.
+They found particularly steep developmental improvements in the preschool years resulting in a relatively stable level of accuracy from ten years onward and a slight decrease starting around age 40.
+
+The studies reported thus far, all relied on data collected in western affluent settings.
+Such settings represent only a minority of the worlds population and are thus insufficient to make claims about universal aspects of human cognition (Amir \& McAuliffe, 2020; Nielsen et al., 2017; Norenzayan \& Heine, 2005).
+Three studies with infants and children from traditionally underrepresented parts of the world (Bhutan, India, Peru, Vanuatu) find that children start gaze following (including head direction) at similar ages, the rates of gaze following, however, differed between cultural settings (Astor et al., 2022; Callaghan et al., 2011; Hernik \& Broesch, 2019).
+
+Rates and accuracy of gaze following do not just differ between cultural settings; there is also substantial variation within settings.
+In fact, the pivotal role of gaze following in many uniquely human activities has been studied by relating individual differences in gaze following to other phenomena -- both cross-sectionally and longitudinally (Brooks \& Meltzoff, 2015; Carpenter et al., 1998).
+For example, gaze following at 10 months predicts language scores at 18 months of age (Brooks \& Meltzoff, 2005; see also Macdonald \& Tatler, 2013).
+Furthermore, difficulties with gaze following have been linked to developmental disorders, including Autism (Itier \& Batty, 2009; Thorup et al., 2016, 2018) and -- at least in some cultural contexts -- to maternal postpartum depression {[}astor2022maternal{]}.
+Individual differences are also key to explaining the -- mainly social-interactional -- driving forces behind the development of gaze following.
+For example, it has been found that early attachment quality or the use of gaze in communicative interactions predict later rates of gaze following (Astor et al., 2020; Movellan \& Watson, 2002; Senju et al., 2015).
+
+\hypertarget{cognitive-universals-and-sources-of-variation}{%
+\subsection{Cognitive universals and sources of variation}\label{cognitive-universals-and-sources-of-variation}}
+
+The existence of variation in gaze following both within and between cultural settings raises the question of how to square these findings with the suggestion that gaze following is a fundamental building block of human social cognition and interaction and that eye movements are processed the same way in humans all over the world.
+Looking at other aspects of social cognition, one could easily make the argument that variation is the norm rather than the exception (Dixson et al., 2018; Mayer \& Träuble, 2013; see e.g., Miller et al., 2018; Taumoepeau et al., 2019; Wellman, 2014).
+As a first step, answering this question requires data from many different cultural settings.
+In a second step, however, we need to a way of detecting universal processes in such data.
+The traditional approach is to compare some sort of aggregate measure (mean level of performance, average age of onset) across cultural settings.
+Absolute differences in mean performance across communities are interpreted as a signal of different underlying cognitive processes (Blake et al., 2015; see e.g., House et al., 2020; Kanngiesser et al., 2022; Van Leeuwen et al., 2018).
+No differences seemingly support the existence of a psychological universal.
+Such an approach, however, neglects the existence of within-cultural variation altogether (see also Gurven, 2018).
+
+In the present study, we want to take a different approach for which we assume that universal processes and variation can co-exist (Greenfield et al., 2003; Jensen, 2012; Kline et al., 2018).
+Instead of starting with the outcome (performance in the task), we start with the process that generates the outcome.
+By defining this process, we make a proposal for the universal aspect of the process.
+At the same time, we define variable aspects in the process that generate individual differences.
+This allows us to define signatures that the process leaves behind that can be detected independent of absolute levels of performance.
+
+For gaze following, we can use the computational model proposed by Prein, Maurits, et al.
+(2024) to derive such predictions.
+They formalized the widely-held view that gaze following involves estimating a vector emanating from the eye center through the pupil (Butterworth \& Jarrett, 1991; Symons et al., 2004; Todorović, 2006; Yaniv \& Shatz, 1990).
+The key innovation of the model is that it explains how individuals may use the same process but still differ in their measured abilities.
+The process always involves estimating a vector but also involves a degree of uncertainty because the eye center is not directly observable.
+Individuals are assumed to differ in their level of uncertainty with which they estimate the vector which causes differences in their observable behavior.
+Importantly, the assumed process leaves a key signature in the data that is observable independent of the absolute level of performance.
+In the present study, we therefore focus on this signature instead of absolute levels of performance when evaluating the claim whether there is evidence for a universal cognitive process underlying gaze following.
+
+\hypertarget{the-current-study}{%
+\subsection{The current study}\label{the-current-study}}
+
+The present study had three goals.
+First, to collect a comprehensive data set and study the ontogeny of gaze following beyond infancy across cultures.
+To make this possible, we used a semi-standardized task that required minimal assistance from an experimenter and no behavioral coding.
+The task is an animated picture book presented on a tablet screen.
+Children watched a balloon disappear behind a hedge.
+An agent followed the trajectory of the balloon with their eyes (Figure \ref{fig:fig1}B).
+The key dependent variable was (im)precision, that is, the deviation between where the agent looked (where the balloon was) and the child's response.
+The task's flexible implementation as a browser-based web-app allowed us to quickly tailor its visual and audio content to each cultural setting (visuals and audio).
+The task has been psychometrically evaluated and has shown to yield reliable individual-level measurements across communities and across ages (Prein, Kalinke, et al., 2024; Prein, Bednarski, et al., 2024).
+
+We collected data in 17 different communities across 14 countries and five continents.
+Communities covered a broad spectrum of geographical locations, social and political systems, languages, and subsistence styles.
+This diversity allowed us to overcome a common pitfall of cross-cultural studies that compare urban communities from the Global North to rural communities from the Global South (Barrett, 2020).
+We aimed for large sample sizes within each community to contrast within- and between cultural variation.
+Our expectation regarding the first goal was to see substantial variation across cultures but even more variation between individuals.
+In all communities, we expected performance to increase with age.
+
+The second goals was to look for signatures in the data of the universal gaze following process predicted by the model of Prein, Bednarski, et al.
+(2024).
+In the task, the hidden object is located on a horizontal plane at the lower end of the screen.
+The agent is located in the upper center of the screen (see Figure \ref{fig:fig1}B).
+The model predicts trials in which the object is hidden further away from the center to be more difficult resulting in higher imprecision.
+The signature is thus a u-shaped relation between object location and imprecision (Figure \ref{fig:fig12}).
+
+Finally, we sought to explain individual differences in gaze following precision by linking them to methodological aspects of the study as well as aggregate measures of children's everyday social experience.
+Experience with tablets and touch screens co-varied with community and we expected children more familiar with this medium to perform better.
+Previous work suggested that gaze following is refined in social interaction (Movellan \& Watson, 2002; Senju et al., 2015).
+To approximate social interaction, we asked parents to fill out a questionnaire about household size and composition.
+We acknowledge that this measure approximates opportunities for social interaction in a rather crude way but we nevertheless expected children living in larger households and with more siblings (relative to their community) to be more accurate when following gaze.
 
@@
 
-{\centering \includegraphics[width=0.75\linewidth]{../visuals/fig1}
+{\centering \includegraphics[width=1\linewidth]{../figures/fig1_2}
 
@@
 \caption{(A) Data collection sites.
-Points show approximate geographical location of the data collection sites, coloring shows the sample sizes.
-(B) Screenshot from the task.
-The scene depicts the choice phase in a test trial.
-Participants had to use the gaze of the agent to locate the balloon and click on the hedge where they thought the balloon was.
-Agents, audio recordings and backgrounds were adpated to each cultural setting.
-(C) Graphical illustration of the cognitive model.
-Individuals infer the target of an agent's attention by estimating a vector based on the position of the pupils within the eyes.
-This process is noisy, illustrated by the different vectors.
-Individuals differ in their level of precision (indicated by alpha).
-Regardless of the level of precision, the further out the target lands, the less precise the model predicts individuals to be.}\label{fig:fig1}
+Points show the approximate geographical location of the data collection sites, coloring shows the sample sizes.
+(B) Screenshots from the task.
+The upper scene depicts the start, and the lower scene depicts the choice phase in a test trial.
+Participants had to use the gaze of the agent to locate the balloon and touch the location on the hedge where they thought the balloon was.
+Agents, audio recordings and backgrounds were adapted to each community.
+(C) Drawings used as agents across communities.}\label{fig:fig1}
 \end{figure}
 
-\begin{table}
+\begin{center}
+\begin{ThreePartTable}
 
-\caption{\label{tab:tab1}Participant demographics.}
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}[t]{llllllll}
+\begin{TableNotes}[para]
+\normalsize{\textit{Note.} 1 Proportion of participants who have access to touchscreens according to parental questionnaire.
+2 Local collaborators and piloting suggested that Nigerian English is suitable for Windhoek as well.}
+\end{TableNotes}
+
+\begin{longtable}{m{0.125\linewidth}m{0.125\linewidth}m{0.125\linewidth}m{0.125\linewidth}m{0.125\linewidth}m{0.125\linewidth}m{0.125\linewidth}}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
+\caption{\label{tab:tab1}Participant demographics.}\\
 \toprule
-Continent & Country & Community & N(male) & Age (range) & Language & Market integration & Touchscreen\\
+Continent & Country & Community & N (male) & Age (range) & Language & Touchscreen exposure1\\
 \midrule
-America & Argentina & Buenos Aires & 105 (53) & 4.72 (3.00 - 6.96) & Spanish (Rioplatense) & high & 0.90\\
- & Mexico & Ocuilan & 125 (61) & 4.97 (2.57 - 6.95) & Spanish (Mexican) & medium & 0.77\\
- & USA & Stanford & 100 (56) & 5.00 (2.52 - 7.90) & English (American) & high & 0.98\\
-Africa & Namibia & Hai||om & 60 (38) & 5.85 (2.74 - 8.34) & Hai||om & low & 0.05\\
- &  & Khwe & 59 (24) & 5.84 (3.38 - 8.63) & Khwedam & low & 0.19\\
+\endfirsthead
+\caption*{\normalfont{Table \ref{tab:tab1} continued}}\\
+\toprule
+Continent & Country & Community & N (male) & Age (range) & Language & Touchscreen exposure1\\
+\midrule
+\endhead
+Americas & Argentina & Buenos Aires & 105 (53) & 4.72 (3.00 - 6.96) & Spanish (Rioplatense) & 0.90\\
+ & México & Ocuilan & 127 (63) & 4.96 (2.57 - 6.95) & Spanish (Mexican) & 0.77\\
+ & USA & Stanford & 98 (54) & 4.99 (2.52 - 7.90) & English (American) & 0.98\\
+Africa & Namibia & Hai||om & 60 (38) & 5.85 (2.74 - 8.34) & Hai||om & 0.05\\
+ &  & Khwe & 59 (24) & 5.84 (3.38 - 8.63) & Khwedam & 0.19\\
+ &  & Windhoek & 39 (17) & 5.69 (2.66 - 8.66) & English (Nigerian)2 & 0.95\\
+ & Nigeria & Akure & 114 (54) & 5.07 (2.57 - 7.33) & English (Nigerian) & 0.91\\
+ & Rep. Congo & BaYaka & 29 (13) & 7.80 (3.94 - 10.56) & Yaka & 0.00\\
+ &  & Bandongo & 30 (11) & 7.45 (3.50 - 10.95) & Lingala & 0.00\\
+ & Uganda & Nyabyeya & 125 (62) & 5.94 (2.67 - 8.92) & Kiswahili & 0.34\\
+ & Zambia & Chimfunshi & 22 (5) & 5.98 (2.88 - 8.00) & Bemba & 0.14\\
+Europe & Germany & Leipzig & 100 (48) & 4.88 (2.53 - 6.95) & German & 0.89\\
+ & UK & Plymouth & 70 (30) & 6.02 (2.38 - 8.94) & English (British) & 0.99\\
+Asia & China & Beijing & 123 (62) & 5.47 (2.69 - 8.48) & Mandarin & 0.95\\
+ & India & Pune & 148 (73) & 6.14 (3.06 - 8.83) & English (Indian) / Marathi & 0.93\\
+ & Türkiye & Malatya & 85 (40) & 5.02 (2.75 - 7.12) & Turkish & 1.00\\
+Oceania & New Zealand & Auckland & 43 (19) & 5.14 (2.81 - 8.75) & English (New Zealand) & 0.95\\
+\bottomrule
 \addlinespace
- &  & Windhoek & 41 (18) & 5.68 (2.66 - 8.66) & English (Nigerian) & high & 0.95\\
- & Nigeria & Akure & 114 (53) & 5.07 (2.57 - 7.33) & English (Nigerian) & high & 0.91\\
- & Rep. Congo & BaYaka & 28 (12) & 7.86 (3.94 - 10.56) & BaYaka & low & 0.00\\
- &  & Bandongo & 30 (11) & 7.45 (3.50 - 10.95) & Lingala & low & 0.00\\
- & Sambia & Chimfunshi & 22 (5) & 5.98 (2.88 - 8.00) & Bemba & medium & 0.14\\
-\addlinespace
- & Uganda & Nyabyeya & 51 (27) & 5.41 (3.27 - 8.21) & Swahili & medium & 0.49\\
-Europe & Germany & Leipzig & 100 (48) & 4.88 (2.53 - 6.95) & German & high & 0.89\\
- & UK & Plymouth & 70 (30) & 6.02 (2.38 - 8.94) & English (British) & high & 0.99\\
-Asia & China & Beijing & 123 (62) & 5.47 (2.69 - 8.48) & Mandarin & high & 0.95\\
- & India & Pune & 155 (75) & 6.14 (3.06 - 8.83) & English (Indian) / Marathi & high & 0.92\\
-\addlinespace
- & Turkey & Malatya & 85 (40) & 5.02 (2.75 - 7.12) & Turkish & high & 1.00\\
-Oceania & New Zealand & Auckland & 43 (19) & 5.14 (2.81 - 8.75) & English (New Zealand) & high & 0.95\\
-\bottomrule
-\end{tabular}}
-\end{table}
+\insertTableNotes
+\end{longtable}
 
-We used an animated picture book tablet task in which participants were asked to locate a hidden object based on observing an agent's gaze.
+\end{ThreePartTable}
+\end{center}
+
+We used an animated picture book tablet task in which participants had to locate a hidden object based on observing an agent's gaze.
 Children watched a balloon disappear behind a hedge.
@@
 \ref{fig:fig1}B).
-The key dependent variable was the precision with which children located the agent's focus of attention, that is, the deviation between where the agent looked (where the object was) and where the child thought the agent looked.
-We adapted visuals and audio instructions specifically to each of the 17 communities.
-Previous work demonstrated excellent individual-level measurement properties for this task (\emph{17}).
-Thus, in addition to group-level trends, we were able to investigate individual-level variation.
+The key dependent variable was the (im)precision with which children located the agent's focus of attention, that is, the deviation between where the agent looked (where the balloon was) and the child's response.
+We adapted visuals and audio instructions specifically for each of the 17 communities.
+Previous work demonstrated excellent individual-level measurement properties for this task in a German sample (Prein, Kalinke, et al., 2024).
 
-As the first step, we investigated developmental gains.
-Across all 17 communities, we found a substantial increase in average levels of precision with age (fixed effect: \(\beta\) = -0.30, 95\% HDI (-0.39 - -0.21); range of community-level effects: \(\beta_{min}\) = -0.06, 95\% HDI (-0.17 - 0.06) to \(\beta_{max}\) = -0.58, 95\% HDI (-0.69 - -0.46).
-There were marked differences between communities: highly market-integrated communities around the globe showed higher levels of precision compared to less market-integrated communities.
-However, we believe that these results are better explained by exposure to technology than market integration.
-We discuss them in more detail below.
-Differences between communities were small compared to differences between individuals: communities did not form homogeneous clusters but largely overlapping distributions in that some individuals from communities with a lower average level of precision performed better compared to some individuals from a setting with a very high average level of precision.
-Furthermore, in all communities, some 4-year-olds outperformed children two years older than them (see Fig.
-\ref{fig:fig2}A).
+\hypertarget{methods}{%
+\section{Methods}\label{methods}}
 
-\begin{figure}
+\hypertarget{preregistration}{%
+\subsection{Preregistration}\label{preregistration}}
 
-{\centering \includegraphics[width=0.75\linewidth]{../visuals/pvis_pred}
+The study design, the sampling strategy and the general analytic strategy were preregistered prior to data collection (\url{https://osf.io/tdsvc}).
+The final sample size was not preregistered because we did not know how many communities would participate when the study began.
+Instead, we stated the age range we intended to study in each community (3.0 to 5.9 years of age) along and that we planned to test 20 children per year bin.
+We achieved this goal for most ages in most communities, but not for all (see Supplementary Table 1).
+The analysis reported here deviated from the preregistration in the following ways: In the pre-registration, in the regression models, we did not include random slopes for target centrality (i.e.~the distance of the location where the balloon landed from the center of the screen), neither within subject nor within cultural setting.
+Instead, we included random slopes for trial within subject.
+We decided to change this and remove random slopes for trial but include them for target centrality because trial effects in the sense of learning across trials were unlikely because participants did not receive differential feedback.
+Furthermore, multiple studies with the same task since the registration found no trial effects (Prein, Kalinke, et al., 2024; Prein, Maurits, et al., 2024).
+On the other hand, we included random slopes for target centrality to be able to look at cross-cultural variation.
+The cognitive models were not mentioned in the pre-registration because it is a more recent development (Prein, Maurits, et al., 2024).
 
-}
+\hypertarget{open-data-and-materials}{%
+\subsection{Open data and materials}\label{open-data-and-materials}}
 
-\caption{A) Developmental trajectories by cultural settings.
-Transparent dots show aggregated data for each individual.
-The color dentoes the different cultural settings.
-The developmental trajectories are predicted based on a model of the data aggregated for each participant.
-B) Performance by screen section and cultural setting.
-Each bin covers 1/10th of the screen.
-Points show means and eroor bars 95\% confidence intervals for the data within that bin aggregated across participants.}\label{fig:fig2}
-\end{figure}
+All study materials (\url{https://ccp-odc.eva.mpg.de/tango-cc/}), primary data and analysis scripts are publicly available (\url{https://github.com/ccp-eva/gafo-cc-analysis/}).
 
-Consistent developmental gains alone cannot inform us about the cognitive processes children use when locating the agent's focus of attention.
-Recent computational work modeled gaze following as social vector estimation (\emph{18}).
-When observing the eyes, onlookers estimate a vector from the center of the eye through the pupil.
-The focus of attention is the location wherever the estimated vectors from both eyes hit a surface (Fig.
-\ref{fig:fig1}C).
-The estimation process is not perfect, but each individual has a systematic level of uncertainty, which is conceptualized as the cause of individual differences.
-Importantly, this process model predicts a clear performance signature in our cross-cultural gaze following task: Trials in which the agent looks further away from the center (i.e.~to the left or right side of the screen) should result in lower levels of precision, compared to trials in which the agent looks closer to the middle.
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
+
+A total of 1377 children between 2.38 and 10.95 years of age provided data for the study.
+Children lived in 17 different communities, located in 14 different countries across five continents.
+Table \ref{tab:tab1} gives the sample size per community together with basic demographic information and age.
+For some children, the exact birthday was unknown.
+In such cases, we set the birthday to the 30th of June of the year that would make them fall into the reported age category.
+We provide a detailed description of the sample characteristics, the study site and recruitment strategy for each community in the Supplementary Material.
+
+Data from children was only included in the study when they contributed at least four valid test trials.
+We also excluded the data from children with a diagnosed developmental disorder.
+In sum, in addition to the sample size reported above, 74 additional children participated in the study but did not contribute data.
+The main reasons for exclusion were: contribution of less than four valid test trials, technical failures, and missing or implausible demographic information (e.g., when the number of children living in the household was reported to be larger than the household itself or when the number of children reported to live in the household equaled the number of children younger than the child being tested).
+We did not exclude any participants for performance reasons.
+A detailed description of each data collection site and the way children were recruited can be found in the Supplementary Material.
+
+\hypertarget{material-and-procedure}{%
+\subsection{Material and Procedure}\label{material-and-procedure}}
+
+The task was implemented as a browser-based interactive picture book using \texttt{HTML}, \texttt{CSS}, and \texttt{JavaScript}.
+Participants saw animated agents on a touch screen device, listened to pre-recorded audio instructions and responded by touching the screen.
+In all communities, a research assistant, fluent in the local language(s), guided the child through the task.
+That is, the research assistant guided the child through the introduction and advanced the study from trial to trial.
+
+Figure \ref{fig:fig1}B shows a screenshot from the task.
+The task was introduced verbally by the assistant as the balloon game in which the participant would play with other children to find a balloon.
+On each trial, participants saw an agent located in a window in the center of the screen.
+A balloon fell down from its starting position just below the agent.
+The agent's gaze followed the trajectory of the balloon.
+That is, the pupils and the iris were programmed to align with the center of the balloon.
+Once the balloon had landed on the ground, the agent was instructed to locate it, that is, to touch the location on the screen where they thought the balloon was.
+On each trial, we recorded the exact x-coordinate of the participant's touch.
+
+There were two types of training trials.
+In training 1 trials, the balloon fell down and landed in plain sight.
+Participants simply had to touch the visible balloon.
+In training 2 trials, the trajectory of the balloon was visible but it landed behind a small barrier (a hedge -- see Figure \ref{fig:fig1}B).
+Thus, participants needed to touch the hedge where they saw the balloon land.
+Next came test trials.
+Here, the barrier moved up and covered the balloon's trajectory.
+That is, participants only saw the agent's eyes move, but not the balloon.
+They had to infer the location of the balloon based on the agent's gaze direction.
+During training 1, training 2 and the first test trial, children heard voice-overs commenting what happened on the screen.
+Critically, the agent was described as wanting to help the child and always looking at the balloon.
+
+Children completed one training 1, two training 2 trials and 16 test trials.
+We excluded the first test trial from the analysis because of the voice-over.
+Thus, 15 test trials were used in the analysis below.
+Each child saw eight different agents (four male, four female).
+The agent changed from trial to trial, with alternating genders.
+A coin toss before the first trial decided whether the first agent was male or female.
+The order in which agents were shown was randomized with the constraint that all agents had to be shown once until an agent was shown again.
+The color of the balloon also changed from trial to trial in a random order, also with the constraint that all colors appeared once before any one was repeated.
+
+The location (x-coordinate) where the balloon landed was determined in the following way: The screen was divided in ten equally sized bins.
+On each trial, one of the bins was randomly selected and the exact x-coordinate was randomly chosen within that bin.
+Constraints were that the balloon landed in each bin once in the first ten trials and, for the remaining six test trials, it landed in a different om each trial.
+Thus, each bin appeared a no more than twice.
+
+All children were tested with a touchscreen device with a size between 11 and 13 inch equipped with a webcam.
+The data was either stored locally or sent to a server.
+In addition to the behavioral data, we stored the webcam recording of the session for verification purposes.
+Community-specific adaptations were made by changing the visuals and the audio instructions (see Supplementary Material for details).
+
+In addition to the gaze following task, caregivers responded to a short questionnaire about children's access to screens and touchscreens (binary answer) as well as the number of people, children and children younger than the focal child living in the household (numeric; see Supplementary Material for details).
+
+\hypertarget{analysis}{%
+\section{Analysis}\label{analysis}}
+
+\hypertarget{cross-cultural-variation}{%
+\subsection{Cross-cultural variation}\label{cross-cultural-variation}}
+
+We used Bayesian Regression models fit in \texttt{R} (R Core Team, 2023) using the package \texttt{brms} (Bürkner, 2017).
+We used default priors built into \texttt{brms}.
+The dependent variable in all regression models was imprecision, that is, the absolute distance between the true location of the balloon (x-coordinate of its center) and the location where the participant touched the screen.
+We used a Log-normal distribution to model the data because the natural lower bound for imprecision is zero and the data was right skewed with a long tail.
+Numeric predictors that entered the models were scaled to have a mean of zero and a standard deviation of 1.
+
+The first analysis was focused on cross-cultural variation.
+Fixed effects in the model were age and target centrality (distance of the landing position from the center in pixel/SVG units).
+The latter term accounts for trial difficulty.
+Furthermore, we included participant as a random effect, with a random slope for target centrality.
+To assess cross-cultural variation, we compared three models.
+A null model without cultural setting as a predictor (\texttt{brms} notation: \texttt{imprecision\ \textasciitilde{}\ age\ +\ target\_centrality\ +\ (target\_centrality\ \textbar{}\ participant)}), a model with cultural setting as a random intercept (\texttt{imprecision\ \textasciitilde{}\ age\ +\ target\_centrality\ +\ (target\_centrality\ \textbar{}\ participant)\ +\ (target\_centrality\ \textbar{}\ community)}) and a model with cultural setting as a random intercept and an added random slope for age (\texttt{imprecision\ \textasciitilde{}\ age\ +\ target\_centrality\ +\ (target\_centrality\ \textbar{}\ participant)\ +\ (age\ +\ target\_centrality\ \textbar{}\ community)}).
+Thus, the second model assumes that there is variation across cultures in average levels of precision and the third model assumes that there are additional cultural differences in the effect of age.
+
+As stated in the pre-registration, comparing these models could be problematic.
+Participants are fully nested within cultural setting.
+If there was an effect of cultural setting, we would expect participant random intercepts to cluster by cultural setting.
+This clustering would appear whether or not cultural setting would be included in the model as a random effect or not -- the only difference would be if the participant random intercepts were estimated as a deviation from a grand intercept or a culture-specific one.
+Standard metrics such as \texttt{WAIC} or \texttt{LOO} would penalize the model with additional intercept for cultural setting for having additional parameters that do not help to improve predictive accuracy.
+
+To get around this problem, we used a cross-validation procedure (see e.g., 6).
+For each cultural setting, we randomly sampled a data set that was 5/6 the size of the full data set (training data).
+Then, we fit the model to this training data and used the estimated model parameters to predict the remaining 1/6 of the data (testing data).
+We then compared the model predictions from the different models by computing the mean difference between the true and predicted imprecision, over all trials in the testing data set.
+This approach gets around the problem mentioned above because the model predicts a new data set for which the individual random intercepts are unknown.
+Clustering by culture could therefore only be predicted by a model that included culture as a predictor.
+We repeated the cross-validation procedure 100 times and counted which model performed best most often.
+
+\hypertarget{processing-signatures}{%
+\subsection{Processing signatures}\label{processing-signatures}}
+
+The processing signatures were derived from the model proposed by (Prein, Maurits, et al., 2024).
+The model sees gaze following as social vector estimation.
+When following gaze, onlookers observe the location (and movement) of the pupil within the eye and estimate a vector emanating from the center of the eye through the pupil.
+The focus of attention is the location where the estimated vectors from both eyes hit a surface (Fig.
+\ref{fig:fig12}).
+It is assumed that this estimation process is not perfect but has some uncertainty because the center of the eye is not directly observable.
+Individual differences are conceptualized as differences in the level of uncertainty.
+As a consequence, even though individuals use the same general process, they might differ in their absolute levels of precision.
+
+The process model predicts a clear performance signature in the data: trials in which the agent looks further away from the center should result in lower levels of precision compared to trials in which the agent looks closer to the center.
 This prediction is best understood by considering a similar phenomenon: pointing a torch light to a flat surface.
@@
 When the torch is rotated to the side, the light from one half of the cone must travel further than the light from the other half to reach the surface.
-As a consequence, the light is spread over a wider area.
+As a consequence, the light is spread over a wider area (see Fig.
+\ref{fig:fig12}).
 
-The processing signature was clearly visible across all 17 communities.
-Precision decreased when the agent looked at locations further away from the center (fixed effect: \(\beta\) = 0.48, 95\% HDI ( - 0.54); range of community-level effects: \(\beta_{min}\) = 0.58, 95\% HDI (0.51 - 0.66) to \(\beta_{max}\) = 0.22, 95\% HDI (0.05 - 0.38).
-Visualization of the data showed the predicted u-shaped pattern in all communities (see Fig.
-\ref{fig:fig2}B).
-These results indicate a universal cognitive process used by children in all communities.
-There is, however, an alternative way in which the u = shaped pattern might arise: it would also arise when participants ignored the agent's gaze and instead always selected the middle of the screen (center bias).
-To rule out this alternative explanation, we directly compared three cognitive models that made different assumptions about how participants' responses were generated: the focal vector-based gaze estimation model described above, a center-bias model where participants always select the center, and a random guessing model where participants select random locations.
-For every community, we found overwhelming support for the gaze estimation model (min \(BF_{10}\) \textless{} 1000 for comparisons with both alternative models).
-Taken together, children from all 17 communities processed gaze in similar ways.
+In the following, we give a brief mathematical description of the model. The model inversely models the process generating touches on the screen based on observed eye movements and is defined as:
 
-What is left to explain are the marked community- and individual-level differences.
-In addition to the gaze-following task, caregivers filled out a small questionnaire about children's access to screen-based technology and the composition of their households.
-On an individual level, we found that across communities, children with access to touchscreen devices had higher levels of precision (\(\beta\) = -0.14, SE = 0.04, 95\% CrI = -0.22 - -0.07).
-On a community level, we also saw that average performance was lowest in the communities in which touchscreen devices were the least frequent (Fig.
-\ref{fig:fig3}).
-Thus, methodological factors likely explained the marked differences between communities.
+\begin{equation}
+    P(\theta | x_c, \alpha_l, \alpha_r) \propto P(x_c | \alpha_l, \alpha_r, \theta)P(\theta)
+\end{equation}
+
+Here, \(\theta\) represents an individual's level of precision in locating the focus of the agent's attention, \(x_c\) represents the touched coordinate, and \(\alpha_l\) and \(\alpha_r\) correspond to the left and right pupil angles (each defined as the angle between a line connecting the center of the eye to the pupil and a line extended vertically downward from the center of the eye).
+
+The basic assumption in this model is that participants touch on the screen location where they think the agent is looking.
+The true eye angles (\(\alpha_l\) and \(\alpha_r\)) are not directly observable and are estimated with noise, yielding \(\hat{\alpha_l}\) and \(\hat{\alpha_r}\).
+
+Each touch \(x_c\) implies a ``matched pair'' of estimated pupil angles \(\hat{\alpha_l}\) and \(\hat{\alpha_r}\), with the constraint that the lines extended along those two angles meet at the precise location of where the target is believed to be.
+As a consequence, we can rewrite the likelihood function of the model as:
+
+\begin{equation}
+P(x_c | \alpha_l, \alpha_r, \theta) \propto P(\hat{\alpha_l}, \hat{\alpha_r} | \alpha_l, \alpha_r, \theta) P(x_c)
+\end{equation}
+
+\(P(x_c)\) is a prior over potential target locations.
+Because the target was last visible in the screen and because the agent was located in the center, we assumed that participants have an a priori expectation that the target will land closer to the middle.
+We estimated the strength of this center bias (i.e., the standard deviation of a Normal distribution around the screen center) based on the data: \(P(x_c) \sim \mathcal{N}(960, \sigma^p)\).
+
+The primary inferential task for participants is therefore to estimate the pupil angles (\(\hat{\alpha_l}\) and \(\hat{\alpha_r}\)), that is, to sample from the term \(P(\hat{\alpha_l}, \hat{\alpha_r} | \alpha_l, \alpha_r, \theta)\).
+Here, we assumed that the pair of estimated pupil angles were sampled from a probability distribution which is the product of two Normal distributions of equal variance, \(\sigma_v\), centered on the true pupil angles:
+
+\begin{equation}
+P(\hat{\alpha_l}, \hat{\alpha_r} | \alpha_l, \alpha_r, \theta) \propto \phi(\hat{\alpha}_l ; \alpha_l, \sigma_v)\phi(\hat{\alpha}_r ; \alpha_r, \sigma_v),
+\end{equation}
+
+Thus, \(\sigma_v\) determines the level of accuracy with which participants estimated the pupil angles, and it is thus the component of the model that defines \(\theta\).
+Smaller values of \(\sigma_v\) result in a narrow distribution around the pupil angle, making touches far away from the target less likely.
+Conversely, larger values for \(\sigma_v\) lead to a wider distribution, making touches far away from the target more likely.
+To circle back to the analogy introduced above, \(\sigma_v\) corresponds to the width of the light beam.
+Thus, the goal of the model was to estimate participant-specific values for \(\sigma_v\): \(\sigma_{v_i}\).
+For more details on how \(\sigma_{v_i}\) was estimated, see the Supplementary Material.
+
+As stated above, the key signature prediction of the model is that precision decreases when the balloon lands further away from the center.
+To test this prediction, we fit a model predicting imprecision by age and target centrality with random intercepts for participant and community and random slopes for target centrality within participant and community (\texttt{imprecision\ \textasciitilde{}\ age\ +\ target\_centrality\ +\ (target\_centrality\ \textbar{}\ participant)\ +\ (age\ +\ target\_centrality\ \textbar{}\ community)}).
+As stated above, the predictor target centrality captures the distance from the center so that a positive effect of target centrality (i.e.~a positive estimate with a 95\% CrI not overlapping with zero) would mean support for the processing signature.
+In addition, we visualized the data for each community and inspected the shape of the plot.
+
+The same pattern, however, also arises when participants ignore the agent's gaze completely and instead follow simple heuristics.
+When participants always touch the center of the screen, regardless of where the agent is looking, trials in which the balloon lands further away from the center have a higher imprecision.
+When participants randomly touch a location on the screen -- again ignoring the agent's gaze -- the maximum imprecision for trials in which the balloon lands in the center is half the width of the screen.
+When the balloon lands on one of the far ends of the screen, the maximum imprecision is a full screen widths.
+Thus, across trials, the average imprecision is again higher when the balloon lands further away from the center, resulting in the same pattern as predicted by the model.
+
+Even though these alternatives are unlikely because they assume that participants ignore the agent's gaze, we nevertheless want to rule them out as processes generating the data.
+Thus, we implemented the gaze model along with the two alternative models in the probabilistic programming language \texttt{webppl} (Goodman \& Stuhlmüller, 2014).
+The way the gaze model predicts the participants behavior has been described above.
+The center bias model predicts a participant's touch by sampling from a Normal distribution around the center of the screen \(P(x_c) \sim \mathcal{N}(960, 160)\) (960 is the x-coordinate of the center and 160 is the width of the balloon).
+The random guessing model predicts participant's touch by sampling from a uniform distribution over all possible locations: \(P(x_c) \sim \mathcal{U}(0, 1920)\).
+Information on the prior distributions for all model parameters can be found in the associated online repository.
+
+For each community, we compared models based on the marginal likelihood of the data for each model, which represents the likelihood of the data while averaging over the prior distribution on parameters.
+The pair-wise ratio of marginal likelihoods for two models is known as the Bayes Factor.
+Bayes Factors are a quantitative measure of the predictive quality of a model, taking into account the possible values of the model parameters weighted by their prior probabilities.
+The incorporation of the prior distribution over parameters in the averaging process implicitly considers model complexity: models with more parameters typically exhibit broader prior distributions over parameter values and broader prior distribution can attenuate the potential gains in predictive accuracy that a model with more parameters might otherwise achieve (Lee \& Wagenmakers, 2014).
+
+\hypertarget{predictors-of-variation}{%
+\subsection{Predictors of variation}\label{predictors-of-variation}}
+
+The final analysis focused on whether we could predict performance in the task by methodological aspects of the study and aggregate measures of everyday social experience.
+For the ease of model fitting, we aggregated the data for each participant so that models predicted the average imprecision across trials.
+This approach is justified because the mean is nearly perfectly correlated with a model-based estimate of a participant's ability (\(\sigma_v\) in the model above, see Prein, Maurits, et al., 2024) and because the predictor variables did not vary within child.
+
+In the questionnaire, we asked about children's exposure to screens as well as touchscreens.
+These two variables were largely redundant and so we included only one of them in the model.
+We chose the availability of a touchscreen as a predictor because the task itself was presented on a touchscreen.
+
+For household composition, we asked for the total number of people in the household, the number of children and the number of younger children.
+We standardized each predictor within each community before fitting the models.
+Thus, the interpretation of the coefficient is the gain in precision for living e.g., in a larger household relative to other children from the same community.
+
+We compared a null model (\texttt{mean\_imprecision\ \textasciitilde{}\ age\ +\ (age\ \textbar{}\ community)}) to a model including access to touchscreens only as a fixed effect (\texttt{mean\_imprecision\ \textasciitilde{}\ touchscreen\ +\ age\ +\ (age\ \textbar{}\ culture)}), a model in which the effect of access to touchscreens was also allowed to vary by community (\texttt{mean\_imprecision\ \textasciitilde{}\ touchscreen\ +\ age\ +\ (touchscreen\ +\ age\ \textbar{}\ culture)}) and a model for each of the household-based predictors (e.g., \texttt{mean\_imprecision\ \textasciitilde{}\ household\_size\ +\ touchscreen\ +\ age\ +\ (age\ \textbar{}\ culture)}).
+Models were fit in \texttt{brms} and compared based on the difference in expected log pointwise predictive density (\texttt{ELPD}) computed via the widely applicable information criterion (\texttt{WAIC}) and the standard error of that difference (SE).
+We inspected the estimates for fixed effects in the winning model along with their 95\% CrI.
+
+For a community-level perspective, we correlated the proportion of children with access to touchscreens with an age-corrected performance average for each community.
+To obtain the latter, extracted the random intercept estimates for community from the null model described above.
+Because the model also includes age as a fixed effect, these values reflect variation between communities once differences in age have been accounted for.
+
+\hypertarget{results}{%
+\section{Results}\label{results}}
+
+\hypertarget{cross-cultural-variation-in-development}{%
+\subsection{Cross-cultural variation in development}\label{cross-cultural-variation-in-development}}
+
+There were marked differences between communities (see Figure \ref{fig:fig2}A).
+The cross-validation procedure found that a model assuming cross-cultural variation in average performance as well as developmental trajectories outperformed simpler models in 100\% (no variation in developmental trajectories) and 98\% (no variation between communities at all) of cases, respectively.
+Nevertheless, average differences in precision between communities were small compared to differences between individuals: communities did not form homogeneous clusters but largely overlapping distributions in that some individuals from communities with a lower average level of precision performed better compared to some individuals from a setting with a very high average level of precision.
+Similarly, in all communities, some 4-year-olds outperformed children two years older than them (see Figure \ref{fig:fig2}A).
+
+Next, we investigated developmental gains, that is, the extent to which children become more precise at estimating the target location with age.
+Across all 17 communities, we found a substantial increase in average levels of precision with age (fixed effect of age: \(\beta\) = -0.30, 95\% Credible Interval (CrI) (-0.40 --- -0.21); range of community-level (random) effects: \(\beta_{min}\) = -0.06, 95\% CrI (-0.18 --- 0.05) to \(\beta_{max}\) = -0.59, 95\% CrI (-0.71 --- -0.48)).
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{../figures/pvis_pred} \caption{A) Developmental trajectory across and B) by community.
+The developmental trajectories are predicted based on a model of the data aggregated for each participant.
+C) Performance by target location on the screen across, and D) by community.
+Each bin covers 1/10th of the screen.
+Points show means, and error bars 95\% confidence intervals for the data within that bin aggregated across participants.
+Transparent dots in A) and C) show aggregated data for each individual.}\label{fig:fig2}
+\end{figure}
+
+\hypertarget{processing-signatures-1}{%
+\subsection{Processing signatures}\label{processing-signatures-1}}
 
@@
 
-{\centering \includegraphics[width=0.5\linewidth]{../visuals/pcomtc}
+{\centering \includegraphics[width=1\linewidth]{../figures/fig1_3}
 
@@
 
-\caption{Correlation between performance in the gaze-following task and the exposure to touchscreens on a cultural setting-level.
-Realtive imprecision accounts for differences in age between settings in that it corresponds to the random intercept estimate for each setting in a model predicting performance by age.}\label{fig:fig3}
+\caption{Graphical illustration of the cognitive model.
+Individuals infer the target of an agent’s attention by estimating a vector based on the position of the pupils within the eyes.
+This process is noisy, illustrated by the different vectors (transparent lines).
+Individuals differ in their level of precision (indicated by sigma).
+For a given level of precision, the further the target lands from the center of the screen, the less precise the model predicts individuals to be.
+Solid and transparent dots show simulated means and individual data points to illustrate the predicted effect of target position.}\label{fig:fig12}
 \end{figure}
 
-On an individual level, other factors likely generated individual differences because there was substantial variation even in communities where almost all children had access to touchscreens.
-Previous work suggested that social cognition develops in social interaction (\emph{19}--\emph{21}), in particular, with older siblings (\emph{22}, \emph{23}).
-We found tentative support for this idea in the form of a small but consistent effect in the direction that participants living together with more children older than themselves had slightly higher levels of precision (\(\beta\) = -0.01, SE = 0.01, 95\% CrI = -0.04 - 0.01).
+The key processing signature predicted by the cognitive model was that precision should decrease when the balloon landed further away from the center.
+This signature was clearly visible across all 17 communities (fixed effect for target centrality: \(\beta\) = 0.47, 95\% CrI (0.40 --- 0.54); range of community-level (random) effects: \(\beta_{min}\) = 0.58, 95\% CrI (0.51 --- 0.66) to \(\beta_{max}\) = 0.16, 95\% CrI (-0.01 --- 0.33)).
 
-Following and understanding gaze is a foundational building block of human social cognition (\emph{8}, \emph{9}).
-A substantial body of work has explored the developmental onset of gaze following in a few selected cultural settings (\emph{10}--\emph{12}, \emph{15}, \emph{16}).
-The data reported here provides evidence that children all over the world process gaze in the same way.
-Key performance signatures of a model that sees gaze following as a form of social vector estimation were found in the data of all 17 distinct cultural communities.
-The cognitive processes underlying gaze following are thus likely to be rooted in humans' evolved cognitive architecture, which is -- presumably -- later refined during social interaction.
-The phylogenetic roots of these processes might possibly lie much deeper as primates from a wide range of species follow gaze (\emph{24}--\emph{26}).
-Yet, if they also show the same processing signatures has yet to be explored.
+Visualization of the data also showed the predicted u-shaped pattern in all communities (see Fig.
+\ref{fig:fig2}B).
+The visualization also showed that the u is not symmetric.
+Instead, imprecision seemed to be higher when the target lands on the left side of the screen.
 
-There are important limitations to this study.
-The methodological factors that influenced performance might have overshadowed individual and community-level differences that originate from other sources.
-Importantly, this does not affect our interpretation of the data as evidence for shared cognitive processing because the key processing signatures were present in all communities.
-The role that social interaction plays as a potential driver of development and source of individual differences is vastly under-explored in the current study.
-The small effect of the exposure to older children does not indicate which aspects of social interaction enhance gaze processing.
-Naturalistic data directly recording social interactions across communities would offer crucial information to close this explanatory gap.
-Recent work in the field of language acquisition has shown how technological innovations can be used to close this explanatory gap.
+To rule out alternative explanations, we compared the focal vector-based gaze estimation model described above to the alternative center bias and random guessing models, we found overwhelming support for the gaze estimation model (min \(BF_{10}\) \textgreater{} 100 000 for comparisons with both alternative models, see Supplementary Materials) in every community.
 
-The evidence presented here holds far-reaching implications.
-Our work pioneers a methodological approach that introduces solid individual-level measurement to the cross-cultural study of cognitive development.
-As such, it serves as a blueprint for future research on a broad spectrum of cognitive abilities.
-Most importantly, this study offers a much-needed empirical foundation for theories on human nature.
-The finding that children from diverse cultures deploy similar cognitive processes in interpreting gaze points to an evolutionary basis of basic social cognition, which is refined during development, presumably through social interaction.
+\hypertarget{predictors-of-variation-1}{%
+\subsection{Predictors of variation}\label{predictors-of-variation-1}}
+
+\begin{table}
+
+\caption{\label{tab:predcomptable}comparison of models predicting individual-level variation.}
+\centering
+\begin{tabular}[t]{llllll}
+\toprule
+Model & diff\textsubscript{WAIC} & diff\textsubscript{SE} & WAIC & SE\textsubscript{WAIC} & Weight\\
+\midrule
+touchscreen & 0.00 & 0.00 & 16935.74 & 71.16 & 0.43\\
+touchscreen + younger children & -0.27 & 1.02 & 16936.27 & 71.17 & 0.26\\
+touchscreen + household & -0.76 & 0.51 & 16937.26 & 71.10 & 0.11\\
+touchscreen (by culture) & -0.99 & 0.56 & 16937.73 & 71.12 & 0.00\\
+touchscreen + children & -1.13 & 0.37 & 16938.00 & 71.16 & 0.00\\
+\addlinespace
+null & -4.32 & 3.63 & 16944.38 & 70.97 & 0.20\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+The model comparison favored the model including touchscreen as a fixed effect (no variation between communities) with no additional predictors capturing aspects of household composition (see Table \ref{tab:predcomptable}).
+Children with access to touchscreen devices had higher levels of precision (\(\beta\) = -0.14, 95\% CrI = -0.21 --- -0.07).
+This effect was consistent across communities in that allowing the effect of access to touchscreens to vary across communities did not improve model fit.
+
+On a community level, average performance was lowest in communities in which touchscreen devices were the least frequent (community-level correlation between age-corrected imprecision and proportion of children with access to touchscreens: \emph{r} = -0.90, 95\% CI = -0.96 --- -0.74).
+
+Table \ref{tab:predcomptable} shows that differences between models were small (\texttt{ELPD} \textless{} 1), suggesting that they were largely equivalent.
+For the sake of consistency, we also inspected the posterior estimates for household composition predictors, none of which had a 95\% CrI excluding zero (household size: \(\beta\) = -0.01, 95\% CrI = -0.03 --- 0.02; children size: \(\beta\) = 0, 95\% CrI = -0.02 --- 0.02; younger children: \(\beta\) = 0.01, 95\% CrI = -0.01 --- 0.03).
+
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
+
+Following and understanding gaze is a foundational building block of human social cognition (Langton et al., 2000; Richardson \& Dale, 2005; Rossano, 2012; Scaife \& Bruner, 1975; Sebanz et al., 2006; Tomasello et al., 2007).
+A substantial body of work has explored the developmental onset of gaze following in early infancy and in a few selected cultural communities (Byers-Heinlein et al., 2021; Gredebäck et al., 2010; Moore, 2008; Tang et al., 2023).
+The study reported here presents comparable data (i.e.~collected via the same task with minimal superficial adjustments) on the development of gaze following in young children from 17 communities from five continents.
+We found substantial variation between cultural settings, both in average levels as well as the steepness of developmental trajectories.
+In that, however, individual-level variation greatly outweighed community-level variation.
+Despite this variation, we found evidence that the basic process of gaze following is the same across communities: We found key performance signatures predicted by a model conceptualizing gaze following as a form of social vector estimation process in all communities.
+Individual-differences in gaze following were related to children's exposure to touchscreens but not to aggregate measures of opportunities for social interactions (i.e.~household composition).
+This study provides evidence for a putative universal in basic social cognition and presents a new approach to studying cognitive processing in light of cross-cultural and individual variation.
+
+The task we used has good individual-level measurement properties across cultures (Prein, Bednarski, et al., 2024).
+This puts us in the position to contrast individual-level variability with community-level variability instead of dismissing the former as noise.
+The obvious pattern here was that cultural settings did not form homogeneous clusters but greatly overlapping distributions.
+That is, variation in the average developmental trajectories was small compared to variation between-individuals both within communities and across them.
+Some individuals from the community with the highest average level of imprecision outperformed individuals from the community with the lowest average.
+Thus, the explanatory power of of community-level variables might be limited.
+
+On the face of it, a community-level perspective on the results points to a urban vs.~rural split in the data.
+Importantly, our sample included urban settings from the global north and south so that geographic location and living conditions are only partly confounded (we did not collect data in rural settings in the global north).
+Case in point is Namibia, where we collected data in both types of settings with results mirroring the overall pattern.
+In previous work, such differences are often attributed to specific community-level differences in everyday experiences that come with urbanization (e.g., Amir et al., 2020; Mavridis et al., 2020).
+Correlations identified this way remain speculative because urbanization brings with it a whole suite of differences.
+Furthermore, this approach neglects within-community variation in everyday experience (Bohn et al., 2024).
+It is often chosen because the measures used are not suited to reliably quantify individual-level variation.
+Given the good measurement properties of our task and the individual-level assessment via the parental questionnaire, we were able to directly link aspects of experience and cognitive development, omitting the intermediate community-level.
+
+We investigated both methodological and household composition as potential predictors.
+Familiarity with the device used for data collection explained variation between communities.
+Children with more touchscreen experience were probably better at task handling and thus more likely to precisely touch the location they inferred the agent to look at.
+Importantly, the model comparison showed that this relation did not vary substantially across communities.
+This effect, however, did not explain all variation between individuals.
+For example, in Malatya (Türkiye) where 100\% of children had access to touchscreens there was still substantial variation between individuals.
+This strongly indicates that other factors likely contributed to individual differences.
+
+Social-interactional variables have been linked to the development of gaze following in previous work (Astor et al., 2020; Movellan \& Watson, 2002; Senju et al., 2015).
+Thus, we predicted that opportunities for social interaction -- approximated by household size and composition -- while accounting for absolute differences and the prevalence of touchscreens, would be linked to performance in the task.
+This was not the case.
+This result does not provide strong evidence for the absence of a relation between social-interactional variables and the development of gaze following, however, it suggests that a more granular approach is necessary to identify the relevant aspects of social interaction.
+The coarse approach taken here did not suffice.
+
+Despite substantial variation, we found the expected processing signatures in the data from all communities.
+Alternative accounts for how this pattern might have arisen did not explain the data well.
+These alternative approaches did not present viable alternative theoretical accounts for how participants followed gaze and why they differed from one another because they assumed that participants ignore gaze altogether.
+An alternative account involving the use of gaze cues would be that participants do not differ in the precision with which they estimate the gaze vector but that they differ only in the precision with which they touch the inferred location on the screen.
+This alternative -- motor noise -- account, however, would not predict the effect of target centrality and the u-shaped relation between target location and precision because motor noise should lead to normally distributed touches around the inferred location.
+Thus, we take the results as support for the idea of a universal process that is well-approximated by the model.
+This cognitive process might be rooted in humans' evolved cognitive architecture, which is later refined during ontogeny.
+The phylogenetic roots of these processes might possibly lie much deeper as primates from a wide range of species follow gaze (Itakura, 2004; Kano \& Call, 2014; Rosati \& Hare, 2009; Tomasello et al., 1998).
+Yet, similarities in overt behavior do not imply the same underlying cognitive processes.
+The present study defines clear performance signatures that can be explored in other species to test such evolutionary hypotheses.
+
+An unexpected result was that imprecision seemed to be higher on the left compared to the right side of the screen.
+One candidate explanation for this pattern might be the dominance -- despite variation -- of right-handedness across cultures (Papadatou-Pastou et al., 2020).
+As of now, this is mere specualtion and future research should investigate the origins of this pattern in more detail.
+
+The study has further limitations.
+The fact that performance in the task was correlated with exposure to touchscreens might have overshadowed other sources of variation.
+However, we think it is in an important innovation that we were able to account for this effect.
+Most developmental cross-cultural studies do not even question the portability of their measurement instruments.
+Importantly, the key result that the processing signatures were evident in all communities, is immune to this finding.
+The potential that lies in the precise individual-level measurement that our task achieves was largely unexploited.
+As mentioned above, the questionnaire items only offered a very coarse picture into children's actual lived experiences.
+Future work could increase the resolution with which everyday experiences in children from diverse communities are recorded to compare the drivers behind social-cognitive development as we observe it.
+Recent work in the field of language acquisition has shown how technological innovations allowed for direct recording of social interactions across communities which can be used to close this explanatory gap (Bergelson et al., 2023; Donnelly \& Kidd, 2021).
+
+In sum, our work pioneers an approach that introduces computational modeling and precise individual-level measurement to the cross-cultural study of cognitive development.
+This approach allowed us to identify potential universals in the human cognitive architecture rather than just overt behavior.
+As such, it can serve as a blueprint for future research on a broad spectrum of cognitive abilities.
+Finally, the study provides a much-needed empirical foundation for theories on the nature of the human mind.
+Children from diverse communities deploy similar cognitive processes in interpreting gaze, pointing to a universal foundation of basic social cognition.
 
@@
 \hypertarget{refs}{}
-\begin{CSLReferences}{0}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-tomasello2005understanding}{}}%
-\CSLLeftMargin{1. }%
-\CSLRightInline{M.
-Tomasello, M.
-Carpenter, J.
-Call, T.
-Behne, H.
-Moll, Understanding and sharing intentions: The origins of cultural cognition.
-\emph{Behavioral and Brain Sciences} \textbf{28}, 675--691 (2005).}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-amir2020developmental}{}}%
+Amir, D., Jordan, M.
+R., McAuliffe, K., Valeggia, C.
+R., Sugiyama, L.
+S., Bribiescas, R.
+G., Snodgrass, J.
+J., \& Dunham, Y.
+(2020).
+The developmental origins of risk and time preferences across diverse societies.
+\emph{Journal of Experimental Psychology: General}, \emph{149}(4), 650.
+
+\leavevmode\vadjust pre{\hypertarget{ref-amir2020cross}{}}%
+Amir, D., \& McAuliffe, K. (2020). Cross-cultural, developmental psychology: Integrating approaches and key insights. \emph{Evolution and Human Behavior}, \emph{41}(5), 430--444.
+
+\leavevmode\vadjust pre{\hypertarget{ref-astor2020social}{}}%
+Astor, K., Lindskog, M., Forssman, L., Kenward, B., Fransson, M., Skalkidou, A., Tharner, A., Cassé, J., \& Gredebäck, G.
+(2020).
+Social and emotional contexts predict the development of gaze following in early infancy.
+\emph{Royal Society Open Science}, \emph{7}(9), 201178.
+
+\leavevmode\vadjust pre{\hypertarget{ref-astor2022maternal}{}}%
+Astor, K., Lindskog, M., Juvrud, J., Namgyel, S.
+C., Wangmo, T., Tshering, K., Gredebäck, G., et al.
+(2022).
+Maternal postpartum depression impacts infants' joint attention differentially across cultures.
+\emph{Developmental Psychology}, \emph{58}(12), 2230.
+
+\leavevmode\vadjust pre{\hypertarget{ref-astor2021gaze}{}}%
+Astor, K., Thiele, M., \& Gredebäck, G. (2021). Gaze following emergence relies on both perceptual cues and social awareness. \emph{Cognitive Development}, \emph{60}, 101121.
+
+\leavevmode\vadjust pre{\hypertarget{ref-barrett2020towards}{}}%
+Barrett, H. C. (2020). Towards a cognitive science of the human: Cross-cultural approaches and their urgency. \emph{Trends in Cognitive Sciences}, \emph{24}(8), 620--638.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bergelson2023everyday}{}}%
+Bergelson, E., Soderstrom, M., Schwarz, I.-C., Rowland, C.
+F., Ramirez-Esparza, N., R.
+Hamrick, L., Marklund, E., Kalashnikova, M., Guez, A., Casillas, M., et al.
+(2023).
+Everyday language input and production in 1,001 children from six continents.
+\emph{Proceedings of the National Academy of Sciences}, \emph{120}(52), e2300671120.
+
+\leavevmode\vadjust pre{\hypertarget{ref-blake2015ontogeny}{}}%
+Blake, P.
+R., McAuliffe, K., Corbit, J., Callaghan, T.
+C., Barry, O., Bowie, A., Kleutsch, L., Kramer, K., Ross, E., Vongsachang, H., et al.
+(2015).
+The ontogeny of fairness in seven societies.
+\emph{Nature}, \emph{528}(7581), 258--261.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bohn2024understanding}{}}%
+Bohn, M., Fong, F. T., Pope-Caldwell, S., Stengelin, R., \& Haun, D. B. (2024). Understanding cultural variation in cognition one child at a time. \emph{Nature Reviews Psychology}, 1--3.
+
+\leavevmode\vadjust pre{\hypertarget{ref-brooks2005development}{}}%
+Brooks, R., \& Meltzoff, A. N. (2005). The development of gaze following and its relation to language. \emph{Developmental Science}, \emph{8}(6), 535--543.
+
+\leavevmode\vadjust pre{\hypertarget{ref-brooks2015connecting}{}}%
+Brooks, R., \& Meltzoff, A.
+N.
+(2015).
+Connecting the dots from infancy to childhood: A longitudinal study connecting gaze following, language, and explicit theory of mind.
+\emph{Journal of Experimental Child Psychology}, \emph{130}, 67--78.
+
+\leavevmode\vadjust pre{\hypertarget{ref-brownell2011early}{}}%
+Brownell, C. A. (2011). Early developments in joint action. \emph{Review of Philosophy and Psychology}, \emph{2}, 193--211.
+
+\leavevmode\vadjust pre{\hypertarget{ref-burkner2017brms}{}}%
+Bürkner, P.-C. (2017). Brms: An r package for bayesian multilevel models using stan. \emph{Journal of Statistical Software}, \emph{80}(1), 1--28.
+
+\leavevmode\vadjust pre{\hypertarget{ref-butterworth1991minds}{}}%
+Butterworth, G., \& Jarrett, N.
+(1991).
+What minds have in common is space: Spatial mechanisms serving joint visual attention in infancy.
+\emph{British Journal of Developmental Psychology}, \emph{9}(1), 55--72.
+
+\leavevmode\vadjust pre{\hypertarget{ref-byers2021development}{}}%
+Byers-Heinlein, K., Tsui, R.
+K.-Y., Van Renswoude, D., Black, A.
+K., Barr, R., Brown, A., Colomer, M., Durrant, S., Gampe, A., Gonzalez-Gomez, N., et al.
+(2021).
+The development of gaze following in monolingual and bilingual infants: A multi-laboratory study.
+\emph{Infancy}, \emph{26}(1), 4--38.
+
+\leavevmode\vadjust pre{\hypertarget{ref-callaghan2011early}{}}%
+Callaghan, T., Moll, H., Rakoczy, H., Warneken, F., Liszkowski, U., Behne, T., Tomasello, M., \& Collins, W.
+A.
+(2011).
+Early social cognition in three cultural contexts.
+\emph{Monographs of the Society for Research in Child Development}, i--142.
+
+\leavevmode\vadjust pre{\hypertarget{ref-carpenter1998social}{}}%
+Carpenter, M., Nagell, K., Tomasello, M., Butterworth, G., \& Moore, C.
+(1998).
+Social cognition, joint attention, and communicative competence from 9 to 15 months of age.
+\emph{Monographs of the Society for Research in Child Development}, i--174.
+
+\leavevmode\vadjust pre{\hypertarget{ref-clark2023white}{}}%
+Clark, I.
+R., Lee, K.
+C., Poux, T., Langergraber, K.
+E., Mitani, J.
+C., Watts, D., Reed, J., \& Sandel, A.
+A.
+(2023).
+White sclera is present in chimpanzees and other mammals.
+\emph{Journal of Human Evolution}, \emph{176}, 103322.
+
+\leavevmode\vadjust pre{\hypertarget{ref-d1997demonstration}{}}%
+D'Entremont, B., Hains, S. M., \& Muir, D. W. (1997). A demonstration of gaze following in 3-to 6-month-olds. \emph{Infant Behavior and Development}, \emph{20}(4), 569--572.
+
+\leavevmode\vadjust pre{\hypertarget{ref-deak2000effects}{}}%
+Deák, G.
+O., Flom, R.
+A., \& Pick, A.
+D.
+(2000).
+Effects of gesture and target on 12-and 18-month-olds' joint visual attention to objects in front of or behind them.
+\emph{Developmental Psychology}, \emph{36}(4), 511.
+
+\leavevmode\vadjust pre{\hypertarget{ref-del2019developmental}{}}%
+Del Bianco, T., Falck-Ytter, T., Thorup, E., \& Gredebäck, G. (2019). The developmental origins of gaze-following in human infants. \emph{Infancy}, \emph{24}(3), 433--454.
+
+\leavevmode\vadjust pre{\hypertarget{ref-dixson2018scaling}{}}%
+Dixson, H. G., Komugabe-Dixson, A. F., Dixson, B. J., \& Low, J. (2018). Scaling theory of mind in a small-scale society: A case study from vanuatu. \emph{Child Development}, \emph{89}(6), 2157--2175.
+
+\leavevmode\vadjust pre{\hypertarget{ref-doherty2006development}{}}%
+Doherty, M. J. (2006). The development of mentalistic gaze understanding. \emph{Infant and Child Development}, \emph{15}(2), 179--186.
+
+\leavevmode\vadjust pre{\hypertarget{ref-donnelly2021longitudinal}{}}%
+Donnelly, S., \& Kidd, E.
+(2021).
+The longitudinal relationship between conversational turn-taking and vocabulary growth in early language development.
+\emph{Child Development}, \emph{92}(2), 609--625.
+
+\leavevmode\vadjust pre{\hypertarget{ref-emery2000eyes}{}}%
+Emery, N. J. (2000). The eyes have it: The neuroethology, function and evolution of social gaze. \emph{Neuroscience \& Biobehavioral Reviews}, \emph{24}(6), 581--604.
+
+\leavevmode\vadjust pre{\hypertarget{ref-frischen2007gaze}{}}%
+Frischen, A., Bayliss, A. P., \& Tipper, S. P. (2007). Gaze cueing of attention: Visual attention, social cognition, and individual differences. \emph{Psychological Bulletin}, \emph{133}(4), 694.
+
+\leavevmode\vadjust pre{\hypertarget{ref-dippl}{}}%
+Goodman, N. D., \& Stuhlmüller, A. (2014). \emph{{The design and implementation of probabilistic programming languages}}. \url{http://dippl.org}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-gredeback2010development}{}}%
+Gredebäck, G., Fikke, L., \& Melinder, A.
+(2010).
+The development of joint visual attention: A longitudinal study of gaze following during interactions with mothers and strangers.
+\emph{Developmental Science}, \emph{13}(6), 839--848.
+
+\leavevmode\vadjust pre{\hypertarget{ref-greenfield2003cultural}{}}%
+Greenfield, P. M., Keller, H., Fuligni, A., \& Maynard, A. (2003). Cultural pathways through universal development. \emph{Annual Review of Psychology}, \emph{54}(1), 461--490.
+
+\leavevmode\vadjust pre{\hypertarget{ref-gurven2018broadening}{}}%
+Gurven, M.
+D.
+(2018).
+Broadening horizons: Sample diversity and socioecological theory are essential to the future of psychological science.
+\emph{Proceedings of the National Academy of Sciences}, \emph{115}(45), 11420--11427.
+
+\leavevmode\vadjust pre{\hypertarget{ref-henrich2016secret}{}}%
+Henrich, J. (2016). \emph{The secret of our success: How culture is driving human evolution, domesticating our species, and making us smarter}. princeton University press.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hernik2019infant}{}}%
+Hernik, M., \& Broesch, T. (2019). Infant gaze following depends on communicative signals: An eye-tracking study of 5-to 7-month-olds in vanuatu. \emph{Developmental Science}, \emph{22}(4), e12779.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hessels2020does}{}}%
+Hessels, R. S. (2020). How does gaze to faces support face-to-face interaction? A review and perspective. \emph{Psychonomic Bulletin \& Review}, \emph{27}(5), 856--881.
+
+\leavevmode\vadjust pre{\hypertarget{ref-heyes2018cognitive}{}}%
+Heyes, C. (2018). \emph{Cognitive gadgets}. Harvard University Press.
+
+\leavevmode\vadjust pre{\hypertarget{ref-house2020universal}{}}%
+House, B.
+R., Kanngiesser, P., Barrett, H.
+C., Broesch, T., Cebioglu, S., Crittenden, A.
+N., Erut, A., Lew-Levy, S., Sebastian-Enesco, C., Smith, A.
+M., et al.
+(2020).
+Universal norm psychology leads to societal diversity in prosocial behaviour and development.
+\emph{Nature Human Behaviour}, \emph{4}(1), 36--44.
+
+\leavevmode\vadjust pre{\hypertarget{ref-itakura2004gaze}{}}%
+Itakura, S. (2004). Gaze-following and joint visual attention in nonhuman animals. In \emph{Japanese Psychological Research} (No. 3; Vol. 46, pp. 216--226). Wiley Online Library.
+
+\leavevmode\vadjust pre{\hypertarget{ref-itier2009neural}{}}%
+Itier, R. J., \& Batty, M. (2009). Neural bases of eye and gaze processing: The core of social cognition. \emph{Neuroscience \& Biobehavioral Reviews}, \emph{33}(6), 843--863.
+
+\leavevmode\vadjust pre{\hypertarget{ref-jensen2012bridging}{}}%
+Jensen, L. A. (2012). Bridging universal and cultural perspectives: A vision for developmental psychology in a global world. \emph{Child Development Perspectives}, \emph{6}(1), 98--104.
+
+\leavevmode\vadjust pre{\hypertarget{ref-kanngiesser2022children}{}}%
+Kanngiesser, P., Schäfer, M., Herrmann, E., Zeidler, H., Haun, D., \& Tomasello, M.
+(2022).
+Children across societies enforce conventional norms but in culturally variable ways.
+\emph{Proceedings of the National Academy of Sciences}, \emph{119}(1), e2112521118.
+
+\leavevmode\vadjust pre{\hypertarget{ref-kano2023evolution}{}}%
+Kano, F. (2023). Evolution of the uniformly white sclera in humans: Critical updates. \emph{Trends in Cognitive Sciences}, \emph{27}(1), 10--12.
+
+\leavevmode\vadjust pre{\hypertarget{ref-kano2014cross}{}}%
+Kano, F., \& Call, J. (2014). Cross-species variation in gaze following and conspecific preference among great apes, human infants and adults. \emph{Animal Behaviour}, \emph{91}, 137--150.
+
+\leavevmode\vadjust pre{\hypertarget{ref-kline2018variation}{}}%
+Kline, M.
+A., Shamsudheen, R., \& Broesch, T.
+(2018).
+Variation is the universal: Making cultural evolution work in developmental psychology.
+\emph{Philosophical Transactions of the Royal Society B: Biological Sciences}, \emph{373}(1743), 20170059.
 
 \leavevmode\vadjust pre{\hypertarget{ref-laland2021understanding}{}}%
-\CSLLeftMargin{2. }%
-\CSLRightInline{K. Laland, A. Seed, Understanding human cognitive uniqueness. \emph{Annual Review of Psychology} \textbf{72}, 689--716 (2021).}
+Laland, K., \& Seed, A. (2021). Understanding human cognitive uniqueness. \emph{Annual Review of Psychology}, \emph{72}, 689--716.
+
+\leavevmode\vadjust pre{\hypertarget{ref-langton2000eyes}{}}%
+Langton, S. R., Watt, R. J., \& Bruce, V. (2000). Do the eyes have it? Cues to the direction of social attention. \emph{Trends in Cognitive Sciences}, \emph{4}(2), 50--59.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lee2014bayesian}{}}%
+Lee, M. D., \& Wagenmakers, E.-J. (2014). \emph{Bayesian cognitive modeling: A practical course}. Cambridge University Press.
+
+\leavevmode\vadjust pre{\hypertarget{ref-legare2019development}{}}%
+Legare, C. H. (2019). The development of cumulative cultural learning. \emph{Annual Review of Developmental Psychology}, \emph{1}, 119--147.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lempers1979young}{}}%
+Lempers, J. D. (1979). Young children's production and comprehension of nonverbal deictic behaviors. \emph{The Journal of Genetic Psychology}, \emph{135}(1), 93--102.
+
+\leavevmode\vadjust pre{\hypertarget{ref-macdonald2013eye}{}}%
+Macdonald, R. G., \& Tatler, B. W. (2013). Do as eye say: Gaze cueing and language in a real-world social interaction. \emph{Journal of Vision}, \emph{13}(4), 6--6.
+
+\leavevmode\vadjust pre{\hypertarget{ref-mavridis2020development}{}}%
+Mavridis, P., Kärtner, J., Cavalcante, L.
+I.
+C., Resende, B., Schuhmacher, N., \& Köster, M.
+(2020).
+The development of context-sensitive attention in urban and rural brazil.
+\emph{Frontiers in Psychology}, \emph{11}, 1623.
+
+\leavevmode\vadjust pre{\hypertarget{ref-mayer2013synchrony}{}}%
+Mayer, A., \& Träuble, B.
+E.
+(2013).
+Synchrony in the onset of mental state understanding across cultures?
+A study among children in samoa.
+\emph{International Journal of Behavioral Development}, \emph{37}(1), 21--28.
+
+\leavevmode\vadjust pre{\hypertarget{ref-michel2021effects}{}}%
+Michel, C., Kayhan, E., Pauen, S., \& Hoehl, S.
+(2021).
+Effects of reinforcement learning on gaze following of gaze and head direction in early infancy: An interactive eye-tracking study.
+\emph{Child Development}, \emph{92}(4), e364--e382.
+
+\leavevmode\vadjust pre{\hypertarget{ref-miller2018contributions}{}}%
+Miller, J. G., Wice, M., \& Goyal, N. (2018). Contributions and challenges of cultural research on the development of social cognition. \emph{Developmental Review}, \emph{50}, 65--76.
+
+\leavevmode\vadjust pre{\hypertarget{ref-moll200412}{}}%
+Moll, H., \& Tomasello, M. (2004). 12-and 18-month-old infants follow gaze to spaces behind barriers. \emph{Developmental Science}, \emph{7}(1), F1--F9.
+
+\leavevmode\vadjust pre{\hypertarget{ref-moore2008development}{}}%
+Moore, C. (2008). The development of gaze following. \emph{Child Development Perspectives}, \emph{2}(2), 66--70.
+
+\leavevmode\vadjust pre{\hypertarget{ref-movellan2002development}{}}%
+Movellan, J.
+R., \& Watson, J.
+S.
+(2002).
+The development of gaze following as a bayesian systems identification problem.
+\emph{Proceedings 2nd International Conference on Development and Learning.
+ICDL 2002}, 34--40.
+
+\leavevmode\vadjust pre{\hypertarget{ref-mundy2007attention}{}}%
+Mundy, P., \& Newell, L. (2007). Attention, joint attention, and social cognition. \emph{Current Directions in Psychological Science}, \emph{16}(5), 269--274.
+
+\leavevmode\vadjust pre{\hypertarget{ref-nielsen2017persistent}{}}%
+Nielsen, M., Haun, D., Kärtner, J., \& Legare, C.
+H.
+(2017).
+The persistent sampling bias in developmental psychology: A call to action.
+\emph{Journal of Experimental Child Psychology}, \emph{162}, 31--38.
+
+\leavevmode\vadjust pre{\hypertarget{ref-norenzayan2005psychological}{}}%
+Norenzayan, A., \& Heine, S. J. (2005). Psychological universals: What are they and how can we know? \emph{Psychological Bulletin}, \emph{131}(5), 763.
+
+\leavevmode\vadjust pre{\hypertarget{ref-papadatou2020human}{}}%
+Papadatou-Pastou, M., Ntolka, E., Schmitz, J., Martin, M., Munafò, M.
+R., Ocklenburg, S., \& Paracchini, S.
+(2020).
+Human handedness: A meta-analysis.
+\emph{Psychological Bulletin}, \emph{146}(6), 481.
+
+\leavevmode\vadjust pre{\hypertarget{ref-prein2024measuring}{}}%
+Prein, J.
+C., Bednarski, F.
+M., Dzabatou, A., Frank, M.
+C., Henderson, A.
+M., Kalbitz, J., Kanngiesser, P., Keşşafoğlu, D., Koymen, B., Manrique-Hernandez, M., et al.
+(2024).
+\emph{Measuring variation in gaze following across communities, ages, and individuals---a showcase of the TANGO--CC}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-prein2024tango}{}}%
+Prein, J.
+C., Kalinke, S., Haun, D.
+B.
+M., \& Bohn, M.
+(2024).
+{TANGO}: {A} reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults.
+\emph{Behavior Research Methods}, \emph{56}(3), 2469--2485.
+\url{https://doi.org/10.3758/s13428-023-02159-5}
+
+\leavevmode\vadjust pre{\hypertarget{ref-prein2024variation}{}}%
+Prein, J.
+C., Maurits, L., Werwach, A., Haun, D.
+B.
+M., \& Bohn, M.
+(2024).
+Variation in gaze following across the life span: {A} process-level perspective.
+\emph{Developmental Science}, e13546.
+\url{https://doi.org/10.1111/desc.13546}
+
+\leavevmode\vadjust pre{\hypertarget{ref-r}{}}%
+R Core Team. (2023). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-richardson2005looking}{}}%
+Richardson, D.
+C., \& Dale, R.
+(2005).
+Looking to understand: The coupling between speakers' and listeners' eye movements and its relationship to discourse comprehension.
+\emph{Cognitive Science}, \emph{29}(6), 1045--1060.
+
+\leavevmode\vadjust pre{\hypertarget{ref-rosati2009looking}{}}%
+Rosati, A. G., \& Hare, B. (2009). Looking past the model species: Diversity in gaze-following skills across primates. \emph{Current Opinion in Neurobiology}, \emph{19}(1), 45--51.
+
+\leavevmode\vadjust pre{\hypertarget{ref-rossano2012gaze}{}}%
+Rossano, F. (2012). Gaze in conversation. \emph{The Handbook of Conversation Analysis}, 308--329.
+
+\leavevmode\vadjust pre{\hypertarget{ref-scaife1975capacity}{}}%
+Scaife, M., \& Bruner, J. S. (1975). The capacity for joint visual attention in the infant. \emph{Nature}, \emph{253}(5489), 265--266.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sebanz2006joint}{}}%
+Sebanz, N., Bekkering, H., \& Knoblich, G. (2006). Joint action: Bodies and minds moving together. \emph{Trends in Cognitive Sciences}, \emph{10}(2), 70--76.
+
+\leavevmode\vadjust pre{\hypertarget{ref-senju2015early}{}}%
+Senju, A., Vernetti, A., Ganea, N., Hudry, K., Tucker, L., Charman, T., \& Johnson, M.
+H.
+(2015).
+Early social experience affects the development of eye gaze processing.
+\emph{Current Biology}, \emph{25}(23), 3086--3091.
+
+\leavevmode\vadjust pre{\hypertarget{ref-shepherd2010following}{}}%
+Shepherd, S. V. (2010). Following gaze: Gaze-following behavior as a window into social cognition. \emph{Frontiers in Integrative Neuroscience}, \emph{4}, 5.
+
+\leavevmode\vadjust pre{\hypertarget{ref-stephenson2021gaze}{}}%
+Stephenson, L.
+J., Edwards, S.
+G., \& Bayliss, A.
+P.
+(2021).
+From gaze perception to social cognition: The shared-attention system.
+\emph{Perspectives on Psychological Science}, \emph{16}(3), 553--576.
+
+\leavevmode\vadjust pre{\hypertarget{ref-symons2004you}{}}%
+Symons, L. A., Lee, K., Cedrone, C. C., \& Nishimura, M. (2004). What are you looking at? Acuity for triadic eye gaze. \emph{The Journal of General Psychology}, \emph{131}(4), 451.
+
+\leavevmode\vadjust pre{\hypertarget{ref-tang2023slow}{}}%
+Tang, Y., Gonzalez, M. R., \& Deák, G. O. (2023). The slow emergence of gaze-and point-following: A longitudinal study of infants from 4 to 12 months. \emph{Developmental Science}, e13457.
+
+\leavevmode\vadjust pre{\hypertarget{ref-taumoepeau2019cross}{}}%
+Taumoepeau, M., Sadeghi, S., \& Nobilo, A.
+(2019).
+Cross-cultural differences in children's theory of mind in iran and new zealand: The role of caregiver mental state talk.
+\emph{Cognitive Development}, \emph{51}, 32--45.
+
+\leavevmode\vadjust pre{\hypertarget{ref-thorup2016altered}{}}%
+Thorup, E., Nyström, P., Gredebäck, G., Bölte, S., Falck-Ytter, T., \& Team, E.
+(2016).
+Altered gaze following during live interaction in infants at risk for autism: An eye tracking study.
+\emph{Molecular Autism}, \emph{7}, 1--10.
+
+\leavevmode\vadjust pre{\hypertarget{ref-thorup2018reduced}{}}%
+Thorup, E., Nyström, P., Gredebäck, G., Bölte, S., Falck-Ytter, T., \& Team, E.
+(2018).
+Reduced alternating gaze during social interaction in infancy is associated with elevated symptoms of autism in toddlerhood.
+\emph{Journal of Abnormal Child Psychology}, \emph{46}, 1547--1561.
+
+\leavevmode\vadjust pre{\hypertarget{ref-todorovic2006geometrical}{}}%
+Todorović, D. (2006). Geometrical basis of perception of gaze direction. \emph{Vision Research}, \emph{46}(21), 3549--3562.
+
+\leavevmode\vadjust pre{\hypertarget{ref-tomasello2020adaptive}{}}%
+Tomasello, M. (2020). The adaptive origins of uniquely human sociality. \emph{Philosophical Transactions of the Royal Society B}, \emph{375}(1803), 20190493.
+
+\leavevmode\vadjust pre{\hypertarget{ref-tomasello1998five}{}}%
+Tomasello, M., Call, J., \& Hare, B. (1998). Five primate species follow the visual gaze of conspecifics. \emph{Animal Behaviour}, \emph{55}(4), 1063--1069.
+
+\leavevmode\vadjust pre{\hypertarget{ref-tomasello2007reliance}{}}%
+Tomasello, M., Hare, B., Lehmann, H., \& Call, J.
+(2007).
+Reliance on head versus eyes in the gaze following of great apes and human infants: The cooperative eye hypothesis.
+\emph{Journal of Human Evolution}, \emph{52}(3), 314--320.
+
+\leavevmode\vadjust pre{\hypertarget{ref-tomasello2003makes}{}}%
+Tomasello, M., \& Rakoczy, H. (2003). What makes human cognition unique? From individual to shared to collective intentionality. \emph{Mind \& Language}, \emph{18}(2), 121--147.
+
+\leavevmode\vadjust pre{\hypertarget{ref-van2018development}{}}%
+Van Leeuwen, E.
+J., Cohen, E., Collier-Baker, E., Rapold, C.
+J., Schäfer, M., Schütte, S., \& Haun, D.
+B.
+(2018).
+The development of human social learning across seven societies.
+\emph{Nature Communications}, \emph{9}(1), 2076.
 
 \leavevmode\vadjust pre{\hypertarget{ref-wellman2014making}{}}%
-\CSLLeftMargin{3. }%
-\CSLRightInline{H. M. Wellman, \emph{Making Minds: How Theory of Mind Develops} (Oxford University Press, 2014).}
+Wellman, H. M. (2014). \emph{Making minds: How theory of mind develops}. Oxford University Press.
 
-\leavevmode\vadjust pre{\hypertarget{ref-henrich2016secret}{}}%
-\CSLLeftMargin{4. }%
-\CSLRightInline{J. Henrich, \emph{The Secret of Our Success: How Culture Is Driving Human Evolution, Domesticating Our Species, and Making Us Smarter} (princeton University press, 2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-tomasello2003makes}{}}%
-\CSLLeftMargin{5. }%
-\CSLRightInline{M. Tomasello, H. Rakoczy, What makes human cognition unique? From individual to shared to collective intentionality. \emph{Mind \& language} \textbf{18}, 121--147 (2003).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-legare2019development}{}}%
-\CSLLeftMargin{6. }%
-\CSLRightInline{C. H. Legare, The development of cumulative cultural learning. \emph{Annual Review of Developmental Psychology} \textbf{1}, 119--147 (2019).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-shepherd2010following}{}}%
-\CSLLeftMargin{7. }%
-\CSLRightInline{S. V. Shepherd, Following gaze: Gaze-following behavior as a window into social cognition. \emph{Frontiers in integrative neuroscience} \textbf{4}, 5 (2010).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-tomasello2007reliance}{}}%
-\CSLLeftMargin{8. }%
-\CSLRightInline{M.
-Tomasello, B.
-Hare, H.
-Lehmann, J.
-Call, Reliance on head versus eyes in the gaze following of great apes and human infants: The cooperative eye hypothesis.
-\emph{Journal of human evolution} \textbf{52}, 314--320 (2007).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-scaife1975capacity}{}}%
-\CSLLeftMargin{9. }%
-\CSLRightInline{M. Scaife, J. S. Bruner, The capacity for joint visual attention in the infant. \emph{Nature} \textbf{253}, 265--266 (1975).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-tang2023slow}{}}%
-\CSLLeftMargin{10. }%
-\CSLRightInline{Y. Tang, M. R. Gonzalez, G. O. Deák, The slow emergence of gaze-and point-following: A longitudinal study of infants from 4 to 12 months. \emph{Developmental Science}, e13457 (2023).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-gredeback2010development}{}}%
-\CSLLeftMargin{11. }%
-\CSLRightInline{G.
-Gredebäck, L.
-Fikke, A.
-Melinder, The development of joint visual attention: A longitudinal study of gaze following during interactions with mothers and strangers.
-\emph{Developmental science} \textbf{13}, 839--848 (2010).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-byers2021development}{}}%
-\CSLLeftMargin{12. }%
-\CSLRightInline{K.
-Byers-Heinlein, R.
-K.-Y.
-Tsui, D.
-Van Renswoude, A.
-K.
-Black, R.
-Barr, A.
-Brown, M.
-Colomer, S.
-Durrant, A.
-Gampe, N.
-Gonzalez-Gomez, others, The development of gaze following in monolingual and bilingual infants: A multi-laboratory study.
-\emph{Infancy} \textbf{26}, 4--38 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-brooks2005development}{}}%
-\CSLLeftMargin{13. }%
-\CSLRightInline{R. Brooks, A. N. Meltzoff, The development of gaze following and its relation to language. \emph{Developmental science} \textbf{8}, 535--543 (2005).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-carpenter1998social}{}}%
-\CSLLeftMargin{14. }%
-\CSLRightInline{M.
-Carpenter, K.
-Nagell, M.
-Tomasello, G.
-Butterworth, C.
-Moore, Social cognition, joint attention, and communicative competence from 9 to 15 months of age.
-\emph{Monographs of the society for research in child development}, i--174 (1998).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hernik2019infant}{}}%
-\CSLLeftMargin{15. }%
-\CSLRightInline{M.
-Hernik, T.
-Broesch, Infant gaze following depends on communicative signals: An eye-tracking study of 5-to 7-month-olds in vanuatu.
-\emph{Developmental science} \textbf{22}, e12779 (2019).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-callaghan2011early}{}}%
-\CSLLeftMargin{16. }%
-\CSLRightInline{T.
-Callaghan, H.
-Moll, H.
-Rakoczy, F.
-Warneken, U.
-Liszkowski, T.
-Behne, M.
-Tomasello, W.
-A.
-Collins, Early social cognition in three cultural contexts.
-\emph{Monographs of the society for research in child development}, i--142 (2011).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-prein2023tango}{}}%
-\CSLLeftMargin{17. }%
-\CSLRightInline{J.
-C.
-Prein, S.
-Kalinke, D.
-B.
-Haun, M.
-Bohn, TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults.
-\emph{Behavior Research Methods}, 1--17 (2023).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-prein2023variation}{}}%
-\CSLLeftMargin{18. }%
-\CSLRightInline{J.
-C.
-Prein, L.
-Maurits, A.
-Werwach, D.
-B.
-M.
-Haun, M.
-Bohn, Variation in gaze understanding across the life span: {A} process-level perspective.
-\emph{{PsyArXiv}}, doi: \href{https://doi.org/10.31234/osf.io/dy73a}{10.31234/osf.io/dy73a} (2023).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-barresi1996intentional}{}}%
-\CSLLeftMargin{19. }%
-\CSLRightInline{J. Barresi, C. Moore, Intentional relations and social understanding. \emph{Behavioral and brain sciences} \textbf{19}, 107--122 (1996).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-perner1994theory}{}}%
-\CSLLeftMargin{20. }%
-\CSLRightInline{J. Perner, T. Ruffman, S. R. Leekam, Theory of mind is contagious: You catch it from your sibs. \emph{Child Development} \textbf{65}, 1228--1238 (1994).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rakoczy2022foundations}{}}%
-\CSLLeftMargin{21. }%
-\CSLRightInline{H. Rakoczy, Foundations of theory of mind and its development in early childhood. \emph{Nature Reviews Psychology} \textbf{1}, 223--235 (2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-lewis1996social}{}}%
-\CSLLeftMargin{22. }%
-\CSLRightInline{C.
-Lewis, N.
-H.
-Freeman, C.
-Kyriakidou, K.
-Maridaki-Kassotaki, D.
-M.
-Berridge, Social influences on false belief access: Specific sibling influences or general apprenticeship?
-\emph{Child development} \textbf{67}, 2930--2947 (1996).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ruffman1998older}{}}%
-\CSLLeftMargin{23. }%
-\CSLRightInline{T.
-Ruffman, J.
-Perner, M.
-Naito, L.
-Parkin, W.
-A.
-Clements, Older (but not younger) siblings facilitate false belief understanding.
-\emph{Developmental psychology} \textbf{34}, 161 (1998).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rosati2009looking}{}}%
-\CSLLeftMargin{24. }%
-\CSLRightInline{A. G. Rosati, B. Hare, Looking past the model species: Diversity in gaze-following skills across primates. \emph{Current opinion in neurobiology} \textbf{19}, 45--51 (2009).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-tomasello1998five}{}}%
-\CSLLeftMargin{25. }%
-\CSLRightInline{M. Tomasello, J. Call, B. Hare, Five primate species follow the visual gaze of conspecifics. \emph{Animal behaviour} \textbf{55}, 1063--1069 (1998).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-itakura2004gaze}{}}%
-\CSLLeftMargin{26. }%
-\CSLRightInline{S. Itakura, Gaze-following and joint visual attention in nonhuman animals, \emph{Japanese Psychological Research}. \textbf{46} (2004)pp. 216--226.}
+\leavevmode\vadjust pre{\hypertarget{ref-yaniv1990heuristics}{}}%
+Yaniv, I., \& Shatz, M. (1990). Heuristics of reasoning and analogy in children's visual perspective taking. \emph{Child Development}, \emph{61}(5), 1491--1501.
 

### 2024-10-18 supplement/supplement.Rmd
paper long version review 1

@@
 
-# Participants
-
-```{r demtable, echo=F}
-demtab <- data %>%
-  separate(community, into = c("community", "country"), sep = " \\(")%>%
-  mutate(country = str_remove(country, "\\("),
-         country = str_remove(country, "\\)"))%>%
-  distinct(subjid, .keep_all = T)%>%
-  group_by(community, country, continent)%>%
-  summarise(N = n_distinct(subjid), 
-            m = sum(sex == "m", na.rm = T), 
-            mean_age = mean(ageinyears),
-            min_age = min(ageinyears), 
-            max_age = max(ageinyears))%>%
-  mutate_if(is.numeric, format, digits = 2, nsmall = 2)%>%
-  mutate(age = paste(mean_age, " (", min_age, " - ", max_age, ")"))%>%
-  select(-c(mean_age, min_age, max_age))%>%
-  arrange(continent)
-
-kableExtra::kable(demtab,
-             col.names = c("Community", "Country", "Continent", "N", "Sex (male)", "Age (range)"),
-              caption = "Participant demographics.", 
-             format="latex", booktabs=TRUE
-             )
-```
-
-```{r}
-# page <- data%>%
-#   group_by(community,continent)%>%
-#   distinct(subjid, .keep_all = T)%>%
-#   mutate(dens = approxfun(density(ageinyears))(ageinyears))%>%
-#   ggplot(aes(y = community, x = ageinyears))+
-#   #facet_grid(continent~., scales = "free", space = "free_y")+
-#   geom_density_ridges(
-#     jittered_points = TRUE,
-#     position = position_points_jitter(width = 0, height = 0),
-#     point_shape = '|',  point_alpha = 0.5, alpha = 0.7,
-#   )+
-#   labs(x = "Age (in years)", y= "")+
-#   theme_few()+
-#   theme(strip.background = element_blank(),strip.text.y = element_blank())
-# 
-# pred_agg_i <- data%>%
-#   mutate(older_children = children - 1 - younger_children)%>%
-#   group_by(community, subjid)%>%
-#   summarise(screen = mean(screen, na.rm = T),
-#             touchscreen = mean(touchscreen, na.rm = T),
-#             older_children = mean(older_children, na.rm = T),
-#             household = mean(household, na.rm = T))
-# 
-# pred_agg_g <- data%>%
-#   mutate(older_children = children - 1 - younger_children)%>%
-#   group_by(community, continent)%>%
-#   summarise(screen = mean(screen, na.rm = T),
-#             touchscreen = mean(touchscreen, na.rm = T),
-#             older_children = mean(older_children, na.rm = T),
-#             younger_children = mean(younger_children, na.rm = T),
-#             children = mean(children, na.rm = T),
-#             household = mean(household, na.rm = T))%>%
-#   pivot_longer(names_to = "dem", values_to = "value", cols = c(screen, touchscreen, older_children,children, younger_children, household))
-# 
-# ppred <- pred_agg_g%>%
-#   filter(dem == "screen" | dem == "touchscreen")%>%
-#   ggplot(aes(y = community, x = dem, fill = value))+
-#   geom_point(pch = 22, size = 10, stroke = 0)+
-#   #facet_grid(continent~., scales = "free", space = "free_y")+
-#   labs(x = "", y= "")+
-#   scale_fill_viridis_c(name = "Prevalence")+
-#   theme_few()+
-#   scale_x_discrete(guide = guide_axis(n.dodge = 2))+
-#   theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), strip.text.y.right = element_text(angle = 0))
-```
-
-A total of `r sum(as.numeric(demtab$N))` children between `r round(min(data$ageinyears), 2)` and `r round(max(data$ageinyears), 2)` provided data for the study.
-Children lived in `r n_distinct(data$community)` different communities, located in `r n_distinct(demtab$country)` different countries.
-Table \@ref(tab:demtable) gives the sample size per community together with some basic demographic information.
-The recruitment strategy for each community is reported in the respective site descriptions.
-Figure \@ref(fig:figpred1)A shows the age distribution in each setting.
-For some children, the exact birthday was unknown.
-In such cases, we set the birthday to the 30th of June of the year that would make them fall into the reported age category.
-
-Data from children was only included in the study when they contributed at least four valid test trials.
-We also excluded the data from children with a diagnosed developmental disorder.
-In sum, in addition to the sample size reported above, 74 additional children participated in the study but did not contribute data.
-The main reasons for exclusion were: contribution of less than four valid test trials, technical failures, and missing or implausible demographic information (e.g., when the number of children living in the household was reported to be larger than the household itself or when the number of children reported to live in the household equaled the number of children younger than the child being tested).
-We did not exclude any participants for performance reasons.
-A detailed description of each site and the way children were recruited can be found in the respective site description.
-
-```{r figpred1, include = T, fig.align = "center", fig.cap = "A) Age distribution and B) prevalence of different types of technology by community.
-Left: dots show individual data points.
-Right: color shows the proportion of children with access to screens or touchscreens.", out.width="100%"}
-# techpred <- plot_grid(page, ppred, rel_widths = c(1, 0.5),align = "h", labels = c("A", "B"))
-# 
-# ggsave(plot = techpred, "../figures/techpred.png",  height = 7, width = 10, scale = 1)
-
-knitr::include_graphics("../figures/techpred.png")
-
-```
-
-## Site descriptions
+# Overview
+
+This document supplements the paper "A universal of human social cognition: Children from 17 communities process gaze in similar ways".
+Some text passages and figures are the same in the supplementary material and the main paper.
+This redundancy is intended and ensures that the supplementary material is self-contained and readable.
+
+This document is structured as follows: we first provide a detailed description of the different [study sites](#site-descriptions), inlcuding information about geography, history, subsistence, socialization goals and recruitment strategy.
+Next we summarize the resulting [sample](#participants).
+Then we go on to provide additional details about the [methods](#method) and the [analysis and results](#analysis-and-results).
+The online version in the repository (`.Rmd` file) includes the analysis code for the analysis reported in the paper and the supplementary material.
+In the [appendix](#appendix) we provide the English version of the voice overs children heard during the study.
+
+# Site descriptions
 
@@
 
+# Participants
+
+```{r demtable, echo=F}
+demtab <- bind_rows(
+
+data %>%
+  separate(community, into = c("community", "country"), sep = " \\(")%>%
+  mutate(country = str_remove(country, "\\("),
+         country = str_remove(country, "\\)"))%>%
+  distinct(subjid, .keep_all = T)%>%
+  group_by(community, country, continent)%>%
+  summarise(N = n_distinct(subjid), 
+            m = sum(sex == "m", na.rm = T), 
+            mean_age = mean(ageinyears),
+            min_age = min(ageinyears), 
+            max_age = max(ageinyears))%>%
+  mutate_if(is.numeric, format, digits = 2, nsmall = 2)%>%
+  mutate(age = paste(mean_age, " (", min_age, " - ", max_age, ")"),
+         age_group = "total")%>%
+  select(-c(mean_age, min_age, max_age)),
+
+data %>%
+  separate(community, into = c("community", "country"), sep = " \\(")%>%
+  mutate(country = str_remove(country, "\\("),
+         country = str_remove(country, "\\)"))%>%
+  distinct(subjid, .keep_all = T)%>%
+  group_by(community, country, continent, age_group)%>%
+  summarise(N = n_distinct(subjid),
+            m = sum(sex == "m", na.rm = T))%>%
+  mutate(age_group = paste0(age_group, " years"))%>%
+  mutate_if(is.numeric, format, digits = 2, nsmall = 2)
+
+)%>%
+  arrange(continent, community)%>%
+  select(continent, country, community, age_group, N, m, age)%>%
+  ungroup()%>%
+  mutate(continent = as.character(continent),
+         country = replace(country, duplicated(country), " "),
+         community = replace(community, duplicated(community), " "),
+         continent = replace(continent, duplicated(continent), " "))
+
+kableExtra::kable(demtab,
+             col.names = c("Continent","Country","Community", "Age group","N", "Sex (male)", "Age (range)"),
+              caption = "Participant demographics.", 
+             format="latex", booktabs=TRUE, longtable = TRUE
+             )%>%
+  kable_styling(latex_options = c("hold_position", "repeat_header"))
+```
+
+```{r}
+# page <- data%>%
+#   group_by(community,continent)%>%
+#   distinct(subjid, .keep_all = T)%>%
+#   mutate(dens = approxfun(density(ageinyears))(ageinyears))%>%
+#   ggplot(aes(y = community, x = ageinyears))+
+#   #facet_grid(continent~., scales = "free", space = "free_y")+
+#   geom_density_ridges(
+#     jittered_points = TRUE,
+#     position = position_points_jitter(width = 0, height = 0),
+#     point_shape = '|',  point_alpha = 0.5, alpha = 0.7,
+#   )+
+#   labs(x = "Age (in years)", y= "")+
+#   theme_few()+
+#   theme(strip.background = element_blank(),strip.text.y = element_blank())
+# 
+# pred_agg_i <- data%>%
+#   mutate(older_children = children - 1 - younger_children)%>%
+#   group_by(community, subjid)%>%
+#   summarise(screen = mean(screen, na.rm = T),
+#             touchscreen = mean(touchscreen, na.rm = T),
+#             older_children = mean(older_children, na.rm = T),
+#             household = mean(household, na.rm = T))
+# 
+# pred_agg_g <- data%>%
+#   mutate(older_children = children - 1 - younger_children)%>%
+#   group_by(community, continent)%>%
+#   summarise(screen = mean(screen, na.rm = T),
+#             touchscreen = mean(touchscreen, na.rm = T),
+#             older_children = mean(older_children, na.rm = T),
+#             younger_children = mean(younger_children, na.rm = T),
+#             children = mean(children, na.rm = T),
+#             household = mean(household, na.rm = T))%>%
+#   pivot_longer(names_to = "dem", values_to = "value", cols = c(screen, touchscreen, older_children,children, younger_children, household))
+# 
+# ppred <- pred_agg_g%>%
+#   filter(dem == "screen" | dem == "touchscreen")%>%
+#   ggplot(aes(y = community, x = dem, fill = value))+
+#   geom_point(pch = 22, size = 10, stroke = 0)+
+#   #facet_grid(continent~., scales = "free", space = "free_y")+
+#   labs(x = "", y= "")+
+#   scale_fill_viridis_c(name = "Prevalence")+
+#   theme_few()+
+#   scale_x_discrete(guide = guide_axis(n.dodge = 2))+
+#   theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), strip.text.y.right = element_text(angle = 0))
+```
+
+A total of `r sum(as.numeric(demtab$N))` children between `r round(min(data$ageinyears), 2)` and `r round(max(data$ageinyears), 2)` provided data for the study.
+Children lived in `r n_distinct(data$community)` different communities, located in `r n_distinct(demtab$country)` different countries.
+Table \@ref(tab:demtable) gives the sample size per community together with some basic demographic information.
+The recruitment strategy for each community is reported in the respective site description above.
+Figure \@ref(fig:figpred1)A shows the age distribution in each setting.
+For some children, the exact birthday was unknown.
+In such cases, we set the birthday to the 30th of June of the year that would make them fall into the reported age category.
+
+Data from children was only included in the study when they contributed at least four valid test trials.
+We also excluded the data from children with a diagnosed developmental disorder.
+In sum, in addition to the sample size reported above, 74 additional children participated in the study but did not contribute data.
+The main reasons for exclusion were: contribution of less than four valid test trials, technical failures, and missing or implausible demographic information (e.g., when the number of children living in the household was reported to be larger than the household itself or when the number of children reported to live in the household equaled the number of children younger than the child being tested).
+We did not exclude any participants for performance reasons.
+A detailed description of each site and the way children were recruited can be found in the respective site description.
+
+```{r figpred1, include = T, fig.align = "center", fig.cap = "A) Age distribution and B) prevalence of different types of technology by community.
+Left: dots show individual data points.
+Right: color shows the proportion of children with access to screens or touchscreens.", out.width="100%"}
+# techpred <- plot_grid(page, ppred, rel_widths = c(1, 0.5),align = "h", labels = c("A", "B"))
+# 
+# ggsave(plot = techpred, "../figures/techpred.png",  height = 7, width = 10, scale = 1)
+
+knitr::include_graphics("../figures/techpred.png")
+
+```
+
 # Method
 
-We adapted the task developed by Prein and colleagues [@prein2023tango].
+We adapted the task developed by Prein and colleagues [@prein2024tango].
 We refer to the original publication for a detailed description of its development, implementation and psychometric evaluation (in Germany).
@@
 
-# Analysis
+# Analysis and results
 
@@
 
-We pre-registered an analysis plan at <!--https://osf.io/tdsvc/?view_only=f404d66c967542f28ce4af16371f34e6-->https://osf.io/tdsvc.
-The analyses reported below follow the same logic as the pre-registered analyses but they differ substantially in detail.
-The main difference lies in the random effects structure we used in the models.
-In the pre-registration, we did not include random slopes for target centrality (i.e.
-the distance of the location where the balloon landed from the center of the screen), neither within subject nor within cultural setting.
-Instead, we included random slopes for trial within subject.
-We decided to change this and remove random slopes for trial but include them for target centrality.
-The reasons were as follows: trial effects in the sense of learning across trials were unlikely because participants did not receive differential feedback.
-Furthermore, in multiple studies with the same task since the registration we never found any trial effects [@prein2023tango; @prein2023variation].
-We therefore removed trial from the models completely.
-On the other hand, we included random slopes for target centrality to be able to look at cross-cultural variation.
-The cognitive model was not mentioned in the pre-registration because it is a more recent development [see @prein2023variation].
-
 ## Cross-cultural variation
@@
 ```{r}
-# mdata <- data%>%
-#   ungroup()%>%
-#   mutate(ageinyears = as.numeric(scale(ageinyears)),
-#          targetcentralityx = as.numeric(scale(targetcentralityx)),
-#          click = abs(clickdistfromtargetcenterx))
+mdata <- data%>%
+  ungroup()%>%
+  mutate(ageinyears = as.numeric(scale(ageinyears)),
+         targetcentralityx = as.numeric(scale(targetcentralityx)),
+         click = abs(clickdistfromtargetcenterx))
 
@@
 That is, the further away from the center the balloon lands, the more imprecise should participants be.
-This second signature is derived from the cognitive model introduced in @prein2023variation.
+This second signature is derived from the cognitive model introduced in @prein2024variation.
 It predicts that trials in which the agent looks further away from the center (i.e., to the left or right side of the screen) result in higher levels of imprecision compared to trials in which the agent looks closer to the middle.
@@
 ```{r}
+side_bias <- data%>%
+  mutate(side = ifelse(targetcenterx < 960, "left", "right"),
+         error = ifelse(clickdistfromtargetcenterx < 0, "left", "right"))%>%
+  group_by(side)%>%
+  summarise(left_bias = mean(error == "left"),
+            right_bias = mean(error == "right"))
+```
+
+Visualization of the data also showed the predicted u-shaped pattern in all communities (see Fig.
+\@ref(fig:figdev)C).
+The visualization also showed that the u shape is not symmetric.
+Instead, imprecision was higher when the target landed on the left side of the screen.
+One potential explanation for this pattern could be the wide-spread dominance of right-handedness.
+Remember that participants had a general center bias, that is, they were more likely to touch the screen to the side of the object that was closer to the center.
+Now, when touching a location on the left side of the screen, right-handed participants need to cross their hand in front of their body and might be inclined to touch the screen slightly further to the right compared to when the target lands on the right side of the screen.
+This might amplify the center bias.
+In the data, we saw that when the target landed on the left side of the screen, `r round(side_bias%>%filter(side == "left")%>%pull(right_bias),2)*100`% of touches were to the right of the target and closer to the center of the screen.
+On the other hand, when the target landed on the right, `r round(side_bias%>%filter(side == "right")%>%pull(left_bias),2)*100`% of touches were left of the target and closer to the center.
+A center bias alone would have predicted these numbers to be the same.
+
+```{r}
 # devdata <- data%>%
@@
 # plot_grid(
-#   pagg_dev, pind, rel_widths = c(1,1.5), align = "h", axis = "bt",labels = c("A", "B")
+#   pagg_dev, pind, rel_widths = c(1,1.75), align = "h", axis = "bt",labels = c("A", "B")
 # ),
 # plot_grid(
-#   ptagg, ptind, rel_widths = c(1,1.5), align = "h", axis = "bt", labels = c("C", "D")
+#   ptagg, ptind, rel_widths = c(1,1.75), align = "h", axis = "bt", labels = c("C", "D")
 # ), nrow = 2, align = "v"
@@
 
-The vector-based gaze estimation model has been described in detail in @prein2023variation.
+The vector-based gaze estimation model has been described in detail in @prein2024variation.
 In brief, it inversely models the process generating clicks based on observed eye movements.
@@
 #              control = list(adapt_delta = 0.95),
-#              backend = "cmdstanr",
-#              threads = threading(8)
+#              #backend = "cmdstanr",
+#              #threads = threading(8)
 #              )%>%
@@
 #              control = list(adapt_delta = 0.95),
-#              backend = "cmdstanr",
-#              threads = threading(8))%>%
+#              #backend = "cmdstanr",
+#              #threads = threading(8)
+#              )%>%
 #   add_criterion(., c("waic","loo"))
@@
 #                               cores  = 4,
-#              control = list(adapt_delta = 0.95),
-#              backend = "cmdstanr",
-#              threads = threading(8)
+#              control = list(adapt_delta = 0.95)#,
+#              #backend = "cmdstanr",
+#              #threads = threading(8)
 #              )%>%
@@
 #                               cores  = 4,
-#              control = list(adapt_delta = 0.95),
-#              backend = "cmdstanr",
-#              threads = threading(8)
+#              control = list(adapt_delta = 0.95)#,
+#              #backend = "cmdstanr",
+#              #threads = threading(8)
 #              )%>%
 #   add_criterion(., c("waic","loo"))
-# 
+
 # bm_pred_tc_rand <- brm(mean_click ~ ageinyears + touchscreen + (touchscreen + ageinyears |community),
@@
 The final analysis focused on whether we could predict performance in the task by aspects of everyday experience.
-For the ease of model fitting, we aggregated the data for each participant so that models predicted the average imprecision across trials [@prein2023variation showed that the performance mean is nearly perfectly correlated with $\sigma_v$.
+For the ease of model fitting, we aggregated the data for each participant so that models predicted the average imprecision across trials [@prein2024variation showed that the performance mean is nearly perfectly correlated with $\sigma_v$.
 When re-running the winning model on the trial-by-trial data, the results were qualitatively and quantitatively identical.].
@@
 ```{r predcomptable, echo=F}
-pred_mocel_comp <- readRDS("../saves/model_comp.rds")%>%
+pred_model_comp <- readRDS("../saves/model_comp.rds")%>%
   mutate_if(is.numeric, format, digits = 2, nsmall = 2)%>%
@@
                         bm_pred_tc = "touchscreen",
-                        bm_pred_tc_hh = "household",
-                        bm_pred_tc_c = "children",
-                        bm_pred_tc_yc = "younger children",
+                        bm_pred_tc_hh = "touchscreen + household",
+                        bm_pred_tc_c = "touchscreen + children",
+                        bm_pred_tc_yc = "touchscreen + younger children",
                         bm_pred_tc_rand = "touchscreen (by culture)"))
 
-kableExtra::kable(pred_mocel_comp,
-             col.names = c("Model","diff\\textsubscript{WAIC}", "diff\\textsubscript{SE}", "WAIC", "SE", "Weight"),
-             caption = "Log Bayes Factors in favor of the gaze model compared to two alternative models.",
+kableExtra::kable(pred_model_comp,
+             col.names = linebreak(c("Model","diff\\textsubscript{WAIC}", "diff\\textsubscript{SE}", "WAIC", "SE\\textsubscript{WAIC}", "Weight")),
+             caption = "Comparison of models predicting individual-level variation.",
              format="latex", booktabs=TRUE, escape = F
              )
-
 ```
@@
 Table \@ref(tab:predcomptable) shows that the model predicting average imprecision by the availability of touchscreens performed best and better than any of the models including a predictor referring to household composition.
-However, the difference between the models was very small (`ELPD` < 1, see Table \@ref(tab:predcomptable)), suggesting that they are largely equivalent, and, for the sake of consistency, we therefore inspected the posterior estimates for household composition predictors nevertheless.
+However, the difference between the models was very small ($diff_{ELPD}$ < 1, see Table \@ref(tab:predcomptable)), suggesting that they are largely equivalent, and, for the sake of consistency, we therefore inspected the posterior estimates for household composition predictors nevertheless.
 
@@
 pred_est <- readRDS("../saves/pred_est.rds")
+```
+
+```{r}
+# pred_est_sc <- 
+#   bind_rows(
+#   fixef(bm_pred_tc_hh)%>%
+#   as_tibble(rownames = "term")%>%
+#   filter(term == "household")%>%
+#   mutate_if(is.numeric,round, 2),
+#   
+#     fixef(bm_pred_tc_c)%>%
+#   as_tibble(rownames = "term")%>%
+#   filter(term == "children")%>%
+#   mutate_if(is.numeric,round, 2),
+#   
+#     fixef(bm_pred_tc_yc)%>%
+#   as_tibble(rownames = "term")%>%
+#   filter(term == "younger_children")%>%
+#   mutate_if(is.numeric,round, 2)
+#   
+#   )
+# 
+# saveRDS(pred_est_sc, "../saves/pred_est_sc.rds")
+# 
+# pred_est_sc <- readRDS("../saves/pred_est_sc.rds")
 ```

### 2024-10-19 paper/paper.Rmd
paper long version review 1

@@
   Theoretical accounts assume that key features of human social cognition are universal.
-Here we focus on gaze following, the bedrock of social interactions and coordinated activities, to test this claim.
-In a comprehensive cross-cultural study spanning five continents and 17 distinct cultural communities, we examined the development of gaze following in early childhood.
-We identified key processing signatures through a computational model that assumes that participants follow an individual’s gaze by estimating a vector emanating from the eye center through the pupil.
-We found these signatures in all communities, suggesting that children worldwide processed gaze in highly similar ways.
-Absolute differences between groups were accounted for by a cross-culturally consistent relationship between children’s exposure to touchscreens and their performance in the task.
-These results provide strong evidence for a universal process underlying a foundational socio-cognitive ability in humans that can be reliably inferred even in the presence of cultural variation in overt behavior.
+The present study presents a comprehensive cross-cultural study (17 cultural communities, five continents, N = 1377, 709 female,  mean = 5.50 years ) on gaze following in early childhood.
+To test for universality, a cognitive processing signature was derived from a computational model that treats gaze following as social vector estimation.
+Results showed substantial variation between communities and individuals.
+Importantly, the processing signature was found in all communities.
+Individual differences in performance were related to individual-level measures of familiarity with the data collection device but not opportunities for social interaction.
+These results provide strong evidence for a universal cognitive process that can be inferred despite cultural variation in overt behavior.
 
@@
 output            :
-  papaja::apa6_pdf:
+  papaja::apa6_docx:
     latex_engine: xelatex
@@
 
-Human socio-cognitive skills enable unique forms of communication and cooperation that provide a bedrock for cumulative culture and the formation of complex societies [@tomasello2020adaptive; @laland2021understanding; @wellman2014making; @henrich2016secret; @tomasello2003makes; @legare2019development; @heyes2018cognitive].
-The eyes are the proverbial "window to the mind" and eye gaze is essential for many social reasoning processes [@shepherd2010following; @doherty2006development; @emery2000eyes; @frischen2007gaze].
+Human socio-cognitive skills enable unique forms of communication and cooperation that provide a bedrock for cumulative culture and the formation of complex societies [@laland2021understanding; @wellman2014making; @henrich2016secret; @tomasello2003makes; @legare2019development; @heyes2018cognitive].
+Eye gaze is essential for many social reasoning processes, making the eyes the proverbial ''window to the mind'' [@shepherd2010following; @doherty2006development; @emery2000eyes; @frischen2007gaze].
 Others’ eye gaze is used to infer their focus of visual attention, which is a critical aspect of coordinated activities, including communication and cooperation [@tomasello2007reliance; @scaife1975capacity; @langton2000eyes; @rossano2012gaze; @richardson2005looking; @sebanz2006joint].
@@
 
-The studies reported thus far, relied on data collected in western affluent settings.
-Such settings represent only a minority of the worlds population and are thus insufficient to make claims about universal aspects of human cognition [@nielsen2017persistent; @norenzayan2005psychological; @amir2020cross; @barrett2020towards].
-Three studies with infants and children from traditionally underrepresented parts of the world (Bhutan, India, Peru, Vanuatu) find that even though children start gaze following (gaze and head direction combined) at similar ages, the rates of gaze following differ between cultural settings [@hernik2019infant; @astor2022maternal; @callaghan2011early].
+The studies reported thus far, relied on data collected in western affluent communitites.
+Such communitites represent only a minority of the worlds population and are thus insufficient to make claims about universal aspects of human cognition [@nielsen2017persistent; @norenzayan2005psychological; @amir2020cross; @barrett2020towards].
+Three studies with infants and children from traditionally underrepresented parts of the world (Bhutan, India, Peru, Vanuatu) find that even though children start gaze following (gaze and head direction combined) at similar ages, the rates of gaze following differ between cultural communitites [@hernik2019infant; @astor2022maternal; @callaghan2011early].
 
-Rates and accuracy of gaze following do not just differ between cultural settings; there is also substantial variation within settings.
+Rates and accuracy of gaze following do not just differ between cultural communitites; there is also substantial variation within communitites.
 In fact, the pivotal role of gaze following in many uniquely human activities has been studied by relating individual differences in gaze following to other phenomena -- both cross-sectionally and longitudinally [@carpenter1998social; @brooks2015connecting].
 For example, gaze following at 10 months predicts language scores at 18 months of age [@brooks2005development; @macdonald2013eye].
-Furthermore, difficulties with gaze following have been linked to developmental disorders, including Autism [@itier2009neural; @thorup2016altered; @thorup2018reduced] and -- at least in some cultural contexts -- to maternal postpartum depression [astor2022maternal].
-Individual differences are also key to explaining the -- mainly social-interactional -- driving forces behind the development of gaze following.
+Furthermore, difficulties with gaze following have been linked to developmental disorders, including Autism [@itier2009neural; @thorup2016altered] and -- at least in some cultural contexts -- to maternal postpartum depression [@astor2022maternal].
+Individual differences are also key to explaining the driving forces behind the development of gaze following.
 For example, it has been found that early attachment quality or the use of gaze in communicative interactions predict later rates of gaze following [@astor2020social; @movellan2002development; @senju2015early].
@@
 
-The existence of variation in gaze following both within and between cultural settings raises the question of how to square these findings with the suggestion that gaze following is a fundamental building block of human social cognition and interaction and that eye movements are processed the same way in humans all over the world.
-Looking at other aspects of social cognition, one could easily make the argument that variation is the norm rather than the exception [see e.g., @miller2018contributions; @wellman2014making; @mayer2013synchrony; @dixson2018scaling; @taumoepeau2019cross].
-As a first step, answering this question requires data from many different cultural settings.
+The existence of variation in gaze following both within and between cultural communitites raises the question of how to square these findings with the suggestion that gaze following is a fundamental building block of human social cognition and interaction and that eye movements are processed the same way in humans all over the world.
+Looking at other aspects of social cognition, one could easily make the argument that variation is the norm rather than the exception [see e.g., @dixson2018scaling; @miller2018contributions; @wellman2014making; @mayer2013synchrony;  @taumoepeau2019cross].
+As a first step, answering this question requires data from many different cultural communitites.
 In a second step, however, we need a way of detecting universal processes in such data.
-The traditional approach is to compare some sort of aggregate measure (mean level of performance, average age of onset) across cultural settings.
+The traditional approach is to compare some sort of aggregate measure (mean level of performance, average age of onset) across cultural communitites.
 Absolute differences between communities are interpreted as a signal of different underlying cognitive processes while no differences are taken to support the existence of a psychological universal [@house2020universal; @van2018development; @blake2015ontogeny; @kanngiesser2022children].
@@
 
-For gaze following, we can use the computational model proposed by @prein2024variation to derive such predictions.
-They formalized the widely-held view that gaze following involves estimating some sort of vector emanating from the eye center through the pupil [@todorovic2006geometrical; @yaniv1990heuristics; @butterworth1991minds; @symons2004you].
+The computational model proposed by @prein2024variation can be used to derive such predictions for gaze following.
+They formalized the widely-held view that gaze following involves estimating some sort of line-of-sight vector emanating from the eye center through the pupil [@todorovic2006geometrical; @yaniv1990heuristics; @butterworth1991minds].
 The key innovation of the model is that it explains how individuals may use the same process but still differ in their measured abilities.
@@
 First, to collect a comprehensive data set and study the ontogeny of gaze following beyond infancy across cultures.
-To make this possible, we used a semi-standardized task that required minimal assistance from an experimenter and no behavioral coding.
+To make this possible, we used a semi-standardized task that required minimal assistance from an experimenter and no behavioral coding [TANGO-CC; @prein2024measuring].
 The task is an animated picture book presented on a tablet screen.
@@
 The key dependent variable was (im)precision, that is, the deviation between where the agent looked (where the balloon was) and the child’s response.
-The task's flexible implementation as a browser-based web-app allowed us to quickly tailor its visual and audio content to each cultural setting (visuals and audio).
+The task's flexible implementation as a browser-based web-app allowed us to quickly tailor its visual and audio content to each cultural community (visuals and audio).
+Adaptations were made by researchers or research assistants from the respective community.
 The task has been psychometrically evaluated and has shown to yield reliable individual-level measurements across communities and ages [@prein2024tango; @prein2024measuring].
 
-We collected data in 17 different communities across 14 countries and five continents.
+We collected data in 17 different communities across 14 countries and five continents  (see Figure \@ref(fig:fig1)A).
 Communities covered a broad spectrum of geographical locations, social and political systems, languages, and subsistence styles.
 This diversity allowed us to overcome a common pitfall of cross-cultural studies that compare urban communities from the Global North to rural communities from the Global South [@barrett2020towards].
-We aimed for large sample sizes within each community to contrast within- and between cultural variation.
+We aimed for large sample sizes within each community (n = 20 per year) to contrast within- and between cultural variation.
 Our expectation regarding the first goal was to see substantial variation across cultures but even more variation between individuals.
@@
 
-The second goals was to look for signatures in the data of the universal gaze following process predicted by the model of @prein2024measuring.
+The second goal was to look for signatures in the data of the universal gaze following process specified by the model of @prein2024variation.
 In the task, the hidden object lands on a horizontal plane at the lower end of the screen.
 The agent is located in the upper center of the screen (see Figure \@ref(fig:fig1)B).
-The model predicts that trials in which the object is hidden further away from the center to be more difficult, resulting in higher imprecision.
+The model predicts trials in which the object is hidden further away from the center to be more difficult, resulting in higher imprecision.
 The signature is thus a u-shaped relation between object location and imprecision (Figure \@ref(fig:fig12)).
@@
 Finally, we sought to explain individual differences in gaze following precision by linking them to methodological aspects of the study as well as aggregate measures of children's everyday social experience.
-Experience with tablets and touch screens co-varied with community and we expected children more familiar with this medium to perform better.
+Experience with tablets and touch screens co-varied with community and we expected children more familiar with this medium to perform better in any tablet-based task.
 Previous work suggested that gaze following is refined in social interaction [@movellan2002development; @senju2015early].
@@
 (B) Screenshots from the task.
-The upper scene depicts the start, and the lower scene depicts the choice phase in a test trial.
+The lower scene depicts the choice phase in a test trial.
 Participants had to use the gaze of the agent to locate the balloon and touch the location on the hedge where they thought the balloon was.
 Agents, audio recordings and backgrounds were adapted to each community.
-(C) Drawings used as agents across communities.", out.width="100%"}
+(C) Drawings used as agents across communities.
+Adaptations were made researchers or research assisstants from the respective community.", out.width="100%"}
 knitr::include_graphics("../figures/fig1_2.png")
@@
           caption = "Participant demographics.",
-          align = paste0("m{", 1/(ncol(tba1) + 1), "\\linewidth}"),
+          #align = paste0("m{", 1/(ncol(tba1) + 1), "\\linewidth}"),
           longtable = TRUE,
@@
 ```
-
-We used an animated picture book tablet task in which participants had to locate a hidden object based on observing an agent’s gaze.
-Children watched a balloon disappear behind a hedge.
-An agent followed the trajectory of the balloon with their eyes (Fig.
-\@ref(fig:fig1)B).
-The key dependent variable was the (im)precision with which children located the agent’s focus of attention, that is, the deviation between where the agent looked (where the balloon was) and the child’s response.
-We adapted visuals and audio instructions specifically for each of the 17 communities.
-Previous work demonstrated excellent individual-level measurement properties for this task in a German sample [@prein2024tango].
 
@@
 We achieved this goal for most ages in most communities, but not for all (see Supplementary Table 1).
-The analysis reported here deviated from the preregistration in the following ways: In the pre-registration, in the regression models, we did not include random slopes for target centrality (i.e.
-the distance of the location where the balloon landed from the center of the screen), neither within subject nor within cultural setting.
-Instead, we included random slopes for trial within subject.
-We decided to change this and remove random slopes for trial but include them for target centrality because trial effects in the sense of learning across trials were unlikely because participants did not receive differential feedback.
+For some communities, we also included older and younger children.
+The analysis reported here deviated from the preregistration in the following ways: In the preregistration, the regression models did not include random slopes for target centrality (i.e., the distance between the location where the balloon landed and the center of the screen), neither within subject nor within cultural setting.
+Instead, the preregistration included random slopes for trial within subject.
+We decided to remove random slopes for trial but include them for target centrality because trial effects in the sense of learning across trials were unlikely in the absence of differential feedback.
 Furthermore, multiple studies with the same task since the registration found no trial effects [@prein2024tango; @prein2024variation].
 On the other hand, we included random slopes for target centrality to be able to look at cross-cultural variation.
-The cognitive models were not mentioned in the pre-registration because it is a more recent development [@prein2024variation].
+We preregistered to run the cross-validation 1000 times but decided to scale down to 100 times because the procedure was computationally very intensive and the results very clear.
+The cognitive models were not mentioned in the preregistration because they were developed more recently [@prein2024variation].
 
@@
 
-All study materials <!--[masked for peer review] --> (https://ccp-odc.eva.mpg.de/tango-cc/), primary data and analysis scripts are publicly available <!--[masked for peer review; see .zip file included--> (https://github.com/ccp-eva/gafo-cc-analysis/).
+All study materials <!--[masked for peer review] --> (https://ccp-odc.eva.mpg.de/tango-cc/), primary data, and analysis scripts are publicly available <!--[masked for peer review; see .zip file included--> (https://github.com/ccp-eva/gafo-cc-analysis/).
 
@@
 In such cases, we set the birthday to the 30th of June of the year that would make them fall into the reported age category.
-We provide a detailed description of the sample characteristics, the study site and recruitment strategy for each community in the Supplementary Material.
+We provide a detailed description of the sample characteristics, the age distributions, the study sites and recruitment strategies for each community in the Supplementary Material.
+Samples were convenience samples in all communities.
 
 Data from children was only included in the study when they contributed at least four valid test trials.
-We also excluded the data from children with a diagnosed developmental disorder.
-In sum, in addition to the sample size reported above, 74 additional children participated in the study but did not contribute data.
+We also excluded the data from children when a developmental disorder was reported.
+In addition to the sample size reported above, 74 children participated in the study but did not contribute data.
 The main reasons for exclusion were: contribution of less than four valid test trials, technical failures, and missing or implausible demographic information (e.g., when the number of children living in the household was reported to be larger than the household itself or when the number of children reported to live in the household equaled the number of children younger than the child being tested).
 We did not exclude any participants for performance reasons.
-A detailed description of each data collection site and the way children were recruited can be found in the Supplementary Material.
 
@@
 Participants saw animated agents on a touch screen device, listened to pre-recorded audio instructions and responded by touching the screen.
-In all communities, a research assistant, fluent in the local language(s), guided the child through the task.
-That is, the research assistant guided the child through the introduction and advanced the study from trial to trial.
+In all communities, a research assistant, fluent in the local language(s), guided the child through the introduction and advanced the study from trial to trial.
 
@@
 That is, the pupils and the iris were programmed to align with the center of the balloon.
-Once the balloon had landed on the ground, the agent was instructed to locate it, that is, to touch the location on the screen where they thought the balloon was.
+Once the balloon had landed on the ground, the child was instructed to locate it, that is, to touch the location on the screen where they thought the balloon was.
 On each trial, we recorded the exact x-coordinate of the participant's touch.
@@
 Critically, the agent was described as wanting to help the child and always looking at the balloon.
+These instructions were added to clarify the purpose of the task, establish a clear common ground, and minimize learning effects over trials.
 
@@
 Thus, 15 test trials were used in the analysis below.
-Each child saw eight different agents (four male, four female).
+Each child saw eight different agents (four male, four female; selected by local researchers or research assistants).
 The agent changed from trial to trial, with alternating genders.
@@
 On each trial, one of the bins was randomly selected and the exact x-coordinate was randomly chosen within that bin.
-Constraints were that the balloon landed in each bin once in the first ten trials and, for the remaining six test trials, it landed in a different om each trial.
-Thus, each bin appeared a no more than twice.
+Constraints were that the balloon landed in each bin once in the first ten trials and, for the remaining six test trials, it landed in a different bin on each trial.
+Thus, each bin appeared no more than twice.
 
 All children were tested with a touchscreen device with a size between 11 and 13 inch equipped with a webcam.
-The data was either stored locally or sent to a server.
+The data was stored locally.
 In addition to the behavioral data, we stored the webcam recording of the session for verification purposes.
@@
 The first analysis was focused on cross-cultural variation.
-Fixed effects in the model were age and target centrality (distance of the landing position from the center in pixel/SVG units).
-The latter term accounts for trial difficulty.
+Fixed effects in the model were age and target centrality (distance of the balloon’s landing position from the center in pixel/SVG units).
+The latter term accounts for trial difficulty (see below).
 Furthermore, we included participant as a random effect, with a random slope for target centrality.
-To assess cross-cultural variation, we compared three models.
-A null model without cultural setting as a predictor (`brms` notation: `imprecision ~ age + target_centrality + (target_centrality | participant)`), a model with cultural setting as a random intercept (`imprecision ~ age + target_centrality + (target_centrality | participant) + (target_centrality | community)`) and a model with cultural setting as a random intercept and an added random slope for age (`imprecision ~ age + target_centrality + (target_centrality | participant) + (age + target_centrality | community)`).
+To assess cross-cultural variation, we compared three models: a null model without cultural community as a predictor (`brms` notation: `imprecision ~ age + target_centrality + (target_centrality | participant)`), a model with cultural community as a random intercept (`imprecision ~ age + target_centrality + (target_centrality | participant) + (target_centrality | community)`), and a model with cultural community as a random intercept and an added random slope for age (`imprecision ~ age + target_centrality + (target_centrality | participant) + (age + target_centrality | community)`).
 Thus, the second model assumes that there is variation across cultures in average levels of precision and the third model assumes that there are additional cultural differences in the effect of age.
 
-As stated in the pre-registration, comparing these models could be problematic.
-Participants are fully nested within cultural setting.
+As stated in the preregistration , comparing these models could be problematic.
+Participants are fully nested within a cultural setting.
 If there was an effect of cultural setting, we would expect participant random intercepts to cluster by cultural setting.
-This clustering would appear whether or not cultural setting would be included in the model as a random effect or not -- the only difference would be if the participant random intercepts were estimated as a deviation from a grand intercept or a culture-specific one.
-Standard metrics such as `WAIC` or `LOO` would penalize the model with additional intercept for cultural setting for having additional parameters that do not help to improve predictive accuracy.
+This clustering would appear whether or not cultural community would be included in the model as a random effect or not -- the only difference would be if the participant random intercepts were estimated as a deviation from a grand intercept or a culture-specific one.
+Standard metrics such as `WAIC` or `LOO` would penalize the model with additional intercept for cultural community for having additional parameters that do not help to improve predictive accuracy.
 
-To get around this problem, we used a cross-validation procedure (see e.g., 6).
+To get around this problem, we used a cross-validation procedure [see e.g., @stengelin2023children].
 For each cultural setting, we randomly sampled a data set that was 5/6 the size of the full data set (training data).
@@
 
-The processing signatures were derived from the model proposed by [@prein2024variation].
-The model sees gaze following as social vector estimation.
+The processing signatures were derived from the model proposed by @prein2024variation.
+The model sees gaze following as form of social vector estimation.
 When following gaze, onlookers observe the location (and movement) of the pupil within the eye and estimate a vector emanating from the center of the eye through the pupil.
@@
 Individual differences are conceptualized as differences in the level of uncertainty.
-As a consequence, even though individuals use the same general process, they might differ in their absolute levels of precision.
+As a consequence, even though individuals are assumed to use the same general process, they might differ in their absolute levels of precision.
 
@@
 As stated above, the key signature prediction of the model is that precision decreases when the balloon lands further away from the center.
-To test this prediction, we fit a model predicting imprecision by age and target centrality with random intercepts for participant and community and random slopes for target centrality within participant and community (`imprecision ~ age + target_centrality + (target_centrality | participant) + (age + target_centrality | community)`).
-As stated above, the predictor target centrality captures the distance from the center so that a positive effect of target centrality (i.e.
-a positive estimate with a 95% CrI not overlapping with zero) would mean support for the processing signature.
+To test this prediction, we fit a model predicting imprecision by age and target centrality with random intercepts for participant and community and random slopes for target centrality within participant and age and target centrality within community (`imprecision ~ age + target_centrality + (target_centrality | participant) + (age + target_centrality | community)`).
+As stated above, the predictor target centrality captures the distance from the center so that a positive effect of target centrality (i.e., a positive estimate with a 95% CrI not overlapping with zero) would mean support for the processing signature.
 In addition, we visualized the data for each community and inspected the shape of the plot.
 
-The same pattern, however, also arises when participants ignore the agent's gaze completely and instead follow simple heuristics.
-When participants always touch the center of the screen, regardless of where the agent is looking, trials in which the balloon lands further away from the center have a higher imprecision.
+A similar pattern, however, also arises when participants ignore the agent's gaze completely and instead follow simple heuristics.
+When participants always touch the center of the screen, regardless of where the agent is looking, trials in which the balloon lands further away from the center have a higher imprecision (resembling a v-shape).
 When participants randomly touch a location on the screen -- again ignoring the agent's gaze -- the maximum imprecision for trials in which the balloon lands in the center is half the width of the screen.
-When the balloon lands on one of the far ends of the screen, the maximum imprecision is a full screen widths.
+When the balloon lands on one of the far ends of the screen, the maximum imprecision is a full screen width.
 Thus, across trials, the average imprecision is again higher when the balloon lands further away from the center, resulting in the same pattern as predicted by the model.
@@
 Thus, we implemented the gaze model along with the two alternative models in the probabilistic programming language `webppl` [@dippl].
-The way the gaze model predicts the participants behavior has been described above.
+The way the gaze model predicts the participants' behavior has been described above.
 The center bias model predicts a participant's touch by sampling from a Normal distribution around the center of the screen $P(x_c) \sim \mathcal{N}(960, 160)$ (960 is the x-coordinate of the center and 160 is the width of the balloon).
-The random guessing model predicts participant's touch by sampling from a uniform distribution over all possible locations: $P(x_c) \sim \mathcal{U}(0, 1920)$.
+The random guessing model predicts participant's touch by sampling from a uniform distribution over all possible locations that can be touched: $P(x_c) \sim \mathcal{U}(0, 1920)$.
 Information on the prior distributions for all model parameters can be found in the associated online repository.
@@
 These two variables were largely redundant and so we included only one of them in the model.
-We chose the availability of a touchscreen as a predictor because the task itself was presented on a touchscreen.
+We chose the availability of a touchscreen as a predictor because the task itself was presented on a touchscreen and because there was more variation in this variable.
 
@@
 For a community-level perspective, we correlated the proportion of children with access to touchscreens with an age-corrected performance average for each community.
-To obtain the latter, extracted the random intercept estimates for community from the null model described above.
+To obtain the latter, we extracted the random intercept estimates for community from the null model described above.
 Because the model also includes age as a fixed effect, these values reflect variation between communities once differences in age have been accounted for.
@@
 
-There were marked differences between communities (see Figure \@ref(fig:fig2)A).
+There were marked differences in imprecision between communities (see Figure \@ref(fig:fig2)A).
 The cross-validation procedure found that a model assuming cross-cultural variation in average performance as well as developmental trajectories outperformed simpler models in `r round(mean(cv_cult$m3_beats_m1),2)*100`% (no variation in developmental trajectories) and `r round(mean(cv_cult$m3_beats_m2),2)*100`% (no variation between communities at all) of cases, respectively.
-Nevertheless, average differences in precision between communities were small compared to differences between individuals: communities did not form homogeneous clusters but largely overlapping distributions in that some individuals from communities with a lower average level of precision performed better compared to some individuals from a setting with a very high average level of precision.
+Nevertheless, average differences in precision between communities were small compared to differences between individuals: communities did not form homogeneous clusters but largely overlapping distributions in that some individuals from communities with a lower average level of precision performed better compared to some individuals from a community with a very high average level of precision.
 Similarly, in all communities, some 4-year-olds outperformed children two years older than them (see Figure \@ref(fig:fig2)A).
@@
 Next, we investigated developmental gains, that is, the extent to which children become more precise at estimating the target location with age.
-Across all 17 communities, we found a substantial increase in average levels of precision with age (fixed effect of age: $\beta$ = `r post_fix%>%filter(term == "ageinyears")%>%pull(Estimate)`, 95% Credible Interval (CrI) (`r post_fix%>%filter(term == "ageinyears")%>%pull(Q2.5)` — `r post_fix%>%filter(term == "ageinyears")%>%pull(Q97.5)`); range of community-level (random) effects: $\beta_{min}$ = `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%tail(1)%>%pull(mean)`, 95% CrI (`r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%tail(1)%>%pull(lci)` — `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%tail(1)%>%pull(uci)`) to $\beta_{max}$ = `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%head(1)%>%pull(mean)`, 95% CrI (`r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%head(1)%>%pull(lci)` — `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%head(1)%>%pull(uci)`)).
+Across all 17 communities, we found a substantial increase in average levels of precision (decrease in imprecision) with age (fixed effect of age: $\beta$ = `r post_fix%>%filter(term == "ageinyears")%>%pull(Estimate)`, 95% Credible Interval (CrI) (`r post_fix%>%filter(term == "ageinyears")%>%pull(Q2.5)` — `r post_fix%>%filter(term == "ageinyears")%>%pull(Q97.5)`); range of community-level (random) effects: $\beta_{min}$ = `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%tail(1)%>%pull(mean)`, 95% CrI (`r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%tail(1)%>%pull(lci)` — `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%tail(1)%>%pull(uci)`) to $\beta_{max}$ = `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%head(1)%>%pull(mean)`, 95% CrI (`r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%head(1)%>%pull(lci)` — `r post_agg%>%filter(type == "ageinyears")%>%arrange(mean)%>%head(1)%>%pull(uci)`)).
 
@@
 ```{r fig12, include = T, fig.align = "center", fig.cap = "Graphical illustration of the cognitive model.
-Individuals infer the target of an agent’s attention by estimating a vector based on the position of the pupils within the eyes.
+Individuals infer the target location of an agent’s attention by estimating a vector based on the position of the pupils within the eyes.
 This process is noisy, illustrated by the different vectors (transparent lines).
@@
 
-```{r}
-side_bias <- data%>%
-  mutate(side = ifelse(targetcenterx < 960, "left", "right"),
-         error = ifelse(clickdistfromtargetcenterx < 0, "left", "right"))%>%
-  group_by(side)%>%
-  summarise(left_bias = mean(error == "left"),
-            right_bias = mean(error == "right"))
-```
-
-Visualization of the data also showed the predicted u-shaped pattern in all communities (see Fig.
-\@ref(fig:fig2)B).
-The visualization also showed that the u is not symmetric.
-Instead, imprecision was higher when the target landed on the left side of the screen.
-
-To rule out alternative explanations, we compared the focal vector-based gaze estimation model described above to the alternative center bias and random guessing models, we found overwhelming support for the gaze estimation model (min $BF_{10}$ > 100 000 for comparisons with both alternative models, see Supplementary Materials) in every community.
+To rule out alternative explanations, we compared the focal gaze following model described above to the alternative center bias and random guessing models.
+We found overwhelming support for the gaze estimation model (min $BF_{10}$ > 100 000 for comparisons with both alternative models, see Supplementary Materials) in every community.
 
@@
 
-```{r}
-ptc_com <- readRDS("../saves/ptc_com.rds")
-
-pttest <- cor.test(ptc_com$Estimate, ptc_com$touchscreen)
-```
-
-```{r}
-pred_model_comp <- readRDS("../saves/model_comp.rds")%>%
-  mutate_if(is.numeric, format, digits = 2, nsmall = 2)%>%
-  select(model, elpd_diff, se_diff, waic, se_waic, value)%>%
-  mutate(model = recode(model, 
-                        bm_pred_null = "null",
-                        bm_pred_tc = "touchscreen",
-                        bm_pred_tc_hh = "household",
-                        bm_pred_tc_c = "children",
-                        bm_pred_tc_yc = "younger children",
-                        bm_pred_tc_rand = "touchscreen (by culture)"))
-```
-
 ## Predictors of variation
 
-```{r predcomptable, echo=F}
+```{r tab2, include = T}
 pred_model_comp <- readRDS("../saves/model_comp.rds")%>%
@@
 
-kableExtra::kable(pred_model_comp,
-             col.names = c("Model","diff\\textsubscript{WAIC}", "diff\\textsubscript{SE}", "WAIC", "SE\\textsubscript{WAIC}", "Weight"),
-             caption = "comparison of models predicting individual-level variation.",
-             format="latex", booktabs=TRUE, escape = F
-             )
-
+apa_table(pred_model_comp,
+          col.names = linebreak(c("Model","diff\\textsubscript{WAIC}", "diff\\textsubscript{SE}", "WAIC", "SE\\textsubscript{WAIC}", "Weight")),
+          caption = "Comparison of models predicting individual-level variation.",
+          #align = paste0("m{", 1/(ncol(tba1) + 1), "\\linewidth}"),
+          #longtable = TRUE,
+          escape=TRUE)
 ```
 
-The model comparison favored the model including touchscreen as a fixed effect (no variation between communities) with no additional predictors capturing aspects of household composition (see Table \@ref(tab:predcomptable)).
+The model comparison favored the model including touchscreen as a fixed effect (no variation between communities) with no additional predictors capturing aspects of household composition (see Table \@ref(tab:tab2)).
 Children with access to touchscreen devices had higher levels of precision ($\beta$ = `r pred_est%>%filter(term == "touchscreen")%>%pull(Estimate)`, 95% CrI = `r pred_est%>%filter(term == "touchscreen")%>%pull(Q2.5)` — `r pred_est%>%filter(term == "touchscreen")%>%pull(Q97.5)`).
@@
 
-Table \@ref(tab:predcomptable) shows that differences between models were small (`ELPD` < 1), suggesting that they were largely equivalent.
-For the sake of consistency, we also inspected the posterior estimates for household composition predictors, none of which had a 95% CrI excluding zero (household size: $\beta$ = `r pred_est_sc%>%filter(term == "household")%>%pull(Estimate)`, 95% CrI = `r pred_est_sc%>%filter(term == "household")%>%pull(Q2.5)` — `r pred_est_sc%>%filter(term == "household")%>%pull(Q97.5)`; children size: $\beta$ = `r pred_est_sc%>%filter(term == "children")%>%pull(Estimate)`, 95% CrI = `r pred_est_sc%>%filter(term == "children")%>%pull(Q2.5)` — `r pred_est_sc%>%filter(term == "children")%>%pull(Q97.5)`; younger children: $\beta$ = `r pred_est_sc%>%filter(term == "younger_children")%>%pull(Estimate)`, 95% CrI = `r pred_est_sc%>%filter(term == "younger_children")%>%pull(Q2.5)` — `r pred_est_sc%>%filter(term == "younger_children")%>%pull(Q97.5)`).
+Table \@ref(tab:predcomptable) shows that differences between models were small ($diff_{ELPD}$ < 1), suggesting that they were largely equivalent.
+For the sake of consistency, we also inspected the posterior estimates for household composition predictors, none of which had a 95% CrI excluding zero (household size: $\beta$ = `r pred_est_sc%>%filter(term == "household")%>%pull(Estimate)`, 95% CrI = `r pred_est_sc%>%filter(term == "household")%>%pull(Q2.5)` — `r pred_est_sc%>%filter(term == "household")%>%pull(Q97.5)`; no.
+of children: $\beta$ = `r pred_est_sc%>%filter(term == "children")%>%pull(Estimate)`, 95% CrI = `r pred_est_sc%>%filter(term == "children")%>%pull(Q2.5)` — `r pred_est_sc%>%filter(term == "children")%>%pull(Q97.5)`; younger children: $\beta$ = `r pred_est_sc%>%filter(term == "younger_children")%>%pull(Estimate)`, 95% CrI = `r pred_est_sc%>%filter(term == "younger_children")%>%pull(Q2.5)` — `r pred_est_sc%>%filter(term == "younger_children")%>%pull(Q97.5)`).
 
@@
 A substantial body of work has explored the developmental onset of gaze following in early infancy and in a few selected cultural communities [@moore2008development; @tang2023slow; @gredeback2010development; @byers2021development].
-The study reported here presents comparable data (i.e.
-collected via the same task with minimal superficial adjustments) on the development of gaze following in young children from 17 communities from five continents.
-We found substantial variation between cultural settings, both in average levels as well as the steepness of developmental trajectories.
+The study reported here presents comparable data (i.e., collected via the same task with minimal superficial adjustments for each community) on the development of gaze following in young children from 17 communities from five continents.
+We found substantial variation between cultural communitites, both in average levels as well as the steepness of developmental trajectories.
 In that, however, individual-level variation greatly outweighed community-level variation.
-Despite this variation, we found evidence that the basic process of gaze following is the same across communities: we found key performance signatures predicted by a model conceptualizing gaze following as a form of social vector estimation in all communities.
-Individual-differences in gaze following were related to children's exposure to touchscreens but not to aggregate measures of opportunities for social interaction (i.e.
-household composition).
+Despite community-level variation, we found evidence that the basic process of gaze following is the same across communities: we found key performance signatures in all communities, as predicted by a model conceptualizing gaze following as a form of social vector estimation.
+Individual differences in gaze following were related to children's exposure to touchscreens but not to aggregate measures of opportunities for social interaction (i.e., household composition).
 This study provides evidence for a putative universal in basic social cognition and presents a new approach to studying cognitive processing in light of cross-cultural and individual variation.
@@
 The task we used has good individual-level measurement properties across cultures [@prein2024measuring].
-This puts us in the position to contrast individual-level variability with community-level variability instead of dismissing the former as noise.
-The obvious pattern here was that cultural settings did not form homogeneous clusters but greatly overlapping distributions.
-That is, variation in the average developmental trajectories was small compared to variation between-individuals, both within communities and across them.
+This puts us in the position to contrast individual-level variability with community-level variation instead of dismissing the former as noise.
+The obvious pattern here was that cultural communitites did not form homogeneous clusters but greatly overlapping distributions.
+That is, variation in the average developmental trajectories was small compared to variation between individuals, both within communities and across them.
 Some individuals from the community with the highest average level of imprecision outperformed individuals from the community with the lowest average.
-Thus, the explanatory power of of community-level variables might be limited.
+Thus, the explanatory power of community-level variables might be limited.
 
@@
 rural divide in the data.
-Importantly, our sample included urban settings from the Global North and South so that geographic location and living conditions were only partly confounded (we did not collect data in rural settings in the Global North).
-Case in point is Namibia, where we collected data in both types of settings with results mirroring the overall pattern.
+Importantly, our sample included urban communitites from the Global North and South so that geographic location and living conditions were only partly confounded (we did not collect data in rural communitites in the Global North).
+Case in point is Namibia, where we collected data in both types of communitites with results mirroring the overall pattern.
 In previous work, such differences were often attributed to specific community-level differences in everyday experience that come with urbanization [e.g., @amir2020developmental; @mavridis2020development].
-However, correlations identified this way remain speculative because urban and rural settings differ in a myriad of ways.
+However, correlations identified this way remain speculative because urban and rural communitites differ in a myriad of ways.
 Furthermore, this approach neglects within-community variation in everyday experience [@bohn2024understanding].
 It is often chosen because the measures used are not suited to reliably quantify individual-level variation.
-Given the good measurement properties of our task and the individual-level assessment via the parental questionnaire, we were able to directly link aspects of experience and cognitive development, omitting the intermediate community-level.
+Given the good measurement properties of our task and the individual-level assessment via the parental questionnaire, we were able to directly link aspects of experience and cognitive development, omitting the intermediate community level.
 
@@
 Children with more touchscreen experience were probably better at task handling and thus more likely to precisely touch the location they inferred the agent to look at.
+However, children from all communities were accurate when touching visible targets during training trials [see @prein2024measuring].
 Importantly, the model comparison showed that this relation did not vary substantially across communities.
 The effect, however, did not explain all variation between individuals.
-For example, in Malatya (Türkiye) where 100% of children had access to touchscreens there was still substantial variation between individuals.
+For example, in Malatya (Türkiye) where 100% of children had access to touchscreens, there was still substantial variation between individuals.
 This strongly indicates that other factors likely contributed to individual differences.
@@
 This was not the case.
-Yet, this result does not provide strong evidence for the absence of a relation between social-interactional variables and the development of gaze following, instead, we think it suggests that a more fine-grained approach is necessary to identify the relevant aspects of social interaction.
+Yet, this result does not provide strong evidence for the absence of a relation between social-interactional variables and the development of gaze following.
+Instead, we think it suggests that a more fine-grained measurement is necessary to identify the relevant aspects of social interaction.
 
@@
 Alternative accounts for how this pattern might have arisen did not explain the data well.
-However, these alternative approaches did not present viable alternative theoretical accounts for how participants followed gaze and why they differed from one another because they assumed that participants ignore gaze altogether.
+However, these alternative approaches did not present viable alternative theoretical accounts for how participants followed gaze and why they differed from one another because they assumed that participants ignored gaze altogether.
 An alternative account involving the use of gaze cues would be that participants do not differ in the precision with which they estimate the gaze vector but that they differ only in the precision with which they touch the inferred location on the screen.
@@
 The fact that performance in the task was correlated with exposure to touchscreens might have overshadowed other sources of variation.
-However, we think it is in an important innovation that we were able to account for this effect.
+However, we think it is an important innovation that we were able to account for this effect.
 Most developmental cross-cultural studies do not even question the portability of their measurement instruments.
@@
 As mentioned above, the questionnaire items only offered a very coarse picture into children's actual lived experiences.
-Future work could increase the resolution with which everyday experiences in children from diverse communities are recorded to compare the drivers behind social-cognitive development as we observe it.
+Future work could increase the resolution with which everyday experiences in children from diverse communities are recorded to compare the drivers behind social-cognitive development.
 Recent work in the field of language acquisition has shown how technological innovations allowed for direct recording of social interactions across communities which can be used to close this explanatory gap [@bergelson2023everyday; @donnelly2021longitudinal].

### 2025-02-26 paper/paper.tex
add agent info to the data

@@
 \abstract{%
-Theoretical accounts assume that key features of human social cognition are universal.
-Here we focus on gaze following, the bedrock of social interactions and coordinated activities, to test this claim.
-In a comprehensive cross-cultural study spanning five continents and 17 distinct cultural communities, we examined the development of gaze following in early childhood.
-We identified key processing signatures through a computational model that assumes that participants follow an individual's gaze by estimating a vector emanating from the eye center through the pupil.
-We found these signatures in all communities, suggesting that children worldwide processed gaze in highly similar ways.
-Absolute differences between groups were accounted for by a cross-culturally consistent relationship between children's exposure to touchscreens and their performance in the task.
-These results provide strong evidence for a universal process underlying a foundational socio-cognitive ability in humans that can be reliably inferred even in the presence of cultural variation in overt behavior.
+Theoretical accounts typically assume, but rarely test, that key features of human socio-cognitive development are universal.
+This paper reports a comprehensive cross-cultural study (17 communities, five continents, N = 1377, 709 female, mean = 5.50 years ) on gaze following in early childhood.
+To test for universality, cognitive processing signatures were derived from a computational model treating gaze following as social vector estimation.
+Results showed substantial variation between communities and individuals.
+Importantly, the processing signature was found in all communities.
+Individual differences in performance were related to individual-level measures of familiarity with the data-collection device but not opportunities for social interaction.
+These results provide strong evidence for gaze following as a universal socio-cognitive process despite cultural variation in overt behavior.
 }
@@
 
-\begin{verbatim}
-## # A tibble: 2 x 3
-##   side  left_bias right_bias
-##   <chr>     <dbl>      <dbl>
-## 1 left      0.170      0.830
-## 2 right     0.754      0.246
-\end{verbatim}
-
 \hypertarget{introduction}{%
@@
 
-Human socio-cognitive skills enable unique forms of communication and cooperation that provide a bedrock for cumulative culture and the formation of complex societies (Henrich, 2016; Heyes, 2018; Laland \& Seed, 2021; Legare, 2019; Tomasello, 2020; Tomasello \& Rakoczy, 2003; Wellman, 2014).
-The eyes are the proverbial ``window to the mind'' and eye gaze is essential for many social reasoning processes (Doherty, 2006; Emery, 2000; Frischen et al., 2007; Shepherd, 2010).
+Human socio-cognitive skills enable unique forms of communication and cooperation that provide a bedrock for cumulative culture and the formation of complex societies (Henrich, 2016; Heyes, 2018; Laland \& Seed, 2021; Legare, 2019; Tomasello \& Rakoczy, 2003).
+Eye gaze is essential for many social reasoning processes, making the eyes the proverbial `'window to the mind'' (Doherty, 2006; Emery, 2000; Frischen et al., 2007; Shepherd, 2010).
 Others' eye gaze is used to infer their focus of visual attention, which is a critical aspect of coordinated activities, including communication and cooperation (Langton et al., 2000; Richardson \& Dale, 2005; Rossano, 2012; Scaife \& Bruner, 1975; Sebanz et al., 2006; Tomasello et al., 2007).
-During ontogeny, gaze following is an important aspect of many critical learning objectives that enable children to become functioning members of the society they grow up in, including language, social learning and joint action (Brooks \& Meltzoff, 2005; Brownell, 2011; Carpenter et al., 1998; Moore, 2008; Mundy \& Newell, 2007; Stephenson et al., 2021).
+During ontogeny, gaze following is an important aspect of many critical learning objectives that enable children to become functioning members of the society they grow up in, including language, social learning and cooperation (Brooks \& Meltzoff, 2005; Brownell, 2011; Carpenter et al., 1998; Moore, 2008; Mundy \& Newell, 2007; Stephenson et al., 2021).
 Because of the central role gaze following plays during human ontogeny, it has been widely argued that gaze following has been a target of natural selection (Clark et al., 2023; Emery, 2000; Kano, 2023; Tomasello et al., 2007).
@@
 
-\hypertarget{ontogeny-of-gaze-following}{%
-\subsection{Ontogeny of gaze following}\label{ontogeny-of-gaze-following}}
-
 The ability to follow gaze emerges early in development (Byers-Heinlein et al., 2021; Del Bianco et al., 2019; Gredebäck et al., 2010; Tang et al., 2023).
 The earliest signs of gaze following have been found in infants as young as four months (Astor et al., 2021; D'Entremont et al., 1997).
-Throughout the first two years of life, children refine their abilities: they interpret gaze in mentalistic terms (Butterworth \& Jarrett, 1991; Deák et al., 2000), for example, they follow gaze to locations outside their own visual field by moving around barriers (Moll \& Tomasello, 2004).
 Initially, children rely more on head direction than actual gaze direction (Michel et al., 2021).
-In fact, when head and gaze direction diverge, children fail to accurately locate the agent's focus of attention up until 19 months of age (Lempers, 1979).
+When head and gaze direction diverge, children often fail to accurately locate the agent's focus of attention up until 19 months of age (Lempers, 1979).
+Throughout the first two years of life, children refine their abilities: they begin to interpret gaze in mentalistic terms (Butterworth \& Jarrett, 1991; Deák et al., 2000), for example, they follow gaze to locations outside their own visual field by moving around barriers (Moll \& Tomasello, 2004).
 
@@
 In a recent study, Prein, Maurits, et al.
-(2024) studied the development of gaze following based on eye movements across from three years up until old age.
+(2024) studied the development of gaze following based on eye movements from three years up until old age.
 They found particularly steep developmental improvements in the preschool years resulting in a relatively stable level of accuracy from ten years onward and a slight decrease starting around age 40.
 
-The studies reported thus far, all relied on data collected in western affluent settings.
-Such settings represent only a minority of the worlds population and are thus insufficient to make claims about universal aspects of human cognition (Amir \& McAuliffe, 2020; Nielsen et al., 2017; Norenzayan \& Heine, 2005).
-Three studies with infants and children from traditionally underrepresented parts of the world (Bhutan, India, Peru, Vanuatu) find that children start gaze following (including head direction) at similar ages, the rates of gaze following, however, differed between cultural settings (Astor et al., 2022; Callaghan et al., 2011; Hernik \& Broesch, 2019).
-
-Rates and accuracy of gaze following do not just differ between cultural settings; there is also substantial variation within settings.
+The studies reported thus far, relied on data collected in western affluent communitites.
+Such communitites represent only a minority of the worlds population and are thus insufficient to make claims about universal aspects of human cognition and its development (Amir \& McAuliffe, 2020; Barrett, 2020; Nielsen et al., 2017; Norenzayan \& Heine, 2005).
+Three studies with infants and children from traditionally underrepresented regions (Bhutan, India, Peru, Vanuatu) find that even though children start gaze following (gaze and head direction combined) at similar ages, the rates of gaze following differ between cultural communitites (Astor et al., 2022; Callaghan et al., 2011; Hernik \& Broesch, 2019).
+
+Rates and accuracy of gaze following do not just differ between cultural communitites; there is also substantial variation within communitites.
 In fact, the pivotal role of gaze following in many uniquely human activities has been studied by relating individual differences in gaze following to other phenomena -- both cross-sectionally and longitudinally (Brooks \& Meltzoff, 2015; Carpenter et al., 1998).
-For example, gaze following at 10 months predicts language scores at 18 months of age (Brooks \& Meltzoff, 2005; see also Macdonald \& Tatler, 2013).
-Furthermore, difficulties with gaze following have been linked to developmental disorders, including Autism (Itier \& Batty, 2009; Thorup et al., 2016, 2018) and -- at least in some cultural contexts -- to maternal postpartum depression {[}astor2022maternal{]}.
-Individual differences are also key to explaining the -- mainly social-interactional -- driving forces behind the development of gaze following.
+For example, gaze following at 10 months predicts language scores at 18 months of age (Brooks \& Meltzoff, 2005; Macdonald \& Tatler, 2013).
+Furthermore, difficulties with gaze following have been linked to developmental disorders, including Autism (Itier \& Batty, 2009; Thorup et al., 2016) and -- at least in some cultural contexts -- to maternal postpartum depression (Astor et al., 2022).
+Individual differences are also key to explaining the driving forces behind the development of gaze following.
 For example, it has been found that early attachment quality or the use of gaze in communicative interactions predict later rates of gaze following (Astor et al., 2020; Movellan \& Watson, 2002; Senju et al., 2015).
 
-\hypertarget{cognitive-universals-and-sources-of-variation}{%
-\subsection{Cognitive universals and sources of variation}\label{cognitive-universals-and-sources-of-variation}}
-
-The existence of variation in gaze following both within and between cultural settings raises the question of how to square these findings with the suggestion that gaze following is a fundamental building block of human social cognition and interaction and that eye movements are processed the same way in humans all over the world.
-Looking at other aspects of social cognition, one could easily make the argument that variation is the norm rather than the exception (Dixson et al., 2018; Mayer \& Träuble, 2013; see e.g., Miller et al., 2018; Taumoepeau et al., 2019; Wellman, 2014).
-As a first step, answering this question requires data from many different cultural settings.
-In a second step, however, we need to a way of detecting universal processes in such data.
-The traditional approach is to compare some sort of aggregate measure (mean level of performance, average age of onset) across cultural settings.
-Absolute differences in mean performance across communities are interpreted as a signal of different underlying cognitive processes (Blake et al., 2015; see e.g., House et al., 2020; Kanngiesser et al., 2022; Van Leeuwen et al., 2018).
-No differences seemingly support the existence of a psychological universal.
-Such an approach, however, neglects the existence of within-cultural variation altogether (see also Gurven, 2018).
-
-In the present study, we want to take a different approach for which we assume that universal processes and variation can co-exist (Greenfield et al., 2003; Jensen, 2012; Kline et al., 2018).
-Instead of starting with the outcome (performance in the task), we start with the process that generates the outcome.
-By defining this process, we make a proposal for the universal aspect of the process.
-At the same time, we define variable aspects in the process that generate individual differences.
-This allows us to define signatures that the process leaves behind that can be detected independent of absolute levels of performance.
-
-For gaze following, we can use the computational model proposed by Prein, Maurits, et al.
-(2024) to derive such predictions.
-They formalized the widely-held view that gaze following involves estimating a vector emanating from the eye center through the pupil (Butterworth \& Jarrett, 1991; Symons et al., 2004; Todorović, 2006; Yaniv \& Shatz, 1990).
-The key innovation of the model is that it explains how individuals may use the same process but still differ in their measured abilities.
-The process always involves estimating a vector but also involves a degree of uncertainty because the eye center is not directly observable.
-Individuals are assumed to differ in their level of uncertainty with which they estimate the vector which causes differences in their observable behavior.
-Importantly, the assumed process leaves a key signature in the data that is observable independent of the absolute level of performance.
-In the present study, we therefore focus on this signature instead of absolute levels of performance when evaluating the claim whether there is evidence for a universal cognitive process underlying gaze following.
+The existence of variation in gaze following both within and between cultural communities raises the question of how to square these findings with the suggestion that gaze following is a fundamental building block of human social cognition and interaction and that humans all over the world process eye movements in the same way.
+Looking at other areas of social cognition, one could easily make the argument that variation is the norm rather than the exception (see e.g., Dixson et al., 2018; Kaminski et al., 2024; Mayer \& Träuble, 2013; Miller et al., 2018; Stengelin et al., 2020, 2024; Taumoepeau et al., 2019).
+As a first step, answering this question requires data from many different cultural communitites.
+In a second step, however, we need a way of detecting potential universal processing signatures in such data.
+Aggregate measures (e.g., mean level of performance, average age of onset) are often compared across cultural communities and absolute differences between communities are interpreted as a signal of different underlying cognitive processes while no differences are taken to support the existence of a psychological universal (Blake et al., 2015; House et al., 2020; Kanngiesser et al., 2022; Van Leeuwen et al., 2018).
+Such an approach -- while helpful in broadly mapping cross-cultural variation and similarities -- cannot account for potential within-cultural variation (see also Gurven, 2018).
+
+In the present study, we take a different approach that assumes the potential for universal processes and variation to co-exist (Greenfield et al., 2003; Jensen, 2012; Kline et al., 2018).
+Instead of starting with the outcome (performance in the task), we begin with the process that generates the outcome and propose universal signatures.
+At the same time, we define how individuals may differ from one another when using the process.
+This allows us to define signatures that the process leaves behind in the data that can be detected independent of individual-level or cross-cultural variation in absolute performance.
+
+The computational model proposed by Prein, Maurits, et al.
+(2024) can be used to derive such predictions for gaze following.
+They formalized the widely-held view that gaze following involves estimating a line-of-sight vector emanating from the eye center through the pupil (Butterworth \& Jarrett, 1991; Todorović, 2006; Yaniv \& Shatz, 1990).
+The key innovation of the model is that it explains how the same underlying process can produce different behavioral outcomes.
+The process always involves estimating a vector with a variable degree of uncertainty because the eye center is not directly observable.
+Individuals are assumed to differ in their level of uncertainty when estimating the vector which causes differences in their observable behavior.
+Importantly, this general vector estimation process emerges as a key signature in the data that is detectable independent of the absolute level of performance.
+In the present study, we therefore focus on this signature instead of absolute levels of performance when evaluating whether there is evidence for a universal cognitive process underlying gaze following.
 
@@
 First, to collect a comprehensive data set and study the ontogeny of gaze following beyond infancy across cultures.
-To make this possible, we used a semi-standardized task that required minimal assistance from an experimenter and no behavioral coding.
+To make this possible, we used a semi-standardized task that required minimal assistance from an experimenter and no behavioral coding {[}TANGO-CC; Prein, Bednarski, et al.
+(2024){]}.
 The task is an animated picture book presented on a tablet screen.
@@
 The key dependent variable was (im)precision, that is, the deviation between where the agent looked (where the balloon was) and the child's response.
-The task's flexible implementation as a browser-based web-app allowed us to quickly tailor its visual and audio content to each cultural setting (visuals and audio).
-The task has been psychometrically evaluated and has shown to yield reliable individual-level measurements across communities and across ages (Prein, Kalinke, et al., 2024; Prein, Bednarski, et al., 2024).
-
-We collected data in 17 different communities across 14 countries and five continents.
+The task's flexible implementation as a browser-based web-app allowed us to quickly tailor its visual and audio content to each cultural community (visuals and audio).
+Adaptations were made by researchers or research assistants from the respective community.
+The task has been psychometrically evaluated and has shown to yield reliable individual-level measurements across communities and ages (Prein, Kalinke, et al., 2024; Prein, Bednarski, et al., 2024).
+Furthermore, it has been validated in a German sample predicting language abilities six months later and correlating with conventional real-life perspective taking tasks (Prein, Kalinke, et al., 2024, 2024; Prein, Maurits, et al., 2024).
+
+We collected data in 17 different communities across 14 countries and five continents (see Figure \ref{fig:fig1}A).
 Communities covered a broad spectrum of geographical locations, social and political systems, languages, and subsistence styles.
 This diversity allowed us to overcome a common pitfall of cross-cultural studies that compare urban communities from the Global North to rural communities from the Global South (Barrett, 2020).
-We aimed for large sample sizes within each community to contrast within- and between cultural variation.
+We aimed for large sample sizes within each community (n = 20 per year) to contrast within- and between cultural variation.
 Our expectation regarding the first goal was to see substantial variation across cultures but even more variation between individuals.
-In all communities, we expected performance to increase with age.
-
-The second goals was to look for signatures in the data of the universal gaze following process predicted by the model of Prein, Bednarski, et al.
+In all communities, we expected performance to improve with age.
+
+The second goal was to look for signatures in the data of the universal gaze following process specified by the model of Prein, Maurits, et al.
 (2024).
-In the task, the hidden object is located on a horizontal plane at the lower end of the screen.
+In the task, the hidden object lands on a horizontal plane at the lower end of the screen.
 The agent is located in the upper center of the screen (see Figure \ref{fig:fig1}B).
-The model predicts trials in which the object is hidden further away from the center to be more difficult resulting in higher imprecision.
+The model predicts trials in which the object is hidden further away from the center to be more difficult, resulting in higher imprecision.
 The signature is thus a u-shaped relation between object location and imprecision (Figure \ref{fig:fig12}).
@@
 Finally, we sought to explain individual differences in gaze following precision by linking them to methodological aspects of the study as well as aggregate measures of children's everyday social experience.
-Experience with tablets and touch screens co-varied with community and we expected children more familiar with this medium to perform better.
+Experience with tablets and touch screens co-varied with community and we expected children more familiar with these devices to perform better on tablet-based tasks.
 Previous work suggested that gaze following is refined in social interaction (Movellan \& Watson, 2002; Senju et al., 2015).
 To approximate social interaction, we asked parents to fill out a questionnaire about household size and composition.
-We acknowledge that this measure approximates opportunities for social interaction in a rather crude way but we nevertheless expected children living in larger households and with more siblings (relative to their community) to be more accurate when following gaze.
+We acknowledge that this measure approximates opportunities for social interaction in a rather coarse way but we nevertheless expected children living in larger households and with more siblings (relative to their community) to be more accurate when following gaze.
 
 \begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{../figures/fig1_2}
-
-}
-
-\caption{(A) Data collection sites.
+\includegraphics[width=1\linewidth]{../figures/fig1_2} \caption{(A) Data collection sites.
 Points show the approximate geographical location of the data collection sites, coloring shows the sample sizes.
 (B) Screenshots from the task.
-The upper scene depicts the start, and the lower scene depicts the choice phase in a test trial.
+The lower scene depicts the choice phase in a test trial.
 Participants had to use the gaze of the agent to locate the balloon and touch the location on the hedge where they thought the balloon was.
 Agents, audio recordings and backgrounds were adapted to each community.
-(C) Drawings used as agents across communities.}\label{fig:fig1}
+(C) Drawings used as agents across communities.
+Adaptations were made by researchers or research assistants from the respective community.}\label{fig:fig1}
 \end{figure}
@@
 
-We used an animated picture book tablet task in which participants had to locate a hidden object based on observing an agent's gaze.
-Children watched a balloon disappear behind a hedge.
-An agent followed the trajectory of the balloon with their eyes (Fig.
-\ref{fig:fig1}B).
-The key dependent variable was the (im)precision with which children located the agent's focus of attention, that is, the deviation between where the agent looked (where the balloon was) and the child's response.
-We adapted visuals and audio instructions specifically for each of the 17 communities.
-Previous work demonstrated excellent individual-level measurement properties for this task in a German sample (Prein, Kalinke, et al., 2024).
-
 \hypertarget{methods}{%
 \section{Methods}\label{methods}}
+
+The study obtained ethical clearance from the MPG Ethics Commission in Munich, Germany, falling under an umbrella ethics application (Appl. No.~2021\_45).
 
@@
 We achieved this goal for most ages in most communities, but not for all (see Supplementary Table 1).
-The analysis reported here deviated from the preregistration in the following ways: In the pre-registration, in the regression models, we did not include random slopes for target centrality (i.e.~the distance of the location where the balloon landed from the center of the screen), neither within subject nor within cultural setting.
-Instead, we included random slopes for trial within subject.
-We decided to change this and remove random slopes for trial but include them for target centrality because trial effects in the sense of learning across trials were unlikely because participants did not receive differential feedback.
+For some communities, we also included older and younger children.
+The analysis reported here deviated from the preregistration in the following ways: In the preregistration, the regression models did not include random slopes for target centrality (i.e., the distance between the location where the balloon landed and the center of the screen), neither within subject nor within cultural setting.
+Instead, the preregistration included random slopes for trial within subject.
+We decided to remove random slopes for trial but include them for target centrality because trial effects in the sense of learning across trials were unlikely in the absence of differential feedback.
 Furthermore, multiple studies with the same task since the registration found no trial effects (Prein, Kalinke, et al., 2024; Prein, Maurits, et al., 2024).
 On the other hand, we included random slopes for target centrality to be able to look at cross-cultural variation.
-The cognitive models were not mentioned in the pre-registration because it is a more recent development (Prein, Maurits, et al., 2024).
+We preregistered to run the cross-validation 1000 times but decided to scale down to 100 times because the procedure was computationally very intensive and the results very clear.
+The cognitive models were not mentioned in the preregistration because they were developed more recently (Prein, Maurits, et al., 2024).
 
@@
 
-All study materials (\url{https://ccp-odc.eva.mpg.de/tango-cc/}), primary data and analysis scripts are publicly available (\url{https://github.com/ccp-eva/gafo-cc-analysis/}).
+All study materials (\url{https://ccp-odc.eva.mpg.de/tango-cc/}), primary data, and analysis scripts are publicly available (\url{https://github.com/ccp-eva/gafo-cc-analysis/}).
 
@@
 There were two types of training trials.
-In training 1 trials, the balloon fell down and landed in plain sight.
+In no-hedge training trials, the balloon fell down and landed in plain sight.
 Participants simply had to touch the visible balloon.
-In training 2 trials, the trajectory of the balloon was visible but it landed behind a small barrier (a hedge -- see Figure \ref{fig:fig1}B).
+In hedge training trials, the trajectory of the balloon was visible but it landed behind a small barrier (a hedge -- see Figure \ref{fig:fig1}B).
 Thus, participants needed to touch the hedge where they saw the balloon land.
@@
 They had to infer the location of the balloon based on the agent's gaze direction.
-During training 1, training 2 and the first test trial, children heard voice-overs commenting what happened on the screen.
+During training and the first test trial, children heard voice-overs commenting what happened on the screen.
 Critically, the agent was described as wanting to help the child and always looking at the balloon.
-
-Children completed one training 1, two training 2 trials and 16 test trials.
+These instructions were added to clarify the purpose of the task, establish a clear common ground, and minimize learning effects over trials.
+
+Children completed one no-hedge training, two hedge training trials and 16 test trials.
 We excluded the first test trial from the analysis because of the voice-over.
 Thus, 15 test trials were used in the analysis below.
-Each child saw eight different agents (four male, four female).
+Each child saw eight different agents (four male, four female; selected by local researchers or research assistants).
 The agent changed from trial to trial, with alternating genders.
@@
 The first analysis was focused on cross-cultural variation.
-Fixed effects in the model were age and target centrality (distance of the landing position from the center in pixel/SVG units).
-The latter term accounts for trial difficulty.
+Fixed effects in the model were age and target centrality (distance of the balloon's landing position from the center in pixel/SVG units).
+The latter term accounts for trial difficulty (see below).
 Furthermore, we included participant as a random effect, with a random slope for target centrality.
-To assess cross-cultural variation, we compared three models.
-A null model without cultural setting as a predictor (\texttt{brms} notation: \texttt{imprecision\ \textasciitilde{}\ age\ +\ target\_centrality\ +\ (target\_centrality\ \textbar{}\ participant)}), a model with cultural setting as a random intercept (\texttt{imprecision\ \textasciitilde{}\ age\ +\ target\_centrality\ +\ (target\_centrality\ \textbar{}\ participant)\ +\ (target\_centrality\ \textbar{}\ community)}) and a model with cultural setting as a random intercept and an added random slope for age (\texttt{imprecision\ \textasciitilde{}\ age\ +\ target\_centrality\ +\ (target\_centrality\ \textbar{}\ participant)\ +\ (age\ +\ target\_centrality\ \textbar{}\ community)}).
+To assess cross-cultural variation, we compared three models: a null model without cultural community as a predictor (\texttt{brms} notation: \texttt{imprecision\ \textasciitilde{}\ age\ +\ target\_centrality\ +\ (target\_centrality\ \textbar{}\ participant)}), a model with cultural community as a random intercept (\texttt{imprecision\ \textasciitilde{}\ age\ +\ target\_centrality\ +\ (target\_centrality\ \textbar{}\ participant)\ +\ (target\_centrality\ \textbar{}\ community)}), and a model with cultural community as a random intercept and an added random slope for age (\texttt{imprecision\ \textasciitilde{}\ age\ +\ target\_centrality\ +\ (target\_centrality\ \textbar{}\ participant)\ +\ (age\ +\ target\_centrality\ \textbar{}\ community)}).
 Thus, the second model assumes that there is variation across cultures in average levels of precision and the third model assumes that there are additional cultural differences in the effect of age.
 
-As stated in the pre-registration, comparing these models could be problematic.
-Participants are fully nested within cultural setting.
+As stated in the preregistration , comparing these models could be problematic.
+Participants are fully nested within a cultural setting.
 If there was an effect of cultural setting, we would expect participant random intercepts to cluster by cultural setting.
-This clustering would appear whether or not cultural setting would be included in the model as a random effect or not -- the only difference would be if the participant random intercepts were estimated as a deviation from a grand intercept or a culture-specific one.
-Standard metrics such as \texttt{WAIC} or \texttt{LOO} would penalize the model with additional intercept for cultural setting for having additional parameters that do not help to improve predictive accuracy.
-
-To get around this problem, we used a cross-validation procedure (see e.g., 6).
+This clustering would appear whether or not cultural community would be included in the model as a random effect or not -- the only difference would be if the participant random intercepts were estimated as a deviation from a grand intercept or a culture-specific one.
+Standard metrics such as \texttt{WAIC} or \texttt{LOO} would penalize the model with additional intercept for cultural community for having additional parameters that do not help to improve predictive accuracy.
+
+To get around this problem, we used a cross-validation procedure (see e.g., Stengelin et al., 2023).
 For each cultural setting, we randomly sampled a data set that was 5/6 the size of the full data set (training data).
@@
 
-The processing signatures were derived from the model proposed by (Prein, Maurits, et al., 2024).
-The model sees gaze following as social vector estimation.
+The processing signatures were derived from the model proposed by Prein, Maurits, et al.
+(2024).
+The model sees gaze following as form of social vector estimation.
 When following gaze, onlookers observe the location (and movement) of the pupil within the eye and estimate a vector emanating from the center of the eye through the pupil.
@@
 \ref{fig:fig12}).
-
-In the following, we give a brief mathematical description of the model. The model inversely models the process generating touches on the screen based on observed eye movements and is defined as:
-
-\begin{equation}
-    P(\theta | x_c, \alpha_l, \alpha_r) \propto P(x_c | \alpha_l, \alpha_r, \theta)P(\theta)
-\end{equation}
-
-Here, \(\theta\) represents an individual's level of precision in locating the focus of the agent's attention, \(x_c\) represents the touched coordinate, and \(\alpha_l\) and \(\alpha_r\) correspond to the left and right pupil angles (each defined as the angle between a line connecting the center of the eye to the pupil and a line extended vertically downward from the center of the eye).
-
-The basic assumption in this model is that participants touch on the screen location where they think the agent is looking.
-The true eye angles (\(\alpha_l\) and \(\alpha_r\)) are not directly observable and are estimated with noise, yielding \(\hat{\alpha_l}\) and \(\hat{\alpha_r}\).
-
-Each touch \(x_c\) implies a ``matched pair'' of estimated pupil angles \(\hat{\alpha_l}\) and \(\hat{\alpha_r}\), with the constraint that the lines extended along those two angles meet at the precise location of where the target is believed to be.
-As a consequence, we can rewrite the likelihood function of the model as:
-
-\begin{equation}
-P(x_c | \alpha_l, \alpha_r, \theta) \propto P(\hat{\alpha_l}, \hat{\alpha_r} | \alpha_l, \alpha_r, \theta) P(x_c)
-\end{equation}
-
-\(P(x_c)\) is a prior over potential target locations.
-Because the target was last visible in the screen and because the agent was located in the center, we assumed that participants have an a priori expectation that the target will land closer to the middle.
-We estimated the strength of this center bias (i.e., the standard deviation of a Normal distribution around the screen center) based on the data: \(P(x_c) \sim \mathcal{N}(960, \sigma^p)\).
-
-The primary inferential task for participants is therefore to estimate the pupil angles (\(\hat{\alpha_l}\) and \(\hat{\alpha_r}\)), that is, to sample from the term \(P(\hat{\alpha_l}, \hat{\alpha_r} | \alpha_l, \alpha_r, \theta)\).
-Here, we assumed that the pair of estimated pupil angles were sampled from a probability distribution which is the product of two Normal distributions of equal variance, \(\sigma_v\), centered on the true pupil angles:
-
-\begin{equation}
-P(\hat{\alpha_l}, \hat{\alpha_r} | \alpha_l, \alpha_r, \theta) \propto \phi(\hat{\alpha}_l ; \alpha_l, \sigma_v)\phi(\hat{\alpha}_r ; \alpha_r, \sigma_v),
-\end{equation}
-
-Thus, \(\sigma_v\) determines the level of accuracy with which participants estimated the pupil angles, and it is thus the component of the model that defines \(\theta\).
-Smaller values of \(\sigma_v\) result in a narrow distribution around the pupil angle, making touches far away from the target less likely.
-Conversely, larger values for \(\sigma_v\) lead to a wider distribution, making touches far away from the target more likely.
-To circle back to the analogy introduced above, \(\sigma_v\) corresponds to the width of the light beam.
-Thus, the goal of the model was to estimate participant-specific values for \(\sigma_v\): \(\sigma_{v_i}\).
-For more details on how \(\sigma_{v_i}\) was estimated, see the Supplementary Material.
-
-As stated above, the key signature prediction of the model is that precision decreases when the balloon lands further away from the center.
-To test this prediction, we fit a model predicting imprecision by age and target centrality with random intercepts for participant and community and random slopes for target centrality within participant and community (\texttt{imprecision\ \textasciitilde{}\ age\ +\ target\_centrality\ +\ (target\_centrality\ \textbar{}\ participant)\ +\ (age\ +\ target\_centrality\ \textbar{}\ community)}).
-As stated above, the predictor target centrality captures the distance from the center so that a positive effect of target centrality (i.e.~a positive estimate with a 95\% CrI not overlapping with zero) would mean support for the processing signature.
+In the Supplementary Material, we provide a mathematical description of the model.
+The key signature prediction of the model is thus that precision decreases when the balloon lands further away from the center.
+To test this prediction, we fit a model predicting imprecision by age and target centrality with random intercepts for participant and community and random slopes for target centrality within participant and age and target centrality within community (\texttt{imprecision\ \textasciitilde{}\ age\ +\ target\_centrality\ +\ (target\_centrality\ \textbar{}\ participant)\ +\ (age\ +\ target\_centrality\ \textbar{}\ community)}).
+As stated above, the predictor target centrality captures the distance from the center so that a positive effect of target centrality (i.e., a positive estimate with a 95\% CrI not overlapping with zero) would mean support for the processing signature.
 In addition, we visualized the data for each community and inspected the shape of the plot.
 
-The same pattern, however, also arises when participants ignore the agent's gaze completely and instead follow simple heuristics.
-When participants always touch the center of the screen, regardless of where the agent is looking, trials in which the balloon lands further away from the center have a higher imprecision.
+A similar pattern, however, also arises when participants ignore the agent's gaze completely and instead follow simple heuristics.
+When participants always touch the center of the screen, regardless of where the agent is looking, trials in which the balloon lands further away from the center have a higher imprecision (resembling a v-shape).
 When participants randomly touch a location on the screen -- again ignoring the agent's gaze -- the maximum imprecision for trials in which the balloon lands in the center is half the width of the screen.
-When the balloon lands on one of the far ends of the screen, the maximum imprecision is a full screen widths.
+When the balloon lands on one of the far ends of the screen, the maximum imprecision is a full screen width.
 Thus, across trials, the average imprecision is again higher when the balloon lands further away from the center, resulting in the same pattern as predicted by the model.
@@
 Thus, we implemented the gaze model along with the two alternative models in the probabilistic programming language \texttt{webppl} (Goodman \& Stuhlmüller, 2014).
-The way the gaze model predicts the participants behavior has been described above.
-The center bias model predicts a participant's touch by sampling from a Normal distribution around the center of the screen \(P(x_c) \sim \mathcal{N}(960, 160)\) (960 is the x-coordinate of the center and 160 is the width of the balloon).
-The random guessing model predicts participant's touch by sampling from a uniform distribution over all possible locations: \(P(x_c) \sim \mathcal{U}(0, 1920)\).
-Information on the prior distributions for all model parameters can be found in the associated online repository.
+A mathematical description of the alternative models can be found in the Supplementary Material.
 
@@
 
-There were marked differences between communities (see Figure \ref{fig:fig2}A).
+There were marked differences in imprecision between communities (see Figure \ref{fig:fig2}A).
 The cross-validation procedure found that a model assuming cross-cultural variation in average performance as well as developmental trajectories outperformed simpler models in 100\% (no variation in developmental trajectories) and 98\% (no variation between communities at all) of cases, respectively.
-Nevertheless, average differences in precision between communities were small compared to differences between individuals: communities did not form homogeneous clusters but largely overlapping distributions in that some individuals from communities with a lower average level of precision performed better compared to some individuals from a setting with a very high average level of precision.
+Nevertheless, average differences in precision between communities were small compared to differences between individuals.
+Communities did not form homogeneous clusters but largely overlapping distributions: some individuals from communities with a lower average level of precision performed better compared to some individuals from a community with a very high average level of precision.
 Similarly, in all communities, some 4-year-olds outperformed children two years older than them (see Figure \ref{fig:fig2}A).
@@
 Next, we investigated developmental gains, that is, the extent to which children become more precise at estimating the target location with age.
-Across all 17 communities, we found a substantial increase in average levels of precision with age (fixed effect of age: \(\beta\) = -0.30, 95\% Credible Interval (CrI) (-0.40 --- -0.21); range of community-level (random) effects: \(\beta_{min}\) = -0.06, 95\% CrI (-0.18 --- 0.05) to \(\beta_{max}\) = -0.59, 95\% CrI (-0.71 --- -0.48)).
+Across all 17 communities, we found a substantial increase in average levels of precision (decrease in imprecision) with age (fixed effect of age: \(\beta\) = -0.30, 95\% Credible Interval (CrI) (-0.40 --- -0.21); range of community-level (random) effects: \(\beta_{min}\) = -0.06, 95\% CrI (-0.18 --- 0.05) to \(\beta_{max}\) = -0.59, 95\% CrI (-0.71 --- -0.48)).
 
@@
 
+The key processing signature predicted by the cognitive model was that precision should decrease when the balloon landed further away from the center.
+This signature was clearly visible across all 17 communities (fixed effect for target centrality: \(\beta\) = 0.47, 95\% CrI (0.40 --- 0.54); range of community-level (random) effects: \(\beta_{min}\) = 0.58, 95\% CrI (0.51 --- 0.66) to \(\beta_{max}\) = 0.16, 95\% CrI (-0.01 --- 0.33)).
+
+To rule out alternative explanations, we compared the focal gaze following model described above to the alternative center bias and random guessing models.
+We found overwhelming support for the gaze estimation model (min \(BF_{10}\) \textgreater{} 100 000 for comparisons with both alternative models, see Supplementary Materials) in every community.
+
 \begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{../figures/fig1_3}
-
-}
-
-\caption{Graphical illustration of the cognitive model.
-Individuals infer the target of an agent’s attention by estimating a vector based on the position of the pupils within the eyes.
+\includegraphics[width=1\linewidth]{../figures/fig1_3} \caption{Graphical illustration of the cognitive model.
+Individuals infer the target location of an agent’s attention by estimating a vector based on the position of the pupils within the eyes.
 This process is noisy, illustrated by the different vectors (transparent lines).
@@
 
-The key processing signature predicted by the cognitive model was that precision should decrease when the balloon landed further away from the center.
-This signature was clearly visible across all 17 communities (fixed effect for target centrality: \(\beta\) = 0.47, 95\% CrI (0.40 --- 0.54); range of community-level (random) effects: \(\beta_{min}\) = 0.58, 95\% CrI (0.51 --- 0.66) to \(\beta_{max}\) = 0.16, 95\% CrI (-0.01 --- 0.33)).
-
-Visualization of the data also showed the predicted u-shaped pattern in all communities (see Fig.
-\ref{fig:fig2}B).
-The visualization also showed that the u is not symmetric.
-Instead, imprecision seemed to be higher when the target lands on the left side of the screen.
-
-To rule out alternative explanations, we compared the focal vector-based gaze estimation model described above to the alternative center bias and random guessing models, we found overwhelming support for the gaze estimation model (min \(BF_{10}\) \textgreater{} 100 000 for comparisons with both alternative models, see Supplementary Materials) in every community.
-
 \hypertarget{predictors-of-variation-1}{%
@@
 
-\begin{table}
-
-\caption{\label{tab:predcomptable}comparison of models predicting individual-level variation.}
-\centering
-\begin{tabular}[t]{llllll}
+\begin{center}
+\begin{ThreePartTable}
+
+\begin{longtable}{m{0.125\linewidth}m{0.125\linewidth}m{0.125\linewidth}m{0.125\linewidth}m{0.125\linewidth}m{0.125\linewidth}}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
+\caption{\label{tab:tab2}Comparison of models predicting individual-level variation.}\\
 \toprule
@@
 \midrule
+\endfirsthead
+\caption*{\normalfont{Table \ref{tab:tab2} continued}}\\
+\toprule
+Model & diff\textsubscript{WAIC} & diff\textsubscript{SE} & WAIC & SE\textsubscript{WAIC} & Weight\\
+\midrule
+\endhead
 touchscreen & 0.00 & 0.00 & 16935.74 & 71.16 & 0.43\\
@@
 touchscreen + children & -1.13 & 0.37 & 16938.00 & 71.16 & 0.00\\
-\addlinespace
 null & -4.32 & 3.63 & 16944.38 & 70.97 & 0.20\\
 \bottomrule
-\end{tabular}
-\end{table}
-
-The model comparison favored the model including touchscreen as a fixed effect (no variation between communities) with no additional predictors capturing aspects of household composition (see Table \ref{tab:predcomptable}).
+\end{longtable}
+
+\end{ThreePartTable}
+\end{center}
+
+The model comparison favored the model including touchscreen as a fixed effect (no variation between communities) with no additional predictors capturing aspects of household composition (see Table \ref{tab:tab2}).
 Children with access to touchscreen devices had higher levels of precision (\(\beta\) = -0.14, 95\% CrI = -0.21 --- -0.07).
@@
 
-Table \ref{tab:predcomptable} shows that differences between models were small (\texttt{ELPD} \textless{} 1), suggesting that they were largely equivalent.
-For the sake of consistency, we also inspected the posterior estimates for household composition predictors, none of which had a 95\% CrI excluding zero (household size: \(\beta\) = -0.01, 95\% CrI = -0.03 --- 0.02; children size: \(\beta\) = 0, 95\% CrI = -0.02 --- 0.02; younger children: \(\beta\) = 0.01, 95\% CrI = -0.01 --- 0.03).
+Table \ref{tab:tab2} shows that differences between models were small (\(diff_{ELPD}\) \textless{} 1), suggesting that they were largely equivalent.
+For the sake of consistency, we also inspected the posterior estimates for household composition predictors, none of which had a 95\% CrI excluding zero (household size: \(\beta\) = -0.01, 95\% CrI = -0.03 --- 0.02; no.
+of children: \(\beta\) = 0, 95\% CrI = -0.02 --- 0.02; younger children: \(\beta\) = 0.01, 95\% CrI = -0.01 --- 0.03).
 
@@
 A substantial body of work has explored the developmental onset of gaze following in early infancy and in a few selected cultural communities (Byers-Heinlein et al., 2021; Gredebäck et al., 2010; Moore, 2008; Tang et al., 2023).
-The study reported here presents comparable data (i.e.~collected via the same task with minimal superficial adjustments) on the development of gaze following in young children from 17 communities from five continents.
-We found substantial variation between cultural settings, both in average levels as well as the steepness of developmental trajectories.
-In that, however, individual-level variation greatly outweighed community-level variation.
-Despite this variation, we found evidence that the basic process of gaze following is the same across communities: We found key performance signatures predicted by a model conceptualizing gaze following as a form of social vector estimation process in all communities.
-Individual-differences in gaze following were related to children's exposure to touchscreens but not to aggregate measures of opportunities for social interactions (i.e.~household composition).
+The study reported here presents comparable data (i.e., collected via the same task with minimal superficial adjustments for each community) on the development of gaze following in young children from 17 communities from five continents.
+We found substantial variation between cultural communities, both in average levels as well as in the steepness of developmental trajectories.
+However, individual-level variation greatly outweighed community-level variation.
+Despite community-level variation, we found evidence that the basic process of gaze following is the same across communities: we found key performance signatures in all communities, as predicted by a model conceptualizing gaze following as a form of social vector estimation.
+Individual differences in gaze following were related to children's exposure to touchscreens but not to aggregate measures of opportunities for social interaction (i.e., household composition).
 This study provides evidence for a putative universal in basic social cognition and presents a new approach to studying cognitive processing in light of cross-cultural and individual variation.
 
-The task we used has good individual-level measurement properties across cultures (Prein, Bednarski, et al., 2024).
-This puts us in the position to contrast individual-level variability with community-level variability instead of dismissing the former as noise.
-The obvious pattern here was that cultural settings did not form homogeneous clusters but greatly overlapping distributions.
-That is, variation in the average developmental trajectories was small compared to variation between-individuals both within communities and across them.
-Some individuals from the community with the highest average level of imprecision outperformed individuals from the community with the lowest average.
-Thus, the explanatory power of of community-level variables might be limited.
-
-On the face of it, a community-level perspective on the results points to a urban vs.~rural split in the data.
-Importantly, our sample included urban settings from the global north and south so that geographic location and living conditions are only partly confounded (we did not collect data in rural settings in the global north).
-Case in point is Namibia, where we collected data in both types of settings with results mirroring the overall pattern.
-In previous work, such differences are often attributed to specific community-level differences in everyday experiences that come with urbanization (e.g., Amir et al., 2020; Mavridis et al., 2020).
-Correlations identified this way remain speculative because urbanization brings with it a whole suite of differences.
+Our task has good individual-level measurement properties across cultures (Prein, Bednarski, et al., 2024).
+This allowed us to contrast individual-level variability with community-level variation instead of dismissing the former as noise.
+The obvious pattern here was that cultural communities did not form homogeneous clusters but greatly overlapping distributions.
+That is, variation in the average developmental trajectories was small compared to variation between individuals, both within communities and across them.
+Some individuals from the community with the highest average level of imprecision (Nyabyeya, Uganda) outperformed individuals from the community with the lowest average (Pune, India).
+Thus, the explanatory power of community-level variables on gaze following in the current task remains limited.
+
+Nevertheless, a community-level perspective on the results points to a urban vs.~rural divide in the data.
+Importantly, our sample included urban communities from the Global North and South so that geographic location and living conditions were only partly confounded (we did not collect data in rural communities in the Global North).
+A case in point is Namibia, where we collected data in both clusters of communities with results mirroring the overall pattern.
+In previous work, such differences were often attributed to specific community-level differences in everyday experience that come with urbanization (e.g., Amir et al., 2020; Mavridis et al., 2020).
+However, correlations identified this way remain speculative because urban and rural communities differ in a myriad of ways.
 Furthermore, this approach neglects within-community variation in everyday experience (Bohn et al., 2024).
 It is often chosen because the measures used are not suited to reliably quantify individual-level variation.
-Given the good measurement properties of our task and the individual-level assessment via the parental questionnaire, we were able to directly link aspects of experience and cognitive development, omitting the intermediate community-level.
-
-We investigated both methodological and household composition as potential predictors.
+Given the good measurement properties of our task and the individual-level assessment via the parental questionnaire, we were able to directly link aspects of experience and cognitive development, omitting the intermediate community level.
+
+We investigated both methodological aspects and household composition as potential predictors.
 Familiarity with the device used for data collection explained variation between communities.
 Children with more touchscreen experience were probably better at task handling and thus more likely to precisely touch the location they inferred the agent to look at.
+However, children from all communities were accurate when touching visible targets during training trials (see Prein, Bednarski, et al., 2024).
 Importantly, the model comparison showed that this relation did not vary substantially across communities.
-This effect, however, did not explain all variation between individuals.
-For example, in Malatya (Türkiye) where 100\% of children had access to touchscreens there was still substantial variation between individuals.
+The effect, however, did not explain all variation between individuals.
+For example, in Malatya (Türkiye) where 100\% of children had access to touchscreens, there was still substantial variation between individuals.
 This strongly indicates that other factors likely contributed to individual differences.
@@
 Social-interactional variables have been linked to the development of gaze following in previous work (Astor et al., 2020; Movellan \& Watson, 2002; Senju et al., 2015).
-Thus, we predicted that opportunities for social interaction -- approximated by household size and composition -- while accounting for absolute differences and the prevalence of touchscreens, would be linked to performance in the task.
+Consequently, we predicted that opportunities for social interaction -- approximated by household size and composition -- would be linked to performance in the task while accounting for absolute differences and the prevalence of touchscreens.
 This was not the case.
-This result does not provide strong evidence for the absence of a relation between social-interactional variables and the development of gaze following, however, it suggests that a more granular approach is necessary to identify the relevant aspects of social interaction.
-The coarse approach taken here did not suffice.
-
-Despite substantial variation, we found the expected processing signatures in the data from all communities.
+Yet, this result does not provide strong evidence for the absence of a relation between social-interactional variables and the development of gaze following.
+Instead, we think it suggests that a more fine-grained measurement is necessary to identify relevant aspects of social interaction.
+
+Despite substantial variation, we found the expected processing signatures in all communities.
 Alternative accounts for how this pattern might have arisen did not explain the data well.
-These alternative approaches did not present viable alternative theoretical accounts for how participants followed gaze and why they differed from one another because they assumed that participants ignore gaze altogether.
+However, these alternative approaches did not present viable alternative theoretical accounts for how participants followed gaze and why they differed from one another because they assumed that participants ignored gaze altogether.
 An alternative account involving the use of gaze cues would be that participants do not differ in the precision with which they estimate the gaze vector but that they differ only in the precision with which they touch the inferred location on the screen.
@@
 
-An unexpected result was that imprecision seemed to be higher on the left compared to the right side of the screen.
-One candidate explanation for this pattern might be the dominance -- despite variation -- of right-handedness across cultures (Papadatou-Pastou et al., 2020).
-As of now, this is mere specualtion and future research should investigate the origins of this pattern in more detail.
-
-The study has further limitations.
+An unexpected result was that imprecision was higher on the left compared to the right side of the screen.
+One explanation for this pattern might be the dominance -- despite variation -- of right-handedness across cultures (Papadatou-Pastou et al., 2020).
+The study also has several limitations.
 The fact that performance in the task was correlated with exposure to touchscreens might have overshadowed other sources of variation.
-However, we think it is in an important innovation that we were able to account for this effect.
+However, we think it is an important innovation that we were able to account for this effect.
 Most developmental cross-cultural studies do not even question the portability of their measurement instruments.
 Importantly, the key result that the processing signatures were evident in all communities, is immune to this finding.
-The potential that lies in the precise individual-level measurement that our task achieves was largely unexploited.
-As mentioned above, the questionnaire items only offered a very coarse picture into children's actual lived experiences.
-Future work could increase the resolution with which everyday experiences in children from diverse communities are recorded to compare the drivers behind social-cognitive development as we observe it.
+The potential that lies in the precise individual-level measurement that our task achieved was largely unexploited.
+As mentioned above, the questionnaire items only offered a very coarse picture into children's actual lived experiences (Rogoff et al., 2018).
+Future work could increase the resolution with which everyday experiences in children from diverse communities are recorded to compare the drivers behind social-cognitive development.
 Recent work in the field of language acquisition has shown how technological innovations allowed for direct recording of social interactions across communities which can be used to close this explanatory gap (Bergelson et al., 2023; Donnelly \& Kidd, 2021).
 
-In sum, our work pioneers an approach that introduces computational modeling and precise individual-level measurement to the cross-cultural study of cognitive development.
-This approach allowed us to identify potential universals in the human cognitive architecture rather than just overt behavior.
-As such, it can serve as a blueprint for future research on a broad spectrum of cognitive abilities.
+In sum, our work pioneers an approach that combines computational modeling and precise individual-level measurement with the cross-cultural study of cognitive development.
+This approach allowed us to identify potential universals in the human cognitive architecture rather than just overt behavior and can serve as a blueprint for future research on a broad spectrum of cognitive abilities.
 Finally, the study provides a much-needed empirical foundation for theories on the nature of the human mind.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-kaminski2024understanding}{}}%
+Kaminski, J., Stengelin, R., Girndt, A., Haun, D., \& Liebal, K.
+(2024).
+Understanding others' preferences: A comparison across primate species and human societies.
+\emph{Plos One}, \emph{19}(1), e0295221.
+
 \leavevmode\vadjust pre{\hypertarget{ref-kanngiesser2022children}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-rogoff2018importance}{}}%
+Rogoff, B., Dahl, A., \& Callanan, M. (2018). The importance of understanding children's lived experience. \emph{Developmental Review}, \emph{50}, 5--15.
+
 \leavevmode\vadjust pre{\hypertarget{ref-rosati2009looking}{}}%
@@
 Shepherd, S. V. (2010). Following gaze: Gaze-following behavior as a window into social cognition. \emph{Frontiers in Integrative Neuroscience}, \emph{4}, 5.
+
+\leavevmode\vadjust pre{\hypertarget{ref-stengelin2023children}{}}%
+Stengelin, R., Ball, R., Maurits, L., Kanngiesser, P., \& Haun, D. B. (2023). Children over-imitate adults and peers more than puppets. \emph{Developmental Science}, \emph{26}(2), e13303.
+
+\leavevmode\vadjust pre{\hypertarget{ref-stengelin2020cultural}{}}%
+Stengelin, R., Hepach, R., \& Haun, D.
+B.
+(2020).
+Cultural variation in young children's social motivation for peer collaboration and its relation to the ontogeny of theory of mind.
+\emph{PloS One}, \emph{15}(11), e0242071.
+
+\leavevmode\vadjust pre{\hypertarget{ref-stengelin2024social}{}}%
+Stengelin, R., Petrović, L., Thiele, M., Hepach, R., \& Haun, D.
+B.
+(2024).
+Social reward predicts false belief understanding in namibian hai\textbar\textbar{} om children.
+\emph{Social Development}, e12767.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-symons2004you}{}}%
-Symons, L. A., Lee, K., Cedrone, C. C., \& Nishimura, M. (2004). What are you looking at? Acuity for triadic eye gaze. \emph{The Journal of General Psychology}, \emph{131}(4), 451.
-
 \leavevmode\vadjust pre{\hypertarget{ref-tang2023slow}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-thorup2018reduced}{}}%
-Thorup, E., Nyström, P., Gredebäck, G., Bölte, S., Falck-Ytter, T., \& Team, E.
-(2018).
-Reduced alternating gaze during social interaction in infancy is associated with elevated symptoms of autism in toddlerhood.
-\emph{Journal of Abnormal Child Psychology}, \emph{46}, 1547--1561.
-
 \leavevmode\vadjust pre{\hypertarget{ref-todorovic2006geometrical}{}}%
 Todorović, D. (2006). Geometrical basis of perception of gaze direction. \emph{Vision Research}, \emph{46}(21), 3549--3562.
-
-\leavevmode\vadjust pre{\hypertarget{ref-tomasello2020adaptive}{}}%
-Tomasello, M. (2020). The adaptive origins of uniquely human sociality. \emph{Philosophical Transactions of the Royal Society B}, \emph{375}(1803), 20190493.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-wellman2014making}{}}%
-Wellman, H. M. (2014). \emph{Making minds: How theory of mind develops}. Oxford University Press.
-
 \leavevmode\vadjust pre{\hypertarget{ref-yaniv1990heuristics}{}}%
